### 2017-03-15 notes.tex
Analysis using the new data.
A.0.0. The initial analysis contains plots for measures of the entire
data set. This was done to investigate if anything stands out.
The enviroments still look cooperative.

A.1. Is the analysis at the tournament level of different types.
Now we are ploting the transitions to C.

Everything is still in primary stage.

Last notebook contains the note to myself for
getting back.

The notes.tex contains some notes for the variables.

Overall look, on how cooperation affects performance. In the experiment that was help,
the meta data of given tournaments have been collected. The metadata include:

- cooperation rating $(C_{r})$
- median score
- rank $(r_{i})$
- wins
- cc_rate
- cd_rate
- dc_rate
- dd_rate
- noise
- probend
- repetitions
- seed
- size
- turns.

In this section we will rely on the rank to monitor the perfomance of the individuals within the tournaments and hopefully get some insights on our tournaments. More specificaly we will use the normalized rank $\bar{r_{i}} = \frac{r_{i}}{N_{i}}$, because there are different tournament sizes.

We will make use of some other mathematical representations as well, such as, the
index of the tournament $i$ and the number of players $N_{i}$.

### 2017-03-15 src/submit_meta_workers.sh

@@ -1,0 +1,5 @@
+qsub pbs/0-1999.pbs 
+qsub pbs/2000-3999.pbs 
+qsub pbs/4000-5999.pbs 
+qsub pbs/6000-7999.pbs 
+qsub pbs/8000-9999.pbs 

### 2018-04-05 main.tex
commit before re-running analysis

\documentclass{article}
\usepackage[margin=2.5cm, includefoot, footskip=30pt]{geometry}

\setlength{\parindent}{0em}
\setlength{\parskip}{1em}
\renewcommand{\baselinestretch}{1}

%%%%Packages%%%%
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{graphics}
\usepackage{multicol}
\usepackage{algorithm,algorithmic}
%%%%%%%%%%%%%%%%%

\setlength{\tabcolsep}{3pt}

\title{Applying modern data analysis techniques to tournament results of the
Iterated Prisoner's Dilemma.}
\date{}

\begin{document}

\maketitle

\section{The Prisoner's Dilemma}

The Prisoner's Dilemma is a two player repeated game commonly known in Game Theory
as the model of cooperative behaviour. Each of the players has two strategies,
to either cooperate (C) or defect (D). The decisions are made simultaneously
and independently. The normal form representation of the game is given by
matrix~\ref{matrix:pd}.

\begin{equation}\label{matrix:pd}
    \begin{bmatrix}
    (R,R) & (S,T)  \\
    (T,S) & (P,P)
    \end{bmatrix}
\end{equation}

where the payoffs \((R, P, S, T)\) are constrained by equations (\ref{eq:constrain_one})
and (\ref{eq:constrain_two}).

\begin{equation}\label{eq:constrain_one}
    T > R > P > S,
\end{equation}

\begin{equation}\label{eq:constrain_two}
    2R > T + S.
\end{equation}

In the one shot game the Nash equilibrium is given at (D, D) and both players
received a payoff of \(P\). Thus, at the point where both players defect.
In the repeated form of the game the behaviour becomes more complicated. The optimal
behaviour of a player in the repeated game, in the Iterated Prisoner's Dilemma,
has been the focus of research for years.

An interesting approach was introduced in 1980 by, where a computer tournament
was used to tackle the same question.

\begin{itemize}
    \item The definition of a strategy
    \item The definition of a tournament.
\end{itemize}

\section{Collecting data}

For performing a large number of computer tournaments the open source package
Axelrod Library is used in this work. The package was introduced in 2015,
it is written in the programming language Python and it allow us to perform
a number of tournaments with different strategies. The payoff values used in
Axelrod are \((3, 1, 0, 5)\) and the following type of tournaments have been performed.

There are several tournament types introduced in the literature that have not been
discussed.

\begin{enumerate}
    \item \textbf{Standard tournament}. A round robin tournament where
    the number of turns for each match can vary between 200 and 1. The tournament
    is repeated between 10 and 100 times.
    \item \textbf{Noisy tournament}. Similar to a standard tournament. A noisy
    tournament in a round robin tournament where noise is introduced. Noise is the
    probability that a players action is flipped. The probability of noise is
    ranging between 0 and 1.
    \item \textbf{Probabilistic ending tournament}. Similar to a standard tournament
    however in a probabilistic ending tournament the number of turns is not specified.
    There is a probability (ranges between 0 and 1) that the match will end in
    the next round. Probabilistic ending tournament will be referred to as
    probend hereupon.
    \item \textbf{Noisy and Probabilistic ending tournament}. A combination of
    noisy and probabilistic ending tournaments.
\end{enumerate}

The process for generating the data set is described by Algorithm~\ref{alg:tournaments}.
Every 20 iterations of a random seed a new sample is chosen. For each sample, for 20
repetitions random numbers of turns, repetitions of the tournament, the probability of
noise in the tournament and the probability of the game ending in after each interaction
are sampled.

For that set of parameters, four types of tournaments (as discussed above) are conducted.
A standard one, a noisy one, a probend one and lastly a probend with noise.

\begin{algorithm}
    \caption{Generating data}
    \label{alg:tournaments}
      \begin{algorithmic}[1]
        \FOR{seed \textbf{in} 10000}
            \IF{$seed \ mod \ 20 =0$}
                \STATE size $\gets$ random  size
                \STATE players $\gets$ random players
             \ELSE
                 \STATE turns $\gets$ random turns
                 \STATE repetitions  $\gets$  random  repetitions
                 \STATE noise  $\gets$ random  noise  probability
                 \STATE end  $\gets$  random end probability
                 \STATE standard results $\gets$ tournament(turns, players, repetitions) 
                 \STATE noise results $\gets$ tournament(turns, players, repetitions, noise)
                 \STATE probend results $\gets$ tournament(players, repetitions, end)
                 \STATE probend noise results $\gets$ tournament(players, repetitions, noise, end)
             \ENDIF
             \RETURN standard, noise, probend, probend noise results
        \ENDFOR
      \end{algorithmic}
\end{algorithm}

Once a tournaments is performed we export a summary of the performance
of each strategy in the tournament. In the following sections we discuss how we
manipulate the result set exported by Axelrod and hold a data analysis.

\section{Data preparation}

The data set used for the study is the combination of all of these summary data sets.
The structure of the data set is shown in Table~\ref{table:result_set}. Each row
represents a player in a given tournament.

Name is the name of the strategy. Stochastic, Memory depth and Use of arguments are
characteristics of the given strategy. The performance of the strategy is reflected
by columns Rate, Median score, Rank and Wins.

The environment and the type of tournaments are captured by columns Noise, Probend,
Repetitions, Size and Turns. Note that when turns are non given the tournament is a
probabilistic ending one, and vise versa. Similarly, when Noise argument in non given
the tournament is known to be standard. Finally, when both Noise and Probend are
non zero then the tournament is an probabilistic and noisy tournament

\begin{table}[htpb]
\centering
\resizebox{\columnwidth}{!}{%
\begin{tabular}{ccccccccccccccccccccccccccccccccc}
\toprule
% columns
Name & Stochastic & \multicolumn{1}{p{2cm}}{\centering Memory \\ depth} &
\multicolumn{1}{p{2cm}}{\centering Use of \\ game} &
\multicolumn{1}{p{2cm}}{\centering Use of \\ length} & CC rate &  CD rate &
\multicolumn{1}{p{2cm}}{\centering Cooperation \\rating} & DC rate & DD rate &
Median score &  Rank &  Wins &  Noise  &  Probend & Repetitions &  Seed & Size & Turns \\
\midrule
% first row
Adaptive & False & inf & True & False & 0.195 &  0.214 & 0.409 & 0.279 & 0.310 &
2.430 & 14 &  77.0 &  0.391 & NaN & 25.0 & 0.0 & 101.0 & 148.0 \\
% second row
Adaptive & False & inf & True & False & 0.783 & 0.194 & 0.928 & 0.012 & 0.009 &
2.292 & 88 & 5.0 &  0.391 & 0.370 & 25.0 & 0.0 & 101.0 & NaN \\
\bottomrule
\end{tabular}}
\caption{Result Set}
\label{table:result_set}
\end{table}

\begin{itemize}
    \item the cooperation in each environment
    \item show that got a uniform distribution of our parameters
\end{itemize}
In this work each tournament type is studied individually. An individual data set
containing the following information is constructed for each type.

\begin{multicols}{2}
    \begin{itemize}
        \item tournament index \(i\)
        \item tournament size \(N_{i}\)
        \item cooperation rating \((C_{r})\)
        \item rank \((r_{i})\)
        \item normalized rank \(\bar{r_{i}} = \frac{r_{i}}{N_{i}}\)
        \item maximum cooperation rating \(C^{*}_{r}\)
        \item minimum cooperation rating  \(\tilde{C_{r}}\)
        \item normalised rank of maximum cooperator \(\bar{r_{C}}\)
        \item normalised rank of minimum cooperator \(\bar{r_{D}}\)
        \item mean cooperation rating \(\bar{C_{r}}\)
        \item median cooperation rating \(\breve{C_{r}}\)
        \item \(C\) ratio of the winner \(C_{W}\)
        \item \(C\) ratio of the looser \(C_{L}\)
        \item standard deviation of the cooperating ratio \(\sigma\).
    \end{itemize}
    \end{multicols}

\section{Analysis}

\begin{itemize}
\item add \(r\) plots
\item some more plots
\end{itemize}
\end{document}

### 2019-05-08 paper/main.tex
clean repo

--- 2018-04-05 main.tex
@@
 \usepackage{algorithm,algorithmic}
+\usepackage{graphicx}
+\usepackage{subcaption}
 %%%%%%%%%%%%%%%%%
@@
 
-\section{The Prisoner's Dilemma}
+\section{Introduction}
 
-The Prisoner's Dilemma is a two player repeated game commonly known in Game Theory
-as the model of cooperative behaviour. Each of the players has two strategies,
-to either cooperate (C) or defect (D). The decisions are made simultaneously
-and independently. The normal form representation of the game is given by
-matrix~\ref{matrix:pd}.
+According to Charles Darwin’s theory of evolution~\cite{oldroyd1986}, natural
+selection is ruled by the survival of the fittest. However, in spite of all the
+`selfish genes` it is observed that in interactions both social and biological
+cooperation emerges. Individuals that cooperate more than other can even outperform
+their population. Thus the following question arises: why cooperation emerges;
+More over, how cooperative an individual must be to perform well in their respective
+environment.
+
+In the field of Game Theory the game of the Prisoner's Dilemma (PD) has been used
+to explain the emerge of cooperative behaviour. The PD is a \(2\) player game
+where both players have two strategies. They can either cooperate (C) or defect (D)
+with one another. Their decisions are made simultaneously and independently.
+
+The normal form representation of the game is given by matrix~\ref{matrix:pd}.
 
@@
 
-In the one shot game the Nash equilibrium is given at (D, D) and both players
-received a payoff of \(P\). Thus, at the point where both players defect.
-In the repeated form of the game the behaviour becomes more complicated. The optimal
-behaviour of a player in the repeated game, in the Iterated Prisoner's Dilemma,
-has been the focus of research for years.
+Constraint~\ref{eq:constrain_one} ensures that D dominates the first action C
+and constraint~\ref{eq:constrain_two} ensures that a social dilemma arises. That
+is because the sum of the utilities to both players is best when they both cooperate.
 
-An interesting approach was introduced in 1980 by, where a computer tournament
-was used to tackle the same question.
+Though not many insights can be gained from one shot game, complex behaviour that
+allow further investigation arise in the repeated form; in the Iterated Prisoner's
+Dilemma (IPD).
 
-\begin{itemize}
-    \item The definition of a strategy
-    \item The definition of a tournament.
-\end{itemize}
+In the 1980’s, a political scientist called Robert Axelrod carried out a computer
+tournament. Scholars from various disciplines were invited to submit strategies
+in computer code and they would compete in a round robin tournament where the
+strategy with the highest average score would be the winner. Axelrod’s tournament
+has been used to explain how cooperation can be evolutionarily advantageous.
+
+Strategies are a set of rules used to describe to a player how to play the IPD game.
+The research of computer tournaments includes studying the interactions of such
+strategies and the exploration of a strategy that dominates them all.
 
@@
 For performing a large number of computer tournaments the open source package
-Axelrod Library is used in this work. The package was introduced in 2015,
+Axelrod Library~\cite{axelrodproject} is used. The package was introduced in 2015,
 it is written in the programming language Python and it allow us to perform
-a number of tournaments with different strategies. The payoff values used in
+a number of different tournaments with different strategies. The payoff values used in
 Axelrod are \((3, 1, 0, 5)\) and the following type of tournaments have been performed.
@@
 
-The data set used for the study is the combination of all of these summary data sets.
-The structure of the data set is shown in Table~\ref{table:result_set}. Each row
-represents a player in a given tournament.
-
-Name is the name of the strategy. Stochastic, Memory depth and Use of arguments are
-characteristics of the given strategy. The performance of the strategy is reflected
-by columns Rate, Median score, Rank and Wins.
+Each tournaments exports a summary of the results. These are separated by tournament
+type. The structure of a single row of the results set is shown in
+Table~\ref{table:result_set}. Name is the name of the strategy. Stochastic,
+Memory depth and Use of arguments are characteristics of the given strategy.
+The performance of the strategy is reflected by columns Rate, Median score, Rank and Wins.
 
@@
 the tournament is known to be standard. Finally, when both Noise and Probend are
-non zero then the tournament is an probabilistic and noisy tournament
+non zero then the tournament is an probabilistic and noisy tournament.
 
@@
     2.430 & 14 &  77.0 &  0.391 & NaN & 25.0 & 0.0 & 101.0 & 148.0 \\
-% second row
-Adaptive & False & inf & True & False & 0.783 & 0.194 & 0.928 & 0.012 & 0.009 &
-2.292 & 88 & 5.0 &  0.391 & 0.370 & 25.0 & 0.0 & 101.0 & NaN \\
     \bottomrule
@@
 
-\begin{itemize}
-    \item the cooperation in each environment
-    \item show that got a uniform distribution of our parameters
-\end{itemize}
+Each types is explored separately. Figure~\ref{fig:cooperation_distributions} shows
+the distributions of the cooperation rating for each type. As suggested probabilistic
+ending tournaments are the most cooperative tournaments. Standard tournaments
+appear to be most cooperative as well and any tournament which includes noise
+the cooperation rating appears to follow a normalised distribution.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{images/cooperation_distribution_std}
+        \caption{Standard tournament type.}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{images/cooperation_distribution_noise}
+        \caption{Noise tournament type.}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{images/cooperation_distribution_probend}
+        \caption{Probend tournament type.}
+    \end{subfigure}
+    \begin{subfigure}{0.45\textwidth}
+        \includegraphics[width=\textwidth]{images/cooperation_distribution_noise_probend}
+        \caption{Noise Probend tournament type.}
+    \end{subfigure}
+    \caption{Cooperation rating distribution.}\label{fig:cooperation_distributions}
+\end{figure}
+
 In this work each tournament type is studied individually. An individual data set
@@
         \item tournament size \(N_{i}\)
-        \item cooperation rating \((C_{r})\)
-        \item rank \((r_{i})\)
-        \item normalized rank \(\bar{r_{i}} = \frac{r_{i}}{N_{i}}\)
         \item maximum cooperation rating \(C^{*}_{r}\)
         \item minimum cooperation rating  \(\tilde{C_{r}}\)
+        \item mean cooperation rating \(\bar{C_{r}}\)
+        \item median cooperation rating \(\breve{C_{r}}\)
+        \item standard deviation of the cooperating ratio \(\sigma\)
+        \item \(C\) ratio of the winner \(C_{W}\)
+        \item \(C\) ratio of the looser \(C_{L}\)
+        \item \(C\) to \(CC\) rate of the winner
+        \item \(C\) to \(CD\) rate of the winner
+        \item \(C\) to \(DC\) rate of the winner
+        \item \(C\) to \(DD\) rate of the winner
         \item normalised rank of maximum cooperator \(\bar{r_{C}}\)
         \item normalised rank of minimum cooperator \(\bar{r_{D}}\)
-        \item mean cooperation rating \(\bar{C_{r}}\)
-        \item median cooperation rating \(\breve{C_{r}}\)
-        \item \(C\) ratio of the winner \(C_{W}\)
-        \item \(C\) ratio of the looser \(C_{L}\)
-        \item standard deviation of the cooperating ratio \(\sigma\).
     \end{itemize}
@@
 
-\begin{itemize}
-\item add \(r\) plots
-\item some more plots
-\end{itemize}
+\bibliographystyle{plain}
+\bibliography{bibliography}
 \end{document}

### 2019-05-08 src/pbs_file_generator.py

@@ -1,3 +1,13 @@
+import os
+
+directory_name = 'pbs'
+ 
+try:
+    os.mkdir(directory_name)
+    print("Directory " , directory_name, " Created")
+except FileExistsError:
+    pass
+
 submit_script = ""
 for name, min_seed, max_seed in [("0-999", 0, 1000),
                                  ("1000-1999", 1000, 2000),
@@ -43,4 +53,6 @@ cd /home/c1569433/rsc/axlml/src
 
 with open("submit_meta_workers.sh", 'w') as f:
     f.write(submit_script)
+    print("File submit_meta_workers.sh Created")
+
 

### 2019-05-08 src/pbs_file_generator.py
clean repo

@@ -1,3 +1,13 @@
+import os
+
+directory_name = 'pbs'
+ 
+try:
+    os.mkdir(directory_name)
+    print("Directory " , directory_name, " Created")
+except FileExistsError:
+    pass
+
 submit_script = ""
 for name, min_seed, max_seed in [("0-999", 0, 1000),
                                  ("1000-1999", 1000, 2000),
@@ -33,4 +43,6 @@ cd /home/c1569433/rsc/axlml/src
 
 with open("submit_meta_workers.sh", 'w') as f:
     f.write(submit_script)
+    print("File submit_meta_workers.sh Created")
+
 

### 2019-05-08 src/submit_meta_workers.sh

@@ -1,5 +1,0 @@
-qsub pbs/0-1999.pbs 
-qsub pbs/2000-3999.pbs 
-qsub pbs/4000-5999.pbs 
-qsub pbs/6000-7999.pbs 
-qsub pbs/8000-9999.pbs 

### 2019-05-08 src/pbs_file_generator.py
rename files, run black and tweak code

@@ -1,24 +1,26 @@
 import os
 
-directory_name = 'pbs'
- 
+directory_name = "pbs"
+
 try:
     os.mkdir(directory_name)
-    print("Directory " , directory_name, " Created")
+    print("Directory ", directory_name, " Created")
 except FileExistsError:
     pass
 
 submit_script = ""
-for name, min_seed, max_seed in [("0-999", 0, 1000),
-                                 ("1000-1999", 1000, 2000),
-                                 ("2000-2999", 2000, 3000),
-                                 ("3000-3999", 3000, 4000),
-                                 ("4000-4999", 4000, 5000),
-                                 ("5000-5999", 5000, 6000),
-                                 ("6000-6999", 6000, 7000),
-                                 ("7000-7999", 7000, 8000),
-                                 ("8000-8999", 8000, 9000),
-                                 ("9000-9999", 9000, 10000)]:
+for name, min_seed, max_seed in [
+    ("0-999", 0, 1000),
+    ("1000-1999", 1000, 2000),
+    ("2000-2999", 2000, 3000),
+    ("3000-3999", 3000, 4000),
+    ("4000-4999", 4000, 5000),
+    ("5000-5999", 5000, 6000),
+    ("6000-6999", 6000, 7000),
+    ("7000-7999", 7000, 8000),
+    ("8000-8999", 8000, 9000),
+    ("9000-9999", 9000, 10000),
+]:
 
     pbs_file = """#!/bin/bash
 #PBS -q workq
@@ -34,15 +36,15 @@ export MPLBACKEND="agg"
 # Run std
 cd /home/c1569433/rsc/axlml/src
 /home/c1569433/anaconda3/envs/axlml/bin/python main.py /scratch/c1569433/axlml/data/ {} {} 
-""".format(name, name, name, min_seed, max_seed)
+""".format(
+        name, name, name, min_seed, max_seed
+    )
 
-    with open("pbs/{}.pbs".format(name), 'w') as f:
+    with open("pbs/{}.pbs".format(name), "w") as f:
         f.write(pbs_file)
 
     submit_script += "qsub pbs/{}.pbs \n".format(name)
 
-with open("submit_meta_workers.sh", 'w') as f:
+with open("submit_meta_workers.sh", "w") as f:
     f.write(submit_script)
     print("File submit_meta_workers.sh Created")
-
-

### 2019-05-08 src/prepare_data.py

@@ -1,0 +1,171 @@
+import glob
+import sys
+
+import pandas as pd
+
+import axelrod as axl
+
+
+def strategies_properties():
+    """
+     A function that returns a data frame with the strategies of the Axelrod
+     library and for each strategy it's property.
+    """
+    axl_strategies = pd.DataFrame(
+        columns=[
+            "Name",
+            "Stochastic",
+            "Memory_depth",
+            "Makes_use_of_game",
+            "Makes_use_of_length",
+        ]
+    )
+
+    for i, strategy in enumerate(axl.strategies):
+        use_of_game = False
+        use_of_length = False
+
+        if "game" in strategy().classifier["makes_use_of"]:
+            use_of_game = True
+        if "length" in strategy().classifier["makes_use_of"]:
+            use_of_length = True
+        axl_strategies.loc[i] = [
+            strategy().name,
+            strategy().classifier["stochastic"],
+            strategy().classifier["memory_depth"],
+            use_of_game,
+            use_of_length,
+        ]
+    return axl_strategies
+
+
+def get_parameters_data_frame(directory):
+    """
+    A function for reading in the parameters data frame.
+    """
+    csv_files = glob.glob("{}parameters_*-*.csv".format(directory))
+    dfs = (pd.read_csv(f) for f in csv_files)
+    df = pd.concat(dfs)
+    df = df[["noise", "probend", "repetitions", "seed", "size", "turns"]]
+
+    return df.sort_values(["seed"]).reset_index()
+
+
+class Reader:
+    """
+    A class for retrieving the four data frames corresponding to each
+    row of the parameters csv file.
+    """
+
+    def __init__(self, row, directory=None):
+        if directory:
+            self.directory = directory
+        else:
+            self.directory = "data/raw_data/"
+        self.seed = row.seed
+        self.size = row["size"]
+        self.repetitions = row.repetitions
+        self.noise_param = row.noise
+        self.probend_param = row.probend
+        self.turns_param = row.turns
+
+    def get_noise_df(self):
+        noise = pd.read_csv(
+            "{}noise-data/{}.csv".format(self.directory, int(self.seed))
+        )
+        noise["noise"] = self.noise_param
+        noise["turns"] = self.turns_param
+
+        return noise
+
+    def get_probend_noise_df(self):
+        probend_noise = pd.read_csv(
+            "{}noise-probend-data/{}.csv".format(self.directory, int(self.seed))
+        )
[…]

### 2019-05-08 src/main.py
rename files, run black and tweak code

@@ -34,7 +34,7 @@ except IndexError:
 try:
     min_seed, max_seed = map(int, sys.argv[2:])
 except IndexError:
-    min_seed, max_seed = 0, float('inf')
+    min_seed, max_seed = 0, float("inf")
 
 # Attempt to read directory to count number of tournaments that have been run
 try:
@@ -48,13 +48,13 @@ except ValueError:
     seed = min_seed
 
 try:
-    parameters_df = pd.read_csv("{}parameters_{}-{}.csv".format(directory,
-                                                                min_seed,
-                                                                max_seed))
+    parameters_df = pd.read_csv(
+        "{}parameters_{}-{}.csv".format(directory, min_seed, max_seed)
+    )
 except OSError:
-    parameters_df = pd.DataFrame(columns=["seed", "size",
-                                          "turns", "repetitions",
-                                          "noise", "probend"])
+    parameters_df = pd.DataFrame(
+        columns=["seed", "size", "turns", "repetitions", "noise", "probend"]
+    )
 while seed < max_seed:
 
     # Define parameter
@@ -71,36 +71,46 @@ while seed < max_seed:
         repetitions = random.randint(min_repetitions, max_repetitions)
         noise = random.random()
         prob_end = random.random()
-        df = pd.DataFrame([[seed, size, turns,
-                            repetitions, noise, prob_end] + players],
-                          columns=["seed", "size", "turns",
-                                   "repetitions", "noise", "probend"] +
-                                  ["player_{}".format(i) for i in range(size)])
+        df = pd.DataFrame(
+            [[seed, size, turns, repetitions, noise, prob_end] + players],
+            columns=["seed", "size", "turns", "repetitions", "noise", "probend"]
+            + ["player_{}".format(i) for i in range(size)],
+        )
         parameters_df = pd.concat([parameters_df, df], ignore_index=True)
 
         # Create the tournaments
         tournaments = []
-        tournaments.append(axl.Tournament(players, turns=turns,
-                                          repetitions=repetitions))
-        tournaments.append(axl.Tournament(players, turns=turns,
-                                          repetitions=repetitions, noise=noise))
-        tournaments.append(axl.Tournament(players, prob_end=prob_end,
-                                          repetitions=repetitions))
-        tournaments.append(axl.Tournament(players, prob_end=prob_end,
-                                          repetitions=repetitions, noise=noise))
+        tournaments.append(
+            axl.Tournament(players, turns=turns, repetitions=repetitions)
+        )
+        tournaments.append(
+            axl.Tournament(
[…]

### 2019-05-08 src/pbs_file_generator.py

@@ -1,34 +1,26 @@
 import os
 
-directory_name = 'pbs'
- 
+directory_name = "pbs"
+
 try:
     os.mkdir(directory_name)
-    print("Directory " , directory_name, " Created")
+    print("Directory ", directory_name, " Created")
 except FileExistsError:
     pass
 
 submit_script = ""
-for name, min_seed, max_seed in [("0-999", 0, 1000),
-                                 ("1000-1999", 1000, 2000),
-                                 ("2000-2999", 2000, 3000),
-                                 ("3000-3999", 3000, 4000),
-                                 ("4000-4999", 4000, 5000),
-                                 ("5000-5999", 5000, 6000),
-                                 ("6000-6999", 6000, 7000),
-                                 ("7000-7999", 7000, 8000),
-                                 ("8000-8999", 8000, 9000),
-                                 ("9000-9999", 9000, 10000),
-                                 ("10000-10999", 10000, 11000),
-                                 ("11000-21999", 11000, 12000),
-                                 ("12000-12999", 12000, 13000),
-                                 ("13000-13999", 13000, 14000),
-                                 ("14000-14999", 14000, 15000),
-                                 ("15000-15999", 15000, 16000),
-                                 ("16000-16999", 16000, 17000),
-                                 ("17000-17999", 17000, 18000),
-                                 ("18000-18999", 18000, 19000),
-                                 ("19000-19999", 19000, 20000)]:
+for name, min_seed, max_seed in [
+    ("0-999", 0, 1000),
+    ("1000-1999", 1000, 2000),
+    ("2000-2999", 2000, 3000),
+    ("3000-3999", 3000, 4000),
+    ("4000-4999", 4000, 5000),
+    ("5000-5999", 5000, 6000),
+    ("6000-6999", 6000, 7000),
+    ("7000-7999", 7000, 8000),
+    ("8000-8999", 8000, 9000),
+    ("9000-9999", 9000, 10000),
+]:
 
     pbs_file = """#!/bin/bash
 #PBS -q workq
@@ -44,15 +36,15 @@ export MPLBACKEND="agg"
 # Run std
 cd /home/c1569433/rsc/axlml/src
 /home/c1569433/anaconda3/envs/axlml/bin/python main.py /scratch/c1569433/axlml/data/ {} {} 
-""".format(name, name, name, min_seed, max_seed)
+""".format(
[…]

### 2019-05-08 src/plot.py

@@ -1,0 +1,81 @@
+import matplotlib.pyplot as plt
+import seaborn as sns
+import numpy as np
+
+c = sns.xkcd_rgb["denim blue"]
+
+
+def violin_plot(df, x, y, xlabel, ylabel, title, size=10):
+    join_plot = sns.jointplot(
+        x=x,
+        y=y,
+        data=df,
+        kind="reg",
+        stat_func=None,
+        xlim=(0, 1),
+        ylim=(0, 1),
+        scatter_kws={"s": size},
+    )
+
+    plt.subplots_adjust(top=0.95)
+    join_plot.fig.suptitle(title)
+    join_plot.set_axis_labels(xlabel, ylabel)
+
+    plt.show()
+    return join_plot
+
+
+def r_distribution(
+    x,
+    y1,
+    y2,
+    y3,
+    y4,
+    title,
+    label1="max",
+    label2="min",
+    label3="mean",
+    label4="median",
+):
+    rs = np.linspace(0, 1, 20)
+    fig, axes = plt.subplots(figsize=(6, 5))
+    axes.set_title(title)
+    axes.set_xlabel(r"$r$")
+    colormap = plt.cm.CMRmap
+    plt.gca().set_color_cycle([colormap(i) for i in np.linspace(0, 0.9, 4)])
+    plt.plot(rs, [sum(x >= r * y1) / len(x) for r in rs], label=label1)
+    plt.plot(rs, [sum(x >= r * y2) / len(x) for r in rs], label=label2)
+    plt.plot(rs, [sum(x >= r * y3) / len(x) for r in rs], label=label3)
+    plt.plot(rs, [sum(x >= r * y4) / len(x) for r in rs], label=label4)
+    plt.legend(loc=3)
+
+
+def r_distribution_mult_types(
+    x1,
+    x2,
+    x3,
+    x4,
+    y1,
+    y2,
+    y3,
+    y4,
+    title,
+    label1="standard",
+    label2="noisy",
+    label3="probend",
+    label4="noisy + probend",
+    filename="fig.pdf",
+):
+    rs = np.linspace(0, 1, 20)
+    fig, axes = plt.subplots(figsize=(6, 5))
+    axes.set_title(title)
+    axes.set_xlabel(r"$r$")
+    colormap = plt.cm.CMRmap
+    plt.gca().set_color_cycle([colormap(i) for i in np.linspace(0, 0.9, 4)])
[…]

### 2019-05-08 src/test_prepare_data.py
tests to pytest

@@ -1,0 +1,163 @@
+import prepare_data
+import axelrod
+import pandas
+import numpy as np
+
+
+def test_strategies_properties():
+    df = prepare_data.strategies_properties()
+
+    assert isinstance(df, pandas.DataFrame)
+    assert len(df) == len(axelrod.strategies)
+
+    for memory_depth in df["Memory_depth"]:
+        assert isinstance(memory_depth, float)
+
+    for use_of_game in df["Makes_use_of_game"]:
+        assert isinstance(use_of_game, bool)
+
+    for use_of_length in df["Makes_use_of_length"]:
+        assert isinstance(use_of_length, bool)
+
+
+def test_specific_strategy_properties():
+
+    df = prepare_data.strategies_properties()
+
+    tit_for_tat = df[df["Name"] == "Tit For Tat"]
+    assert tit_for_tat.Name.all() == "Tit For Tat"
+    assert tit_for_tat.Memory_depth.values[0] == 1.0
+    assert tit_for_tat.Stochastic.all() is False
+    assert tit_for_tat.Makes_use_of_game.all() == 0.0
+    assert tit_for_tat.Makes_use_of_length.all() == 0.0
+
+    adaptive = df[df["Name"] == "Adaptive"]
+    assert adaptive.Name.all() == "Adaptive"
+    assert adaptive.Memory_depth.values[0] == np.inf
+    assert adaptive.Stochastic.all() is False
+    assert adaptive.Makes_use_of_game.all() == 1.0
+    assert adaptive.Makes_use_of_length.all() == 0.0
+
+
+parameters_df = prepare_data.get_parameters_data_frame(
+    directory="data/raw_data/"
+)
+
+
+def test_parameters_data_frame():
+    assert isinstance(parameters_df, pandas.DataFrame)
+    assert len(parameters_df) == 13081
+
+
+def test_reader():
+    row = parameters_df.sample(n=1)
+    reader = prepare_data.Reader(row)
+
+    assert reader.noise_param.values[0] == row.noise.values[0]
+
+    assert reader.probend_param.values[0] == row.probend.values[0]
+    assert reader.seed.values[0] == row.seed.values[0]
+    assert reader.size.values[0] == row["size"].values[0]
+    assert reader.turns_param.values[0] == row.turns.values[0]
+
+
+def test_get_noise_df():
+    row = parameters_df.sample(n=1)
+    reader = prepare_data.Reader(row, "data/raw_data/")
+
+    noise = reader.get_noise_df()
[…]

### 2019-08-04 paper/main.tex
week commit

--- 2018-04-05 main.tex
@@
 \usepackage{multicol}
-\usepackage{algorithm,algorithmic}
+\usepackage[]{algorithm2e,setspace}
+\usepackage{graphicx}
+\usepackage{subcaption}
+\usepackage{hyperref}
+\usepackage{color,colortbl}
+\usepackage{array}
+\usepackage{booktabs}
+\usepackage{tabularx}
+\usepackage{wrapfig, blindtext}
 %%%%%%%%%%%%%%%%%
+
+\definecolor{Gray}{gray}{0.95}
+\usepackage[first=0,last=9]{lcg}
+\newcommand{\ra}{\rand0.\arabic{rand}}
 
@@
 
-\title{Applying modern data analysis techniques to tournament results of the
+\title{A meta analysis of tournaments and an evaluation of performance in the
 Iterated Prisoner's Dilemma.}
+\author{Nikoleta E. Glynatsi, Dr Vincent A. Knight}
 \date{}
@@
 
-\section{The Prisoner's Dilemma}
+\section{Abstract}
 
-The Prisoner's Dilemma is a two player repeated game commonly known in Game Theory
-as the model of cooperative behaviour. Each of the players has two strategies,
-to either cooperate (C) or defect (D). The decisions are made simultaneously
-and independently. The normal form representation of the game is given by
-matrix~\ref{matrix:pd}.
+The Iterated Prisoner's Dilemma has been used for decades as a powerful model of
+behavioural interactions. From the celebrated performance of Tit for Tat in the
+early computer tournaments, to the introduction of Pavlov and the use of
+sophisticated strategies such as neural networks, the literature has been
+exploring the performance of strategies in the iterated games for years. With
+the use of an open source package we now have access to most of these
+strategies. This paper conducts a meta analysis of a large number of tournaments
+and evaluates the performance of over 200 strategies from the literature.
 
-\begin{equation}\label{matrix:pd}
-    \begin{bmatrix}
-    (R,R) & (S,T)  \\
-    (T,S) & (P,P)
-    \end{bmatrix}
-\end{equation}
+\section{Background}
 
-where the payoffs \((R, P, S, T)\) are constrained by equations (\ref{eq:constrain_one})
-and (\ref{eq:constrain_two}).
+The Iterated Prisoner's Dilemma is a two players repeated game. At each turn a
+player chooses between cooperation (C) or defection (D) whilst the prior outcomes
+matters. The payoff at each given turn are defined by the matrix,
 
-\begin{equation}\label{eq:constrain_one}
-    T > R > P > S,
-\end{equation}
+\[\begin{pmatrix}
+R & S \\
+T & P
+\end{pmatrix}\]
 
-\begin{equation}\label{eq:constrain_two}
-    2R > T + S.
-\end{equation}
+where \(T > R > P > S\) and \(2R > T + S\).
 
-In the one shot game the Nash equilibrium is given at (D, D) and both players
-received a payoff of \(P\). Thus, at the point where both players defect.
-In the repeated form of the game the behaviour becomes more complicated. The optimal
-behaviour of a player in the repeated game, in the Iterated Prisoner's Dilemma,
-has been the focus of research for years.
+In the early 80's \textbf{literature review on strategies}.
 
-An interesting approach was introduced in 1980 by, where a computer tournament
-was used to tackle the same question.
+Type of tournaments, \textbf{literature review on types}, for example a standard
+tournament is a round robin tournament where the number of turns and the tournament
+is also repeated. A noisy tournament is similar to a standard tournament. A noisy
+tournament in a round robin tournament where noise is introduced. Noise is the
+probability that a players action is flipped.
 
-\begin{itemize}
-    \item The definition of a strategy
-    \item The definition of a tournament.
-\end{itemize}
-
-\section{Collecting data}
-
-For performing a large number of computer tournaments the open source package
-Axelrod Library is used in this work. The package was introduced in 2015,
-it is written in the programming language Python and it allow us to perform
-a number of tournaments with different strategies. The payoff values used in
-Axelrod are \((3, 1, 0, 5)\) and the following type of tournaments have been performed.
-
-There are several tournament types introduced in the literature that have not been
-discussed.
-
-\begin{enumerate}
-    \item \textbf{Standard tournament}. A round robin tournament where
-    the number of turns for each match can vary between 200 and 1. The tournament
-    is repeated between 10 and 100 times.
-    \item \textbf{Noisy tournament}. Similar to a standard tournament. A noisy
-    tournament in a round robin tournament where noise is introduced. Noise is the
-    probability that a players action is flipped. The probability of noise is
-    ranging between 0 and 1.
-    \item \textbf{Probabilistic ending tournament}. Similar to a standard tournament
+A probabilistic ending tournament. Similar to a standard tournament
 however in a probabilistic ending tournament the number of turns is not specified.
 There is a probability (ranges between 0 and 1) that the match will end in
-    the next round. Probabilistic ending tournament will be referred to as
-    probend hereupon.
-    \item \textbf{Noisy and Probabilistic ending tournament}. A combination of
-    noisy and probabilistic ending tournaments.
-\end{enumerate}
+the next round.
 
-The process for generating the data set is described by Algorithm~\ref{alg:tournaments}.
-Every 20 iterations of a random seed a new sample is chosen. For each sample, for 20
-repetitions random numbers of turns, repetitions of the tournament, the probability of
-noise in the tournament and the probability of the game ending in after each interaction
-are sampled.
+\textbf{Over time which strategies were defined as the best}
 
-For that set of parameters, four types of tournaments (as discussed above) are conducted.
-A standard one, a noisy one, a probend one and lastly a probend with noise.
+This manuscript accesses the performance of strategies. This is achieved
+by analysing a large data set containing results of the iterated prisoner's
+dilemma tournaments, which is archived in.
 
-\begin{algorithm}
-    \caption{Generating data}
-    \label{alg:tournaments}
-      \begin{algorithmic}[1]
-        \FOR{seed \textbf{in} 10000}
-            \IF{$seed \ mod \ 20 =0$}
-                \STATE size $\gets$ random  size
-                \STATE players $\gets$ random players
-             \ELSE
-                 \STATE turns $\gets$ random turns
-                 \STATE repetitions  $\gets$  random  repetitions
-                 \STATE noise  $\gets$ random  noise  probability
-                 \STATE end  $\gets$  random end probability
-                 \STATE standard results $\gets$ tournament(turns, players, repetitions) 
-                 \STATE noise results $\gets$ tournament(turns, players, repetitions, noise)
-                 \STATE probend results $\gets$ tournament(players, repetitions, end)
-                 \STATE probend noise results $\gets$ tournament(players, repetitions, noise, end)
-             \ENDIF
-             \RETURN standard, noise, probend, probend noise results
-        \ENDFOR
-      \end{algorithmic}
+The structure of this manuscript is as follows. In
+Section~\ref{section:data_collection} the data collection is covered. In
+Section~\ref{section:top_performances}, the best performed strategies for each
+type of tournament and overall are presented.
+Section~\ref{section:evaluation_of_performance}, explores the traits which
+contribute to good performance and finally in Section~\ref{section:conclusion}
+we conclude and summarise the results.
+
+\section{Data generating process}\label{section:data_collection}
+
+For the purposes of this manuscript a large data set containing results on
+iterate prisoner's dilemma tournaments has been generated. In this section
+the method and the outputs of the data generating process are covered.
+
+This manuscript uses the open source package Axelrod-Python~\cite{axelrodproject}
+to simulate tournaments of the IPD, more specifically, version 3.0.0.
+Axelrod-Python allows for different types of IPD computer tournaments to be
+simulated whilst containing a list of over 200 strategies. Most of these are
+strategies described in the literature, with a few exceptions being strategies
+that have been contributed specifically to the package. Though Axelrod-Python
+features several tournament types, this work considers only standard tournaments,
+noisy tournaments, probabilistic ending tournaments and noisy probabilistic
+ending ones.
+
+\textbf{Standard tournaments}, are tournaments with \(N\)
+strategies and an \(n\) number of turns. Similarly, \textbf{noisy tournaments}
+are of \(N\) strategies and of \(n\) number of turns but at each turn there is a
+noise probability of \(p\) that a player's action will be flipped.
+\textbf{Probabilistic ending tournaments}, are of size \(N\) and after each turn
+a match between strategies ends with a given probability \(e\). Finally,
+\textbf{noisy probabilistic ending} tournaments have both a noise probability
+\(p\) and an ending probability \(e\). For smoothing the simulated results a
+tournament is repeated for \(r\) number of times.
+
+For each run of the generating data process a random size \(N\), a random list
+of strategies are selected and a random number of repetitions \(r\), and for
+these, a standard, noise, probabilistic ending and a noisy probabilistic ending
+tournament are performed. More specifically, the process of data generation is
+given in Algorithm~\ref{algorithm:data_generation}.
+
+\begin{algorithm}[H]
+    \setstretch{1.35}
+    \ForEach{\text{seed} $\in [0, 12285]$}{
+        $N \gets \text{randomly select integer from }[N_{min}, N_{max}]$\;
+        $\text{players} \gets  \text{randomly select players from list of size } [N_{min}, N_{max}]$\;
+        $r \gets  \text{randomly select integer from } [r_{min}, r_{max}]$\;
+        $n \gets  \text{randomly select integer from } [n_{min}, n_{max}]$\;
+        $p \gets  \text{randomly select float from } [p_{min}, p_{max}]$\;
+        $e \gets   \text{randomly select float from } [e_{min}, e_{max}]$\;
+        \vspace{0.4cm}
+        $\text{result standard}$ $\gets$ Axelrod.tournament$(\text{players}, n, r)$\;
+        $\text{result noisy}$ $\gets$ Axelrod.tournament$(\text{players}, n, p, r)$\;
+        $\text{result probabilistic ending}$ $\gets$ Axelrod.tournament$(\text{players}, e, r)$\;
+        $\text{result noisy probabilistic ending}$ $\gets$ Axelrod.tournament$(\text{players}, p, e, r)$\;
+
+    }
+    \KwRet{result standard, result noisy, result probabilistic ending,
+    result noisy probabilistic ending}\;
+    \label{algorithm:data_generation}
 \end{algorithm}
 
-Once a tournaments is performed we export a summary of the performance
-of each strategy in the tournament. In the following sections we discuss how we
-manipulate the result set exported by Axelrod and hold a data analysis.
+At each given run of Algorithm~\ref{algorithm:data_generation} the run parameters
+are randomly selected. The parameters of each run and their respective min and max
+values are given by Table~\ref{table:parameters_values}.
 
-\section{Data preparation}
-
-The data set used for the study is the combination of all of these summary data sets.
-The structure of the data set is shown in Table~\ref{table:result_set}. Each row
-represents a player in a given tournament.
-
-Name is the name of the strategy. Stochastic, Memory depth and Use of arguments are
-characteristics of the given strategy. The performance of the strategy is reflected
-by columns Rate, Median score, Rank and Wins.
-
-The environment and the type of tournaments are captured by columns Noise, Probend,
-Repetitions, Size and Turns. Note that when turns are non given the tournament is a
-probabilistic ending one, and vise versa. Similarly, when Noise argument in non given
-the tournament is known to be standard. Finally, when both Noise and Probend are
-non zero then the tournament is an probabilistic and noisy tournament
-
-\begin{table}[htpb]
-\centering
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{ccccccccccccccccccccccccccccccccc}
+\begin{table}
+    \begin{center}
+        \resizebox{.6\textwidth}{!}{
+        \begin{tabular}{lcccc}
     \toprule
-% columns
-Name & Stochastic & \multicolumn{1}{p{2cm}}{\centering Memory \\ depth} &
-\multicolumn{1}{p{2cm}}{\centering Use of \\ game} &
-\multicolumn{1}{p{2cm}}{\centering Use of \\ length} & CC rate &  CD rate &
-\multicolumn{1}{p{2cm}}{\centering Cooperation \\rating} & DC rate & DD rate &
-Median score &  Rank &  Wins &  Noise  &  Probend & Repetitions &  Seed & Size & Turns \\
+    parameter & parameter explanation &   min value & max value \\
     \midrule
-% first row
-Adaptive & False & inf & True & False & 0.195 &  0.214 & 0.409 & 0.279 & 0.310 &
-2.430 & 14 &  77.0 &  0.391 & NaN & 25.0 & 0.0 & 101.0 & 148.0 \\
-% second row
-Adaptive & False & inf & True & False & 0.783 & 0.194 & 0.928 & 0.012 & 0.009 &
-2.292 & 88 & 5.0 &  0.391 & 0.370 & 25.0 & 0.0 & 101.0 & NaN \\
+    $N$ & number of strategies  & 3 & 195 \\
+    $r$ & number of repetitions  & 10 & 100 \\
+    $n$ & number of turns      & 1 & 200 \\
+    $p$ & probability of flipping action at each turn  & 0 & 1   \\
+    $e$ & probability of match ending in the next turn & 0 & 1   \\
     \bottomrule
         \end{tabular}}
-\caption{Result Set}
-\label{table:result_set}
+    \end{center}
+    \caption{Data generation parameters' values}
+    \label{table:parameters_values}
     \end{table}
 
-\begin{itemize}
-    \item the cooperation in each environment
-    \item show that got a uniform distribution of our parameters
-\end{itemize}
-In this work each tournament type is studied individually. An individual data set
-containing the following information is constructed for each type.
+The source code for the data generating process has been packaged and is
+available here. A total of 12,285 runs of
+Algorithm~\ref{algorithm:data_generation} have been performed. For each run the
+results for 4 different tournaments were collected, thus a total of 49,140
+$(12,285 \times 4)$ tournaments results have been retrieved. Each tournament
+outputs a result summary in the form of Table~\ref{table:output_result}. The
+result summary has a length \(N\) because each row contains information for each
+strategy participated in the tournament.
 
-\begin{multicols}{2}
-    \begin{itemize}
-        \item tournament index \(i\)
-        \item tournament size \(N_{i}\)
-        \item cooperation rating \((C_{r})\)
-        \item rank \((r_{i})\)
-        \item normalized rank \(\bar{r_{i}} = \frac{r_{i}}{N_{i}}\)
-        \item maximum cooperation rating \(C^{*}_{r}\)
-        \item minimum cooperation rating  \(\tilde{C_{r}}\)
-        \item normalised rank of maximum cooperator \(\bar{r_{C}}\)
-        \item normalised rank of minimum cooperator \(\bar{r_{D}}\)
-        \item mean cooperation rating \(\bar{C_{r}}\)
-        \item median cooperation rating \(\breve{C_{r}}\)
-        \item \(C\) ratio of the winner \(C_{W}\)
-        \item \(C\) ratio of the looser \(C_{L}\)
-        \item standard deviation of the cooperating ratio \(\sigma\).
-    \end{itemize}
-    \end{multicols}
+\newcolumntype{g}{>{\columncolor{Gray}}c}
+\begin{table}[h]
+    \begin{center}
+    \resizebox{\textwidth}{!}{
+    \begin{tabular}{ccccccgcgcgcgcg}
+    \toprule 
+    & & & & & &   \multicolumn{8}{g}{Rates}  \\
+    Rank & Name & Median score & Cooperation rating & Win & Initial C &
+    CC & CD & DC & DD & CC to C & CD to C & DC to C & DD to C \\
+    0 &  EvolvedLookerUp2 2 2 & 2.97 & 0.705 & 28.0 & 1.0 & 0.639 & 0.066 & 0.189 &
+    0.106 & 0.836 & 0.481 & 0.568 & 0.8 \\
+    1 &  Evolved FSM 16 Noise 05 & 2.875 & 0.697 & 21.0 & 1.0 & 0.676 & 
+    0.020 & 0.135 & 0.168 & 0.985 & 0.571 & 0.392 & 0.07 \\
+    2 & PSO Gambler 1 1 1 & 2.874 & 0.684 &  23.0 &     1.0 &    0.651 &    0.034 &    0.152 &    0.164
+    & 1.000 & 0.283 & 0.000 & 0.136 \\
+    3 &  PSO Gambler Mem1 &  2.861 &        0.706 &  23.0 &      1.0 &    0.663
+    &    0.042 &    0.145 &    0.150 &  1.000 &  0.510 &  0.000 &  0.122 \\
+    4 &          Winner12 &  2.835 &        0.682 &  20.0 &      1.0 &
+    0.651 &    0.031 &    0.141 &    0.177 &  1.000 &  0.441 &  0.000 &  0.462 \\
+    $\dots$ & $\dots$ & $\dots$ & $\dots$ & $\dots$ & $\dots$ & $\dots$ & $\dots$ &
+    $\dots$ & $\dots$ & $\dots$ & $\dots$ & $\dots$ & $\dots$ \\
+    \bottomrule
+    \end{tabular}}
+\end{center}
+\caption{Output result.}\label{table:output_result}
+\end{table}
 
-\section{Analysis}
+Several other measures are included in tha data set. These include the tournament
+parameters given in Table~\ref{table:parameters_values} and the measures
+described in Table~\ref{table:manual_measures}. A few of this measures are
+strategies' classifiers as given in Axelrod-Python, such as stochastic and
+memory depth. SSeeror is a measure defined in literature and the cooperation
+rating measures are calculated from the outputs of the tournaments.
 
-\begin{itemize}
-\item add \(r\) plots
-\item some more plots
-\end{itemize}
+\begin{table}
+    \begin{center}
+    \resizebox{\textwidth}{!}{
+    \begin{tabular}{lcl}
+    \toprule
+    measure & measure explanation & value  \\
+    \midrule
+stochastic  &  strategy classifier from~\cite{axelrodproject}. Whether a strategy is stochastic  & True or False \\
+memory depth &  strategy classifier from~\cite{axelrodproject}. the number of turns a strategy takes into account to make a decision & 0 to inf \\
+makes use of game &  strategy classifier from~\cite{axelrodproject}. Whether a strategy makes used of the game information & \\
+SSeeror & how extortionate a strategy behaves as stated in & \\
+memory usage & & \\
+cooperation rating max & & \\
+cooperation rating min & & \\
+cooperation rating median  & & \\
+cooperation rating mean & & \\
+cooperation rating comp to max & & \\
+cooperation rating comp to min & & \\
+cooperation rating comp to median & & \\
+cooperation rating comp to mean & & \\
+    \bottomrule
+        \end{tabular}}
+    \end{center}
+    \caption{Manually calculated measures}
+    \label{table:manual_measures}
+    \end{table}
+
+The data collection and the output from the generated tournaments have been covered
+in this section. Several measures that will be used in the analysis of the following
+sections have been presented. These are also summarised in Table in the Appendix.
+In the following Section, the top performances at each tournament
+are overall are presented.
+
+\section{Top Performances}\label{section:top_performances}
+
+In this section the top performed strategies for each tournament type, and overall
+are presented. The strategies have been ranked based on their median normalised
+rank, which is denoted as  \(\bar{R}\).
+
+\subsubsection{Standard Tournaments}
+
+A total of $12,285$ results on standard tournaments have been collected. On
+average a standard tournament had 122 strategies, a lenght of 100 turns and
+were repeated for 55 repetitions. The tournament top 15 performances in such
+tournaments are given
+by Table~\ref{table:std_results} and their distributions are given by
+Figure~\ref{fig:std_results}.
+
+\begin{wraptable}{r}{5.5cm}
+    \resizebox{.4\textwidth}{!}{
+    \input{performance_standard_table.tex}}
+    \caption{Standard top performances}\label{table:std_results}
+\end{wraptable}
+The top 10 out of the 15 strategies, are variations of Evolved FSM, Evolved HMM,
+EvolvedLookerUp and PSO Gambler, are strategies introduced in~\cite{Harper2017}.
+These are all strategies that have be trained using reinforcement learnings
+techniques to adjust their game play. Moreover, they have been trained using the
+strategies within the library~\cite{axelrodproject}, thus their performance is
+not a surprise. DoubleCrosser, and Fool Me Once, do not exist within the
+literature but have been especially written to contribute
+to~\cite{axelrodproject}. Fool me once will forgive one defection and then
+defects for ever when DoubleCrosser will forgive the first 3 defections and then
+defect forever. Moreover DoubleCrosser is a strategy which makes use of the
+lenght of the game. Finally, Winner 12~\cite{Mathieu2017} and DBS are both from
+the the literature. DBS~\cite{Au2006} is strategy specifically trained for noisy
+enviroments, however, it ranks highly only in standard ones.
+
+In the top strategies there appears to be a mixture of 13 complex strategies, and
+2 simple strategies that are quick to turn to defection forever.
+
+The distributions of the normalised ranks of the top 15 strategies is
+given in Figure\ref{fig:std_results}. Overall there is no much variation in the
+distributions, there mainly tailed closer to 0. Thus all these strategoties
+performed well at each given tournament that the have been involved.
+In the later session that other tournaments are explored we will see that
+this is true only to standard tournaments. With stochastic uncearta
+such as noise and probabilistic ending there is more variation in the 
+performances involved.
+
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=\textwidth]{../images/performance_standard.pdf}
+    \caption{P.D.}\label{fig:std_results}
+\end{figure}
+
+\newpage
+\subsubsection{Noisy Tournaments}
+
+The noisy tournament top 14 performances, based on \(\bar{R}\) are given
+by Table~\ref{table:noisy_results}. The distributions of their \(R\) is also
+given by Figure~\ref{fig:std_results}.
+
+\begin{table}
+    \begin{center}
+    \input{performance_noise_table.tex}
+    \caption{Noisy top performances}\label{table:noisy_results}
+    \end{center}
+\end{table}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.9\textwidth]{../images/performance_noise.pdf}
+    \caption{\(R\) distributions for best performed strategies in noisy tournaments.}
+\end{figure}
+
+\subsubsection{Probabilistic ending Tournaments}
+
+\begin{table}
+    \begin{center}
+    \input{performance_probend_table.tex}
+    \end{center}
+\end{table}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.9\textwidth]{../images/performance_probend.pdf}
+\end{figure}
+
+\subsubsection{Noisy \& Probabilistic ending Tournaments}
+
+\begin{table}
+    \begin{center}
+    \input{performance_probend_noise_table.tex}
+    \end{center}
+\end{table}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.9\textwidth]{../images/performance_probend_noise.pdf}
+\end{figure}
+
+\subsubsection{Overall Tournaments}
+
+\begin{table}
+    \begin{center}
+    \input{performance_merged_table.tex}
+    \end{center}
+\end{table}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.9\textwidth]{../images/performance_merged.pdf}
+\end{figure}
+
+\section{Evaluation of performance}\label{section:evaluation_of_performance}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.7\textwidth]{../output/output/standard/feature_importance_bar_plot.pdf}
+\end{figure}
+
+\section{Conclusion and Discussion}\label{section:conclusion}
+
+\bibliographystyle{plain}
+\bibliography{bibliography}
 \end{document}

### 2019-08-04 src/prepare_data.py
week commit

@@ -152,12 +152,16 @@ def prepare_type_dataframes(parameters_df, directory, tournament_type):
 if __name__ == "__main__":
 
     directory = sys.argv[1]
-    tournament_types = ["standard", "probend", "probend_noise"]
+    if sys.argv[2] == 'all':
+        tournament_types = ["standard", "noise", "probend", "probend_noise"]
+    else:
+        tournament_types = sys.argv[2].split(', ')
+    version = sys.argv[3]
 
-    print("Reading parameters data frames.")
+    print("Reading parameters data frame.")
     parameters_df = get_parameters_data_frame(directory)
 
     for tournament_type in tournament_types:
-        print("Creating & exporting %s data frames." % tournament_type)
+        print("Creating & exporting %s data frame." % tournament_type)
         df = prepare_type_dataframes(parameters_df, directory, tournament_type)
-        df.to_csv("data/%s.csv" % tournament_type)
+        df.to_csv("data/%s_%s.csv" % (tournament_type, version))

### 2019-09-05 paper/main.tex
write first sections of papers

--- 2018-04-05 main.tex
@@
 \usepackage{multicol}
-\usepackage{algorithm,algorithmic}
+\usepackage[ruled,vlined]{algorithm2e}
+\usepackage{setspace}
+\usepackage{graphicx}
+\usepackage{subcaption}
+\usepackage{hyperref}
+\usepackage{color,colortbl}
+\usepackage{array}
+\usepackage{booktabs}
+\usepackage{tabularx}
+\usepackage{wrapfig, blindtext}
 %%%%%%%%%%%%%%%%%
+
+\definecolor{Gray}{gray}{0.92}
+\usepackage[first=0,last=9]{lcg}
+\newcommand{\ra}{\rand0.\arabic{rand}}
 
@@
 
-\section{The Prisoner's Dilemma}
+\begin{abstract}
 
-The Prisoner's Dilemma is a two player repeated game commonly known in Game Theory
-as the model of cooperative behaviour. Each of the players has two strategies,
-to either cooperate (C) or defect (D). The decisions are made simultaneously
-and independently. The normal form representation of the game is given by
-matrix~\ref{matrix:pd}.
+The iterated prisoner's dilemma has been used for decades as a powerful model of
+behavioural interactions. From the celebrated performance of Tit for Tat, to the
+introduction of the zero-determinant family, to the use of sophisticated
+strategies such as neural networks, the literature has been exploring the
+performance of strategies in the game for years. Most of these strategies
+are now accessible due to an open source package. This manuscript make use
+of the open source and it's strategy data base to a conducts a meta analysis of
+iterated prisoner's dilemma tournaments. The aim is to evaluate the performance
+of these strategies and finally answer the question: which is the best strategy
+in the game?
+\end{abstract}
 
-\begin{equation}\label{matrix:pd}
-    \begin{bmatrix}
-    (R,R) & (S,T)  \\
-    (T,S) & (P,P)
-    \end{bmatrix}
-\end{equation}
+\section{Background}
 
-where the payoffs \((R, P, S, T)\) are constrained by equations (\ref{eq:constrain_one})
-and (\ref{eq:constrain_two}).
+The iterated prisoner's dilemma is a repeated two player game that models
+situations in which self-interest clashes with collective interest. At each turn,
+the players simultaneously and independently make a choice between cooperation (C) and
+defection (D) whilst their prior interactions matter. The payoffs at each given turn are defined by the matrix,
 
-\begin{equation}\label{eq:constrain_one}
-    T > R > P > S,
-\end{equation}
+\[\begin{pmatrix}
+R & S \\
+T & P
+\end{pmatrix}\]
 
-\begin{equation}\label{eq:constrain_two}
-    2R > T + S.
-\end{equation}
+where \(T > R > P > S\) and \(2R > T + S\). The most common values used in
+the literature, and in this paper, are $R=3, P=1, T=5, S=0$.
 
-In the one shot game the Nash equilibrium is given at (D, D) and both players
-received a payoff of \(P\). Thus, at the point where both players defect.
-In the repeated form of the game the behaviour becomes more complicated. The optimal
-behaviour of a player in the repeated game, in the Iterated Prisoner's Dilemma,
-has been the focus of research for years.
+Since the computer tournaments of R. Axelrod in 1980s several academic papers
+are published in the field regarding the performance of strategies in the
+iterated prisoner's dilemma. In the 80's following the strong performance of Tit For Tat
+in both Axelrod's computer tournaments~\cite{Axelrod1980a, Axelrod1980b}, and
+moreover in a series of evolutionary experiments~\cite{Axelrod1981}, the strategy
+was thought as the most robust basic strategy in the iterated prisoner's
+dilemma. However, the strategy's poor performance in environments with
+noise~\cite{Bendor1991, Donninger1986, Molander1985, Hammerstein1984},
+made room for other protagonists, such as, Nice and Forgiving~\cite{Bendor1991},
+Pavlov~\cite{Nowak1993} and Generous Tit For Tat~\cite{Nowak1992}.
 
-An interesting approach was introduced in 1980 by, where a computer tournament
-was used to tackle the same question.
+Yet again, in 2012 another set of strategies was introduced as the dominant set
+of strategies~\cite{Press2012}. These were called zero-determinant strategies,
+and by forcing a linear relationship between the payoffs they can ensure that
+they will never receive less than their opponents. However, in~\cite{Harper2017}
+a tournament containing over 200 strategies, including the zero-determinant strategies
+introduced in~\cite{Press2012}, was performed and none of the zero-determinant
+strategies ranked in top spots. Instead, the top ranked strategies were a set of
+trained strategies based lookup tables, hidden markov models and finite state
+automata.
+%TODO reference the archetypes of the archetypes used the IPD?
 
-\begin{itemize}
-    \item The definition of a strategy
-    \item The definition of a tournament.
-\end{itemize}
+Thus, the following question is raised here: which are the true dominant
+strategies in the iterated prisoner's dilemma?
 
-\section{Collecting data}
+This manuscript uses the open source package
+Axelrod-Python~\cite{axelrodproject} to simulate a large number of computer
+tournaments using as many strategies as possible from the literature. The aim is
+evaluate the performance of these strategies in a tournament and futhermore,
+explore the factors of their success. This is done not for standard round robin
+tournaments, but also for noisy, probabilistic ending and noisy probabilistic
+ending tournaments.
 
-For performing a large number of computer tournaments the open source package
-Axelrod Library is used in this work. The package was introduced in 2015,
-it is written in the programming language Python and it allow us to perform
-a number of tournaments with different strategies. The payoff values used in
-Axelrod are \((3, 1, 0, 5)\) and the following type of tournaments have been performed.
+The structure of this manuscript is as follows. In
+Section~\ref{section:data_collection} the data collection is covered. In
+Section~\ref{section:top_performances}, the best performed strategies for each
+type of tournament and overall are presented.
+Section~\ref{section:evaluation_of_performance}, explores the traits which
+contribute to good performance and finally in Section~\ref{section:conclusion}
+we conclude and summarise the results.
 
-There are several tournament types introduced in the literature that have not been
-discussed.
+\section{Data generating process}\label{section:data_collection}
 
-\begin{enumerate}
-    \item \textbf{Standard tournament}. A round robin tournament where
-    the number of turns for each match can vary between 200 and 1. The tournament
-    is repeated between 10 and 100 times.
-    \item \textbf{Noisy tournament}. Similar to a standard tournament. A noisy
-    tournament in a round robin tournament where noise is introduced. Noise is the
-    probability that a players action is flipped. The probability of noise is
-    ranging between 0 and 1.
-    \item \textbf{Probabilistic ending tournament}. Similar to a standard tournament
-    however in a probabilistic ending tournament the number of turns is not specified.
-    There is a probability (ranges between 0 and 1) that the match will end in
-    the next round. Probabilistic ending tournament will be referred to as
-    probend hereupon.
-    \item \textbf{Noisy and Probabilistic ending tournament}. A combination of
-    noisy and probabilistic ending tournaments.
-\end{enumerate}
+For the purposes of this manuscript a data set containing results on iterate
+prisoner's dilemma tournaments has been generated, which is available at. This
+was done using the open source package Axelrod-Python~\cite{axelrodproject},
+more specifically, version 3.0.0. Axelrod-Python allows for different types of
+iterated prisoner's dilemma computer tournaments to be simulated whilst
+containing a list of over 190 strategies. Most of these are strategies described
+in the literature with a few exceptions being strategies that have been
+contributed specifically to the package. Though Axelrod-Python features several
+tournament types, this work considers only standard, noisy, probabilistic ending
+and noisy probabilistic ending tournaments.
 
-The process for generating the data set is described by Algorithm~\ref{alg:tournaments}.
-Every 20 iterations of a random seed a new sample is chosen. For each sample, for 20
-repetitions random numbers of turns, repetitions of the tournament, the probability of
-noise in the tournament and the probability of the game ending in after each interaction
-are sampled.
+\textbf{Standard tournaments}, are tournaments similar to that of Axelrod's
+in~\cite{Axelrod1980a}. There are \(N\) strategies which all play an iterated
+game of \(n\) number of turns against each other. Note that self interactions and
+a match against a random strategy are not included. Similarly, \textbf{noisy tournaments}
+have \(N\) strategies and \(n\) number of turns but at each turn there is a
+probability \(p\) that a player's action will be flipped.
+\textbf{Probabilistic ending tournaments}, are of size \(N\) and after each turn
+a match between strategies ends with a given probability \(e\). Finally,
+\textbf{noisy probabilistic ending} tournaments have both a noise probability
+\(p\) and an ending probability \(e\). For smoothing the simulated results a
+tournament is repeated for \(r\) number of times and the ranks are based on the
+average score a strategy achieved and not by number of wins. A summary of
+each tournaments' parameters is given in Table~\ref{table:tournaments_parameters}.
 
-For that set of parameters, four types of tournaments (as discussed above) are conducted.
-A standard one, a noisy one, a probend one and lastly a probend with noise.
+\begin{table}[!htbp]
+    \begin{center}
+        \resizebox{.85\textwidth}{!}{
+        \begin{tabular}{lccccc}
+    \toprule
+    tournament type & number of strategies & turns & noise probability & probability of match ending \\
+    \midrule
+    standard & $N$  & $n$ & - & - \\
+    noisy & $N$  & $n$ & $p$ & - \\
+    probabilistic ending & $N$  & - & - & $e$ \\
+    noisy probabilistic ending & $N$  & - & $p$ & $e$ \\
+    \bottomrule
+        \end{tabular}}
+    \end{center}
+    \caption{Tournament types' parameters.}
+    \label{table:tournaments_parameters}
+\end{table}
 
-\begin{algorithm}
-    \caption{Generating data}
-    \label{alg:tournaments}
-      \begin{algorithmic}[1]
-        \FOR{seed \textbf{in} 10000}
-            \IF{$seed \ mod \ 20 =0$}
-                \STATE size $\gets$ random  size
-                \STATE players $\gets$ random players
-             \ELSE
-                 \STATE turns $\gets$ random turns
-                 \STATE repetitions  $\gets$  random  repetitions
-                 \STATE noise  $\gets$ random  noise  probability
-                 \STATE end  $\gets$  random end probability
-                 \STATE standard results $\gets$ tournament(turns, players, repetitions) 
-                 \STATE noise results $\gets$ tournament(turns, players, repetitions, noise)
-                 \STATE probend results $\gets$ tournament(players, repetitions, end)
-                 \STATE probend noise results $\gets$ tournament(players, repetitions, noise, end)
-             \ENDIF
-             \RETURN standard, noise, probend, probend noise results
-        \ENDFOR
-      \end{algorithmic}
+The process of generating data implemented in this manuscript is given by
+Algorithm~\ref{algorithm:data_generation}. For each trial a random
+size \(N\) is selected, and from the list of 195 strategies
+in~\cite{axelrodproject}, a random list of \(N\) strategies is chosen. For the
+given list of strategies a standard, noise, probabilistic ending and a noisy
+probabilistic ending tournament are performed and repeated \(r\) times.
+The parameters for the tournaments as well as the number of repetitions are
+selected once for each trial. The parameters and their respective minimum and
+maximum values are given by Table~\ref{table:parameters_values}.
+
+The source code for the data generating process as well as the source code for
+the analysis which will be discussed in the following sections have been written
+following best practices~\cite{Aberdour2007, Benureau2018}. It has been packaged
+and is available here.
+
+\begin{algorithm}[!htbp]
+    \setstretch{1.35}
+    \ForEach{\text{seed} $\in [0, 12285]$}{
+        $N \gets \text{randomly select integer}\in [N_{min}, N_{max}]$\;
+        $\text{players} \gets  \text{randomly select $N$ players}$\;
+        $r \gets  \text{randomly select integer}\in [r_{min}, r_{max}]$\;
+        $n \gets  \text{randomly select integer}\in [n_{min}, n_{max}]$\;
+        $p \gets  \text{randomly select float}\in [p_{min}, p_{max}]$\;
+        $e \gets   \text{randomly select float}\in [e_{min}, e_{max}]$\;
+        \vspace{0.4cm}
+        $\text{result standard}$ $\gets$ Axelrod.tournament$(\text{players}, n, r)$\;
+        $\text{result noisy}$ $\gets$ Axelrod.tournament$(\text{players}, n, p, r)$\;
+        $\text{result probabilistic ending}$ $\gets$ Axelrod.tournament$(\text{players}, e, r)$\;
+        $\text{result noisy probabilistic ending}$ $\gets$ Axelrod.tournament$(\text{players}, p, e, r)$\;
+
+    }
+    \KwRet{result standard, result noisy, result probabilistic ending,
+    result noisy probabilistic ending}\;
+    \caption{Data generating Algorithm}
+    \label{algorithm:data_generation}
 \end{algorithm}
 
-Once a tournaments is performed we export a summary of the performance
-of each strategy in the tournament. In the following sections we discuss how we
-manipulate the result set exported by Axelrod and hold a data analysis.
-
-\section{Data preparation}
-
-The data set used for the study is the combination of all of these summary data sets.
-The structure of the data set is shown in Table~\ref{table:result_set}. Each row
-represents a player in a given tournament.
-
-Name is the name of the strategy. Stochastic, Memory depth and Use of arguments are
-characteristics of the given strategy. The performance of the strategy is reflected
-by columns Rate, Median score, Rank and Wins.
-
-The environment and the type of tournaments are captured by columns Noise, Probend,
-Repetitions, Size and Turns. Note that when turns are non given the tournament is a
-probabilistic ending one, and vise versa. Similarly, when Noise argument in non given
-the tournament is known to be standard. Finally, when both Noise and Probend are
-non zero then the tournament is an probabilistic and noisy tournament
-
-\begin{table}[htpb]
-\centering
-\resizebox{\columnwidth}{!}{%
-\begin{tabular}{ccccccccccccccccccccccccccccccccc}
+\begin{table}[!htbp]
+    \begin{center}
+        \resizebox{.6\textwidth}{!}{
+        \begin{tabular}{lcccc}
     \toprule
-% columns
-Name & Stochastic & \multicolumn{1}{p{2cm}}{\centering Memory \\ depth} &
-\multicolumn{1}{p{2cm}}{\centering Use of \\ game} &
-\multicolumn{1}{p{2cm}}{\centering Use of \\ length} & CC rate &  CD rate &
-\multicolumn{1}{p{2cm}}{\centering Cooperation \\rating} & DC rate & DD rate &
-Median score &  Rank &  Wins &  Noise  &  Probend & Repetitions &  Seed & Size & Turns \\
+    parameter & parameter explanation &   min value & max value \\
     \midrule
-% first row
-Adaptive & False & inf & True & False & 0.195 &  0.214 & 0.409 & 0.279 & 0.310 &
-2.430 & 14 &  77.0 &  0.391 & NaN & 25.0 & 0.0 & 101.0 & 148.0 \\
-% second row
-Adaptive & False & inf & True & False & 0.783 & 0.194 & 0.928 & 0.012 & 0.009 &
-2.292 & 88 & 5.0 &  0.391 & 0.370 & 25.0 & 0.0 & 101.0 & NaN \\
+    $N$ & number of strategies  & 3 & 195 \\
+    $r$ & number of repetitions  & 10 & 100 \\
+    $n$ & number of turns      & 1 & 200 \\
+    $p$ & probability of flipping action at each turn  & 0 & 1   \\
+    $e$ & probability of match ending in the next turn & 0 & 1   \\
     \bottomrule
         \end{tabular}}
-\caption{Result Set}
-\label{table:result_set}
+    \end{center}
+    \caption{Data generation parameters' values}
+    \label{table:parameters_values}
 \end{table}
 
-\begin{itemize}
-    \item the cooperation in each environment
-    \item show that got a uniform distribution of our parameters
-\end{itemize}
-In this work each tournament type is studied individually. An individual data set
-containing the following information is constructed for each type.
+A total of 12,285 trials of Algorithm~\ref{algorithm:data_generation} have been
+performed. For each trial the results for 4 different tournaments were collected,
+thus a total of 49,140 $(12,285 \times 4)$ tournament results have been
+retrieved. Each tournament outputs a result summary in the form of
+Table~\ref{table:output_result}. The result summary has a length \(N\) because
+each row contains information for each strategy that participated in the tournament.
+The information include the strategy's rank $(R)$, median score, the rate with
+which the strategy cooperated $(C_r)$, it's wins and the probability that the strategy
+cooperated in the opening move. Moreover the summary result includes the rates
+of a strategy being in any of the four states ($CC, CD, DC, DD$), and the rate
+of which the strategy cooperated after each state.
 
-\begin{multicols}{2}
-    \begin{itemize}
-        \item tournament index \(i\)
-        \item tournament size \(N_{i}\)
-        \item cooperation rating \((C_{r})\)
-        \item rank \((r_{i})\)
-        \item normalized rank \(\bar{r_{i}} = \frac{r_{i}}{N_{i}}\)
-        \item maximum cooperation rating \(C^{*}_{r}\)
-        \item minimum cooperation rating  \(\tilde{C_{r}}\)
-        \item normalised rank of maximum cooperator \(\bar{r_{C}}\)
-        \item normalised rank of minimum cooperator \(\bar{r_{D}}\)
-        \item mean cooperation rating \(\bar{C_{r}}\)
-        \item median cooperation rating \(\breve{C_{r}}\)
-        \item \(C\) ratio of the winner \(C_{W}\)
-        \item \(C\) ratio of the looser \(C_{L}\)
-        \item standard deviation of the cooperating ratio \(\sigma\).
-    \end{itemize}
-    \end{multicols}
+\newcolumntype{g}{>{\columncolor{Gray}}c}
+\begin{table}[!htbp]
+    \begin{center}
+    \resizebox{\textwidth}{!}{
+    \begin{tabular}{ccccccgcgcgcgcg}
+    \toprule 
+    & & & & & &   \multicolumn{8}{g}{Rates}  \\
+    Rank $(R)$ & Name & Median score & Cooperation rating $(C_r)$ & Win & Initial C &
+    CC & CD & DC & DD & CC to C & CD to C & DC to C & DD to C \\
+    0 &  EvolvedLookerUp2 2 2 & 2.97 & 0.705 & 28.0 & 1.0 & 0.639 & 0.066 & 0.189 &
+    0.106 & 0.836 & 0.481 & 0.568 & 0.8 \\
+    1 &  Evolved FSM 16 Noise 05 & 2.875 & 0.697 & 21.0 & 1.0 & 0.676 & 
+    0.020 & 0.135 & 0.168 & 0.985 & 0.571 & 0.392 & 0.07 \\
+    2 & PSO Gambler 1 1 1 & 2.874 & 0.684 &  23.0 &     1.0 &    0.651 &    0.034 &    0.152 &    0.164
+    & 1.000 & 0.283 & 0.000 & 0.136 \\
+    3 &  PSO Gambler Mem1 &  2.861 &        0.706 &  23.0 &      1.0 &    0.663
+    &    0.042 &    0.145 &    0.150 &  1.000 &  0.510 &  0.000 &  0.122 \\
+    4 &          Winner12 &  2.835 &        0.682 &  20.0 &      1.0 &
+    0.651 &    0.031 &    0.141 &    0.177 &  1.000 &  0.441 &  0.000 &  0.462 \\
+    $\dots$ & $\dots$ & $\dots$ & $\dots$ & $\dots$ & $\dots$ & $\dots$ & $\dots$ &
+    $\dots$ & $\dots$ & $\dots$ & $\dots$ & $\dots$ & $\dots$ \\
+    \bottomrule
+    \end{tabular}}
+\end{center}
+\caption{Output result.}\label{table:output_result}
+\end{table}
 
-\section{Analysis}
+Several other measures have been manually calculated/retrieved and have been
+included in the data set. These include properties of the strategies as well as
+measures regarding the tournament, such as the parameters of
+Table~\ref{table:parameters_values}. All these measures are summarized and
+described Table~\ref{table:manual_measures}.
 
-\begin{itemize}
-\item add \(r\) plots
-\item some more plots
-\end{itemize}
+\newcolumntype{g}{>{\columncolor{Gray}}c}
+\begin{table}[h]
+    \begin{center}
+    \resizebox{\textwidth}{!}{
+    \begin{tabular}{gcgcgc}
+    \toprule
+    measure & measure explanation &  source & value type & min value & max value \\
+    \midrule
+normalized rank $(r)$ & The rank of the strategy divided by the tournament size & result summary & float & 0 & 1 \\
+memory depth &  Strategy's memory size & strategy classifier from~\cite{axelrodproject} & integer & 0 & $\infty$ \\
+stochastic  &  If a strategy is stochastic & strategy classifier from~\cite{axelrodproject} & boolean  & False &  True \\
+makes use of game &  If a strategy makes used of the game information & strategy classifier from~\cite{axelrodproject} & boolean  & False &  True \\
+makes use of length &  If a strategy makes used of the number of turns & strategy classifier from~\cite{axelrodproject} & boolean  & False &  True \\
+SSE & A measure of how far a strategy is from extortionate behaviour & method described in [ref] & float & 0 & 1 \\
+max cooperating rate $(C_{\text{max}})$  & The biggest cooperating rate in the tournament & result summary & float & 0 & 1 \\
+min cooperating rate $(C_{\text{min}})$ & The smallest cooperating rate in the tournament & result summary & float & 0 & 1 \\
+median cooperating rate $(C_{\text{median}})$ & The median cooperating rate in the tournament & result summary & float & 0 & 1 \\
+mean cooperating rate $(C_{\text{mean}})$ & The mean cooperating rate in the tournament & result summary & float & 0 & 1 \\
+$C_r$ / $C_{\text{max}}$ & A strategy's cooperating rate divided by the maximum & manually & float & 0 & 1 \\
+$C_r$ / $C_{\text{min}}$ & A strategy's cooperating rate divided by the minimum & manually & float & 0 & 1 \\
+$C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median & manually & float & 0 & 1 \\
+$C_r$ / $C_{\text{mean}}$ & A strategy's cooperating rate divided by the mean & manually & float & 0 & 1 \\
+    \bottomrule
+        \end{tabular}}
+    \end{center}
+    \caption{Manually calculated/retrieved measures.}
+    \label{table:manual_measures}
+    \end{table}
+
+These measures will be used in more detail in the following sections.
+
+% Might move these measures to the sections in which they are actual used as
+% it feels like an overload of info in this section.
+
+The data collection and the output from the generated tournaments have been
+covered in this section. The measures that will be used in the analysis of the
+following sections have been presented. These are also summarised in Table in
+the Appendix. In the following Section, the top performances at each tournament
+are overall are presented.
+
+\section{Top ranked strategies}\label{section:top_performances}
+
+This section evaluates the performance of 186 strategies. These can be find in
+the Appendix. The performance of each strategy will be evaluated for each type
+of tournament independently. In Section~\ref{subsection:standard_tournament} the
+strategies are evaluated on their performance in standard tournaments, in
+Section~\ref{subsection:noisy_tournament} in noisy, and the rest in
+Sections~\ref{subsection:probend_tournament}
+and~\ref{subsection:noisy_probend_tournament}.
+
+Each tournament could have participated in multiple tournaments of the same
+type. On average a strategy participated in 5690 different tournaments of each
+type. For example Tit For Tat has participated in a total of 5569 standard
+tournaments. The strategy's normalised ranks distribution is given in
+Figure~\ref{fig:tit_for_tat_r_distribution}. As a result, of the multiple entries of
+strategies their performance in this manuscript is evaluated based on the median
+normalised rank denoted as \(\bar{r}\). Note that a value of \(\bar{r} = 0\)
+means that a strategy the winner of the tournament where a value of \(\bar{r} = 1\)
+means that the strategy came last.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=.5\textwidth]{../images/tit_for_tat_r_distribution.pdf}
+    \caption{Tit For Tat's $r$ distribution for standard tournaments.}
+    \label{fig:tit_for_tat_r_distribution}
+\end{figure}
+
+Following the analysis of each tournament type, in Section~\ref{subsrction:overall}
+the results are merged and the strategies are evaluated in their overall performances
+over all the different tournaments.
+
+\subsection{Standard tournaments}\label{subsection:standard_tournament}
+
+The results presented in this section are based on $12,285$ different standard
+tournaments. Each tournament has on average 122 participants, a length of
+100 turns and was repeated 55 times.
+
+The top 15 performances in standard tournaments are given by
+Table~\ref{table:std_results}. The 10 out of the 15 are strategies introduced
+in~\cite{Harper2017}. These have been trained using FSM (finite state automata),
+HMM (hidden markov models), ANN (artificial neural networks), lookup tables
+(LookerUp) and stochastic lookup tables (Gambler). Specifically, the have been
+trained using the strategy list of~\cite{axelrodproject} in standard
+tournaments. Thus their performance was to be expected. DoubleCrosser, and Fool
+Me Once, are not from the literature but from~\cite{axelrodproject}.
+DoubleCrosser is a strategy that makes use of the length of the match because is
+set to defect on the last two rounds. The strategy is expected to not perform as
+well in probabilistic ending tournaments. Finally, Winner 12~\cite{Mathieu2017}
+and DBS are both from the the literature. DBS~\cite{Au2006} is strategy
+specifically designed for noisy environments, however, it ranks highly only in
+standard ones.
+
+\begin{table}[!htbp]
+    \centering
+    \resizebox{.3\textwidth}{!}{
+    \input{performance_standard_table.tex}}
+    \caption{Standard top performances}\label{table:std_results}
+\end{table}
+
+The distributions of $\bar{r}$ for top ranked strategies are given in
+Figure~\ref{fig:std_results}. The distributions are skewed towards zero and the
+highest median is at 0.075. These strategies would mostly rank high when they
+participated in a tournament. This is not true for the rest of the tournament
+types. In the following sections $\bar{r}$ and subsequently the performances are
+more variant.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.8\textwidth]{../images/performance_standard.pdf}
+    \caption{$\bar{r}$ distributions of top 15 strategies.}\label{fig:std_results}
+\end{figure}
+
+\subsection{Noisy tournaments}\label{subsection:noisy_tournament}
+
+Similarly to Section~\ref{subsection:standard_tournament} the results presented
+here are based on $12,285$ different noisy tournaments. The strategies have been
+ranked based on their \(\bar{r}\) and the top 15 are given by
+Table~\ref{table:noisy_results}. The distributions of their corresponding
+\(\bar{r}\) is also given by Figure~\ref{fig:noisy_results}.
+
+The top strategies include two well known strategies Tit For 2
+Tats~\cite{Axelrod1980b} and Hard Tit For 2 Tats~\cite{Stewart2012} which are
+strategies that will defect only after the have received two defections from the
+opponent. The Retaliate strategies are set of strategies from~\cite{axelrodproject}
+that start by cooperating but will retaliate once the opponent's wins and
+defections surpass a curtain threshold. Strategies ShortMem~\cite{Carvalho2013},
+Grumpy, $e$ and $\phi$ are strategies that make decisions based on the
+cooperations to defections. Cycler Hunter tries to extort strategies that play
+cyclically and Risky QLearn uses a Q learning algorithm. Notably a very simple
+strategy, Cooperator, has been ranked third.
+
+\begin{table}[!htbp]
+    \centering
+    \resizebox{.28\textwidth}{!}{
+    \input{performance_noise_table.tex}}
+    \caption{Noisy top performances}\label{table:noisy_results}
+\end{table}
+
+From Figure~\ref{fig:std_results} it is evident that the normalised rank distributions
+in noisy environments are more variant and have higher median values compared
+to standard tournament. Moreover, the distributions are skewed both towards
+0 and 1 which indicate that the top ranked strategies ranked first and last
+in several tournaments. However, the low values of the median shows that the
+have won most of the tournaments.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.8\textwidth]{../images/performance_noise.pdf}
+    \caption{\(\bar{r}\) distributions for best performed strategies in noisy tournaments.}
+    \label{fig:noisy_results}
+\end{figure}
+
+\subsection{Probabilistic ending tournaments}\label{subsection:probend_tournament}
+
+In this section the performances in probabilistic ending tournaments are discussed.
+The 15 top ranked strategies are given by Table~\ref{table:prob_end_results}
+and their respective $\bar{r}$ distributions in Figure~\ref{fig:probend_results}.
+
+Fortress 3, Fortress 4 (both introduced in~\cite{Ashlock2006}),
+Raider~\cite{Ashlock2014} and Solution B1~\cite{Ashlock2014} are strategies
+based on finite state automata introduced by Daniel and Wendy Ashlock. These
+strategies have been evolved using reinformed learning. However, there were
+trained to maximise their payoffs in tournaments with fixed turns, 150
+specifically, and not in probabilistic ending tournaments.
+
+Better and Better, Gradual Killer, Hard Prober are strategies from PRISON which
+is a research software tool for the prisoner's dilemma available
+at~\cite{prison}. These, including Bully (Reverse Tit For
+Tat)~\cite{Nachbar1992}, are strategies that are less cooperative strategies and
+more defective. Furthermore, Defector is a strategy which always defects.
+Interestingly, the last two strategies are EasyGo and Fool Me Forever. These
+strategies are actually the same. The will defect until their opponent defect,
+then they will cooperate until the end. Though we would have guessed that these
+two would have been taken advantage off both scored very highly and based on
+their distributions (Figure~\ref{fig:probend_results}) there have managed to win
+tournaments.
+
+\begin{table}[!htbp]
+    \centering
+    \resizebox{.28\textwidth}{!}{
+    \input{performance_probend_table.tex}}
+    \caption{Probabilistic ending top performances}\label{table:prob_end_results}
+\end{table}
+
+The distributions of ranks in probabilistic ending tournaments are less variant
+than those of noisy tournaments. The uncertainty in the number of turns does not
+seem to be having the same effect. The medians are lower than 0.1 and the
+distributions are skewed towards 0. These suggest that the strategies performed
+well in the tournaments that they participated.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.8\textwidth]{../images/performance_probend.pdf}
+    \caption{\(\bar{r}\) distributions for best performed strategies in probabilistic ending tournaments.}
+    \label{fig:probend_results}
+\end{figure}
+
+\subsection{Noisy \& probabilistic ending tournaments}\label{subsection:noisy_probend_tournament}
+
+This section presents the results in tournaments were there are two
+uncertainties. There is the uncertainty that a player's action will be flipped
+and there is the uncertainty that there will not be future interactions.
+The 15 top ranked strategies are given in Table~\ref{table:noisy_prob_end_results}.
+Several of these strategies were highly ranked in noisy tournaments as well
+but the same does not hold for the strategies which were highly ranked in
+probabilistic ending tournaments.
+
+\begin{table}[!htbp]
+    \centering
+    \resizebox{.28\textwidth}{!}{
+    \input{performance_probend_noise_table.tex}}
+    \caption{Noisy and probabilistic ending top performances}\label{table:noisy_prob_end_results}
+\end{table}
+
+The top ranked strategy is Alternator a strategy that alternate between
+cooperation and defection. Alternator is followed by strategies that decide so
+that the ratio of cooperations and defections is close to the equivalent
+mathematical constants. Anti Tit For Tat is similar to Bully, which was covered
+in Section~\ref{subsection:noisy_tournament}, but starts of with cooperation and
+Hopeless~\cite{Van2015} a strategy that will only defect if and only if a mutual
+cooperation. The last spots are occupied by strategies based on the Q learning
+algorithm.
+
+Compared to the distributions in noisy environments,
+Section~\ref{subsection:noisy_tournament}, the distributions here are skewed
+towards the middle, Figure~\ref{fig:noisy_probend_results}. The medians are
+close to 0.5 which seems to indicate a less dominant performance of strategies
+in this environment.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.7\textwidth]{../images/performance_probend_noise.pdf}
+    \caption{\(\bar{r}\) distributions for best performed strategies in noisy probabilistic ending tournaments.}
+    \label{fig:noisy_probend_results}
+\end{figure}
+
+As yet, the performances of 186 different strategies have been evaluated in
+four different tournaments. In standard tournaments the top ranked spots were
+dominated by strategies that have been trained using reinforcement learning
+techniques and have been maximised in a standard tournament against the same
+list of opponents that is being used here. These strategies dominated most
+the tournaments that have been involved in. In noisy tournaments the top ranked
+strategies were all different to those of standard tournaments. Most of the
+top ranked strategies have been strategies that were trying to keep the defection
+and cooperation to a given ratio. These strategies had won most the tournaments
+in which they participated, however, they also ranked last in several tournaments.
+Once again in probabilistic ending tournaments the top ranked strategies were
+different to those before. More defecting strategies occupied the top ranks
+as well as finite state automata that have been introduced all by the same
+authors. Finally, in noisy probabilistic ending tournaments it was the only
+set of tournaments were the highly ranked strategies have been covered before,
+more specifically, in noisy tournaments. In these tournaments however the
+distributions of the ranks had much variation and some strategies even had
+a $\bar{r}$ close to 0.5, indicating that there were successfully only 50\%
+of the time.
+
+In the following section the performance of the strategies is evaluated again.
+However this time the results of the tournament types are included in the
+analysis.
+
+\subsection{Top performance in data set}\label{subsrction:overall}
+
+The data set which was described in Section~\ref{section:data_collection}
+contains results from 49,140 tournaments. The strategies have been ranked based
+on their $\bar{r}$ and the 15 top ranked strategies are given in
+Table~\ref{table:overall_results}. These include several strategies that have
+ranked in the top spots in the separate tournament analysis. The top 6 spaces
+are overtaken by Retaliate strategies, followed by BackStabber and
+DoubleCrosser. DoubleCrosser is just an extension of BackStabber. Nice Meta
+Winner and NMWE Memory One are strategies that are part of a team, Stein and
+Rapoport and Grudger are strategies from Axelrod's original tournament that came
+the 6th and 7th respectively. Forgeful Fool Me once is an extension to Grudger
+and PSO GAmer and Evolved are strategies again introduced in~\cite{Harper2017}.
+
+\begin{table}[!htbp]
+    \centering
+    \resizebox{.35\textwidth}{!}{
+    \input{performance_merged_table.tex}}
+    \caption{Top performances in data set}\label{table:overall_results}
+\end{table}
+
+The distributions between the first six strategies are very similar. From then
+onwards the distributions are skewed to both 0 and 1. The analysis
+of the data set gives us an indication of what performance is successful
+in cases that the environment is not known to you and the Retaliate family
+seem to be doing the trick.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.8\textwidth]{../images/performance_merged.pdf}
+    \caption{\(\bar{r}\) distributions for best performed strategies in data set.}
+    \label{fig:overall_results}
+\end{figure}
+
+In this section the top ranked performances were presented. These one done
+just by simply taking into account the ranks each strategy achieved in each
+tournament type and finally in the data set. Through the analysis only a few
+strategies seem to have been repeated, however, the winner were also
+completely different from type to type. Thus, what does make then successfully
+in those environments? The aim of the next section is that.
+
+\section{Evaluation of performance}\label{section:evaluation_of_performance}
+
+In this section we evaluate what makes a strategy.
+
+% \begin{figure}
+%     \centering
+%     \includegraphics[width=.7\textwidth]{../output/output/standard/feature_importance_bar_plot.pdf}
+% \end{figure}
+
+\section{Conclusion and Discussion}\label{section:conclusion}
+
+\bibliographystyle{plain}
+\bibliography{bibliography}
 \end{document}

### 2019-09-05 src/process_data.py
fix errors and move tests

@@ -1,12 +1,33 @@
 import sys
 
-import matplotlib.pyplot as plt
 import numpy as np
 import pandas as pd
 
 import axelrod as axl
 import dask_ml.cluster
-import prepare_data
+
+
+def get_least_squares(vector, game=axl.game.Game()):
+    """
+    Obtain the least squares directly
+    
+    Returns:
+    
+    - xstar
+    - residual
+    """
+
+    R, P, S, T = game.RPST()
+
+    C = np.array([[R - P, R - P], [S - P, T - P], [T - P, S - P], [0, 0]])
+
+    tilde_p = np.array([vector[0] - 1, vector[1] - 1, vector[2], vector[3]])
+
+    xstar = np.linalg.inv(C.transpose() @ C) @ C.transpose() @ tilde_p
+
+    SSError = tilde_p.transpose() @ tilde_p - tilde_p @ C @ xstar
+
+    return SSError
 
 
 def get_strategies_properties():
@@ -50,25 +71,13 @@ def get_error_for_row(row):
         "DD_to_C_rate",
     ]
     vector = [row[column] for column in columns_for_sse]
-    sse_error = prepare_data.get_least_squares(vector=vector)
+    sse_error = get_least_squares(vector=vector)
 
     return sse_error
 
 
-def get_normalised_rank(row):
-    return row["Rank"] / (row["size"] - 1)
-
-
 def fix_name(row):
     return row["Name"].split(":")[0]
-
-
-def get_memory_percentage(row):
-    if np.isinf(row["Memory_depth"]):
-        return 1
-    if row["Memory_depth"] == 0:
-        return 0
-    return row["Memory_depth"] / row["size"]
 
 
 def get_cooporation_rating_compared_to_max(row):
@@ -84,9 +93,7 @@ def get_cooporation_rating_compared_to_mean(row):
 
 
 def get_cooporation_rating_compared_to_min(row):
-    if row["Cooperation_rating_max"] == 0:
-        return row["Cooperation_rating"]
-    return row["Cooperation_rating"] / row["Cooperation_rating_max"]
+    return row["Cooperation_rating_min"] / row["Cooperation_rating"]
 
 
 if __name__ == "__main__":
@@ -103,8 +110,7 @@ if __name__ == "__main__":
 
     print("Processing")
     df = df.replace(replace)
-    df["SSeeror"] = df.apply(get_error_for_row, axis=1)
[…]

### 2019-09-05 src/prepare_data.py
fix errors and move tests

@@ -7,6 +7,10 @@ import pandas as pd
 import axelrod as axl
 
 
+def get_normalised_rank(row):
+    return row["Rank"] / (row["size"] - 1)
+
+
 def get_parameters_data_frame(directory):
     """
     A function for reading in the parameters data frame.
@@ -21,29 +25,6 @@ def get_parameters_data_frame(directory):
     df = df.drop_duplicates()
 
     return df.sort_values(["seed"]).reset_index()
-
-
-def get_least_squares(vector, game=axl.game.Game()):
-    """
-    Obtain the least squares directly
-    
-    Returns:
-    
-    - xstar
-    - residual
-    """
-
-    R, P, S, T = game.RPST()
-
-    C = np.array([[R - P, R - P], [S - P, T - P], [T - P, S - P], [0, 0]])
-
-    tilde_p = np.array([vector[0] - 1, vector[1] - 1, vector[2], vector[3]])
-
-    xstar = np.linalg.inv(C.transpose() @ C) @ C.transpose() @ tilde_p
-
-    SSError = tilde_p.transpose() @ tilde_p - tilde_p @ C @ xstar
-
-    return SSError
 
 
 class Reader:
@@ -101,6 +82,7 @@ class Reader:
         df["repetitions"] = self.repetitions
         df["size"] = self.size
         df["seed"] = self.seed
+        df["Normalized_Rank"] = df.apply(get_normalised_rank, axis=1)
 
         return df
 
@@ -152,10 +134,10 @@ def prepare_type_dataframes(parameters_df, directory, tournament_type):
 if __name__ == "__main__":
 
     directory = sys.argv[1]
-    if sys.argv[2] == 'all':
+    if sys.argv[2] == "all":
         tournament_types = ["standard", "noise", "probend", "probend_noise"]
     else:
-        tournament_types = sys.argv[2].split(', ')
+        tournament_types = sys.argv[2].split(", ")
     version = sys.argv[3]
 
     print("Reading parameters data frame.")

### 2019-09-05 src/test_prepare_data.py

@@ -1,164 +1,0 @@
-import prepare_data
-import process_data
-import axelrod
-import pandas
-import numpy as np
-
-
-def test_specific_strategy_properties():
-
-    df = process_data.get_strategies_properties()
-
-    tit_for_tat = df[df["Name"] == "Tit For Tat"]
-    assert tit_for_tat.Name.all() == "Tit For Tat"
-    assert tit_for_tat.Memory_depth.values[0] == 1.0
-    assert tit_for_tat.Stochastic.all() == 0.0
-    assert tit_for_tat.Makes_use_of_game.all() == 0.0
-    assert tit_for_tat.Makes_use_of_length.all() == 0.0
-
-    adaptive = df[df["Name"] == "Adaptive"]
-    assert adaptive.Name.all() == "Adaptive"
-    assert adaptive.Memory_depth.values[0] == np.inf
-    assert adaptive.Stochastic.all() == 0.0
-    assert adaptive.Makes_use_of_game.all() == 1.0
-    assert adaptive.Makes_use_of_length.all() == 0.0
-
-
-parameters_df = prepare_data.get_parameters_data_frame(
-    directory="data/raw_data/"
-)
-
-
-def test_parameters_data_frame():
-    expected_columns = [
-        "index",
-        "noise",
-        "probend",
-        "repetitions",
-        "seed",
-        "size",
-        "turns",
-    ]
-    assert isinstance(parameters_df, pandas.DataFrame)
-    assert all(
-        [
-            column == expected_column
-            for column, expected_column in zip(
-                parameters_df.columns, expected_columns
-            )
-        ]
-    )
-
-
-def test_reader():
-    row = parameters_df.sample(n=1)
-    reader = prepare_data.Reader(row)
-
-    assert reader.noise_param.values[0] == row.noise.values[0]
-
-    assert reader.probend_param.values[0] == row.probend.values[0]
-    assert reader.seed.values[0] == row.seed.values[0]
-    assert reader.size.values[0] == row["size"].values[0]
-    assert reader.turns_param.values[0] == row.turns.values[0]
-
-
-def test_get_noise_df():
-    row = parameters_df.sample(n=1)
-    reader = prepare_data.Reader(row, "data/raw_data/")
-
-    noise = reader.get_noise_df()
-    assert isinstance(noise, pandas.DataFrame)
-    assert all(
-        [
-            column in noise.columns.values
-            for column in [
-                "Rank",
-                "Name",
-                "Median_score",
[…]

### 2019-09-05 src/test_process_data.py

@@ -1,63 +1,0 @@
-import numpy as np
-import pandas as pd
-
-import axelrod
-import process_data
-
-
-def test_strategies_properties():
-    df = process_data.get_strategies_properties()
-
-    assert isinstance(df, pd.DataFrame)
-    assert len(df) == len(axelrod.strategies)
-
-    for memory_depth in df["Memory_depth"]:
-        assert isinstance(memory_depth, float)
-
-    for use_of_game in df["Makes_use_of_game"]:
-        assert isinstance(use_of_game, int)
-
-    for use_of_length in df["Makes_use_of_length"]:
-        assert isinstance(use_of_length, int)
-
-
-def test_get_error_for_row():
-    row = {
-        "CC_to_C_rate": 0,
-        "CD_to_C_rate": 0,
-        "DC_to_C_rate": 0,
-        "DD_to_C_rate": 0,
-    }
-    error = process_data.get_error_for_row(row)
-    assert error < 0.1
-
-
-def test_get_normalised_rank():
-    row = {"Rank": 1, "size": 11}
-    normalised_rank = process_data.get_normalised_rank(row)
-
-    assert normalised_rank == 0.1
-
-
-def test_fix_name():
-    row = {"Name": "Tit For Tat: D"}
-    fixed_name = process_data.fix_name(row)
-
-    assert fixed_name == "Tit For Tat"
-
-
-def test_get_memory_percentage():
-    row_example_one = {"Memory_depth": np.Infinity}
-    assert process_data.get_memory_percentage(row_example_one) == 1
-
-    row_example_one = {"Memory_depth": 0}
-    assert process_data.get_memory_percentage(row_example_one) == 0
-
-    row_example_one = {"Memory_depth": 3, "size": 10}
-    assert process_data.get_memory_percentage(row_example_one) == 0.3
-
-
-def get_cooporation_rating_compared_to_max(row):
-    row = {"Cooperation_rating": 0.2, "Cooperation_rating_max": 0.8}
-
-    assert process_data.get_cooporation_rating_compared_to_max(row) == 0.25

### 2019-09-05 tests/test_prepare_data.py
create test file

@@ -1,0 +1,151 @@
+import imp
+
+import numpy as np
+import pandas
+
+import axelrod
+
+prepare_data = imp.load_source('prepare_data', 'src/prepare_data.py')
+parameters_df = prepare_data.get_parameters_data_frame(
+    directory="data/raw_data/"
+)
+
+
+def test_parameters_data_frame():
+    expected_columns = [
+        "index",
+        "noise",
+        "probend",
+        "repetitions",
+        "seed",
+        "size",
+        "turns",
+    ]
+    assert isinstance(parameters_df, pandas.DataFrame)
+    assert all(
+        [
+            column == expected_column
+            for column, expected_column in zip(
+                parameters_df.columns, expected_columns
+            )
+        ]
+    )
+
+def test_get_normalised_rank():
+    row = {"Rank": 1, "size": 11}
+    normalised_rank = prepare_data.get_normalised_rank(row)
+
+    assert normalised_rank == 0.1
+
+def test_reader():
+    row = parameters_df.sample(n=1)
+    reader = prepare_data.Reader(row)
+
+    assert reader.noise_param.values[0] == row.noise.values[0]
+
+    assert reader.probend_param.values[0] == row.probend.values[0]
+    assert reader.seed.values[0] == row.seed.values[0]
+    assert reader.size.values[0] == row["size"].values[0]
+    assert reader.turns_param.values[0] == row.turns.values[0]
+
+
+def test_get_noise_df():
+    row = parameters_df.sample(n=1)
+    reader = prepare_data.Reader(row, "data/raw_data/")
+
+    noise = reader.get_noise_df()
+    assert isinstance(noise, pandas.DataFrame)
+    assert all(
+        [
+            column in noise.columns.values
+            for column in [
+                "Rank",
+                "Name",
+                "Median_score",
+                "Cooperation_rating",
+                "Wins",
+                "CC_rate",
+                "CD_rate",
+                "DC_rate",
+                "DD_rate",
+                "noise",
+                "turns",
+            ]
+        ]
+    )
+
+
+def test_get_probend_noise_df():
+    row = parameters_df.sample(n=1)
+    reader = prepare_data.Reader(row, "data/raw_data/")
+
+    probend_noise = reader.get_probend_noise_df()
+    assert isinstance(probend_noise, pandas.DataFrame)
+    assert all(
+        [
+            column in probend_noise.columns.values
+            for column in [
+                "Rank",
+                "Name",
+                "Median_score",
+                "Cooperation_rating",
+                "Wins",
[…]

### 2019-09-05 tests/test_process_data.py

@@ -1,0 +1,67 @@
+import imp
+
+import numpy as np
+import pandas as pd
+
+import axelrod
+
+process_data = imp.load_source('processe_data', 'src/process_data.py')
+
+def test_strategies_properties():
+    df = process_data.get_strategies_properties()
+
+    assert isinstance(df, pd.DataFrame)
+    assert len(df) == len(axelrod.strategies)
+
+    for memory_depth in df["Memory_depth"]:
+        assert isinstance(memory_depth, float)
+
+    for use_of_game in df["Makes_use_of_game"]:
+        assert isinstance(use_of_game, int)
+
+    for use_of_length in df["Makes_use_of_length"]:
+        assert isinstance(use_of_length, int)
+
+
+def test_get_error_for_row():
+    row = {
+        "CC_to_C_rate": 0,
+        "CD_to_C_rate": 0,
+        "DC_to_C_rate": 0,
+        "DD_to_C_rate": 0,
+    }
+    error = process_data.get_error_for_row(row)
+    assert error < 0.1
+
+
+def test_fix_name():
+    row = {"Name": "Tit For Tat: D"}
+    fixed_name = process_data.fix_name(row)
+
+    assert fixed_name == "Tit For Tat"
+
+
+def get_cooporation_rating_compared_to_max(row):
+    row = {"Cooperation_rating": 0.2, "Cooperation_rating_max": 0.8}
+
+    assert process_data.get_cooporation_rating_compared_to_max(row) == 0.25
+
+def get_cooporation_rating_compared_to_median(row):
+    row = {"Cooperation_rating": 0.2, "Cooperation_rating_median": 0.8}
+
+    assert process_data.get_cooporation_rating_compared_to_median(row) == 0.25
+
+def get_cooporation_rating_compared_to_mean(row):
+    row = {"Cooperation_rating": 0.2, "Cooperation_rating_mean": 0.8}
+
+    assert process_data.get_cooporation_rating_compared_to_mean(row) == 0.25
+
+def get_cooporation_rating_compared_to_min(row):
+    row = {"Cooperation_rating": 0.2, "Cooperation_rating_min": 0.4}
+
+    assert process_data.get_cooporation_rating_compared_to_max(row) == 0.25
+
+def get_cooporation_rating_compared_to_min(row):
+    row = {"Cooperation_rating": 0.2, "Cooperation_rating_min": 0.0}
+
+    assert process_data.get_cooporation_rating_compared_to_max(row) == 0.0

### 2019-09-05 src/process_data.py
create test file

@@ -93,6 +93,8 @@ def get_cooporation_rating_compared_to_mean(row):
 
 
 def get_cooporation_rating_compared_to_min(row):
+    if row["Cooperation_rating_min"] == 0:
+        return row["Cooperation_rating_min"]
     return row["Cooperation_rating_min"] / row["Cooperation_rating"]
 
 

### 2019-09-05 src/cluster_analysis.py
tweats to clustering algorithm

@@ -157,10 +157,9 @@ if __name__ == "__main__":
         "CD_to_C_rate",
         "DC_to_C_rate",
         "DD_to_C_rate",
-        "SSeeror",
+        "SSE",
         "Makes_use_of_game",
         "Makes_use_of_length",
-        "Memory_usage",
         "Stochastic",
         "Cooperation_rating",
         "Cooperation_rating_max",
@@ -195,7 +194,7 @@ if __name__ == "__main__":
     sns.heatmap(corr_data[top_corr_features].corr(), annot=True, cmap="viridis")
 
     plt.savefig(
-        "%scorrelation_plot.pdf" % output_directory, bbox_inches="tight"
+        "%s_correlation_plot.pdf" % output_directory, bbox_inches="tight"
     )
     plt.close()
 
@@ -228,7 +227,7 @@ if __name__ == "__main__":
         .mean()
         .compute(num_workers=num_of_workers)
     )
-    means.to_csv("%smean_table" % (output_directory))
+    means.to_csv("%s_mean_table" % (output_directory))
 
     print("Random Forest Analysis")
     X = da.array(ddf[features].compute(num_workers=num_of_workers))
@@ -279,7 +278,7 @@ if __name__ == "__main__":
     for i, estimator in enumerate(sample_random_forest.estimators_):
         export_random_forest_tree(estimator, i, features, output_directory)
 
-    textfile = open("%soutput.txt" % output_directory, "w")
+    textfile = open("%s_output.txt" % output_directory, "w")
     textfile.write(output)
     textfile.close()
     client.close()

### 2019-09-06 src/cluster_analysis.py
run black and fix plot labels for clustering

@@ -7,7 +7,6 @@ import dask.array as da
 import dask.dataframe as dd
 import matplotlib
 
-matplotlib.use("Agg")
 import matplotlib.pyplot as plt
 import numpy as np
 import pandas as pd
@@ -25,7 +24,7 @@ import pydot
 from treeinterpreter import treeinterpreter as ti
 
 
-def cluster_analysis(data, ddf, columns, upper_n_clusters):
+def cluster_analysis(data, ddf, columns, upper_n_clusters, num_of_workers):
     num_of_clusters_to_fit = range(2, upper_n_clusters)
 
     silhouette_avgs = {}
@@ -57,6 +56,16 @@ def draw_clusters_plot(sample, upper_n_clusters, output_directory):
 
     for i, ax in enumerate(axes):
         ax.scatter(x, y, c=sample["Clusters: n = %s" % (i + 2)].compute())
+
+    fig.text(0.5, 0.04, r"$r$", ha="center", weight="bold")
+    fig.text(
+        0.075,
+        0.5,
+        "median score",
+        va="center",
+        rotation="vertical",
+        weight="bold",
+    )
 
     plt.savefig("%sclusters_plots.pdf" % output_directory, bbox_inches="tight")
     plt.close()
@@ -97,6 +106,25 @@ def random_forest_analysis(X, y, num_of_workers, n_estimators=10):
 def draw_feature_importance_bar_plot(
     X, importances, std, indices, features, output_directory
 ):
+    features_labels = {
+        "CC_to_C_rate": "$CC$ to $C$ rate",
+        "CD_to_C_rate": "$CD$ to $C$ rate",
+        "DC_to_C_rate": "$DC$ to $C$ rate",
+        "DD_to_C_rate": "$DD$ to $C$ rate",
+        "SSE": "SSE",
+        "Makes_use_of_game": "Make use of game",
+        "Makes_use_of_length": "Make use of lenght",
+        "Stochastic": "stochastic",
+        "Cooperation_rating": r"$C_r$",
+        "Cooperation_rating_max": r"$C_{max}$",
+        "Cooperation_rating_min": r"$C_{min}$",
+        "Cooperation_rating_median": r"$C_{median}$",
+        "Cooperation_rating_mean": r"$C_{mean}$",
+        "Cooperation_rating_comp_to_max": r"$C_r$ / $C_{max}$ ",
+        "Cooperation_rating_comp_to_min": r"$C_r$ / $C_{min}$",
[…]

### 2019-09-06 tests/test_process_data.py

@@ -5,7 +5,8 @@ import pandas as pd
 
 import axelrod
 
-process_data = imp.load_source('processe_data', 'src/process_data.py')
+process_data = imp.load_source("processe_data", "src/process_data.py")
+
 
 def test_strategies_properties():
     df = process_data.get_strategies_properties()
@@ -46,20 +47,24 @@ def get_cooporation_rating_compared_to_max(row):
 
     assert process_data.get_cooporation_rating_compared_to_max(row) == 0.25
 
+
 def get_cooporation_rating_compared_to_median(row):
     row = {"Cooperation_rating": 0.2, "Cooperation_rating_median": 0.8}
 
     assert process_data.get_cooporation_rating_compared_to_median(row) == 0.25
+
 
 def get_cooporation_rating_compared_to_mean(row):
     row = {"Cooperation_rating": 0.2, "Cooperation_rating_mean": 0.8}
 
     assert process_data.get_cooporation_rating_compared_to_mean(row) == 0.25
 
+
 def get_cooporation_rating_compared_to_min(row):
     row = {"Cooperation_rating": 0.2, "Cooperation_rating_min": 0.4}
 
     assert process_data.get_cooporation_rating_compared_to_max(row) == 0.25
+
 
 def get_cooporation_rating_compared_to_min(row):
     row = {"Cooperation_rating": 0.2, "Cooperation_rating_min": 0.0}

### 2019-09-06 tests/test_prepare_data.py
run black and fix plot labels for clustering

@@ -5,7 +5,7 @@ import pandas
 
 import axelrod
 
-prepare_data = imp.load_source('prepare_data', 'src/prepare_data.py')
+prepare_data = imp.load_source("prepare_data", "src/prepare_data.py")
 parameters_df = prepare_data.get_parameters_data_frame(
     directory="data/raw_data/"
 )
@@ -31,11 +31,13 @@ def test_parameters_data_frame():
         ]
     )
 
+
 def test_get_normalised_rank():
     row = {"Rank": 1, "size": 11}
     normalised_rank = prepare_data.get_normalised_rank(row)
 
     assert normalised_rank == 0.1
+
 
 def test_reader():
     row = parameters_df.sample(n=1)

### 2019-09-06 src/cluster_analysis.py
add labels for turns, noise and probend

@@ -113,7 +113,7 @@ def draw_feature_importance_bar_plot(
         "DD_to_C_rate": "$DD$ to $C$ rate",
         "SSE": "SSE",
         "Makes_use_of_game": "Make use of game",
-        "Makes_use_of_length": "Make use of lenght",
+        "Makes_use_of_length": "Make use of length",
         "Stochastic": "stochastic",
         "Cooperation_rating": r"$C_r$",
         "Cooperation_rating_max": r"$C_{max}$",
@@ -124,6 +124,9 @@ def draw_feature_importance_bar_plot(
         "Cooperation_rating_comp_to_min": r"$C_r$ / $C_{min}$",
         "Cooperation_rating_comp_to_median": r"$C_r$ / $C_{median}$",
         "Cooperation_rating_comp_to_mean": r"$C_r$ / $C_{mean}$",
+        "turns": r"$n$",
+        "noise": r"$p$",
+        "probend": r"$e$"
     }
     plt.figure()
     plt.title("Feature importances")
@@ -170,8 +173,8 @@ if __name__ == "__main__":
     else:
         num_of_workers = 4
 
-    input_directory = "data/%s_processed.csv" % file
-    output_name = file.split("_processed")[0]
+    input_directory = "data/%s_v_3_processed.csv" % file
+    output_name = file.split("_v_3_processed")[0]
 
     output_directory = "output/%s/" % output_name
     if not os.path.exists(output_directory):

### 2019-09-06 src/cluster_analysis.py
write medians instead of means

@@ -256,12 +256,12 @@ if __name__ == "__main__":
         num_of_clusters_to_fit, silhouette_avgs, chosen_n_cluster
     )
 
-    means = (
+    medians = (
         ddf.groupby(chosen_n_cluster)[clustering_on]
-        .mean()
+        .median()
         .compute(num_workers=num_of_workers)
     )
-    means.to_csv("%s_mean_table" % (output_directory))
+    medians.to_csv("%s_medians_table" % (output_directory))
 
     print("Random Forest Analysis")
     X = da.array(ddf[features].compute(num_workers=num_of_workers))

### 2019-09-06 src/cluster_analysis.py
get median table for clusters

@@ -126,7 +126,7 @@ def draw_feature_importance_bar_plot(
         "Cooperation_rating_comp_to_mean": r"$C_r$ / $C_{mean}$",
         "turns": r"$n$",
         "noise": r"$p$",
-        "probend": r"$e$"
+        "probend": r"$e$",
     }
     plt.figure()
     plt.title("Feature importances")
@@ -256,11 +256,11 @@ if __name__ == "__main__":
         num_of_clusters_to_fit, silhouette_avgs, chosen_n_cluster
     )
 
-    medians = (
-        ddf.groupby(chosen_n_cluster)[clustering_on]
-        .median()
-        .compute(num_workers=num_of_workers)
+    df = ddf[[chosen_n_cluster] + clustering_on].compute(
+        num_workers=num_of_workers
     )
+
+    medians = df.groupby(chosen_n_cluster)[clustering_on].median()
     medians.to_csv("%s_medians_table" % (output_directory))
 
     print("Random Forest Analysis")

### 2019-09-10 paper/main.tex
draft of first sections and will re-write evaluation section

@@
 
-The iterated prisoner's dilemma has been used for decades as a powerful model of
+The Iterated Prisoner's Dilemma has been used for decades as a powerful model of
 behavioural interactions. From the celebrated performance of Tit for Tat, to the
-introduction of the zero-determinant family, to the use of sophisticated
-strategies such as neural networks, the literature has been exploring the
-performance of strategies in the game for years. Most of these strategies
-are now accessible due to an open source package. This manuscript make use
-of the open source and it's strategy data base to a conducts a meta analysis of
-iterated prisoner's dilemma tournaments. The aim is to evaluate the performance
-of these strategies and finally answer the question: which is the best strategy
-in the game?
+introduction of the zero-determinant strategies, to the use of sophisticated
+structures such as neural networks, the literature has been exploring the
+performance of strategies in the game for years. Most of these strategies are
+now accessible due to an open source package; Axelrod-Python. This manuscript
+make use of Axelrod-Python to conduct a meta analysis of 40000 Iterated
+Prisoner's Dilemma tournaments. The aim is to evaluate the performance of
+numerous strategies and finally answer the explore the factors of success in the
+game.
 \end{abstract}
@@
 
-The iterated prisoner's dilemma is a repeated two player game that models
+The Iterated Prisoner's Dilemma (IPD) is a repeated two player game that models
 situations in which self-interest clashes with collective interest. At each turn,
 the players simultaneously and independently make a choice between cooperation (C) and
-defection (D) whilst their prior interactions matter. The payoffs at each given turn are defined by the matrix,
+defection (D) whilst having memory of the prior interactions.
+The payoffs at each given turn are defined by the matrix,
 
@@
 are published in the field regarding the performance of strategies in the
-iterated prisoner's dilemma. In the 80's following the strong performance of Tit For Tat
+IPD. In the 80's following the strong performance of Tit For Tat
 in both Axelrod's computer tournaments~\cite{Axelrod1980a, Axelrod1980b}, and
@@
 
+In 2004, the Anniversary Iterated Prisoner Dilemma Tournament was run with 233
+entries. The winning strategies were based on a mechanism of teams. A team from
+Southampton University took advantage of the fact that a participant was allowed
+to submit multiple strategies. They submitted a total of 60 of strategies that
+could recognised each other and colluded to increase one members
+score~\cite{J.P.Delahaye1993Lp, J.P.Delahaye1995LIeP, A.Rogers2007Ctpw}.
+
 Yet again, in 2012 another set of strategies was introduced as the dominant set
@@
 they will never receive less than their opponents. However, in~\cite{Harper2017}
-a tournament containing over 200 strategies, including the zero-determinant strategies
-introduced in~\cite{Press2012}, was performed and none of the zero-determinant
-strategies ranked in top spots. Instead, the top ranked strategies were a set of
-trained strategies based lookup tables, hidden markov models and finite state
-automata.
+a tournament containing over 200 strategies, zero-determinant, was performed and
+none of the zero-determinant strategies ranked in top spots. Instead, the top
+ranked strategies were a set of evolved strategies based lookup tables, hidden
+markov models and finite state automata.
 %TODO reference the archetypes of the archetypes used the IPD?
@@
 strategies in the iterated prisoner's dilemma?
-
 This manuscript uses the open source package
@@
 tournaments using as many strategies as possible from the literature. The aim is
-evaluate the performance of these strategies in a tournament and futhermore,
+to evaluate the performance of these strategies in a tournament and futhermore,
 explore the factors of their success. This is done not for standard round robin
@@
 
-The structure of this manuscript is as follows. In
-Section~\ref{section:data_collection} the data collection is covered. In
-Section~\ref{section:top_performances}, the best performed strategies for each
-type of tournament and overall are presented.
+The different tournaments and the data generating process are covered in
+Section~\ref{section:data_collection}. Section~\ref{section:top_performances},
+covers the best performed strategies for each type of tournament and overall.
 Section~\ref{section:evaluation_of_performance}, explores the traits which
 contribute to good performance and finally in Section~\ref{section:conclusion}
-we conclude and summarise the results.
+the results are discussed and summarised.
 
@@
 
-For the purposes of this manuscript a data set containing results on iterate
-prisoner's dilemma tournaments has been generated, which is available at. This
+For the purposes of this manuscript a data set containing results on IPD tournaments
+has been generated and is available at. This
 was done using the open source package Axelrod-Python~\cite{axelrodproject},
 more specifically, version 3.0.0. Axelrod-Python allows for different types of
-iterated prisoner's dilemma computer tournaments to be simulated whilst
-containing a list of over 190 strategies. Most of these are strategies described
+IPD computer tournaments to be simulated whilst
+containing a list of over 180 strategies. Most of these are strategies described
 in the literature with a few exceptions being strategies that have been
@@
 in~\cite{Axelrod1980a}. There are \(N\) strategies which all play an iterated
-game of \(n\) number of turns against each other. Note that self interactions and
-a match against a random strategy are not included. Similarly, \textbf{noisy tournaments}
-have \(N\) strategies and \(n\) number of turns but at each turn there is a
-probability \(p\) that a player's action will be flipped.
+game of \(n\) number of turns against each other. Note that self interactions
+and a match against a random strategy are not included. Similarly, \textbf{noisy
+tournaments} have \(N\) strategies and \(n\) number of turns but at each turn
+there is a probability \(p\) that a player's action will be flipped.
 \textbf{Probabilistic ending tournaments}, are of size \(N\) and after each turn
@@
 \(p\) and an ending probability \(e\). For smoothing the simulated results a
-tournament is repeated for \(r\) number of times and the ranks are based on the
-average score a strategy achieved and not by number of wins. A summary of
-each tournaments' parameters is given in Table~\ref{table:tournaments_parameters}.
+tournament is repeated for \(k\) number of times. The winner of each tournament
+is based on the average score a strategy achieved and not by number of wins.
+
+%  A summary of
+% each tournaments' parameters is given in Table~\ref{table:tournaments_parameters}.
+
+% \begin{table}[!htbp]
+%     \begin{center}
+%         \resizebox{.85\textwidth}{!}{
+%         \begin{tabular}{lcccccc}
+%     \toprule
+%     tournament type & number of strategies & repetitions & turns & noise probability & probability of match ending \\
+%     \midrule
+%     standard & $N$ & k & $n$ & - & - \\
+%     noisy & $N$  & k & $n$ & $p$ & - \\
+%     probabilistic ending & $N$ & k & - & - & $e$ \\
+%     noisy probabilistic ending & $N$ & k & - & $p$ & $e$ \\
+%     \bottomrule
+%         \end{tabular}}
+%     \end{center}
+%     \caption{Tournament types' parameters.}
+%     \label{table:tournaments_parameters}
+% \end{table}
+
+The process of generating data implemented in this manuscript is given by
+Algorithm~\ref{algorithm:data_generation}. For each trial a random
+size \(N\) is selected, and from the list of 186 strategies
+in~\cite{axelrodproject}, a random list of \(N\) strategies is chosen. For the
+given list of strategies a standard, a noisy, a probabilistic ending and a noisy
+probabilistic ending tournament are performed and repeated \(k\) times.
+The parameters for the tournaments as well as the number of repetitions are
+selected once for each trial. The parameters and their respective minimum and
+maximum values are given by Table~\ref{table:parameters_values}.
 
@@
     \begin{center}
-        \resizebox{.85\textwidth}{!}{
-        \begin{tabular}{lccccc}
+        \resizebox{.6\textwidth}{!}{
+        \begin{tabular}{lcccc}
     \toprule
-    tournament type & number of strategies & turns & noise probability & probability of match ending \\
+    parameter & parameter explanation &   min value & max value \\
     \midrule
-    standard & $N$  & $n$ & - & - \\
-    noisy & $N$  & $n$ & $p$ & - \\
-    probabilistic ending & $N$  & - & - & $e$ \\
-    noisy probabilistic ending & $N$  & - & $p$ & $e$ \\
+    $N$ & number of strategies  & 3 & 195 \\
+    $k$ & number of repetitions  & 10 & 100 \\
+    $n$ & number of turns      & 1 & 200 \\
+    $p$ & probability of flipping action at each turn  & 0 & 1   \\
+    $e$ & probability of match ending in the next turn & 0 & 1   \\
     \bottomrule
@@
     \end{center}
-    \caption{Tournament types' parameters.}
-    \label{table:tournaments_parameters}
+    \caption{Data generation parameters' values}
+    \label{table:parameters_values}
 \end{table}
-
-The process of generating data implemented in this manuscript is given by
-Algorithm~\ref{algorithm:data_generation}. For each trial a random
-size \(N\) is selected, and from the list of 195 strategies
-in~\cite{axelrodproject}, a random list of \(N\) strategies is chosen. For the
-given list of strategies a standard, noise, probabilistic ending and a noisy
-probabilistic ending tournament are performed and repeated \(r\) times.
-The parameters for the tournaments as well as the number of repetitions are
-selected once for each trial. The parameters and their respective minimum and
-maximum values are given by Table~\ref{table:parameters_values}.
 
@@
         $\text{players} \gets  \text{randomly select $N$ players}$\;
-        $r \gets  \text{randomly select integer}\in [r_{min}, r_{max}]$\;
+        $k \gets  \text{randomly select integer}\in [k_{min}, k_{max}]$\;
         $n \gets  \text{randomly select integer}\in [n_{min}, n_{max}]$\;
@@
         \vspace{0.4cm}
-        $\text{result standard}$ $\gets$ Axelrod.tournament$(\text{players}, n, r)$\;
-        $\text{result noisy}$ $\gets$ Axelrod.tournament$(\text{players}, n, p, r)$\;
-        $\text{result probabilistic ending}$ $\gets$ Axelrod.tournament$(\text{players}, e, r)$\;
-        $\text{result noisy probabilistic ending}$ $\gets$ Axelrod.tournament$(\text{players}, p, e, r)$\;
+        $\text{result standard}$ $\gets$ Axelrod.tournament$(\text{players}, n, k)$\;
+        $\text{result noisy}$ $\gets$ Axelrod.tournament$(\text{players}, n, p, k)$\;
+        $\text{result probabilistic ending}$ $\gets$ Axelrod.tournament$(\text{players}, e, k)$\;
+        $\text{result noisy probabilistic ending}$ $\gets$ Axelrod.tournament$(\text{players}, p, e, k)$\;
 
@@
 
-\begin{table}[!htbp]
-    \begin{center}
-        \resizebox{.6\textwidth}{!}{
-        \begin{tabular}{lcccc}
-    \toprule
-    parameter & parameter explanation &   min value & max value \\
-    \midrule
-    $N$ & number of strategies  & 3 & 195 \\
-    $r$ & number of repetitions  & 10 & 100 \\
-    $n$ & number of turns      & 1 & 200 \\
-    $p$ & probability of flipping action at each turn  & 0 & 1   \\
-    $e$ & probability of match ending in the next turn & 0 & 1   \\
-    \bottomrule
-        \end{tabular}}
-    \end{center}
-    \caption{Data generation parameters' values}
-    \label{table:parameters_values}
-\end{table}
-
 A total of 12,285 trials of Algorithm~\ref{algorithm:data_generation} have been
@@
 retrieved. Each tournament outputs a result summary in the form of
-Table~\ref{table:output_result}. The result summary has a length \(N\) because
-each row contains information for each strategy that participated in the tournament.
-The information include the strategy's rank $(R)$, median score, the rate with
-which the strategy cooperated $(C_r)$, it's wins and the probability that the strategy
-cooperated in the opening move. Moreover the summary result includes the rates
-of a strategy being in any of the four states ($CC, CD, DC, DD$), and the rate
-of which the strategy cooperated after each state.
+Table~\ref{table:output_result}.
+
+The result summary has a length \(N\) because each row contains information for
+each strategy that participated in the tournament. The information include the
+strategy's rank, median score, the rate with which the strategy cooperated
+$(C_r)$, it's wins and the probability that the strategy cooperated in the
+opening move. Moreover, the rates of a strategy being in any of the four states
+($CC, CD, DC, DD$), and the rate of which the strategy cooperated after each
+state.
 
@@
     & & & & & &   \multicolumn{8}{g}{Rates}  \\
-    Rank $(R)$ & Name & Median score & Cooperation rating $(C_r)$ & Win & Initial C &
+    Rank & Name & Median score & Cooperation rating $(C_r)$ & Win & Initial C &
     CC & CD & DC & DD & CC to C & CD to C & DC to C & DD to C \\
@@
 
-Several other measures have been manually calculated/retrieved and have been
-included in the data set. These include properties of the strategies as well as
-measures regarding the tournament, such as the parameters of
-Table~\ref{table:parameters_values}. All these measures are summarized and
-described Table~\ref{table:manual_measures}.
-
-\newcolumntype{g}{>{\columncolor{Gray}}c}
-\begin{table}[h]
-    \begin{center}
-    \resizebox{\textwidth}{!}{
-    \begin{tabular}{gcgcgc}
-    \toprule
-    measure & measure explanation &  source & value type & min value & max value \\
-    \midrule
-normalized rank $(r)$ & The rank of the strategy divided by the tournament size & result summary & float & 0 & 1 \\
-memory depth &  Strategy's memory size & strategy classifier from~\cite{axelrodproject} & integer & 0 & $\infty$ \\
-stochastic  &  If a strategy is stochastic & strategy classifier from~\cite{axelrodproject} & boolean  & False &  True \\
-makes use of game &  If a strategy makes used of the game information & strategy classifier from~\cite{axelrodproject} & boolean  & False &  True \\
-makes use of length &  If a strategy makes used of the number of turns & strategy classifier from~\cite{axelrodproject} & boolean  & False &  True \\
-SSE & A measure of how far a strategy is from extortionate behaviour & method described in [ref] & float & 0 & 1 \\
-max cooperating rate $(C_{\text{max}})$  & The biggest cooperating rate in the tournament & result summary & float & 0 & 1 \\
-min cooperating rate $(C_{\text{min}})$ & The smallest cooperating rate in the tournament & result summary & float & 0 & 1 \\
-median cooperating rate $(C_{\text{median}})$ & The median cooperating rate in the tournament & result summary & float & 0 & 1 \\
-mean cooperating rate $(C_{\text{mean}})$ & The mean cooperating rate in the tournament & result summary & float & 0 & 1 \\
-$C_r$ / $C_{\text{max}}$ & A strategy's cooperating rate divided by the maximum & manually & float & 0 & 1 \\
-$C_r$ / $C_{\text{min}}$ & A strategy's cooperating rate divided by the minimum & manually & float & 0 & 1 \\
-$C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median & manually & float & 0 & 1 \\
-$C_r$ / $C_{\text{mean}}$ & A strategy's cooperating rate divided by the mean & manually & float & 0 & 1 \\
-    \bottomrule
-        \end{tabular}}
-    \end{center}
-    \caption{Manually calculated/retrieved measures.}
-    \label{table:manual_measures}
-    \end{table}
-
-These measures will be used in more detail in the following sections.
-
-% Might move these measures to the sections in which they are actual used as
-% it feels like an overload of info in this section.
-
-The data collection and the output from the generated tournaments have been
-covered in this section. The measures that will be used in the analysis of the
-following sections have been presented. These are also summarised in Table in
-the Appendix. In the following Section, the top performances at each tournament
-are overall are presented.
+The normalised rank is a measure which was manually included. The normalised
+rank, denoted as $r$, is calculated as a strategy's rank divided by the
+tournament's size ($N$). The normalised rank will be used in the next section to
+evaluate the performance of strategies.
 
@@
 
-This section evaluates the performance of 186 strategies. These can be find in
+This section evaluates the performance of 186 strategies which can be found in
 the Appendix. The performance of each strategy will be evaluated for each type
@@
 strategies are evaluated on their performance in standard tournaments, in
-Section~\ref{subsection:noisy_tournament} in noisy, and the rest in
-Sections~\ref{subsection:probend_tournament}
-and~\ref{subsection:noisy_probend_tournament}.
+Section~\ref{subsection:noisy_tournament} in noisy, in
+Sections~\ref{subsection:probend_tournament} in probabilistic ending and in
+\ref{subsection:noisy_probend_tournament} in noisy probabilistic ending.
 
-Each tournament could have participated in multiple tournaments of the same
-type. On average a strategy participated in 5690 different tournaments of each
-type. For example Tit For Tat has participated in a total of 5569 standard
-tournaments. The strategy's normalised ranks distribution is given in
-Figure~\ref{fig:tit_for_tat_r_distribution}. As a result, of the multiple entries of
-strategies their performance in this manuscript is evaluated based on the median
-normalised rank denoted as \(\bar{r}\). Note that a value of \(\bar{r} = 0\)
-means that a strategy the winner of the tournament where a value of \(\bar{r} = 1\)
-means that the strategy came last.
+Each strategy could have participated in multiple tournaments of the same type
+(on average each participated in 5690 different tournaments). For example Tit
+For Tat has participated in a total of 5569 standard tournaments. The strategy's
+normalised rank distribution in different tournament is given in
+Figure~\ref{fig:tit_for_tat_r_distribution}. As a result, of the multiple
+entries of strategies their performance is evaluated based on the median
+normalised rank denoted as \(\bar{r}\). A value of \(\bar{r} = 0\) corresponds
+to a strategy winning the tournament where a a value of \(\bar{r} = 1\)
+corresponds to the strategy coming last.
 
-\begin{figure}
+\begin{figure}[!htbp]
     \centering
-    \includegraphics[width=.5\textwidth]{../images/tit_for_tat_r_distribution.pdf}
-    \caption{Tit For Tat's $r$ distribution for standard tournaments.}
+    \includegraphics[width=.8\textwidth]{../images/tit_for_tat_r_distributions.pdf}
+    \caption{Tit For Tat's $r$ distribution in tournaments.}
     \label{fig:tit_for_tat_r_distribution}
@@
 the results are merged and the strategies are evaluated in their overall performances
-over all the different tournaments.
+over all simulated tournaments of this work.
 
-\subsection{Standard tournaments}\label{subsection:standard_tournament}
+\subsection{Top ranked strategies in: Standard tournaments}\label{subsection:standard_tournament}
 
 The results presented in this section are based on $12,285$ different standard
-tournaments. Each tournament has on average 122 participants, a length of
-100 turns and was repeated 55 times.
-
-The top 15 performances in standard tournaments are given by
-Table~\ref{table:std_results}. The 10 out of the 15 are strategies introduced
-in~\cite{Harper2017}. These have been trained using FSM (finite state automata),
-HMM (hidden markov models), ANN (artificial neural networks), lookup tables
-(LookerUp) and stochastic lookup tables (Gambler). Specifically, the have been
-trained using the strategy list of~\cite{axelrodproject} in standard
-tournaments. Thus their performance was to be expected. DoubleCrosser, and Fool
-Me Once, are not from the literature but from~\cite{axelrodproject}.
-DoubleCrosser is a strategy that makes use of the length of the match because is
-set to defect on the last two rounds. The strategy is expected to not perform as
-well in probabilistic ending tournaments. Finally, Winner 12~\cite{Mathieu2017}
-and DBS are both from the the literature. DBS~\cite{Au2006} is strategy
-specifically designed for noisy environments, however, it ranks highly only in
-standard ones.
+tournaments.
+The top 15 performances in standard tournaments are given in
+Table~\ref{table:std_results}. Ten of these are strategies introduced
+in~\cite{Harper2017}. These have been trained using reinforcement learning
+algorithms and are based on finite state automata (FSM), hidden markov models
+(HMM), artificial neural networks (ANN), lookup tables (LookerUp) and stochastic
+lookup tables (Gambler). Specifically, the have been trained against the
+strategy list of~\cite{axelrodproject} in standard tournaments. Thus their
+performance is to be expected. DoubleCrosser, and Fool Me Once, are not from
+the literature but from~\cite{axelrodproject}. DoubleCrosser is a strategy that
+makes use of the length of the match because is set to defect on the last two
+rounds. The strategy is expected to not perform as well in probabilistic ending
+tournaments. Finally, Winner 12~\cite{Mathieu2017} and DBS are both from the the
+literature. DBS~\cite{Au2006} is strategy specifically designed for noisy
+environments, however, it ranks highly only in standard ones.
 
@@
     \centering
-    \resizebox{.3\textwidth}{!}{
+    \resizebox{.28\textwidth}{!}{
     \input{performance_standard_table.tex}}
@@
 
-The distributions of $\bar{r}$ for top ranked strategies are given in
-Figure~\ref{fig:std_results}. The distributions are skewed towards zero and the
-highest median is at 0.075. These strategies would mostly rank high when they
-participated in a tournament. This is not true for the rest of the tournament
-types. In the following sections $\bar{r}$ and subsequently the performances are
-more variant.
+Figure~\ref{fig:std_results} gives the distributions of $\bar{r}$ for the top
+ranked strategies. The distributions are skewed towards zero and the highest
+median is at 0.075. This indicates that the top ranked strategies are dominating
+strategies in standard tournaments. They are very likely to perform well in
+standard tournament despite the number of opponents, the opponents, the turns
+etc. This does not hold for all the tournament types as it will be discussed
+in the following sections. The next section present the results of noisy
+tournaments.
 
@@
     \centering
-    \includegraphics[width=.8\textwidth]{../images/performance_standard.pdf}
+    \includegraphics[width=.7\textwidth]{../images/performance_standard.pdf}
     \caption{$\bar{r}$ distributions of top 15 strategies.}\label{fig:std_results}
@@
 
-\subsection{Noisy tournaments}\label{subsection:noisy_tournament}
+\subsection{Top ranked strategies in: Noisy tournaments}\label{subsection:noisy_tournament}
 
@@
 Table~\ref{table:noisy_results}. The distributions of their corresponding
-\(\bar{r}\) is also given by Figure~\ref{fig:noisy_results}.
+\(\bar{r}\) is also given in Figure~\ref{fig:noisy_results}.
 
-The top strategies include two well known strategies Tit For 2
-Tats~\cite{Axelrod1980b} and Hard Tit For 2 Tats~\cite{Stewart2012} which are
+The top strategies include the two strategies, Tit For 2
+Tats~\cite{Axelrod1980b} and Hard Tit For 2 Tats~\cite{Stewart2012}, which are
 strategies that will defect only after the have received two defections from the
-opponent. The Retaliate strategies are set of strategies from~\cite{axelrodproject}
-that start by cooperating but will retaliate once the opponent's wins and
-defections surpass a curtain threshold. Strategies ShortMem~\cite{Carvalho2013},
-Grumpy, $e$ and $\phi$ are strategies that make decisions based on the
-cooperations to defections. Cycler Hunter tries to extort strategies that play
-cyclically and Risky QLearn uses a Q learning algorithm. Notably a very simple
-strategy, Cooperator, has been ranked third.
+opponent. The Retaliate strategies are set of strategies
+from~\cite{axelrodproject} that start by cooperating but will retaliate once the
+opponent's wins and defections surpass a curtain threshold.
+ShortMem~\cite{Carvalho2013}, Grumpy, $e$ and $\phi$ are strategies that make
+decisions based on the cooperations to defections ratio. In $5^{\text{th}}$ and
+$6^{\text{th}}$ place are the strategies Cycler Hunter and  Risky QLearn. Cycler
+Hunter tries to extort strategies that play cyclically and Risky QLearn uses a Q
+learning algorithm. Notably, a deterministic and one of the most simple
+strategies in game is ranked $3^{\text{rd}}$. That is Cooperator, a strategy
+that just cooperates.
 
@@
     \centering
-    \resizebox{.28\textwidth}{!}{
+    \resizebox{.25\textwidth}{!}{
     \input{performance_noise_table.tex}}
@@
 in noisy environments are more variant and have higher median values compared
-to standard tournament. Moreover, the distributions are skewed both towards
-0 and 1 which indicate that the top ranked strategies ranked first and last
-in several tournaments. However, the low values of the median shows that the
-have won most of the tournaments.
+to standard tournaments. The distributions are skewed both towards
+0 and 1 which indicates that though the top ranked strategies mainly
+performed well (medians $< 0.3$) there are several tournaments that they performed
+worse than the 60\% of the participants.
 
@@
     \centering
-    \includegraphics[width=.8\textwidth]{../images/performance_noise.pdf}
+    \includegraphics[width=.7\textwidth]{../images/performance_noise.pdf}
     \caption{\(\bar{r}\) distributions for best performed strategies in noisy tournaments.}
@@
 
-\subsection{Probabilistic ending tournaments}\label{subsection:probend_tournament}
+\subsection{Top ranked strategies: Probabilistic ending tournaments}\label{subsection:probend_tournament}
 
-In this section the performances in probabilistic ending tournaments are discussed.
-The 15 top ranked strategies are given by Table~\ref{table:prob_end_results}
-and their respective $\bar{r}$ distributions in Figure~\ref{fig:probend_results}.
-
+In this section the performances in probabilistic ending tournaments are
+discussed. The 15 top ranked strategies are given by
+Table~\ref{table:prob_end_results} and Figure~\ref{fig:probend_results} gives
+their respective $\bar{r}$ distributions.
 Fortress 3, Fortress 4 (both introduced in~\cite{Ashlock2006}),
@@
 based on finite state automata introduced by Daniel and Wendy Ashlock. These
-strategies have been evolved using reinformed learning. However, there were
-trained to maximise their payoffs in tournaments with fixed turns, 150
-specifically, and not in probabilistic ending tournaments.
+strategies have been evolved using reinformed learning, however, there were
+trained to maximise their payoffs in tournaments with fixed turns (150
+specifically) and not in probabilistic ending ones.
 
-Better and Better, Gradual Killer, Hard Prober are strategies from PRISON which
-is a research software tool for the prisoner's dilemma available
-at~\cite{prison}. These, including Bully (Reverse Tit For
-Tat)~\cite{Nachbar1992}, are strategies that are less cooperative strategies and
-more defective. Furthermore, Defector is a strategy which always defects.
-Interestingly, the last two strategies are EasyGo and Fool Me Forever. These
-strategies are actually the same. The will defect until their opponent defect,
-then they will cooperate until the end. Though we would have guessed that these
-two would have been taken advantage off both scored very highly and based on
-their distributions (Figure~\ref{fig:probend_results}) there have managed to win
-tournaments.
+In probabilistic ending tournaments it appears that the top ranks are mostly
+occupied by defecting strategies which include Better and Better, Gradual
+Killer, Hard Prober (all from ~\cite{prison}), Bully (Reverse Tit For
+Tat)~\cite{Nachbar1992} and Defector. Thus, it's surprisingly that EasyGo and
+Fool Me Forever are ranked $14^{\text{th}}$ and $15^{\text{th}}$. These
+strategies are actually the same; they will defect until their opponent defect,
+then they will cooperate until the end. Both strategies have repeatedly ranked highly
+as shown in Figure~\ref{fig:probend_results} and there are cases for which they
+were the winners of tournaments.
 
@@
     \centering
-    \resizebox{.28\textwidth}{!}{
+    \resizebox{.25\textwidth}{!}{
     \input{performance_probend_table.tex}}
@@
 
-The distributions of ranks in probabilistic ending tournaments are less variant
-than those of noisy tournaments. The uncertainty in the number of turns does not
-seem to be having the same effect. The medians are lower than 0.1 and the
-distributions are skewed towards 0. These suggest that the strategies performed
+The distributions of the normalised rank in probabilistic ending tournaments are
+less variant than those of noisy tournaments. The medians are lower than 0.1 and the
+distributions are skewed towards 0. Though the large difference between the means
+and the medians indicates some outliers, the strategies have overall performed
 well in the tournaments that they participated.
@@
 
-This section presents the results in tournaments were there are two
-uncertainties. There is the uncertainty that a player's action will be flipped
-and there is the uncertainty that there will not be future interactions.
-The 15 top ranked strategies are given in Table~\ref{table:noisy_prob_end_results}.
-Several of these strategies were highly ranked in noisy tournaments as well
-but the same does not hold for the strategies which were highly ranked in
-probabilistic ending tournaments.
+This section presents the results in tournaments that have both noise and an
+unspecified number of turns. Several of the top ranked have been covered before
+because they were highly ranked in noisy tournaments as well,
+Table~\ref{table:noisy_prob_end_results}. However, strategies from the
+top ranks of probabilistic ending tournaments did not rank highly here.
+
+The Retaliates, $\phi, e$ and Anti Tit For Tat behaviour strategies appear to
+perform well in noisy environments. So these strategies performed well in this
+setting as well even though now the turns are not specified. The top ranked
+strategy is Alternator a strategy that alternate between cooperation and
+defection. Hopeless~\cite{Van2015} is a strategy that will only defect if and
+only if a mutual cooperation and the last three places are occupied by
+strategies based on a Q learning algorithm.
 
@@
     \centering
-    \resizebox{.28\textwidth}{!}{
+    \resizebox{.25\textwidth}{!}{
     \input{performance_probend_noise_table.tex}}
@@
 
-The top ranked strategy is Alternator a strategy that alternate between
-cooperation and defection. Alternator is followed by strategies that decide so
-that the ratio of cooperations and defections is close to the equivalent
-mathematical constants. Anti Tit For Tat is similar to Bully, which was covered
-in Section~\ref{subsection:noisy_tournament}, but starts of with cooperation and
-Hopeless~\cite{Van2015} a strategy that will only defect if and only if a mutual
-cooperation. The last spots are occupied by strategies based on the Q learning
-algorithm.
-
-Compared to the distributions in noisy environments,
-Section~\ref{subsection:noisy_tournament}, the distributions here are skewed
-towards the middle, Figure~\ref{fig:noisy_probend_results}. The medians are
-close to 0.5 which seems to indicate a less dominant performance of strategies
-in this environment.
+The three Q learning strategies are the only ones that have bimodal
+distributions of normalised ranks similar to those of
+Section~\ref{subsection:noisy_tournament}. In comparison, the rest of the
+distributions are skewed towards 0.3 to 0.4
+Figure~\ref{fig:noisy_probend_results}.
 
@@
     \includegraphics[width=.7\textwidth]{../images/performance_probend_noise.pdf}
-    \caption{\(\bar{r}\) distributions for best performed strategies in noisy probabilistic ending tournaments.}
+    \caption{\(\bar{r}\) distributions for best performed strategies in noisy
+    probabilistic ending tournaments.}
     \label{fig:noisy_probend_results}
@@
 four different tournaments. In standard tournaments the top ranked spots were
-dominated by strategies that have been trained using reinforcement learning
-techniques and have been maximised in a standard tournament against the same
-list of opponents that is being used here. These strategies dominated most
+dominated by complex strategies that have been trained using reinforcement learning
+techniques in a standard tournament. These strategies dominated most
 the tournaments that have been involved in. In noisy tournaments the top ranked
 strategies were all different to those of standard tournaments. Most of the
-top ranked strategies have been strategies that were trying to keep the defection
-and cooperation to a given ratio. These strategies had won most the tournaments
+top ranked strategies have been strategies that were trying to keep the defections
+and cooperations to a given ratio. These strategies had won most the tournaments
 in which they participated, however, they also ranked last in several tournaments.
@@
 set of tournaments were the highly ranked strategies have been covered before,
-more specifically, in noisy tournaments. In these tournaments however the
-distributions of the ranks had much variation and some strategies even had
-a $\bar{r}$ close to 0.5, indicating that there were successfully only 50\%
-of the time.
+more specifically, in noisy tournaments. However, in these tournaments the means
+and medians of the distributions were close to 0.4. Indicating that on average
+these strategies manage to beat only 60\% of the opponents.
 
-In the following section the performance of the strategies is evaluated again.
-However this time the results of the tournament types are included in the
+In the following section the performance of the strategies is evaluated again
+but this time the results of the tournament types are included in the
 analysis.
@@
 
-The data set which was described in Section~\ref{section:data_collection}
-contains results from 49,140 tournaments. The strategies have been ranked based
-on their $\bar{r}$ and the 15 top ranked strategies are given in
-Table~\ref{table:overall_results}. These include several strategies that have
-ranked in the top spots in the separate tournament analysis. The top 6 spaces
-are overtaken by Retaliate strategies, followed by BackStabber and
-DoubleCrosser. DoubleCrosser is just an extension of BackStabber. Nice Meta
-Winner and NMWE Memory One are strategies that are part of a team, Stein and
-Rapoport and Grudger are strategies from Axelrod's original tournament that came
-the 6th and 7th respectively. Forgeful Fool Me once is an extension to Grudger
-and PSO GAmer and Evolved are strategies again introduced in~\cite{Harper2017}.
+The data set described in Section~\ref{section:data_collection} contains results
+from 49,140 tournaments and the performances in this section are 
+based on these tournaments. The top ranked 15 strategies are given in
+Table~\ref{table:overall_results}. It includes several strategies that have
+ranked in the top spots in the separate tournament analysis.
+The top spaces are overtaken by the Retaliate strategies, followed by BackStabber
+and DoubleCrosser. DoubleCrosser is just an extension of BackStabber.
+Nice Meta Winner and NMWE Memory One are strategies based on teams of strategies
+and Stein and Rapoport and Grudger are strategies from Axelrod's original tournament
+where they came 6th and 7th respectively. Forgetful Fool Me Once is a similar
+strategy to Grudger but sometimes forgets and cooperates. Finally, both
+PSO Gambler and Evolved HMM 5 are strategies introduced in~\cite{Harper2017}.
 
@@
 
-The distributions between the first six strategies are very similar. From then
-onwards the distributions are skewed to both 0 and 1. The analysis
-of the data set gives us an indication of what performance is successful
-in cases that the environment is not known to you and the Retaliate family
-seem to be doing the trick.
+The top ranked strategies include a good mixture of strategies. PSO Gambler and
+Evolved HMM 5 are very complex strategies compared to Stein and Rapoport and
+Grudger that are strategies manually designed. There are strategies based on
+teams and the Retaliate strategies which have illustrated to do well in noise.
+The Retaliates' distributions are very similar to each other,
+Figure~\ref{fig:overall_results}, and different compared to the rest of the
+distributions.
 
@@
 
-In this section the top ranked performances were presented. These one done
-just by simply taking into account the ranks each strategy achieved in each
-tournament type and finally in the data set. Through the analysis only a few
-strategies seem to have been repeated, however, the winner were also
-completely different from type to type. Thus, what does make then successfully
-in those environments? The aim of the next section is that.
+However, are these strategies the answer as to how to play the IPD. The distributions
+of their ranks are given for all the tournaments individually. Figure illustrates
+that there are settings that these strategies perform well, that they perform
+badly and settings that they perform average. Thus the conclusion is that there
+is not a single dominant strategy in the IPD.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.8\textwidth]{../images/performance.pdf}
+    \caption{\(\bar{r}\) distributions for best performed strategies in data set.}
+    \label{fig:overall_results}
+\end{figure}
+
+In this section the top ranked performances were presented. This was not done in
+a single tournament of a given list of opponents, as many in the literature, but
+over a number of tournaments where the list and size could vary. Moreover, four
+different type of tournaments were performed in this work. Even with the large
+number of tournaments there some think that is evident, there is not a single
+best strategy. Though some strategies seem to be repeated, there are other
+tournament types that they are not. The top ranks are occupied but almost
+different strategies every time. And in the top spots the strategies behaviour
+differ. There are simple and complex, with small memory and large, deterministic
+and stochastic. Is there a single dominant strategy in the iterated prisoner's
+dilemma? We argue not.
+
+The aim of the next section is to understand which are the factors that made
+these strategies successful. In each setting separately but also overall.
 
@@
 
-In this section we evaluate what makes a strategy.
+This section explores the factors that contributed to the successful performance
+of strategies described in Section~\ref{section:top_performances}.
+The factors
+evaluated in this work are given by Table~\ref{table:manual_measures}. Several
+of these factors include measures regarding the strategies and it's behaviour
+however others are fixed from the tournament or even the type of tournament. The
+measures from Table 1 are also included.
+
+This is achieved by
+separating the strategies performances into successful ones and non. The performances
+are separated on the normalised rank and the median score using the clustering
+algorithm \(k-\)means~\cite{Arthur2007}. The number of clusters is not deterministic
+but the decision is based on the silhouette coefficients~\cite{Rousseeuw1987}.
+
+Consider the performances in the standard tournaments.
+Figure~\ref{fig:standard_clusters} gives the normalised rank against the median
+score for three trials of the clustering algorithm with number of clusters being
+2, 3 and 4. A number of 2 clusters gives the highest silhouette coefficient (0.66)
+and so it's selected for the standard tournaments. More specifically,
+being in cluster 1 corresponds to a low performance whereas being in cluster
+2 corresponds to a high performance. These are based on the median normalised
+rank and median score of each cluster as shown in Table~\ref{table:clusters}.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.7\textwidth]{../output/standard/clusters_plots.png}
+    \caption{Clustering trials for standard tournaments. A number of 2
+    clusters has been chosen with a silhouette score of  0.66 against 0.511 and 0.50
+    respectively.}\label{fig:standard_clusters}
+\end{figure}
+
+\begin{table}[!htbp]
+    \centering
+    \resizebox{.25\textwidth}{!}{
+    \begin{tabular}{lcc}
+    \toprule
+    Cluster                &   $\bar{r}$ & median score \\
+    \midrule
+    1 & 0.769 & 2.065 \\
+    2 & 0.263 & 2.639\\
+    \bottomrule
+    \end{tabular}}
+    \caption{Median normalised rank and median score of each cluster in standard tournaments.}
+    \label{table:clusters}
+\end{table}
+
+Now that the performances have been clustered the aim is to evaluate which
+factors affect the performances being in each respective cluster. The factors
+evaluated in this work are given by Table~\ref{table:manual_measures}. Several
+of these factors include measures regarding the strategies and it's behaviour
+however others are fixed from the tournament or even the type of tournament. The
+measures from Table 1 are also included.
+
+\newcolumntype{g}{>{\columncolor{Gray}}c}
+\begin{table}[h]
+    \begin{center}
+    \resizebox{\textwidth}{!}{
+    \begin{tabular}{gcgcgc}
+    \toprule
+    measure & measure explanation &  source & value type & min value & max value \\
+    \midrule
+stochastic  &  If a strategy is stochastic & strategy classifier from~\cite{axelrodproject} & boolean  & False &  True \\
+makes use of game &  If a strategy makes used of the game information & strategy classifier from~\cite{axelrodproject} & boolean  & False &  True \\
+makes use of length &  If a strategy makes used of the number of turns & strategy classifier from~\cite{axelrodproject} & boolean  & False &  True \\
+SSE & A measure of how far a strategy is from extortionate behaviour & method described in~\cite{Knight2019} & float & 0 & 1 \\
+max cooperating rate $(C_{\text{max}})$  & The biggest cooperating rate in the tournament & result summary & float & 0 & 1 \\
+min cooperating rate $(C_{\text{min}})$ & The smallest cooperating rate in the tournament & result summary & float & 0 & 1 \\
+median cooperating rate $(C_{\text{median}})$ & The median cooperating rate in the tournament & result summary & float & 0 & 1 \\
+mean cooperating rate $(C_{\text{mean}})$ & The mean cooperating rate in the tournament & result summary & float & 0 & 1 \\
+$C_r$ / $C_{\text{max}}$ & A strategy's cooperating rate divided by the maximum & manually & float & 0 & 1 \\
+$C_r$ / $C_{\text{min}}$ & A strategy's cooperating rate divided by the minimum & manually & float & 0 & 1 \\
+$C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median & manually & float & 0 & 1 \\
+$C_r$ / $C_{\text{mean}}$ & A strategy's cooperating rate divided by the mean & manually & float & 0 & 1 \\
+$CC$ to $C$ rate & The probability a strategy will cooperate after a mutual cooperation & result summary & float & 0 & 1 \\
+$CD$ to $C$ rate & The probability a strategy will cooperate after being betrayed by the opponent & result summary & float & 0 & 1 \\
+$DC$ to $C$ rate & The probability a strategy will cooperate after betraying the opponent & result summary & float & 0 & 1 \\
+$DD$ to $C$ rate & The probability a strategy will cooperate after a mutual defection & result summary & float & 0 & 1 \\
+    \bottomrule
+        \end{tabular}}
+    \end{center}
+    \caption{Manually calculated/retrieved measures.}
+    \label{table:manual_measures}
+\end{table}
+
+%memory depth &  Strategy's memory size & strategy classifier from~\cite{axelrodproject} & integer & 0 & $\infty$ \\
+
+To evaluated how significant each factor contribution was a random forest is
+applied to the performances of standard tournaments where the target value
+is their corresponding cluster. Figure~\ref{fig:importance_standard} gives the
+importance of each factor.
+The four factors that have affect more the performances of strategies
+in standard tournaments are the cooperation ratio compared to the mean, the SSE,
+the cooperation ratio compared to the median and the cooperating ratio after
+being betrayed by the opponent.
+
+\begin{figure}
+    \begin{minipage}{.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/standard_correlation_plot.pdf}
+    \end{minipage}
+    \begin{minipage}{.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/noise_correlation_plot.pdf}
+    \end{minipage}
+    \begin{minipage}{.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/probend_correlation_plot.pdf}
+    \end{minipage}
+    \begin{minipage}{.5\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/probend_noise_correlation_plot.pdf}
+    \end{minipage}
+\end{figure}
+
+To delved deeper into the results of the random forest and how each feature
+has helped to be clustered where you were the tree interpreter method
+described in~\cite{} is used. The strongest contributors to predicting that
+a performance was clustered in the successful class were the DC to D ratio,
+the SSE error, the size followed by the cooperating ratio compared to the mean.
+In comparison the strongest impact on being in the non successful cluster
+have the Cd to C rate and the cooperating ration compare to the median.
+
+\begin{figure}[!htbp]
+    \begin{minipage}{.6\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{../output/standard/_feature_importance_bar_plot.pdf}
+    \caption{Importance of features in standard tournaments.}
+    \label{fig:importance_standard}
+    \end{minipage}\hspace{.1cm}
+    \begin{minipage}{.35\textwidth}
+        \vspace{-1.5cm}
+        \centering
+        \resizebox{1.1\textwidth}{!}{
+        \input{tree_interpreter_std.tex}}
+        \caption{The average contribution of each factor in standard tournaments
+        based on the tree interpreter method.}
+    \end{minipage}
+\end{figure}
+
+The same approach is applied to the tournament types individually and in the
+merged performances fom the the tournament types. More specifically, in noisy
+tournament the normalised rank against the median score is given in
+Figure~\ref{fig:noise_clusters}, based on the silhouette coefficient the number
+of clusters is 3 in noisy tournaments. The performance of each cluster is
+a follows, being in cluster 1 corresponds to low performance, 2 in medium
+and 3 high, Table~\ref{table:clusters_noisy}.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.7\textwidth]{../output/noise/clusters_plots.png}
+    \caption{Clustering trials for noisy tournaments. A number of 3
+    clusters has been chosen with a silhouette score of 0.49 against 2 clusters
+    with a coefficient of 0.47 and 4 with 0.45.
+    respectively.}\label{fig:noise_clusters}
+\end{figure}
+
+\begin{table}[!htbp]
+    \centering
+    \resizebox{.25\textwidth}{!}{
+    \begin{tabular}{lcc}
+    \toprule
+    Cluster                &   $\bar{r}$ & median score \\
+    \midrule
+    1 & 0.788 & 2.096 \\
+    2 & 0.316 & 2.290 \\
+    3 & 0.097 & 3.012 \\
+    \bottomrule
+    \end{tabular}}
+    \caption{Median normalised rank and median score of each cluster in noisy tournaments.}
+    \label{table:clusters_noisy}
+\end{table}
+
+The two factor that appear to affect the performance in noisy tournaments, based on the
+average importance, are the cooperating ratio compared to the mean and the mean (Figure~\ref{fig:importance_noisy})
+with both having a strong effect to the contribution of being in the successful
+cluster Table~\ref{table:tree_interpreter_noise}.
+
+\begin{figure}[!htbp]
+    \begin{minipage}{.6\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{../output/noise/_feature_importance_bar_plot.pdf}
+    \caption{Importance of factors from Table 8 in noisy tournaments.}
+    \label{fig:importance_noisy}
+    \end{minipage}\hspace{.1cm}
+    \begin{minipage}{.35\textwidth}
+        \vspace{-1.5cm}
+        \centering
+        \resizebox{1.2\textwidth}{!}{
+        \input{tree_interpreter_noise.tex}}
+        \caption{The average contribution of each factor in standard tournaments
+        based on the tree interpreter method.}\label{table:tree_interpreter_noise}
+    \end{minipage}
+\end{figure}
+
+Similarly for probabilistic ending tournaments, the cluster are given by igure.. Winner is n = 2 with.
+'Clusters: n = 3': 0.51128060607311, 'Clusters: n = 2': 0.6705714418492148, 'Clusters: n = 4': 0.4980365221065629
+
+% \begin{table}[!htbp]
+%     \centering
+%     \resizebox{.25\textwidth}{!}{
+%     \begin{tabular}{lcc}
+%     \toprule
+%     Cluster                &   $\bar{r}$ & median score \\
+%     \midrule
+%     1 & 0.578 & 2.497 \\
+%     2 & 0.090 & 3.611 \\
+%     \bottomrule
+%     \end{tabular}}
+%     \caption{Median normalised rank and median score of each cluster}
+%     \label{table:clusters}
+% \end{table}
+
+% Mean and median as well as max.
 
 % \begin{figure}
+%     \begin{minipage}{.6\textwidth}
 %     \centering
-%     \includegraphics[width=.7\textwidth]{../output/output/standard/feature_importance_bar_plot.pdf}
+%     \includegraphics[width=\textwidth]{../output/probend/_feature_importance_bar_plot.pdf}
+%     \caption{Importance of factors from Table 8 in noise tournaments.}
+%     \label{fig:importance_standard}
+%     \end{minipage}\hspace{.1cm}
+%     \begin{minipage}{.35\textwidth}
+%         \vspace{-2cm}
+%         \centering
+%         \resizebox{1.2\textwidth}{!}{
+%         \input{tree_interpreter_probend.tex}}
+%         \caption{trying the caption}
+%     \end{minipage}
 % \end{figure}
 
+% \begin{figure}
+%     \begin{minipage}{.6\textwidth}
+%     \centering
+%     \includegraphics[width=\textwidth]{../output/probend_noise/_feature_importance_bar_plot.pdf}
+%     \caption{Importance of factors from Table 8 in noise tournaments.}
+%     \label{fig:importance_standard}
+%     \end{minipage}\hspace{.1cm}
+%     \begin{minipage}{.35\textwidth}
+%         \vspace{-2cm}
+%         \centering
+%         \resizebox{1.2\textwidth}{!}{
+%         \input{tree_interpreter_probend_noise.tex}}
+%         \caption{trying the caption}
+%     \end{minipage}
+% \end{figure}
 \section{Conclusion and Discussion}\label{section:conclusion}

### 2019-09-22 paper/main.tex
paper draft

@@
 where \(T > R > P > S\) and \(2R > T + S\). The most common values used in
-the literature, and in this paper, are $R=3, P=1, T=5, S=0$.
+the literature~\cite{Axelrod1981}, and in this paper, are $R=3, P=1, T=5, S=0$.
 
 Since the computer tournaments of R. Axelrod in 1980s several academic papers
-are published in the field regarding the performance of strategies in the
-IPD. In the 80's following the strong performance of Tit For Tat
-in both Axelrod's computer tournaments~\cite{Axelrod1980a, Axelrod1980b}, and
-moreover in a series of evolutionary experiments~\cite{Axelrod1981}, the strategy
-was thought as the most robust basic strategy in the iterated prisoner's
-dilemma. However, the strategy's poor performance in environments with
-noise~\cite{Bendor1991, Donninger1986, Molander1985, Hammerstein1984},
-made room for other protagonists, such as, Nice and Forgiving~\cite{Bendor1991},
-Pavlov~\cite{Nowak1993} and Generous Tit For Tat~\cite{Nowak1992}.
+are published in the field regarding the performance of strategies in the IPD.
+In the 80's following the strong performance of Tit For Tat in both Axelrod's
+computer tournaments~\cite{Axelrod1980a, Axelrod1980b}, and moreover in a series
+of evolutionary experiments~\cite{Axelrod1981}, the strategy was thought as the
+most robust basic strategy in the IPD. However, the strategy was shown to
+perform poorly in environments with noise~\cite{Bendor1991, Donninger1986,
+Molander1985, Hammerstein1984}. More robust strategy in such setting were
+introduced and were the new protagonists, such as, Nice and
+Forgiving~\cite{Bendor1991}, Pavlov~\cite{Nowak1993} and Generous Tit For
+Tat~\cite{Nowak1992}.
 
-In 2004, the Anniversary Iterated Prisoner Dilemma Tournament was run with 233
-entries. The winning strategies were based on a mechanism of teams. A team from
-Southampton University took advantage of the fact that a participant was allowed
-to submit multiple strategies. They submitted a total of 60 of strategies that
-could recognised each other and colluded to increase one members
-score~\cite{J.P.Delahaye1993Lp, J.P.Delahaye1995LIeP, A.Rogers2007Ctpw}.
-
+The $20^{\text{th}}$ Anniversary Iterated Prisoner Dilemma Tournament took place
+in 2004 with 233 entries. The winning strategies were based on a mechanism of
+teams. A team from Southampton University took advantage of the fact that a
+participant was allowed to submit multiple strategies. They submitted a total of
+60 of strategies that could recognised each other and colluded to increase one
+members score~\cite{J.P.Delahaye1993Lp, J.P.Delahaye1995LIeP, A.Rogers2007Ctpw}.
 Yet again, in 2012 another set of strategies was introduced as the dominant set
@@
 none of the zero-determinant strategies ranked in top spots. Instead, the top
-ranked strategies were a set of evolved strategies based lookup tables, hidden
-markov models and finite state automata.
-%TODO reference the archetypes of the archetypes used the IPD?
+ranked strategies were a set of evolved strategies based lookup
+tables~\cite{Axelrod1987}, hidden markov models~\cite{Harper2017} and finite
+state automata~\cite{Miller1996}.
+%TODO reference the archetypes of the archetypes used the IPD? Did IPD for now.
 
@@
 Section~\ref{section:evaluation_of_performance}, explores the traits which
-contribute to good performance and finally in Section~\ref{section:conclusion}
-the results are discussed and summarised.
+contribute to good performance and finally in Section~\ref{section:discussion}
+the results are discussed and concluded in Section~\ref{section:conclusion}.
 
@@
 size \(N\) is selected, and from the list of 186 strategies
-in~\cite{axelrodproject}, a random list of \(N\) strategies is chosen. For the
+in~\cite{axelrodproject}, a random list of \(N\) strategies is chosen. The 186
+strategies used here are given in the Appendix~\ref{app:list_of_players}. For the
 given list of strategies a standard, a noisy, a probabilistic ending and a noisy
@@
 
-The normalised rank is a measure which was manually included. The normalised
+The \textbf{normalised rank} is a measure which was manually included. The normalised
 rank, denoted as $r$, is calculated as a strategy's rank divided by the
@@
 
-This section evaluates the performance of 186 strategies which can be found in
-the Appendix. The performance of each strategy will be evaluated for each type
-of tournament independently. In Section~\ref{subsection:standard_tournament} the
-strategies are evaluated on their performance in standard tournaments, in
-Section~\ref{subsection:noisy_tournament} in noisy, in
-Sections~\ref{subsection:probend_tournament} in probabilistic ending and in
-\ref{subsection:noisy_probend_tournament} in noisy probabilistic ending.
-
-Each strategy could have participated in multiple tournaments of the same type
-(on average each participated in 5690 different tournaments). For example Tit
-For Tat has participated in a total of 5569 standard tournaments. The strategy's
-normalised rank distribution in different tournament is given in
-Figure~\ref{fig:tit_for_tat_r_distribution}. As a result, of the multiple
-entries of strategies their performance is evaluated based on the median
-normalised rank denoted as \(\bar{r}\). A value of \(\bar{r} = 0\) corresponds
-to a strategy winning the tournament where a a value of \(\bar{r} = 1\)
-corresponds to the strategy coming last.
+This section evaluates the performance of 186 strategies. The performance of
+each strategy will be evaluated for each type of tournament independently,
+followed by an evaluation of their performance over all the simulated
+tournaments of this work. Each strategy could have participated in multiple
+tournaments of the same type (on average each participated in 5690 different
+tournaments). For example Tit For Tat has participated in a total of 5569
+tournaments of each type. The strategy's normalised rank distribution in these
+is given in Figure~\ref{fig:tit_for_tat_r_distribution}. As a result, of the
+multiple entries of strategies their performance is evaluated based on the
+\textbf{median normalised rank} denoted as \(\bar{r}\). A value of \(\bar{r} =
+0\) corresponds to a strategy winning the tournament where a a value of
+\(\bar{r} = 1\) corresponds to the strategy coming last.
 
@@
     \includegraphics[width=.8\textwidth]{../images/tit_for_tat_r_distributions.pdf}
-    \caption{Tit For Tat's $r$ distribution in tournaments.}
+    \caption{Tit For Tat's $r$ distribution in tournaments. The best performance
+    of the strategy has been in standard tournaments where it achieved a normalised
+    rank of 0.339.}
     \label{fig:tit_for_tat_r_distribution}
@@
 
-Following the analysis of each tournament type, in Section~\ref{subsrction:overall}
-the results are merged and the strategies are evaluated in their overall performances
-over all simulated tournaments of this work.
+The result of each tournament type are based on $12,285$ trials. The strategies
+are ranked based on the median normalised rank they achieved and the top 15
+strategies of each tournament are given in Table~\ref{table:top_performances}.
 
-\subsection{Top ranked strategies in: Standard tournaments}\label{subsection:standard_tournament}
+\newcolumntype{g}{>{\columncolor{Gray}}l}
+\begin{table}[!htbp]
+    \begin{center}
+    \resizebox{.9\textwidth}{!}{
+        \input{top_perfomances.tex}
+    }
+\end{center}
+\caption{Top performances for each tournament type based on $\bar{r}$.}
+\label{table:top_performances}
+\end{table}
 
-The results presented in this section are based on $12,285$ different standard
-tournaments.
-The top 15 performances in standard tournaments are given in
-Table~\ref{table:std_results}. Ten of these are strategies introduced
+In standard tournaments 10 of the 15 top strategies are strategies introduced
 in~\cite{Harper2017}. These have been trained using reinforcement learning
@@
 strategy list of~\cite{axelrodproject} in standard tournaments. Thus their
-performance is to be expected. DoubleCrosser, and Fool Me Once, are not from
-the literature but from~\cite{axelrodproject}. DoubleCrosser is a strategy that
+performance is to be expected. DoubleCrosser, and Fool Me Once, are not from the
+literature but from~\cite{axelrodproject}. DoubleCrosser is a strategy that
 makes use of the length of the match because is set to defect on the last two
 rounds. The strategy is expected to not perform as well in probabilistic ending
-tournaments. Finally, Winner 12~\cite{Mathieu2017} and DBS are both from the the
+tournaments. Finally, Winner 12~\cite{mathieu2017} and DBS are both from the the
 literature. DBS~\cite{Au2006} is strategy specifically designed for noisy
 environments, however, it ranks highly only in standard ones.
-
-\begin{table}[!htbp]
-    \centering
-    \resizebox{.28\textwidth}{!}{
-    \input{performance_standard_table.tex}}
-    \caption{Standard top performances}\label{table:std_results}
-\end{table}
 
@@
 etc. This does not hold for all the tournament types as it will be discussed
-in the following sections. The next section present the results of noisy
-tournaments.
+in the later parts.
 
@@
     \includegraphics[width=.7\textwidth]{../images/performance_standard.pdf}
-    \caption{$\bar{r}$ distributions of top 15 strategies.}\label{fig:std_results}
+    \caption{$\bar{r}$ distributions of top 15 strategies in standard tournaments.}\label{fig:std_results}
 \end{figure}
 
-\subsection{Top ranked strategies in: Noisy tournaments}\label{subsection:noisy_tournament}
-
-Similarly to Section~\ref{subsection:standard_tournament} the results presented
-here are based on $12,285$ different noisy tournaments. The strategies have been
-ranked based on their \(\bar{r}\) and the top 15 are given by
-Table~\ref{table:noisy_results}. The distributions of their corresponding
-\(\bar{r}\) is also given in Figure~\ref{fig:noisy_results}.
-
-The top strategies include the two strategies, Tit For 2
+The top strategies in noisy tournaments include the two strategies, Tit For 2
 Tats~\cite{Axelrod1980b} and Hard Tit For 2 Tats~\cite{Stewart2012}, which are
@@
 that just cooperates.
-
-\begin{table}[!htbp]
-    \centering
-    \resizebox{.25\textwidth}{!}{
-    \input{performance_noise_table.tex}}
-    \caption{Noisy top performances}\label{table:noisy_results}
-\end{table}
 
@@
 
-\subsection{Top ranked strategies: Probabilistic ending tournaments}\label{subsection:probend_tournament}
-
-In this section the performances in probabilistic ending tournaments are
-discussed. The 15 top ranked strategies are given by
-Table~\ref{table:prob_end_results} and Figure~\ref{fig:probend_results} gives
-their respective $\bar{r}$ distributions.
+The 15 top ranked strategies in probabilistic ending tournaments include
 Fortress 3, Fortress 4 (both introduced in~\cite{Ashlock2006}),
-Raider~\cite{Ashlock2014} and Solution B1~\cite{Ashlock2014} are strategies
+Raider~\cite{Ashlock2014} and Solution B1~\cite{Ashlock2014} which are strategies
 based on finite state automata introduced by Daniel and Wendy Ashlock. These
@@
 specifically) and not in probabilistic ending ones.
-
 In probabilistic ending tournaments it appears that the top ranks are mostly
@@
 as shown in Figure~\ref{fig:probend_results} and there are cases for which they
-were the winners of tournaments.
-
-\begin{table}[!htbp]
-    \centering
-    \resizebox{.25\textwidth}{!}{
-    \input{performance_probend_table.tex}}
-    \caption{Probabilistic ending top performances}\label{table:prob_end_results}
-\end{table}
+were the winners of the tournament.
 
@@
 
-\begin{figure}[!htbp]
+\begin{figure}[h!]
     \centering
-    \includegraphics[width=.8\textwidth]{../images/performance_probend.pdf}
+    \includegraphics[width=.7\textwidth]{../images/performance_probend.pdf}
     \caption{\(\bar{r}\) distributions for best performed strategies in probabilistic ending tournaments.}
@@
 
-\subsection{Noisy \& probabilistic ending tournaments}\label{subsection:noisy_probend_tournament}
-
-This section presents the results in tournaments that have both noise and an
-unspecified number of turns. Several of the top ranked have been covered before
-because they were highly ranked in noisy tournaments as well,
-Table~\ref{table:noisy_prob_end_results}. However, strategies from the
-top ranks of probabilistic ending tournaments did not rank highly here.
-
-The Retaliates, $\phi, e$ and Anti Tit For Tat behaviour strategies appear to
-perform well in noisy environments. So these strategies performed well in this
-setting as well even though now the turns are not specified. The top ranked
-strategy is Alternator a strategy that alternate between cooperation and
-defection. Hopeless~\cite{Van2015} is a strategy that will only defect if and
-only if a mutual cooperation and the last three places are occupied by
-strategies based on a Q learning algorithm.
-
-\begin{table}[!htbp]
-    \centering
-    \resizebox{.25\textwidth}{!}{
-    \input{performance_probend_noise_table.tex}}
-    \caption{Noisy and probabilistic ending top performances}\label{table:noisy_prob_end_results}
-\end{table}
-
-The three Q learning strategies are the only ones that have bimodal
-distributions of normalised ranks similar to those of
-Section~\ref{subsection:noisy_tournament}. In comparison, the rest of the
-distributions are skewed towards 0.3 to 0.4
-Figure~\ref{fig:noisy_probend_results}.
+In tournaments that have both noise and an unspecified number of turns several
+of the top ranked strategies are strategies that were highly ranked in
+noisy tournaments as well. However, strategies from the top ranks of
+probabilistic ending tournaments did not rank highly here. The Retaliate set,
+$\phi, e$ and Anti Tit For Tat behaviour strategies appear to perform well in
+noisy environments. So these strategies performed well in this setting as well
+even though now the turns are not specified.
+The top ranked strategy is Alternator a strategy that alternate between
+cooperation and defection. Hopeless~\cite{Van2015} is a strategy that will only
+defect if and only if a mutual cooperation and the last three places are
+occupied by strategies based on a Q learning algorithm. The three Q learning
+strategies are the only ones that have bimodal distributions of normalised
+ranks. In comparison, the rest of the distributions are skewed towards
+0.4, Figure~\ref{fig:noisy_probend_results}.
 
@@
 
-As yet, the performances of 186 different strategies have been evaluated in
-four different tournaments. In standard tournaments the top ranked spots were
-dominated by complex strategies that have been trained using reinforcement learning
-techniques in a standard tournament. These strategies dominated most
-the tournaments that have been involved in. In noisy tournaments the top ranked
-strategies were all different to those of standard tournaments. Most of the
-top ranked strategies have been strategies that were trying to keep the defections
-and cooperations to a given ratio. These strategies had won most the tournaments
-in which they participated, however, they also ranked last in several tournaments.
-Once again in probabilistic ending tournaments the top ranked strategies were
-different to those before. More defecting strategies occupied the top ranks
-as well as finite state automata that have been introduced all by the same
-authors. Finally, in noisy probabilistic ending tournaments it was the only
-set of tournaments were the highly ranked strategies have been covered before,
-more specifically, in noisy tournaments. However, in these tournaments the means
-and medians of the distributions were close to 0.4. Indicating that on average
-these strategies manage to beat only 60\% of the opponents.
-
-In the following section the performance of the strategies is evaluated again
-but this time the results of the tournament types are included in the
-analysis.
-
-\subsection{Top performance in data set}\label{subsrction:overall}
-
-The data set described in Section~\ref{section:data_collection} contains results
-from 49,140 tournaments and the performances in this section are 
-based on these tournaments. The top ranked 15 strategies are given in
-Table~\ref{table:overall_results}. It includes several strategies that have
-ranked in the top spots in the separate tournament analysis.
-The top spaces are overtaken by the Retaliate strategies, followed by BackStabber
-and DoubleCrosser. DoubleCrosser is just an extension of BackStabber.
-Nice Meta Winner and NMWE Memory One are strategies based on teams of strategies
-and Stein and Rapoport and Grudger are strategies from Axelrod's original tournament
-where they came 6th and 7th respectively. Forgetful Fool Me Once is a similar
-strategy to Grudger but sometimes forgets and cooperates. Finally, both
-PSO Gambler and Evolved HMM 5 are strategies introduced in~\cite{Harper2017}.
-
 \begin{table}[!htbp]
@@
 
-The top ranked strategies include a good mixture of strategies. PSO Gambler and
-Evolved HMM 5 are very complex strategies compared to Stein and Rapoport and
-Grudger that are strategies manually designed. There are strategies based on
-teams and the Retaliate strategies which have illustrated to do well in noise.
-The Retaliates' distributions are very similar to each other,
-Figure~\ref{fig:overall_results}, and different compared to the rest of the
-distributions.
+So far the performances have been evaluated separately for each tournament
+type. The merged data set, which was described in Section~\ref{section:data_collection},
+contains a total of 49,140 result summaries. The 15 top ranked strategies
+overall are given in Table~\ref{table:overall_results}. The top ranks
+include strategies that have been mentioned before due to their performance
+in specific tournaments. The top ranks are overtaken by the set of Retaliate
+strategies followed by BackStabber and DoubleCrosser. DoubleCrosser performed
+well in standard tournaments and the strategy is just an extension of BackStabber.
+The two strategies Nice Meta Winner and NMWE Memory One are strategies based on teams.
+PSO Gambler and Evolved HMM 5 are trained strategies introduced in~\cite{Harper2017}
+and Stein and Rapoport and Grudger are strategies from Axelrod's
+original tournament where they came 6th and 7th respectively. Forgetful Fool Me
+Once is based on the same approach as Grudger.
+
+Figure~\ref{fig:overall_results} gives the normalised rank distributions
+of these strategies. It is evident that the Retaliate strategies performances
+are very similar and their distributions are different in comparison with the
+rest of the top ranked strategies in the setting.
 
@@
 
-However, are these strategies the answer as to how to play the IPD. The distributions
-of their ranks are given for all the tournaments individually. Figure illustrates
-that there are settings that these strategies perform well, that they perform
-badly and settings that they perform average. Thus the conclusion is that there
-is not a single dominant strategy in the IPD.
+This section presented the top ranked performances.
 
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.8\textwidth]{../images/performance.pdf}
-    \caption{\(\bar{r}\) distributions for best performed strategies in data set.}
-    \label{fig:overall_results}
-\end{figure}
+\begin{itemize}
+    \item In standard tournaments the top ranked spots were dominated by complex
+    strategies that have been trained using reinforcement learning techniques.
+    These strategies dominated most the tournaments that have been involved in.
+    \item In noisy tournaments the top ranked strategies were all different to those of standard
+    tournaments. Most of the top ranked strategies were basing their decisions
+    on the he defection to cooperation ratio. These
+    strategies had won most the tournaments in which they participated, however,
+    they also ranked last in several tournaments.
+    \item Once again in probabilistic ending tournaments the top ranked
+    strategies were different to those before. More defecting strategies
+    occupied the top ranks in this setting, as well as finite state automata
+    that have been introduced all by the same authors.
+    \item Moreover, in noisy probabilistic ending tournaments it was the only
+    set of tournaments were the highly ranked strategies have been covered
+    before, more specifically, in noisy tournaments. In these tournaments the
+    means and medians of the distributions were close to 0.4. Indicating that on
+    average these strategies managed to consistently perform on the top 40\% of
+    the strategies.
+    \item Finally, using all the tournaments results, despite their type, the top
+    ranked strategies were a mixture of behaviours that do well in standard
+    tournaments and tournaments with noise. The top ranks also included two
+    strategies that are based on teams.
+\end{itemize}
 
-In this section the top ranked performances were presented. This was not done in
-a single tournament of a given list of opponents, as many in the literature, but
-over a number of tournaments where the list and size could vary. Moreover, four
-different type of tournaments were performed in this work. Even with the large
-number of tournaments there some think that is evident, there is not a single
-best strategy. Though some strategies seem to be repeated, there are other
-tournament types that they are not. The top ranks are occupied but almost
-different strategies every time. And in the top spots the strategies behaviour
-differ. There are simple and complex, with small memory and large, deterministic
-and stochastic. Is there a single dominant strategy in the iterated prisoner's
-dilemma? We argue not.
+In this section the winning strategies in a series of IPD tournaments of
+different settings were presented. Though there have been instances of
+strategies that do well in more than one setting, most of the top ranks were
+occupied by different strategies each time. The top ranks have been occupied
+by strategies with small memory size, with infinite memory size, sophisticated
+and deterministic strategies. Even two of the most basic strategic rules,
+Cooperator and Defector, have been ranked in the top 15 places.
 
-The aim of the next section is to understand which are the factors that made
-these strategies successful. In each setting separately but also overall.
+This indicates that in an IPD tournament a winning strategy exist but only for
+the given environment, however, there is no dominant strategy in the IPD that
+can do well in any tournament where the settings can vary. The aim of the next
+section is to understand which are the factors that made these strategies
+successful. In each setting separately but also overall.
 
@@
 
-This section explores the factors that contributed to the successful performance
-of strategies described in Section~\ref{section:top_performances}.
-The factors
-evaluated in this work are given by Table~\ref{table:manual_measures}. Several
-of these factors include measures regarding the strategies and it's behaviour
-however others are fixed from the tournament or even the type of tournament. The
-measures from Table 1 are also included.
+The aim of this section is to explore the factors that contribute to a
+strategy's successful performance. The factors explored are measures regarding a
+strategy's behaviour but also measures regarding the tournaments the strategies
+competed in. More specifically the factors that are included in the analysis are
+given by Table~\ref{table:manual_measures} and
+Table~\ref{table:parameters_values}.
 
-This is achieved by
-separating the strategies performances into successful ones and non. The performances
-are separated on the normalised rank and the median score using the clustering
-algorithm \(k-\)means~\cite{Arthur2007}. The number of clusters is not deterministic
-but the decision is based on the silhouette coefficients~\cite{Rousseeuw1987}.
-
-Consider the performances in the standard tournaments.
-Figure~\ref{fig:standard_clusters} gives the normalised rank against the median
-score for three trials of the clustering algorithm with number of clusters being
-2, 3 and 4. A number of 2 clusters gives the highest silhouette coefficient (0.66)
-and so it's selected for the standard tournaments. More specifically,
-being in cluster 1 corresponds to a low performance whereas being in cluster
-2 corresponds to a high performance. These are based on the median normalised
-rank and median score of each cluster as shown in Table~\ref{table:clusters}.
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.7\textwidth]{../output/standard/clusters_plots.png}
-    \caption{Clustering trials for standard tournaments. A number of 2
-    clusters has been chosen with a silhouette score of  0.66 against 0.511 and 0.50
-    respectively.}\label{fig:standard_clusters}
-\end{figure}
-
-\begin{table}[!htbp]
-    \centering
-    \resizebox{.25\textwidth}{!}{
-    \begin{tabular}{lcc}
-    \toprule
-    Cluster                &   $\bar{r}$ & median score \\
-    \midrule
-    1 & 0.769 & 2.065 \\
-    2 & 0.263 & 2.639\\
-    \bottomrule
-    \end{tabular}}
-    \caption{Median normalised rank and median score of each cluster in standard tournaments.}
-    \label{table:clusters}
-\end{table}
-
-Now that the performances have been clustered the aim is to evaluate which
-factors affect the performances being in each respective cluster. The factors
-evaluated in this work are given by Table~\ref{table:manual_measures}. Several
-of these factors include measures regarding the strategies and it's behaviour
-however others are fixed from the tournament or even the type of tournament. The
-measures from Table 1 are also included.
+Axelrod-Python makes use of classifiers to classify strategies according to
+various dimensions. The classifiers considered in this work are the stochastic
+classifier, the make use of game and length classifiers. These determine whether
+a strategy is stochastic or deterministic, whether it makes use of the number of
+turns or the game's payoffs. The SSE is a measure extortionate
+behaviour introduced in~\cite{Knight2019}. A value of 1 indicates no
+extortionate behaviour at all whereas a value of 0 indicates that a strategy is
+always trying to extortion the opponent. The rest of the factors considered
+are the $CC$ to $C$, $CD$ to $C$, $DC$ to $C$, and $DD$ to $C$ rates as well as
+cooperating ratio of a strategy. The minimum, maximum, medium and median
+cooperating ratios of each tournament are also included, and finally the number of
+turns, the size and the probabilities of noise or the game ending.
 
@@
 $C_r$ / $C_{\text{mean}}$ & A strategy's cooperating rate divided by the mean & manually & float & 0 & 1 \\
+$C_r$ & The cooperating ratio of a strategy & result summary & float & 0 & 1 \\
 $CC$ to $C$ rate & The probability a strategy will cooperate after a mutual cooperation & result summary & float & 0 & 1 \\
@@
 
-To evaluated how significant each factor contribution was a random forest is
-applied to the performances of standard tournaments where the target value
-is their corresponding cluster. Figure~\ref{fig:importance_standard} gives the
-importance of each factor.
-The four factors that have affect more the performances of strategies
-in standard tournaments are the cooperation ratio compared to the mean, the SSE,
-the cooperation ratio compared to the median and the cooperating ratio after
-being betrayed by the opponent.
+The effect of these factors on a strategy's success is evaluated based on the
+correlation coefficient between the factors, the normalised rank and the median
+score. The correlation coefficients are given by Table~\ref{table:correlations}.
+Note that the correlation for the classifiers is not included because they are
+binary variables and they will evaluated by a different method.
 
-\begin{figure}
-    \begin{minipage}{.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/standard_correlation_plot.pdf}
-    \end{minipage}
-    \begin{minipage}{.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/noise_correlation_plot.pdf}
-    \end{minipage}
-    \begin{minipage}{.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/probend_correlation_plot.pdf}
-    \end{minipage}
-    \begin{minipage}{.5\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/probend_noise_correlation_plot.pdf}
-    \end{minipage}
-\end{figure}
+% The
+% correlations of each factor against each factor, the normalised rank and the
+% median are also given in the Appendix.
 
-To delved deeper into the results of the random forest and how each feature
-has helped to be clustered where you were the tree interpreter method
-described in~\cite{} is used. The strongest contributors to predicting that
-a performance was clustered in the successful class were the DC to D ratio,
-the SSE error, the size followed by the cooperating ratio compared to the mean.
-In comparison the strongest impact on being in the non successful cluster
-have the Cd to C rate and the cooperating ration compare to the median.
+\newcolumntype{g}{>{\columncolor{Gray}}c}
+\begin{table}[!htbp]
+    \begin{center}
+    \resizebox{.8\textwidth}{!}{
+        \input{correlations_table.tex}
+    }
+\end{center}
+\caption{Correlations table.}\label{table:correlations}
+\end{table}
 
-\begin{figure}[!htbp]
-    \begin{minipage}{.6\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{../output/standard/_feature_importance_bar_plot.pdf}
-    \caption{Importance of features in standard tournaments.}
-    \label{fig:importance_standard}
-    \end{minipage}\hspace{.1cm}
-    \begin{minipage}{.35\textwidth}
-        \vspace{-1.5cm}
-        \centering
-        \resizebox{1.1\textwidth}{!}{
-        \input{tree_interpreter_std.tex}}
-        \caption{The average contribution of each factor in standard tournaments
-        based on the tree interpreter method.}
-    \end{minipage}
-\end{figure}
-
-The same approach is applied to the tournament types individually and in the
-merged performances fom the the tournament types. More specifically, in noisy
-tournament the normalised rank against the median score is given in
-Figure~\ref{fig:noise_clusters}, based on the silhouette coefficient the number
-of clusters is 3 in noisy tournaments. The performance of each cluster is
-a follows, being in cluster 1 corresponds to low performance, 2 in medium
-and 3 high, Table~\ref{table:clusters_noisy}.
+In standard tournaments the measures  $CC$ to $C$, $C_r$, $C_r / C_{\text{max}}$
+and the cooperating ratio compared to the median and the mean have a moderate
+negative effect on the normalised rank and a moderate positive on the median
+score. The SSE error and the $DD$ to $C$ have the opposite effects. Thus, in
+standard tournaments behaving cooperative corresponds to a more successful
+performance. However, even though being cooperative pays of that's not true
+against defective strategies. Cooperating after a mutual defection lowers a
+strategy's success. Figure\ref{fig:rates_of_winners_in_standard_tournaments}
+confirms these. The winner of standard tournaments almost always cooperated
+after a mutual cooperation but the 50\% only cooperated with a probability
+of 0.2 after a mutual defection.
 
@@
     \centering
-    \includegraphics[width=.7\textwidth]{../output/noise/clusters_plots.png}
-    \caption{Clustering trials for noisy tournaments. A number of 3
-    clusters has been chosen with a silhouette score of 0.49 against 2 clusters
-    with a coefficient of 0.47 and 4 with 0.45.
-    respectively.}\label{fig:noise_clusters}
+    \includegraphics[width=.7\textwidth]{../images/rates_of_winners_in_standard_tournaments.pdf}
+    \caption{Winners distributions
+    in standard tournaments for $CC$ to $C$ and $DD$ to $C$.}\label{fig:rates_of_winners_in_standard_tournaments}
+\end{figure}
+
+Compared to standard tournaments in both noisy and in probabilistic ending
+tournaments the higher the rates of cooperation the lower a strategy's success
+and median score. Moreover, a strategy would want to cooperate less than both
+the mean and median cooperator in such settings. In probabilistic ending
+tournaments the correlations coefficients have a larger values, indicating a
+stronger effect. Thus a strategy will be punished more by it's cooperative
+behaviour in such environments. The distributions of the $C_r$ of the winners in
+both tournaments is given by Figure~\ref{fig:c_r_distributions}. It confirms
+that the winners in these two settings were more defective strategies, mainly
+in probabilistic ending ones.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.7\textwidth]{../images/c_r_winners_tournaments.pdf}
+    \caption{$C_r$ distributions.}\label{fig:c_r_distributions}
+\end{figure}
+
+In noisy probabilistic ending tournaments and in the overall tournaments the
+only factors that had a moderate affect are $C_r/C_{\text{mean}},
+C_r/C_{\text{max}}$ and $C_r$. In such environments cooperative behaviour
+appears to be punished by not as much as in noisy and probabilistic ending
+tournaments.
+
+To further evaluate the effect of factors on performances a random forest
+classification~\cite{breiman2001} is applied. Initially, the performances are
+clustered based on their normalised rank and the median score by a \(k-\)means
+algorithm~\cite{Arthur2007}. The number of clusters are not deterministically
+chosen but are based on the silhouette coefficients~\cite{Rousseeuw1987}.
+Consider the case of standard tournaments, the chosen number of clusters is
+2 and Figure~\ref{fig:standard_clusters} illustrates the trials of clustering the
+performances in 2, 3 and 4 clusters respectively. The number of chosen clusters
+for each type and overall are given in Table~\ref{table:number_of_clusters}.
+
+\begin{figure}[!htbp]
+\centering
+\includegraphics[width=.7\textwidth]{../output/standard/clusters_plots.png}
+\caption{Clustering trials for standard tournaments. A number of 2 clusters has
+been chosen with a silhouette score of  0.66 against 0.511 and 0.50
+respectively.}\label{fig:standard_clusters}
 \end{figure}
@@
 \begin{table}[!htbp]
-    \centering
-    \resizebox{.25\textwidth}{!}{
-    \begin{tabular}{lcc}
+    \begin{center}
+        \resizebox{.5\textwidth}{!}{
+        \begin{tabular}{lcccc}
     \toprule
-    Cluster                &   $\bar{r}$ & median score \\
+    type & number of clusters &  silhouette coefficient\\
     \midrule
-    1 & 0.788 & 2.096 \\
-    2 & 0.316 & 2.290 \\
-    3 & 0.097 & 3.012 \\
+    standard                   & 2 & 0.648 \\
+    noisy                      & 3 & 0.493 \\
+    probabilistic ending       & 2 & 0.680 \\
+    noisy probabilistic ending & 4 & 0.415\\
+    overall                    & 3 & 0.443\\
     \bottomrule
         \end{tabular}}
-    \caption{Median normalised rank and median score of each cluster in noisy tournaments.}
-    \label{table:clusters_noisy}
+    \end{center}
+    \caption{Number of clusters for each type and overall and the respective silhouette coefficients.}
+    \label{table:number_of_clusters}
 \end{table}
 
-The two factor that appear to affect the performance in noisy tournaments, based on the
-average importance, are the cooperating ratio compared to the mean and the mean (Figure~\ref{fig:importance_noisy})
-with both having a strong effect to the contribution of being in the successful
-cluster Table~\ref{table:tree_interpreter_noise}.
+A random forest approach is applied to the data to predict the cluster to which
+a strategy's performance has been assigned to. The random forest method
+constructs many individual decision trees and the predictions from all trees are
+pooled to make the final prediction. The random forest models are trained on a
+training set of 70\% of the tournaments results. The accuracy of each model
+based on $R^2$ are given by Table~\ref{table:accuracy_random_forest}. The out of
+the bag error~\cite{hastie2005} has also been calculated. The models fit well and
+the values of the accuracy measures on the test data and the OOB error indicate that they are not
+over fitting.
+
+\begin{table}[!htbp]
+    \begin{center}
+        \resizebox{.5\textwidth}{!}{
+        \begin{tabular}{lcccc}
+    \toprule
+    type & $R^2$ training data &  $R^2$ test data  & $R^2$ OBB score\\
+    \midrule
+    standard                   & 0.998545  & 0.989890 & 0.982331\\
+    noisy                      & 0.996677  & 0.950572 & 0.935383\\
+    probabilistic ending       & 0.999592  & 0.995128 & 0.992819 \\
+    noisy probabilistic ending & 0.990490  & 0.813905 & 0.791418\\
+    overall                    & 0.993396 & 0.913409 & 0.898059 \\
+    \bottomrule
+        \end{tabular}}
+    \end{center}
+    \caption{Accuracy metrics for random forest models.}
+    \label{table:accuracy_random_forest}
+\end{table}
+
+The importance of the features on the classification task along with their inter
+trees variability are given by Figure~\ref{fig:importance}. The importance
+indicates that the two factors that affected performances the most were $C_r /
+C_{median}$ and $C_r / C_{mean}$. The classifiers which where not included in
+the previous analysis appear to have no effect, and several of the factors that
+are highted by the importance are inline with the correlation results.
 
 \begin{figure}[!htbp]
-    \begin{minipage}{.6\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{../output/noise/_feature_importance_bar_plot.pdf}
-    \caption{Importance of factors from Table 8 in noisy tournaments.}
-    \label{fig:importance_noisy}
-    \end{minipage}\hspace{.1cm}
-    \begin{minipage}{.35\textwidth}
-        \vspace{-1.5cm}
-        \centering
-        \resizebox{1.2\textwidth}{!}{
-        \input{tree_interpreter_noise.tex}}
-        \caption{The average contribution of each factor in standard tournaments
-        based on the tree interpreter method.}\label{table:tree_interpreter_noise}
+    \begin{minipage}{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../output/standard/_feature_importance_bar_plot.pdf}
+        \end{center}
+        \caption{Standard tournaments}
+    \end{minipage}\hspace{1cm}
+    \begin{minipage}{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../output/noise/_feature_importance_bar_plot.pdf}
+        \end{center}
+        \caption{Noisy tournaments}
+    \end{minipage}\hspace{1cm}
+    \begin{minipage}{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../output/probend/_feature_importance_bar_plot.pdf}
+        \end{center}
+        \caption{Probabilistic ending tournaments}
+    \end{minipage}\hspace{1cm}
+    \begin{minipage}{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../output/probend_noise/_feature_importance_bar_plot.pdf}
+        \end{center}
+        \caption{Noisy probabilistic ending tournaments}
     \end{minipage}
+    \begin{minipage}{0.5\textwidth}
+    \end{minipage}\hspace{4.5cm}
+    \begin{minipage}{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../output/merged/_feature_importance_bar_plot.pdf}
+        \end{center}
+        \caption{overall ending tournaments}
+    \end{minipage}
+    \caption{Importance of features in IPD tournaments.}\label{fig:importance}
 \end{figure}
 
-Similarly for probabilistic ending tournaments, the cluster are given by igure.. Winner is n = 2 with.
-'Clusters: n = 3': 0.51128060607311, 'Clusters: n = 2': 0.6705714418492148, 'Clusters: n = 4': 0.4980365221065629
+The behaviour a strategy adapts in comparison with the mean and median
+cooperator influence the success of a strategy. To gain a better understanding on
+the influence of these measures, in each tournament type the distributions of
+the winner's \(C_r / C_{\text{median}}\) and \(C_r / C_{\text{median}}\)
+are given by Figures~\ref{fig:mean_median_std},~\ref{fig:mean_median_noisy},
+\ref{fig:mean_median_probend}, \ref{fig:mean_median_probend_noisy} and
+\ref{fig:mean_median_overall}. In summary, in a noisy, noisy probabilistic 
+or if a strategy does not know the settings on the environment is about to compete,
+a strategy should cooperate 60\% of times the median/mean cooperator does. In
+standard tournaments a strategy would want to have the same cooperating ratio
+as the mean/median and finally in probabilistic ending tournaments a strategy
+wants to be defective.
 
-% \begin{table}[!htbp]
-%     \centering
-%     \resizebox{.25\textwidth}{!}{
-%     \begin{tabular}{lcc}
-%     \toprule
-%     Cluster                &   $\bar{r}$ & median score \\
-%     \midrule
-%     1 & 0.578 & 2.497 \\
-%     2 & 0.090 & 3.611 \\
-%     \bottomrule
-%     \end{tabular}}
-%     \caption{Median normalised rank and median score of each cluster}
-%     \label{table:clusters}
-% \end{table}
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.7\textwidth]{../images/compared_to_mean_median_standard.pdf}
+    \caption{Distributions of \(C_r / C_{\text{median}}\)
+    and \(C_r / C_{\text{median}}\) for standard tournaments.}\label{fig:mean_median_std}
+\end{figure}
 
-% Mean and median as well as max.
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.7\textwidth]{../images/compared_to_mean_median_noisy.pdf}
+    \caption{Distributions of \(C_r / C_{\text{median}}\)
+    and \(C_r / C_{\text{median}}\) for noisy tournaments.}\label{fig:mean_median_noisy}
+\end{figure}
 
-% \begin{figure}
-%     \begin{minipage}{.6\textwidth}
-%     \centering
-%     \includegraphics[width=\textwidth]{../output/probend/_feature_importance_bar_plot.pdf}
-%     \caption{Importance of factors from Table 8 in noise tournaments.}
-%     \label{fig:importance_standard}
-%     \end{minipage}\hspace{.1cm}
-%     \begin{minipage}{.35\textwidth}
-%         \vspace{-2cm}
-%         \centering
-%         \resizebox{1.2\textwidth}{!}{
-%         \input{tree_interpreter_probend.tex}}
-%         \caption{trying the caption}
-%     \end{minipage}
-% \end{figure}
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.7\textwidth]{../images/compared_to_mean_median_probend.pdf}
+    \caption{Distributions of \(C_r / C_{\text{median}}\)
+    and \(C_r / C_{\text{median}}\) for probabilistic ending tournaments.}\label{fig:mean_median_probend}
+\end{figure}
 
-% \begin{figure}
-%     \begin{minipage}{.6\textwidth}
-%     \centering
-%     \includegraphics[width=\textwidth]{../output/probend_noise/_feature_importance_bar_plot.pdf}
-%     \caption{Importance of factors from Table 8 in noise tournaments.}
-%     \label{fig:importance_standard}
-%     \end{minipage}\hspace{.1cm}
-%     \begin{minipage}{.35\textwidth}
-%         \vspace{-2cm}
-%         \centering
-%         \resizebox{1.2\textwidth}{!}{
-%         \input{tree_interpreter_probend_noise.tex}}
-%         \caption{trying the caption}
-%     \end{minipage}
-% \end{figure}
-\section{Conclusion and Discussion}\label{section:conclusion}
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.7\textwidth]{../images/compared_to_mean_median_probend_noisy.pdf}
+    \caption{Distributions of \(C_r / C_{\text{median}}\)
+    and \(C_r / C_{\text{median}}\) for noisy probabilistic ending tournaments.}\label{fig:mean_median_probend_noisy}
+\end{figure}
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.7\textwidth]{../images/compared_to_mean_median_overall.pdf}
+    \caption{Distributions of \(C_r / C_{\text{median}}\)
+    and \(C_r / C_{\text{median}}\) for over all the tournaments.}\label{fig:mean_median_overall}
+\end{figure}
+
+The factors which have an effect on the performances were presented here by two
+approaches which included the correlation coefficients and a random forest
+analysis. The results of these are discussed in the following section.
+
+\section{Conclusion}\label{section:conclusion}
+
+This manuscript explored a variety of strategic behaviours in the game of the
+Iterated Prisoner's Dilemma and presented an evaluation of performance in the
+game. A large number of computer tournaments have been analysis and demonstrated
+that a single dominant strategy does not exist in the game. Moreover, it
+was shown that from a series of factors that a strategy has control over the
+tge factors that can influence it's performance is the cooperating ratio compared
+to that of it's environment.
+
+A total of 186 strategies were used in this manuscript, which are available via
+an open source software, the Axelrod-Python. By making use of the software a
+total of 49,140 computer tournaments results were gathered. In
+Section~\ref{section:top_performances}, the result summaries were used to
+present the top performances. This was not done over the entire data set. The
+data set contains results from four different settings, and these were also
+studied individually. The top performances were presented for all the different
+combinations of the results summary. Though Retaliate set of families,
+strategies introduced in~\cite{axelrodproject}, did perform well in noisy
+environments and this feature allowed the strategies to rank well in more than
+one tournament type, the analysis concluded that there is not a single dominant
+strategy in the Iterated Prisoner's Dilemma. THough a dominant perform
+was not highlighted by the analysis of this manuscript the factors that made
+performances successful were further explored.
+
+In Section~\ref{section:evaluation_of_performance} an analysis of strategies
+features was covered. The results of this analysis showed that a strategy's
+characteristics such as it's stochasticity and the information it used regarding
+the game had no effect on the strategy's success. The most important
+factors have been those that compared the strategy's behaviour to it's environment.
+The cooperating ratio of the strategy compared to the mean and median cooperator
+was highlighted as the most important feature in the analysis. More specifically,
+if a strategy were to enter a tournament with a theory of mind of it's environment
+it would choose to be the median cooperator in standard tournaments, the
+defector in probabilistic ending tournaments and to cooperate 60\% of the median
+in noisy and noisy probabilistic tournaments. Lastly, if a strategy was
+aware of the opponents but not of the setting on the tournament, a strategy
+would be more likely to be successful if it were to identify the median
+cooperator and cooperated 60\% of the times that they did.
 
@@
 \bibliography{bibliography}
+
+\appendix
+
+\section{List of strategies}\label{app:list_of_players}
+
+The strategies used in this study which are from Axelrod version 3.0.0
+\cite{axelrodproject}.
+
+\begin{multicols}{3}
+	\begin{enumerate}
+		\input{list_of_strategies.tex}
+	\end{enumerate}
+\end{multicols}
+
+\section{Acknowledgements}
+
+A variety of software have been used in this work:
+
+\begin{itemize}
+    \item The Axelrod library for IPD simulations~\cite{axelrodproject}.
+    \item The Matplotlib library for visualisation~\cite{hunter2007matplotlib}.
+    \item The Numpy library for data manipulation~\cite{walt2011numpy}.
+    \item The scikit-learn library for data analysis~\cite{scikit-learn}.
+\end{itemize}
+
 \end{document}

### 2019-09-22 paper/top_perfomances.tex
paper draft

\begin{tabular}{ggllggllr}
\toprule
\multicolumn{2}{g}{Standard} & \multicolumn{2}{c}{Noisy} & \multicolumn{2}{g}{Probabilistic ending} &  \multicolumn{2}{c}{Noisy probabilistic ending} \\
\midrule
    Name &  $\bar{r}$ & Name &  $\bar{r}$ & Name &  $\bar{r}$ & Name &  $\bar{r}$\\
    \midrule
Evolved HMM 5           & 0.00658 & Grumpy              & 0.13953 & Fortress4         &  0.01266 & Alternator          & 0.30390\\
Evolved FSM 16          & 0.00990 & $e$                 & 0.19048 & Defector          &  0.01444 & $\phi$              & 0.31025\\
EvolvedLookerUp2 2 2    & 0.01064 & Cooperator          & 0.19565 & Better and Better &  0.01587 & $e$                 & 0.31293\\
Evolved FSM 16 Noise 05 & 0.01639 & Tit For 2 Tats      & 0.20520 & Tricky Defector   &  0.01869 & $\pi$               & 0.31818\\
PSO Gambler 2 2 2       & 0.02139 & Cycle Hunter        & 0.22222 & Fortress3         &  0.02198 & Limited Retaliate   & 0.35294\\
Evolved ANN             & 0.02874 & Risky QLearner      & 0.22424 & Gradual Killer    &  0.02521 & Anti Tit For Tat    & 0.35429\\
Evolved ANN 5           & 0.03390 & Retaliate 3         & 0.23077 & Aggravater        &  0.02797 & Retaliate 3         & 0.35484\\
PSO Gambler 1 1 1       & 0.03723 & Retaliate 2         & 0.23762 & Raider            &  0.03077 & Limited Retaliate 3 & 0.35563\\
Evolved FSM 4           & 0.04839 & Retaliate           & 0.24309 & Cycler DDC        &  0.04545 & Retaliate           & 0.35588\\
PSO Gambler Mem1        & 0.05000 & Hard Tit For 2 Tats & 0.24658 & Hard Prober       &  0.05085 & Retaliate 2         & 0.35714\\
Winner12                & 0.05946 & Limited Retaliate 3 & 0.25000 & SolutionB1        &  0.06040 & Limited Retaliate 2 & 0.36066\\
Fool Me Once            & 0.06122 & ShortMem            & 0.25272 & Meta Minority     &  0.06040 & Hopeless            & 0.36913\\
DBS                     & 0.07087 & Limited Retaliate   & 0.25698 & Bully             &  0.06061 & Arrogant QLearner   & 0.40526\\
DoubleCrosser           & 0.07190 & Limited Retaliate 2 & 0.26027 & Fool Me Forever   &  0.07018 & Cautious QLearner   & 0.40711\\
BackStabber             & 0.07500 & $\phi$              & 0.26201 & EasyGo            &  0.07065 & Risky QLearner      & 0.41989\\
    \bottomrule
    \end{tabular}

### 2019-10-24 paper/main.tex
draft people hanging it to Vince

@@
 \usepackage{wrapfig, blindtext}
+\usepackage[table]{xcolor}
 %%%%%%%%%%%%%%%%%
@@
 
+\newcommand{\uniquenumberofseeds}{\input{unique_number_of_seeds.tex}}
+\newcommand{\numberofalltournaments}{\input{number_of_all_tournaments.tex}}
+
 \setlength{\tabcolsep}{3pt}
@@
 Iterated Prisoner's Dilemma.}
-\author{Nikoleta E. Glynatsi, Dr Vincent A. Knight}
+\author{Nikoleta E. Glynatsi, Vincent A. Knight}
 \date{}
@@
 
-The Iterated Prisoner's Dilemma has been used for decades as a powerful model of
+The Iterated Prisoner's Dilemma has been used for decades as a model of
 behavioural interactions. From the celebrated performance of Tit for Tat, to the
@@
 now accessible due to an open source package; Axelrod-Python. This manuscript
-make use of Axelrod-Python to conduct a meta analysis of 40000 Iterated
-Prisoner's Dilemma tournaments. The aim is to evaluate the performance of
-numerous strategies and finally answer the explore the factors of success in the
-game.
+make use of Axelrod-Python to conduct a meta analysis of Iterated Prisoner's
+Dilemma tournaments. The aim is to evaluate the performance of 194 strategies
+over \numberofalltournaments Iterated Prisoner's Dilemma tournaments and to
+explore the factors of their success.
 \end{abstract}
@@
 The Iterated Prisoner's Dilemma (IPD) is a repeated two player game that models
-situations in which self-interest clashes with collective interest. At each turn,
-the players simultaneously and independently make a choice between cooperation (C) and
-defection (D) whilst having memory of the prior interactions.
-The payoffs at each given turn are defined by the matrix,
+behavioural interactions, and more specifically, interactions where
+self-interest clashes with collective interest. At each turn of the game both
+players, simultaneously and independently, decide between cooperation (C) and
+defection (D) whilst having memory of their prior interactions. The payoffs for each
+player, at each turn, is influenced by their own choice and the choice of the
+other player. The payoffs of the game are generally defined by:
 
@@
 where \(T > R > P > S\) and \(2R > T + S\). The most common values used in
-the literature~\cite{Axelrod1981}, and in this paper, are $R=3, P=1, T=5, S=0$.
+the literature~\cite{Axelrod1981} are $R=3, P=1, T=5, S=0$. These values are also
+used in this work.
 
-Since the computer tournaments of R. Axelrod in 1980s several academic papers
-are published in the field regarding the performance of strategies in the IPD.
-In the 80's following the strong performance of Tit For Tat in both Axelrod's
-computer tournaments~\cite{Axelrod1980a, Axelrod1980b}, and moreover in a series
-of evolutionary experiments~\cite{Axelrod1981}, the strategy was thought as the
-most robust basic strategy in the IPD. However, the strategy was shown to
-perform poorly in environments with noise~\cite{Bendor1991, Donninger1986,
-Molander1985, Hammerstein1984}. More robust strategy in such setting were
-introduced and were the new protagonists, such as, Nice and
-Forgiving~\cite{Bendor1991}, Pavlov~\cite{Nowak1993} and Generous Tit For
-Tat~\cite{Nowak1992}.
+Conceptualising strategies and understanding the best way of playing the game
+has been of interest to the scientific community since the formulation of the
+game in 1950~\cite{Flood1958}. Following the computer tournaments of Axelrod in
+1980's~\cite{Axelrod1980a, Axelrod1980b}, a strategy's performance in a round
+robin computer tournament became a common evaluation technique for newly designed
+strategies. Today more than 200 strategies exist in the literature and several
+tournaments, excluding Axelrod's, have been undertaken~\cite{Bendor1991,
+Harper2017, Kendall2007, Stephens2002, Stewart2012}.
 
-The $20^{\text{th}}$ Anniversary Iterated Prisoner Dilemma Tournament took place
-in 2004 with 233 entries. The winning strategies were based on a mechanism of
-teams. A team from Southampton University took advantage of the fact that a
-participant was allowed to submit multiple strategies. They submitted a total of
-60 of strategies that could recognised each other and colluded to increase one
-members score~\cite{J.P.Delahaye1993Lp, J.P.Delahaye1995LIeP, A.Rogers2007Ctpw}.
-Yet again, in 2012 another set of strategies was introduced as the dominant set
-of strategies~\cite{Press2012}. These were called zero-determinant strategies,
-and by forcing a linear relationship between the payoffs they can ensure that
-they will never receive less than their opponents. However, in~\cite{Harper2017}
-a tournament containing over 200 strategies, zero-determinant, was performed and
-none of the zero-determinant strategies ranked in top spots. Instead, the top
-ranked strategies were a set of evolved strategies based lookup
-tables~\cite{Axelrod1987}, hidden markov models~\cite{Harper2017} and finite
-state automata~\cite{Miller1996}.
-%TODO reference the archetypes of the archetypes used the IPD? Did IPD for now.
+In the 80's, Axelrod performed two computer tournaments~\cite{Axelrod1980a,
+Axelrod1980b}. The contestants were strategies submitted in the form of computer
+code. They competed against all other entries, a copy of themselves and a random
+strategy. The winner was decided on the average score a strategy achieved. The
+winner of both tournaments was the simple strategy Tit For Tat which cooperated
+on the first turn and then simply copied the previous action of it's opponent.
+Due to the strategy's strong performance in both tournaments, and moreover in a
+series of evolutionary experiments~\cite{Axelrod1981}, Tit For Tat was thought
+to be the most robust basic strategy in the IPD.
 
-Thus, the following question is raised here: which are the true dominant
-strategies in the iterated prisoner's dilemma?
-This manuscript uses the open source package
+However, further research proved that the strategy had weakness, and more
+specifically, it was shown that the strategy suffered in environments with
+noise~\cite{Bendor1991, Donninger1986, Molander1985, Hammerstein1984}. This was
+mainly due to the strategy's lack of generosity and contrition. The strategy was
+quick to punish a defection, and in a noisy environment it could lead to a
+repeated cycle of defections and cooperations. Some new strategies, more
+robust in tournaments with noise, were soon introduced and became the new
+protagonists of the game. These include Nice and Forgiving~\cite{Bendor1991},
+Pavlov~\cite{Nowak1993} and Generous Tit For Tat~\cite{Nowak1992}.
+
+In 2004, a $20^{\text{th}}$ Anniversary Iterated Prisoner Dilemma Tournament
+took place with 233 entries. This time the winning strategy was not designed on
+a reciprocity based approach but on a mechanism of
+teams~\cite{J.P.Delahaye1993Lp, J.P.Delahaye1995LIeP, A.Rogers2007Ctpw}. A team
+from Southampton University took advantage of the fact that a participant was
+allowed to submit multiple strategies. They submitted a total of 60 strategies
+that could recognised each other and colluded to increase one members score.
+This resulted with three of the strategies to be ranked in the top spots. The
+performance of the Southampton University team received mixed attention, though
+they had won the tournament as stated in~\cite{us_blog} "technically this
+strategy violates the spirit of the Prisoner's Dilemma, which assumes that the
+two prisoners cannot communicate with one another".
+
+Another set of IPD strategies that have received a lot of attention, the
+American Mathematical Society's news section stated that ``the world of game
+theory is currently on fire'', are the zero-determinants~\cite{Press2012}. By
+forcing a linear relationship between the payoffs the zero-determinant
+strategies can ensure that they will never receive less than their opponents.
+Zero-determinant strategies are indeed a set of mathematically unique strategies
+and robust in pairwise interactions, however, their simplicity and extortionate
+behaviour have been tested. In~\cite{Harper2017} a tournament containing over
+200 strategies, including zero-determinants, was ran. None of the zero-determinant
+strategies ranked in top spots. Instead, the top ranked strategies were a set of
+trained strategies based lookup tables~\cite{Axelrod1987}, hidden markov
+models~\cite{Harper2017} and finite state automata~\cite{Miller1996}.
+
+Though only a few selected pieces of work have been discussed, the IPD is
+rich, and new strategies and competitions are being published every year.
+The question, however, still remains the same: what is the best way to play the
+game?
+
+This manuscript uses an open source package called
 Axelrod-Python~\cite{axelrodproject} to simulate a large number of computer
-tournaments using as many strategies as possible from the literature. The aim is
-to evaluate the performance of these strategies in a tournament and futhermore,
-explore the factors of their success. This is done not for standard round robin
-tournaments, but also for noisy, probabilistic ending and noisy probabilistic
-ending tournaments.
+tournaments, using as many strategies as possible from the literature. The aim
+is to evaluate the performance of 194 strategies in IPD tournaments, and
+futhermore, explore the factors of their success. This is done not only for
+standard round robin tournaments, but also for tournaments with noisy and
+tournaments with a probabilistic ending. The different tournament types as well
+as the data collection are covered in Section~\ref{section:data_collection}.
+Section~\ref{section:top_performances}, focuses on the best performed strategies
+for each type of tournament and overall.
+Section~\ref{section:evaluation_of_performance}, explores the traits which
+contribute to good performance, and finally the results are summarised in
+Section~\ref{section:conclusion}.
 
-The different tournaments and the data generating process are covered in
-Section~\ref{section:data_collection}. Section~\ref{section:top_performances},
-covers the best performed strategies for each type of tournament and overall.
-Section~\ref{section:evaluation_of_performance}, explores the traits which
-contribute to good performance and finally in Section~\ref{section:discussion}
-the results are discussed and concluded in Section~\ref{section:conclusion}.
+This manuscripts uses several parameters. These are introduced in the following
+sections, however, the full set of parameters and their definitions are given in
+Appendix~\ref{app:parameters}. %TODO: fix table
 
-\section{Data generating process}\label{section:data_collection}
+\section{Data collection}\label{section:data_collection}
 
-For the purposes of this manuscript a data set containing results on IPD tournaments
-has been generated and is available at. This
-was done using the open source package Axelrod-Python~\cite{axelrodproject},
+For the purposes of this manuscript a data set containing results of IPD tournaments
+has been generated and is available at~\cite{data}. This
+was done using the open source package Axelrod-Python~\cite{axelrodproject}, and
 more specifically, version 3.0.0. Axelrod-Python allows for different types of
@@
 in the literature with a few exceptions being strategies that have been
-contributed specifically to the package. Though Axelrod-Python features several
+contributed specifically to the package. This paper make use of 194 strategies
+implemented in version 3.0.0. A list of the strategies is given in the
+Appendix~\ref{app:list_of_players}. Though Axelrod-Python features several
 tournament types, this work considers only standard, noisy, probabilistic ending
@@
 and a match against a random strategy are not included. Similarly, \textbf{noisy
-tournaments} have \(N\) strategies and \(n\) number of turns but at each turn
+tournaments} have \(N\) strategies and \(n\) number of turns, but at each turn
 there is a probability \(p\) that a player's action will be flipped.
@@
 \(p\) and an ending probability \(e\). For smoothing the simulated results a
-tournament is repeated for \(k\) number of times. The winner of each tournament
+tournament is repeated for \(k\) number of times and the winner of each tournament
 is based on the average score a strategy achieved and not by number of wins.
 
-%  A summary of
-% each tournaments' parameters is given in Table~\ref{table:tournaments_parameters}.
+% A summary of each tournaments' parameters is given in
+% Table~\ref{table:tournaments_parameters}.
 
@@
 
-The process of generating data implemented in this manuscript is given by
-Algorithm~\ref{algorithm:data_generation}. For each trial a random
-size \(N\) is selected, and from the list of 186 strategies
-in~\cite{axelrodproject}, a random list of \(N\) strategies is chosen. The 186
-strategies used here are given in the Appendix~\ref{app:list_of_players}. For the
-given list of strategies a standard, a noisy, a probabilistic ending and a noisy
-probabilistic ending tournament are performed and repeated \(k\) times.
-The parameters for the tournaments as well as the number of repetitions are
-selected once for each trial. The parameters and their respective minimum and
-maximum values are given by Table~\ref{table:parameters_values}.
+The process of collecting tournament results implemented in this manuscript is described by
+Algorithm~\ref{algorithm:data_generation}. For each trial a random size \(N\) is
+selected, and from the 194 strategies a random list of \(N\) strategies is
+chosen. For the given list of strategies a standard, a noisy, a probabilistic
+ending and a noisy probabilistic ending tournament are performed and repeated
+\(k\) times. The parameters for the tournaments as well as the number of
+repetitions are selected once for each trial. The parameters and their
+respective minimum and maximum values are given by
+Table~\ref{table:parameters_values}.
 
@@
     \end{center}
-    \caption{Data generation parameters' values}
+    \caption{Data collection; parameters' values}
     \label{table:parameters_values}
@@
 
-The source code for the data generating process as well as the source code for
-the analysis which will be discussed in the following sections have been written
+The source code for the data collection as well as the source code for
+the analysis, which will be discussed in the following sections, have been written
 following best practices~\cite{Aberdour2007, Benureau2018}. It has been packaged
-and is available here.
+and is available here. %TODO archive code
 
@@
     \setstretch{1.35}
-    \ForEach{\text{seed} $\in [0, 12285]$}{
+    \ForEach{\text{seed} $\in [0, 11420]$}{
         $N \gets \text{randomly select integer}\in [N_{min}, N_{max}]$\;
@@
     result noisy probabilistic ending}\;
-    \caption{Data generating Algorithm}
+    \caption{Data collection Algorithm}
     \label{algorithm:data_generation}
@@
 
-A total of 12,285 trials of Algorithm~\ref{algorithm:data_generation} have been
-performed. For each trial the results for 4 different tournaments were collected,
-thus a total of 49,140 $(12,285 \times 4)$ tournament results have been
+A total of \uniquenumberofseeds trials of Algorithm~\ref{algorithm:data_generation} have been
+run. For each trial the results for 4 different tournaments were collected,
+thus a total of \numberofalltournaments $(\uniquenumberofseeds \times 4)$ tournament results have been
 retrieved. Each tournament outputs a result summary in the form of
@@
 
-The result summary has a length \(N\) because each row contains information for
-each strategy that participated in the tournament. The information include the
-strategy's rank, median score, the rate with which the strategy cooperated
-$(C_r)$, it's wins and the probability that the strategy cooperated in the
-opening move. Moreover, the rates of a strategy being in any of the four states
-($CC, CD, DC, DD$), and the rate of which the strategy cooperated after each
-state.
+The result summary, Table~\ref{table:output_result}, has \(N\) number of rows
+because each row contains information for each strategy that participated in the
+tournament. The information include the strategy's rank, median score, the rate
+with which the strategy cooperated $(C_r)$, it's wins and the probability that
+the strategy cooperated in the opening move. Moreover, the rates of a strategy
+being in any of the four states ($CC, CD, DC, DD$), and the rate of which the
+strategy cooperated after each state.
 
 \newcolumntype{g}{>{\columncolor{Gray}}c}
-\begin{table}[!htbp]
+\begin{table}[h!]
     \begin{center}
@@
 \end{center}
-\caption{Output result.}\label{table:output_result}
+\caption{Output result of a signle tournament.}\label{table:output_result}
 \end{table}
 
-The \textbf{normalised rank} is a measure which was manually included. The normalised
-rank, denoted as $r$, is calculated as a strategy's rank divided by the
-tournament's size ($N$). The normalised rank will be used in the next section to
-evaluate the performance of strategies.
+A measure that has been manually included
+is the \textbf{normalised rank}. The normalised rank, denoted as $r$, is
+calculated as a strategy's rank divided by the tournament's size ($N$). The
+normalised rank will be used in the next section to evaluate the performance of
+strategies.
 
@@
 
-This section evaluates the performance of 186 strategies. The performance of
-each strategy will be evaluated for each type of tournament independently,
-followed by an evaluation of their performance over all the simulated
-tournaments of this work. Each strategy could have participated in multiple
-tournaments of the same type (on average each participated in 5690 different
-tournaments). For example Tit For Tat has participated in a total of 5569
+This section evaluates the performance of 194 IPD strategies. The performance of
+each strategy is evaluated in four tournament types, which were presented in Section
+\ref{section:data_collection}, followed by an evaluation of their performance
+over all the \numberofalltournaments simulated tournaments of this work.
+
+Each strategy participated in multiple tournaments of the same type (on average 5180).
+For example Tit For Tat has participated in a total of 5114
 tournaments of each type. The strategy's normalised rank distribution in these
-is given in Figure~\ref{fig:tit_for_tat_r_distribution}. As a result, of the
-multiple entries of strategies their performance is evaluated based on the
+is given in Figure~\ref{fig:tit_for_tat_r_distribution}. Because of the strategies'
+multiple entries their performance is evaluated based on the
 \textbf{median normalised rank} denoted as \(\bar{r}\). A value of \(\bar{r} =
@@
     \centering
-    \includegraphics[width=.8\textwidth]{../images/tit_for_tat_r_distributions.pdf}
+    \includegraphics[width=.45\textwidth]{../images/tit_for_tat_r_distributions.pdf}
     \caption{Tit For Tat's $r$ distribution in tournaments. The best performance
-    of the strategy has been in standard tournaments where it achieved a normalised
-    rank of 0.339.}
+    of the strategy has been in standard tournaments where it achieved a $\bar{r}$
+    of 0.339.}
     \label{fig:tit_for_tat_r_distribution}
@@
 
-The result of each tournament type are based on $12,285$ trials. The strategies
-are ranked based on the median normalised rank they achieved and the top 15
-strategies of each tournament are given in Table~\ref{table:top_performances}.
+The top 15 strategies for each tournament type based on \(\bar{r}\) are given in
+Table~\ref{table:top_performances}.
 
@@
 
-In standard tournaments 10 of the 15 top strategies are strategies introduced
-in~\cite{Harper2017}. These have been trained using reinforcement learning
-algorithms and are based on finite state automata (FSM), hidden markov models
-(HMM), artificial neural networks (ANN), lookup tables (LookerUp) and stochastic
-lookup tables (Gambler). Specifically, the have been trained against the
-strategy list of~\cite{axelrodproject} in standard tournaments. Thus their
-performance is to be expected. DoubleCrosser, and Fool Me Once, are not from the
-literature but from~\cite{axelrodproject}. DoubleCrosser is a strategy that
-makes use of the length of the match because is set to defect on the last two
-rounds. The strategy is expected to not perform as well in probabilistic ending
-tournaments. Finally, Winner 12~\cite{mathieu2017} and DBS are both from the the
-literature. DBS~\cite{Au2006} is strategy specifically designed for noisy
-environments, however, it ranks highly only in standard ones.
+In standard tournaments 10 out of the 15 top strategies are introduced
+in~\cite{Harper2017}. These are strategies based on finite state automata (FSM),
+hidden markov models (HMM), artificial neural networks (ANN), lookup tables
+(LookerUp) and stochastic lookup tables (Gambler) that have been trained using
+reinforcement learning algorithms (evolutionary and particle swarm algorithms).
+They have been trained to perform well against the strategies
+in~\cite{axelrodproject} in a standard setting, thus their performance in the
+specific setting was anticipated. DoubleCrosser, and Fool Me Once, are
+strategies not from the literature but from~\cite{axelrodproject}. DoubleCrosser
+is a strategy that makes use of the number of turns because is set to defect on
+the last two rounds. The strategy was expected to not perform as well in
+tournaments where the number of turns is not specified, but the strategy did not
+perform well in tournaments with noise either. Finally, Winner
+12~\cite{mathieu2017} and DBS~\cite{Au2006} are both from the the literature.
+DBS is strategy specifically designed for noisy environments, however, it ranks
+highly only in standard ones.
 
-Figure~\ref{fig:std_results} gives the distributions of $\bar{r}$ for the top
+Figure~\ref{fig:std_results} gives the distributions of $r$ for the top
 ranked strategies. The distributions are skewed towards zero and the highest
-median is at 0.075. This indicates that the top ranked strategies are dominating
-strategies in standard tournaments. They are very likely to perform well in
-standard tournament despite the number of opponents, the opponents, the turns
-etc. This does not hold for all the tournament types as it will be discussed
-in the later parts.
+median is at 0.075. This indicates that the top ranked strategies are very
+likely to perform well in a standard tournament despite the tournament size,
+the opponents, the turns etc.
 
@@
     \centering
-    \includegraphics[width=.7\textwidth]{../images/performance_standard.pdf}
-    \caption{$\bar{r}$ distributions of top 15 strategies in standard tournaments.}\label{fig:std_results}
+    \includegraphics[width=.55\textwidth]{../images/performance_standard.pdf}
+    \caption{$r$ distributions of top 15 strategies in standard tournaments.}\label{fig:std_results}
 \end{figure}
 
-The top strategies in noisy tournaments include the two strategies, Tit For 2
-Tats~\cite{Axelrod1980b} and Hard Tit For 2 Tats~\cite{Stewart2012}, which are
-strategies that will defect only after the have received two defections from the
-opponent. The Retaliate strategies are set of strategies
-from~\cite{axelrodproject} that start by cooperating but will retaliate once the
-opponent's wins and defections surpass a curtain threshold.
-ShortMem~\cite{Carvalho2013}, Grumpy, $e$ and $\phi$ are strategies that make
-decisions based on the cooperations to defections ratio. In $5^{\text{th}}$ and
-$6^{\text{th}}$ place are the strategies Cycler Hunter and  Risky QLearn. Cycler
-Hunter tries to extort strategies that play cyclically and Risky QLearn uses a Q
-learning algorithm. Notably, a deterministic and one of the most simple
-strategies in game is ranked $3^{\text{rd}}$. That is Cooperator, a strategy
-that just cooperates.
+The top strategies in noisy tournaments include deterministic strategies, such
+as Tit For 2 Tats~\cite{Axelrod1980b}, Hard Tit For 2 Tats~\cite{Stewart2012}
+and Cycler CCCCCD, and strategies which decide their actions based on the
+cooperations to defections ratio, such as ShortMem~\cite{Carvalho2013}, Grumpy,
+$e$, $\pi$ and $\phi$ (all from~\cite{axelrodproject}). The Retaliate and
+Limited Retaliate strategies are implemented in~\cite{axelrodproject} by the
+same contributor. The strategies are designed to defect if the opponent has
+tricked the strategy more often than \(x\%\) of the times that the strategy has
+done the same. Finally, in $4^{\text{th}}$ and $9^{\text{th}}$ are Hunter
+strategies which trying to extort, equivalently, strategies that play cyclically
+and defectors.
 
-From Figure~\ref{fig:std_results} it is evident that the normalised rank distributions
-in noisy environments are more variant and have higher median values compared
-to standard tournaments. The distributions are skewed both towards
-0 and 1 which indicates that though the top ranked strategies mainly
-performed well (medians $< 0.3$) there are several tournaments that they performed
-worse than the 60\% of the participants.
+From Figure~\ref{fig:noisy_results}, it is evident that the normalised rank
+distributions in noisy environments are more variant with higher medians
+compared to standard tournaments. The distributions are skewed both towards 0
+and 1. This indicates that although the top ranked strategies mainly performed
+well, there are several tournaments that they ranked in the bottom half.
 
@@
     \centering
-    \includegraphics[width=.7\textwidth]{../images/performance_noise.pdf}
-    \caption{\(\bar{r}\) distributions for best performed strategies in noisy tournaments.}
+    \includegraphics[width=.55\textwidth]{../images/performance_noise.pdf}
+    \caption{\(r\) distributions for best performed strategies in noisy tournaments.}
     \label{fig:noisy_results}
@@
 Fortress 3, Fortress 4 (both introduced in~\cite{Ashlock2006}),
-Raider~\cite{Ashlock2014} and Solution B1~\cite{Ashlock2014} which are strategies
-based on finite state automata introduced by Daniel and Wendy Ashlock. These
-strategies have been evolved using reinformed learning, however, there were
-trained to maximise their payoffs in tournaments with fixed turns (150
-specifically) and not in probabilistic ending ones.
-In probabilistic ending tournaments it appears that the top ranks are mostly
-occupied by defecting strategies which include Better and Better, Gradual
-Killer, Hard Prober (all from ~\cite{prison}), Bully (Reverse Tit For
-Tat)~\cite{Nachbar1992} and Defector. Thus, it's surprisingly that EasyGo and
-Fool Me Forever are ranked $14^{\text{th}}$ and $15^{\text{th}}$. These
-strategies are actually the same; they will defect until their opponent defect,
-then they will cooperate until the end. Both strategies have repeatedly ranked highly
-as shown in Figure~\ref{fig:probend_results} and there are cases for which they
-were the winners of the tournament.
-
-The distributions of the normalised rank in probabilistic ending tournaments are
-less variant than those of noisy tournaments. The medians are lower than 0.1 and the
-distributions are skewed towards 0. Though the large difference between the means
-and the medians indicates some outliers, the strategies have overall performed
-well in the tournaments that they participated.
+Raider~\cite{Ashlock2014} and Solution B1~\cite{Ashlock2014}, which are
+strategies based on finite state automata introduced by Daniel and Wendy
+Ashlock. These strategies have been evolved using reinformed learning, however,
+there were trained to maximise their payoffs in tournaments with fixed turns
+(150 specifically) and not in probabilistic ending ones. In probabilistic ending
+tournaments it appears that the top ranks are mostly occupied by defecting
+strategies. These include Better and Better, Gradual Killer, Hard Prober (all
+from ~\cite{prison}), Bully (Reverse Tit For Tat)~\cite{Nachbar1992} and
+Defector. Thus, it's surprisingly that EasyGo and Fool Me Forever are ranked
+$14^{\text{th}}$ and $15^{\text{th}}$. These strategies are actually the same;
+they will defect until their opponent defect, then they will cooperate until the
+end. Both strategies have repeatedly ranked highly as shown in
+Figure~\ref{fig:probend_results}, and there are cases for which they were the
+winners of the tournament.
 
@@
     \centering
-    \includegraphics[width=.7\textwidth]{../images/performance_probend.pdf}
-    \caption{\(\bar{r}\) distributions for best performed strategies in probabilistic ending tournaments.}
+    \includegraphics[width=.55\textwidth]{../images/performance_probend.pdf}
+    \caption{\(r\) distributions for best performed strategies in probabilistic ending tournaments.}
     \label{fig:probend_results}
@@
 
-In tournaments that have both noise and an unspecified number of turns several
-of the top ranked strategies are strategies that were highly ranked in
-noisy tournaments as well. However, strategies from the top ranks of
-probabilistic ending tournaments did not rank highly here. The Retaliate set,
-$\phi, e$ and Anti Tit For Tat behaviour strategies appear to perform well in
-noisy environments. So these strategies performed well in this setting as well
-even though now the turns are not specified.
-The top ranked strategy is Alternator a strategy that alternate between
-cooperation and defection. Hopeless~\cite{Van2015} is a strategy that will only
-defect if and only if a mutual cooperation and the last three places are
-occupied by strategies based on a Q learning algorithm. The three Q learning
-strategies are the only ones that have bimodal distributions of normalised
-ranks. In comparison, the rest of the distributions are skewed towards
-0.4, Figure~\ref{fig:noisy_probend_results}.
+The distributions of the normalised rank in probabilistic ending tournaments,
+Figure~\ref{fig:probend_results}, are less variant than those of noisy
+tournaments. The medians are lower than 0.1 and the distributions are skewed
+towards 0. Though the large difference between the means and the medians
+indicates some outliers, the strategies have overall performed well in the
+probabilistic ending tournaments that they participated.
+
+In tournaments with both noise and an unspecified number of turns several of
+the top ranked strategies are strategies that were highly ranked in noisy
+tournaments. This demonstrates that, $e$, $\pi$,
+$\phi$ and the Retaliate family are robust in noisy environments regardless the
+number of turns. However, strategies from the top ranks in probabilistic
+ending tournaments did not rank highly here. The distributions of the top scored
+strategies are shown in Figure~\ref{fig:noisy_probend_results}. There is no
+statistical difference between the distributions (this has been tested using
+an ANOVA test). Thus, on average these strategies had the same performances.
 
@@
     \centering
-    \includegraphics[width=.7\textwidth]{../images/performance_probend_noise.pdf}
-    \caption{\(\bar{r}\) distributions for best performed strategies in noisy
+    \includegraphics[width=.55\textwidth]{../images/performance_probend_noise.pdf}
+    \caption{\(r\) distributions for best performed strategies in noisy
     probabilistic ending tournaments.}
@@
 \end{figure}
+
+Up till now, the performances of the 194 strategies have been evaluated for
+individual tournament types. The data set considered in this work, described in
+Section~\ref{section:data_collection}, contains a total of \numberofalltournaments
+tournament results. For this part of the manuscript the strategies are ranked
+based on the median normalised rank they achieved over the entire data set.
+The top 15 strategies are given in Table~\ref{table:overall_results}
+and their normalised rank distributions are given in Figure~\ref{fig:overall_results}.
 
@@
     \input{performance_merged_table.tex}}
-    \caption{Top performances in data set}\label{table:overall_results}
+    \caption{Top performances over all the tournaments}\label{table:overall_results}
 \end{table}
 
-So far the performances have been evaluated separately for each tournament
-type. The merged data set, which was described in Section~\ref{section:data_collection},
-contains a total of 49,140 result summaries. The 15 top ranked strategies
-overall are given in Table~\ref{table:overall_results}. The top ranks
-include strategies that have been mentioned before due to their performance
-in specific tournaments. The top ranks are overtaken by the set of Retaliate
-strategies followed by BackStabber and DoubleCrosser. DoubleCrosser performed
-well in standard tournaments and the strategy is just an extension of BackStabber.
-The two strategies Nice Meta Winner and NMWE Memory One are strategies based on teams.
-PSO Gambler and Evolved HMM 5 are trained strategies introduced in~\cite{Harper2017}
-and Stein and Rapoport and Grudger are strategies from Axelrod's
-original tournament where they came 6th and 7th respectively. Forgetful Fool Me
-Once is based on the same approach as Grudger.
+The top ranks include strategies that have previously mentioned. The top ranks
+are overtaken by the set of Retaliate strategies followed by BackStabber and
+DoubleCrosser. DoubleCrosser performed well in standard tournaments and the
+strategy is just an extension of BackStabber. PSO Gambler and Evolved HMM 5 are
+trained strategies introduced in~\cite{Harper2017} and Nice Meta Winner and NMWE
+Memory One are strategies based on teams. Grudger is a strategy from Axelrod's
+original tournament and Forgetful Fool Me Once is based on the same approach as
+Grudger.
 
-Figure~\ref{fig:overall_results} gives the normalised rank distributions
-of these strategies. It is evident that the Retaliate strategies performances
-are very similar and their distributions are different in comparison with the
-rest of the top ranked strategies in the setting.
+Figure~\ref{fig:overall_results} gives the normalised rank distributions of
+these strategies. The distributions of the Retaliate strategies have no
+statistical difference. Thus, in an IPD tournament where the type is not
+specified, playing as any of the Retaliate strategies will have the result.
 
@@
     \centering
-    \includegraphics[width=.8\textwidth]{../images/performance_merged.pdf}
-    \caption{\(\bar{r}\) distributions for best performed strategies in data set.}
+    \includegraphics[width=.55\textwidth]{../images/performance_merged.pdf}
+    \caption{\(r\) distributions for best performed strategies in the data set~\cite{data}.}
     \label{fig:overall_results}
@@
 
-This section presented the top ranked performances.
+This section presented the winning strategies in a series of IPD tournaments. In
+standard tournaments the top spots were dominated by complex strategies that had
+been trained using reinforcement learning techniques. In noisy environments,
+whether the number of turns was fixed or not, the winning strategies were
+deterministic strategies designed to defect if the opponent tricked them more
+than a current amount of the times that they had tricked their opponent. In
+probabilistic ending tournaments most of the winning strategies were defecting
+strategies. A few trained finite state automata, designed by the same authors,
+also performed well in this setting. Finally the performance of all 194
+strategies over the \numberofalltournaments tournaments in this manuscript was
+assessed on \(\bar{r}\). The top ranked strategies were a mixture of behaviours
+that did well in standard tournaments and tournaments with noise, as well as a
+few strategies based on teams.
 
-\begin{itemize}
-    \item In standard tournaments the top ranked spots were dominated by complex
-    strategies that have been trained using reinforcement learning techniques.
-    These strategies dominated most the tournaments that have been involved in.
-    \item In noisy tournaments the top ranked strategies were all different to those of standard
-    tournaments. Most of the top ranked strategies were basing their decisions
-    on the he defection to cooperation ratio. These
-    strategies had won most the tournaments in which they participated, however,
-    they also ranked last in several tournaments.
-    \item Once again in probabilistic ending tournaments the top ranked
-    strategies were different to those before. More defecting strategies
-    occupied the top ranks in this setting, as well as finite state automata
-    that have been introduced all by the same authors.
-    \item Moreover, in noisy probabilistic ending tournaments it was the only
-    set of tournaments were the highly ranked strategies have been covered
-    before, more specifically, in noisy tournaments. In these tournaments the
-    means and medians of the distributions were close to 0.4. Indicating that on
-    average these strategies managed to consistently perform on the top 40\% of
-    the strategies.
-    \item Finally, using all the tournaments results, despite their type, the top
-    ranked strategies were a mixture of behaviours that do well in standard
-    tournaments and tournaments with noise. The top ranks also included two
-    strategies that are based on teams.
-\end{itemize}
-
-In this section the winning strategies in a series of IPD tournaments of
-different settings were presented. Though there have been instances of
-strategies that do well in more than one setting, most of the top ranks were
-occupied by different strategies each time. The top ranks have been occupied
-by strategies with small memory size, with infinite memory size, sophisticated
-and deterministic strategies. Even two of the most basic strategic rules,
-Cooperator and Defector, have been ranked in the top 15 places.
-
-This indicates that in an IPD tournament a winning strategy exist but only for
-the given environment, however, there is no dominant strategy in the IPD that
-can do well in any tournament where the settings can vary. The aim of the next
-section is to understand which are the factors that made these strategies
-successful. In each setting separately but also overall.
+The results of this section imply that successful strategies for specific
+settings exist for an IPD tournament. The top ranked strategies in both standard
+tournaments and tournaments with probabilistic ending, managed to rank in the
+top 10\% of the tournament most of the times. Strategies successful in noisy
+environments demonstrated that they were not affected by the number of turns.
+However, there has been not a single strategy that has shown to perform well in
+more than one setting. The aim of the next section is to understand which are
+the factors that made these strategies successful. In each setting separately
+but also overall.
 
@@
 strategy's successful performance. The factors explored are measures regarding a
-strategy's behaviour but also measures regarding the tournaments the strategies
-competed in. More specifically the factors that are included in the analysis are
-given by Table~\ref{table:manual_measures} and
-Table~\ref{table:parameters_values}.
-
-Axelrod-Python makes use of classifiers to classify strategies according to
-various dimensions. The classifiers considered in this work are the stochastic
-classifier, the make use of game and length classifiers. These determine whether
-a strategy is stochastic or deterministic, whether it makes use of the number of
-turns or the game's payoffs. The SSE is a measure extortionate
-behaviour introduced in~\cite{Knight2019}. A value of 1 indicates no
-extortionate behaviour at all whereas a value of 0 indicates that a strategy is
-always trying to extortion the opponent. The rest of the factors considered
-are the $CC$ to $C$, $CD$ to $C$, $DC$ to $C$, and $DD$ to $C$ rates as well as
-cooperating ratio of a strategy. The minimum, maximum, medium and median
-cooperating ratios of each tournament are also included, and finally the number of
-turns, the size and the probabilities of noise or the game ending.
+strategy's behaviour, alogn with measures regarding the tournaments the
+strategies competed in. These are given in Table~\ref{table:manual_measures}.
 
@@
 makes use of length &  If a strategy makes used of the number of turns & strategy classifier from~\cite{axelrodproject} & boolean  & False &  True \\
+memory usage &  The memory size of a strategy divided by the number of turns & memory size from~\cite{axelrodproject} & float & 0 &  1 \\
 SSE & A measure of how far a strategy is from extortionate behaviour & method described in~\cite{Knight2019} & float & 0 & 1 \\
-max cooperating rate $(C_{\text{max}})$  & The biggest cooperating rate in the tournament & result summary & float & 0 & 1 \\
-min cooperating rate $(C_{\text{min}})$ & The smallest cooperating rate in the tournament & result summary & float & 0 & 1 \\
-median cooperating rate $(C_{\text{median}})$ & The median cooperating rate in the tournament & result summary & float & 0 & 1 \\
+max cooperating rate $(C_{\text{max}})$  & The biggest cooperating rate in the tournament  & result summary  & float & 0 & 1\\
+min cooperating rate $(C_{\text{min}})$ & The smallest cooperating rate in the tournament  & result summary  & float & 0 & 1\\
+median cooperating rate $(C_{\text{median}})$ & The median cooperating rate in the tournament  & result summary  & float & 0 & 1\\
 mean cooperating rate $(C_{\text{mean}})$ & The mean cooperating rate in the tournament  & result summary  & float & 0 & 1 \\
-$C_r$ / $C_{\text{max}}$ & A strategy's cooperating rate divided by the maximum & manually & float & 0 & 1 \\
-$C_r$ / $C_{\text{min}}$ & A strategy's cooperating rate divided by the minimum & manually & float & 0 & 1 \\
-$C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median & manually & float & 0 & 1 \\
-$C_r$ / $C_{\text{mean}}$ & A strategy's cooperating rate divided by the mean & manually & float & 0 & 1 \\
+$C_r$ / $C_{\text{max}}$ & A strategy's cooperating rate divided by the maximum & result summary  & float & 0 & 1 \\
+$C_r$ / $C_{\text{min}}$ & A strategy's cooperating rate divided by the minimum & result summary  & float & 0 & 1 \\
+$C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median  & result summary  & float & 0 & 1\\
+$C_r$ / $C_{\text{mean}}$ & A strategy's cooperating rate divided by the mean & result summary  & float & 0 & 1 \\
 $C_r$ & The cooperating ratio of a strategy & result summary  & float & 0 & 1 \\
-$CC$ to $C$ rate & The probability a strategy will cooperate after a mutual cooperation & result summary & float & 0 & 1 \\
+$CC$ to $C$ rate & The probability a strategy will cooperate after a mutual cooperation & result summary  & float & 0 & 1\\
 $CD$ to $C$ rate & The probability a strategy will cooperate after being betrayed by the opponent & result summary  & float & 0 & 1 \\
@@
 $DD$ to $C$ rate & The probability a strategy will cooperate after a mutual defection & result summary  & float & 0 & 1 \\
+$p$ & The probability of a player's action being flip at each interaction & trial summary & float & 0 & 1 \\
+$n$ & The number of turns & trial summary & integer & 1 & 200 \\
+$e$ & The probability of a match ending in the next turn & trial summary & float & 0 & 1 \\
+$N$ & The number of strategies in the tournament & trial summary & integer & 3 & 195 \\
     \bottomrule
@@
     \end{center}
-    \caption{Manually calculated/retrieved measures.}
+    \caption{The measures which are included in the performance evaluation analysis.}
     \label{table:manual_measures}
@@
 
-%memory depth &  Strategy's memory size & strategy classifier from~\cite{axelrodproject} & integer & 0 & $\infty$ \\
+Axelrod-Python makes use of classifiers to classify strategies according to
+various dimensions. The classifiers considered in this work are the stochastic
+classifier, the make use of length and game classifiers. These determine whether
+a strategy is stochastic or deterministic, whether it makes use of the number of
+turns or the game's payoffs. The memory usage measure is calculated as the
+memory size of strategy (which is specified in the strategies implementation
+in~\cite{axelrodproject}) divide by the number of turns. For tournaments with a
+probabilistic ending the number of turns has been not collected, so the memory
+usage measure is not used for probabilistic ending tournaments.
+The SSE is a measure of extortionate behaviour introduced in~\cite{Knight2019}.
+A value of 1 indicates no extortionate behaviour at all whereas a value of 0
+indicates that a strategy is always trying to extortion it's opponent. The rest
+of the factors considered are the $CC$ to $C$, $CD$ to $C$, $DC$ to $C$, and
+$DD$ to $C$ rates as well as cooperating ratio of a strategy. The minimum,
+maximum, medium and median cooperating ratios of each tournament are also
+included, and finally the number of turns, the number of strategies and the
+probabilities of noise and the game ending are also included.
 
-The effect of these factors on a strategy's success is evaluated based on the
-correlation coefficient between the factors, the normalised rank and the median
-score. The correlation coefficients are given by Table~\ref{table:correlations}.
-Note that the correlation for the classifiers is not included because they are
-binary variables and they will evaluated by a different method.
-
-% The
-% correlations of each factor against each factor, the normalised rank and the
-% median are also given in the Appendix.
+Initially, the effect of these measures has on a strategy's success is evaluated
+based on the correlation coefficient. The correlation coefficient between them,
+the normalised rank and the median score are given by
+Table~\ref{table:correlations}. Note that the correlation for the classifiers is
+not included because they are binary variables and they will be evaluated by a
+different method. The correlation coefficients for all the measures in
+Table~\ref{table:manual_measures} against each have also been calculated and apd
+graphical representation can be found in the Appendix~\ref{app:correlations}.
 
@@
     \begin{center}
-    \resizebox{.8\textwidth}{!}{
+    \resizebox{.9\textwidth}{!}{
         \input{correlations_table.tex}
@@
 \end{center}
-\caption{Correlations table.}\label{table:correlations}
+\caption{Correlations table between the measures of Table~\ref{table:manual_measures}
+the normalised rank and the median score.}\label{table:correlations}
 \end{table}
@@
 In standard tournaments the measures  $CC$ to $C$, $C_r$, $C_r / C_{\text{max}}$
-and the cooperating ratio compared to the median and the mean have a moderate
-negative effect on the normalised rank and a moderate positive on the median
-score. The SSE error and the $DD$ to $C$ have the opposite effects. Thus, in
-standard tournaments behaving cooperative corresponds to a more successful
-performance. However, even though being cooperative pays of that's not true
-against defective strategies. Cooperating after a mutual defection lowers a
-strategy's success. Figure\ref{fig:rates_of_winners_in_standard_tournaments}
-confirms these. The winner of standard tournaments almost always cooperated
-after a mutual cooperation but the 50\% only cooperated with a probability
-of 0.2 after a mutual defection.
+and the cooperating ratio compared to $C_{\text{median}}$ and $C_{\text{mean}}$
+have a moderate negative effect on the normalised rank, and a moderate positive
+on the median score. The SSE error and the $DD$ to $C$ have the opposite
+effects. Thus, in standard tournaments behaving cooperative corresponds to a
+more successful performance. Even though being nice pays off,
+that's not true against defective strategies. Cooperating after a mutual
+defection lowers a strategy's success.
+Figure~\ref{fig:rates_of_winners_in_standard_tournaments} confirms that the
+winners of standard tournaments always cooperate after a mutual cooperation and
+almost always defected after a mutual defection.
 
@@
     \includegraphics[width=.7\textwidth]{../images/rates_of_winners_in_standard_tournaments.pdf}
-    \caption{Winners distributions
-    in standard tournaments for $CC$ to $C$ and $DD$ to $C$.}\label{fig:rates_of_winners_in_standard_tournaments}
+    \caption{Distributions of $CC$ to $C$ and $DD$ to $C$ for the winners in
+    standard tournaments.}\label{fig:rates_of_winners_in_standard_tournaments}
 \end{figure}
 
-Compared to standard tournaments in both noisy and in probabilistic ending
+Compared to standard tournaments, in both noisy and in probabilistic ending
 tournaments the higher the rates of cooperation the lower a strategy's success
-and median score. Moreover, a strategy would want to cooperate less than both
+and median score. A strategy would want to cooperate less than both
 the mean and median cooperator in such settings. In probabilistic ending
@@
 stronger effect. Thus a strategy will be punished more by it's cooperative
-behaviour in such environments. The distributions of the $C_r$ of the winners in
+behaviour in probabilistic ending environments. The distributions of the $C_r$ of the winners in
 both tournaments is given by Figure~\ref{fig:c_r_distributions}. It confirms
-that the winners in these two settings were more defective strategies, mainly
-in probabilistic ending ones.
+that the winners in noisy tournaments cooperated less than 35\% of the times
+and in probabilistic ending tournaments less than 10\%.
 
@@
     \includegraphics[width=.7\textwidth]{../images/c_r_winners_tournaments.pdf}
-    \caption{$C_r$ distributions.}\label{fig:c_r_distributions}
+    \caption{$C_r$ distributions of the winners in noisy and in probabilistic
+    ending tournaments.}\label{fig:c_r_distributions}
 \end{figure}
 
-In noisy probabilistic ending tournaments and in the overall tournaments the
-only factors that had a moderate affect are $C_r/C_{\text{mean}},
+In noisy probabilistic ending tournaments and in over all the tournaments' results,
+the pdonly measures that had a moderate affect are $C_r/C_{\text{mean}},
 C_r/C_{\text{max}}$ and $C_r$. In such environments cooperative behaviour
@@
 
-To further evaluate the effect of factors on performances a random forest
-classification~\cite{breiman2001} is applied. Initially, the performances are
+The effect of the measures on performances is further tested using a random forest
+classification~\cite{breiman2001} approach. Initially, the performances are
 clustered based on their normalised rank and the median score by a \(k-\)means
-algorithm~\cite{Arthur2007}. The number of clusters are not deterministically
-chosen but are based on the silhouette coefficients~\cite{Rousseeuw1987}.
+algorithm~\cite{Arthur2007}. The number of clusters is not deterministically
+chosen but it is based on the silhouette coefficients~\cite{Rousseeuw1987}.
 Consider the case of standard tournaments, the chosen number of clusters is
@@
 \centering
-\includegraphics[width=.7\textwidth]{../output/standard/clusters_plots.png}
+\includegraphics[width=.55\textwidth]{../output/standard/clusters_plots.png}
 \caption{Clustering trials for standard tournaments. A number of 2 clusters has
@@
     \toprule
-    type & number of clusters &  silhouette coefficient\\
+    Tournament type & Number of clusters &  Silhouette coefficient\\
     \midrule
@@
     noisy probabilistic ending & 4 & 0.415\\
-    overall                    & 3 & 0.443\\
+    over \numberofalltournaments tournaments         & 3 & 0.443\\
     \bottomrule
@@
     \end{center}
-    \caption{Number of clusters for each type and overall and the respective silhouette coefficients.}
+    \caption{Number of clusters for each type and over all the tournament results
+    and the respective silhouette coefficients.}
     \label{table:number_of_clusters}
@@
 based on $R^2$ are given by Table~\ref{table:accuracy_random_forest}. The out of
-the bag error~\cite{hastie2005} has also been calculated. The models fit well and
-the values of the accuracy measures on the test data and the OOB error indicate that they are not
-over fitting.
+the bag error~\cite{hastie2005} has also been calculated. The models fit well, and
+a high value of both the accuracy measure on the test data and the
+OOB error indicate that the model ispdf not over fitting.
 
@@
     \toprule
-    type & $R^2$ training data &  $R^2$ test data  & $R^2$ OBB score\\
+    Tournament type & $R^2$ training data &  $R^2$ test data  & $R^2$ OBB score\\
     \midrule
@@
     noisy probabilistic ending & 0.990490  & 0.813905 & 0.791418\\
-    overall                    & 0.993396 & 0.913409 & 0.898059 \\
+    over \numberofalltournaments tournaments & 0.993396 & 0.913409 & 0.898059 \\
     \bottomrule
@@
 
-The importance of the features on the classification task along with their inter
-trees variability are given by Figure~\ref{fig:importance}. The importance
-indicates that the two factors that affected performances the most were $C_r /
-C_{median}$ and $C_r / C_{mean}$. The classifiers which where not included in
-the previous analysis appear to have no effect, and several of the factors that
-are highted by the importance are inline with the correlation results.
+The importance that the measures of Table~\ref{table:manual_measures} had on the
+classification task; to which cluster a performance was assigned to, have been
+calculated and are given by Figure~\ref{fig:importance}. The classifiers which
+where not included in the previous analysis appear to have no effect, and
+several of the measures that are highted by the importance are inline with the
+correlation results. The most important measures based on the random forest
+analysis were $C_r / C_{median}$ and $C_r / C_{mean}$.
 
@@
 
-The behaviour a strategy adapts in comparison with the mean and median
-cooperator influence the success of a strategy. To gain a better understanding on
-the influence of these measures, in each tournament type the distributions of
-the winner's \(C_r / C_{\text{median}}\) and \(C_r / C_{\text{median}}\)
-are given by Figures~\ref{fig:mean_median_std},~\ref{fig:mean_median_noisy},
+The effect of both these measures can be further explored. Their distributions
+for the winners of the tournaments are given by
+Figures~\ref{fig:mean_median_std},~\ref{fig:mean_median_noisy},
 \ref{fig:mean_median_probend}, \ref{fig:mean_median_probend_noisy} and
-\ref{fig:mean_median_overall}. In summary, in a noisy, noisy probabilistic 
-or if a strategy does not know the settings on the environment is about to compete,
-a strategy should cooperate 60\% of times the median/mean cooperator does. In
-standard tournaments a strategy would want to have the same cooperating ratio
-as the mean/median and finally in probabilistic ending tournaments a strategy
-wants to be defective.
+\ref{fig:mean_median_overall}. The results suggest that if a strategy with
+a theory of mind competed in a standard tournament, then the strategy would
+want to be the mean/median cooperator of that tournament. In comparison, if the
+same strategy competed in a tournament with noisy or the strategy had no
+information regarding the setting of the tournament, then it would
+want to cooperate 67\% of the times the mean or median cooperator did.
+In probabilistic ending tournament it has already been mentioned that defecting
+strategies prevail. This result is once again confirmed in this section.
 
@@
     \centering
-    \includegraphics[width=.7\textwidth]{../images/compared_to_mean_median_standard.pdf}
+    \includegraphics[width=.5\textwidth]{../images/compared_to_mean_median_standard.pdf}
     \caption{Distributions of \(C_r / C_{\text{median}}\)
@@
     \centering
-    \includegraphics[width=.7\textwidth]{../images/compared_to_mean_median_noisy.pdf}
+    \includegraphics[width=.5\textwidth]{../images/compared_to_mean_median_noisy.pdf}
     \caption{Distributions of \(C_r / C_{\text{median}}\)
@@
     \centering
-    \includegraphics[width=.7\textwidth]{../images/compared_to_mean_median_probend.pdf}
+    \includegraphics[width=.5\textwidth]{../images/compared_to_mean_median_probend.pdf}
     \caption{Distributions of \(C_r / C_{\text{median}}\)
@@
     \centering
-    \includegraphics[width=.7\textwidth]{../images/compared_to_mean_median_probend_noisy.pdf}
+    \includegraphics[width=.5\textwidth]{../images/compared_to_mean_median_probend_noisy.pdf}
     \caption{Distributions of \(C_r / C_{\text{median}}\)
@@
     \centering
-    \includegraphics[width=.7\textwidth]{../images/compared_to_mean_median_overall.pdf}
+    \includegraphics[width=.5\textwidth]{../images/compared_to_mean_median_overall.pdf}
     \caption{Distributions of \(C_r / C_{\text{median}}\)
@@
 
-The factors which have an effect on the performances were presented here by two
-approaches which included the correlation coefficients and a random forest
+In this section the effect of several measures, regarding a strategy's behaviour
+and the tournament, on it's performance were presented. This was done using
+two approaches. pCorrelation coefficients and a random forest
 analysis. The results of these are discussed in the following section.
@@
 
-This manuscript explored a variety of strategic behaviours in the game of the
-Iterated Prisoner's Dilemma and presented an evaluation of performance in the
-game. A large number of computer tournaments have been analysis and demonstrated
-that a single dominant strategy does not exist in the game. Moreover, it
-was shown that from a series of factors that a strategy has control over the
-tge factors that can influence it's performance is the cooperating ratio compared
-to that of it's environment.
+This manuscript has explored the performance of 194 strategies of the Iterated
+Prisoner's Dilemma inp a large number of computer tournaments. The results of
+the analysis demonstrated that, although for specific tournament types, such as
+standard, noisy and probabilistic ending tournaments, dominant strategies exist
+there is not a single dominant strategy that is set to do if the environments
+vary. Moreover, a strategy with a theory of mind should aim to adapt its behaviour
+based on the mean and median cooperators.
 
-A total of 186 strategies were used in this manuscript, which are available via
-an open source software, the Axelrod-Python. By making use of the software a
-total of 49,140 computer tournaments results were gathered. In
-Section~\ref{section:top_performances}, the result summaries were used to
-present the top performances. This was not done over the entire data set. The
-data set contains results from four different settings, and these were also
-studied individually. The top performances were presented for all the different
-combinations of the results summary. Though Retaliate set of families,
-strategies introduced in~\cite{axelrodproject}, did perform well in noisy
-environments and this feature allowed the strategies to rank well in more than
-one tournament type, the analysis concluded that there is not a single dominant
-strategy in the Iterated Prisoner's Dilemma. THough a dominant perform
-was not highlighted by the analysis of this manuscript the factors that made
-performances successful were further explored.
+The 194 strategies used in this manuscript have been mainly for the literature,
+and they have been accessible due to an open source software called
+Axelrod-Python. The software was used to generate a total of
+\numberofalltournaments computer tournaments results with different number of
+strategies and different participants each time. The data collection was
+described in Section~\ref{section:data_collection}. In
+Section~\ref{section:top_performances}, the tournaments results were used to
+present the top performances. This was not done only over the entire data set.
+The data set contained results from four different settings, and these were also
+studied individually. In standard tournaments complex strategies trained using
+reinforcement learning ranked in the top places. In probabilistic ending
+tournaments, several trained strategies based on finite state automata also
+performed well. The rest top strategies, in this setting, were defecting
+strategies. Finally, in tournaments with noisy, the Retaliate set of strategies
+demonstrated their robustness in tournaments with probabilistic ending and not.
 
-In Section~\ref{section:evaluation_of_performance} an analysis of strategies
-features was covered. The results of this analysis showed that a strategy's
-characteristics such as it's stochasticity and the information it used regarding
-the game had no effect on the strategy's success. The most important
-factors have been those that compared the strategy's behaviour to it's environment.
-The cooperating ratio of the strategy compared to the mean and median cooperator
-was highlighted as the most important feature in the analysis. More specifically,
-if a strategy were to enter a tournament with a theory of mind of it's environment
-it would choose to be the median cooperator in standard tournaments, the
-defector in probabilistic ending tournaments and to cooperate 60\% of the median
-in noisy and noisy probabilistic tournaments. Lastly, if a strategy was
-aware of the opponents but not of the setting on the tournament, a strategy
-would be more likely to be successful if it were to identify the median
-cooperator and cooperated 60\% of the times that they did.
+Section~\ref{section:evaluation_of_performance}, covered an analysis of
+performance based on several measures associated with a strategy and with the
+environments it was competing. The results of this analysis showed that a
+strategy's characteristics such as it's stochasticity, and the information it
+used regarding the game had no effect on the strategy's success. The most
+important factors have been those that compared the strategy's behaviour to it's
+environment. The cooperating ratio of the strategy compared to the mean and
+median cooperator was highlighted as the most important feature in the analysis.
+More specifically, if a strategy were to enter a tournament with a theory of
+mind of it's environment it would choose to be the median cooperator in standard
+tournaments, the defector in probabilistic ending tournaments and to cooperate
+60\% of the times the median cooperator did in noisy and noisy probabilistic
+tournaments. Lastly, if a strategy was aware of the opponents but not of the
+setting on the tournament, a strategy would be more likely to be successful if
+it were to identify the median cooperator and cooperated 67\% of the times that
+they did.
 
@@
 
+\section{Acknowledgements}
+
+A variety of software have been used in this work:
+
+\begin{itemize}
+    \item The Axelrod library for IPD simulations~\cite{axelrodproject}.
+    \item The Matplotlib library for visualisation~\cite{hunter2007matplotlib}.
+    \item The Numpy library for data manipulation~\cite{walt2011numpy}.
+    \item The scikit-learn library for data analysis~\cite{scikit-learn}.
+\end{itemize}
+
 \appendix
+
+\section{A summary of parameters}\label{app:parameters}
+
+\begin{table}[h]
+    \begin{center}
+    \resizebox{.7\textwidth}{!}{
+    \begin{tabular}{llc}
+    \toprule
+measure & measure explanation \\
+ \midrule
+stochastic                  & If a strategy is stochastic \\
+makes use of game           & If a strategy makes used of the game information  \\
+makes use of length         & If a strategy makes used of the number of turns \\
+memory usage                & The memory size of a strategy divided by the number of turns \\
+SSE                         & A measure of how far a strategy is from extortionate behaviour \\
+$(C_{\text{max}})$          & The biggest cooperating rate in the tournament \\
+$(C_{\text{min}})$          & The smallest cooperating rate in the tournament \\
+$(C_{\text{median}})$       & The median cooperating rate in the tournament \\
+$(C_{\text{mean}})$         & The mean cooperating rate in the tournament \\
+$C_r$ / $C_{\text{max}}$    & A strategy's cooperating rate divided by the maximum \\
+$C_r$ / $C_{\text{min}}$    & A strategy's cooperating rate divided by the minimum \\
+$C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median \\
+$C_r$ / $C_{\text{mean}}$   & A strategy's cooperating rate divided by the mean \\
+$C_r$                       & The cooperating ratio of a strategy \\
+$CC$ to $C$ rate            & The probability a strategy will cooperate after a mutual cooperation \\
+$CD$ to $C$ rate            & The probability a strategy will cooperate after being betrayed by the opponent \\
+$DC$ to $C$ rate            & The probability a strategy will cooperate after betraying the opponent\\
+$DD$ to $C$ rate            & The probability a strategy will cooperate after a mutual defection\\
+$p$                         & The probability of a player's action being flip at each interaction \\
+$n$                         & The number of turns \\
+$e$                         & The probability of a match ending in the next turn \\
+$N$                         & The number of strategies in the tournament \\
+    \bottomrule
+        \end{tabular}}
+    \end{center}
+    \caption{The measures which are included in the performance evaluation analysis.}
+\end{table}
 
@@
 
-\section{Acknowledgements}
+\section{Correlation coefficients}\label{app:correlations}
 
-A variety of software have been used in this work:
+A graphical representation of the correlation coefficients for the measures in
+Table~\ref{table:manual_measures}.
 
-\begin{itemize}
-    \item The Axelrod library for IPD simulations~\cite{axelrodproject}.
-    \item The Matplotlib library for visualisation~\cite{hunter2007matplotlib}.
-    \item The Numpy library for data manipulation~\cite{walt2011numpy}.
-    \item The scikit-learn library for data analysis~\cite{scikit-learn}.
-\end{itemize}
+\begin{figure}[!htbp]
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../images/standard_correlation_plot.pdf}
+        \end{center}
+        \caption{Correlation coefficients of measures in Table~\ref{table:manual_measures}
+        for standard tournaments}
+\end{figure}
+\begin{figure}[!htbp]
+    \begin{center}
+        \includegraphics[width=.75\linewidth]{../images/noise_correlation_plot.pdf}
+    \end{center}
+    \caption{Correlation coefficients of measures in Table~\ref{table:manual_measures}
+    for noisy tournaments}
+\end{figure}
+\begin{figure}[!htbp]
+    \begin{center}
+        \includegraphics[width=.75\linewidth]{../images/probend_correlation_plot.pdf}
+    \end{center}
+    \caption{Correlation coefficients of measures in Table~\ref{table:manual_measures}
+    for probabilistic ending tournaments}
+\end{figure}
+\begin{figure}[!htbp]
+    \begin{center}
+        \includegraphics[width=.75\linewidth]{../images/probend_noise_correlation_plot.pdf}
+    \end{center}
+    \caption{Correlation coefficients of measures in Table~\ref{table:manual_measures}
+    for noisy probabilistic ending tournaments}
+\end{figure}
 

### 2019-10-24 paper/perfomances_table.tex
draft people hanging it to Vince

\begin{tabular}{lllllllll}
\toprule
{} &                     Name & \$\textbackslash bar\{r\}\$ &                 Name & \$\textbackslash bar\{r\}\$ &               Name & \$\textbackslash bar\{r\}\$ &                 Name & \$\textbackslash bar\{r\}\$ \\
\midrule
0  &            Evolved HMM 5 &   0.00667 &               Grumpy &    0.1402 &          Fortress4 &   0.01266 &           Alternator &    0.3037 \\
1  &           Evolved FSM 16 &   0.00995 &                  \$e\$ &   0.19388 &           Defector &   0.01429 &               \$\textbackslash phi\$ &   0.30978 \\
2  &     EvolvedLookerUp2\_2\_2 &   0.01064 &       Tit For 2 Tats &    0.2069 &  Better and Better &   0.01587 &                  \$e\$ &    0.3125 \\
3  &  Evolved FSM 16 Noise 05 &   0.01667 &         Cycle Hunter &   0.21538 &    Tricky Defector &   0.01875 &                \$\textbackslash pi\$ &   0.31686 \\
4  &        PSO Gambler 2\_2\_2 &   0.02143 &       Risky QLearner &   0.22222 &          Fortress3 &   0.02174 &    Limited Retaliate &   0.35263 \\
5  &              Evolved ANN &   0.02878 &          Retaliate 3 &   0.22887 &     Gradual Killer &   0.02532 &     Anti Tit For Tat &   0.35431 \\
6  &            Evolved ANN 5 &    0.0339 &        Cycler CCCCCD &   0.23507 &         Aggravater &   0.02778 &          Retaliate 3 &   0.35563 \\
7  &        PSO Gambler 1\_1\_1 &   0.03704 &          Retaliate 2 &   0.23913 &             Raider &   0.03077 &  Limited Retaliate 3 &   0.35563 \\
8  &            Evolved FSM 4 &   0.04891 &      Defector Hunter &   0.24038 &         Cycler DDC &   0.04545 &            Retaliate &   0.35714 \\
9  &         PSO Gambler Mem1 &   0.05036 &            Retaliate &   0.24177 &        Hard Prober &   0.05128 &          Retaliate 2 &   0.35767 \\
10 &                 Winner12 &   0.06011 &  Hard Tit For 2 Tats &      0.25 &         SolutionB1 &   0.06024 &  Limited Retaliate 2 &   0.36134 \\
11 &             Fool Me Once &    0.0614 &             ShortMem &   0.25286 &      Meta Minority &   0.06077 &             Hopeless &   0.36842 \\
12 &                      DBS &   0.07143 &  Limited Retaliate 3 &   0.25316 &              Bully &   0.06081 &    Arrogant QLearner &   0.40651 \\
13 &            DoubleCrosser &     0.072 &    Limited Retaliate &   0.25706 &    Fool Me Forever &    0.0708 &    Cautious QLearner &   0.40909 \\
14 &              BackStabber &   0.07519 &                \$\textbackslash pi\$ &   0.25801 &             EasyGo &   0.07101 &      Fool Me Forever &   0.41764 \\
\bottomrule
\end{tabular}

### 2019-10-24 paper/top_perfomances.tex
draft people hanging it to Vince

@@
-\begin{tabular}{ggllggllr}
+\begin{tabular}{lggllggllr}
 \toprule
-\multicolumn{2}{g}{Standard} & \multicolumn{2}{c}{Noisy} & \multicolumn{2}{g}{Probabilistic ending} &  \multicolumn{2}{c}{Noisy probabilistic ending} \\
+& \multicolumn{2}{g}{Standard} & \multicolumn{2}{c}{Noisy} & \multicolumn{2}{g}{Probabilistic ending} &  \multicolumn{2}{c}{Noisy probabilistic ending} \\
 \midrule
-    Name &  $\bar{r}$ & Name &  $\bar{r}$ & Name &  $\bar{r}$ & Name &  $\bar{r}$\\
+& Name & $\bar{r}$ &                 Name & $\bar{r}$ &               Name & $\bar{r}$ &                 Name & $\bar{r}$ \\
 \midrule
-Evolved HMM 5           & 0.00658 & Grumpy              & 0.13953 & Fortress4         &  0.01266 & Alternator          & 0.30390\\
-Evolved FSM 16          & 0.00990 & $e$                 & 0.19048 & Defector          &  0.01444 & $\phi$              & 0.31025\\
-EvolvedLookerUp2 2 2    & 0.01064 & Cooperator          & 0.19565 & Better and Better &  0.01587 & $e$                 & 0.31293\\
-Evolved FSM 16 Noise 05 & 0.01639 & Tit For 2 Tats      & 0.20520 & Tricky Defector   &  0.01869 & $\pi$               & 0.31818\\
-PSO Gambler 2 2 2       & 0.02139 & Cycle Hunter        & 0.22222 & Fortress3         &  0.02198 & Limited Retaliate   & 0.35294\\
-Evolved ANN             & 0.02874 & Risky QLearner      & 0.22424 & Gradual Killer    &  0.02521 & Anti Tit For Tat    & 0.35429\\
-Evolved ANN 5           & 0.03390 & Retaliate 3         & 0.23077 & Aggravater        &  0.02797 & Retaliate 3         & 0.35484\\
-PSO Gambler 1 1 1       & 0.03723 & Retaliate 2         & 0.23762 & Raider            &  0.03077 & Limited Retaliate 3 & 0.35563\\
-Evolved FSM 4           & 0.04839 & Retaliate           & 0.24309 & Cycler DDC        &  0.04545 & Retaliate           & 0.35588\\
-PSO Gambler Mem1        & 0.05000 & Hard Tit For 2 Tats & 0.24658 & Hard Prober       &  0.05085 & Retaliate 2         & 0.35714\\
-Winner12                & 0.05946 & Limited Retaliate 3 & 0.25000 & SolutionB1        &  0.06040 & Limited Retaliate 2 & 0.36066\\
-Fool Me Once            & 0.06122 & ShortMem            & 0.25272 & Meta Minority     &  0.06040 & Hopeless            & 0.36913\\
-DBS                     & 0.07087 & Limited Retaliate   & 0.25698 & Bully             &  0.06061 & Arrogant QLearner   & 0.40526\\
-DoubleCrosser           & 0.07190 & Limited Retaliate 2 & 0.26027 & Fool Me Forever   &  0.07018 & Cautious QLearner   & 0.40711\\
-BackStabber             & 0.07500 & $\phi$              & 0.26201 & EasyGo            &  0.07065 & Risky QLearner      & 0.41989\\
+1 &           Evolved HMM 5 &   0.00667 &               Grumpy &    0.1402 &          Fortress4 &   0.01266 &           Alternator &    0.3037 \\
+2 &          Evolved FSM 16 &   0.00995 &                  $e$ &   0.19388 &           Defector &   0.01429 &               $\phi$ &   0.30978 \\
+3 &    EvolvedLookerUp2 2 2 &   0.01064 &       Tit For 2 Tats &    0.2069 &  Better and Better &   0.01587 &                  $e$ &    0.3125 \\
+4 & Evolved FSM 16 Noise 05 &   0.01667 &         Cycle Hunter &   0.21538 &    Tricky Defector &   0.01875 &                $\pi$ &   0.31686 \\
+5 &       PSO Gambler 2 2 2 &   0.02143 &       Risky QLearner &   0.22222 &          Fortress3 &   0.02174 &    Limited Retaliate &   0.35263 \\
+6 &             Evolved ANN &   0.02878 &          Retaliate 3 &   0.22887 &     Gradual Killer &   0.02532 &     Anti Tit For Tat &   0.35431 \\
+7 &           Evolved ANN 5 &    0.0339 &        Cycler CCCCCD &   0.23507 &         Aggravater &   0.02778 &          Retaliate 3 &   0.35563 \\
+8 &       PSO Gambler 1 1 1 &   0.03704 &          Retaliate 2 &   0.23913 &             Raider &   0.03077 &  Limited Retaliate 3 &   0.35563 \\
+9 &           Evolved FSM 4 &   0.04891 &      Defector Hunter &   0.24038 &         Cycler DDC &   0.04545 &            Retaliate &   0.35714 \\
+10 &        PSO Gambler Mem1 &   0.05036 &            Retaliate &   0.24177 &        Hard Prober &   0.05128 &          Retaliate 2 &   0.35767 \\
+11 &                Winner12 &   0.06011 &  Hard Tit For 2 Tats &      0.25 &         SolutionB1 &   0.06024 &  Limited Retaliate 2 &   0.36134 \\
+12 &            Fool Me Once &    0.0614 &             ShortMem &   0.25286 &      Meta Minority &   0.06077 &             Hopeless &   0.36842 \\
+13 &                     DBS &   0.07143 &  Limited Retaliate 3 &   0.25316 &              Bully &   0.06081 &    Arrogant QLearner &   0.40651 \\
+14 &           DoubleCrosser &     0.072 &    Limited Retaliate &   0.25706 &    Fool Me Forever &    0.0708 &    Cautious QLearner &   0.40909 \\
+15 &             BackStabber &   0.07519 &                $\pi$ &   0.25801 &             EasyGo &   0.07101 &      Fool Me Forever &   0.41764 \\
 \bottomrule

### 2019-11-04 paper/main.tex
address minor comments on draft

@@
 has been of interest to the scientific community since the formulation of the
-game in 1950~\cite{Flood1958}. Following the computer tournaments of Axelrod in
+game in 1950~\cite{Flood1958}. Following the computer tournaments of Axelrod in the
 1980's~\cite{Axelrod1980a, Axelrod1980b}, a strategy's performance in a round
@@
 
-Another set of IPD strategies that have received a lot of attention, the
-American Mathematical Society's news section stated that ``the world of game
-theory is currently on fire'', are the zero-determinants~\cite{Press2012}. By
+Another set of IPD strategies that have received a lot of attention
+are the zero-determinants~\cite{Press2012}. By
 forcing a linear relationship between the payoffs the zero-determinant
 strategies can ensure that they will never receive less than their opponents.
+The
+American Mathematical Society's news section stated that ``the world of game
+theory is currently on fire''.
 Zero-determinant strategies are indeed a set of mathematically unique strategies
@@
 
-Though only a few selected pieces of work have been discussed, the IPD is
+Though only a select pieces of work have been discussed, the IPD is
 rich, and new strategies and competitions are being published every year.
@@
 futhermore, explore the factors of their success. This is done not only for
-standard round robin tournaments, but also for tournaments with noisy and
+standard round robin tournaments, but also for tournaments with noise and
 tournaments with a probabilistic ending. The different tournament types as well
 as the data collection are covered in Section~\ref{section:data_collection}.
-Section~\ref{section:top_performances}, focuses on the best performed strategies
+Section~\ref{section:top_performances}, focuses on the best performing strategies
 for each type of tournament and overall.
@@
 sections, however, the full set of parameters and their definitions are given in
-Appendix~\ref{app:parameters}. %TODO: fix table
+Appendix~\ref{app:parameters}. All the data is available at~\cite{data}.
 
@@
 because each row contains information for each strategy that participated in the
-tournament. The information include the strategy's rank, median score, the rate
-with which the strategy cooperated $(C_r)$, it's wins and the probability that
-the strategy cooperated in the opening move. Moreover, the rates of a strategy
+tournament. The information includes the strategy's rank, median score, the rate
+with which the strategy cooperated $(C_r)$, its match win count and the probability that
+the strategy cooperated in the opening move. Moreover, the probabilities of a strategy
 being in any of the four states ($CC, CD, DC, DD$), and the rate of which the
@@
 \end{center}
-\caption{Output result of a signle tournament.}\label{table:output_result}
+\caption{Output result of a single tournament.}\label{table:output_result}
 \end{table}
@@
 tournaments of each type. The strategy's normalised rank distribution in these
-is given in Figure~\ref{fig:tit_for_tat_r_distribution}. Because of the strategies'
+is given in Figure~\ref{fig:tit_for_tat_r_distribution}. A value of \(r =
+0\) corresponds to a strategy winning the tournament where a value of
+\(r = 1\) corresponds to the strategy coming last. Because of the strategies'
 multiple entries their performance is evaluated based on the
-\textbf{median normalised rank} denoted as \(\bar{r}\). A value of \(\bar{r} =
-0\) corresponds to a strategy winning the tournament where a a value of
-\(\bar{r} = 1\) corresponds to the strategy coming last.
+\textbf{median normalised rank} denoted as \(\bar{r}\).
 
@@
 
-The top strategies in noisy tournaments include deterministic strategies, such
+The top strategies in noisy tournaments are shown in Figure~\ref{fig:noisy_results}. These include deterministic strategies, such
 as Tit For 2 Tats~\cite{Axelrod1980b}, Hard Tit For 2 Tats~\cite{Stewart2012}
@@
 distributions in noisy environments are more variant with higher medians
-compared to standard tournaments. The distributions are skewed both towards 0
-and 1. This indicates that although the top ranked strategies mainly performed
+compared to standard tournaments. The distributions are bimodal.
+This indicates that although the top ranked strategies mainly performed
 well, there are several tournaments that they ranked in the bottom half.
@@
 strategies based on finite state automata introduced by Daniel and Wendy
-Ashlock. These strategies have been evolved using reinformed learning, however,
+Ashlock. These strategies have been evolved using reinforcement learning, however,
 there were trained to maximise their payoffs in tournaments with fixed turns
@@
 The distributions of the normalised rank in probabilistic ending tournaments,
+shown in
 Figure~\ref{fig:probend_results}, are less variant than those of noisy
@@
 tournaments. This demonstrates that, $e$, $\pi$,
-$\phi$ and the Retaliate family are robust in noisy environments regardless the
+$\phi$ and the Retaliate family are robust in noisy environments regardless of the
 number of turns. However, strategies from the top ranks in probabilistic
@@
 
-The top ranks include strategies that have previously mentioned. The top ranks
+The top ranks include strategies that have been previously mentioned. The top ranks
 are overtaken by the set of Retaliate strategies followed by BackStabber and
@@
 memory usage &  The memory size of a strategy divided by the number of turns & memory size from~\cite{axelrodproject} & float & 0 &  1 \\
-SSE & A measure of how far a strategy is from extortionate behaviour & method described in~\cite{Knight2019} & float & 0 & 1 \\
+SSE & A measure of how far a strategy is from ZD behaviour & method described in~\cite{Knight2019} & float & 0 & 1 \\
 max cooperating rate $(C_{\text{max}})$  & The biggest cooperating rate in the tournament  & result summary  & float & 0 & 1\\
@@
 Axelrod-Python makes use of classifiers to classify strategies according to
-various dimensions. The classifiers considered in this work are the stochastic
-classifier, the make use of length and game classifiers. These determine whether
+various dimensions. These determine whether
 a strategy is stochastic or deterministic, whether it makes use of the number of
@@
 
-Initially, the effect of these measures has on a strategy's success is evaluated
-based on the correlation coefficient. The correlation coefficient between them,
-the normalised rank and the median score are given by
-Table~\ref{table:correlations}. Note that the correlation for the classifiers is
-not included because they are binary variables and they will be evaluated by a
+Table~\ref{table:correlations} shows the correlation coefficients between the
+measures of Table~\ref{table:manual_measures} the median score and the median
+normalised rank. Note that the correlation for the classifiers is
+not included because they are binary variables and they will be evaluated using a
 different method. The correlation coefficients for all the measures in
-Table~\ref{table:manual_measures} against each have also been calculated and apd
+Table~\ref{table:manual_measures} against themselves have also been calculated and a
 graphical representation can be found in the Appendix~\ref{app:correlations}.
@@
 on the median score. The SSE error and the $DD$ to $C$ have the opposite
-effects. Thus, in standard tournaments behaving cooperative corresponds to a
+effects. Thus, in standard tournaments behaving cooperatively corresponds to a
 more successful performance. Even though being nice pays off,
@@
 winners of standard tournaments always cooperate after a mutual cooperation and
-almost always defected after a mutual defection.
+almost always defects after a mutual defection.
 
@@
 In noisy probabilistic ending tournaments and in over all the tournaments' results,
-the pdonly measures that had a moderate affect are $C_r/C_{\text{mean}},
+the only measures that had a moderate affect are $C_r/C_{\text{mean}},
 C_r/C_{\text{max}}$ and $C_r$. In such environments cooperative behaviour
@@
 a high value of both the accuracy measure on the test data and the
-OOB error indicate that the model ispdf not over fitting.
+OOB error indicate that the model is not over fitting.
 
@@
     \toprule
-    Tournament type & $R^2$ training data &  $R^2$ test data  & $R^2$ OBB score\\
+    Tournament type & $R^2$ training data &  $R^2$ test data  & $R^2$ OOB score\\
     \midrule
@@
     \caption{Distributions of \(C_r / C_{\text{median}}\)
-    and \(C_r / C_{\text{median}}\) for standard tournaments.}\label{fig:mean_median_std}
+    and \(C_r / C_{\text{median}}\) for winners of standard tournaments.}\label{fig:mean_median_std}
 \end{figure}
@@
     \caption{Distributions of \(C_r / C_{\text{median}}\)
-    and \(C_r / C_{\text{median}}\) for noisy tournaments.}\label{fig:mean_median_noisy}
+    and \(C_r / C_{\text{median}}\) for winners of noisy tournaments.}\label{fig:mean_median_noisy}
 \end{figure}
@@
     \caption{Distributions of \(C_r / C_{\text{median}}\)
-    and \(C_r / C_{\text{median}}\) for probabilistic ending tournaments.}\label{fig:mean_median_probend}
+    and \(C_r / C_{\text{median}}\) for winners of probabilistic ending tournaments.}\label{fig:mean_median_probend}
 \end{figure}
@@
     \caption{Distributions of \(C_r / C_{\text{median}}\)
-    and \(C_r / C_{\text{median}}\) for noisy probabilistic ending tournaments.}\label{fig:mean_median_probend_noisy}
+    and \(C_r / C_{\text{median}}\) for winners of noisy probabilistic ending tournaments.}\label{fig:mean_median_probend_noisy}
 \end{figure}
@@
     \caption{Distributions of \(C_r / C_{\text{median}}\)
-    and \(C_r / C_{\text{median}}\) for over all the tournaments.}\label{fig:mean_median_overall}
+    and \(C_r / C_{\text{median}}\) for winners of over all the tournaments.}\label{fig:mean_median_overall}
 \end{figure}
@@
 and the tournament, on it's performance were presented. This was done using
-two approaches. pCorrelation coefficients and a random forest
+two approaches. Correlation coefficients and a random forest
 analysis. The results of these are discussed in the following section.
@@
 This manuscript has explored the performance of 194 strategies of the Iterated
-Prisoner's Dilemma inp a large number of computer tournaments. The results of
-the analysis demonstrated that, although for specific tournament types, such as
+Prisoner's Dilemma in a large number of computer tournaments. The results of
+the analysis demonstrated that, although for specific tournament type, such as
 standard, noisy and probabilistic ending tournaments, dominant strategies exist
-there is not a single dominant strategy that is set to do if the environments
+there is not a single dominant strategy if the environments
 vary. Moreover, a strategy with a theory of mind should aim to adapt its behaviour
@@
 Section~\ref{section:top_performances}, the tournaments results were used to
-present the top performances. This was not done only over the entire data set.
+present the top performances.
 The data set contained results from four different settings, and these were also
@@
 performed well. The rest top strategies, in this setting, were defecting
-strategies. Finally, in tournaments with noisy, the Retaliate set of strategies
+strategies. Finally, in tournaments with noise, the Retaliate set of strategies
 demonstrated their robustness in tournaments with probabilistic ending and not.
@@
 environments it was competing. The results of this analysis showed that a
-strategy's characteristics such as it's stochasticity, and the information it
+strategy's characteristics such as whether or not it's stochastic, and the information it
 used regarding the game had no effect on the strategy's success. The most

### 2019-11-06 paper/main.tex
re run analysis with repetitions

@@
 game of \(n\) number of turns against each other. Note that self interactions
-and a match against a random strategy are not included. Similarly, \textbf{noisy
-tournaments} have \(N\) strategies and \(n\) number of turns, but at each turn
-there is a probability \(p\) that a player's action will be flipped.
+are not included. Similarly, \textbf{noisy
+tournaments} have \(N\) strategies and \(p_n\) number of turns, but at each turn
+there is a probability \(p_n\) that a player's action will be flipped.
 \textbf{Probabilistic ending tournaments}, are of size \(N\) and after each turn
-a match between strategies ends with a given probability \(e\). Finally,
+a match between strategies ends with a given probability \(p_e\). Finally,
 \textbf{noisy probabilistic ending} tournaments have both a noise probability
-\(p\) and an ending probability \(e\). For smoothing the simulated results a
-tournament is repeated for \(k\) number of times and the winner of each tournament
+\(p_n\) and an ending probability \(p_e\). For smoothing the simulated results a
+tournament is repeated for \(k\) number of times. To evaluate the effect of smoothing
+this is allowed to vary. The winner of each tournament
 is based on the average score a strategy achieved and not by number of wins.
@@
     $n$ & number of turns      & 1 & 200 \\
-    $p$ & probability of flipping action at each turn  & 0 & 1   \\
-    $e$ & probability of match ending in the next turn & 0 & 1   \\
+    $p_n$ & probability of flipping action at each turn  & 0 & 1   \\
+    $p_e$ & probability of match ending in the next turn & 0 & 1   \\
     \bottomrule
@@
         $n \gets  \text{randomly select integer}\in [n_{min}, n_{max}]$\;
-        $p \gets  \text{randomly select float}\in [p_{min}, p_{max}]$\;
-        $e \gets   \text{randomly select float}\in [e_{min}, e_{max}]$\;
+        $p \gets  \text{randomly select float}\in [p_{n\, min}, p_{n\, max}]$\;
+        $e \gets   \text{randomly select float}\in [p_{e\, min}, p_{e\, max}]$\;
         \vspace{0.4cm}
         $\text{result standard}$ $\gets$ Axelrod.tournament$(\text{players}, n, k)$\;
-        $\text{result noisy}$ $\gets$ Axelrod.tournament$(\text{players}, n, p, k)$\;
-        $\text{result probabilistic ending}$ $\gets$ Axelrod.tournament$(\text{players}, e, k)$\;
-        $\text{result noisy probabilistic ending}$ $\gets$ Axelrod.tournament$(\text{players}, p, e, k)$\;
+        $\text{result noisy}$ $\gets$ Axelrod.tournament$(\text{players}, n, p_n, k)$\;
+        $\text{result probabilistic ending}$ $\gets$ Axelrod.tournament$(\text{players}, p_e, k)$\;
+        $\text{result noisy probabilistic ending}$ $\gets$ Axelrod.tournament$(\text{players}, p_n, p_e, k)$\;
 
@@
 
+Table
+A summary of the number of entries each strategy
+has is given by Table.
+Each strategy participated on average in 5180 tournaments of each type. The
+strategy that participated in the most tournaments () is and the strategy
+with the minimum enties is.
+
+\begin{table}[!htbp]
+    \begin{center}
+    \resizebox{.45\textwidth}{!}{
+        \input{summary_table_of_entries.tex}
+    }
+\end{center}
+% \caption{Top performances for each tournament type based on $\bar{r}$.}
+% \label{table:top_performances}
+\end{table}
+
 \section{Top ranked strategies}\label{section:top_performances}
@@
     \centering
-    \includegraphics[width=.45\textwidth]{../images/tit_for_tat_r_distributions.pdf}
+    \includegraphics[width=.55\textwidth]{../images/tit_for_tat_r_distributions.pdf}
     \caption{Tit For Tat's $r$ distribution in tournaments. The best performance
@@
 number of turns. However, strategies from the top ranks in probabilistic
-ending tournaments did not rank highly here. The distributions of the top scored
-strategies are shown in Figure~\ref{fig:noisy_probend_results}. There is no
-statistical difference between the distributions (this has been tested using
-an ANOVA test). Thus, on average these strategies had the same performances.
+ending tournaments did not rank highly here.
 
@@
 $DD$ to $C$ rate & The probability a strategy will cooperate after a mutual defection & result summary  & float & 0 & 1 \\
-$p$ & The probability of a player's action being flip at each interaction & trial summary & float & 0 & 1 \\
+$p_n$ & The probability of a player's action being flip at each interaction & trial summary & float & 0 & 1 \\
 $n$ & The number of turns & trial summary & integer & 1 & 200 \\
-$e$ & The probability of a match ending in the next turn & trial summary & float & 0 & 1 \\
+$p_e$ & The probability of a match ending in the next turn & trial summary & float & 0 & 1 \\
 $N$ & The number of strategies in the tournament & trial summary & integer & 3 & 195 \\
+$k$ & The number of repetitions of a given tournament & trial summary & integer & 10 & 100 \\
     \bottomrule
@@
     \centering
-    \includegraphics[width=.7\textwidth]{../images/rates_of_winners_in_standard_tournaments.pdf}
+    \includegraphics[width=.5\textwidth]{../images/rates_of_winners_in_standard_tournaments.pdf}
     \caption{Distributions of $CC$ to $C$ and $DD$ to $C$ for the winners in
@@
     \centering
-    \includegraphics[width=.7\textwidth]{../images/c_r_winners_tournaments.pdf}
+    \includegraphics[width=.5\textwidth]{../images/c_r_winners_tournaments.pdf}
     \caption{$C_r$ distributions of the winners in noisy and in probabilistic

### 2019-11-06 paper/top_perfomances.tex
re run analysis with repetitions

@@
 \midrule
-1 &           Evolved HMM 5 &   0.00667 &               Grumpy &    0.1402 &          Fortress4 &   0.01266 &           Alternator &    0.3037 \\
-2 &          Evolved FSM 16 &   0.00995 &                  $e$ &   0.19388 &           Defector &   0.01429 &               $\phi$ &   0.30978 \\
-3 &    EvolvedLookerUp2 2 2 &   0.01064 &       Tit For 2 Tats &    0.2069 &  Better and Better &   0.01587 &                  $e$ &    0.3125 \\
-4 & Evolved FSM 16 Noise 05 &   0.01667 &         Cycle Hunter &   0.21538 &    Tricky Defector &   0.01875 &                $\pi$ &   0.31686 \\
-5 &       PSO Gambler 2 2 2 &   0.02143 &       Risky QLearner &   0.22222 &          Fortress3 &   0.02174 &    Limited Retaliate &   0.35263 \\
-6 &             Evolved ANN &   0.02878 &          Retaliate 3 &   0.22887 &     Gradual Killer &   0.02532 &     Anti Tit For Tat &   0.35431 \\
-7 &           Evolved ANN 5 &    0.0339 &        Cycler CCCCCD &   0.23507 &         Aggravater &   0.02778 &          Retaliate 3 &   0.35563 \\
-8 &       PSO Gambler 1 1 1 &   0.03704 &          Retaliate 2 &   0.23913 &             Raider &   0.03077 &  Limited Retaliate 3 &   0.35563 \\
-9 &           Evolved FSM 4 &   0.04891 &      Defector Hunter &   0.24038 &         Cycler DDC &   0.04545 &            Retaliate &   0.35714 \\
-10 &        PSO Gambler Mem1 &   0.05036 &            Retaliate &   0.24177 &        Hard Prober &   0.05128 &          Retaliate 2 &   0.35767 \\
-11 &                Winner12 &   0.06011 &  Hard Tit For 2 Tats &      0.25 &         SolutionB1 &   0.06024 &  Limited Retaliate 2 &   0.36134 \\
-12 &            Fool Me Once &    0.0614 &             ShortMem &   0.25286 &      Meta Minority &   0.06077 &             Hopeless &   0.36842 \\
-13 &                     DBS &   0.07143 &  Limited Retaliate 3 &   0.25316 &              Bully &   0.06081 &    Arrogant QLearner &   0.40651 \\
-14 &           DoubleCrosser &     0.072 &    Limited Retaliate &   0.25706 &    Fool Me Forever &    0.0708 &    Cautious QLearner &   0.40909 \\
-15 &             BackStabber &   0.07519 &                $\pi$ &   0.25801 &             EasyGo &   0.07101 &      Fool Me Forever &   0.41764 \\
+0  &            Evolved HMM 5 &   0.00667 &                 Grumpy &   0.14020 &          Fortress4 &   0.01266 &           Alternator &   0.30370 \\
+1  &           Evolved FSM 16 &   0.00995 &                    $e$ &   0.19388 &           Defector &   0.01429 &               $ phi$ &   0.30978 \\
+2  &     EvolvedLookerUp2 2 2 &   0.01064 &         Tit For 2 Tats &   0.20617 &  Better and Better &   0.01587 &                  $e$ &   0.31250 \\
+3  &  Evolved FSM 16 Noise 05 &   0.01667 &  Slow Tit For Two Tats &   0.20962 &    Tricky Defector &   0.01875 &                $ pi$ &   0.31686 \\
+4  &        PSO Gambler 2 2 2 &   0.02143 &           Cycle Hunter &   0.21538 &          Fortress3 &   0.02174 &    Limited Retaliate &   0.35263 \\
+5  &              Evolved ANN &   0.02878 &         Risky QLearner &   0.22222 &     Gradual Killer &   0.02532 &     Anti Tit For Tat &   0.35431 \\
+6  &            Evolved ANN 5 &   0.03390 &            Retaliate 3 &   0.22887 &         Aggravater &   0.02778 &          Retaliate 3 &   0.35563 \\
+7  &        PSO Gambler 1 1 1 &   0.03704 &          Cycler CCCCCD &   0.23507 &             Raider &   0.03077 &  Limited Retaliate 3 &   0.35563 \\
+8  &            Evolved FSM 4 &   0.04891 &            Retaliate 2 &   0.23913 &         Cycler DDC &   0.04545 &            Retaliate &   0.35714 \\
+9  &         PSO Gambler Mem1 &   0.05036 &        Defector Hunter &   0.24038 &        Hard Prober &   0.05128 &          Retaliate 2 &   0.35767 \\
+10 &                 Winner12 &   0.06011 &              Retaliate &   0.24177 &         SolutionB1 &   0.06024 &  Limited Retaliate 2 &   0.36134 \\
+11 &             Fool Me Once &   0.06140 &    Hard Tit For 2 Tats &   0.25000 &      Meta Minority &   0.06077 &             Hopeless &   0.36842 \\
+12 &                      DBS &   0.07143 &               ShortMem &   0.25286 &              Bully &   0.06081 &    Arrogant QLearner &   0.40651 \\
+13 &            DoubleCrosser &   0.07200 &    Limited Retaliate 3 &   0.25316 &    Fool Me Forever &   0.07080 &    Cautious QLearner &   0.40909 \\
+14 &              BackStabber &   0.07519 &      Limited Retaliate &   0.25706 &             EasyGo &   0.07101 &      Fool Me Forever &   0.41764 \\
 \bottomrule

### 2019-11-06 src/cluster_analysis.py

@@ -114,6 +114,7 @@ def draw_feature_importance_bar_plot(
         "noise": r"$p$",
         "probend": r"$e$",
         "memory_usage": "memory usage",
+        "repetitions": r"$k$"
     }
     color = matplotlib.cm.viridis(0.4)
     plt.figure()
@@ -177,6 +178,7 @@ if __name__ == "__main__":
         "Cooperation_rating_comp_to_min",
         "Cooperation_rating_comp_to_median",
         "Cooperation_rating_comp_to_mean",
+        "repetitions"
     ]
 
     if file == "standard":

### 2019-11-06 src/plot.py

@@ -24,10 +24,13 @@ features_labels = {
     "Cooperation_rating_comp_to_median": r"$C_r$ / $C_{median}$",
     "Cooperation_rating_comp_to_mean": r"$C_r$ / $C_{mean}$",
     "turns": r"$n$",
-    "noise": r"$p$",
-    "probend": r"$e$",
+    "noise": r"$p_n$",
+    "probend": r"$p_e$",
     "Normalized_Rank": r"$\bar{r}$",
     "Median_score": "Median score",
+    "size": r"$N$",
+    "memory_usage": "memory usage",
+    "repetitions": r"$k$",
 }
 
 

### 2019-11-06 src/process_data.py
re run analysis with repetitions

@@ -62,10 +62,10 @@ def get_strategies_properties():
             use_of_game = 1
         if "length" in strategy().classifier["makes_use_of"]:
             use_of_length = 1
-        if 'Hard Go By Majority:' in name:
-            name = ''.join(name.split(':'))
-        if 'Soft Go By Majority:' in name:
-            name = ''.join(name.split(':'))
+        if "Hard Go By Majority:" in name:
+            name = "".join(name.split(":"))
+        if "Soft Go By Majority:" in name:
+            name = "".join(name.split(":"))
         axl_strategies.loc[i] = [
             name,
             int(strategy().classifier["stochastic"]),
@@ -91,10 +91,10 @@ def get_error_for_row(row):
 
 def fix_name(row):
     name = row["Name"]
-    if 'Hard Go By Majority:' in name:
-        return ''.join(name.split(':'))
-    if 'Soft Go By Majority:' in name:
-        return ''.join(name.split(':'))
+    if "Hard Go By Majority:" in name:
+        return "".join(name.split(":"))
+    if "Soft Go By Majority:" in name:
+        return "".join(name.split(":"))
     return name.split(":")[0]
 
 
@@ -116,12 +116,17 @@ def get_cooporation_rating_compared_to_min(row):
     return row["Cooperation_rating_min"] / row["Cooperation_rating"]
 
 
+def get_cluster_on(row, percentage):
+    value = row["Normalized_Rank"] <= percentage
+    return int(value)
+
+
 if __name__ == "__main__":
 
     file = sys.argv[1]
     output = file.replace(".csv", "_processed.csv")
 
-    replace = {"Slow Tit For Two Tats": "Tit For 2 Tats"}
+    # replace = {"Slow Tit For Two Tats": "Tit For 2 Tats"}
 
     strategies_properties = get_strategies_properties()
     strategies_properties = strategies_properties.set_index("Name")
@@ -129,9 +134,15 @@ if __name__ == "__main__":
     df = pd.read_csv(file, index_col=0)
 
     print("Processing")
-    df = df.replace(replace)
+    # df = df.replace(replace)
     df["SSE"] = df.apply(get_error_for_row, axis=1)
     df["Name"] = df.apply(fix_name, axis=1)
+
+    percentages = [0.05, 0.25, 0.5]
+    for percentage in percentages:
+        df[f"cluster_on_{percentage}"] = df.apply(
+            get_cluster_on, args=(percentage,), axis=1
+        )
     df = pd.merge(
         df,
         strategies_properties,

### 2019-11-11 src/cluster_analysis.py
add repetitions to analysis

@@ -114,7 +114,9 @@ def draw_feature_importance_bar_plot(
         "noise": r"$p$",
         "probend": r"$e$",
         "memory_usage": "memory usage",
-        "repetitions": r"$k$"
+        "repetitions": r"$k$",
+        "size": r"$N$",
+
     }
     color = matplotlib.cm.viridis(0.4)
     plt.figure()
@@ -147,8 +149,8 @@ if __name__ == "__main__":
     else:
         num_of_workers = 4
 
-    input_directory = "data/%s_v_3_processed.csv" % file
-    output_name = file.split("_v_3_processed")[0]
+    input_directory = "data/%s_3_processed.csv" % file
+    output_name = file.split("_3_processed")[0]
 
     output_directory = "output/%s/" % output_name
     if not os.path.exists(output_directory):
@@ -178,7 +180,8 @@ if __name__ == "__main__":
         "Cooperation_rating_comp_to_min",
         "Cooperation_rating_comp_to_median",
         "Cooperation_rating_comp_to_mean",
-        "repetitions"
+        "repetitions",
+        "size"
     ]
 
     if file == "standard":

### 2019-11-11 src/plot.py

@@ -26,7 +26,7 @@ features_labels = {
     "turns": r"$n$",
     "noise": r"$p_n$",
     "probend": r"$p_e$",
-    "Normalized_Rank": r"$\bar{r}$",
+    "Normalized_Rank": r"$r$",
     "Median_score": "Median score",
     "size": r"$N$",
     "memory_usage": "memory usage",

### 2019-11-11 paper/top_perfomances.tex
add slow tit for two tats

--- 2019-10-24 paper/top_perfomances.tex
@@
 \midrule
-1 &           Evolved HMM 5 &   0.00667 &               Grumpy &    0.1402 &          Fortress4 &   0.01266 &           Alternator &    0.3037 \\
-2 &          Evolved FSM 16 &   0.00995 &                  $e$ &   0.19388 &           Defector &   0.01429 &               $\phi$ &   0.30978 \\
-3 &    EvolvedLookerUp2 2 2 &   0.01064 &       Tit For 2 Tats &    0.2069 &  Better and Better &   0.01587 &                  $e$ &    0.3125 \\
-4 & Evolved FSM 16 Noise 05 &   0.01667 &         Cycle Hunter &   0.21538 &    Tricky Defector &   0.01875 &                $\pi$ &   0.31686 \\
-5 &       PSO Gambler 2 2 2 &   0.02143 &       Risky QLearner &   0.22222 &          Fortress3 &   0.02174 &    Limited Retaliate &   0.35263 \\
-6 &             Evolved ANN &   0.02878 &          Retaliate 3 &   0.22887 &     Gradual Killer &   0.02532 &     Anti Tit For Tat &   0.35431 \\
-7 &           Evolved ANN 5 &    0.0339 &        Cycler CCCCCD &   0.23507 &         Aggravater &   0.02778 &          Retaliate 3 &   0.35563 \\
-8 &       PSO Gambler 1 1 1 &   0.03704 &          Retaliate 2 &   0.23913 &             Raider &   0.03077 &  Limited Retaliate 3 &   0.35563 \\
-9 &           Evolved FSM 4 &   0.04891 &      Defector Hunter &   0.24038 &         Cycler DDC &   0.04545 &            Retaliate &   0.35714 \\
-10 &        PSO Gambler Mem1 &   0.05036 &            Retaliate &   0.24177 &        Hard Prober &   0.05128 &          Retaliate 2 &   0.35767 \\
-11 &                Winner12 &   0.06011 &  Hard Tit For 2 Tats &      0.25 &         SolutionB1 &   0.06024 &  Limited Retaliate 2 &   0.36134 \\
-12 &            Fool Me Once &    0.0614 &             ShortMem &   0.25286 &      Meta Minority &   0.06077 &             Hopeless &   0.36842 \\
-13 &                     DBS &   0.07143 &  Limited Retaliate 3 &   0.25316 &              Bully &   0.06081 &    Arrogant QLearner &   0.40651 \\
-14 &           DoubleCrosser &     0.072 &    Limited Retaliate &   0.25706 &    Fool Me Forever &    0.0708 &    Cautious QLearner &   0.40909 \\
-15 &             BackStabber &   0.07519 &                $\pi$ &   0.25801 &             EasyGo &   0.07101 &      Fool Me Forever &   0.41764 \\
+0  &            Evolved HMM 5 &   0.00667 &                 Grumpy &   0.14020 &          Fortress4 &   0.01266 &           Alternator &   0.30370 \\
+1  &           Evolved FSM 16 &   0.00995 &                    $e$ &   0.19388 &           Defector &   0.01429 &               $\phi$ &   0.30978 \\
+2  &     EvolvedLookerUp2 2 2 &   0.01064 &         Tit For 2 Tats &   0.20617 &  Better and Better &   0.01587 &                  $e$ &   0.31250 \\
+3  &  Evolved FSM 16 Noise 05 &   0.01667 &  Slow Tit For Two Tats &   0.20962 &    Tricky Defector &   0.01875 &                $\pi$ &   0.31686 \\
+4  &        PSO Gambler 2 2 2 &   0.02143 &           Cycle Hunter &   0.21538 &          Fortress3 &   0.02174 &    Limited Retaliate &   0.35263 \\
+5  &              Evolved ANN &   0.02878 &         Risky QLearner &   0.22222 &     Gradual Killer &   0.02532 &     Anti Tit For Tat &   0.35431 \\
+6  &            Evolved ANN 5 &   0.03390 &            Retaliate 3 &   0.22887 &         Aggravater &   0.02778 &          Retaliate 3 &   0.35563 \\
+7  &        PSO Gambler 1 1 1 &   0.03704 &          Cycler CCCCCD &   0.23507 &             Raider &   0.03077 &  Limited Retaliate 3 &   0.35563 \\
+8  &            Evolved FSM 4 &   0.04891 &            Retaliate 2 &   0.23913 &         Cycler DDC &   0.04545 &            Retaliate &   0.35714 \\
+9  &         PSO Gambler Mem1 &   0.05036 &        Defector Hunter &   0.24038 &        Hard Prober &   0.05128 &          Retaliate 2 &   0.35767 \\
+10 &                 Winner12 &   0.06011 &              Retaliate &   0.24177 &         SolutionB1 &   0.06024 &  Limited Retaliate 2 &   0.36134 \\
+11 &             Fool Me Once &   0.06140 &    Hard Tit For 2 Tats &   0.25000 &      Meta Minority &   0.06077 &             Hopeless &   0.36842 \\
+12 &                      DBS &   0.07143 &               ShortMem &   0.25286 &              Bully &   0.06081 &    Arrogant QLearner &   0.40651 \\
+13 &            DoubleCrosser &   0.07200 &    Limited Retaliate 3 &   0.25316 &    Fool Me Forever &   0.07080 &    Cautious QLearner &   0.40909 \\
+14 &              BackStabber &   0.07519 &      Limited Retaliate &   0.25706 &             EasyGo &   0.07101 &      Fool Me Forever &   0.41764 \\
 \bottomrule

### 2019-11-11 paper/main.tex
new draft with additions

@@
 \newcommand{\numberofalltournaments}{\input{number_of_all_tournaments.tex}}
+\newcommand{\numberofstrategies}{\input{unique_number_of_strategies.tex}}
 
@@
 \begin{abstract}
-
 The Iterated Prisoner's Dilemma has been used for decades as a model of
@@
 structures such as neural networks, the literature has been exploring the
-performance of strategies in the game for years. Most of these strategies are
-now accessible due to an open source package; Axelrod-Python. This manuscript
-make use of Axelrod-Python to conduct a meta analysis of Iterated Prisoner's
-Dilemma tournaments. The aim is to evaluate the performance of 194 strategies
-over \numberofalltournaments Iterated Prisoner's Dilemma tournaments and to
-explore the factors of their success.
+performance of strategies in the game for years. The results of the literature,
+however, have been relying on the performance of specific strategies in a finite
+number of tournaments, whereas this manuscript evaluates
+\numberofstrategies strategies' effectiveness in more than 40000 tournaments.
+The top ranked strategies are presented, and moreover, the impact of features on
+their success are analysed using machine learning techniques. The analysis
+determines that the cooperating ratio of a
+strategy in a given tournament compared to the mean and median cooperator is the
+most important feature. The conclusions are distinct for different types of
+tournaments. A strategy with a theory of mind would aim to be the mean/median
+cooperator in standard tournaments, whereas in tournaments with probabilistic
+ending it would aim to cooperate 10\% of the times the median cooperator did.
+In tournaments with noise and a probability of ending an effective strategy
+cooperates 60\% of the times the median/mean cooperator did, and in tourmanents
+with only noise or even in a setting that the tournament can be any of the
+above a strategy should aim to play 67\% as a median/mean cooperator.
 \end{abstract}
@@
 Another set of IPD strategies that have received a lot of attention
-are the zero-determinants~\cite{Press2012}. By
-forcing a linear relationship between the payoffs the zero-determinant
-strategies can ensure that they will never receive less than their opponents.
-The
+are the zero-determinant strategies (ZDs)~\cite{Press2012}. By
+forcing a linear relationship between the payoffs ZDs can ensure that they will
+never receive less than their opponents. The
 American Mathematical Society's news section stated that ``the world of game
 theory is currently on fire''.
-Zero-determinant strategies are indeed a set of mathematically unique strategies
+ZDs are indeed a set of mathematically unique strategies
 and robust in pairwise interactions, however, their simplicity and extortionate
 behaviour have been tested. In~\cite{Harper2017} a tournament containing over
-200 strategies, including zero-determinants, was ran. None of the zero-determinant
-strategies ranked in top spots. Instead, the top ranked strategies were a set of
-trained strategies based lookup tables~\cite{Axelrod1987}, hidden markov
+200 strategies, including ZDs, was ran and none of the them
+ranked in top spots. Instead, the top ranked strategies were a set of
+trained strategies based on lookup tables~\cite{Axelrod1987}, hidden markov
 models~\cite{Harper2017} and finite state automata~\cite{Miller1996}.
 
-Though only a select pieces of work have been discussed, the IPD is
-rich, and new strategies and competitions are being published every year.
-The question, however, still remains the same: what is the best way to play the
-game?
-
-This manuscript uses an open source package called
-Axelrod-Python~\cite{axelrodproject} to simulate a large number of computer
-tournaments, using as many strategies as possible from the literature. The aim
-is to evaluate the performance of 194 strategies in IPD tournaments, and
-futhermore, explore the factors of their success. This is done not only for
-standard round robin tournaments, but also for tournaments with noise and
-tournaments with a probabilistic ending. The different tournament types as well
-as the data collection are covered in Section~\ref{section:data_collection}.
-Section~\ref{section:top_performances}, focuses on the best performing strategies
-for each type of tournament and overall.
+Though only a select pieces of work have been discussed, the IPD literature is
+rich, and new strategies and competitions are being published every year. The
+question, however, still remains the same: what is the best way to play the
+game? Compared to other works, whereas a few selected strategies are evaluated
+on a small number of tournaments, this manuscript evaluates the performance of \numberofstrategies
+strategies in \numberofalltournaments tournaments. These tournaments do not
+consist by just standard round robin tournaments, but also by tournaments with noise
+and tournaments with a probabilistic ending. The later part of the paper, evaluates
+the impact of features on the performance of the strategies using modern
+machine learning techniques. These features include measures regarding a
+strategy's behaviour and measures regarding the tournaments. The data set used
+in this work has been made publicly available~\cite{data} and can be used
+for further analysis and insights.
+
+The different tournament types as well as the data collection, which is made
+possible due an open source package called Axelrod-Python~\cite{axelrodproject},
+are covered in Section~\ref{section:data_collection}.
+Section~\ref{section:top_performances}, focuses on the best performing
+strategies for each type of tournament and overall.
 Section~\ref{section:evaluation_of_performance}, explores the traits which
 contribute to good performance, and finally the results are summarised in
-Section~\ref{section:conclusion}.
-
-This manuscripts uses several parameters. These are introduced in the following
-sections, however, the full set of parameters and their definitions are given in
-Appendix~\ref{app:parameters}. All the data is available at~\cite{data}.
+Section~\ref{section:conclusion}. This manuscripts uses several parameters.
+These are introduced in the following sections, however, the full set of
+parameters and their definitions are given in Appendix~\ref{app:parameters}.
 
@@
 
-For the purposes of this manuscript a data set containing results of IPD tournaments
-has been generated and is available at~\cite{data}. This
-was done using the open source package Axelrod-Python~\cite{axelrodproject}, and
-more specifically, version 3.0.0. Axelrod-Python allows for different types of
-IPD computer tournaments to be simulated whilst
-containing a list of over 180 strategies. Most of these are strategies described
-in the literature with a few exceptions being strategies that have been
-contributed specifically to the package. This paper make use of 194 strategies
-implemented in version 3.0.0. A list of the strategies is given in the
-Appendix~\ref{app:list_of_players}. Though Axelrod-Python features several
-tournament types, this work considers only standard, noisy, probabilistic ending
-and noisy probabilistic ending tournaments.
+For the purposes of this manuscript a data set containing results of IPD
+tournaments has been generated and is available at~\cite{data}. This was done using the
+open source package Axelrod-Python~\cite{axelrodproject}, and more specifically,
+version 3.0.0. Axelrod-Python allows for different types of IPD computer
+tournaments to be simulated whilst containing a list of over 180 strategies.
+Most of these are strategies described in the literature with a few exceptions
+being strategies that have been contributed specifically to the package. This
+paper make use of \numberofstrategies strategies implemented in version 3.0.0. A
+list of the strategies is given in the Appendix~\ref{app:list_of_players}.
+Though Axelrod-Python features several tournament types, this work considers
+only standard, noisy, probabilistic ending and noisy probabilistic ending
+tournaments.
 
@@
 are not included. Similarly, \textbf{noisy
-tournaments} have \(N\) strategies and \(p_n\) number of turns, but at each turn
+tournaments} have \(N\) strategies and \(n\) number of turns, but at each turn
 there is a probability \(p_n\) that a player's action will be flipped.
@@
 \(p_n\) and an ending probability \(p_e\). For smoothing the simulated results a
-tournament is repeated for \(k\) number of times. To evaluate the effect of smoothing
-this is allowed to vary. The winner of each tournament
-is based on the average score a strategy achieved and not by number of wins.
-
-% A summary of each tournaments' parameters is given in
-% Table~\ref{table:tournaments_parameters}.
-
-% \begin{table}[!htbp]
-%     \begin{center}
-%         \resizebox{.85\textwidth}{!}{
-%         \begin{tabular}{lcccccc}
-%     \toprule
-%     tournament type & number of strategies & repetitions & turns & noise probability & probability of match ending \\
-%     \midrule
-%     standard & $N$ & k & $n$ & - & - \\
-%     noisy & $N$  & k & $n$ & $p$ & - \\
-%     probabilistic ending & $N$ & k & - & - & $e$ \\
-%     noisy probabilistic ending & $N$ & k & - & $p$ & $e$ \\
-%     \bottomrule
-%         \end{tabular}}
-%     \end{center}
-%     \caption{Tournament types' parameters.}
-%     \label{table:tournaments_parameters}
-% \end{table}
+tournament is repeated for \(k\) number of times. This was allowed to vary 
+in order to evaluate the effect of smoothing. The winner of each tournament
+is based on the average score a strategy achieved and not by the number of wins.
 
@@
 Algorithm~\ref{algorithm:data_generation}. For each trial a random size \(N\) is
-selected, and from the 194 strategies a random list of \(N\) strategies is
+selected, and from the \numberofstrategies strategies a random list of \(N\) strategies is
 chosen. For the given list of strategies a standard, a noisy, a probabilistic
 ending and a noisy probabilistic ending tournament are performed and repeated
-\(k\) times. The parameters for the tournaments as well as the number of
-repetitions are selected once for each trial. The parameters and their
+\(k\) times. The parameters for the tournaments, as well as the number of
+repetitions, are selected once for each trial. The parameters and their
 respective minimum and maximum values are given by
@@
 
-The source code for the data collection as well as the source code for
+The source code for the data collection, as well as the source code for
 the analysis, which will be discussed in the following sections, have been written
@@
         $n \gets  \text{randomly select integer}\in [n_{min}, n_{max}]$\;
-        $p \gets  \text{randomly select float}\in [p_{n\, min}, p_{n\, max}]$\;
-        $e \gets   \text{randomly select float}\in [p_{e\, min}, p_{e\, max}]$\;
+        $p_n \gets  \text{randomly select float}\in [p_{n\, min}, p_{n\, max}]$\;
+        $p_e \gets   \text{randomly select float}\in [p_{e\, min}, p_{e\, max}]$\;
         \vspace{0.4cm}
@@
 retrieved. Each tournament outputs a result summary in the form of
-Table~\ref{table:output_result}.
+Table~\ref{table:output_result}. Each strategy have participated on average in
+5154 tournaments of each type. The strategy with the maximum participation in each
+tournament type is Inverse Punisher with 5639 entries. The strategy with the
+minimum entries is EvolvedLookerUp 1 1 1 which was selected in 4693 trials.
 
@@
 tournament. The information includes the strategy's rank, median score, the rate
-with which the strategy cooperated $(C_r)$, its match win count and the probability that
-the strategy cooperated in the opening move. Moreover, the probabilities of a strategy
-being in any of the four states ($CC, CD, DC, DD$), and the rate of which the
-strategy cooperated after each state.
+with which the strategy cooperated $(C_r)$, its match win count and the
+probability that the strategy cooperated in the opening move. Moreover, the
+probabilities of a strategy being in any of the four states ($CC, CD, DC, DD$),
+and the rate of which the strategy cooperated after each state. A measure that
+has been manually included is the \textbf{normalised rank}. The normalised rank,
+denoted as $r$, is calculated as a strategy's rank divided by the tournament's
+size ($N$). In the next section the performance of these strategies is evaluated
+based on their normalised rank.
 
 \newcolumntype{g}{>{\columncolor{Gray}}c}
-\begin{table}[h!]
+\begin{table}[!htbp]
     \begin{center}
@@
 
-A measure that has been manually included
-is the \textbf{normalised rank}. The normalised rank, denoted as $r$, is
-calculated as a strategy's rank divided by the tournament's size ($N$). The
-normalised rank will be used in the next section to evaluate the performance of
-strategies.
-
-Table
-A summary of the number of entries each strategy
-has is given by Table.
-Each strategy participated on average in 5180 tournaments of each type. The
-strategy that participated in the most tournaments () is and the strategy
-with the minimum enties is.
-
-\begin{table}[!htbp]
-    \begin{center}
-    \resizebox{.45\textwidth}{!}{
-        \input{summary_table_of_entries.tex}
-    }
-\end{center}
-% \caption{Top performances for each tournament type based on $\bar{r}$.}
-% \label{table:top_performances}
-\end{table}
-
 \section{Top ranked strategies}\label{section:top_performances}
 
-This section evaluates the performance of 194 IPD strategies. The performance of
+This section evaluates the performance of \numberofstrategies IPD strategies. The performance of
 each strategy is evaluated in four tournament types, which were presented in Section
@@
 
-Each strategy participated in multiple tournaments of the same type (on average 5180).
+Each strategy participated in multiple tournaments of the same type (on average 5154).
 For example Tit For Tat has participated in a total of 5114
@@
     \centering
-    \includegraphics[width=.55\textwidth]{../images/tit_for_tat_r_distributions.pdf}
+    \includegraphics[width=.6\textwidth]{../images/tit_for_tat_r_distributions.pdf}
     \caption{Tit For Tat's $r$ distribution in tournaments. The best performance
@@
 ranked strategies. The distributions are skewed towards zero and the highest
-median is at 0.075. This indicates that the top ranked strategies are very
-likely to perform well in a standard tournament despite the tournament size,
-the opponents, the turns etc.
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.55\textwidth]{../images/performance_standard.pdf}
+median, of the top 15 strategies, is at 0.075. This indicates that the top ranked
+strategies perform well in any given standard tournament, despite the opponents and
+the number of turns.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.7\textwidth]{../images/performance_standard.pdf}
     \caption{$r$ distributions of top 15 strategies in standard tournaments.}\label{fig:std_results}
@@
 The top strategies in noisy tournaments are shown in Figure~\ref{fig:noisy_results}. These include deterministic strategies, such
-as Tit For 2 Tats~\cite{Axelrod1980b}, Hard Tit For 2 Tats~\cite{Stewart2012}
+as Tit For 2 Tats~\cite{Axelrod1980b}, Slow Tit For Tats~\cite{axelrodproject}, Hard Tit For 2 Tats~\cite{Stewart2012}
 and Cycler CCCCCD, and strategies which decide their actions based on the
-cooperations to defections ratio, such as ShortMem~\cite{Carvalho2013}, Grumpy,
-$e$, $\pi$ and $\phi$ (all from~\cite{axelrodproject}). The Retaliate and
+cooperations to defections ratio, such as ShortMem~\cite{Carvalho2013}, Grumpy
+and $e$~\cite{axelrodproject}. The Retaliate and
 Limited Retaliate strategies are implemented in~\cite{axelrodproject} by the
-same contributor. The strategies are designed to defect if the opponent has
-tricked the strategy more often than \(x\%\) of the times that the strategy has
-done the same. Finally, in $4^{\text{th}}$ and $9^{\text{th}}$ are Hunter
+same contributor. They are strategies designed to defect if the opponent has
+tricked them more often than \(x\%\) of the times that they have
+done the same. Finally, in $4^{\text{th}}$ and $9^{\text{th}}$ place are Hunter
 strategies which trying to extort, equivalently, strategies that play cyclically
@@
 distributions in noisy environments are more variant with higher medians
-compared to standard tournaments. The distributions are bimodal.
-This indicates that although the top ranked strategies mainly performed
-well, there are several tournaments that they ranked in the bottom half.
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.55\textwidth]{../images/performance_noise.pdf}
+compared to standard tournaments. The distributions are bimodal. This indicates
+that although the top ranked strategies mainly performed well, there are several
+tournaments that they ranked in the bottom half. To gain a better understanding
+of behaviour in noisy tournaments, the \(r\) distribution over the noise
+probability \(p_n\) for the top 6 strategies of Figure~\ref{fig:noisy_results},
+are given in Figure~\ref{fig:effect_of_noise}.
+
+For \(p_n\) strictly lower than 0.5, Grumpy, Tit For 2 Tats and Slow Tit For Two Tat
+have a moderate performing, whereas \(e\), Cycle Hunter and Ricky QLearner are
+behaving poorly. At \(p_n=0.5\), all the distributions are bimodal because
+with a 0.5 probability of noise any strategies corresponds to a random player.
+Interestedly, for a \(p_n\) larger than 0.5 all of the 6 strategies become
+successful. Note that a value \(p_n=1\) corresponds to a strategy playing the
+exact opposite from what they intended. Thus, the successful strategies in
+noisy tournaments presented here, are effective when they are not playing as
+themselves. If \(p_n\) was strictly less 0.5 then the top ranked strategies
+are different, Table~\ref{table:subset_noise_result}. The top spots are mainly
+overtaken by the Meta strategies which are based on teams.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.7\textwidth]{../images/performance_noise.pdf}
     \caption{\(r\) distributions for best performed strategies in noisy tournaments.}
@@
 \end{figure}
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=\textwidth]{../images/noise_effect.pdf}
+    \caption{\(r\) distributions for top 6 strategies in noisy tournaments over
+    the probability of noisy ($p_n$).}
+    \label{fig:effect_of_noise}
+\end{figure}
+
+\begin{table}[!htbp]
+    \centering
+    \resizebox{.30\textwidth}{!}{
+    \input{performance_noise_subset_table.tex}}
+    \caption{Top performances in noisy tournaments where \(p_n<0.5\).}\label{table:subset_noise_result}
+\end{table}
 
@@
 from ~\cite{prison}), Bully (Reverse Tit For Tat)~\cite{Nachbar1992} and
-Defector. Thus, it's surprisingly that EasyGo and Fool Me Forever are ranked
-$14^{\text{th}}$ and $15^{\text{th}}$. These strategies are actually the same;
-they will defect until their opponent defect, then they will cooperate until the
-end. Both strategies have repeatedly ranked highly as shown in
-Figure~\ref{fig:probend_results}, and there are cases for which they were the
-winners of the tournament.
+Defector. Thus, it's surprisingly that EasyGo and Fool Me Forever which are
+strategies that will defect until their opponent defect, then they will cooperate
+until the end, ranked $14^{\text{th}}$ and $15^{\text{th}}$. Upon inspection,
+it was concluded that they are actually the same strategy. This was not known to
+the authors at the time of data collection. Figure~\ref{fig:probend_results}
+verifies that their perfomance is the same. Both strategies have repeatedly
+ranked highly and there are cases for which they were the winners of the
+tournament.
 
@@
     \centering
-    \includegraphics[width=.55\textwidth]{../images/performance_probend.pdf}
+    \includegraphics[width=.7\textwidth]{../images/performance_probend.pdf}
     \caption{\(r\) distributions for best performed strategies in probabilistic ending tournaments.}
@@
 Figure~\ref{fig:probend_results}, are less variant than those of noisy
-tournaments. The medians are lower than 0.1 and the distributions are skewed
+tournaments. The medians of the top 15 strategies are lower than 0.1 and the distributions are skewed
 towards 0. Though the large difference between the means and the medians
@@
 
+The distributions of \(r\) over \(p_e\) for the top 6 strategies are also given
+by Figure~\ref{fig:effect_of_probend}. It is shown that the rank of the
+strategies is decreasing as the probability of the game ending increases and at
+the point of \(p_e=0.1\) the strategies become dominant. All the top ranked
+strategies in this setting are defecting strategies, and what is exhibited is
+that they do better as the probability of the game ending in the next turn
+increases, which is inline with the Folk Theorem~\cite{Fudenberg2009}. Consider
+tournaments where the probability of the game ending was less than 0.1, the top
+ranked strategies based on \(\bar{r}\) are given
+by~Table~\ref{table:subset_probend_result}. The top ranked strategies include
+strategies based on teams, trained strategies, Grudger and Spiteful Tit for Tat.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=\textwidth]{../images/folk_theorem.pdf}
+    \caption{\(r\) distributions for top 6 strategies in probabilistic ending tournaments
+    over $p_e$.}
+    \label{fig:effect_of_probend}
+\end{figure}
+
+\begin{table}[!htbp]
+    \centering
+    \resizebox{.30\textwidth}{!}{
+    \input{performance_probend_subset_table.tex}}
+    \caption{Top performances in probabilistic ending tournaments with \(p_e < 0.1\)}
+    \label{table:subset_probend_result}
+\end{table}
+
 In tournaments with both noise and an unspecified number of turns several of
@@
 tournaments. This demonstrates that, $e$, $\pi$,
-$\phi$ and the Retaliate family are robust in noisy environments regardless of the
+$\phi$ ($\pi$, $\phi$ are based on the same approach as $e$) and the Retaliate
+family are robust in noisy environments regardless of the
 number of turns. However, strategies from the top ranks in probabilistic
-ending tournaments did not rank highly here.
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.55\textwidth]{../images/performance_probend_noise.pdf}
+ending tournaments did not rank highly here. The distributions of
+\(r\) shown in Figure~\ref{fig:noisy_probend_results} have the largest
+median values compared to the top rank strategies of the other tournament
+types.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.7\textwidth]{../images/performance_probend_noise.pdf}
     \caption{\(r\) distributions for best performed strategies in noisy
@@
 
-Up till now, the performances of the 194 strategies have been evaluated for
+The distributions of \(r\) for the tournament types indicate that
+for probabilistic ending and standard tournaments successful strategies do exist.
+For these settings, the top 15 strategies have frequently ranked in
+the top spots with only a few exceptions. Contrarily, it appears that noise
+cause variation in the normalised ranks, and the strategies can always guarantee
+a spot in the top ranks.
+
+Up till now, the performances of the \numberofstrategies strategies have been evaluated for
 individual tournament types. The data set considered in this work, described in
@@
 
-The top ranks include strategies that have been previously mentioned. The top ranks
-are overtaken by the set of Retaliate strategies followed by BackStabber and
-DoubleCrosser. DoubleCrosser performed well in standard tournaments and the
-strategy is just an extension of BackStabber. PSO Gambler and Evolved HMM 5 are
+The top ranks include strategies that have been previously mentioned. The
+set of Retaliate strategies occupy the top spots followed by BackStabber
+and DoubleCrosser. Figure~\ref{fig:overall_results} gives the normalised rank distributions of
+these strategies. The distributions of the Retaliate strategies have no
+statistical difference. Thus, in an IPD tournament where the type is not
+specified, playing as any of the Retaliate strategies will have the result.
+DoubleCrosser performed well in standard tournaments and the
+strategy is just an extension of BackStabber. It should be noted that these
+strategies can be characterised as "cheaters". The source code of the strategies
+allows them to known the number of turns in a match (if they are specified).
+PSO Gambler and Evolved HMM 5 are
 trained strategies introduced in~\cite{Harper2017} and Nice Meta Winner and NMWE
@@
 original tournament and Forgetful Fool Me Once is based on the same approach as
-Grudger.
-
-Figure~\ref{fig:overall_results} gives the normalised rank distributions of
-these strategies. The distributions of the Retaliate strategies have no
-statistical difference. Thus, in an IPD tournament where the type is not
-specified, playing as any of the Retaliate strategies will have the result.
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.55\textwidth]{../images/performance_merged.pdf}
+Grudger. All the top 15 strategies are fundamentally different. Some are cheaters,
+some are complex, others are simple deterministic strategies and strategies based
+on teams. The results of \numberofalltournaments tournaments used in this work imply the following:
+they is not a single type of strategy which can performance well in any IPD interaction.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.7\textwidth]{../images/performance_merged.pdf}
     \caption{\(r\) distributions for best performed strategies in the data set~\cite{data}.}
@@
 probabilistic ending tournaments most of the winning strategies were defecting
-strategies. A few trained finite state automata, designed by the same authors,
-also performed well in this setting. Finally the performance of all 194
+strategies and trained finite state automata, designed by the same authors.
+Finally the performance of all \numberofstrategies
 strategies over the \numberofalltournaments tournaments in this manuscript was
@@
 tournaments and tournaments with probabilistic ending, managed to rank in the
-top 10\% of the tournament most of the times. Strategies successful in noisy
-environments demonstrated that they were not affected by the number of turns.
-However, there has been not a single strategy that has shown to perform well in
+top 10\% of the tournament most of the times. Strategies in noisy
+environments demonstrated that no strategy can be consistently
+successful. Overall, there has been not a single strategy that has shown to perform well in
 more than one setting. The aim of the next section is to understand which are
-the factors that made these strategies successful. In each setting separately
+the factors that made these strategies successful, in each setting separately
 but also overall.
@@
 strategy's successful performance. The factors explored are measures regarding a
-strategy's behaviour, alogn with measures regarding the tournaments the
+strategy's behaviour, along with measures regarding the tournaments the
 strategies competed in. These are given in Table~\ref{table:manual_measures}.
@@
     \midrule
-stochastic  &  If a strategy is stochastic & strategy classifier from~\cite{axelrodproject} & boolean  & False &  True \\
-makes use of game &  If a strategy makes used of the game information & strategy classifier from~\cite{axelrodproject} & boolean  & False &  True \\
-makes use of length &  If a strategy makes used of the number of turns & strategy classifier from~\cite{axelrodproject} & boolean  & False &  True \\
+stochastic  &  If a strategy is stochastic & strategy classifier from~\cite{axelrodproject} & boolean  & Na &  Na \\
+makes use of game &  If a strategy makes used of the game information & strategy classifier from~\cite{axelrodproject} & boolean  & Na &  Na \\
+makes use of length &  If a strategy makes used of the number of turns & strategy classifier from~\cite{axelrodproject} & boolean  & Na &  Na \\
 memory usage &  The memory size of a strategy divided by the number of turns & memory size from~\cite{axelrodproject} & float & 0 &  1 \\
 SSE & A measure of how far a strategy is from ZD behaviour & method described in~\cite{Knight2019} & float & 0 & 1 \\
-max cooperating rate $(C_{\text{max}})$  & The biggest cooperating rate in the tournament  & result summary  & float & 0 & 1\\
-min cooperating rate $(C_{\text{min}})$ & The smallest cooperating rate in the tournament  & result summary  & float & 0 & 1\\
-median cooperating rate $(C_{\text{median}})$ & The median cooperating rate in the tournament  & result summary  & float & 0 & 1\\
-mean cooperating rate $(C_{\text{mean}})$ & The mean cooperating rate in the tournament  & result summary  & float & 0 & 1 \\
+max cooperating rate $(C_{\text{max}})$  & The biggest cooperating rate in a given tournament  & result summary  & float & 0 & 1\\
+min cooperating rate $(C_{\text{min}})$ & The smallest cooperating rate in a given tournament  & result summary  & float & 0 & 1\\
+median cooperating rate $(C_{\text{median}})$ & The median cooperating rate in a given tournament  & result summary  & float & 0 & 1\\
+mean cooperating rate $(C_{\text{mean}})$ & The mean cooperating rate in a given tournament  & result summary  & float & 0 & 1 \\
 $C_r$ / $C_{\text{max}}$ & A strategy's cooperating rate divided by the maximum & result summary  & float & 0 & 1 \\
@@
 memory size of strategy (which is specified in the strategies implementation
-in~\cite{axelrodproject}) divide by the number of turns. For tournaments with a
-probabilistic ending the number of turns has been not collected, so the memory
-usage measure is not used for probabilistic ending tournaments.
-The SSE is a measure of extortionate behaviour introduced in~\cite{Knight2019}.
-A value of 1 indicates no extortionate behaviour at all whereas a value of 0
-indicates that a strategy is always trying to extortion it's opponent. The rest
-of the factors considered are the $CC$ to $C$, $CD$ to $C$, $DC$ to $C$, and
-$DD$ to $C$ rates as well as cooperating ratio of a strategy. The minimum,
-maximum, medium and median cooperating ratios of each tournament are also
-included, and finally the number of turns, the number of strategies and the
-probabilities of noise and the game ending are also included.
+in~\cite{axelrodproject}) divide by the number of turns. For example, Evolved
+FSM 16 Noise 05 has a memory size of 16 and participated in a tournament where
+$n$ was 134. In the given tournament Evolved FSM 16 Noise 05 has a memory usage
+of 0.119. For tournaments with a probabilistic ending the number of turns was
+not collected, so the memory usage measure is not used for probabilistic ending
+tournaments. The SSE is a measure introduced in~\cite{Knight2019} which shows
+how close a strategy is to behaving as a ZDs, and subsequently, in an
+extortionate way. The method identifies the ZDs closest to a given strategy and
+calculates the algebraic distance between them, defined as SSE. A SSE value of 1
+indicates no extortionate behaviour at all whereas a value of 0 indicates that a
+strategy is behaving a ZDs. The rest of the factors considered are the $CC$ to
+$C$, $CD$ to $C$, $DC$ to $C$, and $DD$ to $C$ rates as well as cooperating
+ratio of a strategy. The minimum, maximum, medium and median cooperating ratios
+of each tournament are also included, and finally the number of turns, the
+number of strategies, the number of repetitions and the probabilities of noise
+and the game ending are also included.
 
@@
     \centering
-    \includegraphics[width=.5\textwidth]{../images/rates_of_winners_in_standard_tournaments.pdf}
+    \includegraphics[width=.65\textwidth]{../images/rates_of_winners_in_standard_tournaments.pdf}
     \caption{Distributions of $CC$ to $C$ and $DD$ to $C$ for the winners in
@@
 stronger effect. Thus a strategy will be punished more by it's cooperative
-behaviour in probabilistic ending environments. The distributions of the $C_r$ of the winners in
+behaviour in probabilistic ending environments, this was seen in Section~\ref{section:evaluation_of_performance}
+as well. The distributions of the $C_r$ of the winners in
 both tournaments is given by Figure~\ref{fig:c_r_distributions}. It confirms
@@
 and in probabilistic ending tournaments less than 10\%.
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.5\textwidth]{../images/c_r_winners_tournaments.pdf}
-    \caption{$C_r$ distributions of the winners in noisy and in probabilistic
-    ending tournaments.}\label{fig:c_r_distributions}
-\end{figure}
-
 In noisy probabilistic ending tournaments and in over all the tournaments' results,
@@
 
-The effect of the measures on performances is further tested using a random forest
-classification~\cite{breiman2001} approach. Initially, the performances are
-clustered based on their normalised rank and the median score by a \(k-\)means
-algorithm~\cite{Arthur2007}. The number of clusters is not deterministically
-chosen but it is based on the silhouette coefficients~\cite{Rousseeuw1987}.
-Consider the case of standard tournaments, the chosen number of clusters is
-2 and Figure~\ref{fig:standard_clusters} illustrates the trials of clustering the
-performances in 2, 3 and 4 clusters respectively. The number of chosen clusters
-for each type and overall are given in Table~\ref{table:number_of_clusters}.
-
-\begin{figure}[!htbp]
-\centering
-\includegraphics[width=.55\textwidth]{../output/standard/clusters_plots.png}
-\caption{Clustering trials for standard tournaments. A number of 2 clusters has
-been chosen with a silhouette score of  0.66 against 0.511 and 0.50
-respectively.}\label{fig:standard_clusters}
-\end{figure}
-
-\begin{table}[!htbp]
-    \begin{center}
-        \resizebox{.5\textwidth}{!}{
-        \begin{tabular}{lcccc}
-    \toprule
-    Tournament type & Number of clusters &  Silhouette coefficient\\
-    \midrule
-    standard                   & 2 & 0.648 \\
-    noisy                      & 3 & 0.493 \\
-    probabilistic ending       & 2 & 0.680 \\
-    noisy probabilistic ending & 4 & 0.415\\
-    over \numberofalltournaments tournaments         & 3 & 0.443\\
-    \bottomrule
-        \end{tabular}}
-    \end{center}
-    \caption{Number of clusters for each type and over all the tournament results
-    and the respective silhouette coefficients.}
-    \label{table:number_of_clusters}
-\end{table}
-
-A random forest approach is applied to the data to predict the cluster to which
-a strategy's performance has been assigned to. The random forest method
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.65\textwidth]{../images/c_r_winners_tournaments.pdf}
+    \caption{$C_r$ distributions of the winners in noisy and in probabilistic
+    ending tournaments.}\label{fig:c_r_distributions}
+\end{figure}
+
+The performances are clustered in two clusters based on the nornalised rank.
+More specifically, there are clustered based on whether the normalised rank was
+in the top 5\%, the 25\% and the 50\%. A random forest
+approach~\cite{breiman2001} is applied to the data to predict the cluster to
+which a strategy's performance has been assigned to. The random forest method
 constructs many individual decision trees and the predictions from all trees are
@@
 based on $R^2$ are given by Table~\ref{table:accuracy_random_forest}. The out of
-the bag error~\cite{hastie2005} has also been calculated. The models fit well, and
-a high value of both the accuracy measure on the test data and the
-OOB error indicate that the model is not over fitting.
+the bag error~\cite{hastie2005} has also been calculated. The models fit well,
+and a high value of both the accuracy measure on the test data and the OOB error
+indicate that the model is not over fitting.
+
+The performances have also been clustered   based on their normalised rank and
+their median score by a \(k-\)means algorithm~\cite{Arthur2007}. The number of
+clusters is not deterministically chosen but it is based on the silhouette
+coefficients~\cite{Rousseeuw1987}. The chosen cluster for each tournament type,
+as well as the accuracy for random forest models, are given in
+Table~\ref{table:accuracy_random_forest}.
 
@@
     \begin{center}
-        \resizebox{.5\textwidth}{!}{
-        \begin{tabular}{lcccc}
+        \resizebox{.9\textwidth}{!}{
+        \begin{tabular}{lccccc}
     \toprule
-    Tournament type & $R^2$ training data &  $R^2$ test data  & $R^2$ OOB score\\
+    Tournament type & Clustering on & Number of clusters & $R^2$ training data &  $R^2$ test data  & $R^2$ OOB score\\
     \midrule
-    standard                   & 0.998545  & 0.989890 & 0.982331\\
-    noisy                      & 0.996677  & 0.950572 & 0.935383\\
-    probabilistic ending       & 0.999592  & 0.995128 & 0.992819 \\
-    noisy probabilistic ending & 0.990490  & 0.813905 & 0.791418\\
-    over \numberofalltournaments tournaments & 0.993396 & 0.913409 & 0.898059 \\
+    standard  & top 5\% $r$              & 2  & 0.998831  & 0.987041 & 0.983708 \\
+              & top 25\% $r$             & 2  & 0.998643  & 0.978626 & 0.969202 \\
+              & top 50\% $r$             & 2  & 0.998417  & 0.985217 & 0.976538 \\
+              & $r$  \& normalised score & 2  & 0.998794  & 0.990677 & 0.982959 \\
+    \midrule
+    noisy     & top 5\% $r$              & 2 & 0.996677  & 0.950572 & 0.935383\\
+              & top 25\% $r$             & 2 & 0.996677  & 0.950572 & 0.935383\\
+              & top 50\% $r$             & 2 & 0.996677  & 0.950572 & 0.935383\\
+              & $r$  \& normalised score & 3 & 0.996677  & 0.950572 & 0.935383\\
+    \midrule
+    probabilistic ending & top 5\% $r$              & 2 & 0.999592  & 0.995128 & 0.992819 \\
+                         & top 25\% $r$             & 2 & 0.999592  & 0.995128 & 0.992819 \\
+                         & top 50\% $r$             & 2 & 0.999592  & 0.995128 & 0.992819 \\
+                         & $r$  \& normalised score & 2 & 0.999592  & 0.995128 & 0.992819 \\
+    \midrule
+    noisy probabilistic ending & top 5\% $r$              & 2 & 0.990490  & 0.813905 & 0.791418\\
+                               & top 25\% $r$             & 2 & 0.990490  & 0.813905 & 0.791418\\
+                               & top 50\% $r$             & 2 & 0.990490  & 0.813905 & 0.791418\\
+                               & $r$  \& normalised score & 4 & 0.990490  & 0.813905 & 0.791418\\
+    \midrule
+    over \numberofalltournaments tournaments & top 5\% $r$               & 2 & 0.993396 & 0.913409 & 0.898059 \\
+                                             & top 25\% $r$              & 2 & 0.993396 & 0.913409 & 0.898059 \\
+                                             & top 50\% $r$              & 2 & 0.993396 & 0.913409 & 0.898059 \\
+                                             & $r$  \& normalised score  & 3 & 0.993396 & 0.913409 & 0.898059 \\
     \bottomrule
@@
 The importance that the measures of Table~\ref{table:manual_measures} had on the
-classification task; to which cluster a performance was assigned to, have been
-calculated and are given by Figure~\ref{fig:importance}. The classifiers which
-where not included in the previous analysis appear to have no effect, and
-several of the measures that are highted by the importance are inline with the
+classification tasks; to which cluster a performance was assigned to, have been
+calculated and are given by Figures~\ref{fig:clustering_importance_standard},
+\ref{fig:clustering_importance_noise},~\ref{fig:clustering_importance_probend},
+\ref{fig:clustering_importance_probend_noise}
+and~\ref{fig:clustering_importance_overall}. These show that the classifiers
+stochastic, make use of game and make use of length have no significant effect,
+and several of the measures that are highted by the importance are inline with the
 correlation results. The most important measures based on the random forest
@@
 \begin{figure}[!htbp]
-    \begin{minipage}{0.5\textwidth}
+    \begin{subfigure}[t]{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../new_output/standard/_feature_importance_bar_plot_cluster_on_0_05.pdf}
+        \end{center}
+        \caption{Importance of features for clusters on 5\% performance.}
+    \end{subfigure}\hfill
+    \begin{subfigure}[t]{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../new_output/standard/_feature_importance_bar_plot_cluster_on_0_25.pdf}
+        \end{center}
+        \caption{Importance of features for clusters on 25\% performance.}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../new_output/standard/_feature_importance_bar_plot_cluster_on_0_5.pdf}
+        \end{center}
+        \caption{Importance of features for clusters on 50\% performance.}
+    \end{subfigure}\hfill
+    \begin{subfigure}[t]{0.5\textwidth}
         \begin{center}
@@
         \end{center}
-        \caption{Standard tournaments}
-    \end{minipage}\hspace{1cm}
-    \begin{minipage}{0.5\textwidth}
+        \caption{Importance of features for clusters based on \(k\)means algorithm.}
+    \end{subfigure}
+    \caption{Importance of features in standard tournaments for different
+    clustering methods.}\label{fig:clustering_importance_standard}
+\end{figure}
+
+\begin{figure}[!htbp]
+    \begin{subfigure}{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../new_output/noise/_feature_importance_bar_plot_cluster_on_0_05.pdf}
+        \end{center}
+        \caption{Importance of features for clusters on 5\% performance.}
+    \end{subfigure}\hfill
+    \begin{subfigure}{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../new_output/noise/_feature_importance_bar_plot_cluster_on_0_25.pdf}
+        \end{center}
+        \caption{Importance of features for clusters on 25\% performance.}
+    \end{subfigure}
+    \begin{subfigure}{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../new_output/noise/_feature_importance_bar_plot_cluster_on_0_5.pdf}
+        \end{center}
+        \caption{Importance of features for clusters on 50\% performance.}
+    \end{subfigure}\hfill
+    \begin{subfigure}{0.5\textwidth}
         \begin{center}
@@
         \end{center}
-        \caption{Noisy tournaments}
-    \end{minipage}\hspace{1cm}
-    \begin{minipage}{0.5\textwidth}
+        \caption{Importance of features for clusters based on \(k\)means algorithm.}
+    \end{subfigure}
+    \caption{Importance of features in noisy tournaments for different
+    clustering methods.}\label{fig:clustering_importance_noise}
+\end{figure}
+
+\begin{figure}[!htbp]
+    \begin{subfigure}[t]{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../new_output/probend/_feature_importance_bar_plot_cluster_on_0_05.pdf}
+        \end{center}
+        \caption{Importance of features for clusters on 5\% performance.}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../new_output/probend/_feature_importance_bar_plot_cluster_on_0_25.pdf}
+        \end{center}
+        \caption{Importance of features for clusters on 25\% performance.}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../new_output/probend/_feature_importance_bar_plot_cluster_on_0_5.pdf}
+        \end{center}
+        \caption{Importance of features for clusters on 50\% performance.}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.5\textwidth}
         \begin{center}
@@
         \end{center}
-        \caption{Probabilistic ending tournaments}
-    \end{minipage}\hspace{1cm}
-    \begin{minipage}{0.5\textwidth}
+        \caption{Importance of features for clusters based on \(k\)means algorithm.}
+    \end{subfigure}
+    \caption{Importance of features in probabilistic ending tournaments for different
+    clustering methods.}\label{fig:clustering_importance_probend}
+\end{figure}
+
+\begin{figure}[!htbp]
+    \begin{subfigure}[t]{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../new_output/probend_noise/_feature_importance_bar_plot_cluster_on_0_05.pdf}
+        \end{center}
+        \caption{Importance of features for clusters on 5\% performance.}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../new_output/probend_noise/_feature_importance_bar_plot_cluster_on_0_25.pdf}
+        \end{center}
+        \caption{Importance of features for clusters on 25\% performance.}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../new_output/probend_noise/_feature_importance_bar_plot_cluster_on_0_5.pdf}
+        \end{center}
+        \caption{Importance of features for clusters on 50\% performance.}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.5\textwidth}
         \begin{center}
@@
         \end{center}
-        \caption{Noisy probabilistic ending tournaments}
-    \end{minipage}
-    \begin{minipage}{0.5\textwidth}
-    \end{minipage}\hspace{4.5cm}
-    \begin{minipage}{0.5\textwidth}
+        \caption{Importance of features for clusters based on \(k\)means algorithm.}
+    \end{subfigure}
+    \caption{Importance of features in noisy probabilistic ending tournaments for different
+    clustering methods.}\label{fig:clustering_importance_probend_noise}
+\end{figure}
+
+\begin{figure}[!htbp]
+    \begin{subfigure}[t]{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../new_output/merged/_feature_importance_bar_plot_cluster_on_0_05.pdf}
+        \end{center}
+        \caption{Importance of features for clusters on 5\% performance.}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../new_output/merged/_feature_importance_bar_plot_cluster_on_0_25.pdf}
+        \end{center}
+        \caption{Importance of features for clusters on 25\% performance.}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.5\textwidth}
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../new_output/merged/_feature_importance_bar_plot_cluster_on_0_5.pdf}
+        \end{center}
+        \caption{Importance of features for clusters on 50\% performance.}
+    \end{subfigure}
+    \begin{subfigure}[t]{0.5\textwidth}
         \begin{center}
@@
         \end{center}
-        \caption{overall ending tournaments}
-    \end{minipage}
-    \caption{Importance of features in IPD tournaments.}\label{fig:importance}
-\end{figure}
-
-The effect of both these measures can be further explored. Their distributions
-for the winners of the tournaments are given by
-Figures~\ref{fig:mean_median_std},~\ref{fig:mean_median_noisy},
-\ref{fig:mean_median_probend}, \ref{fig:mean_median_probend_noisy} and
-\ref{fig:mean_median_overall}. The results suggest that if a strategy with
-a theory of mind competed in a standard tournament, then the strategy would
-want to be the mean/median cooperator of that tournament. In comparison, if the
-same strategy competed in a tournament with noisy or the strategy had no
-information regarding the setting of the tournament, then it would
-want to cooperate 67\% of the times the mean or median cooperator did.
-In probabilistic ending tournament it has already been mentioned that defecting
-strategies prevail. This result is once again confirmed in this section.
+        \caption{Importance of features for clusters based on \(k\)means algorithm.}
+    \end{subfigure}
+    \caption{Importance of features over all the tournaments for different
+    clustering methods.}\label{fig:clustering_importance_overall}
+\end{figure}
+
+The effect of both these measures can be further explored. In
+Figure~\ref{fig:mean_median_std} the distributions of \(C_ / C_{\text{mean}}\)
+and \(C_ / C_{\text{median}}\) are given for the winners. A value of \(C_ /
+C_{\text{mean}} = 1\) imply that the cooperating ratio of the winner was the
+same as the mean / median cooperating ratio. In standard tournaments, the mean
+for both ratios is 1. Therefore, an effective strategy in standard tournaments
+was the mean / median cooperator of its respective tournament. In comparison,
+Figure \ref{fig:mean_median_noisy} shows the distributions of the measure for
+the winners in noisy tournaments. The mean is at 0.67, thereupon the winners
+cooperated 67\% of the times the mean / median cooperator did. This analysis is
+applied to the rest of the tournaments and the distributions are given by
+Figures \ref{fig:mean_median_probend}, \ref{fig:mean_median_probend_noisy} and
+\ref{fig:mean_median_overall}. In a tournament with noisy and a probabilistic
+ending the winners cooperated 60\%, whereas in settings that the type of the
+tournament can vary between the types considered in this work the winners
+cooperated 67\% of the times the mean or median cooperator did. Finally, in
+probabilistic ending tournament it has already been mentioned that defecting
+strategies prevail and this result is once again confirmed in this section.
 
@@
 
+Further data mining could be applied to the data set of this work, available
+at~\cite{data}.
+
 \bibliographystyle{plain}
@@
 SSE                         & A measure of how far a strategy is from extortionate behaviour \\
-$(C_{\text{max}})$          & The biggest cooperating rate in the tournament \\
-$(C_{\text{min}})$          & The smallest cooperating rate in the tournament \\
-$(C_{\text{median}})$       & The median cooperating rate in the tournament \\
-$(C_{\text{mean}})$         & The mean cooperating rate in the tournament \\
+$C_{\text{max}}$          & The biggest cooperating rate in the tournament \\
+$C_{\text{min}}$          & The smallest cooperating rate in the tournament \\
+$C_{\text{median}}$       & The median cooperating rate in the tournament \\
+$C_{\text{mean}}$         & The mean cooperating rate in the tournament \\
 $C_r$ / $C_{\text{max}}$    & A strategy's cooperating rate divided by the maximum \\
@@
 $DD$ to $C$ rate            & The probability a strategy will cooperate after a mutual defection\\
-$p$                         & The probability of a player's action being flip at each interaction \\
+$p_n$                       & The probability of a player's action being flip at each interaction \\
 $n$                         & The number of turns \\
-$e$                         & The probability of a match ending in the next turn \\
+$p_e$                       & The probability of a match ending in the next turn \\
 $N$                         & The number of strategies in the tournament \\
+$k$                         & The number that a given tournament is repeated \\
     \bottomrule
@@
 \end{figure}
+\begin{figure}[!htbp]
+    \begin{center}
+        \includegraphics[width=.75\linewidth]{../images/merged_correlation_plot.pdf}
+    \end{center}
+    \caption{Correlation coefficients of measures in Table~\ref{table:manual_measures}
+    for data set}
+\end{figure}
 

### 2019-11-14 paper/main.tex
finalising draft

@@
 most important feature. The conclusions are distinct for different types of
-tournaments. A strategy with a theory of mind would aim to be the mean/median
+tournaments. For instance a strategy with a theory of mind would aim to be the mean/median
 cooperator in standard tournaments, whereas in tournaments with probabilistic
 ending it would aim to cooperate 10\% of the times the median cooperator did.
-In tournaments with noise and a probability of ending an effective strategy
-cooperates 60\% of the times the median/mean cooperator did, and in tourmanents
-with only noise or even in a setting that the tournament can be any of the
-above a strategy should aim to play 67\% as a median/mean cooperator.
 \end{abstract}
@@
 behaviour have been tested. In~\cite{Harper2017} a tournament containing over
-200 strategies, including ZDs, was ran and none of the them
+200 strategies, including ZDs, was ran and none of them
 ranked in top spots. Instead, the top ranked strategies were a set of
@@
     of the strategy has been in standard tournaments where it achieved a $\bar{r}$
-    of 0.339.}
+    of 0.34.}
     \label{fig:tit_for_tat_r_distribution}
@@
 They have been trained to perform well against the strategies
-in~\cite{axelrodproject} in a standard setting, thus their performance in the
+in~\cite{axelrodproject} in a standard tournament, thus their performance in the
 specific setting was anticipated. DoubleCrosser, and Fool Me Once, are
@@
 The top strategies in noisy tournaments are shown in Figure~\ref{fig:noisy_results}. These include deterministic strategies, such
-as Tit For 2 Tats~\cite{Axelrod1980b}, Slow Tit For Tats~\cite{axelrodproject}, Hard Tit For 2 Tats~\cite{Stewart2012}
+as Tit For 2 Tats~\cite{Axelrod1980b}, Slow Tit For Two Tats~\cite{axelrodproject}, Hard Tit For 2 Tats~\cite{Stewart2012}
 and Cycler CCCCCD, and strategies which decide their actions based on the
 cooperations to defections ratio, such as ShortMem~\cite{Carvalho2013}, Grumpy
-and $e$~\cite{axelrodproject}. The Retaliate and
+and $e$~\cite{axelrodproject}. Slow Tit For Two Tats is the same strategy as 
+Tit For 2 Tats, and at the time of writing this manuscript the
+contributors of~\cite{axelrodproject} made a new release where the strategy
+has been removed. However, for the purpose of this work the strategy is kept.
+The Retaliate and
 Limited Retaliate strategies are implemented in~\cite{axelrodproject} by the
@@
 tournaments that they ranked in the bottom half. To gain a better understanding
-of behaviour in noisy tournaments, the \(r\) distribution over the noise
-probability \(p_n\) for the top 6 strategies of Figure~\ref{fig:noisy_results},
+of the behaviour in noisy tournaments, the \(r\) distributions for the top 6
+of Figure~\ref{fig:noisy_results} strategies over the noise probability \(p_n\),
 are given in Figure~\ref{fig:effect_of_noise}.
-
-For \(p_n\) strictly lower than 0.5, Grumpy, Tit For 2 Tats and Slow Tit For Two Tat
-have a moderate performing, whereas \(e\), Cycle Hunter and Ricky QLearner are
-behaving poorly. At \(p_n=0.5\), all the distributions are bimodal because
-with a 0.5 probability of noise any strategies corresponds to a random player.
-Interestedly, for a \(p_n\) larger than 0.5 all of the 6 strategies become
-successful. Note that a value \(p_n=1\) corresponds to a strategy playing the
-exact opposite from what they intended. Thus, the successful strategies in
-noisy tournaments presented here, are effective when they are not playing as
-themselves. If \(p_n\) was strictly less 0.5 then the top ranked strategies
-are different, Table~\ref{table:subset_noise_result}. The top spots are mainly
-overtaken by the Meta strategies which are based on teams.
 
@@
 \end{figure}
+
+Figure~\ref{fig:effect_of_noise} shows that for \(p_n\) values lower than 0.5
+Grumpy, Tit For 2 Tats and Slow Tit For Two Tat perform moderately, and \(e\),
+Cycle Hunter and Ricky QLearner perform poorly. At \(p_n=0.5\) all the
+distributions become bimodal. This is because with a noise probability of 0.5,
+all strategies correspond to a random player. Interestedly, for a \(p_n\) larger
+than 0.5 all of the 6 strategies become successful. Note that a value \(p_n=1\)
+corresponds to a strategy playing opposite from what it intended to. Thus, it is
+demonstrated that the successful strategies is noisy tournaments are sometimes
+effective when \(p_n=0.5\) but overall they are very successful whn they are
+playing opposite from their original design. If during the data collection a
+\(p_n\) strictly less 0.5 was considered then the top ranked strategies would be
+different. There are a total of 5661 trials where \(p_n<0.5\) and the top ranked
+strategies are given in Table~\ref{table:subset_noise_result}. The median ranks
+are lower than before and the top spots are mainly overtaken by Meta strategies
+which include NMWE deterministic and NMWE Long Memory. The Meta
+strategies~\cite{axelrodproject} create a team of strategies for themselves and
+choose to play as a member of their team based on their scores against a given
+opponent.
 
@@
     \input{performance_noise_subset_table.tex}}
-    \caption{Top performances in noisy tournaments where \(p_n<0.5\).}\label{table:subset_noise_result}
+    \caption{Top performances in 5661 noisy tournaments where \(p_n<0.5\).}\label{table:subset_noise_result}
 \end{table}
@@
 until the end, ranked $14^{\text{th}}$ and $15^{\text{th}}$. Upon inspection,
-it was concluded that they are actually the same strategy. This was not known to
+it was found that they are actually the same strategy. This was not known to
 the authors at the time of data collection. Figure~\ref{fig:probend_results}
-verifies that their perfomance is the same. Both strategies have repeatedly
+verifies that their performance is the same. Both strategies have repeatedly
 ranked highly and there are cases for which they were the winners of the
 tournament.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=.7\textwidth]{../images/performance_probend.pdf}
-    \caption{\(r\) distributions for best performed strategies in probabilistic ending tournaments.}
-    \label{fig:probend_results}
-\end{figure}
 
@@
 
-The distributions of \(r\) over \(p_e\) for the top 6 strategies are also given
-by Figure~\ref{fig:effect_of_probend}. It is shown that the rank of the
-strategies is decreasing as the probability of the game ending increases and at
-the point of \(p_e=0.1\) the strategies become dominant. All the top ranked
-strategies in this setting are defecting strategies, and what is exhibited is
-that they do better as the probability of the game ending in the next turn
-increases, which is inline with the Folk Theorem~\cite{Fudenberg2009}. Consider
-tournaments where the probability of the game ending was less than 0.1, the top
-ranked strategies based on \(\bar{r}\) are given
-by~Table~\ref{table:subset_probend_result}. The top ranked strategies include
-strategies based on teams, trained strategies, Grudger and Spiteful Tit for Tat.
+\begin{figure}[h!]
+    \centering
+    \includegraphics[width=.7\textwidth]{../images/performance_probend.pdf}
+    \caption{\(r\) distributions for best performed strategies in probabilistic ending tournaments.}
+    \label{fig:probend_results}
+\end{figure}
+
+The distributions of \(r\) for the top 6 strategies in probabilistic ending
+tournaments over \(p_e\) are given in Figure~\ref{fig:effect_of_probend}.
+Figure~\ref{fig:effect_of_probend} shows that the 6 strategies start of with a
+high median rank, however, their ranked decreased as the the probability of the
+game ending increased and at the point of \(p_e=0.1\) they became the dominant
+strategies in their respective tournaments. In essence, what is demonstrated is
+that defecting strategies did better when the likelihood of the game ending in
+the next turn increased, which is inline with the Folk
+Theorem~\cite{Fudenberg2009}. If tournaments where the probability of the game
+ending was less than 0.1 were considered then the the top ranked spots are not
+dominated by just defecting strategies anymore,
+Table~\ref{table:subset_probend_result}. Instead the effective strategies are
+now the Meta strategies, trained strategies, Grudger~\cite{axelrodproject} and
+Spiteful Tit for Tat~\cite{prison}.
 
@@
     \input{performance_probend_subset_table.tex}}
-    \caption{Top performances in probabilistic ending tournaments with \(p_e < 0.1\)}
+    \caption{Top performances in 1139 probabilistic ending tournaments with \(p_e < 0.1\)}
     \label{table:subset_probend_result}
@@
 
-In tournaments with both noise and an unspecified number of turns several of
-the top ranked strategies are strategies that were highly ranked in noisy
-tournaments. This demonstrates that, $e$, $\pi$,
-$\phi$ ($\pi$, $\phi$ are based on the same approach as $e$) and the Retaliate
-family are robust in noisy environments regardless of the
-number of turns. However, strategies from the top ranks in probabilistic
-ending tournaments did not rank highly here. The distributions of
-\(r\) shown in Figure~\ref{fig:noisy_probend_results} have the largest
-median values compared to the top rank strategies of the other tournament
-types.
+In tournaments with both noise and an unspecified number of turns several of the
+top ranked strategies are strategies that were highly ranked in noisy
+tournaments. However, strategies from the top ranks in probabilistic ending
+tournaments did not rank highly here. Other strategies include $\pi$, $\phi$
+which are based on the same approach as $e$. The distributions of \(r\) shown in
+Figure~\ref{fig:noisy_probend_results} have the largest median values compared
+to the top rank strategies of the other tournament types. A subset of noisy
+probabilistic ending tournaments has been considered such that \(p_e < 0.1\) and
+\(p_n < 0.5\). The top ranked strategies are given in
+Table~\ref{table:subset_probend_noise_result} and it is shown that the Meta
+strategies which performed well in noisy tournaments with \(p_n < 0.5\), perform
+well once again even the number of turns is not specified. Moreover, several
+strategies that did well in probabilistic ending tournaments such as Fortress 3,
+Fortress 4, Defector and Better and Better are effective here as well.
 
@@
 
-The distributions of \(r\) for the tournament types indicate that
+\begin{table}[!htbp]
+    \centering
+    \resizebox{.30\textwidth}{!}{
+    \input{performance_probend_noise_subset_table.tex}}
+    \caption{Top performances in 568 probabilistic ending tournaments with \(p_e < 0.1\) and \(p_n < 0.5\).}
+    \label{table:subset_probend_noise_result}
+\end{table}
+
+Up till now, the performances of the \numberofstrategies strategies have been evaluated for
+individual tournament types. The distributions of \(r\) for the tournament types indicate that
 for probabilistic ending and standard tournaments successful strategies do exist.
@@
 
-Up till now, the performances of the \numberofstrategies strategies have been evaluated for
-individual tournament types. The data set considered in this work, described in
+The data set considered in this work, described in
 Section~\ref{section:data_collection}, contains a total of \numberofalltournaments
@@
 set of Retaliate strategies occupy the top spots followed by BackStabber
-and DoubleCrosser. Figure~\ref{fig:overall_results} gives the normalised rank distributions of
-these strategies. The distributions of the Retaliate strategies have no
+and DoubleCrosser. The distributions of the Retaliate strategies have no
 statistical difference. Thus, in an IPD tournament where the type is not
@@
 original tournament and Forgetful Fool Me Once is based on the same approach as
-Grudger. All the top 15 strategies are fundamentally different. Some are cheaters,
+Grudger. Overall the top 15 strategies are fundamentally different. Some are cheaters,
 some are complex, others are simple deterministic strategies and strategies based
@@
 deterministic strategies designed to defect if the opponent tricked them more
-than a current amount of the times that they had tricked their opponent. In
+than a current amount of the times that they had tricked their opponent. However,
+if a value of noise strictly less than 0.5 was considered, then the successful
+strategies were strategies based on teams. In
 probabilistic ending tournaments most of the winning strategies were defecting
 strategies and trained finite state automata, designed by the same authors.
+These strategies only did better when the probability of the game ending after
+each turn was increased.
 Finally the performance of all \numberofstrategies
@@
 tournaments and tournaments with probabilistic ending, managed to rank in the
-top 10\% of the tournament most of the times. Strategies in noisy
+top 10\% of the tournament most of the times.
+Strategies in noisy
 environments demonstrated that no strategy can be consistently
-successful. Overall, there has been not a single strategy that has shown to perform well in
+successful, expected if the value of noise is constrained to less than a half.
+Overall, there has been not a single strategy that has shown to perform well in
 more than one setting. The aim of the next section is to understand which are
@@
 
-The performances are clustered in two clusters based on the nornalised rank.
-More specifically, there are clustered based on whether the normalised rank was
-in the top 5\%, the 25\% and the 50\%. A random forest
-approach~\cite{breiman2001} is applied to the data to predict the cluster to
-which a strategy's performance has been assigned to. The random forest method
+The performances are clustered based on the normalised rank. More specifically,
+they are clustered 3 times into 2 different clusters based on  on whether their
+normalised rank was in the top 5\%, 25\% or 50\% respectively. A random forest
+approach~\cite{breiman2001} is then applied to each performance to predict the cluster to
+which it has been assigned to. The random forest method
 constructs many individual decision trees and the predictions from all trees are
@@
 coefficients~\cite{Rousseeuw1987}. The chosen cluster for each tournament type,
-as well as the accuracy for random forest models, are given in
+as well as the accuracy for random forest models are also given in
 Table~\ref{table:accuracy_random_forest}.
@@
 
-The importance that the measures of Table~\ref{table:manual_measures} had on the
-classification tasks; to which cluster a performance was assigned to, have been
+The importance that the measures of Table~\ref{table:manual_measures} had on
+each classification task; to which cluster a performance was assigned to based
+on the normalised rank, and their normalised rank and median score have been
 calculated and are given by Figures~\ref{fig:clustering_importance_standard},
@@
 stochastic, make use of game and make use of length have no significant effect,
-and several of the measures that are highted by the importance are inline with the
-correlation results. The most important measures based on the random forest
-analysis were $C_r / C_{median}$ and $C_r / C_{mean}$.
+and several of the measures that are highted by the importance are inline with
+the correlation results. Moreover, the smoothing parameter \(k\) appears to no
+have a significant effect either. The most important measures based on the
+random forest analysis were $C_{r} / C_{median}$ and $C_r / C_{mean}$.
 
@@
 The effect of both these measures can be further explored. In
-Figure~\ref{fig:mean_median_std} the distributions of \(C_ / C_{\text{mean}}\)
-and \(C_ / C_{\text{median}}\) are given for the winners. A value of \(C_ /
+Figure~\ref{fig:mean_median_std} the distributions of \(C_r / C_{\text{mean}}\)
+and \(C_r / C_{\text{median}}\) are given for the winners in standard tournaments. A value of \(C_r /
 C_{\text{mean}} = 1\) imply that the cooperating ratio of the winner was the
-same as the mean / median cooperating ratio. In standard tournaments, the mean
+same as the mean/median cooperating ratio of the tournament. In standard tournaments, the mean
 for both ratios is 1. Therefore, an effective strategy in standard tournaments
-was the mean / median cooperator of its respective tournament. In comparison,
-Figure \ref{fig:mean_median_noisy} shows the distributions of the measure for
-the winners in noisy tournaments. The mean is at 0.67, thereupon the winners
-cooperated 67\% of the times the mean / median cooperator did. This analysis is
+was the mean/median cooperator of its respective tournament. In comparison,
+Figure~\ref{fig:mean_median_noisy} shows the distributions of the measures for
+the winners in noisy tournaments where the mean is at 0.67. Thereupon the winners
+cooperated 67\% of the times the mean/median cooperator did. This analysis is
 applied to the rest of the tournaments and the distributions are given by
@@
 In this section the effect of several measures, regarding a strategy's behaviour
-and the tournament, on it's performance were presented. This was done using
-two approaches. Correlation coefficients and a random forest
-analysis. The results of these are discussed in the following section.
+and the tournament in which it participated on its performance were presented.
+This was done using two approaches. Correlation coefficients and a random forest
+analysis. The results of these are summarised in the following section.
 
@@
 
-This manuscript has explored the performance of 194 strategies of the Iterated
+This manuscript has explored the performance of \numberofstrategies strategies of the Iterated
 Prisoner's Dilemma in a large number of computer tournaments. The results of
-the analysis demonstrated that, although for specific tournament type, such as
-standard, noisy and probabilistic ending tournaments, dominant strategies exist
-there is not a single dominant strategy if the environments
+the analysis demonstrated that, although for specific tournament types such as
+standard and probabilistic ending tournaments, dominant strategies exist
+there is not a single dominant type of strategies if the environments
 vary. Moreover, a strategy with a theory of mind should aim to adapt its behaviour
@@
 
-The 194 strategies used in this manuscript have been mainly for the literature,
-and they have been accessible due to an open source software called
-Axelrod-Python. The software was used to generate a total of
+The \numberofstrategies strategies used in this manuscript have been mainly for
+the literature, and they have been accessible due to an open source software
+called Axelrod-Python. The software was used to generate a total of
 \numberofalltournaments computer tournaments results with different number of
@@
 Section~\ref{section:top_performances}, the tournaments results were used to
-present the top performances.
-The data set contained results from four different settings, and these were also
-studied individually. In standard tournaments complex strategies trained using
-reinforcement learning ranked in the top places. In probabilistic ending
-tournaments, several trained strategies based on finite state automata also
-performed well. The rest top strategies, in this setting, were defecting
-strategies. Finally, in tournaments with noise, the Retaliate set of strategies
-demonstrated their robustness in tournaments with probabilistic ending and not.
+present the top performances. The data set contained results from four different
+settings, and these were also studied individually. In standard tournaments
+complex strategies trained using reinforcement learning ranked in the top spots.
+Some of these strategies ranked again in the top spots in probabilistic
+ending tournaments when a \(p_e\) of less 0.1 was considered. In probabilistic
+ending tournaments \(p_e\) was designed to vary between 0 and 1. It was demonstrated
+that for values larger than 0.1, as stated in the Folk Theorem, defecting strategies
+were winning the tournaments because there was a high likelihood of the game
+ending in the next turn. In tournaments with noise the median ranks of the top
+15 strategies had the highest values and the \(r\) distributions were bimodal.
+The top rank strategies were performing both well and bad, and this indicates
+that in noisy tournaments there are not strategies that can guarantee winning.
+Overall, the top ranked strategies differed from one tournament type to
+another and the mechanism behind the winning strategies were all different.
+Even strategies designed to do good in one setting did better in others.
+On the whole ... (the ipd interactions are unique and there is no winning
+strategy) %TODO help from Vince
 
@@
 More specifically, if a strategy were to enter a tournament with a theory of
-mind of it's environment it would choose to be the median cooperator in standard
-tournaments, the defector in probabilistic ending tournaments and to cooperate
-60\% of the times the median cooperator did in noisy and noisy probabilistic
-tournaments. Lastly, if a strategy was aware of the opponents but not of the
+mind of its environment it would choose to be the median cooperator in standard
+tournaments, to cooperate 10\% in probabilistic ending tournaments and 
+60\% in noisy and noisy probabilistic
+tournaments of the times the median cooperator did. Lastly, if a strategy was aware of the opponents but not of the
 setting on the tournament, a strategy would be more likely to be successful if
@@
 
-Further data mining could be applied to the data set of this work, available
-at~\cite{data}.
+The data set described in this work contains the largest number of IPD tournaments,
+to the authors knowledge, and it available at~\cite{data}. Further data mining
+could be applied and provide new insights in the field.
 

### 2019-12-24 paper/main.tex
address minor comments

@@
 however, have been relying on the performance of specific strategies in a finite
-number of tournaments, whereas this manuscript evaluates
+number of tournaments. This manuscript evaluates
 \numberofstrategies strategies' effectiveness in more than 40000 tournaments.
@@
 their success are analysed using machine learning techniques. The analysis
-determines that the cooperating ratio of a
+determines that the cooperation ratio of a
 strategy in a given tournament compared to the mean and median cooperator is the
@@
 strategies. Today more than 200 strategies exist in the literature and several
-tournaments, excluding Axelrod's, have been undertaken~\cite{Bendor1991,
+tournaments, following on from Axelrod's, have been undertaken~\cite{Bendor1991,
 Harper2017, Kendall2007, Stephens2002, Stewart2012}.
@@
 
-However, further research proved that the strategy had weakness, and more
+However, further research proved that the strategy had weaknesses, and more
 specifically, it was shown that the strategy suffered in environments with
@@
 allowed to submit multiple strategies. They submitted a total of 60 strategies
-that could recognised each other and colluded to increase one members score.
+that could recognise each other and colluded to increase one members score.
 This resulted with three of the strategies to be ranked in the top spots. The
@@
 strategies in \numberofalltournaments tournaments. These tournaments do not
-consist by just standard round robin tournaments, but also by tournaments with noise
+consist of just standard round robin tournaments, but also tournaments with noise
 and tournaments with a probabilistic ending. The later part of the paper, evaluates
@@
 The different tournament types as well as the data collection, which is made
-possible due an open source package called Axelrod-Python~\cite{axelrodproject},
+possible due to an open source package called Axelrod-Python~\cite{axelrodproject},
 are covered in Section~\ref{section:data_collection}.
@@
 parameters and their definitions are given in Appendix~\ref{app:parameters}.
+A list of all strategies including citations of their origins is given in
+Appendix~\ref{app:list_of_players}.
 
@@
 Though Axelrod-Python features several tournament types, this work considers
-only standard, noisy, probabilistic ending and noisy probabilistic ending
+standard, noisy, probabilistic ending and noisy probabilistic ending
 tournaments.
@@
 
-The result summary, Table~\ref{table:output_result}, has \(N\) number of rows
+The result summary, Table~\ref{table:output_result}, has \(N\) rows
 because each row contains information for each strategy that participated in the
@@
 Each strategy participated in multiple tournaments of the same type (on average 5154).
-For example Tit For Tat has participated in a total of 5114
+For example Tit For Tat participated in a total of 5114
 tournaments of each type. The strategy's normalised rank distribution in these
@@
 strategies not from the literature but from~\cite{axelrodproject}. DoubleCrosser
-is a strategy that makes use of the number of turns because is set to defect on
+is a strategy that makes use of the number of turns because it is set to defect on
 the last two rounds. The strategy was expected to not perform as well in
@@
 median, of the top 15 strategies, is at 0.075. This indicates that the top ranked
-strategies perform well in any given standard tournament, despite the opponents and
+strategies perform well in any given standard tournament, regardless of the opponents and
 the number of turns.
@@
 done the same. Finally, in $4^{\text{th}}$ and $9^{\text{th}}$ place are Hunter
-strategies which trying to extort, equivalently, strategies that play cyclically
+strategies which try to extort strategies that play cyclically
 and defectors.
@@
 ending was less than 0.1 were considered then the the top ranked spots are not
-dominated by just defecting strategies anymore,
+dominated by just defecting strategies anymore, as shown in
 Table~\ref{table:subset_probend_result}. Instead the effective strategies are
@@
 statistical difference. Thus, in an IPD tournament where the type is not
-specified, playing as any of the Retaliate strategies will have the result.
+specified, playing as any of the Retaliate strategies seems like a good approach.
 DoubleCrosser performed well in standard tournaments and the
 strategy is just an extension of BackStabber. It should be noted that these
-strategies can be characterised as "cheaters". The source code of the strategies
+strategies can be characterised as ``cheaters". The source code of the strategies
 allows them to known the number of turns in a match (if they are specified).
@@
 on teams. The results of \numberofalltournaments tournaments used in this work imply the following:
-they is not a single type of strategy which can performance well in any IPD interaction.
+there is not a single type of strategy which can performance well in any IPD interaction.
 
@@
 environments demonstrated that no strategy can be consistently
-successful, expected if the value of noise is constrained to less than a half.
+successful, except if the value of noise is constrained to less than a half.
 Overall, there has been not a single strategy that has shown to perform well in
-more than one setting. The aim of the next section is to understand which are
-the factors that made these strategies successful, in each setting separately
+more than one setting. The aim of the next section is to understand the features
+that made these strategies successful, in each setting separately
 but also overall.
@@
     \end{center}
-    \caption{The measures which are included in the performance evaluation analysis.}
+    \caption{The features which are included in the performance evaluation analysis.}
     \label{table:manual_measures}
@@
 based on $R^2$ are given by Table~\ref{table:accuracy_random_forest}. The out of
-the bag error~\cite{hastie2005} has also been calculated. The models fit well,
+the bag error (OOB)~\cite{hastie2005} has also been calculated. The models fit well,
 and a high value of both the accuracy measure on the test data and the OOB error
@@
         \begin{center}
-            \includegraphics[width=.75\linewidth]{../output/standard/_feature_importance_bar_plot.pdf}
+            \includegraphics[width=.75\linewidth]{../k_means_output/standard/_feature_importance_bar_plot.pdf}
         \end{center}
@@
         \begin{center}
-            \includegraphics[width=.75\linewidth]{../output/noise/_feature_importance_bar_plot.pdf}
+            \includegraphics[width=.75\linewidth]{../k_means_output/noise/_feature_importance_bar_plot.pdf}
         \end{center}
@@
         \begin{center}
-            \includegraphics[width=.75\linewidth]{../output/probend/_feature_importance_bar_plot.pdf}
+            \includegraphics[width=.75\linewidth]{../k_means_output/probend/_feature_importance_bar_plot.pdf}
         \end{center}
@@
         \begin{center}
-            \includegraphics[width=.75\linewidth]{../output/probend_noise/_feature_importance_bar_plot.pdf}
+            \includegraphics[width=.75\linewidth]{../k_means_output/probend_noise/_feature_importance_bar_plot.pdf}
         \end{center}
@@
         \begin{center}
-            \includegraphics[width=.75\linewidth]{../output/merged/_feature_importance_bar_plot.pdf}
+            \includegraphics[width=.75\linewidth]{../k_means_output/merged/_feature_importance_bar_plot.pdf}
         \end{center}
@@
 
-The \numberofstrategies strategies used in this manuscript have been mainly for
+The \numberofstrategies strategies used in this manuscript have been mainly from
 the literature, and they have been accessible due to an open source software
-called Axelrod-Python. The software was used to generate a total of
+called Axelrod-Python~\cite{axelrodproject}. The software was used to generate a total of
 \numberofalltournaments computer tournaments results with different number of
@@
 mind of its environment it would choose to be the median cooperator in standard
-tournaments, to cooperate 10\% in probabilistic ending tournaments and 
+tournaments, to cooperate 10\% of the times the median cooperator did in probabilistic ending tournaments and 
 60\% in noisy and noisy probabilistic
-tournaments of the times the median cooperator did. Lastly, if a strategy was aware of the opponents but not of the
+tournaments. Lastly, if a strategy was aware of the opponents but not of the
 setting on the tournament, a strategy would be more likely to be successful if
@@
 The data set described in this work contains the largest number of IPD tournaments,
-to the authors knowledge, and it available at~\cite{data}. Further data mining
+to the authors knowledge, and available at~\cite{data}. Further data mining
 could be applied and provide new insights in the field.
@@
 \section{A summary of parameters}\label{app:parameters}
+
+A summary of the parameters and features used in this work are given
+by Table~\ref{table:parameters_summary}.
 
@@
     \end{center}
-    \caption{The measures which are included in the performance evaluation analysis.}
+    \caption{The measures which are included in the performance evaluation analysis.}\label{table:parameters_summary}
 \end{table}

### 2019-12-28 paper/main.tex
add bibliometric paper as reference
It is stated that several publication on the PD happen every year.
The reference backs up the statement

@@
 Though only a select pieces of work have been discussed, the IPD literature is
-rich, and new strategies and competitions are being published every year. The
+rich, and new strategies and competitions are being published every year~\cite{Glynatsi2019}. The
 question, however, still remains the same: what is the best way to play the

### 2019-12-28 paper/main.tex
gets consistent with the use of Axelrod-Python library/APL/citation

@@
 The different tournament types as well as the data collection, which is made
-possible due an open source package called Axelrod-Python~\cite{axelrodproject},
+possible due to an open source package called Axelrod-Python,
 are covered in Section~\ref{section:data_collection}.
@@
 tournaments has been generated and is available at~\cite{data}. This was done using the
-open source package Axelrod-Python~\cite{axelrodproject}, and more specifically,
-version 3.0.0. Axelrod-Python allows for different types of IPD computer
+open source package Axelrod-Python library~\cite{axelrodproject} (APL), and more specifically,
+version 3.0.0. APL allows for different types of IPD computer
 tournaments to be simulated whilst containing a list of over 180 strategies.
@@
 list of the strategies is given in the Appendix~\ref{app:list_of_players}.
-Though Axelrod-Python features several tournament types, this work considers
-only standard, noisy, probabilistic ending and noisy probabilistic ending
+Though APL features several tournament types, this work considers
+standard, noisy, probabilistic ending and noisy probabilistic ending
 tournaments.
@@
 They have been trained to perform well against the strategies
-in~\cite{axelrodproject} in a standard tournament, thus their performance in the
+in APL in a standard tournament, thus their performance in the
 specific setting was anticipated. DoubleCrosser, and Fool Me Once, are
-strategies not from the literature but from~\cite{axelrodproject}. DoubleCrosser
-is a strategy that makes use of the number of turns because is set to defect on
+strategies not from the literature but from the APL. DoubleCrosser
+is a strategy that makes use of the number of turns because it is set to defect on
 the last two rounds. The strategy was expected to not perform as well in
@@
 The Retaliate and
-Limited Retaliate strategies are implemented in~\cite{axelrodproject} by the
+Limited Retaliate strategies are implemented in APL by the
 same contributor. They are strategies designed to defect if the opponent has
@@
     \midrule
-stochastic  &  If a strategy is stochastic & strategy classifier from~\cite{axelrodproject} & boolean  & Na &  Na \\
-makes use of game &  If a strategy makes used of the game information & strategy classifier from~\cite{axelrodproject} & boolean  & Na &  Na \\
-makes use of length &  If a strategy makes used of the number of turns & strategy classifier from~\cite{axelrodproject} & boolean  & Na &  Na \\
-memory usage &  The memory size of a strategy divided by the number of turns & memory size from~\cite{axelrodproject} & float & 0 &  1 \\
+stochastic  &  If a strategy is stochastic & strategy classifier from APL & boolean  & Na &  Na \\
+makes use of game &  If a strategy makes used of the game information & strategy classifier from APL & boolean  & Na &  Na \\
+makes use of length &  If a strategy makes used of the number of turns & strategy classifier from APL & boolean  & Na &  Na \\
+memory usage &  The memory size of a strategy divided by the number of turns & memory size from APL & float & 0 &  1 \\
 SSE & A measure of how far a strategy is from ZD behaviour & method described in~\cite{Knight2019} & float & 0 & 1 \\
@@
 
-Axelrod-Python makes use of classifiers to classify strategies according to
+APL makes use of classifiers to classify strategies according to
 various dimensions. These determine whether
@@
 memory size of strategy (which is specified in the strategies implementation
-in~\cite{axelrodproject}) divide by the number of turns. For example, Evolved
+in the APL) divide by the number of turns. For example, Evolved
 FSM 16 Noise 05 has a memory size of 16 and participated in a tournament where
@@
 the literature, and they have been accessible due to an open source software
-called Axelrod-Python. The software was used to generate a total of
+called Axelrod-Python library. The software was used to generate a total of
 \numberofalltournaments computer tournaments results with different number of
@@
 \begin{itemize}
-    \item The Axelrod library for IPD simulations~\cite{axelrodproject}.
+    \item The Axelrod-Python library for IPD simulations~\cite{axelrodproject}.
     \item The Matplotlib library for visualisation~\cite{hunter2007matplotlib}.
@@
 
-The strategies used in this study which are from Axelrod version 3.0.0
-\cite{axelrodproject}.
+The strategies used in this study which are from Axelrod-Python library version 3.0.0.
 

### 2019-12-28 paper/main.tex
gets consistent with the use of Axelrod-Python library/APL/citation

@@
 
-The \numberofstrategies strategies used in this manuscript have been mainly for
+The \numberofstrategies strategies used in this manuscript have been mainly from
 the literature, and they have been accessible due to an open source software

### 2019-12-28 paper/main.tex
factors/measures to feautures in the text

--- 2019-12-28 paper/main.tex
@@
 
-The aim of this section is to explore the factors that contribute to a
-strategy's successful performance. The factors explored are measures regarding a
+The aim of this section is to explore the features that contribute to a
+strategy's successful performance. The features explored are measures regarding a
 strategy's behaviour, along with measures regarding the tournaments the
@@
 indicates no extortionate behaviour at all whereas a value of 0 indicates that a
-strategy is behaving a ZDs. The rest of the factors considered are the $CC$ to
+strategy is behaving a ZDs. The rest of the features considered are the $CC$ to
 $C$, $CD$ to $C$, $DC$ to $C$, and $DD$ to $C$ rates as well as cooperating
@@
 Table~\ref{table:correlations} shows the correlation coefficients between the
-measures of Table~\ref{table:manual_measures} the median score and the median
+features of Table~\ref{table:manual_measures} the median score and the median
 normalised rank. Note that the correlation for the classifiers is
 not included because they are binary variables and they will be evaluated using a
-different method. The correlation coefficients for all the measures in
+different method. The correlation coefficients for all the features in
 Table~\ref{table:manual_measures} against themselves have also been calculated and a
@@
 \end{center}
-\caption{Correlations table between the measures of Table~\ref{table:manual_measures}
+\caption{Correlations table between the features of Table~\ref{table:manual_measures}
 the normalised rank and the median score.}\label{table:correlations}
@@
 
-In standard tournaments the measures  $CC$ to $C$, $C_r$, $C_r / C_{\text{max}}$
+In standard tournaments the features  $CC$ to $C$, $C_r$, $C_r / C_{\text{max}}$
 and the cooperating ratio compared to $C_{\text{median}}$ and $C_{\text{mean}}$
@@
 In noisy probabilistic ending tournaments and in over all the tournaments' results,
-the only measures that had a moderate affect are $C_r/C_{\text{mean}},
+the only features that had a moderate affect are $C_r/C_{\text{mean}},
 C_r/C_{\text{max}}$ and $C_r$. In such environments cooperative behaviour
@@
 
-The importance that the measures of Table~\ref{table:manual_measures} had on
+The importance that the features of Table~\ref{table:manual_measures} had on
 each classification task; to which cluster a performance was assigned to based
@@
 stochastic, make use of game and make use of length have no significant effect,
-and several of the measures that are highted by the importance are inline with
+and several of the features that are highted by the importance are inline with
 the correlation results. Moreover, the smoothing parameter \(k\) appears to no
-have a significant effect either. The most important measures based on the
+have a significant effect either. The most important features based on the
 random forest analysis were $C_{r} / C_{median}$ and $C_r / C_{mean}$.
@@
 
-The effect of both these measures can be further explored. In
+The effect of both these features can be further explored. In
 Figure~\ref{fig:mean_median_std} the distributions of \(C_r / C_{\text{mean}}\)
@@
 was the mean/median cooperator of its respective tournament. In comparison,
-Figure~\ref{fig:mean_median_noisy} shows the distributions of the measures for
+Figure~\ref{fig:mean_median_noisy} shows the distributions of the features for
 the winners in noisy tournaments where the mean is at 0.67. Thereupon the winners
@@
 
-In this section the effect of several measures, regarding a strategy's behaviour
+In this section the effect of several features, regarding a strategy's behaviour
 and the tournament in which it participated on its performance were presented.
@@
 Section~\ref{section:evaluation_of_performance}, covered an analysis of
-performance based on several measures associated with a strategy and with the
+performance based on several features associated with a strategy and with the
 environments it was competing. The results of this analysis showed that a
@@
 used regarding the game had no effect on the strategy's success. The most
-important factors have been those that compared the strategy's behaviour to it's
+important features have been those that compared the strategy's behaviour to it's
 environment. The cooperating ratio of the strategy compared to the mean and
@@
     \end{center}
-    \caption{The measures which are included in the performance evaluation analysis.}
+    \caption{The features which are included in the performance evaluation analysis.}\label{table:parameters_summary}
 \end{table}
@@
 
-A graphical representation of the correlation coefficients for the measures in
+A graphical representation of the correlation coefficients for the features in
 Table~\ref{table:manual_measures}.
@@
         \end{center}
-        \caption{Correlation coefficients of measures in Table~\ref{table:manual_measures}
+        \caption{Correlation coefficients of features in Table~\ref{table:manual_measures}
         for standard tournaments}
@@
     \end{center}
-    \caption{Correlation coefficients of measures in Table~\ref{table:manual_measures}
+    \caption{Correlation coefficients of features in Table~\ref{table:manual_measures}
     for noisy tournaments}
@@
     \end{center}
-    \caption{Correlation coefficients of measures in Table~\ref{table:manual_measures}
+    \caption{Correlation coefficients of features in Table~\ref{table:manual_measures}
     for probabilistic ending tournaments}
@@
     \end{center}
-    \caption{Correlation coefficients of measures in Table~\ref{table:manual_measures}
+    \caption{Correlation coefficients of features in Table~\ref{table:manual_measures}
     for noisy probabilistic ending tournaments}
@@
     \end{center}
-    \caption{Correlation coefficients of measures in Table~\ref{table:manual_measures}
+    \caption{Correlation coefficients of features in Table~\ref{table:manual_measures}
     for data set}

### 2019-12-28 paper/main.tex
measure to feature in labels

@@
 probabilities of a strategy being in any of the four states ($CC, CD, DC, DD$),
-and the rate of which the strategy cooperated after each state. A measure that
+and the rate of which the strategy cooperated after each state. A feature that
 has been manually included is the \textbf{normalised rank}. The normalised rank,
@@
 strategy's behaviour, along with measures regarding the tournaments the
-strategies competed in. These are given in Table~\ref{table:manual_measures}.
+strategies competed in. These are given in Table~\ref{table:manual_features}.
 
@@
     \toprule
-    measure & measure explanation &  source & value type & min value & max value \\
+    feature & feature explanation &  source & value type & min value & max value \\
     \midrule
@@
     \caption{The features which are included in the performance evaluation analysis.}
-    \label{table:manual_measures}
+    \label{table:manual_features}
 \end{table}
@@
 a strategy is stochastic or deterministic, whether it makes use of the number of
-turns or the game's payoffs. The memory usage measure is calculated as the
+turns or the game's payoffs. The memory usage feature is calculated as the
 memory size of strategy (which is specified in the strategies implementation
@@
 of 0.119. For tournaments with a probabilistic ending the number of turns was
-not collected, so the memory usage measure is not used for probabilistic ending
-tournaments. The SSE is a measure introduced in~\cite{Knight2019} which shows
+not collected, so the memory usage feature is not used for probabilistic ending
+tournaments. The SSE is a feature introduced in~\cite{Knight2019} which shows
 how close a strategy is to behaving as a ZDs, and subsequently, in an
@@
 Table~\ref{table:correlations} shows the correlation coefficients between the
-features of Table~\ref{table:manual_measures} the median score and the median
+features of Table~\ref{table:manual_features} the median score and the median
 normalised rank. Note that the correlation for the classifiers is
@@
 different method. The correlation coefficients for all the features in
-Table~\ref{table:manual_measures} against themselves have also been calculated and a
+Table~\ref{table:manual_features} against themselves have also been calculated and a
 graphical representation can be found in the Appendix~\ref{app:correlations}.
@@
 \end{center}
-\caption{Correlations table between the features of Table~\ref{table:manual_measures}
+\caption{Correlations table between the features of Table~\ref{table:manual_features}
 the normalised rank and the median score.}\label{table:correlations}
@@
 
-The importance that the features of Table~\ref{table:manual_measures} had on
+The importance that the features of Table~\ref{table:manual_features} had on
 each classification task; to which cluster a performance was assigned to based
@@
     \toprule
-measure & measure explanation \\
+feature & feature explanation \\
  \midrule
@@
 A graphical representation of the correlation coefficients for the features in
-Table~\ref{table:manual_measures}.
+Table~\ref{table:manual_features}.
 
@@
         \end{center}
-        \caption{Correlation coefficients of features in Table~\ref{table:manual_measures}
+        \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
         for standard tournaments}
@@
     \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_measures}
+    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
     for noisy tournaments}
@@
     \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_measures}
+    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
     for probabilistic ending tournaments}
@@
     \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_measures}
+    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
     for noisy probabilistic ending tournaments}
@@
     \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_measures}
+    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
     for data set}

### 2019-12-28 paper/main.tex
measure to feature in labels

--- 2019-12-28 paper/main.tex
@@
     \end{center}
-    \caption{The measures which are included in the performance evaluation analysis.}
-    \label{table:manual_measures}
+    \caption{The features which are included in the performance evaluation analysis.}
+    \label{table:manual_features}
 \end{table}

### 2019-12-28 paper/main.tex
adds explanation on r being R / N - 1

--- 2019-12-28 paper/main.tex
@@
 and the rate of which the strategy cooperated after each state. A feature that
-has been manually included is the \textbf{normalised rank}. The normalised rank,
+has been manually included is the \textbf{normalised rank}. The rank of a given
+strategy, denoted as \(R\), can vary between 0 and \(N-1\). Thus, the normalised rank,
 denoted as $r$, is calculated as a strategy's rank divided by the tournament's
-size ($N$). In the next section the performance of these strategies is evaluated
+size $N$ minus 1. In the next section the performance of these strategies is evaluated
 based on their normalised rank.

### 2019-12-29 paper/main.tex
fixes re writes.
This was meant to be 3 different commits but I forgot to commit.
The re writes are the following:

- Conclusion in noisy tourmanets. Explain better that the highly ranked
strategies did so because of their performance in tournaments with p>0.5
- Final conclusion of top rank strategies section. Tweaked the text
a little bit
- Better explanation regarding the clustering of the performances.
The different approaches are now bullet points.

@@
 that although the top ranked strategies mainly performed well, there are several
-tournaments that they ranked in the bottom half. To gain a better understanding
-of the behaviour in noisy tournaments, the \(r\) distributions for the top 6
-of Figure~\ref{fig:noisy_results} strategies over the noise probability \(p_n\),
-are given in Figure~\ref{fig:effect_of_noise}.
+tournaments that they ranked in the bottom half. The bimodality of the \(r\)
+distributions can be explained by Figure~\ref{fig:noisy_results} which gives the
+\(r\) distributions for the top 6 strategies over the noise probability \(p_n\).
+Note that for \(p_n=0.5\) a strategy corresponds to a random player and for
+\(p_n=1\) a strategy is behaving in the exact opposite way than its design.
 
@@
 
-Figure~\ref{fig:effect_of_noise} shows that for \(p_n\) values lower than 0.5
-Grumpy, Tit For 2 Tats and Slow Tit For Two Tat perform moderately, and \(e\),
-Cycle Hunter and Ricky QLearner perform poorly. At \(p_n=0.5\) all the
-distributions become bimodal. This is because with a noise probability of 0.5,
-all strategies correspond to a random player. Interestedly, for a \(p_n\) larger
-than 0.5 all of the 6 strategies become successful. Note that a value \(p_n=1\)
-corresponds to a strategy playing opposite from what it intended to. Thus, it is
-demonstrated that the successful strategies is noisy tournaments are sometimes
-effective when \(p_n=0.5\) but overall they are very successful whn they are
-playing opposite from their original design. If during the data collection a
-\(p_n\) strictly less 0.5 was considered then the top ranked strategies would be
+From Figure~\ref{fig:effect_of_noise} it is evident that the strategies highly
+ranked in noisy environments did so because of their performance in tournaments
+with \(p_n>0.5\). In tournaments with a noise probability lower than \(0.5\) the
+strategies performed poorly which is why their \(r\) distributions are bimodal.
+If during the data collection a \(p_n\) strictly less 0.5 was considered then the top ranked strategies would be
 different. There are a total of 5661 trials where \(p_n<0.5\) and the top ranked
@@
 if a value of noise strictly less than 0.5 was considered, then the successful
-strategies were strategies based on teams. In
-probabilistic ending tournaments most of the winning strategies were defecting
-strategies and trained finite state automata, designed by the same authors.
-These strategies only did better when the probability of the game ending after
-each turn was increased.
+strategies were strategies based on the behaviour of many strategies. In
+probabilistic ending tournaments most of the highly ranked strategies were defecting
+strategies and trained finite state automata, all by the authors of~\cite{Ashlock2006, Ashlock2014}.
+These strategies ranked high due to their performance in tournaments where the probability of the game ending after
+each turn was bigger than 0.1.
 Finally the performance of all \numberofstrategies
@@
 
-The performances are clustered based on the normalised rank. More specifically,
-they are clustered 3 times into 2 different clusters based on  on whether their
-normalised rank was in the top 5\%, 25\% or 50\% respectively. A random forest
-approach~\cite{breiman2001} is then applied to each performance to predict the cluster to
-which it has been assigned to. The random forest method
-constructs many individual decision trees and the predictions from all trees are
-pooled to make the final prediction. The random forest models are trained on a
-training set of 70\% of the tournaments results. The accuracy of each model
-based on $R^2$ are given by Table~\ref{table:accuracy_random_forest}. The out of
-the bag error~\cite{hastie2005} has also been calculated. The models fit well,
-and a high value of both the accuracy measure on the test data and the OOB error
-indicate that the model is not over fitting.
-
-The performances have also been clustered based on their normalised rank and
+To further explore the features that contribute to a strategy's success the
+performances are divided into clusters based on whether they were successful or
+not. A random forest approach~\cite{breiman2001} is then applied to each
+performance to predict the cluster to which it has been assigned to. This allows
+for the importance of each feature in the classification to be calculated. In
+essence, to calculate which are the important features when one is trying to
+predict whether a performance was successful or not.
+
+The performances are clustered into successful and unsuccessful clusters based on
+4 different approaches. More specifically:
+
+\begin{itemize}
+    \item \textbf{Approach 1:} The performances are divided into two clusters based
+    on whether their performance was in the top \(5\%\) of their respective tournaments.
+    Thus, whether \(r\) was smaller or larger than 0.05.
+    \item \textbf{Approach 2:} The performances are divided into two clusters based
+    on whether their performance was in the top \(25\%\) of their respective tournaments.
+    Thus, whether \(r\) was smaller or larger than 0.25.
+    \item \textbf{Approach 3:} The performances are divided into two clusters based
+    on whether their performance was in the top \(50\%\) of their respective tournaments.
+    Thus, whether \(r\) was smaller or larger than 0.50.
+    \item \textbf{Approach 4:} The performances are clustered based on their normalised rank and
     their median score by a \(k-\)means algorithm~\cite{Arthur2007}. The number of
     clusters is not deterministically chosen but it is based on the silhouette
-coefficients~\cite{Rousseeuw1987}. The chosen cluster for each tournament type,
-as well as the accuracy for random forest models are also given in
-Table~\ref{table:accuracy_random_forest}.
+    coefficients~\cite{Rousseeuw1987}.
+\end{itemize}
+
+The random forest method constructs many individual decision trees and the
+predictions from all trees are pooled to make the final prediction. The random
+forest models are trained on a training set of 70\% of the tournaments results.
+The accuracy of each model based on $R^2$ and the number of clusters for each
+tournament type (because in the case of Approach 4 it is not
+deterministically chosen) are given by Table~\ref{table:accuracy_random_forest}.
+The out of the bag error (OOB)~\cite{hastie2005} has also been calculated. The
+models fit well, and a high value of both the accuracy measure on the test data
+and the OOB error indicate that the model is not over fitting.
 
@@
     \toprule
-    Tournament type & Clustering on & Number of clusters & $R^2$ training data &  $R^2$ test data  & $R^2$ OOB score\\
+    Tournament type & Clustering Approach & Number of clusters & $R^2$ training data &  $R^2$ test data  & $R^2$ OOB score\\
     \midrule
-    standard  & top 5\% $r$              & 2  & 0.998831  & 0.987041 & 0.983708 \\
-              & top 25\% $r$             & 2  & 0.998643  & 0.978626 & 0.969202 \\
-              & top 50\% $r$             & 2  & 0.998417  & 0.985217 & 0.976538 \\
-              & $r$  \& normalised score & 2  & 0.998794  & 0.990677 & 0.982959 \\
+    standard  & Approach 1 & 2  & 0.998831  & 0.987041 & 0.983708 \\
+              & Approach 2 & 2  & 0.998643  & 0.978626 & 0.969202 \\
+              & Approach 3 & 2  & 0.998417  & 0.985217 & 0.976538 \\
+              & Approach 4 & 2  & 0.998794  & 0.990677 & 0.982959 \\
     \midrule
-    noisy     & top 5\% $r$              & 2 & 0.996677  & 0.950572 & 0.935383\\
-              & top 25\% $r$             & 2 & 0.996677  & 0.950572 & 0.935383\\
-              & top 50\% $r$             & 2 & 0.996677  & 0.950572 & 0.935383\\
-              & $r$  \& normalised score & 3 & 0.996677  & 0.950572 & 0.935383\\
+    noisy     & Approach 1  & 2 & 0.996677  & 0.950572 & 0.935383\\
+              & Approach 2  & 2 & 0.996677  & 0.950572 & 0.935383\\
+              & Approach 3  & 2 & 0.996677  & 0.950572 & 0.935383\\
+              & Approach 4  & 3 & 0.996677  & 0.950572 & 0.935383\\
     \midrule
-    probabilistic ending & top 5\% $r$              & 2 & 0.999592  & 0.995128 & 0.992819 \\
-                         & top 25\% $r$             & 2 & 0.999592  & 0.995128 & 0.992819 \\
-                         & top 50\% $r$             & 2 & 0.999592  & 0.995128 & 0.992819 \\
-                         & $r$  \& normalised score & 2 & 0.999592  & 0.995128 & 0.992819 \\
+    probabilistic ending & Approach 1  & 2 & 0.999592  & 0.995128 & 0.992819 \\
+                         & Approach 2  & 2 & 0.999592  & 0.995128 & 0.992819 \\
+                         & Approach 3  & 2 & 0.999592  & 0.995128 & 0.992819 \\
+                         & Approach 4  & 2 & 0.999592  & 0.995128 & 0.992819 \\
     \midrule
-    noisy probabilistic ending & top 5\% $r$              & 2 & 0.990490  & 0.813905 & 0.791418\\
-                               & top 25\% $r$             & 2 & 0.990490  & 0.813905 & 0.791418\\
-                               & top 50\% $r$             & 2 & 0.990490  & 0.813905 & 0.791418\\
-                               & $r$  \& normalised score & 4 & 0.990490  & 0.813905 & 0.791418\\
+    noisy probabilistic ending & Approach 1  & 2 & 0.990490  & 0.813905 & 0.791418\\
+                               & Approach 2  & 2 & 0.990490  & 0.813905 & 0.791418\\
+                               & Approach 3  & 2 & 0.990490  & 0.813905 & 0.791418\\
+                               & Approach 4  & 4 & 0.990490  & 0.813905 & 0.791418\\
     \midrule
-    over \numberofalltournaments tournaments & top 5\% $r$               & 2 & 0.993396 & 0.913409 & 0.898059 \\
-                                             & top 25\% $r$              & 2 & 0.993396 & 0.913409 & 0.898059 \\
-                                             & top 50\% $r$              & 2 & 0.993396 & 0.913409 & 0.898059 \\
-                                             & $r$  \& normalised score  & 3 & 0.993396 & 0.913409 & 0.898059 \\
+    over \numberofalltournaments tournaments & Approach 1  & 2 & 0.993396 & 0.913409 & 0.898059 \\
+                                             & Approach 2  & 2 & 0.993396 & 0.913409 & 0.898059 \\
+                                             & Approach 3  & 2 & 0.993396 & 0.913409 & 0.898059 \\
+                                             & Approach 4  & 3 & 0.993396 & 0.913409 & 0.898059 \\
     \bottomrule
@@
 The importance that the features of Table~\ref{table:manual_features} had on
-each classification task; to which cluster a performance was assigned to based
-on the normalised rank, and their normalised rank and median score have been
+each random forest model while the perfomances were clustered based on the
+different approaches have been
 calculated and are given by Figures~\ref{fig:clustering_importance_standard},

### 2020-01-16 paper/main.tex
add sentence about behaving too cooperative in conclusion
address comments on pr

--- 2019-12-29 paper/main.tex
@@
 list of the strategies is given in the Appendix~\ref{app:list_of_players}.
-Though APL features several tournament types, this work considers
+Although APL features several tournament types, this work considers
 standard, noisy, probabilistic ending and noisy probabilistic ending
@@
 denoted as $r$, is calculated as a strategy's rank divided by the tournament's
-size $N$ minus 1. In the next section the performance of these strategies is evaluated
+size \(N - 1\). In the next section the performance of these strategies is evaluated
 based on their normalised rank.
@@
 The out of the bag error (OOB)~\cite{hastie2005} has also been calculated. The
-models fit well, and a high value of both the accuracy measure on the test data
+models fit well, and a high value of both the accuracy measures on the test data
 and the OOB error indicate that the model is not over fitting.
@@
 stochastic, make use of game and make use of length have no significant effect,
-and several of the features that are highted by the importance are inline with
+and several of the features that are highlighted by the importance are inline with
 the correlation results. Moreover, the smoothing parameter \(k\) appears to no
@@
 vary. Moreover, a strategy with a theory of mind should aim to adapt its behaviour
-based on the mean and median cooperators.
+based on the mean and median cooperators and should in general not be too
+cooperative.
 
@@
 the literature, and they have been accessible due to an open source software
-called Axelrod-Python library. The software was used to generate a total of
+called the Axelrod-Python library. The software was used to generate a total of
 \numberofalltournaments computer tournaments results with different number of
@@
 mind of its environment it would choose to be the median cooperator in standard
-tournaments, to cooperate 10\% in probabilistic ending tournaments and 
+tournaments, to cooperate 10\% of the time the median cooperator did in probabilistic ending tournaments and 
 60\% in noisy and noisy probabilistic
-tournaments of the times the median cooperator did. Lastly, if a strategy was aware of the opponents but not of the
-setting on the tournament, a strategy would be more likely to be successful if
+tournaments. Lastly, if a strategy was aware of the opponents but not of the
+setting of the tournament, a strategy would be more likely to be successful if
 it were to identify the median cooperator and cooperated 67\% of the times that

### 2020-01-16 paper/main.tex
address comments on pr

--- 2019-12-29 paper/main.tex
@@
 mind of its environment it would choose to be the median cooperator in standard
-tournaments, to cooperate 10\% of the times the median cooperator did in probabilistic ending tournaments and 
+tournaments, to cooperate 10\% of the time the median cooperator did in probabilistic ending tournaments and 
 60\% in noisy and noisy probabilistic
 tournaments. Lastly, if a strategy was aware of the opponents but not of the
-setting on the tournament, a strategy would be more likely to be successful if
+setting of the tournament, a strategy would be more likely to be successful if
 it were to identify the median cooperator and cooperated 67\% of the times that

### 2020-01-28 paper/main.tex
address TODO in conclusion
Prepares paper (#13)
* re-run analysis with new data

* clean repo

* move notebooks

* rename files, run black and tweak code

* tests to pytest

* test and implement prepare, process src files

* create clystering analysis script

* update enviroment yml

* add feautures to analysis

* add lines to run on siren

* tweaks to outputs

* add new meausures to analysis

* add probend, noise and turns to cluster analysis

* fix failure

* remove turns as default cluster feauture

* week commit

* write first sections of papers

* fix errors and move tests

* create test

--- 2020-01-16 paper/main.tex
@@
 Though only a select pieces of work have been discussed, the IPD literature is
-rich, and new strategies and competitions are being published every year~\cite{Glynatsi2019}. The
+rich, and new strategies and competitions are being published every year. The
 question, however, still remains the same: what is the best way to play the
@@
 The different tournament types as well as the data collection, which is made
-possible due to an open source package called Axelrod-Python,
+possible due an open source package called Axelrod-Python~\cite{axelrodproject},
 are covered in Section~\ref{section:data_collection}.
@@
 tournaments has been generated and is available at~\cite{data}. This was done using the
-open source package Axelrod-Python library~\cite{axelrodproject} (APL), and more specifically,
-version 3.0.0. APL allows for different types of IPD computer
+open source package Axelrod-Python~\cite{axelrodproject}, and more specifically,
+version 3.0.0. Axelrod-Python allows for different types of IPD computer
 tournaments to be simulated whilst containing a list of over 180 strategies.
@@
 list of the strategies is given in the Appendix~\ref{app:list_of_players}.
-Although APL features several tournament types, this work considers
-standard, noisy, probabilistic ending and noisy probabilistic ending
+Though Axelrod-Python features several tournament types, this work considers
+only standard, noisy, probabilistic ending and noisy probabilistic ending
 tournaments.
@@
 probabilities of a strategy being in any of the four states ($CC, CD, DC, DD$),
-and the rate of which the strategy cooperated after each state. A feature that
-has been manually included is the \textbf{normalised rank}. The rank of a given
-strategy, denoted as \(R\), can vary between 0 and \(N-1\). Thus, the normalised rank,
+and the rate of which the strategy cooperated after each state. A measure that
+has been manually included is the \textbf{normalised rank}. The normalised rank,
 denoted as $r$, is calculated as a strategy's rank divided by the tournament's
-size \(N - 1\). In the next section the performance of these strategies is evaluated
+size ($N$). In the next section the performance of these strategies is evaluated
 based on their normalised rank.
@@
 They have been trained to perform well against the strategies
-in APL in a standard tournament, thus their performance in the
+in~\cite{axelrodproject} in a standard tournament, thus their performance in the
 specific setting was anticipated. DoubleCrosser, and Fool Me Once, are
-strategies not from the literature but from the APL. DoubleCrosser
-is a strategy that makes use of the number of turns because it is set to defect on
+strategies not from the literature but from~\cite{axelrodproject}. DoubleCrosser
+is a strategy that makes use of the number of turns because is set to defect on
 the last two rounds. The strategy was expected to not perform as well in
@@
 The Retaliate and
-Limited Retaliate strategies are implemented in APL by the
+Limited Retaliate strategies are implemented in~\cite{axelrodproject} by the
 same contributor. They are strategies designed to defect if the opponent has
@@
 that although the top ranked strategies mainly performed well, there are several
-tournaments that they ranked in the bottom half. The bimodality of the \(r\)
-distributions can be explained by Figure~\ref{fig:noisy_results} which gives the
-\(r\) distributions for the top 6 strategies over the noise probability \(p_n\).
-Note that for \(p_n=0.5\) a strategy corresponds to a random player and for
-\(p_n=1\) a strategy is behaving in the exact opposite way than its design.
+tournaments that they ranked in the bottom half. To gain a better understanding
+of the behaviour in noisy tournaments, the \(r\) distributions for the top 6
+of Figure~\ref{fig:noisy_results} strategies over the noise probability \(p_n\),
+are given in Figure~\ref{fig:effect_of_noise}.
 
@@
 
-From Figure~\ref{fig:effect_of_noise} it is evident that the strategies highly
-ranked in noisy environments did so because of their performance in tournaments
-with \(p_n>0.5\). In tournaments with a noise probability lower than \(0.5\) the
-strategies performed poorly which is why their \(r\) distributions are bimodal.
-If during the data collection a \(p_n\) strictly less 0.5 was considered then the top ranked strategies would be
+Figure~\ref{fig:effect_of_noise} shows that for \(p_n\) values lower than 0.5
+Grumpy, Tit For 2 Tats and Slow Tit For Two Tat perform moderately, and \(e\),
+Cycle Hunter and Ricky QLearner perform poorly. At \(p_n=0.5\) all the
+distributions become bimodal. This is because with a noise probability of 0.5,
+all strategies correspond to a random player. Interestedly, for a \(p_n\) larger
+than 0.5 all of the 6 strategies become successful. Note that a value \(p_n=1\)
+corresponds to a strategy playing opposite from what it intended to. Thus, it is
+demonstrated that the successful strategies is noisy tournaments are sometimes
+effective when \(p_n=0.5\) but overall they are very successful whn they are
+playing opposite from their original design. If during the data collection a
+\(p_n\) strictly less 0.5 was considered then the top ranked strategies would be
 different. There are a total of 5661 trials where \(p_n<0.5\) and the top ranked
@@
 if a value of noise strictly less than 0.5 was considered, then the successful
-strategies were strategies based on the behaviour of many strategies. In
-probabilistic ending tournaments most of the highly ranked strategies were defecting
-strategies and trained finite state automata, all by the authors of~\cite{Ashlock2006, Ashlock2014}.
-These strategies ranked high due to their performance in tournaments where the probability of the game ending after
-each turn was bigger than 0.1.
+strategies were strategies based on teams. In
+probabilistic ending tournaments most of the winning strategies were defecting
+strategies and trained finite state automata, designed by the same authors.
+These strategies only did better when the probability of the game ending after
+each turn was increased.
 Finally the performance of all \numberofstrategies
@@
 
-The aim of this section is to explore the features that contribute to a
-strategy's successful performance. The features explored are measures regarding a
+The aim of this section is to explore the factors that contribute to a
+strategy's successful performance. The factors explored are measures regarding a
 strategy's behaviour, along with measures regarding the tournaments the
-strategies competed in. These are given in Table~\ref{table:manual_features}.
+strategies competed in. These are given in Table~\ref{table:manual_measures}.
 
@@
     \toprule
-    feature & feature explanation &  source & value type & min value & max value \\
+    measure & measure explanation &  source & value type & min value & max value \\
     \midrule
-stochastic  &  If a strategy is stochastic & strategy classifier from APL & boolean  & Na &  Na \\
-makes use of game &  If a strategy makes used of the game information & strategy classifier from APL & boolean  & Na &  Na \\
-makes use of length &  If a strategy makes used of the number of turns & strategy classifier from APL & boolean  & Na &  Na \\
-memory usage &  The memory size of a strategy divided by the number of turns & memory size from APL & float & 0 &  1 \\
+stochastic  &  If a strategy is stochastic & strategy classifier from~\cite{axelrodproject} & boolean  & Na &  Na \\
+makes use of game &  If a strategy makes used of the game information & strategy classifier from~\cite{axelrodproject} & boolean  & Na &  Na \\
+makes use of length &  If a strategy makes used of the number of turns & strategy classifier from~\cite{axelrodproject} & boolean  & Na &  Na \\
+memory usage &  The memory size of a strategy divided by the number of turns & memory size from~\cite{axelrodproject} & float & 0 &  1 \\
 SSE & A measure of how far a strategy is from ZD behaviour & method described in~\cite{Knight2019} & float & 0 & 1 \\
@@
     \end{center}
-    \caption{The features which are included in the performance evaluation analysis.}
-    \label{table:manual_features}
+    \caption{The measures which are included in the performance evaluation analysis.}
+    \label{table:manual_measures}
 \end{table}
 
-APL makes use of classifiers to classify strategies according to
+Axelrod-Python makes use of classifiers to classify strategies according to
 various dimensions. These determine whether
 a strategy is stochastic or deterministic, whether it makes use of the number of
-turns or the game's payoffs. The memory usage feature is calculated as the
+turns or the game's payoffs. The memory usage measure is calculated as the
 memory size of strategy (which is specified in the strategies implementation
-in the APL) divide by the number of turns. For example, Evolved
+in~\cite{axelrodproject}) divide by the number of turns. For example, Evolved
 FSM 16 Noise 05 has a memory size of 16 and participated in a tournament where
@@
 of 0.119. For tournaments with a probabilistic ending the number of turns was
-not collected, so the memory usage feature is not used for probabilistic ending
-tournaments. The SSE is a feature introduced in~\cite{Knight2019} which shows
+not collected, so the memory usage measure is not used for probabilistic ending
+tournaments. The SSE is a measure introduced in~\cite{Knight2019} which shows
 how close a strategy is to behaving as a ZDs, and subsequently, in an
@@
 indicates no extortionate behaviour at all whereas a value of 0 indicates that a
-strategy is behaving a ZDs. The rest of the features considered are the $CC$ to
+strategy is behaving a ZDs. The rest of the factors considered are the $CC$ to
 $C$, $CD$ to $C$, $DC$ to $C$, and $DD$ to $C$ rates as well as cooperating
@@
 Table~\ref{table:correlations} shows the correlation coefficients between the
-features of Table~\ref{table:manual_features} the median score and the median
+measures of Table~\ref{table:manual_measures} the median score and the median
 normalised rank. Note that the correlation for the classifiers is
 not included because they are binary variables and they will be evaluated using a
-different method. The correlation coefficients for all the features in
-Table~\ref{table:manual_features} against themselves have also been calculated and a
+different method. The correlation coefficients for all the measures in
+Table~\ref{table:manual_measures} against themselves have also been calculated and a
 graphical representation can be found in the Appendix~\ref{app:correlations}.
@@
 \end{center}
-\caption{Correlations table between the features of Table~\ref{table:manual_features}
+\caption{Correlations table between the measures of Table~\ref{table:manual_measures}
 the normalised rank and the median score.}\label{table:correlations}
@@
 
-In standard tournaments the features  $CC$ to $C$, $C_r$, $C_r / C_{\text{max}}$
+In standard tournaments the measures  $CC$ to $C$, $C_r$, $C_r / C_{\text{max}}$
 and the cooperating ratio compared to $C_{\text{median}}$ and $C_{\text{mean}}$
@@
 In noisy probabilistic ending tournaments and in over all the tournaments' results,
-the only features that had a moderate affect are $C_r/C_{\text{mean}},
+the only measures that had a moderate affect are $C_r/C_{\text{mean}},
 C_r/C_{\text{max}}$ and $C_r$. In such environments cooperative behaviour
@@
 
-To further explore the features that contribute to a strategy's success the
-performances are divided into clusters based on whether they were successful or
-not. A random forest approach~\cite{breiman2001} is then applied to each
-performance to predict the cluster to which it has been assigned to. This allows
-for the importance of each feature in the classification to be calculated. In
-essence, to calculate which are the important features when one is trying to
-predict whether a performance was successful or not.
-
-The performances are clustered into successful and unsuccessful clusters based on
-4 different approaches. More specifically:
-
-\begin{itemize}
-    \item \textbf{Approach 1:} The performances are divided into two clusters based
-    on whether their performance was in the top \(5\%\) of their respective tournaments.
-    Thus, whether \(r\) was smaller or larger than 0.05.
-    \item \textbf{Approach 2:} The performances are divided into two clusters based
-    on whether their performance was in the top \(25\%\) of their respective tournaments.
-    Thus, whether \(r\) was smaller or larger than 0.25.
-    \item \textbf{Approach 3:} The performances are divided into two clusters based
-    on whether their performance was in the top \(50\%\) of their respective tournaments.
-    Thus, whether \(r\) was smaller or larger than 0.50.
-    \item \textbf{Approach 4:} The performances are clustered based on their normalised rank and
+The performances are clustered based on the normalised rank. More specifically,
+they are clustered 3 times into 2 different clusters based on  on whether their
+normalised rank was in the top 5\%, 25\% or 50\% respectively. A random forest
+approach~\cite{breiman2001} is then applied to each performance to predict the cluster to
+which it has been assigned to. The random forest method
+constructs many individual decision trees and the predictions from all trees are
+pooled to make the final prediction. The random forest models are trained on a
+training set of 70\% of the tournaments results. The accuracy of each model
+based on $R^2$ are given by Table~\ref{table:accuracy_random_forest}. The out of
+the bag error~\cite{hastie2005} has also been calculated. The models fit well,
+and a high value of both the accuracy measure on the test data and the OOB error
+indicate that the model is not over fitting.
+
+The performances have also been clustered based on their normalised rank and
 their median score by a \(k-\)means algorithm~\cite{Arthur2007}. The number of
 clusters is not deterministically chosen but it is based on the silhouette
-    coefficients~\cite{Rousseeuw1987}.
-\end{itemize}
-
-The random forest method constructs many individual decision trees and the
-predictions from all trees are pooled to make the final prediction. The random
-forest models are trained on a training set of 70\% of the tournaments results.
-The accuracy of each model based on $R^2$ and the number of clusters for each
-tournament type (because in the case of Approach 4 it is not
-deterministically chosen) are given by Table~\ref{table:accuracy_random_forest}.
-The out of the bag error (OOB)~\cite{hastie2005} has also been calculated. The
-models fit well, and a high value of both the accuracy measures on the test data
-and the OOB error indicate that the model is not over fitting.
+coefficients~\cite{Rousseeuw1987}. The chosen cluster for each tournament type,
+as well as the accuracy for random forest models are also given in
+Table~\ref{table:accuracy_random_forest}.
 
@@
     \toprule
-    Tournament type & Clustering Approach & Number of clusters & $R^2$ training data &  $R^2$ test data  & $R^2$ OOB score\\
+    Tournament type & Clustering on & Number of clusters & $R^2$ training data &  $R^2$ test data  & $R^2$ OOB score\\
     \midrule
-    standard  & Approach 1 & 2  & 0.998831  & 0.987041 & 0.983708 \\
-              & Approach 2 & 2  & 0.998643  & 0.978626 & 0.969202 \\
-              & Approach 3 & 2  & 0.998417  & 0.985217 & 0.976538 \\
-              & Approach 4 & 2  & 0.998794  & 0.990677 & 0.982959 \\
+    standard  & top 5\% $r$              & 2  & 0.998831  & 0.987041 & 0.983708 \\
+              & top 25\% $r$             & 2  & 0.998643  & 0.978626 & 0.969202 \\
+              & top 50\% $r$             & 2  & 0.998417  & 0.985217 & 0.976538 \\
+              & $r$  \& normalised score & 2  & 0.998794  & 0.990677 & 0.982959 \\
     \midrule
-    noisy     & Approach 1  & 2 & 0.996677  & 0.950572 & 0.935383\\
-              & Approach 2  & 2 & 0.996677  & 0.950572 & 0.935383\\
-              & Approach 3  & 2 & 0.996677  & 0.950572 & 0.935383\\
-              & Approach 4  & 3 & 0.996677  & 0.950572 & 0.935383\\
+    noisy     & top 5\% $r$              & 2 & 0.996677  & 0.950572 & 0.935383\\
+              & top 25\% $r$             & 2 & 0.996677  & 0.950572 & 0.935383\\
+              & top 50\% $r$             & 2 & 0.996677  & 0.950572 & 0.935383\\
+              & $r$  \& normalised score & 3 & 0.996677  & 0.950572 & 0.935383\\
     \midrule
-    probabilistic ending & Approach 1  & 2 & 0.999592  & 0.995128 & 0.992819 \\
-                         & Approach 2  & 2 & 0.999592  & 0.995128 & 0.992819 \\
-                         & Approach 3  & 2 & 0.999592  & 0.995128 & 0.992819 \\
-                         & Approach 4  & 2 & 0.999592  & 0.995128 & 0.992819 \\
+    probabilistic ending & top 5\% $r$              & 2 & 0.999592  & 0.995128 & 0.992819 \\
+                         & top 25\% $r$             & 2 & 0.999592  & 0.995128 & 0.992819 \\
+                         & top 50\% $r$             & 2 & 0.999592  & 0.995128 & 0.992819 \\
+                         & $r$  \& normalised score & 2 & 0.999592  & 0.995128 & 0.992819 \\
     \midrule
-    noisy probabilistic ending & Approach 1  & 2 & 0.990490  & 0.813905 & 0.791418\\
-                               & Approach 2  & 2 & 0.990490  & 0.813905 & 0.791418\\
-                               & Approach 3  & 2 & 0.990490  & 0.813905 & 0.791418\\
-                               & Approach 4  & 4 & 0.990490  & 0.813905 & 0.791418\\
+    noisy probabilistic ending & top 5\% $r$              & 2 & 0.990490  & 0.813905 & 0.791418\\
+                               & top 25\% $r$             & 2 & 0.990490  & 0.813905 & 0.791418\\
+                               & top 50\% $r$             & 2 & 0.990490  & 0.813905 & 0.791418\\
+                               & $r$  \& normalised score & 4 & 0.990490  & 0.813905 & 0.791418\\
     \midrule
-    over \numberofalltournaments tournaments & Approach 1  & 2 & 0.993396 & 0.913409 & 0.898059 \\
-                                             & Approach 2  & 2 & 0.993396 & 0.913409 & 0.898059 \\
-                                             & Approach 3  & 2 & 0.993396 & 0.913409 & 0.898059 \\
-                                             & Approach 4  & 3 & 0.993396 & 0.913409 & 0.898059 \\
+    over \numberofalltournaments tournaments & top 5\% $r$               & 2 & 0.993396 & 0.913409 & 0.898059 \\
+                                             & top 25\% $r$              & 2 & 0.993396 & 0.913409 & 0.898059 \\
+                                             & top 50\% $r$              & 2 & 0.993396 & 0.913409 & 0.898059 \\
+                                             & $r$  \& normalised score  & 3 & 0.993396 & 0.913409 & 0.898059 \\
     \bottomrule
@@
 
-The importance that the features of Table~\ref{table:manual_features} had on
-each random forest model while the perfomances were clustered based on the
-different approaches have been
+The importance that the measures of Table~\ref{table:manual_measures} had on
+each classification task; to which cluster a performance was assigned to based
+on the normalised rank, and their normalised rank and median score have been
 calculated and are given by Figures~\ref{fig:clustering_importance_standard},
@@
 stochastic, make use of game and make use of length have no significant effect,
-and several of the features that are highlighted by the importance are inline with
+and several of the measures that are highted by the importance are inline with
 the correlation results. Moreover, the smoothing parameter \(k\) appears to no
-have a significant effect either. The most important features based on the
+have a significant effect either. The most important measures based on the
 random forest analysis were $C_{r} / C_{median}$ and $C_r / C_{mean}$.
@@
 
-The effect of both these features can be further explored. In
+The effect of both these measures can be further explored. In
 Figure~\ref{fig:mean_median_std} the distributions of \(C_r / C_{\text{mean}}\)
@@
 was the mean/median cooperator of its respective tournament. In comparison,
-Figure~\ref{fig:mean_median_noisy} shows the distributions of the features for
+Figure~\ref{fig:mean_median_noisy} shows the distributions of the measures for
 the winners in noisy tournaments where the mean is at 0.67. Thereupon the winners
@@
 
-In this section the effect of several features, regarding a strategy's behaviour
+In this section the effect of several measures, regarding a strategy's behaviour
 and the tournament in which it participated on its performance were presented.
@@
 vary. Moreover, a strategy with a theory of mind should aim to adapt its behaviour
-based on the mean and median cooperators and should in general not be too
-cooperative.
+based on the mean and median cooperators.
 
@@
 the literature, and they have been accessible due to an open source software
-called the Axelrod-Python library. The software was used to generate a total of
+called Axelrod-Python. The software was used to generate a total of
 \numberofalltournaments computer tournaments results with different number of
@@
 Section~\ref{section:evaluation_of_performance}, covered an analysis of
-performance based on several features associated with a strategy and with the
+performance based on several measures associated with a strategy and with the
 environments it was competing. The results of this analysis showed that a
@@
 used regarding the game had no effect on the strategy's success. The most
-important features have been those that compared the strategy's behaviour to it's
+important factors have been those that compared the strategy's behaviour to it's
 environment. The cooperating ratio of the strategy compared to the mean and
@@
 mind of its environment it would choose to be the median cooperator in standard
-tournaments, to cooperate 10\% of the time the median cooperator did in probabilistic ending tournaments and 
+tournaments, to cooperate 10\% in probabilistic ending tournaments and 
 60\% in noisy and noisy probabilistic
-tournaments. Lastly, if a strategy was aware of the opponents but not of the
-setting of the tournament, a strategy would be more likely to be successful if
+tournaments of the times the median cooperator did. Lastly, if a strategy was aware of the opponents but not of the
+setting on the tournament, a strategy would be more likely to be successful if
 it were to identify the median cooperator and cooperated 67\% of the times that
@@
 \begin{itemize}
-    \item The Axelrod-Python library for IPD simulations~\cite{axelrodproject}.
+    \item The Axelrod library for IPD simulations~\cite{axelrodproject}.
     \item The Matplotlib library for visualisation~\cite{hunter2007matplotlib}.
@@
     \toprule
-feature & feature explanation \\
+measure & measure explanation \\
  \midrule
@@
     \end{center}
-    \caption{The features which are included in the performance evaluation analysis.}\label{table:parameters_summary}
+    \caption{The measures which are included in the performance evaluation analysis.}
 \end{table}
@@
 
-The strategies used in this study which are from Axelrod-Python library version 3.0.0.
+The strategies used in this study which are from Axelrod version 3.0.0
+\cite{axelrodproject}.
 
@@
 
-A graphical representation of the correlation coefficients for the features in
-Table~\ref{table:manual_features}.
+A graphical representation of the correlation coefficients for the measures in
+Table~\ref{table:manual_measures}.
 
@@
         \end{center}
-        \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
+        \caption{Correlation coefficients of measures in Table~\ref{table:manual_measures}
         for standard tournaments}
@@
     \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
+    \caption{Correlation coefficients of measures in Table~\ref{table:manual_measures}
     for noisy tournaments}
@@
     \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
+    \caption{Correlation coefficients of measures in Table~\ref{table:manual_measures}
     for probabilistic ending tournaments}
@@
     \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
+    \caption{Correlation coefficients of measures in Table~\ref{table:manual_measures}
     for noisy probabilistic ending tournaments}
@@
     \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
+    \caption{Correlation coefficients of measures in Table~\ref{table:manual_measures}
     for data set}

### 2020-01-28 paper/perfomances_table.tex
Prepares paper (#13)
* re-run analysis with new data

* clean repo

* move notebooks

* rename files, run black and tweak code

* tests to pytest

* test and implement prepare, process src files

* create clystering analysis script

* update enviroment yml

* add feautures to analysis

* add lines to run on siren

* tweaks to outputs

* add new meausures to analysis

* add probend, noise and turns to cluster analysis

* fix failure

* remove turns as default cluster feauture

* week commit

* write first sections of papers

* fix errors and move tests

* create test file

* tweats to clusterin

@@
 1  &           Evolved FSM 16 &   0.00995 &                    \$e\$ &   0.19388 &           Defector &   0.01429 &               \$\textbackslash phi\$ &   0.30978 \\
-2  &     EvolvedLookerUp2\_2\_2 &   0.01064 &       Tit For 2 Tats &    0.2069 &  Better and Better &   0.01587 &                  \$e\$ &    0.3125 \\
-3  &  Evolved FSM 16 Noise 05 &   0.01667 &         Cycle Hunter &   0.21538 &    Tricky Defector &   0.01875 &                \$\textbackslash pi\$ &   0.31686 \\
-4  &        PSO Gambler 2\_2\_2 &   0.02143 &       Risky QLearner &   0.22222 &          Fortress3 &   0.02174 &    Limited Retaliate &   0.35263 \\
-5  &              Evolved ANN &   0.02878 &          Retaliate 3 &   0.22887 &     Gradual Killer &   0.02532 &     Anti Tit For Tat &   0.35431 \\
-6  &            Evolved ANN 5 &    0.0339 &        Cycler CCCCCD &   0.23507 &         Aggravater &   0.02778 &          Retaliate 3 &   0.35563 \\
-7  &        PSO Gambler 1\_1\_1 &   0.03704 &          Retaliate 2 &   0.23913 &             Raider &   0.03077 &  Limited Retaliate 3 &   0.35563 \\
-8  &            Evolved FSM 4 &   0.04891 &      Defector Hunter &   0.24038 &         Cycler DDC &   0.04545 &            Retaliate &   0.35714 \\
-9  &         PSO Gambler Mem1 &   0.05036 &            Retaliate &   0.24177 &        Hard Prober &   0.05128 &          Retaliate 2 &   0.35767 \\
-10 &                 Winner12 &   0.06011 &  Hard Tit For 2 Tats &      0.25 &         SolutionB1 &   0.06024 &  Limited Retaliate 2 &   0.36134 \\
-11 &             Fool Me Once &    0.0614 &             ShortMem &   0.25286 &      Meta Minority &   0.06077 &             Hopeless &   0.36842 \\
-12 &                      DBS &   0.07143 &  Limited Retaliate 3 &   0.25316 &              Bully &   0.06081 &    Arrogant QLearner &   0.40651 \\
-13 &            DoubleCrosser &     0.072 &    Limited Retaliate &   0.25706 &    Fool Me Forever &    0.0708 &    Cautious QLearner &   0.40909 \\
-14 &              BackStabber &   0.07519 &                \$\textbackslash pi\$ &   0.25801 &             EasyGo &   0.07101 &      Fool Me Forever &   0.41764 \\
+2  &     EvolvedLookerUp2\_2\_2 &   0.01064 &         Tit For 2 Tats &   0.20617 &  Better and Better &   0.01587 &                  \$e\$ &    0.3125 \\
+3  &  Evolved FSM 16 Noise 05 &   0.01667 &  Slow Tit For Two Tats &   0.20962 &    Tricky Defector &   0.01875 &                \$\textbackslash pi\$ &   0.31686 \\
+4  &        PSO Gambler 2\_2\_2 &   0.02143 &           Cycle Hunter &   0.21538 &          Fortress3 &   0.02174 &    Limited Retaliate &   0.35263 \\
+5  &              Evolved ANN &   0.02878 &         Risky QLearner &   0.22222 &     Gradual Killer &   0.02532 &     Anti Tit For Tat &   0.35431 \\
+6  &            Evolved ANN 5 &    0.0339 &            Retaliate 3 &   0.22887 &         Aggravater &   0.02778 &          Retaliate 3 &   0.35563 \\
+7  &        PSO Gambler 1\_1\_1 &   0.03704 &          Cycler CCCCCD &   0.23507 &             Raider &   0.03077 &  Limited Retaliate 3 &   0.35563 \\
+8  &            Evolved FSM 4 &   0.04891 &            Retaliate 2 &   0.23913 &         Cycler DDC &   0.04545 &            Retaliate &   0.35714 \\
+9  &         PSO Gambler Mem1 &   0.05036 &        Defector Hunter &   0.24038 &        Hard Prober &   0.05128 &          Retaliate 2 &   0.35767 \\
+10 &                 Winner12 &   0.06011 &              Retaliate &   0.24177 &         SolutionB1 &   0.06024 &  Limited Retaliate 2 &   0.36134 \\
+11 &             Fool Me Once &    0.0614 &    Hard Tit For 2 Tats &      0.25 &      Meta Minority &   0.06077 &             Hopeless &   0.36842 \\
+12 &                      DBS &   0.07143 &               ShortMem &   0.25286 &              Bully &   0.06081 &    Arrogant QLearner &   0.40651 \\
+13 &            DoubleCrosser &     0.072 &    Limited Retaliate 3 &   0.25316 &    Fool Me Forever &    0.0708 &    Cautious QLearner &   0.40909 \\
+14 &              BackStabber &   0.07519 &      Limited Retaliate &   0.25706 &             EasyGo &   0.07101 &      Fool Me Forever &   0.41764 \\
 \bottomrule

### 2020-01-28 src/cluster_analysis.py

@@ -1,0 +1,283 @@
+import operator
+import os
+import random
+import sys
+
+import dask.array as da
+import dask.dataframe as dd
+import joblib
+import matplotlib
+import matplotlib.pyplot as plt
+import numpy as np
+import pandas as pd
+import seaborn as sns
+from dask.distributed import Client
+from sklearn.ensemble import RandomForestClassifier
+from sklearn.metrics import silhouette_score
+from sklearn.model_selection import train_test_split
+from sklearn.tree import export_graphviz
+
+import dask_ml.cluster
+import lime
+import lime.lime_tabular
+import pydot
+from treeinterpreter import treeinterpreter as ti
+
+matplotlib.use("Agg")
+
+
+def cluster_analysis(data, ddf, columns, upper_n_clusters, num_of_workers):
+    num_of_clusters_to_fit = range(2, upper_n_clusters)
+
+    silhouette_avgs = {}
+    for n_clusters in num_of_clusters_to_fit:
+        kmeans = dask_ml.cluster.KMeans(
+            n_clusters=n_clusters, random_state=0
+        ).fit(data)
+        ddf["Clusters: n = %s" % n_clusters] = dd.from_dask_array(
+            kmeans.labels_
+        )
+
+        with joblib.parallel_backend("dask", n_jobs=num_of_workers):
+            silhouette_avg = silhouette_score(
+                data, kmeans.labels_, sample_size=int(len(data) * 0.001)
+            )
+            silhouette_avgs["Clusters: n = %s" % n_clusters] = silhouette_avg
+
+    return ddf, silhouette_avgs, num_of_clusters_to_fit
+
+
+def draw_clusters_plot(sample, upper_n_clusters, output_directory):
+
+    fig, axes = plt.subplots(
+        nrows=1, ncols=upper_n_clusters - 2, figsize=(10, 4)
+    )
+
+    x = sample["Normalized_Rank"].compute()
+    y = sample["Median_score"].compute()
+
+    for i, ax in enumerate(axes):
+        ax.scatter(x, y, c=sample["Clusters: n = %s" % (i + 2)].compute())
+
+    fig.text(0.5, 0.04, r"$r$", ha="center", weight="bold")
+    fig.text(
+        0.075,
+        0.5,
+        "median score",
+        va="center",
+        rotation="vertical",
+        weight="bold",
+    )
+
+    plt.savefig("%sclusters_plots.pdf" % output_directory, bbox_inches="tight")
+    plt.close()
+
+
[…]

### 2020-01-28 src/pbs_file_generator.py

@@ -1,24 +1,26 @@
+import os
+
+directory_name = "pbs"
+
+try:
+    os.mkdir(directory_name)
+    print("Directory ", directory_name, " Created")
+except FileExistsError:
+    pass
+
 submit_script = ""
-for name, min_seed, max_seed in [("0-999", 0, 1000),
-                                 ("1000-1999", 1000, 2000),
-                                 ("2000-2999", 2000, 3000),
-                                 ("3000-3999", 3000, 4000),
-                                 ("4000-4999", 4000, 5000),
-                                 ("5000-5999", 5000, 6000),
-                                 ("6000-6999", 6000, 7000),
-                                 ("7000-7999", 7000, 8000),
-                                 ("8000-8999", 8000, 9000),
-                                 ("9000-9999", 9000, 10000),
-                                 ("10000-10999", 10000, 11000),
-                                 ("11000-21999", 11000, 12000),
-                                 ("12000-12999", 12000, 13000),
-                                 ("13000-13999", 13000, 14000),
-                                 ("14000-14999", 14000, 15000),
-                                 ("15000-15999", 15000, 16000),
-                                 ("16000-16999", 16000, 17000),
-                                 ("17000-17999", 17000, 18000),
-                                 ("18000-18999", 18000, 19000),
-                                 ("19000-19999", 19000, 20000)]:
+for name, min_seed, max_seed in [
+    ("0-999", 0, 1000),
+    ("1000-1999", 1000, 2000),
+    ("2000-2999", 2000, 3000),
+    ("3000-3999", 3000, 4000),
+    ("4000-4999", 4000, 5000),
+    ("5000-5999", 5000, 6000),
+    ("6000-6999", 6000, 7000),
+    ("7000-7999", 7000, 8000),
+    ("8000-8999", 8000, 9000),
+    ("9000-9999", 9000, 10000),
+]:
 
     pbs_file = """#!/bin/bash
 #PBS -q workq
@@ -34,13 +36,15 @@ export MPLBACKEND="agg"
 # Run std
 cd /home/c1569433/rsc/axlml/src
 /home/c1569433/anaconda3/envs/axlml/bin/python main.py /scratch/c1569433/axlml/data/ {} {} 
-""".format(name, name, name, min_seed, max_seed)
+""".format(
+        name, name, name, min_seed, max_seed
+    )
 
-    with open("pbs/{}.pbs".format(name), 'w') as f:
[…]

### 2020-01-28 src/plot.py

@@ -1,0 +1,110 @@
+import matplotlib.pyplot as plt
+import seaborn as sns
+import numpy as np
+
+c = sns.xkcd_rgb["denim blue"]
+
+
+features_labels = {
+    "CC_to_C_rate": "$CC$ to $C$ rate",
+    "CD_to_C_rate": "$CD$ to $C$ rate",
+    "DC_to_C_rate": "$DC$ to $C$ rate",
+    "DD_to_C_rate": "$DD$ to $C$ rate",
+    "SSE": "SSE",
+    "Makes_use_of_game": "Make use of game",
+    "Makes_use_of_length": "Make use of length",
+    "Stochastic": "stochastic",
+    "Cooperation_rating": r"$C_r$",
+    "Cooperation_rating_max": r"$C_{max}$",
+    "Cooperation_rating_min": r"$C_{min}$",
+    "Cooperation_rating_median": r"$C_{median}$",
+    "Cooperation_rating_mean": r"$C_{mean}$",
+    "Cooperation_rating_comp_to_max": r"$C_r$ / $C_{max}$ ",
+    "Cooperation_rating_comp_to_min": r"$C_r$ / $C_{min}$",
+    "Cooperation_rating_comp_to_median": r"$C_r$ / $C_{median}$",
+    "Cooperation_rating_comp_to_mean": r"$C_r$ / $C_{mean}$",
+    "turns": r"$n$",
+    "noise": r"$p_n$",
+    "probend": r"$p_e$",
+    "Normalized_Rank": r"$r$",
+    "Median_score": "Median score",
+    "size": r"$N$",
+    "memory_usage": "memory usage",
+    "repetitions": r"$k$",
+}
+
+
+def violin_plot(df, x, y, xlabel, ylabel, title, size=10):
+    join_plot = sns.jointplot(
+        x=x,
+        y=y,
+        data=df,
+        kind="reg",
+        stat_func=None,
+        xlim=(0, 1),
+        ylim=(0, 1),
+        scatter_kws={"s": size},
+    )
+
+    plt.subplots_adjust(top=0.95)
+    join_plot.fig.suptitle(title)
+    join_plot.set_axis_labels(xlabel, ylabel)
+
+    plt.show()
+    return join_plot
+
+
+def r_distribution(
+    x,
+    y1,
+    y2,
+    y3,
+    y4,
+    title,
+    label1="max",
+    label2="min",
+    label3="mean",
[…]

### 2020-01-28 src/prepare_data.py

@@ -1,0 +1,149 @@
+import glob
+import sys
+
+import numpy as np
+import pandas as pd
+
+import axelrod as axl
+
+
+def get_normalised_rank(row):
+    return row["Rank"] / (row["size"] - 1)
+
+
+def get_parameters_data_frame(directory):
+    """
+    A function for reading in the parameters data frame.
+    """
+    csv_files = glob.glob("{}parameters_*-*.csv".format(directory))
+    dfs = [pd.read_csv(f) for f in csv_files]
+    dfs = [
+        df[["noise", "probend", "repetitions", "seed", "size", "turns"]]
+        for df in dfs
+    ]
+    df = pd.concat(dfs, ignore_index=True)
+    df = df.drop_duplicates()
+
+    return df.sort_values(["seed"]).reset_index()
+
+
+class Reader:
+    """
+    A class for retrieving the four data frames corresponding to each
+    row of the parameters csv file.
+    """
+
+    def __init__(self, row, directory=None):
+        if directory:
+            self.directory = directory
+        else:
+            self.directory = "data/raw_data/"
+        self.seed = row.seed
+        self.size = row["size"]
+        self.repetitions = row.repetitions
+        self.noise_param = row.noise
+        self.probend_param = row.probend
+        self.turns_param = row.turns
+
+    def get_noise_df(self):
+        noise = pd.read_csv(
+            "{}noise-data/{}.csv".format(self.directory, int(self.seed))
+        )
+        noise["noise"] = self.noise_param
+        noise["turns"] = self.turns_param
+
+        return noise
+
+    def get_probend_noise_df(self):
+        probend_noise = pd.read_csv(
+            "{}noise-probend-data/{}.csv".format(self.directory, int(self.seed))
+        )
+        probend_noise["noise"] = self.noise_param
+        probend_noise["probend"] = self.probend_param
+
+        return probend_noise
+
+    def get_standard_df(self):
+        std = pd.read_csv(
+            "{}std-data/{}.csv".format(self.directory, int(self.seed))
+        )
+        std["turns"] = self.turns_param
+        return std
+
+    def get_proend_df(self):
+        probend = pd.read_csv(
+            "{}probend-data/{}.csv".format(self.directory, int(self.seed))
+        )
+        probend["probend"] = self.probend_param
+
+        return probend
+
+    def common_rows(self, df):
+        df["repetitions"] = self.repetitions
+        df["size"] = self.size
+        df["seed"] = self.seed
[…]

### 2020-01-28 src/process_data.py

@@ -1,0 +1,208 @@
+import sys
+
+import numpy as np
+import pandas as pd
+
+import axelrod as axl
+import dask_ml.cluster
+
+
+def get_least_squares(vector, game=axl.game.Game()):
+    """
+    Obtain the least squares directly
+    
+    Returns:
+    
+    - xstar
+    - residual
+    """
+
+    R, P, S, T = game.RPST()
+
+    C = np.array([[R - P, R - P], [S - P, T - P], [T - P, S - P], [0, 0]])
+
+    tilde_p = np.array([vector[0] - 1, vector[1] - 1, vector[2], vector[3]])
+
+    xstar = np.linalg.inv(C.transpose() @ C) @ C.transpose() @ tilde_p
+
+    SSError = tilde_p.transpose() @ tilde_p - tilde_p @ C @ xstar
+
+    return SSError
+
+
+def get_memory_percentage(row):
+    if np.isinf(row["Memory_depth"]):
+        return 1
+    if row["Memory_depth"] == 0:
+        return 0
+    return row["Memory_depth"] / row["turns"]
+
+
+def get_strategies_properties():
+    """
+     A function that returns a data frame with the strategies of the Axelrod
+     library and for each strategy it's property.
+    """
+    axl_strategies = pd.DataFrame(
+        columns=[
+            "Name",
+            "Stochastic",
+            "Memory_depth",
+            "Makes_use_of_game",
+            "Makes_use_of_length",
+        ]
+    )
+
+    for i, strategy in enumerate(axl.strategies):
+        use_of_game = 0
+        use_of_length = 0
+        name = strategy().name
+
+        if "game" in strategy().classifier["makes_use_of"]:
+            use_of_game = 1
+        if "length" in strategy().classifier["makes_use_of"]:
+            use_of_length = 1
+        if "Hard Go By Majority:" in name:
+            name = "".join(name.split(":"))
+        if "Soft Go By Majority:" in name:
+            name = "".join(name.split(":"))
+        axl_strategies.loc[i] = [
+            name,
+            int(strategy().classifier["stochastic"]),
+            strategy().classifier["memory_depth"],
+            use_of_game,
+            use_of_length,
+        ]
+    return axl_strategies
+
+
+def get_error_for_row(row):
+    columns_for_sse = [
+        "CC_to_C_rate",
+        "CD_to_C_rate",
+        "DC_to_C_rate",
[…]

### 2020-01-28 tests/test_prepare_data.py

@@ -1,0 +1,153 @@
+import imp
+
+import numpy as np
+import pandas
+
+import axelrod
+
+prepare_data = imp.load_source("prepare_data", "src/prepare_data.py")
+parameters_df = prepare_data.get_parameters_data_frame(
+    directory="data/raw_data/"
+)
+
+
+def test_parameters_data_frame():
+    expected_columns = [
+        "index",
+        "noise",
+        "probend",
+        "repetitions",
+        "seed",
+        "size",
+        "turns",
+    ]
+    assert isinstance(parameters_df, pandas.DataFrame)
+    assert all(
+        [
+            column == expected_column
+            for column, expected_column in zip(
+                parameters_df.columns, expected_columns
+            )
+        ]
+    )
+
+
+def test_get_normalised_rank():
+    row = {"Rank": 1, "size": 11}
+    normalised_rank = prepare_data.get_normalised_rank(row)
+
+    assert normalised_rank == 0.1
+
+
+def test_reader():
+    row = parameters_df.sample(n=1)
+    reader = prepare_data.Reader(row)
+
+    assert reader.noise_param.values[0] == row.noise.values[0]
+
+    assert reader.probend_param.values[0] == row.probend.values[0]
+    assert reader.seed.values[0] == row.seed.values[0]
+    assert reader.size.values[0] == row["size"].values[0]
+    assert reader.turns_param.values[0] == row.turns.values[0]
+
+
+def test_get_noise_df():
+    row = parameters_df.sample(n=1)
+    reader = prepare_data.Reader(row, "data/raw_data/")
+
+    noise = reader.get_noise_df()
+    assert isinstance(noise, pandas.DataFrame)
+    assert all(
+        [
+            column in noise.columns.values
+            for column in [
+                "Rank",
+                "Name",
+                "Median_score",
+                "Cooperation_rating",
+                "Wins",
+                "CC_rate",
+                "CD_rate",
+                "DC_rate",
+                "DD_rate",
+                "noise",
+                "turns",
+            ]
+        ]
+    )
+
+
+def test_get_probend_noise_df():
+    row = parameters_df.sample(n=1)
+    reader = prepare_data.Reader(row, "data/raw_data/")
+
+    probend_noise = reader.get_probend_noise_df()
+    assert isinstance(probend_noise, pandas.DataFrame)
+    assert all(
+        [
+            column in probend_noise.columns.values
+            for column in [
+                "Rank",
+                "Name",
+                "Median_score",
+                "Cooperation_rating",
+                "Wins",
[…]

### 2020-01-28 tests/test_process_data.py

@@ -1,0 +1,72 @@
+import imp
+
+import numpy as np
+import pandas as pd
+
+import axelrod
+
+process_data = imp.load_source("processe_data", "src/process_data.py")
+
+
+def test_strategies_properties():
+    df = process_data.get_strategies_properties()
+
+    assert isinstance(df, pd.DataFrame)
+    assert len(df) == len(axelrod.strategies)
+
+    for memory_depth in df["Memory_depth"]:
+        assert isinstance(memory_depth, float)
+
+    for use_of_game in df["Makes_use_of_game"]:
+        assert isinstance(use_of_game, int)
+
+    for use_of_length in df["Makes_use_of_length"]:
+        assert isinstance(use_of_length, int)
+
+
+def test_get_error_for_row():
+    row = {
+        "CC_to_C_rate": 0,
+        "CD_to_C_rate": 0,
+        "DC_to_C_rate": 0,
+        "DD_to_C_rate": 0,
+    }
+    error = process_data.get_error_for_row(row)
+    assert error < 0.1
+
+
+def test_fix_name():
+    row = {"Name": "Tit For Tat: D"}
+    fixed_name = process_data.fix_name(row)
+
+    assert fixed_name == "Tit For Tat"
+
+
+def get_cooporation_rating_compared_to_max(row):
+    row = {"Cooperation_rating": 0.2, "Cooperation_rating_max": 0.8}
+
+    assert process_data.get_cooporation_rating_compared_to_max(row) == 0.25
+
+
+def get_cooporation_rating_compared_to_median(row):
+    row = {"Cooperation_rating": 0.2, "Cooperation_rating_median": 0.8}
+
+    assert process_data.get_cooporation_rating_compared_to_median(row) == 0.25
+
+
+def get_cooporation_rating_compared_to_mean(row):
+    row = {"Cooperation_rating": 0.2, "Cooperation_rating_mean": 0.8}
+
+    assert process_data.get_cooporation_rating_compared_to_mean(row) == 0.25
+
+
+def get_cooporation_rating_compared_to_min(row):
+    row = {"Cooperation_rating": 0.2, "Cooperation_rating_min": 0.4}
+
+    assert process_data.get_cooporation_rating_compared_to_max(row) == 0.25
+
+
+def get_cooporation_rating_compared_to_min(row):
+    row = {"Cooperation_rating": 0.2, "Cooperation_rating_min": 0.0}
+
+    assert process_data.get_cooporation_rating_compared_to_max(row) == 0.0

### 2020-01-31 paper/main.tex
fixes typos and table with r squares

--- 2020-01-16 paper/main.tex
@@
 being strategies that have been contributed specifically to the package. This
-paper make use of \numberofstrategies strategies implemented in version 3.0.0. A
+paper makes use of \numberofstrategies strategies implemented in version 3.0.0. A
 list of the strategies is given in the Appendix~\ref{app:list_of_players}.
@@
 Raider~\cite{Ashlock2014} and Solution B1~\cite{Ashlock2014}, which are
-strategies based on finite state automata introduced by Daniel and Wendy
+strategies based on finite state automata introduced by Daniel Ashlock and Wendy
 Ashlock. These strategies have been evolved using reinforcement learning, however,
@@
 from ~\cite{prison}), Bully (Reverse Tit For Tat)~\cite{Nachbar1992} and
-Defector. Thus, it's surprisingly that EasyGo and Fool Me Forever which are
-strategies that will defect until their opponent defect, then they will cooperate
+Defector. Thus, it's surprising that EasyGo and Fool Me Forever which are
+strategies that will defect until their opponent defects, then they will cooperate
 until the end, ranked $14^{\text{th}}$ and $15^{\text{th}}$. Upon inspection,
@@
 on teams. The results of \numberofalltournaments tournaments used in this work imply the following:
-they is not a single type of strategy which can performance well in any IPD interaction.
+they is not a single type of strategy performs well in any IPD interaction.
 
@@
 tournaments the correlations coefficients have a larger values, indicating a
-stronger effect. Thus a strategy will be punished more by it's cooperative
+stronger effect. Thus a strategy will be punished more by its cooperative
 behaviour in probabilistic ending environments, this was seen in Section~\ref{section:evaluation_of_performance}
@@
     \midrule
-    noisy     & Approach 1  & 2 & 0.996677  & 0.950572 & 0.935383\\
-              & Approach 2  & 2 & 0.996677  & 0.950572 & 0.935383\\
-              & Approach 3  & 2 & 0.996677  & 0.950572 & 0.935383\\
-              & Approach 4  & 3 & 0.996677  & 0.950572 & 0.935383\\
+    noisy     & Approach 1  & 2 & 0.997786  & 0.972229    & 0.968332\\
+              & Approach 2  & 2 & 0.997442  & 0.963254    & 0.955219\\
+              & Approach 3  & 2 & 0.997152  & 0.953164    & 0.940528\\
+              & Approach 4  & 3 & 0.996923  & 0.950728    & 0.935444\\
     \midrule
-    probabilistic ending & Approach 1  & 2 & 0.999592  & 0.995128 & 0.992819 \\
-                         & Approach 2  & 2 & 0.999592  & 0.995128 & 0.992819 \\
-                         & Approach 3  & 2 & 0.999592  & 0.995128 & 0.992819 \\
-                         & Approach 4  & 2 & 0.999592  & 0.995128 & 0.992819 \\
+    probabilistic ending & Approach 1 & 2 & 0.997909   & 0.981490  & 0.978120 \\
+                         & Approach 2 & 2 & 0.997883   & 0.973492  & 0.967150 \\
+                         & Approach 3 & 2 & 0.990448   & 0.890068  & 0.875822 \\
+                         & Approach 4 & 2 & 0.999636   & 0.995183  & 0.992809 \\
     \midrule
-    noisy probabilistic ending & Approach 1  & 2 & 0.990490  & 0.813905 & 0.791418\\
-                               & Approach 2  & 2 & 0.990490  & 0.813905 & 0.791418\\
-                               & Approach 3  & 2 & 0.990490  & 0.813905 & 0.791418\\
-                               & Approach 4  & 4 & 0.990490  & 0.813905 & 0.791418\\
+    noisy probabilistic ending & Approach 1  & 2 & 0.995347 & 0.957846   & 0.952353\\
+                               & Approach 2  & 2 & 0.992813 & 0.909346   & 0.898613\\
+                               & Approach 3  & 2 & 0.990579 & 0.824794   & 0.806540\\
+                               & Approach 4  & 4 & 0.989465 & 0.841652   & 0.824052\\
     \midrule
-    over \numberofalltournaments tournaments & Approach 1  & 2 & 0.993396 & 0.913409 & 0.898059 \\
-                                             & Approach 2  & 2 & 0.993396 & 0.913409 & 0.898059 \\
-                                             & Approach 3  & 2 & 0.993396 & 0.913409 & 0.898059 \\
-                                             & Approach 4  & 3 & 0.993396 & 0.913409 & 0.898059 \\
+    over \numberofalltournaments tournaments   & Approach 1 & 2 & 0.997271& 0.972914& 0.969198 \\
+                                               & Approach 2 & 2 & 0.996323& 0.951194& 0.940563 \\
+                                               & Approach 3 & 2 & 0.993707& 0.906941& 0.891532 \\
+                                               & Approach 4 & 3 & 0.993556& 0.913335& 0.898453 \\
     \bottomrule
@@
 another and the mechanism behind the winning strategies were all different.
-Even strategies designed to do good in one setting did better in others.
-On the whole ... (the ipd interactions are unique and there is no winning
-strategy) %TODO help from Vince
-
-Section~\ref{section:evaluation_of_performance}, covered an analysis of
+Even strategies designed to perform well in one setting were demonstrated to be
+better in others.
+
+Section~\ref{section:evaluation_of_performance} covered an analysis of
 performance based on several features associated with a strategy and with the
-environments it was competing. The results of this analysis showed that a
+environments in which it was competing. The results of this analysis showed that a
 strategy's characteristics such as whether or not it's stochastic, and the information it
 used regarding the game had no effect on the strategy's success. The most
-important features have been those that compared the strategy's behaviour to it's
+important features have been those that compared the strategy's behaviour to its
 environment. The cooperating ratio of the strategy compared to the mean and
@@
 $DD$ to $C$ rate            & The probability a strategy will cooperate after a mutual defection\\
-$p_n$                       & The probability of a player's action being flip at each interaction \\
+$p_n$                       & The probability of a player's action being flipped at each interaction \\
 $n$                         & The number of turns \\

### 2020-02-03 paper/main.tex
tweak abstract

@@
 performance of strategies in the game for years. The results of the literature,
-however, have been relying on the performance of specific strategies in a finite
-number of tournaments, whereas this manuscript evaluates
-\numberofstrategies strategies' effectiveness in more than 40000 tournaments.
-The top ranked strategies are presented, and moreover, the impact of features on
-their success are analysed using machine learning techniques. The analysis
-determines that the cooperating ratio of a
-strategy in a given tournament compared to the mean and median cooperator is the
-most important feature. The conclusions are distinct for different types of
-tournaments. For instance a strategy with a theory of mind would aim to be the mean/median
-cooperator in standard tournaments, whereas in tournaments with probabilistic
-ending it would aim to cooperate 10\% of the times the median cooperator did.
+however, have been relying on a small number of somewhat arbitrarily selected
+strategies in a very small number of tournaments,
+casting doubt on the generalizability of results from statistical perspective.
+This manuscript evaluates \numberofstrategies strategies in more than 40000
+tournaments, presents the top performing strategies, and analyzes their
+salient features.
+The outcomes support that a strategy with a theory of mind should adjust it’s
+cooperations based on the mean/median cooperator of its environment to be
+successful; the adjustments are distinct for different tournament types.
 \end{abstract}

### 2020-02-03 paper/perfomances_table.tex
add to the performance table for p_e and p_n smaller than 0.1

--- 2019-10-24 paper/perfomances_table.tex
@@
-\begin{tabular}{lllllllll}
+\begin{tabular}{lllllllllllll}
 \toprule
-{} &                     Name & \$\textbackslash bar\{r\}\$ &                 Name & \$\textbackslash bar\{r\}\$ &               Name & \$\textbackslash bar\{r\}\$ &                 Name & \$\textbackslash bar\{r\}\$ \\
+{} &                     Name & $ \bar\{r\}$  &                   Name & $ \bar\{r\}$  &                        Name & $ \bar\{r\}$  &               Name & $ \bar\{r\}$  &                       Name & $ \bar\{r\}$  &                 Name & $ \bar\{r\}$  \\
 \midrule
-0  &            Evolved HMM 5 &   0.00667 &               Grumpy &    0.1402 &          Fortress4 &   0.01266 &           Alternator &    0.3037 \\
-1  &           Evolved FSM 16 &   0.00995 &                  \$e\$ &   0.19388 &           Defector &   0.01429 &               \$\textbackslash phi\$ &   0.30978 \\
-2  &     EvolvedLookerUp2\_2\_2 &   0.01064 &       Tit For 2 Tats &    0.2069 &  Better and Better &   0.01587 &                  \$e\$ &    0.3125 \\
-3  &  Evolved FSM 16 Noise 05 &   0.01667 &         Cycle Hunter &   0.21538 &    Tricky Defector &   0.01875 &                \$\textbackslash pi\$ &   0.31686 \\
-4  &        PSO Gambler 2\_2\_2 &   0.02143 &       Risky QLearner &   0.22222 &          Fortress3 &   0.02174 &    Limited Retaliate &   0.35263 \\
-5  &              Evolved ANN &   0.02878 &          Retaliate 3 &   0.22887 &     Gradual Killer &   0.02532 &     Anti Tit For Tat &   0.35431 \\
-6  &            Evolved ANN 5 &    0.0339 &        Cycler CCCCCD &   0.23507 &         Aggravater &   0.02778 &          Retaliate 3 &   0.35563 \\
-7  &        PSO Gambler 1\_1\_1 &   0.03704 &          Retaliate 2 &   0.23913 &             Raider &   0.03077 &  Limited Retaliate 3 &   0.35563 \\
-8  &            Evolved FSM 4 &   0.04891 &      Defector Hunter &   0.24038 &         Cycler DDC &   0.04545 &            Retaliate &   0.35714 \\
-9  &         PSO Gambler Mem1 &   0.05036 &            Retaliate &   0.24177 &        Hard Prober &   0.05128 &          Retaliate 2 &   0.35767 \\
-10 &                 Winner12 &   0.06011 &  Hard Tit For 2 Tats &      0.25 &         SolutionB1 &   0.06024 &  Limited Retaliate 2 &   0.36134 \\
-11 &             Fool Me Once &    0.0614 &             ShortMem &   0.25286 &      Meta Minority &   0.06077 &             Hopeless &   0.36842 \\
-12 &                      DBS &   0.07143 &  Limited Retaliate 3 &   0.25316 &              Bully &   0.06081 &    Arrogant QLearner &   0.40651 \\
-13 &            DoubleCrosser &     0.072 &    Limited Retaliate &   0.25706 &    Fool Me Forever &    0.0708 &    Cautious QLearner &   0.40909 \\
-14 &              BackStabber &   0.07519 &                \$\textbackslash pi\$ &   0.25801 &             EasyGo &   0.07101 &      Fool Me Forever &   0.41764 \\
+0  &            Evolved HMM 5 &     0.007 &                 Grumpy &      0.14 &                         DBS &         0 &          Fortress4 &     0.013 &             Evolved FSM 16 &         0 &           Alternator &     0.304 \\
+1  &           Evolved FSM 16 &      0.01 &                    $ e$  &     0.194 &     Evolved FSM 16 Noise 05 &     0.008 &           Defector &     0.014 &    Evolved FSM 16 Noise 05 &     0.013 &               $ \textbackslash phi$  &      0.31 \\
+2  &     EvolvedLookerUp2 2 2 &     0.011 &         Tit For 2 Tats &     0.206 &      Evolved ANN 5 Noise 05 &     0.013 &  Better and Better &     0.016 &                       MEM2 &     0.027 &                  $ e$  &     0.312 \\
+3  &  Evolved FSM 16 Noise 05 &     0.017 &  Slow Tit For Two Tats &      0.21 &                 BackStabber &     0.024 &    Tricky Defector &     0.019 &              Evolved HMM 5 &     0.044 &                $ \textbackslash pi$  &     0.317 \\
+4  &        PSO Gambler 2 2 2 &     0.021 &           Cycle Hunter &     0.215 &               DoubleCrosser &     0.025 &          Fortress3 &     0.022 &       EvolvedLookerUp2 2 2 &     0.049 &    Limited Retaliate &     0.353 \\
+5  &              Evolved ANN &     0.029 &         Risky QLearner &     0.222 &               Evolved ANN 5 &     0.028 &     Gradual Killer &     0.025 &       Spiteful Tit For Tat &      0.06 &     Anti Tit For Tat &     0.354 \\
+6  &            Evolved ANN 5 &     0.034 &            Retaliate 3 &     0.229 &                 Evolved ANN &     0.038 &         Aggravater &     0.028 &           Nice Meta Winner &     0.068 &  Limited Retaliate 3 &     0.356 \\
+7  &        PSO Gambler 1 1 1 &     0.037 &          Cycler CCCCCD &     0.235 &        Spiteful Tit For Tat &     0.051 &             Raider &     0.031 &         NMWE Finite Memory &     0.069 &          Retaliate 3 &     0.356 \\
+8  &            Evolved FSM 4 &     0.049 &            Retaliate 2 &     0.239 &               Evolved HMM 5 &     0.051 &         Cycler DDC &     0.045 &         NMWE Deterministic &      0.07 &            Retaliate &     0.357 \\
+9  &         PSO Gambler Mem1 &      0.05 &        Defector Hunter &      0.24 &              Level Punisher &     0.052 &        Hard Prober &     0.051 &                    Grudger &      0.07 &          Retaliate 2 &     0.358 \\
+10 &                 Winner12 &      0.06 &              Retaliate &     0.242 &                   Omega TFT &     0.059 &         SolutionB1 &      0.06 &           NMWE Long Memory &     0.074 &  Limited Retaliate 2 &     0.361 \\
+11 &             Fool Me Once &     0.061 &    Hard Tit For 2 Tats &      0.25 &                Fool Me Once &     0.059 &      Meta Minority &     0.061 &  Nice Meta Winner Ensemble &     0.076 &             Hopeless &     0.368 \\
+12 &                      DBS &     0.071 &    Limited Retaliate 3 &     0.253 &  PSO Gambler 2 2 2 Noise 05 &     0.067 &              Bully &     0.061 &       EvolvedLookerUp1 1 1 &     0.077 &    Arrogant QLearner &     0.407 \\
+13 &            DoubleCrosser &     0.072 &               ShortMem &     0.253 &              Evolved FSM 16 &     0.078 &             EasyGo &     0.071 &            NMWE Memory One &      0.08 &    Cautious QLearner &     0.409 \\
+14 &              BackStabber &     0.075 &      Limited Retaliate &     0.257 &                  EugineNier &      0.08 &    Fool Me Forever &     0.071 &                   Winner12 &     0.085 &      Fool Me Forever &     0.418 \\
 \bottomrule

### 2020-02-03 paper/top_perfomances.tex
add to the performance table for p_e and p_n smaller than 0.1

--- 2019-10-24 paper/top_perfomances.tex
@@
-\begin{tabular}{lggllggllr}
+\begin{tabular}{lggllggllggllr}
 \toprule
-& \multicolumn{2}{g}{Standard} & \multicolumn{2}{c}{Noisy} & \multicolumn{2}{g}{Probabilistic ending} &  \multicolumn{2}{c}{Noisy probabilistic ending} \\
+& \multicolumn{2}{g}{Standard} & \multicolumn{2}{c}{Noisy} &  \multicolumn{2}{g}{Noisy (\(p_n < 0.1\))} & \multicolumn{2}{c}{Probabilistic ending} & \multicolumn{2}{g}{Probabilistic ending (\(p_e < 0.1\))} &  \multicolumn{2}{c}{Noisy probabilistic ending} \\
 \midrule
-& Name & $\bar{r}$ &                 Name & $\bar{r}$ &               Name & $\bar{r}$ &                 Name & $\bar{r}$ \\
+& Name & $\bar{r}$ &                 Name & $\bar{r}$ &               Name & $\bar{r}$ &                 Name & $\bar{r}$ &                 Name & $\bar{r}$ &                 Name & $\bar{r}$ \\
 \midrule
-1 &           Evolved HMM 5 &   0.00667 &               Grumpy &    0.1402 &          Fortress4 &   0.01266 &           Alternator &    0.3037 \\
-2 &          Evolved FSM 16 &   0.00995 &                  $e$ &   0.19388 &           Defector &   0.01429 &               $\phi$ &   0.30978 \\
-3 &    EvolvedLookerUp2 2 2 &   0.01064 &       Tit For 2 Tats &    0.2069 &  Better and Better &   0.01587 &                  $e$ &    0.3125 \\
-4 & Evolved FSM 16 Noise 05 &   0.01667 &         Cycle Hunter &   0.21538 &    Tricky Defector &   0.01875 &                $\pi$ &   0.31686 \\
-5 &       PSO Gambler 2 2 2 &   0.02143 &       Risky QLearner &   0.22222 &          Fortress3 &   0.02174 &    Limited Retaliate &   0.35263 \\
-6 &             Evolved ANN &   0.02878 &          Retaliate 3 &   0.22887 &     Gradual Killer &   0.02532 &     Anti Tit For Tat &   0.35431 \\
-7 &           Evolved ANN 5 &    0.0339 &        Cycler CCCCCD &   0.23507 &         Aggravater &   0.02778 &          Retaliate 3 &   0.35563 \\
-8 &       PSO Gambler 1 1 1 &   0.03704 &          Retaliate 2 &   0.23913 &             Raider &   0.03077 &  Limited Retaliate 3 &   0.35563 \\
-9 &           Evolved FSM 4 &   0.04891 &      Defector Hunter &   0.24038 &         Cycler DDC &   0.04545 &            Retaliate &   0.35714 \\
-10 &        PSO Gambler Mem1 &   0.05036 &            Retaliate &   0.24177 &        Hard Prober &   0.05128 &          Retaliate 2 &   0.35767 \\
-11 &                Winner12 &   0.06011 &  Hard Tit For 2 Tats &      0.25 &         SolutionB1 &   0.06024 &  Limited Retaliate 2 &   0.36134 \\
-12 &            Fool Me Once &    0.0614 &             ShortMem &   0.25286 &      Meta Minority &   0.06077 &             Hopeless &   0.36842 \\
-13 &                     DBS &   0.07143 &  Limited Retaliate 3 &   0.25316 &              Bully &   0.06081 &    Arrogant QLearner &   0.40651 \\
-14 &           DoubleCrosser &     0.072 &    Limited Retaliate &   0.25706 &    Fool Me Forever &    0.0708 &    Cautious QLearner &   0.40909 \\
-15 &             BackStabber &   0.07519 &                $\pi$ &   0.25801 &             EasyGo &   0.07101 &      Fool Me Forever &   0.41764 \\
+0  &            Evolved HMM 5 &     0.007 &                 Grumpy &     0.140 &                         DBS &     0.000 &          Fortress4 &     0.013 &             Evolved FSM 16 &     0.000 &           Alternator &     0.304 \\
+1  &           Evolved FSM 16 &     0.010 &                    $e$ &     0.194 &     Evolved FSM 16 Noise 05 &     0.008 &           Defector &     0.014 &    Evolved FSM 16 Noise 05 &     0.013 &              $\phi$  &     0.310 \\
+2  &     EvolvedLookerUp2 2 2 &     0.011 &         Tit For 2 Tats &     0.206 &      Evolved ANN 5 Noise 05 &     0.013 &  Better and Better &     0.016 &                       MEM2 &     0.027 &                $e$   &     0.312 \\
+3  &  Evolved FSM 16 Noise 05 &     0.017 &  Slow Tit For Two Tats &     0.210 &                 BackStabber &     0.024 &    Tricky Defector &     0.019 &              Evolved HMM 5 &     0.044 &               $\pi$  &     0.317 \\
+4  &        PSO Gambler 2 2 2 &     0.021 &           Cycle Hunter &     0.215 &               DoubleCrosser &     0.025 &          Fortress3 &     0.022 &       EvolvedLookerUp2 2 2 &     0.049 &    Limited Retaliate &     0.353 \\
+5  &              Evolved ANN &     0.029 &         Risky QLearner &     0.222 &               Evolved ANN 5 &     0.028 &     Gradual Killer &     0.025 &       Spiteful Tit For Tat &     0.060 &     Anti Tit For Tat &     0.354 \\
+6  &            Evolved ANN 5 &     0.034 &            Retaliate 3 &     0.229 &                 Evolved ANN &     0.038 &         Aggravater &     0.028 &           Nice Meta Winner &     0.068 &  Limited Retaliate 3 &     0.356 \\
+7  &        PSO Gambler 1 1 1 &     0.037 &          Cycler CCCCCD &     0.235 &        Spiteful Tit For Tat &     0.051 &             Raider &     0.031 &         NMWE Finite Memory &     0.069 &          Retaliate 3 &     0.356 \\
+8  &            Evolved FSM 4 &     0.049 &            Retaliate 2 &     0.239 &               Evolved HMM 5 &     0.051 &         Cycler DDC &     0.045 &         NMWE Deterministic &     0.070 &            Retaliate &     0.357 \\
+9  &         PSO Gambler Mem1 &     0.050 &        Defector Hunter &     0.240 &              Level Punisher &     0.052 &        Hard Prober &     0.051 &                    Grudger &     0.070 &          Retaliate 2 &     0.358 \\
+10 &                 Winner12 &     0.060 &              Retaliate &     0.242 &                   Omega TFT &     0.059 &         SolutionB1 &     0.060 &           NMWE Long Memory &     0.074 &  Limited Retaliate 2 &     0.361 \\
+11 &             Fool Me Once &     0.061 &    Hard Tit For 2 Tats &     0.250 &                Fool Me Once &     0.059 &      Meta Minority &     0.061 &  Nice Meta Winner Ensemble &     0.076 &             Hopeless &     0.368 \\
+12 &                      DBS &     0.071 &    Limited Retaliate 3 &     0.253 &  PSO Gambler 2 2 2 Noise 05 &     0.067 &              Bully &     0.061 &       EvolvedLookerUp1 1 1 &     0.077 &    Arrogant QLearner &     0.407 \\
+13 &            DoubleCrosser &     0.072 &               ShortMem &     0.253 &              Evolved FSM 16 &     0.078 &             EasyGo &     0.071 &            NMWE Memory One &     0.080 &    Cautious QLearner &     0.409 \\
+14 &              BackStabber &     0.075 &      Limited Retaliate &     0.257 &                  EugineNier &     0.080 &    Fool Me Forever &     0.071 &                   Winner12 &     0.085 &      Fool Me Forever &     0.418 \\
 \bottomrule

### 2020-02-04 paper/main.tex
add sentence about new columns of perfomance

@@
 The top 15 strategies for each tournament type based on \(\bar{r}\) are given in
-Table~\ref{table:top_performances}.
+Table~\ref{table:top_performances}. Table~\ref{table:top_performances} includes
+the top 15 strategies in noisy tournaments with \(p_n < 0.1\) and probabilistic
+ending tournaments with \(p_e < 0.1\). These are included because the most common
+values in the literature for the probabilities of noise and a match ending are
+less than 0.1.
 
@@
     \begin{center}
-    \resizebox{.9\textwidth}{!}{
+    \resizebox{\textwidth}{!}{
         \input{top_perfomances.tex}
@@
 DBS is strategy specifically designed for noisy environments, however, it ranks
-highly only in standard ones.
+highly in standard tournaments as well.
 
@@
 
-\begin{table}[!htbp]
-    \centering
-    \resizebox{.30\textwidth}{!}{
-    \input{performance_noise_subset_table.tex}}
-    \caption{Top performances in 5661 noisy tournaments where \(p_n<0.5\).}\label{table:subset_noise_result}
-\end{table}
+% \begin{table}[!htbp]
+%     \centering
+%     \resizebox{.30\textwidth}{!}{
+%     \input{performance_noise_subset_table.tex}}
+%     \caption{Top performances in 5661 noisy tournaments where \(p_n<0.5\).}\label{table:subset_noise_result}
+% \end{table}
 
@@
 
-\begin{table}[!htbp]
-    \centering
-    \resizebox{.30\textwidth}{!}{
-    \input{performance_probend_subset_table.tex}}
-    \caption{Top performances in 1139 probabilistic ending tournaments with \(p_e < 0.1\)}
-    \label{table:subset_probend_result}
-\end{table}
+% \begin{table}[!htbp]
+%     \centering
+%     \resizebox{.30\textwidth}{!}{
+%     \input{performance_probend_subset_table.tex}}
+%     \caption{Top performances in 1139 probabilistic ending tournaments with \(p_e < 0.1\)}
+%     \label{table:subset_probend_result}
+% \end{table}
 
@@
 \end{figure}
+
+\newcolumntype{g}{>{\columncolor{Gray}}c}
+\begin{table}[h]
+    \begin{center}
+\resizebox{.8\textwidth}{!}{
+    \input{regression_table.tex}}
+    \end{center}
+\end{table}
 
@@
 
-\section{Acknowledgements}
-
-A variety of software have been used in this work:
-
-\begin{itemize}
-    \item The Axelrod-Python library for IPD simulations~\cite{axelrodproject}.
-    \item The Matplotlib library for visualisation~\cite{hunter2007matplotlib}.
-    \item The Numpy library for data manipulation~\cite{walt2011numpy}.
-    \item The scikit-learn library for data analysis~\cite{scikit-learn}.
-\end{itemize}
-
-\appendix
-
-\section{A summary of parameters}\label{app:parameters}
-
-\begin{table}[h]
-    \begin{center}
-    \resizebox{.7\textwidth}{!}{
-    \begin{tabular}{llc}
-    \toprule
-feature & feature explanation \\
- \midrule
-stochastic                  & If a strategy is stochastic \\
-makes use of game           & If a strategy makes used of the game information  \\
-makes use of length         & If a strategy makes used of the number of turns \\
-memory usage                & The memory size of a strategy divided by the number of turns \\
-SSE                         & A measure of how far a strategy is from extortionate behaviour \\
-$C_{\text{max}}$          & The biggest cooperating rate in the tournament \\
-$C_{\text{min}}$          & The smallest cooperating rate in the tournament \\
-$C_{\text{median}}$       & The median cooperating rate in the tournament \\
-$C_{\text{mean}}$         & The mean cooperating rate in the tournament \\
-$C_r$ / $C_{\text{max}}$    & A strategy's cooperating rate divided by the maximum \\
-$C_r$ / $C_{\text{min}}$    & A strategy's cooperating rate divided by the minimum \\
-$C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median \\
-$C_r$ / $C_{\text{mean}}$   & A strategy's cooperating rate divided by the mean \\
-$C_r$                       & The cooperating ratio of a strategy \\
-$CC$ to $C$ rate            & The probability a strategy will cooperate after a mutual cooperation \\
-$CD$ to $C$ rate            & The probability a strategy will cooperate after being betrayed by the opponent \\
-$DC$ to $C$ rate            & The probability a strategy will cooperate after betraying the opponent\\
-$DD$ to $C$ rate            & The probability a strategy will cooperate after a mutual defection\\
-$p_n$                       & The probability of a player's action being flipped at each interaction \\
-$n$                         & The number of turns \\
-$p_e$                       & The probability of a match ending in the next turn \\
-$N$                         & The number of strategies in the tournament \\
-$k$                         & The number that a given tournament is repeated \\
-    \bottomrule
-        \end{tabular}}
-    \end{center}
-    \caption{The features which are included in the performance evaluation analysis.}\label{table:parameters_summary}
-\end{table}
-
-\section{List of strategies}\label{app:list_of_players}
-
-The strategies used in this study which are from Axelrod-Python library version 3.0.0.
-
-\begin{multicols}{3}
-	\begin{enumerate}
-		\input{list_of_strategies.tex}
-	\end{enumerate}
-\end{multicols}
-
-\section{Correlation coefficients}\label{app:correlations}
-
-A graphical representation of the correlation coefficients for the features in
-Table~\ref{table:manual_features}.
-
-\begin{figure}[!htbp]
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../images/standard_correlation_plot.pdf}
-        \end{center}
-        \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-        for standard tournaments}
-\end{figure}
-\begin{figure}[!htbp]
-    \begin{center}
-        \includegraphics[width=.75\linewidth]{../images/noise_correlation_plot.pdf}
-    \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-    for noisy tournaments}
-\end{figure}
-\begin{figure}[!htbp]
-    \begin{center}
-        \includegraphics[width=.75\linewidth]{../images/probend_correlation_plot.pdf}
-    \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-    for probabilistic ending tournaments}
-\end{figure}
-\begin{figure}[!htbp]
-    \begin{center}
-        \includegraphics[width=.75\linewidth]{../images/probend_noise_correlation_plot.pdf}
-    \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-    for noisy probabilistic ending tournaments}
-\end{figure}
-\begin{figure}[!htbp]
-    \begin{center}
-        \includegraphics[width=.75\linewidth]{../images/merged_correlation_plot.pdf}
-    \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-    for data set}
-\end{figure}
+% \section{Acknowledgements}
+
+% A variety of software have been used in this work:
+
+% \begin{itemize}
+%     \item The Axelrod-Python library for IPD simulations~\cite{axelrodproject}.
+%     \item The Matplotlib library for visualisation~\cite{hunter2007matplotlib}.
+%     \item The Numpy library for data manipulation~\cite{walt2011numpy}.
+%     \item The scikit-learn library for data analysis~\cite{scikit-learn}.
+% \end{itemize}
+
+% \appendix
+
+% \section{A summary of parameters}\label{app:parameters}
+
+% \begin{table}[h]
+%     \begin{center}
+%     \resizebox{.7\textwidth}{!}{
+%     \begin{tabular}{llc}
+%     \toprule
+% feature & feature explanation \\
+%  \midrule
+% stochastic                  & If a strategy is stochastic \\
+% makes use of game           & If a strategy makes used of the game information  \\
+% makes use of length         & If a strategy makes used of the number of turns \\
+% memory usage                & The memory size of a strategy divided by the number of turns \\
+% SSE                         & A measure of how far a strategy is from extortionate behaviour \\
+% $C_{\text{max}}$          & The biggest cooperating rate in the tournament \\
+% $C_{\text{min}}$          & The smallest cooperating rate in the tournament \\
+% $C_{\text{median}}$       & The median cooperating rate in the tournament \\
+% $C_{\text{mean}}$         & The mean cooperating rate in the tournament \\
+% $C_r$ / $C_{\text{max}}$    & A strategy's cooperating rate divided by the maximum \\
+% $C_r$ / $C_{\text{min}}$    & A strategy's cooperating rate divided by the minimum \\
+% $C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median \\
+% $C_r$ / $C_{\text{mean}}$   & A strategy's cooperating rate divided by the mean \\
+% $C_r$                       & The cooperating ratio of a strategy \\
+% $CC$ to $C$ rate            & The probability a strategy will cooperate after a mutual cooperation \\
+% $CD$ to $C$ rate            & The probability a strategy will cooperate after being betrayed by the opponent \\
+% $DC$ to $C$ rate            & The probability a strategy will cooperate after betraying the opponent\\
+% $DD$ to $C$ rate            & The probability a strategy will cooperate after a mutual defection\\
+% $p_n$                       & The probability of a player's action being flipped at each interaction \\
+% $n$                         & The number of turns \\
+% $p_e$                       & The probability of a match ending in the next turn \\
+% $N$                         & The number of strategies in the tournament \\
+% $k$                         & The number that a given tournament is repeated \\
+%     \bottomrule
+%         \end{tabular}}
+%     \end{center}
+%     \caption{The features which are included in the performance evaluation analysis.}\label{table:parameters_summary}
+% \end{table}
+
+% \section{List of strategies}\label{app:list_of_players}
+
+% The strategies used in this study which are from Axelrod-Python library version 3.0.0.
+
+% \begin{multicols}{3}
+% 	\begin{enumerate}
+% 		\input{list_of_strategies.tex}
+% 	\end{enumerate}
+% \end{multicols}
+
+% \section{Correlation coefficients}\label{app:correlations}
+
+% A graphical representation of the correlation coefficients for the features in
+% Table~\ref{table:manual_features}.
+
+% \begin{figure}[!htbp]
+%         \begin{center}
+%             \includegraphics[width=.75\linewidth]{../images/standard_correlation_plot.pdf}
+%         \end{center}
+%         \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
+%         for standard tournaments}
+% \end{figure}
+% \begin{figure}[!htbp]
+%     \begin{center}
+%         \includegraphics[width=.75\linewidth]{../images/noise_correlation_plot.pdf}
+%     \end{center}
+%     \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
+%     for noisy tournaments}
+% \end{figure}
+% \begin{figure}[!htbp]
+%     \begin{center}
+%         \includegraphics[width=.75\linewidth]{../images/probend_correlation_plot.pdf}
+%     \end{center}
+%     \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
+%     for probabilistic ending tournaments}
+% \end{figure}
+% \begin{figure}[!htbp]
+%     \begin{center}
+%         \includegraphics[width=.75\linewidth]{../images/probend_noise_correlation_plot.pdf}
+%     \end{center}
+%     \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
+%     for noisy probabilistic ending tournaments}
+% \end{figure}
+% \begin{figure}[!htbp]
+%     \begin{center}
+%         \includegraphics[width=.75\linewidth]{../images/merged_correlation_plot.pdf}
+%     \end{center}
+%     \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
+%     for data set}
+% \end{figure}
 

### 2020-02-04 paper/main.tex
fixes the discussion on the top performances and on the evaluation approaches

@@
     \centering
-    \includegraphics[width=.6\textwidth]{../images/tit_for_tat_r_distributions.pdf}
+    \includegraphics[width=.60\textwidth]{../images/tit_for_tat_r_distributions.pdf}
     \caption{Tit For Tat's $r$ distribution in tournaments. The best performance
@@
 the last two rounds. The strategy was expected to not perform as well in
-tournaments where the number of turns is not specified, but the strategy did not
-perform well in tournaments with noise either. Finally, Winner
+tournaments where the number of turns is not specified. Finally, Winner
 12~\cite{mathieu2017} and DBS~\cite{Au2006} are both from the the literature.
-DBS is strategy specifically designed for noisy environments, however, it ranks
+DBS is a strategy specifically designed for noisy environments, however, it ranks
 highly in standard tournaments as well.
@@
 
-The top strategies in noisy tournaments are shown in Figure~\ref{fig:noisy_results}. These include deterministic strategies, such
-as Tit For 2 Tats~\cite{Axelrod1980b}, Slow Tit For Two Tats~\cite{axelrodproject}, Hard Tit For 2 Tats~\cite{Stewart2012}
-and Cycler CCCCCD, and strategies which decide their actions based on the
-cooperations to defections ratio, such as ShortMem~\cite{Carvalho2013}, Grumpy
-and $e$~\cite{axelrodproject}. Slow Tit For Two Tats is the same strategy as 
-Tit For 2 Tats, and at the time of writing this manuscript the
-contributors of~\cite{axelrodproject} made a new release where the strategy
-has been removed. However, for the purpose of this work the strategy is kept.
-The Retaliate and
-Limited Retaliate strategies are implemented in APL by the
-same contributor. They are strategies designed to defect if the opponent has
-tricked them more often than \(x\%\) of the times that they have
-done the same. Finally, in $4^{\text{th}}$ and $9^{\text{th}}$ place are Hunter
-strategies which trying to extort, equivalently, strategies that play cyclically
-and defectors.
-
-From Figure~\ref{fig:noisy_results}, it is evident that the normalised rank
-distributions in noisy environments are more variant with higher medians
-compared to standard tournaments. The distributions are bimodal. This indicates
-that although the top ranked strategies mainly performed well, there are several
-tournaments that they ranked in the bottom half. The bimodality of the \(r\)
-distributions can be explained by Figure~\ref{fig:noisy_results} which gives the
-\(r\) distributions for the top 6 strategies over the noise probability \(p_n\).
-Note that for \(p_n=0.5\) a strategy corresponds to a random player and for
-\(p_n=1\) a strategy is behaving in the exact opposite way than its design.
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.7\textwidth]{../images/performance_noise.pdf}
-    \caption{\(r\) distributions for best performed strategies in noisy tournaments.}
-    \label{fig:noisy_results}
-\end{figure}
-
-From Figure~\ref{fig:effect_of_noise} it is evident that the strategies highly
-ranked in noisy environments did so because of their performance in tournaments
-with \(p_n>0.5\). In tournaments with a noise probability lower than \(0.5\) the
-strategies performed poorly which is why their \(r\) distributions are bimodal.
-If during the data collection a \(p_n\) strictly less 0.5 was considered then the top ranked strategies would be
-different. There are a total of 5661 trials where \(p_n<0.5\) and the top ranked
-strategies are given in Table~\ref{table:subset_noise_result}. The median ranks
-are lower than before and the top spots are mainly overtaken by Meta strategies
-which include NMWE deterministic and NMWE Long Memory. The Meta
-strategies~\cite{axelrodproject} create a team of strategies for themselves and
-choose to play as a member of their team based on their scores against a given
-opponent.
+In noisy tournaments the top strategies differ when \(p_n\) is restricted and
+when it is not. The \(r\) distributions of the top 6 strategies when \(p_n\in
+[0, 1]\) are given by Figure~\ref{fig:effect_of_noise}. It is evident that these
+strategies were highly ranked due to the their performance in tournaments with
+\(p_n>0.5\), and that in tournaments with a noise probability lower than \(0.5\) they
+performed poorly. In comparison, when considering a \(p_n < 0.1\) the
+performances of the top strategies are more stable,
+Figure~\ref{fig:noise_results}. The top strategies in noisy tournaments with
+\(p_n < 0.1\) include DBS, Evolved FSM 16 Noise 05, Evolved ANN 5 Noise 05, PSO
+Gambler 2 2 2 Noise 05 and Omega Tit For Tat~\cite{kendall2007iterated} which
+are strategies specifically designed for noisy tournaments, strategies such as
+BackStabber, DoubleCrosser, Evolved ANN, FSM and HMM which performed well in
+standard tournaments as well, and deterministic strategies such as Spiteful Tit For
+Tat~\cite{prison}, Level Punisher~\cite{Eckhart2015}, Eugine Nier~\cite{lesswrong}.
 
@@
 
-% \begin{table}[!htbp]
-%     \centering
-%     \resizebox{.30\textwidth}{!}{
-%     \input{performance_noise_subset_table.tex}}
-%     \caption{Top performances in 5661 noisy tournaments where \(p_n<0.5\).}\label{table:subset_noise_result}
-% \end{table}
-
-The 15 top ranked strategies in probabilistic ending tournaments include
-Fortress 3, Fortress 4 (both introduced in~\cite{Ashlock2006}),
-Raider~\cite{Ashlock2014} and Solution B1~\cite{Ashlock2014}, which are
-strategies based on finite state automata introduced by Daniel Ashlock and Wendy
-Ashlock. These strategies have been evolved using reinforcement learning, however,
-there were trained to maximise their payoffs in tournaments with fixed turns
-(150 specifically) and not in probabilistic ending ones. In probabilistic ending
-tournaments it appears that the top ranks are mostly occupied by defecting
-strategies. These include Better and Better, Gradual Killer, Hard Prober (all
-from ~\cite{prison}), Bully (Reverse Tit For Tat)~\cite{Nachbar1992} and
-Defector. Thus, it's surprising that EasyGo and Fool Me Forever which are
-strategies that will defect until their opponent defects, then they will cooperate
-until the end, ranked $14^{\text{th}}$ and $15^{\text{th}}$. Upon inspection,
-it was found that they are actually the same strategy. This was not known to
-the authors at the time of data collection. Figure~\ref{fig:probend_results}
-verifies that their performance is the same. Both strategies have repeatedly
-ranked highly and there are cases for which they were the winners of the
-tournament.
-
-The distributions of the normalised rank in probabilistic ending tournaments,
-shown in
-Figure~\ref{fig:probend_results}, are less variant than those of noisy
-tournaments. The medians of the top 15 strategies are lower than 0.1 and the distributions are skewed
-towards 0. Though the large difference between the means and the medians
-indicates some outliers, the strategies have overall performed well in the
-probabilistic ending tournaments that they participated.
-
-\begin{figure}[h!]
-    \centering
-    \includegraphics[width=.7\textwidth]{../images/performance_probend.pdf}
-    \caption{\(r\) distributions for best performed strategies in probabilistic ending tournaments.}
-    \label{fig:probend_results}
-\end{figure}
-
-The distributions of \(r\) for the top 6 strategies in probabilistic ending
-tournaments over \(p_e\) are given in Figure~\ref{fig:effect_of_probend}.
-Figure~\ref{fig:effect_of_probend} shows that the 6 strategies start of with a
-high median rank, however, their ranked decreased as the the probability of the
-game ending increased and at the point of \(p_e=0.1\) they became the dominant
-strategies in their respective tournaments. In essence, what is demonstrated is
-that defecting strategies did better when the likelihood of the game ending in
-the next turn increased, which is inline with the Folk
-Theorem~\cite{Fudenberg2009}. If tournaments where the probability of the game
-ending was less than 0.1 were considered then the the top ranked spots are not
-dominated by just defecting strategies anymore,
-Table~\ref{table:subset_probend_result}. Instead the effective strategies are
-now the Meta strategies, trained strategies, Grudger~\cite{axelrodproject} and
-Spiteful Tit for Tat~\cite{prison}.
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.7\textwidth]{../images/noise_performance_subset.pdf}
+    \caption{$r$ distributions of top 15 strategies in 1151 noisy tournaments with \(p_n < 0.1\).}\label{fig:noise_results}
+\end{figure}
+
+In probabilistic ending tournaments it appears that the top ranks are mostly
+occupied by defecting strategies and a series of strategies based on finite state
+automata introduced by Daniel Ashlock and Wendy Ashlock; Fortress 3, Fortress 4
+(both introduced in~\cite{Ashlock2006}), Raider~\cite{Ashlock2014} and
+Solution B1~\cite{Ashlock2014}. Values of \(p_e > 0.5\) effectively turn an IPD
+match to a one/two shot game, thus it is not surprise that defecting strategies
+perform well. From Figure~\ref{fig:effect_of_probend}, which gives the
+distributions of \(r\) for the top 6 strategies in probabilistic ending tournaments
+over \(p_e\), shows that at the point of \(p_e=0.1\) defecting strategies become
+the dominant strategies in their respective tournaments. In essence, what is
+demonstrated in Figure~\ref{fig:effect_of_probend} is that defecting strategies
+do better when the likelihood of the game ending in the next turn increased,
+which is inline with the Folk Theorem~\cite{Fudenberg2009}.
 
@@
 
-% \begin{table}[!htbp]
-%     \centering
-%     \resizebox{.30\textwidth}{!}{
-%     \input{performance_probend_subset_table.tex}}
-%     \caption{Top performances in 1139 probabilistic ending tournaments with \(p_e < 0.1\)}
-%     \label{table:subset_probend_result}
-% \end{table}
+The top spots are not not dominated by just defecting strategies anymore when
+\(p_e < 0.1\) is considered, Table~\ref{table:top_performances}. The effective
+strategies are now Meta strategies which include Nice Meta Winner, NMWE Finite
+Memory, NMWE Deterministic, trained strategies, Grudger~\cite{axelrodproject}
+and Spiteful Tit for Tat~\cite{prison}. The Meta
+strategies~\cite{axelrodproject} create a team of strategies for themselves and
+play as an ensemble or some other combination of the team.
+The distributions of the normalised rank in probabilistic ending tournaments,
+shown in Figure~\ref{fig:probend_results}, are less variant than those of noisy
+tournaments. The medians of the top 15 strategies are lower than 0.1 and the
+distributions are skewed towards 0. The strategies have overall performed well
+in the probabilistic ending tournaments that they participated.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.6\textwidth]{../images/probend_performance_subset.pdf}
+    \caption{\(r\) distributions for best performed strategies in 1139 probabilistic ending
+    tournaments with \(p_e < 0.1\).}
+    \label{fig:probend_results}
+\end{figure}
 
@@
 tournaments. However, strategies from the top ranks in probabilistic ending
-tournaments did not rank highly here. Other strategies include $\pi$, $\phi$
-which are based on the same approach as $e$. The distributions of \(r\) shown in
-Figure~\ref{fig:noisy_probend_results} have the largest median values compared
-to the top rank strategies of the other tournament types. A subset of noisy
-probabilistic ending tournaments has been considered such that \(p_e < 0.1\) and
-\(p_n < 0.5\). The top ranked strategies are given in
-Table~\ref{table:subset_probend_noise_result} and it is shown that the Meta
-strategies which performed well in noisy tournaments with \(p_n < 0.5\), perform
-well once again even the number of turns is not specified. Moreover, several
-strategies that did well in probabilistic ending tournaments such as Fortress 3,
-Fortress 4, Defector and Better and Better are effective here as well.
+tournaments did not rank highly here.
+
+The distributions of \(r\) shown in Figure~\ref{fig:noisy_probend_results} have
+the largest median values compared to the top rank strategies of the other
+tournament types. A subset of noisy probabilistic ending tournaments has been
+considered such that \(p_e < 0.1\) and \(p_n < 0.1\). The top ranked strategies
+are given in Table~\ref{table:subset_probend_noise_result} and it is shown that
+the Meta strategies which performed well in noisy tournaments with \(p_n <
+0.1\), perform well once again even the number of turns is not specified.
+Moreover, several strategies that did well in probabilistic ending tournaments
+such as Fortress 4, MEM2 and Spiteful Tit For Tat.
 
@@
     \centering
-    \resizebox{.30\textwidth}{!}{
+    \resizebox{.27\textwidth}{!}{
     \input{performance_probend_noise_subset_table.tex}}
-    \caption{Top performances in 568 probabilistic ending tournaments with \(p_e < 0.1\) and \(p_n < 0.5\).}
+    \caption{Top performances in 117 probabilistic ending tournaments with \(p_e < 0.1\) and \(p_n < 0.1\).}
     \label{table:subset_probend_noise_result}
@@
 For these settings, the top 15 strategies have frequently ranked in
-the top spots with only a few exceptions. Contrarily, it appears that noise
-cause variation in the normalised ranks, and the strategies can always guarantee
-a spot in the top ranks.
+the top spots with only a few exceptions. The behaviour of the winning strategies
+in probabilistic ending tournaments vary when \(p_e\) is restricted to 0.1.
+For larger values of \(p_e\) the dominant strategies are defecting strategies,
+and in comparison for smaller values the dominant strategies are evolved
+and strategies based on teams. Similarly, in noisy tournaments the behaviour
+of the dominant strategies varied when the probability of noisy was restricted
+to 0.1. In noise tournaments with \(p_n \in [0, 1]\) there is much variation
+in the normalised ranks, and the strategies can always guarantee a spot in the
+top ranks. However, in the restricted case the dominant strategies are strategies
+specifically trained for noise tournaments.
 
 The data set considered in this work, described in
-Section~\ref{section:data_collection}, contains a total of \numberofalltournaments
-tournament results. For this part of the manuscript the strategies are ranked
-based on the median normalised rank they achieved over the entire data set.
-The top 15 strategies are given in Table~\ref{table:overall_results}
-and their normalised rank distributions are given in Figure~\ref{fig:overall_results}.
+Section~\ref{section:data_collection}, contains a total of
+\numberofalltournaments tournament results. For this part of the manuscript the
+strategies are ranked based on the median normalised rank they achieved over the
+entire data set. The top 15 strategies are given in
+Table~\ref{table:overall_results} and their normalised rank distributions are
+given in Figure~\ref{fig:overall_results}.
 
@@
     \centering
-    \resizebox{.35\textwidth}{!}{
+    \resizebox{.27\textwidth}{!}{
     \input{performance_merged_table.tex}}
@@
 
+\textbf{Evaluation based on correlation.}
+
 Table~\ref{table:correlations} shows the correlation coefficients between the
@@
 
-\newcolumntype{g}{>{\columncolor{Gray}}c}
-\begin{table}[h]
-    \begin{center}
-\resizebox{.8\textwidth}{!}{
-    \input{regression_table.tex}}
-    \end{center}
-\end{table}
-
-To further explore the features that contribute to a strategy's success the
-performances are divided into clusters based on whether they were successful or
-not. A random forest approach~\cite{breiman2001} is then applied to each
-performance to predict the cluster to which it has been assigned to. This allows
-for the importance of each feature in the classification to be calculated. In
-essence, to calculate which are the important features when one is trying to
-predict whether a performance was successful or not.
-
-The performances are clustered into successful and unsuccessful clusters based on
-4 different approaches. More specifically:
+\textbf{Evaluation based on clustering and random forest.}
+
+A second approach for evaluating the features importance in a strategy's success
+is a combination of clustering and a random forest algorithm. Initially,
+the strategies performances are clustered four different time based on the
+following approaches:
 
@@
 
-The random forest method constructs many individual decision trees and the
-predictions from all trees are pooled to make the final prediction. The random
+Once the performances have been assigned to a cluster for each approach a
+random forest algorithm~\cite{breiman2001} is applied. The problem is a supervised
+problem where the random forest algorithm predicts the cluster to which a performance
+has been assigned to using the features of Table~\ref{table:manual_features}.
+The random
 forest models are trained on a training set of 70\% of the tournaments results.
@@
 The importance that the features of Table~\ref{table:manual_features} had on
-each random forest model while the perfomances were clustered based on the
+each random forest model while the performances were clustered based on the
 different approaches have been
@@
 
-The effect of both these features can be further explored. In
+\textbf{Evaluation based on linear regression.}
+
+A multivariate linear regression is also fitted to model the relationship of the
+features and the normalised rank. The \(p-\)values of each feature as well as
+their coefficients are given by Table~\ref{table:linear_regression}. The
+coefficient of determination \(R\) squared fo each model is also report in
+Table~\ref{table:linear_regression}. Based on \(R\) square the model explain 90\% of
+the variability of the response data around its mean.
+
+\newcolumntype{g}{>{\columncolor{Gray}}c}
+\begin{table}[h]
+    \begin{center}
+\resizebox{.8\textwidth}{!}{
+    \input{regression_table.tex}}
+    \end{center}
+    \caption{Multivariate linear regression with \(r\) as the depended variable results.}
+    \label{table:linear_regression}
+\end{table}
+
+The results of the linear regression verify the results of the previous approaches.
+
+The features $C_{r} / C_{median}$ and $C_r / C_{mean}$ have been repeatably
+highlighted as importance feature in explaining the variability of the performances.
+Thus the effect of these tow measures is further explored.In
 Figure~\ref{fig:mean_median_std} the distributions of \(C_r / C_{\text{mean}}\)

### 2020-02-04 paper/main.tex
clean conclusion on first section

@@
 than a current amount of the times that they had tricked their opponent. However,
-if a value of noise strictly less than 0.5 was considered, then the successful
-strategies were strategies based on the behaviour of many strategies. In
+if a value of noise strictly less than 0.1 was considered, then the successful
+strategies were strategies based on the behaviour of many strategies and strategies
+specifically designed for noisy tournaments. In
 probabilistic ending tournaments most of the highly ranked strategies were defecting
@@
 These strategies ranked high due to their performance in tournaments where the probability of the game ending after
-each turn was bigger than 0.1.
+each turn was bigger than 0.1. In probabilistic tournaments with \(p_e\) less than 0.1
+the highly ranked strategies were trained and Meta strategies.
 Finally the performance of all \numberofstrategies
@@
 assessed on \(\bar{r}\). The top ranked strategies were a mixture of behaviours
-that did well in standard tournaments and tournaments with noise, as well as a
-few strategies based on teams.
+that did well in standard tournaments, tournaments with noise and a
+few Meta strategies.
 
@@
 environments demonstrated that no strategy can be consistently
-successful, expected if the value of noise is constrained to less than a half.
-Overall, there has been not a single strategy that has shown to perform well in
-more than one setting. The aim of the next section is to understand which are
+successful, expected if the value of noise is constrained to less than a 0.1.
+Trained strategies, meta strategies and some deterministic defecting strategies
+have demonstrated good performance over several tournament types, however,
+there exists no one single strategy which appears to be dominant in an IPD
+competition. The aim of the next section is to understand which are
 the factors that made these strategies successful, in each setting separately

### 2020-02-04 paper/main.tex
last line on section two
fix lat conclusion

@@
 and the tournament in which it participated on its performance were presented.
-This was done using two approaches. Correlation coefficients and a random forest
-analysis. The results of these are summarised in the following section.
+This was done using three approaches. Correlation coefficients, a random forest
+analysis and a linear regression. The results of these are summarised in the following section.
 
@@
 the analysis demonstrated that, although for specific tournament types such as
-standard and probabilistic ending tournaments, dominant strategies exist
-there is not a single dominant type of strategies if the environments
+standard and probabilistic ending tournaments, dominant types of strategies exist
+there is not a single dominant strategy in an IPD competition if the environments
 vary. Moreover, a strategy with a theory of mind should aim to adapt its behaviour
@@
 Some of these strategies ranked again in the top spots in probabilistic
-ending tournaments when a \(p_e\) of less 0.1 was considered. In probabilistic
+ending tournaments when a \(p_e\) of less 0.1 was considered and in noisy tournaments
+when \(p_n\) was less than 0.1. In probabilistic
 ending tournaments \(p_e\) was designed to vary between 0 and 1. It was demonstrated
@@
 that in noisy tournaments there are not strategies that can guarantee winning.
+However, if the probability of noisy was constrained at 0.1 then strategies
+designed for noisy tournaments indeed performed well.
 Overall, the top ranked strategies differed from one tournament type to

### 2020-02-16 paper/main.tex
finalises up to evaluation of performance before sending it off to Marc

@@
 The top 15 strategies for each tournament type based on \(\bar{r}\) are given in
-Table~\ref{table:top_performances}. Table~\ref{table:top_performances} includes
-the top 15 strategies in noisy tournaments with \(p_n < 0.1\) and probabilistic
-ending tournaments with \(p_e < 0.1\). These are included because the most common
-values in the literature for the probabilities of noise and a match ending are
-less than 0.1.
+Table~\ref{table:top_performances}. The data collection process was design such
+as that the probabilities of noise and ending of the match to vary between 0 and
+1. However, the most common values for these probabilities in the literature are
+values less than 0.1. Thus,
+Table~\ref{table:top_performances} also includes the top 15 strategies in noisy
+tournaments with \(p_n < 0.1\) and probabilistic ending tournaments with \(p_e <
+0.1\).
 
@@
 
-In noisy tournaments the top strategies differ when \(p_n\) is restricted and
-when it is not. The \(r\) distributions of the top 6 strategies when \(p_n\in
-[0, 1]\) are given by Figure~\ref{fig:effect_of_noise}. It is evident that these
-strategies were highly ranked due to the their performance in tournaments with
-\(p_n>0.5\), and that in tournaments with a noise probability lower than \(0.5\) they
-performed poorly. In comparison, when considering a \(p_n < 0.1\) the
-performances of the top strategies are more stable,
-Figure~\ref{fig:noise_results}. The top strategies in noisy tournaments with
-\(p_n < 0.1\) include DBS, Evolved FSM 16 Noise 05, Evolved ANN 5 Noise 05, PSO
-Gambler 2 2 2 Noise 05 and Omega Tit For Tat~\cite{kendall2007iterated} which
-are strategies specifically designed for noisy tournaments, strategies such as
-BackStabber, DoubleCrosser, Evolved ANN, FSM and HMM which performed well in
-standard tournaments as well, and deterministic strategies such as Spiteful Tit For
-Tat~\cite{prison}, Level Punisher~\cite{Eckhart2015}, Eugine Nier~\cite{lesswrong}.
+In the case of noisy tournaments with \(p_n < 0.1\) the top performed strategies
+include strategies specifically designed for noisy tournaments such as DBS,
+Evolved FSM 16 Noise 05, Evolved ANN 5 Noise 05, PSO Gambler 2 2 2 Noise 05 and
+Omega Tit For Tat~\cite{kendall2007iterated}, strategies which performed well in
+standard tournaments such as BackStabber, DoubleCrosser, Evolved ANN, FSM and
+HMM and deterministic strategies such as Spiteful Tit For Tat~\cite{prison},
+Level Punisher~\cite{Eckhart2015}, Eugine Nier~\cite{lesswrong}. The \(r\) distributions
+of these strategies are given in Figure~\ref{fig:noise_results} where it is evident
+that these strategies overall performed well in noisy tournaments.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.7\textwidth]{../images/noise_performance_subset.pdf}
+    \caption{$r$ distributions of top 15 strategies in 1151 noisy tournaments with \(p_n < 0.1\).}\label{fig:noise_results}
+\end{figure}
+
+In comparison, the top ranked strategies in noisy environments when \(p_n\in [0,
+1]\) include strategies which decide their actions based on the cooperations to
+defections ratio, such as ShortMem~\cite{Andre2013},
+Grumpy~\cite{axelrodproject} and e~\cite{axelrodproject}, and the Retaliate
+strategies which are designed to defect if the opponent has tricked them more
+often than x\% of the times that they have done the same. The overall
+performance of these strategies is bimodal,
+Figure~\ref{fig:noise_overall_results}. This indicates that although the top
+ranked strategies mainly performed well, there are several tournaments that they
+ranked in the bottom half. The bimodality of the \(r\) distributions can be
+explained by Figure~\ref{fig:effect_of_noise} which gives the \(r\)
+distributions for the top 6 strategies over the noise probability \(p_n\).
+It is evident that the highly ranked strategies
+were highly ranked due to the their performance in tournaments with \(p_n>0.5\),
+and that in tournaments with a noise probability lower than \(0.5\) they
+performed poorly.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.7\textwidth]{../images/performance_noise.pdf}
+    \caption{$r$ distributions of top 15 strategies in noisy tournaments.}\label{fig:noise_overall_results}
+\end{figure}
 
@@
 
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.7\textwidth]{../images/noise_performance_subset.pdf}
-    \caption{$r$ distributions of top 15 strategies in 1151 noisy tournaments with \(p_n < 0.1\).}\label{fig:noise_results}
-\end{figure}
-
-In probabilistic ending tournaments it appears that the top ranks are mostly
-occupied by defecting strategies and a series of strategies based on finite state
-automata introduced by Daniel Ashlock and Wendy Ashlock; Fortress 3, Fortress 4
-(both introduced in~\cite{Ashlock2006}), Raider~\cite{Ashlock2014} and
-Solution B1~\cite{Ashlock2014}. Values of \(p_e > 0.5\) effectively turn an IPD
-match to a one/two shot game, thus it is not surprise that defecting strategies
-perform well. From Figure~\ref{fig:effect_of_probend}, which gives the
+In probabilistic ending tournaments with \(p_e < 0.1\) the effective strategies
+are Meta strategies which include Nice Meta Winner, NMWE Finite Memory, NMWE
+Deterministic, trained strategies which performed well in standard tournaments,
+Grudger~\cite{axelrodproject} and Spiteful Tit for Tat~\cite{prison}. The Meta
+strategies~\cite{axelrodproject} are a set of rules that create a team of
+strategies and play as an ensemble or some other combination of their team
+members. The distributions of the normalised rank in the 1139 probabilistic
+ending tournaments with \(p_e < 0.1\), are shown in
+Figure~\ref{fig:probend_results}. The medians of the top 15 strategies are lower
+than 0.1 and the distributions are skewed towards 0. The strategies have overall
+performed well in the probabilistic ending tournaments that they participated.
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.6\textwidth]{../images/probend_performance_subset.pdf}
+    \caption{\(r\) distributions for best performed strategies in 1139 probabilistic ending
+    tournaments with \(p_e < 0.1\).}
+    \label{fig:probend_results}
+\end{figure}
+
+In probabilistic ending tournaments with \(p_e \in [0, 1]\) the top ranks are
+mostly occupied by defecting strategies such as Better and Better, Gradual
+Killer, Hard Prober (all from~\cite{axelrodproject}), Bully (Reverse Tit For
+Tat)~\cite{Nachbar1992} and Defector, and a series of strategies based on finite
+state automata introduced by Daniel Ashlock and Wendy Ashlock; Fortress 3,
+Fortress 4 (both introduced in~\cite{Ashlock2006}), Raider~\cite{Ashlock2014}
+and Solution B1~\cite{Ashlock2014}. As stated in the Folk Theorem~\cite{Fudenberg2009}
+defecting strategies do better when the likelihood of the game ending in the
+next turn increased. This is demonstrated by Figure~\ref{fig:effect_of_probend}, which gives the
 distributions of \(r\) for the top 6 strategies in probabilistic ending tournaments
-over \(p_e\), shows that at the point of \(p_e=0.1\) defecting strategies become
-the dominant strategies in their respective tournaments. In essence, what is
-demonstrated in Figure~\ref{fig:effect_of_probend} is that defecting strategies
-do better when the likelihood of the game ending in the next turn increased,
-which is inline with the Folk Theorem~\cite{Fudenberg2009}.
+over \(p_e\). It  shows that the 6 strategies start of with a high median rank,
+however, their ranked decreased as the the probability of the game ending
+increased and at the point of \(p_e = 0.1\).
 
@@
 
-The top spots are not not dominated by just defecting strategies anymore when
-\(p_e < 0.1\) is considered, Table~\ref{table:top_performances}. The effective
-strategies are now Meta strategies which include Nice Meta Winner, NMWE Finite
-Memory, NMWE Deterministic, trained strategies, Grudger~\cite{axelrodproject}
-and Spiteful Tit for Tat~\cite{prison}. The Meta
-strategies~\cite{axelrodproject} create a team of strategies for themselves and
-play as an ensemble or some other combination of the team.
-The distributions of the normalised rank in probabilistic ending tournaments,
-shown in Figure~\ref{fig:probend_results}, are less variant than those of noisy
-tournaments. The medians of the top 15 strategies are lower than 0.1 and the
-distributions are skewed towards 0. The strategies have overall performed well
-in the probabilistic ending tournaments that they participated.
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.6\textwidth]{../images/probend_performance_subset.pdf}
-    \caption{\(r\) distributions for best performed strategies in 1139 probabilistic ending
-    tournaments with \(p_e < 0.1\).}
-    \label{fig:probend_results}
-\end{figure}
-
 In tournaments with both noise and an unspecified number of turns several of the
@@
 tournaments did not rank highly here.
-
 The distributions of \(r\) shown in Figure~\ref{fig:noisy_probend_results} have
@@
 
-Up till now, the performances of the \numberofstrategies strategies have been evaluated for
-individual tournament types. The distributions of \(r\) for the tournament types indicate that
-for probabilistic ending and standard tournaments successful strategies do exist.
-For these settings, the top 15 strategies have frequently ranked in
-the top spots with only a few exceptions. The behaviour of the winning strategies
-in probabilistic ending tournaments vary when \(p_e\) is restricted to 0.1.
-For larger values of \(p_e\) the dominant strategies are defecting strategies,
-and in comparison for smaller values the dominant strategies are evolved
-and strategies based on teams. Similarly, in noisy tournaments the behaviour
+Up till now, the performances of the \numberofstrategies strategies have been
+evaluated for individual tournament types. The distributions of \(r\) for the
+tournament types indicate that for standard, probabilistic ending and noisy
+tournaments with \(p_n <0.1\) successful strategies do exist. For these settings
+the top 15 strategies frequently ranked in the top spots with only a few
+exceptions. The behaviour of the winning strategies in probabilistic ending
+tournaments varied when \(p_e\) was restricted to 0.1. For larger values of
+\(p_e\) the dominant strategies were defecting ones and for smaller values the
+dominant strategies were evolved strategies and strategies based on teams.
+In noisy tournaments Similarly the behaviour
 of the dominant strategies varied when the probability of noisy was restricted
-to 0.1. In noise tournaments with \(p_n \in [0, 1]\) there is much variation
-in the normalised ranks, and the strategies can always guarantee a spot in the
-top ranks. However, in the restricted case the dominant strategies are strategies
-specifically trained for noise tournaments.
+to. In noise tournaments with \(p_n < 0.1\) the dominant strategies were strategies
+specifically trained for noise tournaments, and the performed well in most of the
+tournaments they participated. However, in noisy tournaments with \(p_n \in [0, 1]\)
+the performances of the top ranked strategies were bimodal. Indicating that with
+high values of noisy a successful set of strategies does not exist.
 
@@
 standard tournaments the top spots were dominated by complex strategies that had
-been trained using reinforcement learning techniques. In noisy environments,
-whether the number of turns was fixed or not, the winning strategies were
-deterministic strategies designed to defect if the opponent tricked them more
-than a current amount of the times that they had tricked their opponent. However,
-if a value of noise strictly less than 0.1 was considered, then the successful
+been trained using reinforcement learning techniques. In noisy environments where
+the a noise probability strictly less than 0.1 was considered the successful
 strategies were strategies based on the behaviour of many strategies and strategies
@@
 
-% \section{Acknowledgements}
-
-% A variety of software have been used in this work:
-
-% \begin{itemize}
-%     \item The Axelrod-Python library for IPD simulations~\cite{axelrodproject}.
-%     \item The Matplotlib library for visualisation~\cite{hunter2007matplotlib}.
-%     \item The Numpy library for data manipulation~\cite{walt2011numpy}.
-%     \item The scikit-learn library for data analysis~\cite{scikit-learn}.
-% \end{itemize}
-
-% \appendix
-
-% \section{A summary of parameters}\label{app:parameters}
-
-% \begin{table}[h]
-%     \begin{center}
-%     \resizebox{.7\textwidth}{!}{
-%     \begin{tabular}{llc}
-%     \toprule
-% feature & feature explanation \\
-%  \midrule
-% stochastic                  & If a strategy is stochastic \\
-% makes use of game           & If a strategy makes used of the game information  \\
-% makes use of length         & If a strategy makes used of the number of turns \\
-% memory usage                & The memory size of a strategy divided by the number of turns \\
-% SSE                         & A measure of how far a strategy is from extortionate behaviour \\
-% $C_{\text{max}}$          & The biggest cooperating rate in the tournament \\
-% $C_{\text{min}}$          & The smallest cooperating rate in the tournament \\
-% $C_{\text{median}}$       & The median cooperating rate in the tournament \\
-% $C_{\text{mean}}$         & The mean cooperating rate in the tournament \\
-% $C_r$ / $C_{\text{max}}$    & A strategy's cooperating rate divided by the maximum \\
-% $C_r$ / $C_{\text{min}}$    & A strategy's cooperating rate divided by the minimum \\
-% $C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median \\
-% $C_r$ / $C_{\text{mean}}$   & A strategy's cooperating rate divided by the mean \\
-% $C_r$                       & The cooperating ratio of a strategy \\
-% $CC$ to $C$ rate            & The probability a strategy will cooperate after a mutual cooperation \\
-% $CD$ to $C$ rate            & The probability a strategy will cooperate after being betrayed by the opponent \\
-% $DC$ to $C$ rate            & The probability a strategy will cooperate after betraying the opponent\\
-% $DD$ to $C$ rate            & The probability a strategy will cooperate after a mutual defection\\
-% $p_n$                       & The probability of a player's action being flipped at each interaction \\
-% $n$                         & The number of turns \\
-% $p_e$                       & The probability of a match ending in the next turn \\
-% $N$                         & The number of strategies in the tournament \\
-% $k$                         & The number that a given tournament is repeated \\
-%     \bottomrule
-%         \end{tabular}}
-%     \end{center}
-%     \caption{The features which are included in the performance evaluation analysis.}\label{table:parameters_summary}
-% \end{table}
-
-% \section{List of strategies}\label{app:list_of_players}
-
-% The strategies used in this study which are from Axelrod-Python library version 3.0.0.
-
-% \begin{multicols}{3}
-% 	\begin{enumerate}
-% 		\input{list_of_strategies.tex}
-% 	\end{enumerate}
-% \end{multicols}
-
-% \section{Correlation coefficients}\label{app:correlations}
-
-% A graphical representation of the correlation coefficients for the features in
-% Table~\ref{table:manual_features}.
-
-% \begin{figure}[!htbp]
-%         \begin{center}
-%             \includegraphics[width=.75\linewidth]{../images/standard_correlation_plot.pdf}
-%         \end{center}
-%         \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-%         for standard tournaments}
-% \end{figure}
-% \begin{figure}[!htbp]
-%     \begin{center}
-%         \includegraphics[width=.75\linewidth]{../images/noise_correlation_plot.pdf}
-%     \end{center}
-%     \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-%     for noisy tournaments}
-% \end{figure}
-% \begin{figure}[!htbp]
-%     \begin{center}
-%         \includegraphics[width=.75\linewidth]{../images/probend_correlation_plot.pdf}
-%     \end{center}
-%     \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-%     for probabilistic ending tournaments}
-% \end{figure}
-% \begin{figure}[!htbp]
-%     \begin{center}
-%         \includegraphics[width=.75\linewidth]{../images/probend_noise_correlation_plot.pdf}
-%     \end{center}
-%     \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-%     for noisy probabilistic ending tournaments}
-% \end{figure}
-% \begin{figure}[!htbp]
-%     \begin{center}
-%         \includegraphics[width=.75\linewidth]{../images/merged_correlation_plot.pdf}
-%     \end{center}
-%     \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-%     for data set}
-% \end{figure}
+\section{Acknowledgements}
+
+A variety of software have been used in this work:
+
+\begin{itemize}
+    \item The Axelrod-Python library for IPD simulations~\cite{axelrodproject}.
+    \item The Matplotlib library for visualisation~\cite{hunter2007matplotlib}.
+    \item The Numpy library for data manipulation~\cite{walt2011numpy}.
+    \item The scikit-learn library for data analysis~\cite{scikit-learn}.
+\end{itemize}
+
+\appendix
+
+\section{A summary of parameters}\label{app:parameters}
+
+\begin{table}[h]
+    \begin{center}
+    \resizebox{.7\textwidth}{!}{
+    \begin{tabular}{llc}
+    \toprule
+feature & feature explanation \\
+ \midrule
+stochastic                  & If a strategy is stochastic \\
+makes use of game           & If a strategy makes used of the game information  \\
+makes use of length         & If a strategy makes used of the number of turns \\
+memory usage                & The memory size of a strategy divided by the number of turns \\
+SSE                         & A measure of how far a strategy is from extortionate behaviour \\
+$C_{\text{max}}$          & The biggest cooperating rate in the tournament \\
+$C_{\text{min}}$          & The smallest cooperating rate in the tournament \\
+$C_{\text{median}}$       & The median cooperating rate in the tournament \\
+$C_{\text{mean}}$         & The mean cooperating rate in the tournament \\
+$C_r$ / $C_{\text{max}}$    & A strategy's cooperating rate divided by the maximum \\
+$C_r$ / $C_{\text{min}}$    & A strategy's cooperating rate divided by the minimum \\
+$C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median \\
+$C_r$ / $C_{\text{mean}}$   & A strategy's cooperating rate divided by the mean \\
+$C_r$                       & The cooperating ratio of a strategy \\
+$CC$ to $C$ rate            & The probability a strategy will cooperate after a mutual cooperation \\
+$CD$ to $C$ rate            & The probability a strategy will cooperate after being betrayed by the opponent \\
+$DC$ to $C$ rate            & The probability a strategy will cooperate after betraying the opponent\\
+$DD$ to $C$ rate            & The probability a strategy will cooperate after a mutual defection\\
+$p_n$                       & The probability of a player's action being flipped at each interaction \\
+$n$                         & The number of turns \\
+$p_e$                       & The probability of a match ending in the next turn \\
+$N$                         & The number of strategies in the tournament \\
+$k$                         & The number that a given tournament is repeated \\
+    \bottomrule
+        \end{tabular}}
+    \end{center}
+    \caption{The features which are included in the performance evaluation analysis.}\label{table:parameters_summary}
+\end{table}
+
+\section{List of strategies}\label{app:list_of_players}
+
+The strategies used in this study which are from Axelrod-Python library version 3.0.0.
+
+\begin{multicols}{3}
+	\begin{enumerate}
+		\input{list_of_strategies.tex}
+	\end{enumerate}
+\end{multicols}
+
+\section{Correlation coefficients}\label{app:correlations}
+
+A graphical representation of the correlation coefficients for the features in
+Table~\ref{table:manual_features}.
+
+\begin{figure}[!htbp]
+        \begin{center}
+            \includegraphics[width=.75\linewidth]{../images/standard_correlation_plot.pdf}
+        \end{center}
+        \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
+        for standard tournaments}
+\end{figure}
+\begin{figure}[!htbp]
+    \begin{center}
+        \includegraphics[width=.75\linewidth]{../images/noise_correlation_plot.pdf}
+    \end{center}
+    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
+    for noisy tournaments}
+\end{figure}
+\begin{figure}[!htbp]
+    \begin{center}
+        \includegraphics[width=.75\linewidth]{../images/probend_correlation_plot.pdf}
+    \end{center}
+    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
+    for probabilistic ending tournaments}
+\end{figure}
+\begin{figure}[!htbp]
+    \begin{center}
+        \includegraphics[width=.75\linewidth]{../images/probend_noise_correlation_plot.pdf}
+    \end{center}
+    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
+    for noisy probabilistic ending tournaments}
+\end{figure}
+\begin{figure}[!htbp]
+    \begin{center}
+        \includegraphics[width=.75\linewidth]{../images/merged_correlation_plot.pdf}
+    \end{center}
+    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
+    for data set}
+\end{figure}
 

### 2020-02-17 paper/main.tex
finalise regression and conclustion

@@
 strategy's behaviour, along with measures regarding the tournaments the
-strategies competed in. These are given in Table~\ref{table:manual_features}.
+strategies competed in. A summary of the features is given in
+Table~\ref{table:manual_features}.
 
@@
 $n$ was 134. In the given tournament Evolved FSM 16 Noise 05 has a memory usage
-of 0.119. For tournaments with a probabilistic ending the number of turns was
+of 0.119. If the memory size of a strategy is infinite then memory usage is 1.
+For tournaments with a probabilistic ending the number of turns was
 not collected, so the memory usage feature is not used for probabilistic ending
@@
 and the game ending are also included.
+
+The performances are evaluated based on different methods.
 
@@
 
-A second approach for evaluating the features importance in a strategy's success
-is a combination of clustering and a random forest algorithm. Initially,
-the strategies performances are clustered four different time based on the
-following approaches:
+The second method to evaluate the features importance in a strategy's success
+is a combination of a clustering task and a random forest algorithm.
+Initially the performances are clustered into different clusters
+based on them being successful or not. The performances are clustered into
+successful and unsuccessful clusters based on 4 different approaches.
+More specifically:
 
@@
 The importance that the features of Table~\ref{table:manual_features} had on
-each random forest model while the performances were clustered based on the
-different approaches have been
-calculated and are given by Figures~\ref{fig:clustering_importance_standard},
+each random forest model are given by Figures~\ref{fig:clustering_importance_standard},
 \ref{fig:clustering_importance_noise},~\ref{fig:clustering_importance_probend},
@@
 
-A multivariate linear regression is also fitted to model the relationship of the
-features and the normalised rank. The \(p-\)values of each feature as well as
-their coefficients are given by Table~\ref{table:linear_regression}. The
-coefficient of determination \(R\) squared fo each model is also report in
-Table~\ref{table:linear_regression}. Based on \(R\) square the model explain 90\% of
-the variability of the response data around its mean.
+Finally, a multivariate linear regression is fitted to model the relationship of
+Table's~\ref{table:manual_features} and the normalised rank. The \(p-\)values of
+each feature as well as their coefficients are given by
+Table~\ref{table:linear_regression}. The coefficient of determination, \(R\)
+squared, for each model is also reported in Table~\ref{table:linear_regression}.
 
@@
     \end{center}
-    \caption{Multivariate linear regression with \(r\) as the depended variable results.}
+    \caption{Results of multivariate linear regressions with \(r\) as the depended variable.}
     \label{table:linear_regression}
@@
 
-The results of the linear regression verify the results of the previous approaches.
+The results of the linear regression verify the results of the previous
+approaches. The only features that do no have a significant effect on the
+models are the number of repetitions and memory usage in noisy tournaments,
+and the number of turns, number of repetitions and thr probability \(p_e\) in
+probabilistic ending tournaments. Over all the models, the features that are the
+most important predictors are $C_r$, $C_r$ / $C_{max}$ and $C_r$ / $C_{mean}$.
 
 The features $C_{r} / C_{median}$ and $C_r / C_{mean}$ have been repeatably
-highlighted as importance feature in explaining the variability of the performances.
-Thus the effect of these tow measures is further explored.In
+highlighted as importance features in explaining the variability of the performances.
+Thus, the effect of these two measures is further explored. In
 Figure~\ref{fig:mean_median_std} the distributions of \(C_r / C_{\text{mean}}\)
@@
 and the tournament in which it participated on its performance were presented.
-This was done using three approaches. Correlation coefficients, a random forest
+This was done using three methods. Correlation coefficients, a random forest
 analysis and a linear regression. The results of these are summarised in the following section.
@@
 the analysis demonstrated that, although for specific tournament types such as
-standard and probabilistic ending tournaments, dominant types of strategies exist
+standard, probabilistic ending tournaments and noisy tournaments with \(p_n <0.1\), dominant types of strategies exist
 there is not a single dominant strategy in an IPD competition if the environments
@@
 Overall, the top ranked strategies differed from one tournament type to
-another and the mechanism behind the winning strategies were all different.
-Even strategies designed to perform well in one setting were demonstrated to be
-better in others.
+another and the mechanism behind the winning strategies were all different, with some
+exceptions which include trained (Evolved) and Meta strategies.
 

### 2020-03-03 paper/main.tex
minor typos

@@
 structures such as neural networks, the literature has been exploring the
-performance of strategies in the game for years. The results of the literature,
+performance of strategies in the game for decades. The results of the literature,
 however, have been relying on a small number of somewhat arbitrarily selected
@@
 salient features.
-The outcomes support that a strategy with a theory of mind should adjust it’s
+The outcomes support that a strategy with a theory of mind should adjust its
 cooperations based on the mean/median cooperator of its environment to be
@@
 robin computer tournament became a common evaluation technique for newly designed
-strategies. Today more than 200 strategies exist in the literature and several
-tournaments, excluding Axelrod's, have been undertaken~\cite{Bendor1991,
-Harper2017, Kendall2007, Stephens2002, Stewart2012}.
+strategies. Many tournaments have followed Axelrod's~\cite{Bendor1991,
+Harper2017, Kendall2007, Stephens2002, Stewart2012} and today more than 200
+strategies exist in the literature.
 
@@
 winner of both tournaments was the simple strategy Tit For Tat which cooperated
-on the first turn and then simply copied the previous action of it's opponent.
+on the first turn and then simply copied the previous action of its opponent.
 Due to the strategy's strong performance in both tournaments, and moreover in a
-series of evolutionary experiments~\cite{Axelrod1981}, Tit For Tat was thought
-to be the most robust basic strategy in the IPD.
+series of evolutionary experiments~\cite{Axelrod1981}, Tit For Tat was often
+claimed to be the most robust basic strategy in the IPD.
 
@@
 allowed to submit multiple strategies. They submitted a total of 60 strategies
-that could recognised each other and colluded to increase one members score.
-This resulted with three of the strategies to be ranked in the top spots. The
+that could recognise each other and collude to increase one members score.
+This resulted in three of the strategies ranking in the top spots. The
 performance of the Southampton University team received mixed attention, though
@@
 ZDs are indeed a set of mathematically unique strategies
-and robust in pairwise interactions, however, their simplicity and extortionate
-behaviour have been tested. In~\cite{Harper2017} a tournament containing over
+and robust in pairwise interactions, however, their superiority in tournament settings
+have been tested. In~\cite{Harper2017} a tournament containing over
 200 strategies, including ZDs, was ran and none of them
@@
 
-Though only a select pieces of work have been discussed, the IPD literature is
+Though only select pieces of work have been discussed, the IPD literature is
 rich, and new strategies and competitions are being published every year~\cite{Glynatsi2019}. The
@@
 on a small number of tournaments, this manuscript evaluates the performance of \numberofstrategies
-strategies in \numberofalltournaments tournaments. These tournaments do not
-consist by just standard round robin tournaments, but also by tournaments with noise
-and tournaments with a probabilistic ending. The later part of the paper, evaluates
+strategies in \numberofalltournaments tournaments. These tournaments come in a
+number of variations including tournaments with noise, probabilistic match
+length and both noise and probabilistic match length.
+The later part of the paper, evaluates
 the impact of features on the performance of the strategies using modern
@@
 performance of these strategies is bimodal,
-Figure~\ref{fig:noise_overall_results}. This indicates that although the top
+Figure~\ref{fig:noise_overall_results}, indicating that although the top
 ranked strategies mainly performed well, there are several tournaments that they
@@
 dominant strategies were evolved strategies and strategies based on teams.
-In noisy tournaments Similarly the behaviour
-of the dominant strategies varied when the probability of noisy was restricted
-to. In noise tournaments with \(p_n < 0.1\) the dominant strategies were strategies
+Similarly the behaviour
+of the dominant strategies varied when the probability of noisy was restricted.
+In noisy tournaments with \(p_n < 0.1\) the dominant strategies were strategies
 specifically trained for noise tournaments, and the performed well in most of the
@@
 statistical difference. Thus, in an IPD tournament where the type is not
-specified, playing as any of the Retaliate strategies will have the result.
+specified, playing as any of the Retaliate strategies will have same the result.
 DoubleCrosser performed well in standard tournaments and the
@@
 
-APL makes use of classifiers to classify strategies according to
-various dimensions. These determine whether
+APL classifies strategies along several dimensions. These determine whether
 a strategy is stochastic or deterministic, whether it makes use of the number of
@@
 the mean and median cooperator in such settings. In probabilistic ending
-tournaments the correlations coefficients have a larger values, indicating a
+tournaments the correlation coefficients have a larger values, indicating a
 stronger effect. Thus a strategy will be punished more by its cooperative
@@
 standard, probabilistic ending tournaments and noisy tournaments with \(p_n <0.1\), dominant types of strategies exist
-there is not a single dominant strategy in an IPD competition if the environments
+there is not a single dominant strategy, from the collection on strategies considered in this work, in an IPD competition if the environments
 vary. Moreover, a strategy with a theory of mind should aim to adapt its behaviour
@@
 that in noisy tournaments there are not strategies that can guarantee winning.
-However, if the probability of noisy was constrained at 0.1 then strategies
+However, if the probability of noise was constrained at 0.1 then strategies
 designed for noisy tournaments indeed performed well.

### 2020-03-26 src/plot.py
fix label for c_min over c_r

@@ -20,7 +20,7 @@ features_labels = {
     "Cooperation_rating_median": r"$C_{median}$",
     "Cooperation_rating_mean": r"$C_{mean}$",
     "Cooperation_rating_comp_to_max": r"$C_r$ / $C_{max}$ ",
-    "Cooperation_rating_comp_to_min": r"$C_r$ / $C_{min}$",
+    "Cooperation_rating_comp_to_min": r"$C_{min}$ / $C_r$",
     "Cooperation_rating_comp_to_median": r"$C_r$ / $C_{median}$",
     "Cooperation_rating_comp_to_mean": r"$C_r$ / $C_{mean}$",
     "turns": r"$n$",

### 2020-03-26 paper/main.tex
first go at marc's second suggestions

@@
 
-\title{A meta analysis of tournaments and an evaluation of performance in the
-Iterated Prisoner's Dilemma.}
-\author{Nikoleta E. Glynatsi, Vincent A. Knight}
+\title{Properties of winning Iterated Prisoner's Dilemma strategies.}
+\author{Nikoleta E. Glynatsi, Vincent A. Knight, Marc Harper}
 \date{}
@@
 \begin{abstract}
-The Iterated Prisoner's Dilemma has been used for decades as a model of
-behavioural interactions. From the celebrated performance of Tit for Tat, to the
+From the celebrated performance of Tit for Tat, to the
 introduction of the zero-determinant strategies, to the use of sophisticated
 structures such as neural networks, the literature has been exploring the
-performance of strategies in the game for decades. The results of the literature,
+performance of Iterated Prisoner's Dilemma strategies for decades. The results of the literature,
 however, have been relying on a small number of somewhat arbitrarily selected
@@
 casting doubt on the generalizability of results from statistical perspective.
-This manuscript evaluates \numberofstrategies strategies in more than 40000
+This manuscript evaluates \numberofstrategies strategies in 45686
 tournaments, presents the top performing strategies, and analyzes their
-salient features.
-The outcomes support that a strategy with a theory of mind should adjust its
-cooperations based on the mean/median cooperator of its environment to be
-successful; the adjustments are distinct for different tournament types.
+salient features. The results of the tournaments imply that there is not a single
+type of strategy that performs well in any Iterated Prisoner's Dilemma interaction.
+There are several properties, however, that heavily influence the best performing
+strategies: be nice, be provocable, be a little envious and be clever.
 \end{abstract}
@@
 In the 80's, Axelrod performed two computer tournaments~\cite{Axelrod1980a,
-Axelrod1980b}. The contestants were strategies submitted in the form of computer
-code. They competed against all other entries, a copy of themselves and a random
-strategy. The winner was decided on the average score a strategy achieved. The
+Axelrod1980b}. The
 winner of both tournaments was the simple strategy Tit For Tat which cooperated
 on the first turn and then simply copied the previous action of its opponent.
-Due to the strategy's strong performance in both tournaments, and moreover in a
+Axelrod concluded that the strategy's robustness was due to four different
+properties:
+
+\begin{itemize}
+    \item Do not be envious
+    \item Be "nice"; Do not be the first to defect
+    \item Reciprocate both cooperation and defection
+    \item Do not be too clever
+\end{itemize}
+
+As a result of the strategy's strong performance in both tournaments, and moreover in a
 series of evolutionary experiments~\cite{Axelrod1981}, Tit For Tat was often
@@
 
-However, further research proved that the strategy had weakness, and more
+Further research proved that the strategy had weakness, and more
 specifically, it was shown that the strategy suffered in environments with
@@
 Pavlov~\cite{Nowak1993} and Generous Tit For Tat~\cite{Nowak1992}.
-
-In 2004, a $20^{\text{th}}$ Anniversary Iterated Prisoner Dilemma Tournament
-took place with 233 entries. This time the winning strategy was not designed on
-a reciprocity based approach but on a mechanism of
-teams~\cite{J.P.Delahaye1993Lp, J.P.Delahaye1995LIeP, A.Rogers2007Ctpw}. A team
-from Southampton University took advantage of the fact that a participant was
-allowed to submit multiple strategies. They submitted a total of 60 strategies
-that could recognise each other and collude to increase one members score.
-This resulted in three of the strategies ranking in the top spots. The
-performance of the Southampton University team received mixed attention, though
-they had won the tournament as stated in~\cite{us_blog} "technically this
-strategy violates the spirit of the Prisoner's Dilemma, which assumes that the
-two prisoners cannot communicate with one another".
-
-Another set of IPD strategies that have received a lot of attention
+Several works extended the reciprocity based approach which has led to new
+strategies. For example Gradual~\cite{Beaufils1997} which was constructed to
+have the same qualities as those of Tit for Tat except one,
+\textit{Gradual} had a memory of the game since the beginning of it. Gradual
+recorded the number of defections by the opponent and punished them with a
+growing number of defections. It would then enter a calming state in which it
+would cooperates for two rounds. In a tournament of 12 strategies, including
+both Tit for Tat and Pavlov, Gradual managed to outperformed them all. A
+strategy with the same intuition as Gradual is \textit{Adaptive Tit for
+Tat}~\cite{tzafestas-2000a}. Adaptive Tit for Tat does not keep a permanent
+count of past defections, it maintains a continually updated estimate of the
+opponent’s behaviour, and uses this estimate to condition its future actions. In
+the exact same tournament as in~\cite{Beaufils1997} with now 13 strategies Adaptive
+Tit for Tat ranked first.
+A set of IPD strategies that have received a lot of attention
 are the zero-determinant strategies (ZDs)~\cite{Press2012}. By
@@
 machine learning techniques. These features include measures regarding a
-strategy's behaviour and measures regarding the tournaments. The data set used
+strategy's behaviour and measures regarding the tournaments. The outcomes of our
+work reinforce the discussion started by Axelrod:
+
+\begin{itemize}
+    \item Do not be envious
+    \item Be "nice"; Do not be the first to defect
+    \item Reciprocate both cooperation and defection
+    \item Do not be too clever
+\end{itemize}
+
+Furthermore, the data set used
 in this work has been made publicly available~\cite{data} and can be used
@@
 version 3.0.0. APL allows for different types of IPD computer
-tournaments to be simulated whilst containing a list of over 180 strategies.
+tournaments to be simulated whilst containing a large list of strategies.
 Most of these are strategies described in the literature with a few exceptions
@@
 the analysis, which will be discussed in the following sections, have been written
-following best practices~\cite{Aberdour2007, Benureau2018}. It has been packaged
+following best practices~\cite{Aberdour2007, Benureau2018}
 and is available here. %TODO archive code
@@
     \includegraphics[width=.60\textwidth]{../images/tit_for_tat_r_distributions.pdf}
-    \caption{Tit For Tat's $r$ distribution in tournaments. The best performance
+    \caption{Tit For Tat's $r$ distribution in tournaments. Lower values of \(r\)
+    correspond to better performances. The best performance
     of the strategy has been in standard tournaments where it achieved a $\bar{r}$
@@
 as that the probabilities of noise and ending of the match to vary between 0 and
-1. However, the most common values for these probabilities in the literature are
+1. However, commonly used values of these probabilities are
 values less than 0.1. Thus,
@@
 \end{center}
-\caption{Top performances for each tournament type based on $\bar{r}$.}
+\caption{Top performances for each tournament type based on $\bar{r}$. The results
+of each type are based on 11420 unique tournaments of each type. The results
+for noisy tournaments with \(p_n < 0.1\) are based on 1151 tournaments, and 
+for probabilistic ending tournaments with \(p_e < 0.1\) on 1139. The top ranks
+indicate that trained strategies perform well in a variety of environments,
+but so do simple deterministic strategies. The normalised medians are close to 0
+for most environments, except environments with noise not restricted to 0.1.
+These two tournaments have the highest medians, implying that strategies from
+the collection of this work can not perform well in environments with such high
+values of noise.}
 \label{table:top_performances}
 \end{table}
+
+Distributions of these top ranked strategies are given by Figure~\ref{fig:r_distributions}.
+\newpage
+
+\begin{figure*}[!htbp]
+    \centering
+    \begin{subfigure}{0.475\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/performance_standard.pdf}
+        \caption{$r$ distributions in standard tournaments.}\label{fig:std_results}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.475\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/noise_performance_subset.pdf}
+        \caption{$r$ distributions of top 15 strategies in 1151 noisy tournaments with \(p_n < 0.1\).}\label{fig:noise_results}
+    \end{subfigure}
+    \vskip\baselineskip
+    \begin{subfigure}{0.475\textwidth}
+        \centering 
+        \includegraphics[width=\textwidth]{../images/performance_noise.pdf}
+        \caption{$r$ distributions of top 15 strategies in noisy tournaments.}\label{fig:noise_overall_results}
+    \end{subfigure}
+    \quad
+    \begin{subfigure}{0.475\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/probend_performance_subset.pdf}
+        \caption{\(r\) distributions for best performed strategies in 1139 probabilistic ending
+        tournaments with \(p_e < 0.1\).}
+        \label{fig:probend_results}
+    \end{subfigure}
+    \caption{\(r\) distributions of the top 15 strategies in different environments. A lower value of
+    \(\bar{r}\) corresponds to a more successful performance. A strategy's \(r\) distribution skewed towards zero
+    indicates that the strategy ranked highly in most tournaments it participated in.}\label{fig:r_distributions}
+\end{figure*}
 
@@
 in APL in a standard tournament, thus their performance in the
-specific setting was anticipated. DoubleCrosser, and Fool Me Once, are
-strategies not from the literature but from the APL. DoubleCrosser
-is a strategy that makes use of the number of turns because it is set to defect on
-the last two rounds. The strategy was expected to not perform as well in
+specific setting was anticipated. DoubleCrosser, BackStabber and Fool Me Once, are
+strategies not from the literature but from the APL. DoubleCrosser is an extension
+of BackStabber and both strategies make use of the number of turns because they are
+set to defect on the last two rounds. It should be noted that these
+strategies can be characterised as "cheaters". The source code of the strategies
+allows them to known the number of turns in a match (if they are specified).
+These strategies were expected to not perform as well in
 tournaments where the number of turns is not specified. Finally, Winner
 12~\cite{mathieu2017} and DBS~\cite{Au2006} are both from the the literature.
-DBS is a strategy specifically designed for noisy environments, however, it ranks
+DBS is a strategy specifically designed for noisy environments and it ranks
 highly in standard tournaments as well.
-
 Figure~\ref{fig:std_results} gives the distributions of $r$ for the top
@@
 the number of turns.
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.7\textwidth]{../images/performance_standard.pdf}
-    \caption{$r$ distributions of top 15 strategies in standard tournaments.}\label{fig:std_results}
-\end{figure}
 
@@
 that these strategies overall performed well in noisy tournaments.
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.7\textwidth]{../images/noise_performance_subset.pdf}
-    \caption{$r$ distributions of top 15 strategies in 1151 noisy tournaments with \(p_n < 0.1\).}\label{fig:noise_results}
-\end{figure}
-
 In comparison, the top ranked strategies in noisy environments when \(p_n\in [0,
@@
     \centering
-    \includegraphics[width=.7\textwidth]{../images/performance_noise.pdf}
-    \caption{$r$ distributions of top 15 strategies in noisy tournaments.}\label{fig:noise_overall_results}
-\end{figure}
-
-\begin{figure}[!htbp]
-    \centering
     \includegraphics[width=\textwidth]{../images/noise_effect.pdf}
@@
 performed well in the probabilistic ending tournaments that they participated.
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.6\textwidth]{../images/probend_performance_subset.pdf}
-    \caption{\(r\) distributions for best performed strategies in 1139 probabilistic ending
-    tournaments with \(p_e < 0.1\).}
-    \label{fig:probend_results}
-\end{figure}
 
@@
 
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.7\textwidth]{../images/performance_probend_noise.pdf}
-    \caption{\(r\) distributions for best performed strategies in noisy
-    probabilistic ending tournaments.}
-    \label{fig:noisy_probend_results}
-\end{figure}
-
 \begin{table}[!htbp]
     \centering
-    \resizebox{.27\textwidth}{!}{
+    \resizebox{.55\textwidth}{!}{
     \input{performance_probend_noise_subset_table.tex}}
@@
 
-Up till now, the performances of the \numberofstrategies strategies have been
-evaluated for individual tournament types. The distributions of \(r\) for the
-tournament types indicate that for standard, probabilistic ending and noisy
-tournaments with \(p_n <0.1\) successful strategies do exist. For these settings
-the top 15 strategies frequently ranked in the top spots with only a few
-exceptions. The behaviour of the winning strategies in probabilistic ending
-tournaments varied when \(p_e\) was restricted to 0.1. For larger values of
-\(p_e\) the dominant strategies were defecting ones and for smaller values the
-dominant strategies were evolved strategies and strategies based on teams.
-Similarly the behaviour
-of the dominant strategies varied when the probability of noisy was restricted.
-In noisy tournaments with \(p_n < 0.1\) the dominant strategies were strategies
-specifically trained for noise tournaments, and the performed well in most of the
-tournaments they participated. However, in noisy tournaments with \(p_n \in [0, 1]\)
-the performances of the top ranked strategies were bimodal. Indicating that with
-high values of noisy a successful set of strategies does not exist.
-
-The data set considered in this work, described in
-Section~\ref{section:data_collection}, contains a total of
-\numberofalltournaments tournament results. For this part of the manuscript the
-strategies are ranked based on the median normalised rank they achieved over the
-entire data set. The top 15 strategies are given in
-Table~\ref{table:overall_results} and their normalised rank distributions are
-given in Figure~\ref{fig:overall_results}.
-
-\begin{table}[!htbp]
-    \centering
-    \resizebox{.27\textwidth}{!}{
-    \input{performance_merged_table.tex}}
-    \caption{Top performances over all the tournaments}\label{table:overall_results}
-\end{table}
-
-The top ranks include strategies that have been previously mentioned. The
-set of Retaliate strategies occupy the top spots followed by BackStabber
-and DoubleCrosser. The distributions of the Retaliate strategies have no
-statistical difference. Thus, in an IPD tournament where the type is not
-specified, playing as any of the Retaliate strategies will have same the result.
-DoubleCrosser performed well in standard tournaments and the
-strategy is just an extension of BackStabber. It should be noted that these
-strategies can be characterised as "cheaters". The source code of the strategies
-allows them to known the number of turns in a match (if they are specified).
-PSO Gambler and Evolved HMM 5 are
-trained strategies introduced in~\cite{Harper2017} and Nice Meta Winner and NMWE
-Memory One are strategies based on teams. Grudger is a strategy from Axelrod's
-original tournament and Forgetful Fool Me Once is based on the same approach as
-Grudger. Overall the top 15 strategies are fundamentally different. Some are cheaters,
-some are complex, others are simple deterministic strategies and strategies based
-on teams. The results of \numberofalltournaments tournaments used in this work imply the following:
-they is not a single type of strategy performs well in any IPD interaction.
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.7\textwidth]{../images/performance_merged.pdf}
+\begin{figure}[!htbp]
+    \centering
+    \begin{subfigure}{0.475\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/performance_probend_noise.pdf}
+        \caption{\(r\) distributions for best performed strategies in noisy
+        probabilistic ending tournaments.}
+        \label{fig:noisy_probend_results}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.475\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/performance_merged.pdf}
         \caption{\(r\) distributions for best performed strategies in the data set~\cite{data}.}
         \label{fig:overall_results}
+    \end{subfigure}
+    % \caption{\(r\) distributions of the top 15 strategies in different environments. A lower value of
+    % \(\bar{r}\) corresponds to a more successful performance. A strategy's \(r\) distribution skewed towards zero
+    % indicates that the strategy ranked highly in most tournaments it participated in.}\label{fig:r_distributions}
 \end{figure}
@@
 few Meta strategies.
-
 The results of this section imply that successful strategies for specific
@@
 but also overall.
+
+Be envious and be clever.
 
@@
 $C_r$ / $C_{\text{max}}$ & A strategy's cooperating rate divided by the maximum & result summary  & float & 0 & 1 \\
-$C_r$ / $C_{\text{min}}$ & A strategy's cooperating rate divided by the minimum & result summary  & float & 0 & 1 \\
+$C_{\text{min}}$ / $C_r$ & A strategy's cooperating rate divided by the minimum & result summary  & float & 0 & 1 \\
 $C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median  & result summary  & float & 0 & 1\\
@@
 memory size of strategy (which is specified in the strategies implementation
-in the APL) divide by the number of turns. For example, Evolved
-FSM 16 Noise 05 has a memory size of 16 and participated in a tournament where
-$n$ was 134. In the given tournament Evolved FSM 16 Noise 05 has a memory usage
-of 0.119. If the memory size of a strategy is infinite then memory usage is 1.
+in the APL) divide by the number of turns. For example, Winner12 has a memory
+size of 2 and participated in a tournament where $n$ was 101. In the given
+tournament Winner12 has a memory usage of 0.014925. There are strategies with
+an infinite memory size, for example Evolved FSM 16 Noise 05. These strategies
+have a memory usage of 1.
 For tournaments with a probabilistic ending the number of turns was
@@
 and the game ending are also included.
-
-The performances are evaluated based on different methods.
-
-\textbf{Evaluation based on correlation.}
 
@@
 
-\textbf{Evaluation based on clustering and random forest.}
-
-The second method to evaluate the features importance in a strategy's success
-is a combination of a clustering task and a random forest algorithm.
-Initially the performances are clustered into different clusters
-based on them being successful or not. The performances are clustered into
-successful and unsuccessful clusters based on 4 different approaches.
-More specifically:
-
-\begin{itemize}
-    \item \textbf{Approach 1:} The performances are divided into two clusters based
-    on whether their performance was in the top \(5\%\) of their respective tournaments.
-    Thus, whether \(r\) was smaller or larger than 0.05.
-    \item \textbf{Approach 2:} The performances are divided into two clusters based
-    on whether their performance was in the top \(25\%\) of their respective tournaments.
-    Thus, whether \(r\) was smaller or larger than 0.25.
-    \item \textbf{Approach 3:} The performances are divided into two clusters based
-    on whether their performance was in the top \(50\%\) of their respective tournaments.
-    Thus, whether \(r\) was smaller or larger than 0.50.
-    \item \textbf{Approach 4:} The performances are clustered based on their normalised rank and
-    their median score by a \(k-\)means algorithm~\cite{Arthur2007}. The number of
-    clusters is not deterministically chosen but it is based on the silhouette
-    coefficients~\cite{Rousseeuw1987}.
-\end{itemize}
-
-Once the performances have been assigned to a cluster for each approach a
-random forest algorithm~\cite{breiman2001} is applied. The problem is a supervised
-problem where the random forest algorithm predicts the cluster to which a performance
-has been assigned to using the features of Table~\ref{table:manual_features}.
-The random
-forest models are trained on a training set of 70\% of the tournaments results.
-The accuracy of each model based on $R^2$ and the number of clusters for each
-tournament type (because in the case of Approach 4 it is not
-deterministically chosen) are given by Table~\ref{table:accuracy_random_forest}.
-The out of the bag error (OOB)~\cite{hastie2005} has also been calculated. The
-models fit well, and a high value of both the accuracy measures on the test data
-and the OOB error indicate that the model is not over fitting.
-
-\begin{table}[!htbp]
-    \begin{center}
-        \resizebox{.9\textwidth}{!}{
-        \begin{tabular}{lccccc}
-    \toprule
-    Tournament type & Clustering Approach & Number of clusters & $R^2$ training data &  $R^2$ test data  & $R^2$ OOB score\\
-    \midrule
-    standard  & Approach 1  & 2 & 0.998831  & 0.987041    & 0.983708 \\
-              & Approach 2  & 2 & 0.998643  & 0.978626    & 0.969202 \\
-              & Approach 3  & 2 & 0.998417  & 0.985217    & 0.976538 \\
-              & Approach 4  & 2 & 0.998794  & 0.990677    & 0.982959 \\
-    \midrule
-    noisy     & Approach 1  & 2 & 0.997786  & 0.972229    & 0.968332\\
-              & Approach 2  & 2 & 0.997442  & 0.963254    & 0.955219\\
-              & Approach 3  & 2 & 0.997152  & 0.953164    & 0.940528\\
-              & Approach 4  & 3 & 0.996923  & 0.950728    & 0.935444\\
-    \midrule
-    probabilistic ending & Approach 1 & 2 & 0.997909   & 0.981490  & 0.978120 \\
-                         & Approach 2 & 2 & 0.997883   & 0.973492  & 0.967150 \\
-                         & Approach 3 & 2 & 0.990448   & 0.890068  & 0.875822 \\
-                         & Approach 4 & 2 & 0.999636   & 0.995183  & 0.992809 \\
-    \midrule
-    noisy probabilistic ending & Approach 1  & 2 & 0.995347 & 0.957846   & 0.952353\\
-                               & Approach 2  & 2 & 0.992813 & 0.909346   & 0.898613\\
-                               & Approach 3  & 2 & 0.990579 & 0.824794   & 0.806540\\
-                               & Approach 4  & 4 & 0.989465 & 0.841652   & 0.824052\\
-    \midrule
-    over \numberofalltournaments tournaments   & Approach 1 & 2 & 0.997271& 0.972914& 0.969198 \\
-                                               & Approach 2 & 2 & 0.996323& 0.951194& 0.940563 \\
-                                               & Approach 3 & 2 & 0.993707& 0.906941& 0.891532 \\
-                                               & Approach 4 & 3 & 0.993556& 0.913335& 0.898453 \\
-    \bottomrule
-        \end{tabular}}
-    \end{center}
-    \caption{Accuracy metrics for random forest models.}
-    \label{table:accuracy_random_forest}
-\end{table}
-
-The importance that the features of Table~\ref{table:manual_features} had on
-each random forest model are given by Figures~\ref{fig:clustering_importance_standard},
-\ref{fig:clustering_importance_noise},~\ref{fig:clustering_importance_probend},
-\ref{fig:clustering_importance_probend_noise}
-and~\ref{fig:clustering_importance_overall}. These show that the classifiers
-stochastic, make use of game and make use of length have no significant effect,
-and several of the features that are highlighted by the importance are inline with
-the correlation results. Moreover, the smoothing parameter \(k\) appears to no
-have a significant effect either. The most important features based on the
-random forest analysis were $C_{r} / C_{median}$ and $C_r / C_{mean}$.
-
-\begin{figure}[!htbp]
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../new_output/standard/_feature_importance_bar_plot_cluster_on_0_05.pdf}
-        \end{center}
-        \caption{Importance of features for clusters on 5\% performance.}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../new_output/standard/_feature_importance_bar_plot_cluster_on_0_25.pdf}
-        \end{center}
-        \caption{Importance of features for clusters on 25\% performance.}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../new_output/standard/_feature_importance_bar_plot_cluster_on_0_5.pdf}
-        \end{center}
-        \caption{Importance of features for clusters on 50\% performance.}
-    \end{subfigure}\hfill
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../k_means_output/standard/_feature_importance_bar_plot.pdf}
-        \end{center}
-        \caption{Importance of features for clusters based on \(k\)means algorithm.}
-    \end{subfigure}
-    \caption{Importance of features in standard tournaments for different
-    clustering methods.}\label{fig:clustering_importance_standard}
-\end{figure}
-
-\begin{figure}[!htbp]
-    \begin{subfigure}{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../new_output/noise/_feature_importance_bar_plot_cluster_on_0_05.pdf}
-        \end{center}
-        \caption{Importance of features for clusters on 5\% performance.}
-    \end{subfigure}\hfill
-    \begin{subfigure}{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../new_output/noise/_feature_importance_bar_plot_cluster_on_0_25.pdf}
-        \end{center}
-        \caption{Importance of features for clusters on 25\% performance.}
-    \end{subfigure}
-    \begin{subfigure}{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../new_output/noise/_feature_importance_bar_plot_cluster_on_0_5.pdf}
-        \end{center}
-        \caption{Importance of features for clusters on 50\% performance.}
-    \end{subfigure}\hfill
-    \begin{subfigure}{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../k_means_output/noise/_feature_importance_bar_plot.pdf}
-        \end{center}
-        \caption{Importance of features for clusters based on \(k\)means algorithm.}
-    \end{subfigure}
-    \caption{Importance of features in noisy tournaments for different
-    clustering methods.}\label{fig:clustering_importance_noise}
-\end{figure}
-
-\begin{figure}[!htbp]
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../new_output/probend/_feature_importance_bar_plot_cluster_on_0_05.pdf}
-        \end{center}
-        \caption{Importance of features for clusters on 5\% performance.}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../new_output/probend/_feature_importance_bar_plot_cluster_on_0_25.pdf}
-        \end{center}
-        \caption{Importance of features for clusters on 25\% performance.}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../new_output/probend/_feature_importance_bar_plot_cluster_on_0_5.pdf}
-        \end{center}
-        \caption{Importance of features for clusters on 50\% performance.}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../k_means_output/probend/_feature_importance_bar_plot.pdf}
-        \end{center}
-        \caption{Importance of features for clusters based on \(k\)means algorithm.}
-    \end{subfigure}
-    \caption{Importance of features in probabilistic ending tournaments for different
-    clustering methods.}\label{fig:clustering_importance_probend}
-\end{figure}
-
-\begin{figure}[!htbp]
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../new_output/probend_noise/_feature_importance_bar_plot_cluster_on_0_05.pdf}
-        \end{center}
-        \caption{Importance of features for clusters on 5\% performance.}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../new_output/probend_noise/_feature_importance_bar_plot_cluster_on_0_25.pdf}
-        \end{center}
-        \caption{Importance of features for clusters on 25\% performance.}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../new_output/probend_noise/_feature_importance_bar_plot_cluster_on_0_5.pdf}
-        \end{center}
-        \caption{Importance of features for clusters on 50\% performance.}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../k_means_output/probend_noise/_feature_importance_bar_plot.pdf}
-        \end{center}
-        \caption{Importance of features for clusters based on \(k\)means algorithm.}
-    \end{subfigure}
-    \caption{Importance of features in noisy probabilistic ending tournaments for different
-    clustering methods.}\label{fig:clustering_importance_probend_noise}
-\end{figure}
-
-\begin{figure}[!htbp]
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../new_output/merged/_feature_importance_bar_plot_cluster_on_0_05.pdf}
-        \end{center}
-        \caption{Importance of features for clusters on 5\% performance.}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../new_output/merged/_feature_importance_bar_plot_cluster_on_0_25.pdf}
-        \end{center}
-        \caption{Importance of features for clusters on 25\% performance.}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../new_output/merged/_feature_importance_bar_plot_cluster_on_0_5.pdf}
-        \end{center}
-        \caption{Importance of features for clusters on 50\% performance.}
-    \end{subfigure}
-    \begin{subfigure}[t]{0.5\textwidth}
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../k_means_output/merged/_feature_importance_bar_plot.pdf}
-        \end{center}
-        \caption{Importance of features for clusters based on \(k\)means algorithm.}
-    \end{subfigure}
-    \caption{Importance of features over all the tournaments for different
-    clustering methods.}\label{fig:clustering_importance_overall}
-\end{figure}
-
-\textbf{Evaluation based on linear regression.}
-
-Finally, a multivariate linear regression is fitted to model the relationship of
-Table's~\ref{table:manual_features} and the normalised rank. The \(p-\)values of
+A multivariate linear regression is fitted to model the relationship of
+Table's~\ref{table:manual_features} and the normalised rank. Based on the
+correlation matrices. Appendix~\ref{app:correlations} the depended variables are
+correlated. The median cooperating ration \(C_median\) and \(C_r/ C_median\) are highly
+correlated with \(C_mean\) and \(C_r / C_mean\). So these features are dropped from
+the analysis. The \(C_r\) is also correlated and drop. Finally for some environments
+the \(C_max\) and \(C_min\) are correlated and dropped for the models of those types.
+More specifically, the list of features their p values and \(p-\)values of
 each feature as well as their coefficients are given by
@@
     \centering
-    \includegraphics[width=.5\textwidth]{../images/compared_to_mean_median_standard.pdf}
-    \caption{Distributions of \(C_r / C_{\text{median}}\)
-    and \(C_r / C_{\text{median}}\) for winners of standard tournaments.}\label{fig:mean_median_std}
-\end{figure}
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.5\textwidth]{../images/compared_to_mean_median_noisy.pdf}
-    \caption{Distributions of \(C_r / C_{\text{median}}\)
-    and \(C_r / C_{\text{median}}\) for winners of noisy tournaments.}\label{fig:mean_median_noisy}
-\end{figure}
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.5\textwidth]{../images/compared_to_mean_median_probend.pdf}
-    \caption{Distributions of \(C_r / C_{\text{median}}\)
-    and \(C_r / C_{\text{median}}\) for winners of probabilistic ending tournaments.}\label{fig:mean_median_probend}
-\end{figure}
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.5\textwidth]{../images/compared_to_mean_median_probend_noisy.pdf}
-    \caption{Distributions of \(C_r / C_{\text{median}}\)
-    and \(C_r / C_{\text{median}}\) for winners of noisy probabilistic ending tournaments.}\label{fig:mean_median_probend_noisy}
-\end{figure}
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.5\textwidth]{../images/compared_to_mean_median_overall.pdf}
-    \caption{Distributions of \(C_r / C_{\text{median}}\)
-    and \(C_r / C_{\text{median}}\) for winners of over all the tournaments.}\label{fig:mean_median_overall}
+    \begin{subfigure}{0.35\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/compared_to_mean_standard.pdf}
+        \caption{Distributions of \(C_r / C_{\text{mean}}\) for winners of standard tournaments.}
+        % \label{fig:noisy_probend_results}
+    \end{subfigure}
+    \begin{subfigure}{0.35\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/sse_standard.pdf}
+        \caption{Distributions of SSE for winners of standard tournaments.}
+        % \label{fig:overall_results}
+    \end{subfigure}
+\end{figure}
+
+\begin{figure}[!htbp]
+    \centering
+    \begin{subfigure}{0.35\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/compared_to_mean_noisy.pdf}
+        \caption{Distributions of \(C_r / C_{\text{mean}}\) for winners of noisy tournaments.}
+        % \label{fig:noisy_probend_results}
+    \end{subfigure}
+    \begin{subfigure}{0.35\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/sse_noisy.pdf}
+        \caption{Distributions of SSE for winners of noisy tournaments.}
+        % \label{fig:overall_results}
+    \end{subfigure}
+\end{figure}
+
+\begin{figure}[!htbp]
+    \centering
+    \begin{subfigure}{0.35\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/compared_to_mean_probend.pdf}
+        \caption{Distributions of \(C_r / C_{\text{mean}}\) for winners of probabilistic ending tournaments.}
+        % \label{fig:noisy_probend_results}
+    \end{subfigure}
+    \begin{subfigure}{0.35\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/sse_probend.pdf}
+        \caption{Distributions of SSE for winners of probabilistic ending tournaments.}
+        % \label{fig:overall_results}
+    \end{subfigure}
+\end{figure}
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.5\textwidth]{../images/cd_to_c_probend.pdf}
+    % \caption{Distributions of \(C_r / C_{\text{median}}\)
+    % and \(C_r / C_{\text{median}}\) for winners of noisy probabilistic ending tournaments.}\label{fig:mean_median_probend_noisy}
+\end{figure}
+
+\begin{figure}[!htbp]
+    \centering
+    \begin{subfigure}{0.35\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/compared_to_mean_probend_noisy.pdf}
+        \caption{Distributions of \(C_r / C_{\text{mean}}\) for winners of noisy probabilistic ending tournaments.}
+        % \label{fig:noisy_probend_results}
+    \end{subfigure}
+    \begin{subfigure}{0.35\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/sse_probend_noisy.pdf}
+        \caption{Distributions of SSE for winners of noisy probabilistic ending tournaments.}
+        % \label{fig:overall_results}
+    \end{subfigure}
+\end{figure}
+
+\begin{figure}[!htbp]
+    \centering
+    \includegraphics[width=.65\textwidth]{../images/rates_of_winners_in_probend_noisy_tournaments.pdf}
+    % \caption{Distributions of \(C_r / C_{\text{median}}\)
+    % and \(C_r / C_{\text{median}}\) for winners of noisy probabilistic ending tournaments.}\label{fig:mean_median_probend_noisy}
+\end{figure}
+
+\begin{figure}[!htbp]
+    \centering
+    \begin{subfigure}{0.35\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/compared_to_mean_overall.pdf}
+        % \caption{Distributions of \(C_r / C_{\text{mean}}\) for winners of noisy probabilistic ending tournaments.}
+        % \label{fig:noisy_probend_results}
+    \end{subfigure}
+    \begin{subfigure}{0.35\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/rate_overall.pdf}
+        % \caption{Distributions of SSE for winners of noisy probabilistic ending tournaments.}
+        % \label{fig:overall_results}
+    \end{subfigure}
 \end{figure}
@@
 
-\section{A summary of parameters}\label{app:parameters}
-
-\begin{table}[h]
-    \begin{center}
-    \resizebox{.7\textwidth}{!}{
-    \begin{tabular}{llc}
-    \toprule
-feature & feature explanation \\
- \midrule
-stochastic                  & If a strategy is stochastic \\
-makes use of game           & If a strategy makes used of the game information  \\
-makes use of length         & If a strategy makes used of the number of turns \\
-memory usage                & The memory size of a strategy divided by the number of turns \\
-SSE                         & A measure of how far a strategy is from extortionate behaviour \\
-$C_{\text{max}}$          & The biggest cooperating rate in the tournament \\
-$C_{\text{min}}$          & The smallest cooperating rate in the tournament \\
-$C_{\text{median}}$       & The median cooperating rate in the tournament \\
-$C_{\text{mean}}$         & The mean cooperating rate in the tournament \\
-$C_r$ / $C_{\text{max}}$    & A strategy's cooperating rate divided by the maximum \\
-$C_r$ / $C_{\text{min}}$    & A strategy's cooperating rate divided by the minimum \\
-$C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median \\
-$C_r$ / $C_{\text{mean}}$   & A strategy's cooperating rate divided by the mean \\
-$C_r$                       & The cooperating ratio of a strategy \\
-$CC$ to $C$ rate            & The probability a strategy will cooperate after a mutual cooperation \\
-$CD$ to $C$ rate            & The probability a strategy will cooperate after being betrayed by the opponent \\
-$DC$ to $C$ rate            & The probability a strategy will cooperate after betraying the opponent\\
-$DD$ to $C$ rate            & The probability a strategy will cooperate after a mutual defection\\
-$p_n$                       & The probability of a player's action being flipped at each interaction \\
-$n$                         & The number of turns \\
-$p_e$                       & The probability of a match ending in the next turn \\
-$N$                         & The number of strategies in the tournament \\
-$k$                         & The number that a given tournament is repeated \\
-    \bottomrule
-        \end{tabular}}
-    \end{center}
-    \caption{The features which are included in the performance evaluation analysis.}\label{table:parameters_summary}
-\end{table}
-
-\section{List of strategies}\label{app:list_of_players}
-
-The strategies used in this study which are from Axelrod-Python library version 3.0.0.
-
-\begin{multicols}{3}
-	\begin{enumerate}
-		\input{list_of_strategies.tex}
-	\end{enumerate}
-\end{multicols}
-
-\section{Correlation coefficients}\label{app:correlations}
-
-A graphical representation of the correlation coefficients for the features in
-Table~\ref{table:manual_features}.
-
-\begin{figure}[!htbp]
-        \begin{center}
-            \includegraphics[width=.75\linewidth]{../images/standard_correlation_plot.pdf}
-        \end{center}
-        \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-        for standard tournaments}
-\end{figure}
-\begin{figure}[!htbp]
-    \begin{center}
-        \includegraphics[width=.75\linewidth]{../images/noise_correlation_plot.pdf}
-    \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-    for noisy tournaments}
-\end{figure}
-\begin{figure}[!htbp]
-    \begin{center}
-        \includegraphics[width=.75\linewidth]{../images/probend_correlation_plot.pdf}
-    \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-    for probabilistic ending tournaments}
-\end{figure}
-\begin{figure}[!htbp]
-    \begin{center}
-        \includegraphics[width=.75\linewidth]{../images/probend_noise_correlation_plot.pdf}
-    \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-    for noisy probabilistic ending tournaments}
-\end{figure}
-\begin{figure}[!htbp]
-    \begin{center}
-        \includegraphics[width=.75\linewidth]{../images/merged_correlation_plot.pdf}
-    \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-    for data set}
-\end{figure}
+\input{parameters_section}
+% \input{overall_results}
+\input{correlation_section}
+\input{random_forest_evaluation}
 

### 2020-03-27 src/process_data.py
fix fsm strategies memory

@@ -37,6 +37,11 @@ def get_memory_percentage(row):
         return 0
     return row["Memory_depth"] / row["turns"]
 
+def fix_fsm_memory(row):
+    if 'FSM' in row['Name']:
+        return np.inf
+    else:
+        return row['Memory_depth']
 
 def get_strategies_properties():
     """
@@ -126,15 +131,12 @@ if __name__ == "__main__":
     file = sys.argv[1]
     output = file.replace(".csv", "_processed.csv")
 
-    # replace = {"Slow Tit For Two Tats": "Tit For 2 Tats"}
-
     strategies_properties = get_strategies_properties()
     strategies_properties = strategies_properties.set_index("Name")
 
     df = pd.read_csv(file, index_col=0)
 
     print("Processing")
-    # df = df.replace(replace)
     df["SSE"] = df.apply(get_error_for_row, axis=1)
     df["Name"] = df.apply(fix_name, axis=1)
 
@@ -200,6 +202,8 @@ if __name__ == "__main__":
     to_drop = df[df["Normalized_Rank"] > 1]["seed"].unique()
     if len(to_drop) != 0:
         df = df[~(df["seed"].isin(to_drop))]
+
+    df["Memory_depth"] = df.apply(get_memory_percentage, axis=1)
 
     if "turns" in df.columns:
         df["memory_usage"] = df.apply(get_memory_percentage, axis=1)

### 2020-03-27 paper/main.tex
finalise introduction

@@
 \usepackage{wrapfig, blindtext}
+\usepackage{soul}
 \usepackage[table]{xcolor}
@@
 tournaments, presents the top performing strategies, and analyzes their
-salient features. The results of the tournaments imply that there is not a single
-type of strategy that performs well in any Iterated Prisoner's Dilemma interaction.
+salient features. The results imply that there is not a single
+strategy that performs well in any Iterated Prisoner's Dilemma interaction.
 There are several properties, however, that heavily influence the best performing
-strategies: be nice, be provocable, be a little envious and be clever.
+strategies, these are: be nice, be provocable, be a little envious, be clever
+and adapt to the environment.
 \end{abstract}
@@
 
-In the 80's, Axelrod performed two computer tournaments~\cite{Axelrod1980a,
-Axelrod1980b}. The
+Axelrod performed two computer tournaments~\cite{Axelrod1980a,
+Axelrod1980b} in the 80's. The
 winner of both tournaments was the simple strategy Tit For Tat which cooperated
 on the first turn and then simply copied the previous action of its opponent.
-Axelrod concluded that the strategy's robustness was due to four different
-properties:
+Axelrod concluded that the strategy's robustness was due to four properties, which
+he adapted in four suggestions on doing well in an IPD:
 
@@
     \item Be "nice"; Do not be the first to defect
-    \item Reciprocate both cooperation and defection
+    \item Reciprocate both cooperation and defection; Be provocable
     \item Do not be too clever
@@
 
-Further research proved that the strategy had weakness, and more
-specifically, it was shown that the strategy suffered in environments with
-noise~\cite{Bendor1991, Donninger1986, Molander1985, Hammerstein1984}. This was
+There are strategies which have built upon Tit For Tat, and the reciprocity based approach.
+In~\cite{Beaufils1997} Gradual was introduced which was constructed to have the
+same qualities as those of Tit for Tat except one, Gradual had a memory
+of the game since the beginning of it. Gradual recorded the number of defections
+by the opponent and punished them with a growing number of defections. It would
+then enter a calming state in which it would cooperates for two rounds. A
+strategy with the same intuition as Gradual is Adaptive Tit for
+Tat~\cite{tzafestas-2000a}. Adaptive Tit for Tat does not keep a permanent
+count of past defections, it maintains a continually updated estimate of the
+opponent's behaviour, and uses this estimate to condition its future actions.
+
+Other works have built upon the limitations of the strategy, and others have shown
+that suggestions made by Axelrod were incomplete.
+In~\cite{Bendor1991, Donninger1986, Molander1985, Hammerstein1984} it was shown
+that Tit For Tat suffered in environments with noise. This was
 mainly due to the strategy's lack of generosity and contrition. The strategy was
@@
 Pavlov~\cite{Nowak1993} and Generous Tit For Tat~\cite{Nowak1992}.
-Several works extended the reciprocity based approach which has led to new
-strategies. For example Gradual~\cite{Beaufils1997} which was constructed to
-have the same qualities as those of Tit for Tat except one,
-\textit{Gradual} had a memory of the game since the beginning of it. Gradual
-recorded the number of defections by the opponent and punished them with a
-growing number of defections. It would then enter a calming state in which it
-would cooperates for two rounds. In a tournament of 12 strategies, including
-both Tit for Tat and Pavlov, Gradual managed to outperformed them all. A
-strategy with the same intuition as Gradual is \textit{Adaptive Tit for
-Tat}~\cite{tzafestas-2000a}. Adaptive Tit for Tat does not keep a permanent
-count of past defections, it maintains a continually updated estimate of the
-opponent’s behaviour, and uses this estimate to condition its future actions. In
-the exact same tournament as in~\cite{Beaufils1997} with now 13 strategies Adaptive
-Tit for Tat ranked first.
-A set of IPD strategies that have received a lot of attention
-are the zero-determinant strategies (ZDs)~\cite{Press2012}. By
+In~\cite{Press2012} a set of envious IPD strategies that have received a lot of
+attention were introduced called the zero-determinant strategies (ZDs). By
 forcing a linear relationship between the payoffs ZDs can ensure that they will
-never receive less than their opponents. The
-American Mathematical Society's news section stated that ``the world of game
-theory is currently on fire''.
-ZDs are indeed a set of mathematically unique strategies
-and robust in pairwise interactions, however, their superiority in tournament settings
-have been tested. In~\cite{Harper2017} a tournament containing over
-200 strategies, including ZDs, was ran and none of them
-ranked in top spots. Instead, the top ranked strategies were a set of
-trained strategies based on lookup tables~\cite{Axelrod1987}, hidden markov
+never receive less than their opponents. ZDs are indeed a set of mathematically
+unique strategies and robust in pairwise interactions, however, their
+superiority in tournament settings have been tested. In~\cite{Harper2017} a
+series of clever strategies were introduced, and a tournament containing over
+200 strategies was ran and none of the aforementioned strategies ranked in top
+spots. Instead, the top ranked strategies were the set of clever trained
+strategies based on lookup tables~\cite{Axelrod1987}, hidden markov
 models~\cite{Harper2017} and finite state automata~\cite{Miller1996}.
 
-Though only select pieces of work have been discussed, the IPD literature is
-rich, and new strategies and competitions are being published every year~\cite{Glynatsi2019}. The
-question, however, still remains the same: what is the best way to play the
-game? Compared to other works, whereas a few selected strategies are evaluated
+Though only select pieces of work have been discussed, there is a board number
+of strategies in the literature, and new strategies and competitions are being
+published every year~\cite{Glynatsi2019}. The question, however, still remains
+the same: what is the best way to play the game?
+
+Compared to other works, whereas a few selected strategies are evaluated
 on a small number of tournaments, this manuscript evaluates the performance of \numberofstrategies
@@
 strategy's behaviour and measures regarding the tournaments. The outcomes of our
-work reinforce the discussion started by Axelrod:
+work reinforce the discussion started by Axelrod, and it concludes that the properties
+of a successful strategy in the IPD are:
 
 \begin{itemize}
-    \item Do not be envious
+    \item \st{Do not be envious}
     \item Be "nice"; Do not be the first to defect
-    \item Reciprocate both cooperation and defection
-    \item Do not be too clever
+    \item Reciprocate both cooperation and defection; Be provocable
+    \item \st{Do not be too clever}
+    \item Adapt to the environment; Adjust to the mean cooperator
 \end{itemize}
-
-Furthermore, the data set used
-in this work has been made publicly available~\cite{data} and can be used
-for further analysis and insights.
 
@@
 possible due to an open source package called Axelrod-Python,
-are covered in Section~\ref{section:data_collection}.
+are covered in Section~\ref{section:data_collection}. The data set generated
+for this work has been made publicly available~\cite{data} and can be used
+for further analysis and insights.
 Section~\ref{section:top_performances}, focuses on the best performing

### 2020-03-27 paper/parameters_section.tex
finalise introduction

\section{Parameters Summary}\label{app:parameters}

All the parameters used in this manuscript alongside their explanation are
given by Table~\ref{table:parameters_summary}.

\begin{table}[!htbp]
    \begin{center}
    \resizebox{.7\textwidth}{!}{
    \begin{tabular}{ll}
    \toprule
Feature & Explanation \\
 \midrule
SSE                       & A measure of how far a strategy is from extortionate behaviour defined in~\cite{Knight2019}. \\
$C_{\text{max}}$          & The biggest cooperating rate in the tournament. \\
$C_{\text{min}}$          & The smallest cooperating rate in the tournament. \\
$C_{\text{median}}$       & The median cooperating rate in the tournament. \\
$C_{\text{mean}}$         & The mean cooperating rate in the tournament. \\
$C_r$ / $C_{\text{max}}$    & A strategy's cooperating rate divided by the maximum cooperating rate in the tournament. \\
$C_{\text{min}}$ / $C_r$    & The minimum in the tournament divided by a strategy's cooperating rate. \\
$C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median cooperating rate in the tournament. \\
$C_r$ / $C_{\text{mean}}$   & A strategy's cooperating rate divided by the mean cooperating rate in the tournament. \\
$C_r$                       & The cooperating rate of a strategy. \\
$CC$ to $C$ rate            & The probability a strategy will cooperate after a mutual cooperation. \\
$CD$ to $C$ rate            & The probability a strategy will cooperate after being betrayed by the opponent. \\
$DC$ to $C$ rate            & The probability a strategy will cooperate after betraying the opponent. \\
$DD$ to $C$ rate            & The probability a strategy will cooperate after a mutual defection. \\
$p_n$                       & The probability of a player's action being flipped at each interaction. \\
$n$                         & The number of turns in a match. \\
$p_e$                       & The probability of a match ending in the next turn. \\
$N$                         & The number of strategies in the tournament. \\
$k$                         & The number that a given tournament is repeated. \\
    \bottomrule
        \end{tabular}}
    \end{center}
    \caption{The features which are included in the performance evaluation analysis.}\label{table:parameters_summary}
\end{table}

### 2020-03-27 paper/main.tex
finalise data collection section

@@
 
-The process of collecting tournament results implemented in this manuscript is described by
+The process of collecting tournament results is described by
 Algorithm~\ref{algorithm:data_generation}. For each trial a random size \(N\) is
@@
 
-The result summary, Table~\ref{table:output_result}, has \(N\) number of rows
+A result summary (Table~\ref{table:output_result}) has \(N\) number of rows
 because each row contains information for each strategy that participated in the
@@
 strategy, denoted as \(R\), can vary between 0 and \(N-1\). Thus, the normalised rank,
-denoted as $r$, is calculated as a strategy's rank divided by the tournament's
-size \(N - 1\). In the next section the performance of these strategies is evaluated
-based on their normalised rank.
+denoted as $r$, is calculated as a strategy's rank divided by \(N - 1\).
 
@@
 \end{table}
+
+In the next section the performance of the \numberofstrategies IPD strategies is
+evaluated based on their normalised rank.
 

### 2020-03-27 paper/main.tex
finalises top performances section

@@
 
-This section evaluates the performance of \numberofstrategies IPD strategies. The performance of
-each strategy is evaluated in four tournament types, which were presented in Section
-\ref{section:data_collection}, followed by an evaluation of their performance
-over all the \numberofalltournaments simulated tournaments of this work.
-
-Each strategy participated in multiple tournaments of the same type (on average 5154).
-For example Tit For Tat has participated in a total of 5114
-tournaments of each type. The strategy's normalised rank distribution in these
-is given in Figure~\ref{fig:tit_for_tat_r_distribution}. A value of \(r =
-0\) corresponds to a strategy winning the tournament where a value of
-\(r = 1\) corresponds to the strategy coming last. Because of the strategies'
-multiple entries their performance is evaluated based on the
+The performance of each strategy is evaluated in four tournament types, which
+were presented in Section \ref{section:data_collection}, followed by an
+evaluation of their performance over all the \numberofalltournaments simulated
+tournaments of this work. Each strategy participated in multiple tournaments of
+the same type (on average 5154). For example Tit For Tat has participated in a
+total of 5114 tournaments of each type. The strategy's normalised rank
+distribution in these is given in Figure~\ref{fig:tit_for_tat_r_distribution}. A
+value of \(r = 0\) corresponds to a strategy winning the tournament where a
+value of \(r = 1\) corresponds to the strategy coming last. Because of the
+strategies' multiple entries their performance is evaluated based on the
 \textbf{median normalised rank} denoted as \(\bar{r}\).
@@
 Table~\ref{table:top_performances}. The data collection process was design such
-as that the probabilities of noise and ending of the match to vary between 0 and
+as that the probabilities of noise and ending of the match varied between 0 and
 1. However, commonly used values of these probabilities are
@@
 \end{center}
-\caption{Top performances for each tournament type based on $\bar{r}$. The results
-of each type are based on 11420 unique tournaments of each type. The results
-for noisy tournaments with \(p_n < 0.1\) are based on 1151 tournaments, and 
-for probabilistic ending tournaments with \(p_e < 0.1\) on 1139. The top ranks
-indicate that trained strategies perform well in a variety of environments,
-but so do simple deterministic strategies. The normalised medians are close to 0
-for most environments, except environments with noise not restricted to 0.1.
-These two tournaments have the highest medians, implying that strategies from
-the collection of this work can not perform well in environments with such high
-values of noise.}
+\caption{Top performances for each tournament type based on $\bar{r}$. The
+results of each type are based on 11420 unique tournaments of each type. The
+results for noisy tournaments with \(p_n < 0.1\) are based on 1151 tournaments,
+and for probabilistic ending tournaments with \(p_e < 0.1\) on 1139. The top
+ranks indicate that trained strategies perform well in a variety of
+environments, but so do simple deterministic strategies. The normalised medians
+are close to 0 for most environments, except environments with noise not
+restricted to 0.1 regardless the number of turns. Noisy and noisy probabilistic
+ending tournaments have the highest medians. This implies that strategies from
+the collection of this work do not perform well in environments with high values
+of noise.}
 \label{table:top_performances}
@@
 
-Distributions of these top ranked strategies are given by Figure~\ref{fig:r_distributions}.
-\newpage
+The \(r\) distributions for the top ranked strategies of Table~\ref{table:top_performances}
+are given by Figure~\ref{fig:r_distributions}.
 
@@
     \centering
-    \begin{subfigure}{0.475\textwidth}
+    \begin{subfigure}{0.485\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{../images/performance_standard.pdf}
-        \caption{$r$ distributions in standard tournaments.}\label{fig:std_results}
+        \includegraphics[width=\textwidth]{../images/r_distribution_standard.pdf}
+        \caption{$r$ distributions of top 15 strategies in standard tournaments.}\label{fig:std_results}
     \end{subfigure}
     \hfill
-    \begin{subfigure}{0.475\textwidth}
+    \begin{subfigure}{0.485\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{../images/noise_performance_subset.pdf}
-        \caption{$r$ distributions of top 15 strategies in 1151 noisy tournaments with \(p_n < 0.1\).}\label{fig:noise_results}
+        \includegraphics[width=\textwidth]{../images/r_distribution_noise_subset.pdf}
+        \caption{$r$ distributions of top 15 strategies in noisy tournaments with \(p_n < 0.1\).}\label{fig:noise_subset_results}
     \end{subfigure}
     \vskip\baselineskip
-    \begin{subfigure}{0.475\textwidth}
+    \begin{subfigure}{0.485\textwidth}
         \centering 
-        \includegraphics[width=\textwidth]{../images/performance_noise.pdf}
-        \caption{$r$ distributions of top 15 strategies in noisy tournaments.}\label{fig:noise_overall_results}
+        \includegraphics[width=\textwidth]{../images/r_distribution_noise.pdf}
+        \caption{$r$ distributions of top 15 strategies in noisy tournaments.}\label{fig:noise_results}
     \end{subfigure}
     \quad
-    \begin{subfigure}{0.475\textwidth}
+    \begin{subfigure}{0.485\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{../images/probend_performance_subset.pdf}
-        \caption{\(r\) distributions for best performed strategies in 1139 probabilistic ending
+        \includegraphics[width=\textwidth]{../images/r_distribution_probend_subset.pdf}
+        \caption{\(r\) distributions of top 15 strategies in 1139 probabilistic ending
         tournaments with \(p_e < 0.1\).}
-        \label{fig:probend_results}
+        \label{fig:probend_subset_results}
     \end{subfigure}
-    \caption{\(r\) distributions of the top 15 strategies in different environments. A lower value of
-    \(\bar{r}\) corresponds to a more successful performance. A strategy's \(r\) distribution skewed towards zero
-    indicates that the strategy ranked highly in most tournaments it participated in.}\label{fig:r_distributions}
+    \vskip\baselineskip
+    \begin{subfigure}{0.485\textwidth}
+        \centering 
+        \includegraphics[width=\textwidth]{../images/r_distribution_probend.pdf}
+        \caption{$r$ distributions of top 15 strategies in probabilistic ending tournaments.}\label{fig:probend_results}
+    \end{subfigure}
+    \quad
+    \begin{subfigure}{0.485\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/r_distribution_probend_noise.pdf}
+        \caption{$r$ distributions of top 15 strategies in noisy probabilistic ending tournaments.}
+        \label{fig:probend_noise_results}
+    \end{subfigure}
+    \caption{\(r\) distributions of the top 15 strategies in different
+    environments. A lower value of \(\bar{r}\) corresponds to a more successful
+    performance. A strategy's \(r\) distribution skewed towards zero indicates
+    that the strategy ranked highly in most tournaments it participated in. Most
+    distributions are skewed towards zero except the distributions with
+    unrestricted noise, supporting the conclusions from
+    Table~\ref{table:top_performances}.}\label{fig:r_distributions}
 \end{figure*}
@@
 set to defect on the last two rounds. It should be noted that these
-strategies can be characterised as "cheaters". The source code of the strategies
+strategies can be characterised as "cheaters" because the source code of the strategies
 allows them to known the number of turns in a match (if they are specified).
@@
 tournaments where the number of turns is not specified. Finally, Winner
-12~\cite{mathieu2017} and DBS~\cite{Au2006} are both from the the literature.
-DBS is a strategy specifically designed for noisy environments and it ranks
+12~\cite{mathieu2017} and DBS~\cite{Au2006} are both from the literature.
+DBS is a strategy specifically designed for noisy environments, however, it ranks
 highly in standard tournaments as well.
-Figure~\ref{fig:std_results} gives the distributions of $r$ for the top
-ranked strategies. The distributions are skewed towards zero and the highest
-median, of the top 15 strategies, is at 0.075. This indicates that the top ranked
-strategies perform well in any given standard tournament, despite the opponents and
-the number of turns.
+Figure~\ref{fig:std_results} supports that these strategies are to perform
+well in any standard tournament they participate.
 
 In the case of noisy tournaments with \(p_n < 0.1\) the top performed strategies
-include strategies specifically designed for noisy tournaments such as DBS,
+include strategies specifically designed for noisy tournaments. These are DBS,
 Evolved FSM 16 Noise 05, Evolved ANN 5 Noise 05, PSO Gambler 2 2 2 Noise 05 and
-Omega Tit For Tat~\cite{kendall2007iterated}, strategies which performed well in
-standard tournaments such as BackStabber, DoubleCrosser, Evolved ANN, FSM and
-HMM and deterministic strategies such as Spiteful Tit For Tat~\cite{prison},
-Level Punisher~\cite{Eckhart2015}, Eugine Nier~\cite{lesswrong}. The \(r\) distributions
-of these strategies are given in Figure~\ref{fig:noise_results} where it is evident
-that these strategies overall performed well in noisy tournaments.
-In comparison, the top ranked strategies in noisy environments when \(p_n\in [0,
-1]\) include strategies which decide their actions based on the cooperations to
-defections ratio, such as ShortMem~\cite{Andre2013},
-Grumpy~\cite{axelrodproject} and e~\cite{axelrodproject}, and the Retaliate
-strategies which are designed to defect if the opponent has tricked them more
-often than x\% of the times that they have done the same. The overall
-performance of these strategies is bimodal,
-Figure~\ref{fig:noise_overall_results}, indicating that although the top
-ranked strategies mainly performed well, there are several tournaments that they
-ranked in the bottom half. The bimodality of the \(r\) distributions can be
-explained by Figure~\ref{fig:effect_of_noise} which gives the \(r\)
-distributions for the top 6 strategies over the noise probability \(p_n\).
-It is evident that the highly ranked strategies
+Omega Tit For Tat~\cite{kendall2007iterated}. The rest of the top ranks are
+occupied by strategies which performed well in standard tournaments and
+deterministic strategies such as Spiteful Tit For Tat~\cite{prison}, Level
+Punisher~\cite{Eckhart2015}, Eugine Nier~\cite{lesswrong}. Similarly to standard
+tournaments, the successful strategies in this given setting performed well
+overall in the tournaments they participated in,
+Figure~\ref{fig:noise_subset_results}.
+
+In comparison, the performance the top ranked strategies in noisy environments
+when \(p_n\in [0, 1]\) is bimodal. The top strategies include strategies which
+decide their actions based on the cooperations to defections ratio, such as
+ShortMem~\cite{Andre2013}, Grumpy~\cite{axelrodproject} and
+e~\cite{axelrodproject}, and the Retaliate strategies which are designed to
+defect if the opponent has tricked them more often than x\% of the times that
+they have done the same. The bimodality of the \(r\) distributions is explained
+by Figure~\ref{fig:effect_of_noise} which demonstrates that the top 6 strategies
 were highly ranked due to the their performance in tournaments with \(p_n>0.5\),
@@
     \centering
-    \includegraphics[width=\textwidth]{../images/noise_effect.pdf}
+    \includegraphics[width=.92\textwidth]{../images/noise_effect.pdf}
     \caption{\(r\) distributions for top 6 strategies in noisy tournaments over
@@
 
-In probabilistic ending tournaments with \(p_e < 0.1\) the effective strategies
-are Meta strategies which include Nice Meta Winner, NMWE Finite Memory, NMWE
-Deterministic, trained strategies which performed well in standard tournaments,
-Grudger~\cite{axelrodproject} and Spiteful Tit for Tat~\cite{prison}. The Meta
-strategies~\cite{axelrodproject} are a set of rules that create a team of
+The most effective strategies in probabilistic ending tournaments with \(p_e
+< 0.1\) are a series of Meta strategies, trained strategies which performed well
+in standard tournaments, and  Grudger~\cite{axelrodproject} and Spiteful Tit for
+Tat~\cite{prison}. he Meta strategies~\cite{axelrodproject} create a team of
 strategies and play as an ensemble or some other combination of their team
-members. The distributions of the normalised rank in the 1139 probabilistic
-ending tournaments with \(p_e < 0.1\), are shown in
-Figure~\ref{fig:probend_results}. The medians of the top 15 strategies are lower
-than 0.1 and the distributions are skewed towards 0. The strategies have overall
-performed well in the probabilistic ending tournaments that they participated.
+members. Figure~\ref{fig:probend_subset_results} indicates that these strategies
+performed well in any probabilistic ending tournament they competed in.
 
@@
 Fortress 4 (both introduced in~\cite{Ashlock2006}), Raider~\cite{Ashlock2014}
-and Solution B1~\cite{Ashlock2014}. As stated in the Folk Theorem~\cite{Fudenberg2009}
-defecting strategies do better when the likelihood of the game ending in the
-next turn increased. This is demonstrated by Figure~\ref{fig:effect_of_probend}, which gives the
+and Solution B1~\cite{Ashlock2014}. The success of defecting strategies in
+probabilistic ending tournaments was excepted. As stated in the Folk
+Theorem~\cite{Fudenberg2009} defecting strategies do better when the likelihood
+of the game ending in the next turn increases.
+This is demonstrated by Figure~\ref{fig:effect_of_probend}, which gives the
 distributions of \(r\) for the top 6 strategies in probabilistic ending tournaments
-over \(p_e\). It  shows that the 6 strategies start of with a high median rank,
-however, their ranked decreased as the the probability of the game ending
-increased and at the point of \(p_e = 0.1\).
+over \(p_e\).
 
@@
     \centering
-    \includegraphics[width=\textwidth]{../images/folk_theorem.pdf}
+    \includegraphics[width=.92\textwidth]{../images/folk_theorem.pdf}
     \caption{\(r\) distributions for top 6 strategies in probabilistic ending tournaments
-    over $p_e$.}
+    over $p_e$. The 6 strategies start of with a high median rank,
+    however, their ranked decreased as the the probability of the game ending
+    increased and at the point of \(p_e = 0.1\).}
     \label{fig:effect_of_probend}
@@
 
-In tournaments with both noise and an unspecified number of turns several of the
-top ranked strategies are strategies that were highly ranked in noisy
-tournaments. However, strategies from the top ranks in probabilistic ending
-tournaments did not rank highly here.
-The distributions of \(r\) shown in Figure~\ref{fig:noisy_probend_results} have
-the largest median values compared to the top rank strategies of the other
-tournament types. A subset of noisy probabilistic ending tournaments has been
-considered such that \(p_e < 0.1\) and \(p_n < 0.1\). The top ranked strategies
-are given in Table~\ref{table:subset_probend_noise_result} and it is shown that
-the Meta strategies which performed well in noisy tournaments with \(p_n <
-0.1\), perform well once again even the number of turns is not specified.
-Moreover, several strategies that did well in probabilistic ending tournaments
-such as Fortress 4, MEM2 and Spiteful Tit For Tat.
+The top performances in tournaments with both noise and a probabilistic ending
+and the top performances over the entire data set have the largest median values
+compared to the top rank strategies of the other tournament types,
+Figure~\ref{fig:probend_noise_results} and Figure~\ref{fig:overall_results}. The
+\(\bar{r}\) for the top strategy is approximately at 0.3, indicating that the
+most successful strategy can on average just place at the top 30\% of the
+competition.
 
@@
     \centering
-    \resizebox{.55\textwidth}{!}{
-    \input{performance_probend_noise_subset_table.tex}}
-    \caption{Top performances in 117 probabilistic ending tournaments with \(p_e < 0.1\) and \(p_n < 0.1\).}
-    \label{table:subset_probend_noise_result}
+    \resizebox{.30\textwidth}{!}{
+    \input{performance_merged_table.tex}}
+    \caption{Top performances over all the tournaments. The top ranks include
+    strategies that have been previously mentioned. The set of Retaliate
+    strategies occupy the top spots followed by BackStabber and DoubleCrosser.
+    The distributions of the Retaliate strategies have no statistical
+    difference. Thus, in an IPD tournament where the type is not specified,
+    playing as any of the Retaliate strategies will have same the result. PSO
+    Gambler and Evolved HMM 5 are trained strategies introduced
+    in~\cite{Harper2017} and Nice Meta Winner and NMWE Memory One are strategies
+    based on teams. Grudger is a strategy from Axelrod's original tournament and
+    Forgetful Fool Me Once is based on the same approach as
+    Grudger.}\label{table:overall_results}
 \end{table}
@@
         \centering
-    \begin{subfigure}{0.475\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/performance_probend_noise.pdf}
-        \caption{\(r\) distributions for best performed strategies in noisy
-        probabilistic ending tournaments.}
-        \label{fig:noisy_probend_results}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.475\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/performance_merged.pdf}
-        \caption{\(r\) distributions for best performed strategies in the data set~\cite{data}.}
+        \includegraphics[width=.65\textwidth]{../images/performance_merged.pdf}
+        \caption{\(r\) distributions for best performed strategies in the data set~\cite{data}.
+        A lower value of \(\bar{r}\) corresponds to a more successful
+        performance.}
         \label{fig:overall_results}
-    \end{subfigure}
-    % \caption{\(r\) distributions of the top 15 strategies in different environments. A lower value of
-    % \(\bar{r}\) corresponds to a more successful performance. A strategy's \(r\) distribution skewed towards zero
-    % indicates that the strategy ranked highly in most tournaments it participated in.}\label{fig:r_distributions}
 \end{figure}
 
-This section presented the winning strategies in a series of IPD tournaments. In
-standard tournaments the top spots were dominated by complex strategies that had
-been trained using reinforcement learning techniques. In noisy environments where
-the a noise probability strictly less than 0.1 was considered the successful
-strategies were strategies based on the behaviour of many strategies and strategies
-specifically designed for noisy tournaments. In
-probabilistic ending tournaments most of the highly ranked strategies were defecting
-strategies and trained finite state automata, all by the authors of~\cite{Ashlock2006, Ashlock2014}.
-These strategies ranked high due to their performance in tournaments where the probability of the game ending after
-each turn was bigger than 0.1. In probabilistic tournaments with \(p_e\) less than 0.1
-the highly ranked strategies were trained and Meta strategies.
-Finally the performance of all \numberofstrategies
-strategies over the \numberofalltournaments tournaments in this manuscript was
-assessed on \(\bar{r}\). The top ranked strategies were a mixture of behaviours
-that did well in standard tournaments, tournaments with noise and a
-few Meta strategies.
-The results of this section imply that successful strategies for specific
-settings exist for an IPD tournament. The top ranked strategies in both standard
-tournaments and tournaments with probabilistic ending, managed to rank in the
-top 10\% of the tournament most of the times.
-Strategies in noisy
-environments demonstrated that no strategy can be consistently
-successful, expected if the value of noise is constrained to less than a 0.1.
-Trained strategies, meta strategies and some deterministic defecting strategies
-have demonstrated good performance over several tournament types, however,
-there exists no one single strategy which appears to be dominant in an IPD
-competition. The aim of the next section is to understand which are
-the factors that made these strategies successful, in each setting separately
-but also overall.
+On the whole, the analysis of this manuscript has shown that:
 
-Be envious and be clever.
+\begin{itemize}
+    \item In standard tournaments the dominating strategies were clever
+    strategies that had been trained using reinforcement learning techniques.
+    \item In noisy environments where the noise probability strictly less than
+    0.1 was considered, the successful strategies were strategies specifically
+    designed for noisy environments.
+    \item In probabilistic ending tournaments most of the highly ranked
+    strategies were defecting strategies and trained finite state automata, all
+    by the authors of~\cite{Ashlock2006, Ashlock2014}. These strategies ranked
+    high due to their performance in tournaments where the probability of the
+    game ending after each turn was bigger than 0.1.
+    \item In probabilistic tournaments with \(p_e\) less than 0.1 the highly
+    ranked strategies were strategies based on the behaviour of others.
+    \item From the collection of strategies considered here,  no strategy can be
+    consistently successful in noisy environments, except if the value of noise
+    is constrained to less than a 0.1.
+\end{itemize}
+
+Though there is not a single strategy that repeatably outranks all others in any
+of the distinct tournament types, or even across the tournaments type, there
+are specific types of strategies have been repeatably ranked in the top ranks.
+These have been strategies that have been trained, strategies that defected
+and strategies that would adapt their behaviour based on preassigned rules
+to achieve the highest outcome. These results contradict Axelrod's suggestions,
+and more specifically, the suggestions `Do not be clever' and `Do not be envious'.
 
@@
 \input{parameters_section}
-% \input{overall_results}
 \input{correlation_section}
 \input{random_forest_evaluation}
+\input{strategies_list_section}
 

### 2020-03-27 paper/perfomances_table.tex
finalises top performances section

--- 2019-10-24 paper/perfomances_table.tex
@@
-\begin{tabular}{lllllllll}
+\begin{tabular}{lllllllllllll}
 \toprule
-{} &                     Name & \$\textbackslash bar\{r\}\$ &                 Name & \$\textbackslash bar\{r\}\$ &               Name & \$\textbackslash bar\{r\}\$ &                 Name & \$\textbackslash bar\{r\}\$ \\
+{} &                     Name & \$\textbackslash bar\{r\}\$ &                   Name & \$\textbackslash bar\{r\}\$ &                        Name & \$\textbackslash bar\{r\}\$ &               Name & \$\textbackslash bar\{r\}\$ &                       Name & \$\textbackslash bar\{r\}\$ &                 Name & \$\textbackslash bar\{r\}\$ \\
 \midrule
-0  &            Evolved HMM 5 &   0.00667 &               Grumpy &    0.1402 &          Fortress4 &   0.01266 &           Alternator &    0.3037 \\
-1  &           Evolved FSM 16 &   0.00995 &                  \$e\$ &   0.19388 &           Defector &   0.01429 &               \$\textbackslash phi\$ &   0.30978 \\
-2  &     EvolvedLookerUp2\_2\_2 &   0.01064 &       Tit For 2 Tats &    0.2069 &  Better and Better &   0.01587 &                  \$e\$ &    0.3125 \\
-3  &  Evolved FSM 16 Noise 05 &   0.01667 &         Cycle Hunter &   0.21538 &    Tricky Defector &   0.01875 &                \$\textbackslash pi\$ &   0.31686 \\
-4  &        PSO Gambler 2\_2\_2 &   0.02143 &       Risky QLearner &   0.22222 &          Fortress3 &   0.02174 &    Limited Retaliate &   0.35263 \\
-5  &              Evolved ANN &   0.02878 &          Retaliate 3 &   0.22887 &     Gradual Killer &   0.02532 &     Anti Tit For Tat &   0.35431 \\
-6  &            Evolved ANN 5 &    0.0339 &        Cycler CCCCCD &   0.23507 &         Aggravater &   0.02778 &          Retaliate 3 &   0.35563 \\
-7  &        PSO Gambler 1\_1\_1 &   0.03704 &          Retaliate 2 &   0.23913 &             Raider &   0.03077 &  Limited Retaliate 3 &   0.35563 \\
-8  &            Evolved FSM 4 &   0.04891 &      Defector Hunter &   0.24038 &         Cycler DDC &   0.04545 &            Retaliate &   0.35714 \\
-9  &         PSO Gambler Mem1 &   0.05036 &            Retaliate &   0.24177 &        Hard Prober &   0.05128 &          Retaliate 2 &   0.35767 \\
-10 &                 Winner12 &   0.06011 &  Hard Tit For 2 Tats &      0.25 &         SolutionB1 &   0.06024 &  Limited Retaliate 2 &   0.36134 \\
-11 &             Fool Me Once &    0.0614 &             ShortMem &   0.25286 &      Meta Minority &   0.06077 &             Hopeless &   0.36842 \\
-12 &                      DBS &   0.07143 &  Limited Retaliate 3 &   0.25316 &              Bully &   0.06081 &    Arrogant QLearner &   0.40651 \\
-13 &            DoubleCrosser &     0.072 &    Limited Retaliate &   0.25706 &    Fool Me Forever &    0.0708 &    Cautious QLearner &   0.40909 \\
-14 &              BackStabber &   0.07519 &                \$\textbackslash pi\$ &   0.25801 &             EasyGo &   0.07101 &      Fool Me Forever &   0.41764 \\
+0  &            Evolved HMM 5 &     0.007 &                 Grumpy &      0.14 &                         DBS &         0 &          Fortress4 &     0.013 &             Evolved FSM 16 &         0 &           Alternator &     0.304 \\
+1  &           Evolved FSM 16 &      0.01 &                    \$e\$ &     0.194 &     Evolved FSM 16 Noise 05 &     0.008 &           Defector &     0.014 &    Evolved FSM 16 Noise 05 &     0.013 &               \$\textbackslash phi\$ &      0.31 \\
+2  &     EvolvedLookerUp2\_2\_2 &     0.011 &         Tit For 2 Tats &     0.206 &      Evolved ANN 5 Noise 05 &     0.013 &  Better and Better &     0.016 &                       MEM2 &     0.027 &                  \$e\$ &     0.312 \\
+3  &  Evolved FSM 16 Noise 05 &     0.017 &  Slow Tit For Two Tats &      0.21 &                 BackStabber &     0.024 &    Tricky Defector &     0.019 &              Evolved HMM 5 &     0.044 &                \$\textbackslash pi\$ &     0.317 \\
+4  &        PSO Gambler 2\_2\_2 &     0.021 &           Cycle Hunter &     0.215 &               DoubleCrosser &     0.025 &          Fortress3 &     0.022 &       EvolvedLookerUp2\_2\_2 &     0.049 &    Limited Retaliate &     0.353 \\
+5  &              Evolved ANN &     0.029 &         Risky QLearner &     0.222 &               Evolved ANN 5 &     0.028 &     Gradual Killer &     0.025 &       Spiteful Tit For Tat &      0.06 &     Anti Tit For Tat &     0.354 \\
+6  &            Evolved ANN 5 &     0.034 &            Retaliate 3 &     0.229 &                 Evolved ANN &     0.038 &         Aggravater &     0.028 &           Nice Meta Winner &     0.068 &  Limited Retaliate 3 &     0.356 \\
+7  &        PSO Gambler 1\_1\_1 &     0.037 &          Cycler CCCCCD &     0.235 &        Spiteful Tit For Tat &     0.051 &             Raider &     0.031 &         NMWE Finite Memory &     0.069 &          Retaliate 3 &     0.356 \\
+8  &            Evolved FSM 4 &     0.049 &            Retaliate 2 &     0.239 &               Evolved HMM 5 &     0.051 &         Cycler DDC &     0.045 &         NMWE Deterministic &      0.07 &            Retaliate &     0.357 \\
+9  &         PSO Gambler Mem1 &      0.05 &        Defector Hunter &      0.24 &              Level Punisher &     0.052 &        Hard Prober &     0.051 &                    Grudger &      0.07 &          Retaliate 2 &     0.358 \\
+10 &                 Winner12 &      0.06 &              Retaliate &     0.242 &                   Omega TFT &     0.059 &         SolutionB1 &      0.06 &           NMWE Long Memory &     0.074 &  Limited Retaliate 2 &     0.361 \\
+11 &             Fool Me Once &     0.061 &    Hard Tit For 2 Tats &      0.25 &                Fool Me Once &     0.059 &      Meta Minority &     0.061 &  Nice Meta Winner Ensemble &     0.076 &             Hopeless &     0.368 \\
+12 &                      DBS &     0.071 &    Limited Retaliate 3 &     0.253 &  PSO Gambler 2\_2\_2 Noise 05 &     0.067 &              Bully &     0.061 &       EvolvedLookerUp1\_1\_1 &     0.077 &    Arrogant QLearner &     0.407 \\
+13 &            DoubleCrosser &     0.072 &               ShortMem &     0.253 &              Evolved FSM 16 &     0.078 &             EasyGo &     0.071 &            NMWE Memory One &      0.08 &    Cautious QLearner &     0.409 \\
+14 &              BackStabber &     0.075 &      Limited Retaliate &     0.257 &                  EugineNier &      0.08 &    Fool Me Forever &     0.071 &                   Winner12 &     0.085 &      Fool Me Forever &     0.418 \\
 \bottomrule

### 2020-03-29 paper/random_forest_evaluation.tex
moves sections to appendix and retrieves results from siren

\section{Evaluation based on clustering and random forest.}\label{app:clustering}

The final method to evaluate the features importance in a strategy's success
is a combination of a clustering task and a random forest algorithm.
Initially the performances are clustered into different clusters
based on them being successful or not. The performances are clustered into
successful and unsuccessful clusters based on 4 different approaches.
More specifically:

\begin{itemize}
    \item \textbf{Approach 1:} The performances are divided into two clusters based
    on whether their performance was in the top \(5\%\) of their respective tournaments.
    Thus, whether \(r\) was smaller or larger than 0.05.
    \item \textbf{Approach 2:} The performances are divided into two clusters based
    on whether their performance was in the top \(25\%\) of their respective tournaments.
    Thus, whether \(r\) was smaller or larger than 0.25.
    \item \textbf{Approach 3:} The performances are divided into two clusters based
    on whether their performance was in the top \(50\%\) of their respective tournaments.
    Thus, whether \(r\) was smaller or larger than 0.50.
    \item \textbf{Approach 4:} The performances are clustered based on their normalised rank and
    their median score by a \(k-\)means algorithm~\cite{Arthur2007}. The number of
    clusters is not deterministically chosen but it is based on the silhouette
    coefficients~\cite{Rousseeuw1987}.
\end{itemize}

Once the performances have been assigned to a cluster for each approach a
random forest algorithm~\cite{breiman2001} is applied. The problem is a supervised
problem where the random forest algorithm predicts the cluster to which a performance
has been assigned to using the features of Table~\ref{table:manual_features}.
The random
forest models are trained on a training set of 70\% of the tournaments results.
The accuracy of each model based on $R^2$ and the number of clusters for each
tournament type (because in the case of Approach 4 it is not
deterministically chosen) are given by Table~\ref{table:accuracy_random_forest}.
The out of the bag error (OOB)~\cite{hastie2005} has also been calculated. The
models fit well, and a high value of both the accuracy measures on the test data
and the OOB error indicate that the model is not over fitting.

\begin{table}[!htbp]
    \begin{center}
        \resizebox{.9\textwidth}{!}{
        \begin{tabular}{lccccc}
    \toprule
    Tournament type & Clustering Approach & Number of clusters & $R^2$ training data &  $R^2$ test data  & $R^2$ OOB score\\
    \midrule
    standard  & Approach 1  & 2 & 0.998831  & 0.987041    & 0.983708 \\
              & Approach 2  & 2 & 0.998643  & 0.978626    & 0.969202 \\
              & Approach 3  & 2 & 0.998417  & 0.985217    & 0.976538 \\
              & Approach 4  & 2 & 0.998794  & 0.990677    & 0.982959 \\
    \midrule
    noisy     & Approach 1  & 2 & 0.997786  & 0.972229    & 0.968332\\
              & Approach 2  & 2 & 0.997442  & 0.963254    & 0.955219\\
              & Approach 3  & 2 & 0.997152  & 0.953164    & 0.940528\\
              & Approach 4  & 3 & 0.996923  & 0.950728    & 0.935444\\
    \midrule
    probabilistic ending & Approach 1 & 2 & 0.997909   & 0.981490  & 0.978120 \\
                         & Approach 2 & 2 & 0.997883   & 0.973492  & 0.967150 \\
                         & Approach 3 & 2 & 0.990448   & 0.890068  & 0.875822 \\
                         & Approach 4 & 2 & 0.999636   & 0.995183  & 0.992809 \\
    \midrule
    noisy probabilistic ending & Approach 1  & 2 & 0.995347 & 0.957846   & 0.952353\\
                               & Approach 2  & 2 & 0.992813 & 0.909346   & 0.898613\\
                               & Approach 3  & 2 & 0.990579 & 0.824794   & 0.806540\\
                               & Approach 4  & 4 & 0.989465 & 0.841652   & 0.824052\\
    \midrule
    over \numberofalltournaments tournaments   & Approach 1 & 2 & 0.997271& 0.972914& 0.969198 \\
                                               & Approach 2 & 2 & 0.996323& 0.951194& 0.940563 \\
                                               & Approach 3 & 2 & 0.993707& 0.906941& 0.891532 \\
                                               & Approach 4 & 3 & 0.993556& 0.913335& 0.898453 \\
    \bottomrule
        \end{tabular}}
    \end{center}
    \caption{Accuracy metrics for random forest models.}
    \label{table:accuracy_random_forest}
\end{table}

The importance that the features of Table~\ref{table:manual_features} had on
each random forest model are given by Figures~\ref{fig:clustering_importance_standard},
\ref{fig:clustering_importance_noise},~\ref{fig:clustering_importance_probend},
\ref{fig:clustering_importance_probend_noise}
and~\ref{fig:clustering_importance_overall}. These show that the classifiers
stochastic, make use of game and make use of length have no significant effect,
and several of the features that are highlighted by the importance are inline with
the correlation results. Moreover, the smoothing parameter \(k\) appears to no
have a significant effect either. The most important features based on the
random forest analysis were $C_{r} / C_{median}$ and $C_r / C_{mean}$.

\begin{figure}[!htbp]
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../new_output/standard/_feature_importance_bar_plot_cluster_on_0_05.pdf}
        \end{center}
        \caption{Importance of features for clusters on 5\% performance.}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../new_output/standard/_feature_importance_bar_plot_cluster_on_0_25.pdf}
        \end{center}
        \caption{Importance of features for clusters on 25\% performance.}
    \end{subfigure}
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../new_output/standard/_feature_importance_bar_plot_cluster_on_0_5.pdf}
        \end{center}
        \caption{Importance of features for clusters on 50\% performance.}
    \end{subfigure}\hfill
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../k_means_output/standard/_feature_importance_bar_plot.pdf}
        \end{center}
        \caption{Importance of features for clusters based on \(k\)means algorithm.}
    \end{subfigure}
    \caption{Importance of features in standard tournaments for different
    clustering methods.}\label{fig:clustering_importance_standard}
\end{figure}

\begin{figure}[!htbp]
    \begin{subfigure}{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../new_output/noise/_feature_importance_bar_plot_cluster_on_0_05.pdf}
        \end{center}
        \caption{Importance of features for clusters on 5\% performance.}
    \end{subfigure}\hfill
    \begin{subfigure}{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../new_output/noise/_feature_importance_bar_plot_cluster_on_0_25.pdf}
        \end{center}
        \caption{Importance of features for clusters on 25\% performance.}
    \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../new_output/noise/_feature_importance_bar_plot_cluster_on_0_5.pdf}
        \end{center}
        \caption{Importance of features for clusters on 50\% performance.}
    \end{subfigure}\hfill
    \begin{subfigure}{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../k_means_output/noise/_feature_importance_bar_plot.pdf}
        \end{center}
        \caption{Importance of features for clusters based on \(k\)means algorithm.}
    \end{subfigure}
    \caption{Importance of features in noisy tournaments for different
    clustering methods.}\label{fig:clustering_importance_noise}
\end{figure}

\begin{figure}[!htbp]
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../new_output/probend/_feature_importance_bar_plot_cluster_on_0_05.pdf}
        \end{center}
        \caption{Importance of features for clusters on 5\% performance.}
    \end{subfigure}
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../new_output/probend/_feature_importance_bar_plot_cluster_on_0_25.pdf}
        \end{center}
        \caption{Importance of features for clusters on 25\% performance.}
    \end{subfigure}
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../new_output/probend/_feature_importance_bar_plot_cluster_on_0_5.pdf}
        \end{center}
        \caption{Importance of features for clusters on 50\% performance.}
    \end{subfigure}
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../k_means_output/probend/_feature_importance_bar_plot.pdf}
        \end{center}
        \caption{Importance of features for clusters based on \(k\)means algorithm.}
    \end{subfigure}
    \caption{Importance of features in probabilistic ending tournaments for different
    clustering methods.}\label{fig:clustering_importance_probend}
\end{figure}

\begin{figure}[!htbp]
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../new_output/probend_noise/_feature_importance_bar_plot_cluster_on_0_05.pdf}
        \end{center}
        \caption{Importance of features for clusters on 5\% performance.}
    \end{subfigure}
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../new_output/probend_noise/_feature_importance_bar_plot_cluster_on_0_25.pdf}
        \end{center}
        \caption{Importance of features for clusters on 25\% performance.}
    \end{subfigure}
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../new_output/probend_noise/_feature_importance_bar_plot_cluster_on_0_5.pdf}
        \end{center}
        \caption{Importance of features for clusters on 50\% performance.}
    \end{subfigure}
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../k_means_output/probend_noise/_feature_importance_bar_plot.pdf}
        \end{center}
        \caption{Importance of features for clusters based on \(k\)means algorithm.}
    \end{subfigure}
    \caption{Importance of features in noisy probabilistic ending tournaments for different
    clustering methods.}\label{fig:clustering_importance_probend_noise}
\end{figure}

\begin{figure}[!htbp]
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../new_output/merged/_feature_importance_bar_plot_cluster_on_0_05.pdf}
        \end{center}
        \caption{Importance of features for clusters on 5\% performance.}
    \end{subfigure}
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../new_output/merged/_feature_importance_bar_plot_cluster_on_0_25.pdf}
        \end{center}
        \caption{Importance of features for clusters on 25\% performance.}
    \end{subfigure}
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../new_output/merged/_feature_importance_bar_plot_cluster_on_0_5.pdf}
        \end{center}
        \caption{Importance of features for clusters on 50\% performance.}
    \end{subfigure}
    \begin{subfigure}[t]{0.5\textwidth}
        \begin{center}
            \includegraphics[width=.75\linewidth]{../k_means_output/merged/_feature_importance_bar_plot.pdf}
        \end{center}
        \caption{Importance of features for clusters based on \(k\)means algorithm.}
    \end{subfigure}
    \caption{Importance of features over all the tournaments for different
    clustering methods.}\label{fig:clustering_importance_overall}
\end{figure}

### 2020-03-29 src/process_data.py
tweak fix of FSM memory
The new data sets have been uploaded on zenodo

@@ -203,7 +203,7 @@ if __name__ == "__main__":
     if len(to_drop) != 0:
         df = df[~(df["seed"].isin(to_drop))]
 
-    df["Memory_depth"] = df.apply(get_memory_percentage, axis=1)
+    df["Memory_depth"] = df.apply(fix_fsm_memory, axis=1)
 
     if "turns" in df.columns:
         df["memory_usage"] = df.apply(get_memory_percentage, axis=1)

### 2020-03-29 paper/main.tex
finalise evaluation section

@@
 and more specifically, the suggestions `Do not be clever' and `Do not be envious'.
+The features and properties contributing a strategy's success are further
+explored in Section~\ref{section:evaluation_of_performance}.
 
@@
 
-The aim of this section is to explore the features that contribute to a
-strategy's successful performance. The features explored are measures regarding a
-strategy's behaviour, along with measures regarding the tournaments the
-strategies competed in. A summary of the features is given in
-Table~\ref{table:manual_features}.
+The performance of the strategies is evaluated based on the features of
+Table~\ref{table:manual_features}. These feature are measures regarding a
+strategy's behaviour and the tournaments the strategies competed in are
+explored.
 
 \newcolumntype{g}{>{\columncolor{Gray}}c}
-\begin{table}[h]
+\begin{table}[!htbp]
     \begin{center}
-    \resizebox{\textwidth}{!}{
+    \resizebox{.99\textwidth}{!}{
     \begin{tabular}{gcgcgc}
@@
     \end{center}
-    \caption{The features which are included in the performance evaluation analysis.}
+    \caption{The features which are included in the performance evaluation
+    analysis. stochastic, makes use of game and makes use of game are APL
+    classifies that determine whether a strategy is stochastic or deterministic,
+    whether it makes use of the number of turns or the game's payoffs. The
+    memory usage is calculated as the number of turns the strategy considers to
+    make an action (which is specified in the APL) divide by the number of
+    turns. The SSE (introduced in~\cite{Knight2019}) shows how close a strategy
+    is to behaving as a ZDs, and subsequently, in an extortionate way. The
+    method identifies the ZDs closest to a given strategy and calculates the
+    algebraic distance between them, defined as SSE. A SSE value of 1 indicates
+    no extortionate behaviour at all whereas a value of 0 indicates that a
+    strategy is behaving a ZDs. The rest of the features considered are the $CC$
+    to $C$, $CD$ to $C$, $DC$ to $C$, and $DD$ to $C$ rates as well as
+    cooperating ratio of a strategy, the minimum (\(C_{min}\)), maximum
+    (\(C_{max}\)), mean (\(C_{mean}\)) and median (\(C_{median}\)) cooperating
+    ratios of each tournament.}
     \label{table:manual_features}
@@
 
-APL classifies strategies along several dimensions. These determine whether
-a strategy is stochastic or deterministic, whether it makes use of the number of
-turns or the game's payoffs. The memory usage feature is calculated as the
-memory size of strategy (which is specified in the strategies implementation
-in the APL) divide by the number of turns. For example, Winner12 has a memory
-size of 2 and participated in a tournament where $n$ was 101. In the given
-tournament Winner12 has a memory usage of 0.014925. There are strategies with
-an infinite memory size, for example Evolved FSM 16 Noise 05. These strategies
-have a memory usage of 1.
-For tournaments with a probabilistic ending the number of turns was
-not collected, so the memory usage feature is not used for probabilistic ending
-tournaments. The SSE is a feature introduced in~\cite{Knight2019} which shows
-how close a strategy is to behaving as a ZDs, and subsequently, in an
-extortionate way. The method identifies the ZDs closest to a given strategy and
-calculates the algebraic distance between them, defined as SSE. A SSE value of 1
-indicates no extortionate behaviour at all whereas a value of 0 indicates that a
-strategy is behaving a ZDs. The rest of the features considered are the $CC$ to
-$C$, $CD$ to $C$, $DC$ to $C$, and $DD$ to $C$ rates as well as cooperating
-ratio of a strategy. The minimum, maximum, medium and median cooperating ratios
-of each tournament are also included, and finally the number of turns, the
-number of strategies, the number of repetitions and the probabilities of noise
-and the game ending are also included.
+The memory usage of strategies with an infinite memory size, for example Evolved
+FSM 16 Noise 05 is 1. There rest is calculated as explained in Table
+\ref{table:manual_features}. For example,  Winner12 has a memory size of 2 and
+participated in a tournament where $n$ was 101. In the given tournament Winner12
+has a memory usage of 0.014925. Note that for tournaments with a probabilistic
+ending the number of turns was not collected, so the memory usage feature is not
+used for probabilistic ending tournaments.
 
-Table~\ref{table:correlations} shows the correlation coefficients between the
-features of Table~\ref{table:manual_features} the median score and the median
-normalised rank. Note that the correlation for the classifiers is
-not included because they are binary variables and they will be evaluated using a
-different method. The correlation coefficients for all the features in
-Table~\ref{table:manual_features} against themselves have also been calculated and a
-graphical representation can be found in the Appendix~\ref{app:correlations}.
+The correlation coefficients between the features of
+Table~\ref{table:manual_features} the median score and the median normalised
+rank are given by Table~\ref{table:correlations}. The correlation coefficients
+between all features of Table~\ref{table:manual_features} have been calculated
+and a graphical representation can be found in the
+Appendix~\ref{app:correlations}.
 
@@
     \centering
-    \includegraphics[width=.65\textwidth]{../images/rates_of_winners_in_standard_tournaments.pdf}
+    \includegraphics[width=.57\textwidth]{../images/rates_of_winners_in_standard_tournaments.pdf}
     \caption{Distributions of $CC$ to $C$ and $DD$ to $C$ for the winners in
@@
 stronger effect. Thus a strategy will be punished more by its cooperative
-behaviour in probabilistic ending environments, this was seen in Section~\ref{section:evaluation_of_performance}
+behaviour in probabilistic ending environments, supporting the results of Section~\ref{section:evaluation_of_performance}
 as well. The distributions of the $C_r$ of the winners in
-both tournaments is given by Figure~\ref{fig:c_r_distributions}. It confirms
+both tournaments are given by Figure~\ref{fig:c_r_distributions}. It confirms
 that the winners in noisy tournaments cooperated less than 35\% of the times
@@
     \centering
-    \includegraphics[width=.65\textwidth]{../images/c_r_winners_tournaments.pdf}
+    \includegraphics[width=.57\textwidth]{../images/c_r_winners_tournaments.pdf}
     \caption{$C_r$ distributions of the winners in noisy and in probabilistic
@@
 
-A multivariate linear regression is fitted to model the relationship of
-Table's~\ref{table:manual_features} and the normalised rank. Based on the
-correlation matrices. Appendix~\ref{app:correlations} the depended variables are
-correlated. The median cooperating ration \(C_median\) and \(C_r/ C_median\) are highly
-correlated with \(C_mean\) and \(C_r / C_mean\). So these features are dropped from
-the analysis. The \(C_r\) is also correlated and drop. Finally for some environments
-the \(C_max\) and \(C_min\) are correlated and dropped for the models of those types.
-More specifically, the list of features their p values and \(p-\)values of
-each feature as well as their coefficients are given by
-Table~\ref{table:linear_regression}. The coefficient of determination, \(R\)
-squared, for each model is also reported in Table~\ref{table:linear_regression}.
+A multivariate linear regression has been fitted to model the relationship between
+the features and the normalised rank. Based on the graphical representation of
+the correlation matrices given in Appendix~\ref{app:correlations} several of the
+features are highly correlated. Highly correlated features have been removed
+before fitting the linear regression model. The features included are given
+by Table~\ref{table:linear_regression} alongside their corresponding \(p\) values
+in the distinct tournaments and their regression coefficients.
 
@@
     \end{center}
-    \caption{Results of multivariate linear regressions with \(r\) as the depended variable.}
+    \caption{Results of multivariate linear regressions with \(r\) as the depended variable.
+    \(R\) square is reported for each model. An \(R\) square of 1 represents a model
+    that explains all of the variation in the response variable around its mean.}
     \label{table:linear_regression}
@@
 
-The results of the linear regression verify the results of the previous
-approaches. The only features that do no have a significant effect on the
-models are the number of repetitions and memory usage in noisy tournaments,
-and the number of turns, number of repetitions and thr probability \(p_e\) in
-probabilistic ending tournaments. Over all the models, the features that are the
-most important predictors are $C_r$, $C_r$ / $C_{max}$ and $C_r$ / $C_{mean}$.
+The feature \(C_{r} / C_{\text{mean}}\) has a statistically significant effect
+across all models and a high regression coefficient. It has both a positive and
+negative impact on the normalised rank depending on the environment. For
+standard tournaments, Figure~\ref{fig:discussion_standard} gives the
+distributions of several features for the winners of standard tournaments. The
+\(C_{r} / C_{\text{mean}}\) distribution of the winner is also given in
+Figure~\ref{fig:discussion_standard}. A value of \(C_r / C_{\text{mean}} = 1\)
+implies that the cooperating ratio of the winner was the same as the mean
+cooperating ratio of the tournament, and in standard tournaments, the median is
+1. Therefore, an effective strategy in standard tournaments was the mean
+cooperator of its respective tournament.
 
-The features $C_{r} / C_{median}$ and $C_r / C_{mean}$ have been repeatably
-highlighted as importance features in explaining the variability of the performances.
-Thus, the effect of these two measures is further explored. In
-Figure~\ref{fig:mean_median_std} the distributions of \(C_r / C_{\text{mean}}\)
-and \(C_r / C_{\text{median}}\) are given for the winners in standard tournaments. A value of \(C_r /
-C_{\text{mean}} = 1\) imply that the cooperating ratio of the winner was the
-same as the mean/median cooperating ratio of the tournament. In standard tournaments, the mean
-for both ratios is 1. Therefore, an effective strategy in standard tournaments
-was the mean/median cooperator of its respective tournament. In comparison,
-Figure~\ref{fig:mean_median_noisy} shows the distributions of the features for
-the winners in noisy tournaments where the mean is at 0.67. Thereupon the winners
-cooperated 67\% of the times the mean/median cooperator did. This analysis is
-applied to the rest of the tournaments and the distributions are given by
-Figures \ref{fig:mean_median_probend}, \ref{fig:mean_median_probend_noisy} and
-\ref{fig:mean_median_overall}. In a tournament with noisy and a probabilistic
-ending the winners cooperated 60\%, whereas in settings that the type of the
-tournament can vary between the types considered in this work the winners
-cooperated 67\% of the times the mean or median cooperator did. Finally, in
-probabilistic ending tournament it has already been mentioned that defecting
-strategies prevail and this result is once again confirmed in this section.
+The distributions of SSE and \(CC\) to \(D\) rate for the winners of standard
+tournaments are also given in Figure~\ref{fig:discussion_standard}. The SSE
+distributions for the winners indicate that they strategy's behaved in ZD way in
+several tournaments, however, not constantly. The winners participated in
+matches where they did not try to extortionate their opponents. Futhermore, the
+\(CC\) to \(D\) distribution indicates that if a strategy were to defect against
+the winners they would reciprocate on average with a probability of 0.5.
 
@@
     \centering
-    \begin{subfigure}{0.35\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{../images/compared_to_mean_standard.pdf}
-        \caption{Distributions of \(C_r / C_{\text{mean}}\) for winners of standard tournaments.}
-        % \label{fig:noisy_probend_results}
-    \end{subfigure}
-    \begin{subfigure}{0.35\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/sse_standard.pdf}
-        \caption{Distributions of SSE for winners of standard tournaments.}
-        % \label{fig:overall_results}
-    \end{subfigure}
+        \includegraphics[width=\textwidth]{../images/standard_discussion.pdf}
+        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
+        for the winners of standard tournaments. A
+        value of \(C_r / C_{\text{mean}} = 1\) imply that the cooperating ratio of the
+        winner was the same as the mean cooperating ratio of the tournament. An SSE distribution
+        skewed towards 0 indicates a ZD behaviour by the strategy.}
+        \label{fig:discussion_standard}
 \end{figure}
+
+Similarly for the reset of the different tournaments types, and the entire data
+set the distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
+are given by Figures~\ref{fig:discussion_noisy},~\ref{fig:discussion_probend},
+\ref{fig:discussion_probend_noisy} and~\ref{fig:discussion_entire_data}.
+
+Based on the \(C_r / C_{\text{mean}}\) distributions the successful strategies
+have adapted differently to the mean cooperator depending on the tournament
+type. In noisy tournaments where the median of the distribution is at 0.67, and
+thereupon the winners cooperated 67\% of the times the mean cooperator did. In
+tournaments with noise and a probabilistic ending the winners cooperated 60\%,
+whereas in settings that the type of the tournament can vary between all the
+types the winners cooperated 67\% of the times the mean cooperator did. Lastly,
+in probabilistic ending tournaments it has already been mentioned that defecting
+strategies prevail (Section~\ref{section:top_performances}), and this result is
+once again confirmed here.
 
@@
     \centering
-    \begin{subfigure}{0.35\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{../images/compared_to_mean_noisy.pdf}
-        \caption{Distributions of \(C_r / C_{\text{mean}}\) for winners of noisy tournaments.}
-        % \label{fig:noisy_probend_results}
-    \end{subfigure}
-    \begin{subfigure}{0.35\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/sse_noisy.pdf}
-        \caption{Distributions of SSE for winners of noisy tournaments.}
-        % \label{fig:overall_results}
-    \end{subfigure}
+        \includegraphics[width=\textwidth]{../images/noisy_discussion.pdf}
+        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
+        for the winners of noisy tournaments.}
+        \label{fig:discussion_noisy}
 \end{figure}
+
+The distributions of the SSE across the tournament types suggest that successful
+strategies exhibit ZD behaviour, but not constantly. ZDs are a set of strategies
+that are envious as they try to exploit their opponents. The winners of the
+tournaments considered in this work are envious, but not as much as ZDs.
 
@@
     \centering
-    \begin{subfigure}{0.35\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{../images/compared_to_mean_probend.pdf}
-        \caption{Distributions of \(C_r / C_{\text{mean}}\) for winners of probabilistic ending tournaments.}
-        % \label{fig:noisy_probend_results}
-    \end{subfigure}
-    \begin{subfigure}{0.35\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/sse_probend.pdf}
-        \caption{Distributions of SSE for winners of probabilistic ending tournaments.}
-        % \label{fig:overall_results}
-    \end{subfigure}
+        \includegraphics[width=\textwidth]{../images/probend_discussion.pdf}
+        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
+        for the winners of probabilistic ending tournaments.}
+        \label{fig:discussion_probend}
 \end{figure}
+
+The distributions of the \(CD\) to \(C\) rate evaluate the behaviour of a
+successful strategy after it's opponent has defected against it. In standard
+tournaments it was observed that a successful strategy reciprocates with a
+probability of 0.5. This is distinct between the tournament types. In
+tournaments with noise a strategy is less likely to cooperate following a
+defection compared to standard tournaments, and in probabilistic ending
+tournaments a strategy will reciprocate a defection. In a setting that the type
+of the tournament can vary between all the examined types a winning strategy
+would reciprocate on average with a probability of 0.58.
 
@@
     \centering
-    \includegraphics[width=.5\textwidth]{../images/cd_to_c_probend.pdf}
-    % \caption{Distributions of \(C_r / C_{\text{median}}\)
-    % and \(C_r / C_{\text{median}}\) for winners of noisy probabilistic ending tournaments.}\label{fig:mean_median_probend_noisy}
+        \centering
+        \includegraphics[width=\textwidth]{../images/probend_noisy_discussion.pdf}
+        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
+        for the winners of noisy probabilistic ending tournaments.}
+        \label{fig:discussion_probend_noisy}
 \end{figure}
+
+Further statistically significant features with strong effects include \(C_r /
+C_{\text{min}}\), \(C_r / C_{\text{max}}\), \(C_{\text{min}}\) and
+\(C_{\text{max}}\). These add more emphasis on how important it is for a  a
+strategy to adapt to it's environment. Finally, the features number of turns,
+repetitions and the probabilities of noise and the game ending had not
+significant effect based on the multivariate regression models.
 
@@
     \centering
-    \begin{subfigure}{0.35\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{../images/compared_to_mean_probend_noisy.pdf}
-        \caption{Distributions of \(C_r / C_{\text{mean}}\) for winners of noisy probabilistic ending tournaments.}
-        % \label{fig:noisy_probend_results}
-    \end{subfigure}
-    \begin{subfigure}{0.35\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/sse_probend_noisy.pdf}
-        \caption{Distributions of SSE for winners of noisy probabilistic ending tournaments.}
-        % \label{fig:overall_results}
-    \end{subfigure}
+        \includegraphics[width=\textwidth]{../images/entire_data_discussion.pdf}
+        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
+        for the winners over the tournaments of the entire data set.}
+        \label{fig:discussion_entire_data}
 \end{figure}
 
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.65\textwidth]{../images/rates_of_winners_in_probend_noisy_tournaments.pdf}
-    % \caption{Distributions of \(C_r / C_{\text{median}}\)
-    % and \(C_r / C_{\text{median}}\) for winners of noisy probabilistic ending tournaments.}\label{fig:mean_median_probend_noisy}
-\end{figure}
-
-\begin{figure}[!htbp]
-    \centering
-    \begin{subfigure}{0.35\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/compared_to_mean_overall.pdf}
-        % \caption{Distributions of \(C_r / C_{\text{mean}}\) for winners of noisy probabilistic ending tournaments.}
-        % \label{fig:noisy_probend_results}
-    \end{subfigure}
-    \begin{subfigure}{0.35\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/rate_overall.pdf}
-        % \caption{Distributions of SSE for winners of noisy probabilistic ending tournaments.}
-        % \label{fig:overall_results}
-    \end{subfigure}
-\end{figure}
-
-In this section the effect of several features, regarding a strategy's behaviour
-and the tournament in which it participated on its performance were presented.
-This was done using three methods. Correlation coefficients, a random forest
-analysis and a linear regression. The results of these are summarised in the following section.
+A third method that evaluates the importance of the features in
+Table~\ref{table:manual_features} has been carried out and it can be found in
+the Appendix~\ref{app:clustering}. The results uphold the outcomes of the
+correlation and multivariate regression methods. It also evaluates the effects
+of the classifiers stochastic, make use of game and make use of length which
+have not been evaluated by the methods above because there are binary variables.
+The results imply that they have no significant effect on a strategy's
+performance.
 

### 2020-03-29 paper/main.tex
finalise conclusion

@@
 There are several properties, however, that heavily influence the best performing
-strategies, these are: be nice, be provocable, be a little envious, be clever
+strategies, these are: be nice, be provocable and contrite, be a little envious, be clever
 and adapt to the environment.
@@
 \begin{itemize}
-    \item \st{Do not be envious}
+    \item \st{Do not be envious} Be a little bit envious
     \item Be "nice"; Do not be the first to defect
-    \item Reciprocate both cooperation and defection; Be provocable
-    \item \st{Do not be too clever}
+    \item Reciprocate both cooperation and defection; Be provocable and contrite
+    \item \st{Do not be too clever} Be clever
     \item Adapt to the environment; Adjust to the mean cooperator
@@
 
-This manuscript has explored the performance of \numberofstrategies strategies of the Iterated
-Prisoner's Dilemma in a large number of computer tournaments. The results of
-the analysis demonstrated that, although for specific tournament types such as
-standard, probabilistic ending tournaments and noisy tournaments with \(p_n <0.1\), dominant types of strategies exist
-there is not a single dominant strategy, from the collection on strategies considered in this work, in an IPD competition if the environments
-vary. Moreover, a strategy with a theory of mind should aim to adapt its behaviour
-based on the mean and median cooperators and should in general not be too
-cooperative.
-
+This manuscript has explored the performance of \numberofstrategies strategies
+of the Iterated Prisoner's Dilemma in a large number of computer tournaments.
 The \numberofstrategies strategies used in this manuscript have been mainly for
@@
 strategies and different participants each time. The data collection was
-described in Section~\ref{section:data_collection}. In
+described in Section~\ref{section:data_collection}.
+
+In
 Section~\ref{section:top_performances}, the tournaments results were used to
@@
 designed for noisy tournaments indeed performed well.
-Overall, the top ranked strategies differed from one tournament type to
-another and the mechanism behind the winning strategies were all different, with some
-exceptions which include trained (Evolved) and Meta strategies.
 
@@
 important features have been those that compared the strategy's behaviour to its
-environment. The cooperating ratio of the strategy compared to the mean and
-median cooperator was highlighted as the most important feature in the analysis.
-More specifically, if a strategy were to enter a tournament with a theory of
-mind of its environment it would choose to be the median cooperator in standard
-tournaments, to cooperate 10\% of the time the median cooperator did in probabilistic ending tournaments and 
-60\% in noisy and noisy probabilistic
-tournaments. Lastly, if a strategy was aware of the opponents but not of the
-setting of the tournament, a strategy would be more likely to be successful if
-it were to identify the median cooperator and cooperated 67\% of the times that
-they did.
+environment. The cooperating ratio of the strategy compared to the mean
+cooperator was highlighted as the most important feature in the analysis.
+Other significant features included the SSE of a strategy and it's cooperating
+rate after being in either state \(CC\) and \(CD\).
+
+So what is the best way of playing the game? and is there a single dominant
+strategy in the IPD? There is not a single strategy, from the collection of the
+195 strategies, that has managed to will all the tournaments it competed in.
+Even if on average a strategy ranked highly in a specific environment it did not
+guarantee its success over the different tournament types. However, he results
+of sections~\ref{section:top_performances}
+and~\ref{section:evaluation_of_performance} have demonstrated that there are
+properties associated with the success of strategies. A few the properties that
+have been identified by this manuscript's analysis contradict the properties of
+Axelrod~\cite{Axelrod1981}. Namely, in Section~\ref{section:top_performances} it
+was shown that trained strategies and strategies that decided their actions
+based on pre designed strategies to maximise their utility dominated several
+tournaments across tournament types. Hinting that successful IPD strategies are
+clever. Most of the successful strategies highlighted
+in~Section~\ref{section:top_performances} were strategies that did open with a
+cooperation.
+
+Furthermore, in Section~\ref{section:top_performances}
+and~\ref{section:evaluation_of_performance} it was shown that envious strategies
+performed well. Though these were not the most envious strategies in the
+tournaments (ZDs were included) these strategies benefited by being a bit
+envious. From Section~\ref{section:evaluation_of_performance} it was concluded
+that there is a significant importance in adapting to the environment, and more
+specifically in this work, to the mean cooperator. This section also
+demonstrated that a strategy should reciprocate, as suggested by Axelrod, but in
+some environments, such as standard and noisy, it should relax it's readiness to
+do so.
+
+Thus, the five properties successful strategies need to have in a IPD competition
+are: be nice, be provocable and contrite, be a little envious, be clever and adapt to the
+environment.
 

### 2020-03-29 paper/main.tex
Copy edits, mostly

@@
 tournaments, presents the top performing strategies, and analyzes their
-salient features. The results imply that there is not a single
-strategy that performs well in any Iterated Prisoner's Dilemma interaction.
+salient features. The results imply that there is not yet a single
+strategy that performs well in every Iterated Prisoner's Dilemma interaction.
 There are several properties, however, that heavily influence the best performing
@@
 Axelrod1980b} in the 80's. The
-winner of both tournaments was the simple strategy Tit For Tat which cooperated
+winner of both tournaments was the simple strategy Tit For Tat (TFT) which cooperated
 on the first turn and then simply copied the previous action of its opponent.
@@
 As a result of the strategy's strong performance in both tournaments, and moreover in a
-series of evolutionary experiments~\cite{Axelrod1981}, Tit For Tat was often
+series of evolutionary experiments~\cite{Axelrod1981}, TFT was often
 claimed to be the most robust basic strategy in the IPD.
 
-There are strategies which have built upon Tit For Tat, and the reciprocity based approach.
+There are strategies which have built upon TFT and the reciprocity based approach.
 In~\cite{Beaufils1997} Gradual was introduced which was constructed to have the
-same qualities as those of Tit for Tat except one, Gradual had a memory
+same qualities as those of TFT except one: Gradual had a memory
 of the game since the beginning of it. Gradual recorded the number of defections
@@
 
-Other works have built upon the limitations of the strategy, and others have shown
+Other works have built upon the limitations of the TFT, and others have shown
 that suggestions made by Axelrod were incomplete.
 In~\cite{Bendor1991, Donninger1986, Molander1985, Hammerstein1984} it was shown
-that Tit For Tat suffered in environments with noise. This was
-mainly due to the strategy's lack of generosity and contrition. The strategy was
-quick to punish a defection, and in a noisy environment it could lead to a
+that TFT suffered in environments with noise. This was
+mainly due to the strategy's lack of generosity and contrition. The strategy immediately
+punishes a defection and in a noisy environment it could lead to a
 repeated cycle of defections and cooperations. Some new strategies, more
@@
 protagonists of the game. These include Nice and Forgiving~\cite{Bendor1991},
-Pavlov~\cite{Nowak1993} and Generous Tit For Tat~\cite{Nowak1992}.
-In~\cite{Press2012} a set of envious IPD strategies that have received a lot of
-attention were introduced called the zero-determinant strategies (ZDs). By
-forcing a linear relationship between the payoffs ZDs can ensure that they will
+Pavlov (aka Win Stay Lose Shift) ~\cite{Nowak1993}, Generous Tit For Tat~\cite{Nowak1992}.
+In~\cite{Press2012} a set of envious IPD strategies
+were introduced called zero-determinant strategies (ZDs). By
+forcing a linear relationship between stationary payoffs ZDs can ensure that they will
 never receive less than their opponents. ZDs are indeed a set of mathematically
@@
 strategies based on lookup tables~\cite{Axelrod1987}, hidden markov
-models~\cite{Harper2017} and finite state automata~\cite{Miller1996}.
+models~\cite{Harper2017}, and finite state automata~\cite{Miller1996}.
 
-Though only select pieces of work have been discussed, there is a board number
+Though only select pieces of work have been discussed, there is a broad number
 of strategies in the literature, and new strategies and competitions are being
@@
 
-Compared to other works, whereas a few selected strategies are evaluated
+Compared to other works, where a few selected strategies are evaluated
 on a small number of tournaments, this manuscript evaluates the performance of \numberofstrategies
@@
 length and both noise and probabilistic match length.
-The later part of the paper, evaluates
+The later part of the paper evaluates
 the impact of features on the performance of the strategies using modern
@@
     \item \st{Do not be too clever} Be clever
-    \item Adapt to the environment; Adjust to the mean cooperator
+    \item Adapt to the environment; Adjust to the mean population cooperation
 \end{itemize}
 
-The different tournament types as well as the data collection, which is made
-possible due to an open source package called Axelrod-Python,
+The different tournament types as well as the data collection, made
+possible due to an open source libary called Axelrod-Python (APL),
 are covered in Section~\ref{section:data_collection}. The data set generated
@@
 contribute to good performance, and finally the results are summarised in
-Section~\ref{section:conclusion}. This manuscripts uses several parameters.
-These are introduced in the following sections, however, the full set of
+Section~\ref{section:conclusion}. This manuscripts uses several parameters,
+introduced in the following sections. The full set of
 parameters and their definitions are given in Appendix~\ref{app:parameters}.
@@
 
-For the purposes of this manuscript a data set containing results of IPD
-tournaments has been generated and is available at~\cite{data}. This was done using the
-open source package Axelrod-Python library~\cite{axelrodproject} (APL), and more specifically,
-version 3.0.0. APL allows for different types of IPD computer
-tournaments to be simulated whilst containing a large list of strategies.
+The data set generated for this manuscript was created with APL version 3.0.0.
+APL allows for different types of IPD computer
+tournaments to be simulated and contains a large list of strategies.
 Most of these are strategies described in the literature with a few exceptions
-being strategies that have been contributed specifically to the package. This
+of strategies that have been contributed specifically to the package. This
 paper makes use of \numberofstrategies strategies implemented in version 3.0.0. A
@@
 Although APL features several tournament types, this work considers
-standard, noisy, probabilistic ending and noisy probabilistic ending
+standard, noisy, probabilistic ending, and noisy probabilistic ending
 tournaments.
 
-\textbf{Standard tournaments}, are tournaments similar to that of Axelrod's
-in~\cite{Axelrod1980a}. There are \(N\) strategies which all play an iterated
+\textbf{Standard tournaments} are tournaments similar to that of Axelrod's well-known
+tournaments ~\cite{Axelrod1980a}. There are \(N\) strategies which all play an iterated
 game of \(n\) number of turns against each other. Note that self interactions
@@
 tournament. The information includes the strategy's rank, median score, the rate
-with which the strategy cooperated $(C_r)$, its match win count and the
+with which the strategy cooperated $(C_r)$, its match win count, and the
 probability that the strategy cooperated in the opening move. Moreover, the
 probabilities of a strategy being in any of the four states ($CC, CD, DC, DD$),
-and the rate of which the strategy cooperated after each state. A feature that
-has been manually included is the \textbf{normalised rank}. The rank of a given
-strategy, denoted as \(R\), can vary between 0 and \(N-1\). Thus, the normalised rank,
+and the rate of which the strategy cooperated after each state. The \textbf{normalised rank}
+feature that is manually added. The rank \(R\) of a given
+strategy can vary between 0 and \(N-1\). Thus, the normalised rank,
 denoted as $r$, is calculated as a strategy's rank divided by \(N - 1\).
@@
 
-In the next section the performance of the \numberofstrategies IPD strategies is
-evaluated based on their normalised rank.
-
 \section{Top ranked strategies}\label{section:top_performances}
 
-The performance of each strategy is evaluated in four tournament types, which
-were presented in Section \ref{section:data_collection}, followed by an
+The performance of each strategy is evaluated in four tournament types, as
+presented in Section \ref{section:data_collection}, followed by an
 evaluation of their performance over all the \numberofalltournaments simulated
 tournaments of this work. Each strategy participated in multiple tournaments of
-the same type (on average 5154). For example Tit For Tat has participated in a
+the same type (on average 5154). For example TFT participated in a
 total of 5114 tournaments of each type. The strategy's normalised rank
@@
     \includegraphics[width=.60\textwidth]{../images/tit_for_tat_r_distributions.pdf}
-    \caption{Tit For Tat's $r$ distribution in tournaments. Lower values of \(r\)
+    \caption{TFT's $r$ distribution in tournaments. Lower values of \(r\)
     correspond to better performances. The best performance
@@
 set to defect on the last two rounds. It should be noted that these
-strategies can be characterised as "cheaters" because the source code of the strategies
+strategies can be characterised as ``cheaters'' because the source code of the strategies
 allows them to known the number of turns in a match (if they are specified).
@@
 in standard tournaments, and  Grudger~\cite{axelrodproject} and Spiteful Tit for
-Tat~\cite{prison}. he Meta strategies~\cite{axelrodproject} create a team of
+Tat~\cite{prison}. The Meta strategies~\cite{axelrodproject} create a team of
 strategies and play as an ensemble or some other combination of their team
@@
     The distributions of the Retaliate strategies have no statistical
-    difference. Thus, in an IPD tournament where the type is not specified,
-    playing as any of the Retaliate strategies will have same the result. PSO
-    Gambler and Evolved HMM 5 are trained strategies introduced
+    difference. PSO Gambler and Evolved HMM 5 are trained strategies introduced
     in~\cite{Harper2017} and Nice Meta Winner and NMWE Memory One are strategies
@@
 are specific types of strategies have been repeatably ranked in the top ranks.
-These have been strategies that have been trained, strategies that defected
+These have been strategies that have been trained, strategies that retailiate,
 and strategies that would adapt their behaviour based on preassigned rules
-to achieve the highest outcome. These results contradict Axelrod's suggestions,
+to achieve the highest outcome. These results contradict some of Axelrod's suggestions,
 and more specifically, the suggestions `Do not be clever' and `Do not be envious'.
@@
     \caption{The features which are included in the performance evaluation
-    analysis. stochastic, makes use of game and makes use of game are APL
-    classifies that determine whether a strategy is stochastic or deterministic,
+    analysis. Stochastic, makes use of length and makes use of game are APL
+    classifiers that determine whether a strategy is stochastic or deterministic,
     whether it makes use of the number of turns or the game's payoffs. The
@@
 The memory usage of strategies with an infinite memory size, for example Evolved
-FSM 16 Noise 05 is 1. There rest is calculated as explained in Table
+FSM 16 Noise 05 is set to 1. The others are calculated as explained in Table
 \ref{table:manual_features}. For example,  Winner12 has a memory size of 2 and
@@
 more successful performance. Even though being nice pays off,
-that's not true against defective strategies. Cooperating after a mutual
-defection lowers a strategy's success.
+that's not true against defective strategies. Being more cooperative after a mutual
+defection is indicative of lesser overall success.
 Figure~\ref{fig:rates_of_winners_in_standard_tournaments} confirms that the
 winners of standard tournaments always cooperate after a mutual cooperation and
-almost always defects after a mutual defection.
+almost always defect after a mutual defection.
 
@@
 the mean and median cooperator in such settings. In probabilistic ending
-tournaments the correlation coefficients have a larger values, indicating a
+tournaments the correlation coefficients have larger values, indicating a
 stronger effect. Thus a strategy will be punished more by its cooperative
@@
 both tournaments are given by Figure~\ref{fig:c_r_distributions}. It confirms
-that the winners in noisy tournaments cooperated less than 35\% of the times
+that the winners in noisy tournaments cooperated less than 35\% of the time
 and in probabilistic ending tournaments less than 10\%.
-In noisy probabilistic ending tournaments and in over all the tournaments' results,
-the only features that had a moderate affect are $C_r/C_{\text{mean}},
+In noisy probabilistic ending tournaments and over all the tournaments' results,
+the only features that had a moderate effect are $C_r/C_{\text{mean}},
 C_r/C_{\text{max}}$ and $C_r$. In such environments cooperative behaviour
-appears to be punished by not as much as in noisy and probabilistic ending
+appears to be punished less than in noisy and probabilistic ending
 tournaments.
@@
     \end{center}
-    \caption{Results of multivariate linear regressions with \(r\) as the depended variable.
-    \(R\) square is reported for each model. An \(R\) square of 1 represents a model
-    that explains all of the variation in the response variable around its mean.}
+    \caption{Results of multivariate linear regressions with \(r\) as the dependent variable.
+    \(R\) squared is reported for each model.}
     \label{table:linear_regression}
@@
         winner was the same as the mean cooperating ratio of the tournament. An SSE distribution
-        skewed towards 0 indicates a ZD behaviour by the strategy.}
+        skewed towards 0 indicates a extortionate behaviour by the strategy.}
         \label{fig:discussion_standard}
@@
 
-Similarly for the reset of the different tournaments types, and the entire data
+Similarly for the rest of the different tournaments types, and the entire data
 set the distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
@@
 type. In noisy tournaments where the median of the distribution is at 0.67, and
-thereupon the winners cooperated 67\% of the times the mean cooperator did. In
+thereupon the winners cooperated 67\% of the time the mean cooperator did. In
 tournaments with noise and a probabilistic ending the winners cooperated 60\%,
 whereas in settings that the type of the tournament can vary between all the
-types the winners cooperated 67\% of the times the mean cooperator did. Lastly,
-in probabilistic ending tournaments it has already been mentioned that defecting
+types the winners cooperated 67\% of the time the mean cooperator did. Lastly,
+in probabilistic ending tournaments it has already been mentioned that more defecting
 strategies prevail (Section~\ref{section:top_performances}), and this result is
@@
 The distributions of the SSE across the tournament types suggest that successful
-strategies exhibit ZD behaviour, but not constantly. ZDs are a set of strategies
-that are envious as they try to exploit their opponents. The winners of the
-tournaments considered in this work are envious, but not as much as ZDs.
+strategies exhibit some extortionate behaviour, but not constantly.
+ZDs are a set of strategies that are envious as they try to exploit their
+opponents. The winners of the tournaments considered in this work are
+envious, but not as much as many ZDs. This highlights why TFT's early tournament
+success fails to generalize -- it never attempts to defect against a cooperating
+or exploitable opponent (e.g. Alternator).
 
@@
 The distributions of the \(CD\) to \(C\) rate evaluate the behaviour of a
-successful strategy after it's opponent has defected against it. In standard
+successful strategy after its opponent has defected against it. In standard
 tournaments it was observed that a successful strategy reciprocates with a
@@
 \(C_{\text{max}}\). These add more emphasis on how important it is for a  a
-strategy to adapt to it's environment. Finally, the features number of turns,
-repetitions and the probabilities of noise and the game ending had not
-significant effect based on the multivariate regression models.
+strategy to adapt to its environment. Finally, the features number of turns,
+repetitions and the probabilities of noise and the game ending had no
+significant effects based on the multivariate regression models.
 
@@
 A third method that evaluates the importance of the features in
-Table~\ref{table:manual_features} has been carried out and it can be found in
+Table~\ref{table:manual_features} using random forests can be found in
 the Appendix~\ref{app:clustering}. The results uphold the outcomes of the
 correlation and multivariate regression methods. It also evaluates the effects
-of the classifiers stochastic, make use of game and make use of length which
+of the classifiers stochastic, make use of game, and make use of length which
 have not been evaluated by the methods above because there are binary variables.
@@
 The \numberofstrategies strategies used in this manuscript have been mainly for
-the literature, and they have been accessible due to an open source software
+the literature, accessible due to an open source software library
 called the Axelrod-Python library. The software was used to generate a total of
@@
 strategy in the IPD? There is not a single strategy, from the collection of the
-195 strategies, that has managed to will all the tournaments it competed in.
+195 strategies, that has managed to perform well in all the tournaments it competed in.
 Even if on average a strategy ranked highly in a specific environment it did not
-guarantee its success over the different tournament types. However, he results
+guarantee its success over the different tournament types. However, the results
 of sections~\ref{section:top_performances}
@@
 was shown that trained strategies and strategies that decided their actions
-based on pre designed strategies to maximise their utility dominated several
-tournaments across tournament types. Hinting that successful IPD strategies are
-clever. Most of the successful strategies highlighted
-in~Section~\ref{section:top_performances} were strategies that did open with a
+based on pre-designed strategies to maximise their utility dominated several
+tournaments across tournament types, hinting that successful IPD strategies are
+often clever or more complex than simple strategies like TFT. Most of the
+successful strategies highlighted
+in~Section~\ref{section:top_performances} were strategies that begin with
 cooperation.
@@
 performed well. Though these were not the most envious strategies in the
-tournaments (ZDs were included) these strategies benefited by being a bit
+tournaments (ZDs were included), these strategies benefited by being a bit
 envious. From Section~\ref{section:evaluation_of_performance} it was concluded
@@
 demonstrated that a strategy should reciprocate, as suggested by Axelrod, but in
-some environments, such as standard and noisy, it should relax it's readiness to
+some environments, such as standard and noisy, it should relax its readiness to
 do so.
@@
 Thus, the five properties successful strategies need to have in a IPD competition
-are: be nice, be provocable and contrite, be a little envious, be clever and adapt to the
-environment.
+are: be nice, be provocable and contrite, be a little envious, be clever, and adapt to the
+environment (the population of strategies).
 

### 2020-03-30 paper/main.tex
Revise abstract

@@
 \begin{abstract}
-From the celebrated performance of Tit for Tat, to the
-introduction of the zero-determinant strategies, to the use of sophisticated
-structures such as neural networks, the literature has been exploring the
-performance of Iterated Prisoner's Dilemma strategies for decades. The results of the literature,
-however, have been relying on a small number of somewhat arbitrarily selected
-strategies in a very small number of tournaments,
-casting doubt on the generalizability of results from statistical perspective.
-This manuscript evaluates \numberofstrategies strategies in 45686
-tournaments, presents the top performing strategies, and analyzes their
-salient features. The results imply that there is not yet a single
-strategy that performs well in every Iterated Prisoner's Dilemma interaction.
-There are several properties, however, that heavily influence the best performing
-strategies, these are: be nice, be provocable and contrite, be a little envious, be clever
-and adapt to the environment.
+Researchers have explored the performance of Iterated Prisoner's Dilemma strategies
+for decades: from the celebrated performance of Tit for Tat, to the
+introduction of the zero-determinant strategies, to the use of sophisticated learning
+structures such as neural networks, many new strategies have been introduced and tested
+in a variety of tournaments and population dynamics. Typical results in the literature,
+however, rely on performance against a small number of somewhat arbitrarily selected
+strategies in a very small number of tournaments, casting doubt on the generalizability
+of conclusions. We analyze a large collection of \numberofstrategies
+strategies in \numberofalltournaments tournaments, present the top performing strategies across multiple
+tournament types, and distill their salient features. The results show that there is not yet a single
+strategy that performs well in diverse Iterated Prisoner's Dilemma scenarios.
+Nevertheless there are several properties that heavily influence the best performing
+strategies, refining the properties described by R. Axelrod in light of
+recent and more diverse opponent populations. These are: be nice, be provocable and contrite,
+be a little envious, be clever, and adapt to the environment, which includes the parameters
+of the tournament (e.g. noise) and the population of opponents. More precisely,
+we find that strategies perform best when their probability of cooperation
+matches the total tournament population's aggregate cooperation probabilities,
+or a proportion thereof in the case of noisy and probabilistically ending tournaments,
+and that the manner in which a strategy achieves the ideal cooperation rate is crucial.
 \end{abstract}

### 2020-03-30 paper/main.tex
Revise introduction

@@
 strategies in a very small number of tournaments, casting doubt on the generalizability
-of conclusions. We analyze a large collection of \numberofstrategies
+of conclusions. We analyze a large collection of \numberofstrategies typically known
 strategies in \numberofalltournaments tournaments, present the top performing strategies across multiple
@@
 The Iterated Prisoner's Dilemma (IPD) is a repeated two player game that models
-behavioural interactions, and more specifically, interactions where
+behavioural interactions, specifically interactions where
 self-interest clashes with collective interest. At each turn of the game both
 players, simultaneously and independently, decide between cooperation (C) and
-defection (D) whilst having memory of their prior interactions. The payoffs for each
+defection (D), given memory of their prior interactions. The payoffs for each
 player, at each turn, is influenced by their own choice and the choice of the
-other player. The payoffs of the game are generally defined by:
+other player. The payoffs of the game are defined by:
 
@@
 
-where \(T > R > P > S\) and \(2R > T + S\). The most common values used in
+where typically \(T > R > P > S\) and \(2R > T + S\). The most common values used in
 the literature~\cite{Axelrod1981} are $R=3, P=1, T=5, S=0$. These values are also
@@
 robin computer tournament became a common evaluation technique for newly designed
-strategies. Many tournaments have followed Axelrod's~\cite{Bendor1991,
-Harper2017, Kendall2007, Stephens2002, Stewart2012} and today more than 200
-strategies exist in the literature.
+strategies. Many tournaments have followed Axelrod's~\cite{Bendor1991, Stephens2002,
+Kendall2007, Stewart2012, Harper2017} and today more hundreds of strategies exist
+in the literature.
 
-Axelrod performed two computer tournaments~\cite{Axelrod1980a,
-Axelrod1980b} in the 80's. The
+Axelrod performed two widely-known computer tournaments~\cite{Axelrod1980a,
+Axelrod1980b} in the 1980's. The
 winner of both tournaments was the simple strategy Tit For Tat (TFT) which cooperated
-on the first turn and then simply copied the previous action of its opponent.
-Axelrod concluded that the strategy's robustness was due to four properties, which
-he adapted in four suggestions on doing well in an IPD:
+on the first turn and then simply copied the previous action of its opponent,
+retailiating against defections with a defection, and forgiving a defection if followed
+by a cooperation. Axelrod concluded that the strategy's robustness was due to four
+properties, which he adapted into four suggestions on doing well in an IPD:
 
 \begin{itemize}
-    \item Do not be envious
+    \item Do not be envious by striving for a payoff larger than the opponent's payoff
     \item Be "nice"; Do not be the first to defect
-    \item Reciprocate both cooperation and defection; Be provocable
-    \item Do not be too clever
+    \item Reciprocate both cooperation and defection; Be provocable to retaliation and forgiveness
+    \item Do not be too clever by scheming to exploit the opponent
 \end{itemize}
@@
 Other works have built upon the limitations of the TFT, and others have shown
-that suggestions made by Axelrod were incomplete.
+that suggestions made by Axelrod did not necessarily lift to alternative environmental rules.
 In~\cite{Bendor1991, Donninger1986, Molander1985, Hammerstein1984} it was shown
 that TFT suffered in environments with noise. This was
-mainly due to the strategy's lack of generosity and contrition. The strategy immediately
-punishes a defection and in a noisy environment it could lead to a
+mainly due to the strategy's lack of generosity and contrition. Since TFT immediately
+punishes a defection, in a noisy environment it can get stuck in a
 repeated cycle of defections and cooperations. Some new strategies, more
-robust in tournaments with noise, were soon introduced and became the new
-protagonists of the game. These include Nice and Forgiving~\cite{Bendor1991},
-Pavlov (aka Win Stay Lose Shift) ~\cite{Nowak1993}, Generous Tit For Tat~\cite{Nowak1992}.
-In~\cite{Press2012} a set of envious IPD strategies
-were introduced called zero-determinant strategies (ZDs). By
+robust in tournaments with noise, were soon introduced, including
+Nice and Forgiving~\cite{Bendor1991}, Generous Tit For Tat~\cite{Nowak1992},
+and Pavlov (aka Win Stay Lose Shift) ~\cite{Nowak1993}, as well as later
+variants such as OmegaTFT \cite{kendall2007iterated}. Introduction of new strategies
+is often accompanied by a claim that the new strategy is the best known despite
+only being tested against a small number of opponents, or specific classes of
+opponents not necessarily representative of all possible or all published strategies.
+The lack of testing against formally defined strategies and tournament winners
+is understandable given the effort required to implement
+\footnote{Implementing prior strategies faithfully is often extremely difficult or impossible
+due to insufficient descriptions and lack of published implementations or code.}
+the hundreds of published IPD strategies, yet calls into question any claims of superiority
+or robustness of newly introduced
+strategies.
+
+A set of envious IPD strategies were introduced called zero-determinant strategies (ZDs)
+in~\cite{Press2012}. By
 forcing a linear relationship between stationary payoffs ZDs can ensure that they will
-never receive less than their opponents. ZDs are indeed a set of mathematically
-unique strategies and robust in pairwise interactions, however, their
-superiority in tournament settings have been tested. In~\cite{Harper2017} a
+never receive less than their memory-one opponents. While ZD strategies
+were introduced with a small tournament in which some were reportedly
+successful \cite{Stewart2012}, this result has not generally held in future
+work. In~\cite{Harper2017} a
 series of clever strategies were introduced, and a tournament containing over
-200 strategies was ran and none of the aforementioned strategies ranked in top
-spots. Instead, the top ranked strategies were the set of clever trained
-strategies based on lookup tables~\cite{Axelrod1987}, hidden markov
+200 strategies featured no ZD strategies ranked in top
+spots. Instead, the top ranked strategies were a set of ``clever''
+(in the sense of Axelrod's characteristics) trained
+strategies based on lookup tables~\cite{Axelrod1987}, hidden Markov
 models~\cite{Harper2017}, and finite state automata~\cite{Miller1996}.
+Similarly, in \cite{mathieu2017}, a set of evolutionarily-trained strategies,
+and a pre-selected set of known strategies, outperformed a collection of 12 ZD strategies.
 
-Though only select pieces of work have been discussed, there is a broad number
+Though only select pieces of work have been discussed, there is a broad collection
 of strategies in the literature, and new strategies and competitions are being
-published every year~\cite{Glynatsi2019}. The question, however, still remains
+published frequently~\cite{Glynatsi2019}. The question, however, still remains
 the same: what is the best way to play the game?
 
-Compared to other works, where a few selected strategies are evaluated
-on a small number of tournaments, this manuscript evaluates the performance of \numberofstrategies
-strategies in \numberofalltournaments tournaments. These tournaments come in a
-number of variations including tournaments with noise, probabilistic match
-length and both noise and probabilistic match length.
+Compared to other works, where typically a few selected or introduced strategies
+are evaluated on a small number of tournaments and/or small number of opponents,
+this manuscript evaluates the performance of \numberofstrategies
+strategies in \numberofalltournaments tournaments. Furthermore a large portion
+of the strategies used in this manuscript are drawn from the known and named strategies
+in IPD literature, including many previous tournament winners,
+in contrast to other work that may have randomly generated many essentially arbitrary
+strategies (typically restrained to a class such as memory-one strategies,
+or those of a certain structural form such as finite state machines or deterministic
+memory two strategies). Additionally, our tournaments come in a
+number of variations including standard tournaments emulating Axelrod's original tournaments,
+tournaments with noise, probabilistic match length, and both noise and probabilistic match length.
+This diversity of strategies and tournament types yields new insights and tests
+earlier claims in alternative settings against known powerful strategies.
+
 The later part of the paper evaluates
@@
     \item Be "nice"; Do not be the first to defect
-    \item Reciprocate both cooperation and defection; Be provocable and contrite
-    \item \st{Do not be too clever} Be clever
+    \item Reciprocate both cooperation and defection; Be provocable and forgiving
+    \item \st{Do not be too clever} It's ok to be clever
     \item Adapt to the environment; Adjust to the mean population cooperation
@@
 The different tournament types as well as the data collection, made
-possible due to an open source libary called Axelrod-Python (APL),
+possible due to an open source library called Axelrod-Python (APL),
 are covered in Section~\ref{section:data_collection}. The data set generated

### 2020-03-30 paper/main.tex
Revise tournament results

@@
 tournaments ~\cite{Axelrod1980a}. There are \(N\) strategies which all play an iterated
-game of \(n\) number of turns against each other. Note that self interactions
+game of \(n\) number of turns against each other. Note that self-interactions
 are not included. Similarly, \textbf{noisy
@@
 The top 15 strategies for each tournament type based on \(\bar{r}\) are given in
-Table~\ref{table:top_performances}. The data collection process was design such
-as that the probabilities of noise and ending of the match varied between 0 and
+Table~\ref{table:top_performances}. The data collection process was designed such
+that the probabilities of noise and ending of the match varied between 0 and
 1. However, commonly used values of these probabilities are
-values less than 0.1. Thus,
+values are often less than 0.1. Thus,
 Table~\ref{table:top_performances} also includes the top 15 strategies in noisy
@@
 strategies can be characterised as ``cheaters'' because the source code of the strategies
-allows them to known the number of turns in a match (if they are specified).
+allows them to know the number of turns in a match (if they are specified).
 These strategies were expected to not perform as well in
@@
 DBS is a strategy specifically designed for noisy environments, however, it ranks
-highly in standard tournaments as well.
-Figure~\ref{fig:std_results} supports that these strategies are to perform
-well in any standard tournament they participate.
+highly in standard tournaments as well. Similarly the fourth ranked player,
+Evolved FSM 16 Noise 05, was
+trained for noisy tournaments yet performs well in standard tournaments.
+Figure~\ref{fig:std_results} shows that these strategies typically perform
+well in any standard tournament in which they participate.
 
@@
 Evolved FSM 16 Noise 05, Evolved ANN 5 Noise 05, PSO Gambler 2 2 2 Noise 05 and
-Omega Tit For Tat~\cite{kendall2007iterated}. The rest of the top ranks are
+Omega Tit For Tat~\cite{kendall2007iterated}. Omega TFT, another strategy designed
+to break the deadlocking cycles of CD and DC that TFT can fall into in noisy
+environments, places 10th. The rest of the top ranks are
 occupied by strategies which performed well in standard tournaments and
@@
 when \(p_n\in [0, 1]\) is bimodal. The top strategies include strategies which
-decide their actions based on the cooperations to defections ratio, such as
+decide their actions based on the cooperation to defection ratio, such as
 ShortMem~\cite{Andre2013}, Grumpy~\cite{axelrodproject} and
@@
 and that in tournaments with a noise probability lower than \(0.5\) they
-performed poorly.
+performed poorly. At a noisy level of \(0.5\) or greater, mostly cooperative strategies
+become mostly defectors and vice versa.
 
@@
 
-The most effective strategies in probabilistic ending tournaments with \(p_e
-< 0.1\) are a series of Meta strategies, trained strategies which performed well
+The new entrants to the most effective strategies list in probabilistic ending
+tournaments with \(p_e< 0.1\) are a series of Meta strategies, trained strategies
+which performed well
 in standard tournaments, and Grudger~\cite{axelrodproject} and Spiteful Tit for
@@
 and Solution B1~\cite{Ashlock2014}. The success of defecting strategies in
-probabilistic ending tournaments was excepted. As stated in the Folk
-Theorem~\cite{Fudenberg2009} defecting strategies do better when the likelihood
+probabilistic ending tournaments is due to larger values of
+\(p_e\) which lead to shorter matches (the expected number of rounds is $1\p_e$), so the
+impact of the prisoner's dilemma being iterated is subdued. This is captured by the Folk
+Theorem~\cite{Fudenberg2009} as defecting strategies do better when the likelihood
 of the game ending in the next turn increases.

### 2020-03-30 paper/main.tex
Revise evaluation of performance

@@
 and that the manner in which a strategy achieves the ideal cooperation rate is crucial.
+The features of high performing strategies reveal why strategies such as Tit For Tat
+performed historically well in tournaments and why Zero Determinant strategies
+typically do not fare well in tournament settings.
 \end{abstract}
@@
 
-The performance of the strategies is evaluated based on the features of
+Now we examine performance of the strategies based on features of strategies described in
 Table~\ref{table:manual_features}. These feature are measures regarding a
-strategy's behaviour and the tournaments the strategies competed in are
-explored.
+strategy's behaviour from the tournaments the strategies competed in as well as
+intrinsic properties such as whether a strategy is deterministic or stochastic.
 
@@
     memory usage is calculated as the number of turns the strategy considers to
-    make an action (which is specified in the APL) divide by the number of
+    make an action (which is specified in the APL) divided by the number of
     turns. The SSE (introduced in~\cite{Knight2019}) shows how close a strategy
@@
 The memory usage of strategies with an infinite memory size, for example Evolved
-FSM 16 Noise 05 is set to 1. The others are calculated as explained in Table
-\ref{table:manual_features}. For example,  Winner12 has a memory size of 2 and
-participated in a tournament where $n$ was 101. In the given tournament Winner12
-has a memory usage of 0.014925. Note that for tournaments with a probabilistic
+FSM 16 Noise 05, is equal to 1. Otherwise the memory usage is the number of
+rounds of play used by the strategy divided by the number of turns in each match.
+For example, Winner12 uses the previous two rounds of play, and if participating in a
+participated in a tournament where $n$ was 100 the memory usage would be 2/100.
+Note that for tournaments with a probabilistic
 ending the number of turns was not collected, so the memory usage feature is not
@@
 that's not true against defective strategies. Being more cooperative after a mutual
-defection is indicative of lesser overall success.
+defection is associated to lesser overall success in terms of normalised rank.
 Figure~\ref{fig:rates_of_winners_in_standard_tournaments} confirms that the
@@
 stronger effect. Thus a strategy will be punished more by its cooperative
-behaviour in probabilistic ending environments, supporting the results of Section~\ref{section:evaluation_of_performance}
+behaviour in probabilistic ending environments, supporting the results of
+Section~\ref{section:evaluation_of_performance}
 as well. The distributions of the $C_r$ of the winners in
@@
 tournaments.
+
+Moreover, the manner in which as strategy achieves a given cooperation rate
+relative to the tournament population average is important. Playing a strategy
+that randomly cooperates with $C_mean$ is unlikely to be as effective as it will
+randomly have cooperations matched with defections. In contrast, TFT naturally
+achieves a cooperation rate near $C_mean$ by virtue of copying its opponent's
+last move while also minimizing instances where it is exploited by an opponent
+(cooperating while the opponent defects), at least in non-noisy tournaments.
+TFT forces the opponent to pay back the (C, D) round with a (D, C) round before
+returning to mutual cooperation. This explains why TFT performed well
+in Axelrod's original tournaments as most strategies submitted to those tournaments
+were typically cooperative and relatively few strategies used an easily exploitable
+pattern. TFT does not appear in the top ranks in
+these tournaments because it is too nice. Strategies like Grudger will always
+defect after a fixed number of opponent defections, which allows them to
+effectively exploit strategies like Alternator or stochastic strategies that
+have a non-zero chance of cooperating after mutual defection, which TFT will
+not do. Moreover in a noisy environment these strategies will naturally tend
+toward always defecting, leading them to exploit strategies like Cooperator. In
+such a scenario the noisy environment effectively voids Axelrod's rule to be nice,
+allowing strategies to attempt exploitation, whereas in a noise-free environment,
+exploitation is risky because several strategies exhibit a Grudger-like behavior,
+reducing the overall value in attempting to exploit strategies like Cooperator.
+
+Similarly, these results suggest an explanation regarding the perhaps intuitively unexpected
+effectiveness of memory one strategies historically. Given that among the important
+features associated to success are the relative cooperation rate to the population
+average and the four memory-one probabilities of cooperating conditional on the
+previous round of play, all five features can be optimized by a memory one
+strategy such as TFT. Usage of more history becomes valuable when there are
+exploitable opponent patterns, indicated by the importance of SSE as a feature,
+that the first-approximation provided by a memory-one strategy is no longer
+sufficient.
 
@@
 several tournaments, however, not constantly. The winners participated in
-matches where they did not try to extortionate their opponents. Futhermore, the
+matches where they did not try to extortionate their opponents. Furthermore, the
 \(CC\) to \(D\) distribution indicates that if a strategy were to defect against
@@
 types the winners cooperated 67\% of the time the mean cooperator did. Lastly,
-in probabilistic ending tournaments it has already been mentioned that more defecting
+in probabilistic ending tournaments above more defecting
 strategies prevail (Section~\ref{section:top_performances}), and this result is
-once again confirmed here.
+reflected here.
 
@@
 success fails to generalize -- it never attempts to defect against a cooperating
-or exploitable opponent (e.g. Alternator).
+or exploitable opponent (e.g. Alternator). Moreover, many of the strategies in
+the library will not tolerate exploitation attempts. A clever strategy can
+achieve mutual cooperation with stronger strategies while also being able to
+exploit weaker strategies. This is why ZD strategies fail to appear in the top
+ranks -- they try to exploit all opponents and cannot actively adapt back to
+mutual cooperation against stronger strategies, which requires more depth of memory.
+\footnote{Note that ZD strategies also tend to perform poorly in population games for
+a similar reason: they attempt to exploit other players using ZD strategies, failing to
+form a cooperative subpopulation. This makes them good invaders but poor resisters of invasion.}
 
@@
 A third method that evaluates the importance of the features in
-Table~\ref{table:manual_features} using random forests can be found in
+Table~\ref{table:manual_features} using clustering and random forests can be found in
 the Appendix~\ref{app:clustering}. The results uphold the outcomes of the

### 2020-03-30 paper/main.tex
Revise conclusion

@@
 of the Iterated Prisoner's Dilemma in a large number of computer tournaments.
-The \numberofstrategies strategies used in this manuscript have been mainly for
-the literature, accessible due to an open source software library
-called the Axelrod-Python library. The software was used to generate a total of
-\numberofalltournaments computer tournaments results with different number of
-strategies and different participants each time. The data collection was
-described in Section~\ref{section:data_collection}.
-
-In
-Section~\ref{section:top_performances}, the tournaments results were used to
+We analyzed and extracted the salient features of the best performing strategies
+across various tournament types, casting the results in terms of Axelrod's
+original suggested features of good IPD strategies. Moreover, our results
+shed light on the historic performance of TFT, zero determinant strategies,
+and memory-one strategies generally. Strategies need to match their play
+to the cooperativeness of the tournament population and do so in a way that
+prevents or minimizes exploitation. Overall we see that complex or clever
+strategies can be effective, whether trained against a corpus of possible
+opponents or purposely designed to mitigate the impact of noise such as
+in the strategy DBS. Further, we showed that while the type of exploitation
+attempted by ZD strategies is not typically effective in tournaments, more
+sophisticated strategies capable of selectively exploiting weaker opponents
+while mutually cooperating with stronger opponents can be highly successful.
+This fact was also indicated numerically by the importance of the strategy
+feature SSE in the analysis of strategy features,
+
+Highly noisy or tournaments with short matches favor less cooperative strategies.
+These environments mitigate the value of being nice. The
+added uncertainty reduces the ability of maintaining mutual cooperation and
+also triggers grudging strategies. Accordingly we find that in noisy tournaments
+that the best performing players cooperate a lower rate than the tournament
+population on average. Nevertheless we found some strategies designed or trained
+for noisy environments were also highly ranked in noise-free tournaments. This
+indicates that strategy complexity is not necessarily a liability, rather it
+can confer adaptability to a more diverse set of environments.
+
+In Section~\ref{section:top_performances}, the tournaments results were used to
 present the top performances. The data set contained results from four different
@@
 The top rank strategies were performing both well and bad, and this indicates
-that in noisy tournaments there are not strategies that can guarantee winning.
+that in noisy tournaments where the noise can vary substantially,
+there were no strategies that can guarantee winning across a range of noise.
 However, if the probability of noise was constrained at 0.1 then strategies
@@
 
-Section~\ref{section:evaluation_of_performance} covered an analysis of
-performance based on several features associated with a strategy and with the
-environments in which it was competing. The results of this analysis showed that a
-strategy's characteristics such as whether or not it's stochastic, and the information it
-used regarding the game had no effect on the strategy's success. The most
-important features have been those that compared the strategy's behaviour to its
-environment. The cooperating ratio of the strategy compared to the mean
-cooperator was highlighted as the most important feature in the analysis.
-Other significant features included the SSE of a strategy and it's cooperating
-rate after being in either state \(CC\) and \(CD\).
-
-So what is the best way of playing the game? and is there a single dominant
-strategy in the IPD? There is not a single strategy, from the collection of the
-195 strategies, that has managed to perform well in all the tournaments it competed in.
+So what is the best way of playing the IPD? And is there a single dominant
+strategy for the IPD? There was not a single strategy within the collection of the
+\numberofstrategies strategies, that has managed to perform well in all the
+tournaments variations it competed in.
 Even if on average a strategy ranked highly in a specific environment it did not
@@
 are: be nice, be provocable and contrite, be a little envious, be clever, and adapt to the
-environment (the population of strategies).
+environment (including the population of strategies).
 

### 2020-03-30 paper/main.tex
Conclusion --> Discussion and a few more edits

@@
 (cooperating while the opponent defects), at least in non-noisy tournaments.
+\footnote{This also explains why Tit For N Tats does not fare well -- it fails
+to achieve the proper cooperation ratio.}
 TFT forces the opponent to pay back the (C, D) round with a (D, C) round before
@@
 
-\section{Conclusion}\label{section:conclusion}
+\section{Discussion}\label{section:conclusion}
 
@@
 This fact was also indicated numerically by the importance of the strategy
-feature SSE in the analysis of strategy features,
+feature SSE in the analysis of strategy features. These results highlight
+a central idea in evolutionary game theory in this context: the fitness
+landscape is a function of the population (where fitness in this case is
+tournament performance). While that may seem obvious now, it shows why
+historical tournament results on small or arbitrary populations of strategies
+have so often failed to produce generalizable results.
 
 Highly noisy or tournaments with short matches favor less cooperative strategies.
-These environments mitigate the value of being nice. The
-added uncertainty reduces the ability of maintaining mutual cooperation and
-also triggers grudging strategies. Accordingly we find that in noisy tournaments
+These environments mitigate the value of being nice. Uncertainty enables
+exploitation, reducing the ability of maintaining or enforcing mutual cooperation,
+while triggering grudging strategies to switch from typically cooperating to
+typically defecting. Accordingly we find that in noisy tournaments
 that the best performing players cooperate a lower rate than the tournament

### 2020-03-30 paper/main.tex
Commit suggestion on line 138
Co-Authored-By: Nikoleta Glynatsi <GlynatsiNE@cardiff.ac.uk>

@@
 Nice and Forgiving~\cite{Bendor1991}, Generous Tit For Tat~\cite{Nowak1992},
-and Pavlov (aka Win Stay Lose Shift) ~\cite{Nowak1993}, as well as later
+and Pavlov (aka Win Stay Lose Shift)~\cite{Nowak1993}, as well as later
 variants such as OmegaTFT \cite{kendall2007iterated}. Introduction of new strategies

### 2020-03-30 paper/main.tex

@@
 forcing a linear relationship between stationary payoffs ZDs can ensure that they will
-never receive less than their memory-one opponents. While ZD strategies
+never receive less than their memory-one opponents. While ZDs
 were introduced with a small tournament in which some were reportedly
@@
 Similarly, in \cite{mathieu2017}, a set of evolutionarily-trained strategies,
-and a pre-selected set of known strategies, outperformed a collection of 12 ZD strategies.
+and a pre-selected set of known strategies, outperformed a collection of 12 ZDs.
 
@@
 \(p_e\) which lead to shorter matches (the expected number of rounds is $1\p_e$), so the
-impact of the prisoner's dilemma being iterated is subdued. This is captured by the Folk
+impact of the PD being iterated is subdued. This is captured by the Folk
 Theorem~\cite{Fudenberg2009} as defecting strategies do better when the likelihood
@@
 
-Moreover, the manner in which as strategy achieves a given cooperation rate
+Moreover, the manner in which a strategy achieves a given cooperation rate
 relative to the tournament population average is important. Playing a strategy
@@
 exploitable opponent patterns, indicated by the importance of SSE as a feature,
-that the first-approximation provided by a memory-one strategy is no longer
+that the first-approximation provided by a memory one strategy is no longer
 sufficient.
@@
 achieve mutual cooperation with stronger strategies while also being able to
-exploit weaker strategies. This is why ZD strategies fail to appear in the top
+exploit weaker strategies. This is why ZDs fail to appear in the top
 ranks -- they try to exploit all opponents and cannot actively adapt back to
 mutual cooperation against stronger strategies, which requires more depth of memory.
-\footnote{Note that ZD strategies also tend to perform poorly in population games for
-a similar reason: they attempt to exploit other players using ZD strategies, failing to
+\footnote{Note that ZDs also tend to perform poorly in population games for
+a similar reason: they attempt to exploit other players using ZDs, failing to
 form a cooperative subpopulation. This makes them good invaders but poor resisters of invasion.}
@@
 original suggested features of good IPD strategies. Moreover, our results
-shed light on the historic performance of TFT, zero determinant strategies,
-and memory-one strategies generally. Strategies need to match their play
+shed light on the historic performance of TFT, zero-determinant strategies,
+and memory one strategies generally. Strategies need to match their play
 to the cooperativeness of the tournament population and do so in a way that
@@
 in the strategy DBS. Further, we showed that while the type of exploitation
-attempted by ZD strategies is not typically effective in tournaments, more
+attempted by ZDs is not typically effective in tournaments, more
 sophisticated strategies capable of selectively exploiting weaker opponents
@@
 while triggering grudging strategies to switch from typically cooperating to
-typically defecting. Accordingly we find that in noisy tournaments
-that the best performing players cooperate a lower rate than the tournament
+typically defecting. Accordingly, we find that in noisy tournaments
+the best performing players cooperate a lower rate than the tournament
 population on average. Nevertheless we found some strategies designed or trained

### 2020-03-30 paper/main.tex
minor tweaks I missed on the pr

@@
 The features of high performing strategies reveal why strategies such as Tit For Tat
-performed historically well in tournaments and why Zero Determinant strategies
+performed historically well in tournaments and why zero-determinant strategies
 typically do not fare well in tournament settings.
@@
 probabilistic ending tournaments is due to larger values of
-\(p_e\) which lead to shorter matches (the expected number of rounds is $1\p_e$), so the
+\(p_e\) which lead to shorter matches (the expected number of rounds is \(1 / p_e\)), so the
 impact of the PD being iterated is subdued. This is captured by the Folk
@@
 relative to the tournament population average is important. Playing a strategy
-that randomly cooperates with $C_mean$ is unlikely to be as effective as it will
+that randomly cooperates with $C_{\text{mean}}$ is unlikely to be as effective as it will
 randomly have cooperations matched with defections. In contrast, TFT naturally
-achieves a cooperation rate near $C_mean$ by virtue of copying its opponent's
+achieves a cooperation rate near $C_{\text{mean}}$ by virtue of copying its opponent's
 last move while also minimizing instances where it is exploited by an opponent

### 2020-03-30 paper/main.tex
adds plots of adjustments to mean cooperator over noise

@@
 
+The probability of noise has been observed to excessively affect optimal
+behaviour. In environments with considerable values of noise no strategy from
+our collection managed to perform sufficiently.
+Figure~\ref{fig:compared_to_mean_over_noise_probability} gives the ratio \(C_r /
+C_{\text{mean}}\) for the winners in tournaments with noise, over the
+probability of noise. From Figure~\ref{fig:noisy_discussion_over_noise} it is
+clear that the cooperating only 67\% of the time the mean cooperator did is
+optimal only when \(p_n \in [0.2, 0.4)\) and \(p_n \in [0.6, 0.7]\). In
+environments with \(p_n < 0.1\) the winners want to be close to the mean
+cooperator, similarly to standard tournaments, and as the probability of noise
+is exceeding 0.5 (the game becomes unreasonable) strategies should aim to be
+less and less cooperative.
+
+Figure~\ref{fig:compared_to_mean_over_noise_probability} gives \(C_r /
+C_{\text{mean}}\) for the winners over \(p_n\) in tournaments with noise and a
+probabilistic ending. The optimal proportions of cooperations are different
+now that the number of turns is not fixed, successful strategies
+want to be more defecting that the mean cooperator, that only changes when
+\(p_n\) approaches 0.5. Figure~\ref{fig:compared_to_mean_over_noise_probability}
+demonstrates how the adjustments to \(C_r /C_{\text{mean}}\) change over the
+noise in the to the environment, and thus supports how important adapting to
+the environment is for a strategy to be successful.
+
+\begin{figure}[!htbp]
+    \centering
+    \begin{subfigure}{0.485\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/noisy_discussion_over_noise.pdf}
+        \caption{\(C_r / C_{\text{mean}}\) distribution for winners in noisy tournaments over
+        \(p_n\).}\label{fig:noisy_discussion_over_noise}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}{0.485\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{../images/noisy_probend_discussion_over_noise.pdf}
+        \caption{\(C_r / C_{\text{mean}}\) distribution for winners in noisy probabilistic ending tournaments over
+        \(p_n\).}\label{fig:noisy_probend_discussion_over_noise}
+    \end{subfigure}
+    \caption{\(C_r / C_{\text{mean}}\) distributions over intervals of \(p_n\).
+    These distributions model the optimal proportion of cooperation
+    compared to \(C_{\text{mean}}\) as a function of (\(p_n\)).}
+    \label{fig:compared_to_mean_over_noise_probability}
+\end{figure}
+
 The distributions of the SSE across the tournament types suggest that successful

### 2020-03-30 paper/regression_on_median_score.tex
run regression on median score

\section{Multivariate linear regression on median score}\label{app:regression_median_score}

A multivariate linear regression has also been fitted to model the relationship between
the features and the median score. The features included are given
by Table~\ref{table:linear_regression_on_median} alongside their corresponding \(p\) values
in the distinct tournaments and their regression coefficients.

\newcolumntype{g}{>{\columncolor{Gray}}c}
\begin{table}[h]
    \begin{center}
\resizebox{\textwidth}{!}{
\begin{tabular}{lggccggccgg}
    \toprule
    & \multicolumn{2}{g}{Standard} & \multicolumn{2}{c}{Noisy} & \multicolumn{2}{g}{Probabilistic ending} & \multicolumn{2}{c}{Noisy probabilistic ending} & \multicolumn{2}{g}{Overall}\\
    \midrule
    & \multicolumn{2}{g}{\(R\) adjusted: 0.576} & \multicolumn{2}{c}{\(R\) adjusted: 0.679} & \multicolumn{2}{g}{\(R\) adjusted: 0.816} & \multicolumn{2}{c}{\(R\) adjusted: 0.930} & \multicolumn{2}{g}{\(R\) adjusted: 0.318} \\
    {} &  Coefficient &  \(p\)-value &  Coefficient &  \(p\)-value &  Coefficient &  \(p\)-value &  Coefficient &  \(p\)-value &  Coefficient &  \(p\)-value \\
    \midrule
    $CC$ to $C$ rate   &  0.043 &  0.000 & -0.380 &  0.000 &  0.224 &  0.000 &  0.078 &    0.0 &  0.308 &    0.0 \\
    $CD$ to $C$ rate   & -0.325 &  0.000 &  0.124 &  0.000 &  0.060 &  0.000 &  0.073 &    0.0 & -0.014 &    0.0 \\
    $C_r$ / $C_{max}$  &      - &      - & -1.044 &  0.000 &      - &      - & -1.251 &    0.0 &      - &      - \\
    $C_r$ / $C_{mean}$ &  0.553 &  0.000 & -0.101 &  0.000 & -1.136 &  0.000 & -0.089 &    0.0 & -0.665 &    0.0 \\
    $C_{max}$          &  0.059 &  0.000 &      - &      - & -0.044 &  0.086 & -1.396 &    0.0 &      - &      - \\
    $C_{mean}$         &  1.837 &  0.000 &  3.078 &  0.000 &  1.506 &  0.000 &  3.645 &    0.0 &      - &      - \\
    $C_{min}$          &  0.156 &  0.000 &  1.528 &  0.000 &  0.311 &  0.000 &      - &      - &      - &      - \\
    $C_{min}$ / $C_r$  & -0.049 &  0.000 & -0.378 &  0.000 & -0.204 &  0.000 &      - &      - & -0.257 &    0.0 \\
    $DC$ to $C$ rate   & -0.204 &  0.000 &  0.074 &  0.000 &  0.066 &  0.000 &  0.066 &    0.0 &  0.007 &    0.0 \\
    $k$                & -0.000 &  0.853 & -0.000 &  0.987 &  0.000 &  0.008 &  0.000 &    0.0 &      - &      - \\
    $n$                & -0.000 &  0.000 &      - &      - &      - &      - &      - &      - &      - &      - \\
    $p_e$              &      - &      - &      - &      - &  0.025 &  0.000 & -0.095 &    0.0 &      - &      - \\
    $p_n$              &      - &      - &  0.124 &  0.000 &      - &      - &      - &      - &      - &      - \\
    SSE                & -0.294 &  0.000 & -0.319 &  0.000 &  0.055 &  0.000 &  0.010 &    0.0 & -0.015 &    0.0 \\
    constant           &  0.925 &  0.000 &  1.536 &  0.000 &  2.466 &  0.000 &  2.299 &    0.0 &  2.924 &    0.0 \\
    memory usage       &  0.010 &  0.000 & -0.004 &  0.000 &      - &      - &      - &      - &      - &      - \\
    \bottomrule
\end{tabular}}
\end{center}
\caption{Results of multivariate linear regressions with the median score as the dependent variable.
\(R\) squared is reported for each model.}
\label{table:linear_regression_on_median}
\end{table}

### 2020-04-01 paper/main.tex
run regression on median score
minor suggestions by VK
Co-Authored-By: Vince Knight <vincent.knight@gmail.com>

@@
 
-Other works have built upon the limitations of the TFT, and others have shown
+Other works have built upon the limitations of TFT, and others have shown
 that suggestions made by Axelrod did not necessarily lift to alternative environmental rules.
@@
 
-In comparison, the performance the top ranked strategies in noisy environments
+In comparison, the performance of the top ranked strategies in noisy environments
 when \(p_n\in [0, 1]\) is bimodal. The top strategies include strategies which
@@
 \begin{itemize}
-    \item In standard tournaments the dominating strategies were clever
+    \item In standard tournaments the dominating strategies were 
     strategies that had been trained using reinforcement learning techniques.
@@
 Now we examine performance of the strategies based on features of strategies described in
-Table~\ref{table:manual_features}. These feature are measures regarding a
+Table~\ref{table:manual_features}. These features are measures regarding a
 strategy's behaviour from the tournaments the strategies competed in as well as
@@
 
-Similarly, these results suggest an explanation regarding the perhaps intuitively unexpected
+Similarly, these results suggest an explanation regarding the intuitively unexpected
 effectiveness of memory one strategies historically. Given that among the important
-features associated to success are the relative cooperation rate to the population
+features associated with success are the relative cooperation rate to the population
 average and the four memory-one probabilities of cooperating conditional on the
@@
     \begin{center}
-\resizebox{.8\textwidth}{!}{
+\resizebox{\textwidth}{!}{
     \input{regression_table.tex}}
@@
 \end{table}
+
+A multivariate linear regression has also be fitted on the median score. The
+coefficients and \(p\) values of the features can be found in
+Appendix~\ref{app:regression_median_score}. The results of the two methods
+are in agreement.
 
@@
 tournaments are also given in Figure~\ref{fig:discussion_standard}. The SSE
-distributions for the winners indicate that they strategy's behaved in ZD way in
+distributions for the winners indicate that the strategy behaved in a ZD way in
 several tournaments, however, not constantly. The winners participated in
@@
 the Appendix~\ref{app:clustering}. The results uphold the outcomes of the
-correlation and multivariate regression methods. It also evaluates the effects
+correlation and multivariate regression. It also evaluates the effects
 of the classifiers stochastic, make use of game, and make use of length which
@@
 and~\ref{section:evaluation_of_performance} have demonstrated that there are
-properties associated with the success of strategies. A few the properties that
+properties associated with the success of strategies. A few of the properties that
 have been identified by this manuscript's analysis contradict the properties of
@@
 \input{random_forest_evaluation}
+\input{regression_on_median_score}
 \input{strategies_list_section}

### 2020-04-09 paper/main.tex
minor re writes by v.k.
Co-Authored-By: Vince Knight <vincent.knight@gmail.com>

@@
 robin computer tournament became a common evaluation technique for newly designed
-strategies. Many tournaments have followed Axelrod's~\cite{Bendor1991, Stephens2002,
+strategies. Many tournaments have followed Axelrod's~\cite{Bendor1991, Beaufils1997, Stephens2002,
 Kendall2007, Stewart2012, Harper2017} and today more hundreds of strategies exist
@@
 
-Axelrod performed two widely-known computer tournaments~\cite{Axelrod1980a,
-Axelrod1980b} in the 1980's. The
-winner of both tournaments was the simple strategy Tit For Tat (TFT) which cooperated
+The
+winner of both of Axelrod's tournaments~\cite{Axelrod1980a,
+Axelrod1980b} was the simple strategy Tit For Tat (TFT) which cooperated
 on the first turn and then simply copied the previous action of its opponent,
@@
 strategy with the same intuition as Gradual is Adaptive Tit for
-Tat~\cite{tzafestas-2000a}. Adaptive Tit for Tat does not keep a permanent
-count of past defections, it maintains a continually updated estimate of the
+Tat~\cite{tzafestas-2000a}. Adaptive Tit for Tat maintains a continually updated estimate of the
 opponent's behaviour, and uses this estimate to condition its future actions.
@@
 Other works have built upon the limitations of TFT, and others have shown
-that suggestions made by Axelrod did not necessarily lift to alternative environmental rules.
+that suggestions made by Axelrod did not necessarily apply in alternative environmental settings.
 In~\cite{Bendor1991, Donninger1986, Molander1985, Hammerstein1984} it was shown
@@
 work. In~\cite{Harper2017} a
-series of clever strategies were introduced, and a tournament containing over
+series of strategies trained using reinforcement learning were introduced, and a tournament containing over
 200 strategies featured no ZD strategies ranked in top
@@
 strategies can be characterised as ``cheaters'' because the source code of the strategies
-allows them to know the number of turns in a match (if they are specified).
+allows them to know the number of turns in a match (unless the match has a probabilistic ending).
 These strategies were expected to not perform as well in
@@
 e~\cite{axelrodproject}, and the Retaliate strategies which are designed to
-defect if the opponent has tricked them more often than x\% of the times that
+defect if the opponent has tricked them more often than a given percentage of the times that
 they have done the same. The bimodality of the \(r\) distributions is explained

### 2020-04-13 paper/correlation_section.tex

\section{Correlation coefficients}\label{app:correlations}

A graphical representation of the correlation coefficients for the features in
Table~\ref{table:manual_features}.

\begin{figure}[!htbp]
        \begin{center}
            \includegraphics[width=.75\linewidth]{../images/standard_correlation_plot.pdf}
        \end{center}
        \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
        for standard tournaments}
\end{figure}
\begin{figure}[!htbp]
    \begin{center}
        \includegraphics[width=.75\linewidth]{../images/noise_correlation_plot.pdf}
    \end{center}
    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
    for noisy tournaments}
\end{figure}
\begin{figure}[!htbp]
    \begin{center}
        \includegraphics[width=.75\linewidth]{../images/probend_correlation_plot.pdf}
    \end{center}
    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
    for probabilistic ending tournaments}
\end{figure}
\begin{figure}[!htbp]
    \begin{center}
        \includegraphics[width=.75\linewidth]{../images/probend_noise_correlation_plot.pdf}
    \end{center}
    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
    for noisy probabilistic ending tournaments}
\end{figure}
\begin{figure}[!htbp]
    \begin{center}
        \includegraphics[width=.75\linewidth]{../images/merged_correlation_plot.pdf}
    \end{center}
    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
    for data set}
\end{figure}

### 2020-04-13 paper/main.tex

@@
 and the rate of which the strategy cooperated after each state. The \textbf{normalised rank}
-feature that is manually added. The rank \(R\) of a given
+feature that is manually added. The rank \(R\) of a given. % TODO Clarify how strategies are ranked (see email discussion)
 strategy can vary between 0 and \(N-1\). Thus, the normalised rank,
@@
     method identifies the ZDs closest to a given strategy and calculates the
-    algebraic distance between them, defined as SSE. A SSE value of 1 indicates
+    algebraic distance between them as the sum of squared error (SSE). A SSE value of 1 indicates
     no extortionate behaviour at all whereas a value of 0 indicates that a
-    strategy is behaving a ZDs. The rest of the features considered are the $CC$
+    strategy is behaving as a ZDs. The rest of the features considered are the $CC$
     to $C$, $CD$ to $C$, $DC$ to $C$, and $DD$ to $C$ rates as well as
@@
 
-The memory usage of strategies with an infinite memory size, for example Evolved
-FSM 16 Noise 05, is equal to 1. Otherwise the memory usage is the number of
+The memory usage of strategies is the number of
 rounds of play used by the strategy divided by the number of turns in each match. 
 For example, Winner12 uses the previous two rounds of play, and if participating in a
-participated in a tournament where $n$ was 100 the memory usage would be 2/100.
+participated in a match with 100 turns, the memory usage would be 2/100.
+For strategies with an infinite memory size, for example Evolved
+FSM 16 Noise 05, is equal to 1.
 Note that for tournaments with a probabilistic
@@
 pattern. TFT does not appear in the top ranks in
-these tournaments because it is too nice. Strategies like Grudger will always
+ tournaments with more aggressive strategies because it is too nice. Strategies like Grudger will always
 defect after a fixed number of opponent defections, which allows them to
@@
 strategy such as TFT. Usage of more history becomes valuable when there are
-exploitable opponent patterns, indicated by the importance of SSE as a feature,
-that the first-approximation provided by a memory one strategy is no longer
+exploitable opponent patterns. This is indicated by the importance of SSE as a feature,
+showing that the first-approximation provided by a memory one strategy is no longer
 sufficient.
@@
 the correlation matrices given in Appendix~\ref{app:correlations} several of the
-features are highly correlated. Highly correlated features have been removed
+features are highly correlated and have been removed
 before fitting the linear regression model. The features included are given
@@
 coefficients and \(p\) values of the features can be found in
-Appendix~\ref{app:regression_median_score}. The results of the two methods
-are in agreement.
+Appendix~\ref{app:regression_median_score}. This approach leads to similar conclusions.
 
@@
 correlation and multivariate regression. It also evaluates the effects
-of the classifiers stochastic, make use of game, and make use of length which
-have not been evaluated by the methods above because there are binary variables.
-The results imply that they have no significant effect on a strategy's
+of the whether or not a strategy is stochastic, makes use of the knowledge of the utility values, or makes use of match length.
+These were not evaluated by the methods above because there are binary variables.
+The results showed that they have no significant effect on a strategy's
 performance.
@@
 So what is the best way of playing the IPD? And is there a single dominant
-strategy for the IPD? There was not a single strategy within the collection of the
+strategy for the IPD?
+
+There was not a single strategy within the collection of the
 \numberofstrategies strategies, that has managed to perform well in all the
@@
 Axelrod~\cite{Axelrod1981}. Namely, in Section~\ref{section:top_performances} it
-was shown that trained strategies and strategies that decided their actions
-based on pre-designed strategies to maximise their utility dominated several
+was shown that trained strategies dominated several
 tournaments across tournament types, hinting that successful IPD strategies are
@@
 Thus, the five properties successful strategies need to have in a IPD competition
-are: be nice, be provocable and contrite, be a little envious, be clever, and adapt to the
-environment (including the population of strategies).
+are:
+
+\begin{itemize}
+\item be nice, 
+    \item be provocable and contrite, 
+    \item be a little envious, 
+    \item be clever, 
+    \item adapt to theenvironment (including the population of strategies).
+\end{itemize}
 

### 2020-04-14 paper/main.tex

@@
 
-\title{Properties of winning Iterated Prisoner's Dilemma strategies.}
+\title{Properties of Winning Iterated Prisoner's Dilemma Strategies.}
 \author{Nikoleta E. Glynatsi, Vincent A. Knight, Marc Harper}
@@
 
-\[\begin{pmatrix}
-R & S \\
-T & P
-\end{pmatrix}\]
+\begin{center}
+\begin{tabular}{c|c|c}
+& Cooperate (C) & Defect (D) \\
+\hline
+Cooperate (C) & R & S \\
+\hline
+Defect (D) & T & P \\
+\end{tabular}
+\end{center}
 
@@
 
-The
-winner of both of Axelrod's tournaments~\cite{Axelrod1980a,
-Axelrod1980b} was the simple strategy Tit For Tat (TFT) which cooperated
-on the first turn and then simply copied the previous action of its opponent,
+The winner of both of Axelrod's tournaments~\cite{Axelrod1980a, Axelrod1980b}
+was the simple strategy Tit For Tat (TFT) which cooperates
+on the first turn and thereafter copies the previous action of its opponent,
 retailiating against defections with a defection, and forgiving a defection if followed
@@
 series of evolutionary experiments~\cite{Axelrod1981}, TFT was often
-claimed to be the most robust basic strategy in the IPD.
+claimed to be a highly robust (and sometimes the most robust) strategy for the IPD.
 
 There are strategies which have built upon TFT and the reciprocity based approach.
-In~\cite{Beaufils1997} Gradual was introduced which was constructed to have the
-same qualities as those of TFT except one: Gradual had a memory
-of the game since the beginning of it. Gradual recorded the number of defections
-by the opponent and punished them with a growing number of defections. It would
-then enter a calming state in which it would cooperates for two rounds. A
+In~\cite{Beaufils1997} a strategy called Gradual was introduced, constructed to have the
+same qualities as those of TFT with one addition. Gradual has a memory
+of the previous rounds of play of the game , recording the number of defections
+by the opponent and punishing them with a growing number of defections. It
+then enters a calming state in which it cooperates for two rounds. A
 strategy with the same intuition as Gradual is Adaptive Tit for
 Tat~\cite{tzafestas-2000a}. Adaptive Tit for Tat maintains a continually updated estimate of the
-opponent's behaviour, and uses this estimate to condition its future actions.
-
-Other works have built upon the limitations of TFT, and others have shown
+opponent's behaviour and uses this estimate to condition its future actions.
+
+Other work has built upon the limitations of TFT, and in some cases have shown
 that suggestions made by Axelrod did not necessarily apply in alternative environmental settings.
@@
 and Pavlov (aka Win Stay Lose Shift)~\cite{Nowak1993}, as well as later
-variants such as OmegaTFT \cite{kendall2007iterated}. Introduction of new strategies
-is often accompanied by a claim that the new strategy is the best known despite
-only being tested against a small number of opponents, or specific classes of
+variants such as OmegaTFT \cite{kendall2007iterated}. The introduction of a new strategy
+is often accompanied by a claim that the new strategy is the best known, despite
+only being tested against a small number of opponents or against specific classes of
 opponents not necessarily representative of all possible or all published strategies.
 The lack of testing against formally defined strategies and tournament winners
-is understandable given the effort required to implement
-\footnote{Implementing prior strategies faithfully is often extremely difficult or impossible
-due to insufficient descriptions and lack of published implementations or code.}
-the hundreds of published IPD strategies, yet calls into question any claims of superiority
-or robustness of newly introduced
-strategies.
+is understandable given the effort required to implement the hundreds of published IPD strategies 
+\footnote{Implementing prior strategies faithfully is often extremely difficult or impossible due to insufficient descriptions and lack of published implementations or code.}, 
+yet calls into question any claims of superiority or robustness of newly introduced strategies.
 
 A set of envious IPD strategies were introduced called zero-determinant strategies (ZDs)
-in~\cite{Press2012}. By
-forcing a linear relationship between stationary payoffs ZDs can ensure that they will
-never receive less than their memory-one opponents. While ZDs
-were introduced with a small tournament in which some were reportedly
-successful \cite{Stewart2012}, this result has not generally held in future
-work. In~\cite{Harper2017} a
-series of strategies trained using reinforcement learning were introduced, and a tournament containing over
-200 strategies featured no ZD strategies ranked in top
-spots. Instead, the top ranked strategies were a set of ``clever''
-(in the sense of Axelrod's characteristics) trained
+in~\cite{Press2012}. These strategies attempt to force a linear relationship between
+stationary payoffs against other memory-one opponents, potentally ensuring that they
+receive a higher average payout. While ZDs were introduced with a small tournament in
+which some were reportedly successful \cite{Stewart2012}, this result has not generally
+held in future work. In~\cite{Harper2017} a series of strategies trained using
+reinforcement learning were introduced, and a tournament containing over 200 strategies
+featured no ZD strategies ranked in top spots. Instead, the top ranked strategies
+were a set of ``clever'' (in the sense of Axelrod's characteristics) trained
 strategies based on lookup tables~\cite{Axelrod1987}, hidden Markov
@@
 
-The later part of the paper evaluates
-the impact of features on the performance of the strategies using modern
-machine learning techniques. These features include measures regarding a
-strategy's behaviour and measures regarding the tournaments. The outcomes of our
-work reinforce the discussion started by Axelrod, and it concludes that the properties
-of a successful strategy in the IPD are:
+The later part of the paper evaluates the impact of various strategy features
+on the performance of the strategies using standard statistical and machine learning techniques. These
+features include measures regarding a strategy's behaviour and measures regarding
+the tournaments. The outcomes of our work reinforce the discussion started by Axelrod
+and concludes that the properties of a successful strategy in the IPD are:
 
@@
     \item \st{Do not be envious} Be a little bit envious
-    \item Be "nice"; Do not be the first to defect
+    \item Be "nice" in non-noisy environments or when game lengths are longer
     \item Reciprocate both cooperation and defection; Be provocable and forgiving
@@
 
-\textbf{Standard tournaments} are tournaments similar to that of Axelrod's well-known
+\textbf{Standard tournaments} are tournaments similar to that of R. Axelrod's well-known
 tournaments ~\cite{Axelrod1980a}. There are \(N\) strategies which all play an iterated
@@
 reinforcement learning algorithms (evolutionary and particle swarm algorithms).
-They have been trained to perform well against the strategies
+They have been trained to perform well against a subset of the strategies
 in APL in a standard tournament, thus their performance in the
@@
 strategies can be characterised as ``cheaters'' because the source code of the strategies
-allows them to know the number of turns in a match (unless the match has a probabilistic ending).
-These strategies were expected to not perform as well in
+allows them to know the number of turns in a match (unless the match has a probabilistic ending). These strategies were expected to not perform as well in
 tournaments where the number of turns is not specified. Finally, Winner
@@
 
-In the case of noisy tournaments with \(p_n < 0.1\) the top performed strategies
+In the case of noisy tournaments with smaller noise \(p_n < 0.1\) the top performed strategies
 include strategies specifically designed for noisy tournaments. These are DBS,
 Evolved FSM 16 Noise 05, Evolved ANN 5 Noise 05, PSO Gambler 2 2 2 Noise 05 and
-Omega Tit For Tat~\cite{kendall2007iterated}. Omega TFT, another strategy designed
+Omega Tit For Tat~\cite{kendall2007iterated}. Omega TFT, a strategy designed
 to break the deadlocking cycles of CD and DC that TFT can fall into in noisy
@@
 tournaments, the successful strategies in this given setting performed well
-overall in the tournaments they participated in,
-Figure~\ref{fig:noise_subset_results}.
-
-In comparison, the performance of the top ranked strategies in noisy environments
+overall in the tournaments they participated in (see Figure~\ref{fig:noise_subset_results}).
+
+In contrast, the performance of the top ranked strategies in noisy environments
 when \(p_n\in [0, 1]\) is bimodal. The top strategies include strategies which
@@
     \includegraphics[width=.92\textwidth]{../images/noise_effect.pdf}
-    \caption{\(r\) distributions for top 6 strategies in noisy tournaments over
+    \caption{Normalised rank \(r\) distributions for top 6 strategies in noisy tournaments over
     the probability of noisy ($p_n$).}
@@
 The new entrants to the most effective strategies list in probabilistic ending
-tournaments with \(p_e< 0.1\) are a series of Meta strategies, trained strategies
+tournaments with \(p_e< 0.1\) are a series of ensembled Meta-strategies, trained strategies
 which performed well
 in standard tournaments, and Grudger~\cite{axelrodproject} and Spiteful Tit for
-Tat~\cite{prison}. The Meta strategies~\cite{axelrodproject} create a team of
-strategies and play as an ensemble or some other combination of their team
-members. Figure~\ref{fig:probend_subset_results} indicates that these strategies
+Tat~\cite{prison}. The Meta strategies~\cite{axelrodproject} utilize a team of
+strategies and aggregate the potential actions of the team members into a single action
+in various ways. Figure~\ref{fig:probend_subset_results} indicates that these strategies
 performed well in any probabilistic ending tournament they competed in.
@@
 Tat)~\cite{Nachbar1992} and Defector, and a series of strategies based on finite
-state automata introduced by Daniel Ashlock and Wendy Ashlock; Fortress 3,
+state automata introduced by Daniel Ashlock and Wendy Ashlock: Fortress 3,
 Fortress 4 (both introduced in~\cite{Ashlock2006}), Raider~\cite{Ashlock2014}
@@
     \includegraphics[width=.92\textwidth]{../images/folk_theorem.pdf}
-    \caption{\(r\) distributions for top 6 strategies in probabilistic ending tournaments
+    \caption{Normalised rank \(r\) distributions for top 6 strategies in probabilistic ending tournaments
     over $p_e$. The 6 strategies start of with a high median rank,
@@
         \includegraphics[width=.65\textwidth]{../images/performance_merged.pdf}
-        \caption{\(r\) distributions for best performed strategies in the data set~\cite{data}.
+        \caption{Normalised rank \(r\) distributions for best performed strategies in the data set~\cite{data}.
         A lower value of \(\bar{r}\) corresponds to a more successful
@@
     0.1 was considered, the successful strategies were strategies specifically
-    designed for noisy environments.
+    designed or trained for noisy environments.
     \item In probabilistic ending tournaments most of the highly ranked
@@
 and more specifically, the suggestions `Do not be clever' and `Do not be envious'.
-The features and properties contributing a strategy's success are further
-explored in Section~\ref{section:evaluation_of_performance}.
+We dig deeper into the crucial strategy features for success in the following sections.
 
@@
 
-Now we examine performance of the strategies based on features of strategies described in
+For each strategy we have a variety of features, described in
 Table~\ref{table:manual_features}. These features are measures regarding a
@@
 and the cooperating ratio compared to $C_{\text{median}}$ and $C_{\text{mean}}$
-have a moderate negative effect on the normalised rank, and a moderate positive
+have a moderate negative effect on the normalised rank (smaller rank is better), and a moderate positive
 on the median score. The SSE error and the $DD$ to $C$ have the opposite
 effects. Thus, in standard tournaments behaving cooperatively corresponds to a
-more successful performance. Even though being nice pays off,
-that's not true against defective strategies. Being more cooperative after a mutual
-defection is associated to lesser overall success in terms of normalised rank.
+more successful performance. Even though being nice generally pays off
+that does not hold against defective strategies. Being more cooperative after a mutual
+defection, that is not retaliating, is associated to lesser overall success in terms of normalised rank.
 Figure~\ref{fig:rates_of_winners_in_standard_tournaments} confirms that the
@@
 that randomly cooperates with $C_{\text{mean}}$ is unlikely to be as effective as it will
-randomly have cooperations matched with defections. In contrast, TFT naturally
+randomly have cooperations matched with defections, and it may be punished for
+defections against cooperations by retailiating opponents. In contrast, TFT naturally
 achieves a cooperation rate near $C_{\text{mean}}$ by virtue of copying its opponent's
@@
 (cooperating while the opponent defects), at least in non-noisy tournaments.
-\footnote{This also explains why Tit For N Tats does not fare well -- it fails
-to achieve the proper cooperation ratio.}
+\footnote{This also explains why Tit For N Tats does not fare well for $N > 1$ -- it fails
+to achieve the proper cooperation ratio by tolerating too many defections.}
 TFT forces the opponent to pay back the (C, D) round with a (D, C) round before
@@
 in Axelrod's original tournaments as most strategies submitted to those tournaments
-were typically cooperative and relatively few strategies used an easily exploitable
-pattern. TFT does not appear in the top ranks in
- tournaments with more aggressive strategies because it is too nice. Strategies like Grudger will always
+were typically cooperative and relatively few strategies played with an easily exploitable
+pattern. TFT does not appear in the top ranks in tournaments with more aggressive
+strategies because it is too nice. Strategies like Grudger will always
 defect after a fixed number of opponent defections, which allows them to
@@
 allowing strategies to attempt exploitation, whereas in a noise-free environment,
-exploitation is risky because several strategies exhibit a Grudger-like behavior,
-reducing the overall value in attempting to exploit strategies like Cooperator.
+attempting exploitation can be risky if strategies that exhibit a Grudger-like behavior
+are present, reducing the overall value in attempting to exploit strategies like Cooperator.
 
@@
 average and the four memory-one probabilities of cooperating conditional on the
-previous round of play, all five features can be optimized by a memory one
+previous round of play, these features can be optimized by a memory one
 strategy such as TFT. Usage of more history becomes valuable when there are
@@
 
-The probability of noise has been observed to excessively affect optimal
-behaviour. In environments with considerable values of noise no strategy from
-our collection managed to perform sufficiently.
+The probability of noise has been observed to substantially affect optimal
+behaviour.
 Figure~\ref{fig:compared_to_mean_over_noise_probability} gives the ratio \(C_r /
@@
 cooperator, similarly to standard tournaments, and as the probability of noise
-is exceeding 0.5 (the game becomes unreasonable) strategies should aim to be
-less and less cooperative.
+is exceeding 0.5 (where the game is effectively inverted) strategies should
+aim to be less and less cooperative.
 
@@
 strategies exhibit some extortionate behaviour, but not constantly.
-ZDs are a set of strategies that are envious as they try to exploit their
+ZDs are a set of strategies that are often envious as they try to exploit their
 opponents. The winners of the tournaments considered in this work are
@@
 achieve mutual cooperation with stronger strategies while also being able to
-exploit weaker strategies. This is why ZDs fail to appear in the top
+exploit weaker strategies. This is why ZDs fail to appear in the tops
 ranks -- they try to exploit all opponents and cannot actively adapt back to
@@
 There was not a single strategy within the collection of the
-\numberofstrategies strategies, that has managed to perform well in all the
+\numberofstrategies strategies that managed to perform well in all the
 tournaments variations it competed in.
-Even if on average a strategy ranked highly in a specific environment it did not
+Even if on average a strategy ranked highly in a specific environment this did not
 guarantee its success over the different tournament types. However, the results
 of sections~\ref{section:top_performances}
-and~\ref{section:evaluation_of_performance} have demonstrated that there are
+and~\ref{section:evaluation_of_performance} demonstrated that there are
 properties associated with the success of strategies. A few of the properties that
@@
 \begin{itemize}
-\item be nice, 
+\item be nice, if the environment isn't noisy and the games are long
     \item be provocable and contrite, 
     \item be a little envious, 
-    \item be clever, 
-    \item adapt to theenvironment (including the population of strategies).
+    \item it's ok to be clever, 
+    \item adapt to the environment (including the population of strategies).
 \end{itemize}

### 2020-04-14 paper/main.tex
reads over introduction

@@
 strategies, refining the properties described by R. Axelrod in light of
-recent and more diverse opponent populations. These are: be nice, be provocable and contrite,
+recent and more diverse opponent populations. These are: be nice, be provocable and forgiving,
 be a little envious, be clever, and adapt to the environment, which includes the parameters
@@
 \begin{center}
+{\renewcommand{\arraystretch}{2}%
 \begin{tabular}{c|c|c}
@@
 Defect (D) & T & P \\
-\end{tabular}
+\end{tabular}}
 \end{center}
@@
 same qualities as those of TFT with one addition. Gradual has a memory
-of the previous rounds of play of the game , recording the number of defections
+of the previous rounds of play of the game, recording the number of defections
 by the opponent and punishing them with a growing number of defections. It
@@
 reinforcement learning were introduced, and a tournament containing over 200 strategies
-featured no ZD strategies ranked in top spots. Instead, the top ranked strategies
+featured no ZDs ranked in top spots. Instead, the top ranked strategies
 were a set of ``clever'' (in the sense of Axelrod's characteristics) trained

### 2020-04-14 paper/main.tex
replace Axelrod with R. Axelrod
Based on Marc's suggestion

@@
 has been of interest to the scientific community since the formulation of the
-game in 1950~\cite{Flood1958}. Following the computer tournaments of Axelrod in the
+game in 1950~\cite{Flood1958}. Following the computer tournaments of R. Axelrod in the
 1980's~\cite{Axelrod1980a, Axelrod1980b}, a strategy's performance in a round
@@
 
-The winner of both of Axelrod's tournaments~\cite{Axelrod1980a, Axelrod1980b}
+The winner of both of R. Axelrod's tournaments~\cite{Axelrod1980a, Axelrod1980b}
 was the simple strategy Tit For Tat (TFT) which cooperates
@@
 retailiating against defections with a defection, and forgiving a defection if followed
-by a cooperation. Axelrod concluded that the strategy's robustness was due to four
+by a cooperation. R. Axelrod concluded that the strategy's robustness was due to four
 properties, which he adapted into four suggestions on doing well in an IPD:
@@
 Other work has built upon the limitations of TFT, and in some cases have shown
-that suggestions made by Axelrod did not necessarily apply in alternative environmental settings.
+that suggestions made by R. Axelrod did not necessarily apply in alternative environmental settings.
 In~\cite{Bendor1991, Donninger1986, Molander1985, Hammerstein1984} it was shown
@@
 featured no ZDs ranked in top spots. Instead, the top ranked strategies
-were a set of ``clever'' (in the sense of Axelrod's characteristics) trained
+were a set of ``clever'' (in the sense of R. Axelrod's characteristics) trained
 strategies based on lookup tables~\cite{Axelrod1987}, hidden Markov
@@
 memory two strategies). Additionally, our tournaments come in a
-number of variations including standard tournaments emulating Axelrod's original tournaments,
+number of variations including standard tournaments emulating R. Axelrod's original tournaments,
 tournaments with noise, probabilistic match length, and both noise and probabilistic match length.
@@
 features include measures regarding a strategy's behaviour and measures regarding
-the tournaments. The outcomes of our work reinforce the discussion started by Axelrod
+the tournaments. The outcomes of our work reinforce the discussion started by R. Axelrod
 and concludes that the properties of a successful strategy in the IPD are:

### 2020-04-14 paper/main.tex
reads over data collection
reads over top ranked strategies

@@
 \textbf{Standard tournaments} are tournaments similar to that of R. Axelrod's well-known
-tournaments ~\cite{Axelrod1980a}. There are \(N\) strategies which all play an iterated
+tournaments~\cite{Axelrod1980a}. There are \(N\) strategies which all play an iterated
 game of \(n\) number of turns against each other. Note that self-interactions
@@
 that the probabilities of noise and ending of the match varied between 0 and
-1. However, commonly used values of these probabilities are
-values are often less than 0.1. Thus,
+1. However, commonly used values for these probabilities are values less than 0.1.
+Thus,
 Table~\ref{table:top_performances} also includes the top 15 strategies in noisy
@@
 in~\cite{Harper2017}. These are strategies based on finite state automata (FSM),
-hidden markov models (HMM), artificial neural networks (ANN), lookup tables
+hidden Markov models (HMM), artificial neural networks (ANN), lookup tables
 (LookerUp) and stochastic lookup tables (Gambler) that have been trained using
@@
 Omega Tit For Tat~\cite{kendall2007iterated}. Omega TFT, a strategy designed
-to break the deadlocking cycles of CD and DC that TFT can fall into in noisy
+to break the deadlocking cycles of \(CD\) and \(DC\) that TFT can fall into in noisy
 environments, places 10th. The rest of the top ranks are
@@
 tournaments, the successful strategies in this given setting performed well
-overall in the tournaments they participated in (see Figure~\ref{fig:noise_subset_results}).
+overall the tournaments they participated in (see Figure~\ref{fig:noise_subset_results}).
 
@@
 The new entrants to the most effective strategies list in probabilistic ending
-tournaments with \(p_e< 0.1\) are a series of ensembled Meta-strategies, trained strategies
+tournaments with \(p_e< 0.1\) are a series of ensembled Meta strategies, trained strategies
 which performed well
@@
     in~\cite{Harper2017} and Nice Meta Winner and NMWE Memory One are strategies
-    based on teams. Grudger is a strategy from Axelrod's original tournament and
+    based on teams. Grudger is a strategy from R. Axelrod's original tournament and
     Forgetful Fool Me Once is based on the same approach as
@@
 Though there is not a single strategy that repeatably outranks all others in any
-of the distinct tournament types, or even across the tournaments type, there
+of the distinct tournament types, or even across the tournament types, there
 are specific types of strategies have been repeatably ranked in the top ranks.
@@
 and strategies that would adapt their behaviour based on preassigned rules
-to achieve the highest outcome. These results contradict some of Axelrod's suggestions,
+to achieve the highest outcome. These results contradict some of R. Axelrod's suggestions,
 and more specifically, the suggestions `Do not be clever' and `Do not be envious'.

### 2020-04-14 paper/main.tex
reads over evaluation of performance
Fixes correlation table

@@
 rounds of play used by the strategy divided by the number of turns in each match.
-For example, Winner12 uses the previous two rounds of play, and if participating in a
-participated in a match with 100 turns, the memory usage would be 2/100.
+For example, Winner12 uses the previous two rounds of play, and if participating
+in a match with 100 turns its memory usage would be 2/100.
 For strategies with an infinite memory size, for example Evolved
-FSM 16 Noise 05, is equal to 1.
+FSM 16 Noise 05, memory usage is equal to 1.
 Note that for tournaments with a probabilistic
@@
 to achieve the proper cooperation ratio by tolerating too many defections.}
-TFT forces the opponent to pay back the (C, D) round with a (D, C) round before
+TFT forces the opponent to pay back the \((C, D)\) round with a \((D, C)\) round before
 returning to mutual cooperation. This explains why TFT performed well
@@
 toward always defecting, leading them to exploit strategies like Cooperator. In
-such a scenario the noisy environment effectively voids Axelrod's rule to be nice,
+such a scenario the noisy environment effectively voids R. Axelrod's rule to be nice,
 allowing strategies to attempt exploitation, whereas in a noise-free environment,
@@
 Similarly, these results suggest an explanation regarding the intuitively unexpected
-effectiveness of memory one strategies historically. Given that among the important
+effectiveness of memory-one strategies historically. Given that among the important
 features associated with success are the relative cooperation rate to the population
 average and the four memory-one probabilities of cooperating conditional on the
-previous round of play, these features can be optimized by a memory one
+previous round of play, these features can be optimized by a memory-one
 strategy such as TFT. Usage of more history becomes valuable when there are
 exploitable opponent patterns. This is indicated by the importance of SSE as a feature,
-showing that the first-approximation provided by a memory one strategy is no longer
+showing that the first-approximation provided by a memory-one strategy is no longer
 sufficient.
@@
 
-The distributions of SSE and \(CC\) to \(D\) rate for the winners of standard
+The distributions of SSE and \(CD\) to \(D\) rate for the winners of standard
 tournaments are also given in Figure~\ref{fig:discussion_standard}. The SSE
@@
 matches where they did not try to extortionate their opponents. Furthermore, the
-\(CC\) to \(D\) distribution indicates that if a strategy were to defect against
+\(CD\) to \(D\) distribution indicates that if a strategy were to defect against
 the winners they would reciprocate on average with a probability of 0.5.

### 2020-04-14 paper/main.tex
reads over conclusion

@@
 This manuscript has explored the performance of \numberofstrategies strategies
-of the Iterated Prisoner's Dilemma in a large number of computer tournaments.
+of the IPD in a large number of computer tournaments.
 We analyzed and extracted the salient features of the best performing strategies
-across various tournament types, casting the results in terms of Axelrod's
+across various tournament types, casting the results in terms of R. Axelrod's
 original suggested features of good IPD strategies. Moreover, our results
 shed light on the historic performance of TFT, zero-determinant strategies,
-and memory one strategies generally. Strategies need to match their play
+and memory-one strategies generally. Strategies need to match their play
 to the cooperativeness of the tournament population and do so in a way that
@@
 specifically in this work, to the mean cooperator. This section also
-demonstrated that a strategy should reciprocate, as suggested by Axelrod, but in
+demonstrated that a strategy should reciprocate, as suggested by R. Axelrod, but in
 some environments, such as standard and noisy, it should relax its readiness to
@@
 \item be nice, if the environment isn't noisy and the games are long
-    \item be provocable and contrite, 
+    \item be provocable and forgiving,
     \item be a little envious,

### 2020-04-14 src/correlations.py
Final read (#26)
* reads over introduction

* replace Axelrod with R. Axelrod

Based on Marc's suggestion

* reads over data collection

* reads over top ranked strategies

* reads over evaluation of performance

Fixes correlation table

* reads over conclusion

@@ -1,0 +1,97 @@
+import matplotlib
+import matplotlib.pyplot as plt
+import pandas as pd
+import seaborn as sns
+
+font = {"size": 10, "weight": "bold"}
+matplotlib.rc("font", **font)
+
+import imp
+
+plot = imp.load_source("plot", "src/plot.py")
+
+df = pd.read_csv("data/merged_3_processed.csv")
+clustering_on = ["Normalized_Rank", "Median_score"]
+
+features = [
+    "CC_to_C_rate",
+    "CD_to_C_rate",
+    "DC_to_C_rate",
+    "DD_to_C_rate",
+    "SSE",
+    "Makes_use_of_game",
+    "Makes_use_of_length",
+    "Stochastic",
+    "Cooperation_rating",
+    "Cooperation_rating_max",
+    "Cooperation_rating_min",
+    "Cooperation_rating_median",
+    "Cooperation_rating_mean",
+    "Cooperation_rating_comp_to_max",
+    "Cooperation_rating_comp_to_min",
+    "Cooperation_rating_comp_to_median",
+    "Cooperation_rating_comp_to_mean",
+    "size",
+    "turns",
+    "probend",
+    "noise",
+    "memory_usage",
+    "repetitions",
+]
+
+sort = [
+    "$CC$ to $C$ rate",
+    "$CD$ to $C$ rate",
+    "$C_r$",
+    "$C_r$ / $C_{max}$ ",
+    "$C_r$ / $C_{mean}$",
+    "$C_r$ / $C_{median}$",
+    "$C_{max}$",
+    "$C_{mean}$",
+    "$C_{median}$",
+    "$C_{min}$",
+    "$C_{min}$ / $C_r$",
+    "$DC$ to $C$ rate",
+    "$DD$ to $C$ rate",
+    "$N$",
+    "$k$",
+    "$n$",
+    "$p_e$",
+    "$p_n$",
+    "Make use of game",
+    "Make use of length",
+    "SSE",
+    "memory usage",
+    "stochastic",
+]
+
+corr_data = df[features + clustering_on].corr()
+table = corr_data[clustering_on].iloc[:-2].round(3)
+table.index = [plot.features_labels[index] for index in table.index]
+
+textfile = open("correlation_table_merged.tex", "w")
+textfile.write(
+    table.reindex(sort)
+    .to_latex()
+    .replace("\$", "$")
+    .replace("\_", "_")
+    .replace("\{", "{")
+    .replace("\}", "}")
+)
+textfile.close()
+
[…]

### 2020-04-15 src/submit_meta_workers.sh
remove any pbs files
Add documentation on running the main script with pbs files

@@ -1,20 +1,0 @@
-qsub pbs/0-999.pbs 
-qsub pbs/1000-1999.pbs 
-qsub pbs/2000-2999.pbs 
-qsub pbs/3000-3999.pbs 
-qsub pbs/4000-4999.pbs 
-qsub pbs/5000-5999.pbs 
-qsub pbs/6000-6999.pbs 
-qsub pbs/7000-7999.pbs 
-qsub pbs/8000-8999.pbs 
-qsub pbs/9000-9999.pbs 
-qsub pbs/10000-10999.pbs 
-qsub pbs/11000-21999.pbs 
-qsub pbs/12000-12999.pbs 
-qsub pbs/13000-13999.pbs 
-qsub pbs/14000-14999.pbs 
-qsub pbs/15000-15999.pbs 
-qsub pbs/16000-16999.pbs 
-qsub pbs/17000-17999.pbs 
-qsub pbs/18000-18999.pbs 
-qsub pbs/19000-19999.pbs

### 2020-04-15 src/tools.py
remove tools.py

@@ -1,77 +1,0 @@
-import matplotlib.pyplot as plt
-import seaborn as sns
-import numpy as np
-
-c = sns.xkcd_rgb["denim blue"]
-
-
-def violin_plot(df, x, y, xlabel, ylabel, title, size=10):
-    join_plot = sns.jointplot(x=x, y=y, data=df,
-                              kind="reg", stat_func=None, xlim=(0, 1),
-                              ylim=(0, 1), scatter_kws={"s": size})
-
-    plt.subplots_adjust(top=0.95)
-    join_plot.fig.suptitle(title)
-    join_plot.set_axis_labels(xlabel, ylabel)
-
-    plt.show()
-    return join_plot
-
-
-def r_distribution(x, y1, y2, y3, y4, title, label1='max', label2='min',
-                   label3='mean', label4='median'):
-    rs = np.linspace(0, 1, 20)
-    fig, axes = plt.subplots(figsize=(6, 5))
-    axes.set_title(title)
-    axes.set_xlabel(r'$r$')
-    colormap = plt.cm.CMRmap
-    plt.gca().set_color_cycle([colormap(i) for i in np.linspace(0, 0.9, 4)])
-    plt.plot(rs,
-             [sum(x >= r * y1) / len(x) for r in
-              rs],
-             label=label1)
-    plt.plot(rs,
-             [sum(x >= r * y2) / len(x) for r in
-              rs],
-             label=label2)
-    plt.plot(rs,
-             [sum(x >= r * y3) / len(x) for r in
-              rs],
-             label=label3)
-    plt.plot(rs,
-             [sum(x >= r * y4) / len(x) for r in
-              rs],
-             label=label4)
-    plt.legend(loc=3)
-
-
-def r_distribution_mult_types(x1, x2, x3, x4, y1, y2, y3, y4, title,
-                              label1='standard', label2='noisy',
-                              label3='probend', label4='noisy + probend',
-                              filename='fig.pdf'):
-    rs = np.linspace(0, 1, 20)
-    fig, axes = plt.subplots(figsize=(6, 5))
-    axes.set_title(title)
-    axes.set_xlabel(r'$r$')
-    colormap = plt.cm.CMRmap
-    plt.gca().set_color_cycle([colormap(i) for i in np.linspace(0, 0.9, 4)])
-    plt.plot(rs,
-             [sum(x1 >= r * y1) / len(x1) for r in
-              rs],
-             label=label1)
-    plt.plot(rs,
[…]

### 2020-04-15 paper/main.tex
Make copy edits and add some TODO tags.
One of the TODO tags is about a particular paragraph that I really
struggle with. If I'm alone in not liking the paragraph then I'm happy
for it to be left as it is (I'm not
entirely sure I could offer my own version of it as I'm not sure I
understand it).

@@
 however, rely on performance against a small number of somewhat arbitrarily selected
-strategies in a very small number of tournaments, casting doubt on the generalizability
-of conclusions. We analyze a large collection of \numberofstrategies typically known
+strategies in a small number of tournaments, casting doubt on the generalizability
+of conclusions. We analyze a large collection of \numberofstrategies
 strategies in \numberofalltournaments tournaments, present the top performing strategies across multiple
@@
 strategies, refining the properties described by R. Axelrod in light of
-recent and more diverse opponent populations. These are: be nice, be provocable and forgiving,
-be a little envious, be clever, and adapt to the environment, which includes the parameters
-of the tournament (e.g. noise) and the population of opponents. More precisely,
+recent and more diverse opponent populations. These are: be nice, be provocable and forgiving,  % TODO modify this based on discussion about vocabulary.
+be a little envious, be clever, and adapt to the environment. More precisely,
 we find that strategies perform best when their probability of cooperation
@@
 players, simultaneously and independently, decide between cooperation (C) and
-defection (D), given memory of their prior interactions. The payoffs for each
+defection (D), given memory of all prior interactions. The payoffs for each
 player, at each turn, is influenced by their own choice and the choice of the
@@
 strategies. Many tournaments have followed Axelrod's~\cite{Bendor1991, Beaufils1997, Stephens2002,
-Kendall2007, Stewart2012, Harper2017} and today more hundreds of strategies exist
+Kendall2007, Stewart2012, Harper2017} and today more hundreds of strategies exist  % TODO Order these citations
 in the literature.
@@
 The winner of both of R. Axelrod's tournaments~\cite{Axelrod1980a, Axelrod1980b}
-was the simple strategy Tit For Tat (TFT) which cooperates
+was the simple strategy Tit For Tat (TFT) which cooperates  % TODO In the appendix we referr to TFT as TfT, we need to be consistent throughout.
 on the first turn and thereafter copies the previous action of its opponent,
@@
     \item Do not be envious by striving for a payoff larger than the opponent's payoff
-    \item Be "nice"; Do not be the first to defect
+    \item Be ``nice''; Do not be the first to defect
     \item Reciprocate both cooperation and defection; Be provocable to retaliation and forgiveness
@@
 is understandable given the effort required to implement the hundreds of published IPD strategies
-\footnote{Implementing prior strategies faithfully is often extremely difficult or impossible due to insufficient descriptions and lack of published implementations or code.}, 
-yet calls into question any claims of superiority or robustness of newly introduced strategies.
+Implementing prior strategies faithfully is often extremely difficult or
+impossible due to insufficient descriptions and lack of published
+implementations or code.
+This calls into question any claims of superiority or robustness of newly introduced strategies.
 
@@
 reinforcement learning were introduced, and a tournament containing over 200 strategies
-featured no ZDs ranked in top spots. Instead, the top ranked strategies
+featured no ZDs ranking in top spots. Instead, the top ranked strategies
 were a set of ``clever'' (in the sense of R. Axelrod's characteristics) trained
@@
 Though only select pieces of work have been discussed, there is a broad collection
-of strategies in the literature, and new strategies and competitions are being
+of strategies in the literature, and new strategies and competitions are
 published frequently~\cite{Glynatsi2019}. The question, however, still remains
@@
 strategies in \numberofalltournaments tournaments. Furthermore a large portion
-of the strategies used in this manuscript are drawn from the known and named strategies
+of the strategies used in this manuscript are drawn from known and named strategies
 in IPD literature, including many previous tournament winners,
@@
 features include measures regarding a strategy's behaviour and measures regarding
-the tournaments. The outcomes of our work reinforce the discussion started by R. Axelrod
+the tournaments. This rigorous analysis reinforces the discussion started by R. Axelrod
 and concludes that the properties of a successful strategy in the IPD are:
@@
     \item \st{Do not be envious} Be a little bit envious
-    \item Be "nice" in non-noisy environments or when game lengths are longer
-    \item Reciprocate both cooperation and defection; Be provocable and forgiving
+    \item Be ``nice'' in non-noisy environments or when game lengths are longer
+    \item Reciprocate both cooperation and defection; Be provocable and forgiving  % TODO Modify this following decision on vocabulary
     \item \st{Do not be too clever} It's ok to be clever
@@
 possible due to an open source library called Axelrod-Python (APL),
-are covered in Section~\ref{section:data_collection}. The data set generated
+are covered in Section~\ref{section:data_collection}. The data set generated  % TODO Modify this when the raw as well as the processed data is archived
 for this work has been made publicly available~\cite{data} and can be used
@@
 list of the strategies is given in the Appendix~\ref{app:list_of_players}.
-Although APL features several tournament types, this work considers
+APL features several tournament types, this work considers
 standard, noisy, probabilistic ending, and noisy probabilistic ending
@@
 in order to evaluate the effect of smoothing. The winner of each tournament
-is based on the average score a strategy achieved and not by the number of wins.
+is based on the median score a strategy achieved and not by the number of wins.
 
@@
 following best practices~\cite{Aberdour2007, Benureau2018}
-and is available here. %TODO archive code
+and is available here. %TODO archive code and include github url as well.
 
@@
 retrieved. Each tournament outputs a result summary in the form of
-Table~\ref{table:output_result}. Each strategy have participated on average in
+Table~\ref{table:output_result}. Each strategy has participated on average in
 5154 tournaments of each type. The strategy with the maximum participation in each
@@
 
-A result summary (Table~\ref{table:output_result}) has \(N\) number of rows
+A result summary (Table~\ref{table:output_result}) has \(N\) rows
 because each row contains information for each strategy that participated in the
@@
 and the rate of which the strategy cooperated after each state. The \textbf{normalised rank}
-feature that is manually added. The rank \(R\) of a given. % TODO Clarify how strategies are ranked (see email discussion)
-strategy can vary between 0 and \(N-1\). Thus, the normalised rank,
+feature that is manually added. The rank \(R\) of a given.
+strategy can vary between 0 (first) and \(N-1\) (last). Thus, the normalised rank,
 denoted as $r$, is calculated as a strategy's rank divided by \(N - 1\).
@@
 
-The performance of each strategy is evaluated in four tournament types, as
+The performance of each strategy is evaluated in the four tournament types
 presented in Section \ref{section:data_collection}, followed by an
@@
 value of \(r = 1\) corresponds to the strategy coming last. Because of the
-strategies' multiple entries their performance is evaluated based on the
+strategies' multiple entries their overall performance is evaluated based on the
 \textbf{median normalised rank} denoted as \(\bar{r}\).
@@
     \centering
-    \includegraphics[width=.60\textwidth]{../images/tit_for_tat_r_distributions.pdf}
+    \includegraphics[width=.8\textwidth]{../images/tit_for_tat_r_distributions.pdf}
     \caption{TFT's $r$ distribution in tournaments. Lower values of \(r\)
@@
 \caption{Top performances for each tournament type based on $\bar{r}$. The
-results of each type are based on 11420 unique tournaments of each type. The
+results of each type are based on 11420 unique tournaments. The
 results for noisy tournaments with \(p_n < 0.1\) are based on 1151 tournaments,
@@
 are close to 0 for most environments, except environments with noise not
-restricted to 0.1 regardless the number of turns. Noisy and noisy probabilistic
-ending tournaments have the highest medians. This implies that strategies from
-the collection of this work do not perform well in environments with high values
-of noise.}
+restricted to 0.1 regardless of the number of turns. Noisy and noisy probabilistic
+ending tournaments have the highest medians.}
 \label{table:top_performances}
@@
 
-In standard tournaments 10 out of the 15 top strategies are introduced
+In standard tournaments 10 out of the 15 top strategies were introduced
 in~\cite{Harper2017}. These are strategies based on finite state automata (FSM),
@@
 in APL in a standard tournament, thus their performance in the
-specific setting was anticipated. DoubleCrosser, BackStabber and Fool Me Once, are
+specific setting was anticipated although still noteworthy given the random
+sampling of tournament participants. DoubleCrosser, BackStabber and Fool Me Once, are
 strategies not from the literature but from the APL. DoubleCrosser is an extension
@@
 
-In the case of noisy tournaments with smaller noise \(p_n < 0.1\) the top performed strategies
+In the case of noisy tournaments with smaller noise \(p_n < 0.1\) the top
+performing strategies
 include strategies specifically designed for noisy tournaments. These are DBS,
@@
 deterministic strategies such as Spiteful Tit For Tat~\cite{prison}, Level
-Punisher~\cite{Eckhart2015}, Eugine Nier~\cite{lesswrong}. Similarly to standard
-tournaments, the successful strategies in this given setting performed well
-overall the tournaments they participated in (see Figure~\ref{fig:noise_subset_results}).
+Punisher~\cite{Eckhart2015}, Eugine Nier~\cite{lesswrong}.
 
@@
 were highly ranked due to the their performance in tournaments with \(p_n>0.5\),
-and that in tournaments with a noise probability lower than \(0.5\) they
+and that in tournaments with \(p_n<0.5\) they
 performed poorly. At a noisy level of \(0.5\) or greater, mostly cooperative strategies
@@
 
-The new entrants to the most effective strategies list in probabilistic ending
-tournaments with \(p_e< 0.1\) are a series of ensembled Meta strategies, trained strategies
+The most effective strategies in probabilistic ending
+tournaments with \(p_e< 0.1\) are a series of ensemble Meta strategies, trained strategies
 which performed well
@@
 in various ways. Figure~\ref{fig:probend_subset_results} indicates that these strategies
-performed well in any probabilistic ending tournament they competed in.
+performed well in any probabilistic ending tournament.
 
@@
 \(\bar{r}\) for the top strategy is approximately at 0.3, indicating that the
-most successful strategy can on average just place at the top 30\% of the
+most successful strategy can on average just place in the top 30\% of the
 competition.
@@
 
-For each strategy we have a variety of features, described in
+For each strategy, for each tournament we have a variety of features, described in
 Table~\ref{table:manual_features}. These features are measures regarding a
@@
 \end{center}
-\caption{Correlations table between the features of Table~\ref{table:manual_features}
-the normalised rank and the median score.}\label{table:correlations}
+\caption{Correlations between the features of Table~\ref{table:manual_features}
+and the normalised rank and the median score.}\label{table:correlations}
 \end{table}
@@
 and the cooperating ratio compared to $C_{\text{median}}$ and $C_{\text{mean}}$
-have a moderate negative effect on the normalised rank (smaller rank is better), and a moderate positive
-on the median score. The SSE error and the $DD$ to $C$ have the opposite
+have a moderately negative effect on the normalised rank (smaller rank is better), and a moderate positive
+on the median score. The SSE error and the $DD$ to $C$ rate have the opposite
 effects. Thus, in standard tournaments behaving cooperatively corresponds to a
@@
     \centering
-    \includegraphics[width=.57\textwidth]{../images/rates_of_winners_in_standard_tournaments.pdf}
+    \includegraphics[width=.8\textwidth]{../images/rates_of_winners_in_standard_tournaments.pdf}
     \caption{Distributions of $CC$ to $C$ and $DD$ to $C$ for the winners in
@@
 relative to the tournament population average is important. Playing a strategy
-that randomly cooperates with $C_{\text{mean}}$ is unlikely to be as effective as it will
+that randomly cooperates with probability $C_{\text{mean}}$ is unlikely to be as effective as it will
 randomly have cooperations matched with defections, and it may be punished for
@@
 (cooperating while the opponent defects), at least in non-noisy tournaments.
-\footnote{This also explains why Tit For N Tats does not fare well for $N > 1$ -- it fails
-to achieve the proper cooperation ratio by tolerating too many defections.}
+This also explains why Tit For N Tats does not fare well for $N > 1$ as it fails
+to achieve the proper cooperation ratio by tolerating too many defections.
 TFT forces the opponent to pay back the \((C, D)\) round with a \((D, C)\) round before
@@
 are present, reducing the overall value in attempting to exploit strategies like Cooperator.
+% TODO Both NG and MH seem happy with this paragraph but I find it quite a
+% mouthful and not very too the point (took me a few reads). If you're both
+% happy with it that's fine with me but can we just be sure.
 
@@
     \centering
-    \includegraphics[width=.57\textwidth]{../images/c_r_winners_tournaments.pdf}
+    \includegraphics[width=.8\textwidth]{../images/c_r_winners_tournaments.pdf}
     \caption{$C_r$ distributions of the winners in noisy and in probabilistic
@@
 original suggested features of good IPD strategies. Moreover, our results
-shed light on the historic performance of TFT, zero-determinant strategies,
+shed light on the historic performance of TFT, ZDs,
 and memory-one strategies generally. Strategies need to match their play
@@
 tournaments across tournament types, hinting that successful IPD strategies are
-often clever or more complex than simple strategies like TFT. Most of the
+often clever or more complex than simple strategies like TFT or ZDs. Most of the
 successful strategies highlighted
@@
     \item be a little envious,
-    \item it's ok to be clever,
+    \item be clever,
     \item adapt to the environment (including the population of strategies).
@@
 The data set described in this work contains the largest number of IPD tournaments,
-to the authors knowledge, and it available at~\cite{data}. Further data mining
+to the authors knowledge, and it available at~\cite{data}. Further data mining % TODO Modify this when the raw data is also archived
 could be applied and provide new insights in the field.

### 2020-04-15 tests/test_read_in.py
move test_read_in and transfer to pytests

@@ -1,0 +1,188 @@
+import imp
+import unittest
+
+import axelrod
+import numpy
+import pandas
+
+read_in = imp.load_source("read_in", "src/read_in.py")
+
+df = read_in.strategies_properties()
+
+
+def test_strategies_properties():
+    assert isinstance(df, pandas.DataFrame)
+    assert len(df) == len(axelrod.strategies)
+
+    for memory_depth in df["Memory_depth"]:
+        assert isinstance(memory_depth, float)
+
+    for use_of_game in df["Makes_use_of_game"]:
+        assert isinstance(use_of_game, bool)
+
+    for use_of_length in df["Makes_use_of_length"]:
+        assert isinstance(use_of_length, bool)
+
+
+def test_specific_strategy_properties():
+
+    tit_for_tat = df[df["Name"] == "Tit For Tat"]
+    assert tit_for_tat.Name.all() == "Tit For Tat"
+    assert tit_for_tat.Memory_depth.values == 1.0
+    assert tit_for_tat.Stochastic.values == False
+    assert tit_for_tat.Makes_use_of_game.values == 0.0
+    assert tit_for_tat.Makes_use_of_length.values == 0.0
+
+    adaptive = df[df["Name"] == "Adaptive"]
+    assert adaptive.Name.all() == "Adaptive"
+    assert adaptive.Memory_depth.values == numpy.inf
+    assert adaptive.Stochastic.values == False
+    assert adaptive.Makes_use_of_game.values == 1.0
+    assert adaptive.Makes_use_of_length.values == 0.0
+
+
+def test_parameters_data_frame():
+    parameters_df = read_in.parameters_data_frame("data/raw_data/")
+
+    assert isinstance(parameters_df, pandas.DataFrame)
+    assert all(
+        parameters_df.columns.values
+        == ["index", "noise", "probend", "repetitions", "seed", "size", "turns"]
+    )
+
+
+parameters_df = read_in.parameters_data_frame("data/raw_data/")
+row = parameters_df.sample(n=1)
+reader = read_in.Reader(row, "data/raw_data/")
+
+
+def test_reader_init():
+    assert reader.noise_param.values[0] == row.noise.values[0]
+    assert reader.probend_param.values[0] == row.probend.values[0]
+    assert reader.seed.values[0] == row.seed.values[0]
+    assert reader.size.values[0] == row["size"].values[0]
+    assert reader.turns_param.values[0] == row.turns.values[0]
+
+
+def test_get_noise_df():
+    noise = reader.get_noise_df()
[…]

### 2020-04-15 src/read_in.py
remove read_in script as it is a duplicate of prepare data

@@ -1,130 +1,0 @@
-import pandas as pd
-import glob
-import axelrod as axl
-
-
-def strategies_properties():
-    """
-     A function that returns a data frame with the strategies of the Axelrod
-     library and for each strategy it's property.
-    """
-    axl_strategies = pd.DataFrame(columns=['Name', 'Stochastic',
-                                           'Memory_depth', 'Makes_use_of_game',
-                                           'Makes_use_of_length'])
-
-    for i, strategy in enumerate(axl.strategies):
-        use_of_game = False
-        use_of_length = False
-
-        if 'game' in strategy().classifier['makes_use_of']:
-            use_of_game = True
-        if 'length' in strategy().classifier['makes_use_of']:
-            use_of_length = True
-        axl_strategies.loc[i] = [strategy().name,
-                                 strategy().classifier['stochastic'],
-                                 strategy().classifier['memory_depth'],
-                                 use_of_game,
-                                 use_of_length]
-    return axl_strategies
-
-
-def parameters_data_frame(directory):
-    """
-    A function for reading in the parameters data frame.
-    """
-    csv_files = glob.glob("{}parameters_*-*.csv".format(directory))
-    dfs = (pd.read_csv(f) for f in csv_files)
-    df = pd.concat(dfs)
-    df = df[['noise', 'probend', 'repetitions', 'seed', 'size', 'turns']]
-
-    return df.sort_values(['seed']).reset_index()
-
-
-class Reader():
-    """
-    A class for retrieving the four data frames corresponding to each
-    row of the parameters csv file.
-    """
-
-    def __init__(self, row, directory):
-        if directory:
-            self.directory = directory
-        else:
-            self.directory = "../data/"
-        self.seed = row.seed
-        self.size = row['size']
-        self.repetitions = row.repetitions
-        self.noise_param = row.noise
-        self.probend_param = row.probend
-        self.turns_param = row.turns
-
-    def get_noise_df(self):
-        noise = pd.read_csv('{}noise-data/{}.csv'.format(self.directory,
-                                                         int(self.seed)))
-        noise['noise'] = self.noise_param
-        noise['turns'] = self.turns_param
-
-        return noise
-
-    def get_probend_noise_df(self):
-        probend_noise = pd.read_csv('{}noise-probend-data/{}.csv'.format(
-                                                self.directory, int(self.seed)))
-        probend_noise['noise'] = self.noise_param
-        probend_noise['probend'] = self.probend_param
[…]

### 2020-04-15 tests/test_read_in.py

@@ -1,188 +1,0 @@
-import imp
-import unittest
-
-import axelrod
-import numpy
-import pandas
-
-read_in = imp.load_source("read_in", "src/read_in.py")
-
-df = read_in.strategies_properties()
-
-
-def test_strategies_properties():
-    assert isinstance(df, pandas.DataFrame)
-    assert len(df) == len(axelrod.strategies)
-
-    for memory_depth in df["Memory_depth"]:
-        assert isinstance(memory_depth, float)
-
-    for use_of_game in df["Makes_use_of_game"]:
-        assert isinstance(use_of_game, bool)
-
-    for use_of_length in df["Makes_use_of_length"]:
-        assert isinstance(use_of_length, bool)
-
-
-def test_specific_strategy_properties():
-
-    tit_for_tat = df[df["Name"] == "Tit For Tat"]
-    assert tit_for_tat.Name.all() == "Tit For Tat"
-    assert tit_for_tat.Memory_depth.values == 1.0
-    assert tit_for_tat.Stochastic.values == False
-    assert tit_for_tat.Makes_use_of_game.values == 0.0
-    assert tit_for_tat.Makes_use_of_length.values == 0.0
-
-    adaptive = df[df["Name"] == "Adaptive"]
-    assert adaptive.Name.all() == "Adaptive"
-    assert adaptive.Memory_depth.values == numpy.inf
-    assert adaptive.Stochastic.values == False
-    assert adaptive.Makes_use_of_game.values == 1.0
-    assert adaptive.Makes_use_of_length.values == 0.0
-
-
-def test_parameters_data_frame():
-    parameters_df = read_in.parameters_data_frame("data/raw_data/")
-
-    assert isinstance(parameters_df, pandas.DataFrame)
-    assert all(
-        parameters_df.columns.values
-        == ["index", "noise", "probend", "repetitions", "seed", "size", "turns"]
-    )
-
-
-parameters_df = read_in.parameters_data_frame("data/raw_data/")
-row = parameters_df.sample(n=1)
-reader = read_in.Reader(row, "data/raw_data/")
-
-
-def test_reader_init():
-    assert reader.noise_param.values[0] == row.noise.values[0]
-    assert reader.probend_param.values[0] == row.probend.values[0]
-    assert reader.seed.values[0] == row.seed.values[0]
-    assert reader.size.values[0] == row["size"].values[0]
-    assert reader.turns_param.values[0] == row.turns.values[0]
-
-
-def test_get_noise_df():
-    noise = reader.get_noise_df()
[…]

### 2020-04-15 tasks.py
adds invoke for tests

@@ -1,0 +1,8 @@
+from invoke import task
+
+@task
+def test(c):
+    """
+    Test all packaged code and notebooks
+    """
+    c.run("pytest tests")

### 2020-04-15 tasks.py
add tasks for downloading data, unpacking and processing

@@ -1,6 +1,61 @@
 from invoke import task
 
 @task
+def unpack(c):
+    """
+    Unpack downloaded `tar.gz` file
+    """
+    c.run("tar -xzf raw_data.tar.gz --directory data")
+
+
+@task
+def get(c):
+    """
+    Download the data from the online archive
+    """
+    c.run(
+        "wget https://zenodo.org/record/3753498/files/raw_data.tar.gz?download=1 -O raw_data.tar.gz"
+    )
+
+
+@task
+def data(c):
+    """
+    Download and unpack data from online archive
+    """
+    print("Downloading data")
+    get(c)
+    print("Unpacking data")
+    unpack(c)
+
+
+@task
+def process(c):
+    """
+    Process raw data
+    """
+    print("Prepare raw data")
+    c.run("python src/prepare_data.py data/raw_data/ all 3")
+
+    for data_type in ['standard', 'noise', 'probend', 'probend_noise']:
+        print(f"Process {data_type} data set")
+        c.run(f"python src/process_data.py data/{data_type}_3.csv")
+
+
+@task
+def prodata(c):
+    """
+    Download and unpack data from online archive
+    """
+    print("Downloading processed data")
+    c.run(
+        "wget https://zenodo.org/record/3753565/files/data.tar.gz?download=1 -O data.tar.gz"
+    )
+    print("Unpacking data")
+    c.run("tar -xzf data.tar.gz")
+
+
+@task
 def test(c):
     """
     Test all packaged code and notebooks

### 2020-04-15 tasks.py
add information for the merged data set analysis

@@ -61,3 +61,8 @@ def test(c):
     Test all packaged code and notebooks
     """
     c.run("pytest tests")
+
+
+@task
+def merge(c):
+    c.run("cat src/*_3_processed.csv > src/merged_3_processed.csv")

### 2020-04-15 src/correlation.py
update readme with analysis of merged data set

@@ -1,3 +1,5 @@
+"""A script for running the correlation analysis on the marged data set."""
+
 import matplotlib
 import matplotlib.pyplot as plt
 import pandas as pd
@@ -69,7 +71,7 @@ corr_data = df[features + clustering_on].corr()
 table = corr_data[clustering_on].iloc[:-2].round(3)
 table.index = [plot.features_labels[index] for index in table.index]
 
-textfile = open("correlation_table_merged.tex", "w")
+textfile = open("paper/correlation_table_merged.tex", "w")
 textfile.write(
     table.reindex(sort)
     .to_latex()
@@ -94,4 +96,4 @@ plt.figure(figsize=(20, 15))
 
 sns.heatmap(data, annot=True, cmap="viridis")
 
-plt.savefig("merged_correlation_plot.pdf", bbox_inches="tight")
+plt.savefig("images/merged_correlation_plot.pdf", bbox_inches="tight")

### 2020-04-15 src/regression.py

@@ -1,0 +1,36 @@
+"""A script for running the regression analysis on the marged data set."""
+import imp
+
+import pandas as pd
+import statsmodels.api as sm
+
+plot = imp.load_source("plot", "src/plot.py")
+
+df =  pd.read_csv('data/merged_3_processed.csv')
+
+features = [
+    "CC_to_C_rate",
+    "CD_to_C_rate",
+    "DC_to_C_rate",
+    "SSE",
+    "Cooperation_rating_comp_to_min",
+    "Cooperation_rating_comp_to_mean",
+]
+
+xs = features.copy()
+X = df[xs].values
+y = df['Median_score'].values
+
+X = sm.add_constant(X)
+model = sm.OLS(y, X).fit()
+
+table = model.summary2(xname=['constant'] +xs)
+rs = table.tables[0][2][0] + table.tables[0][3][0]
+table = table.tables[1][['Coef.', 'P>|t|']].round(5)
+table.index = ['constant'] + [plot.features_labels[index] for index in table.index[1:]]
+
+file = open('paper/regression_merged_result_on_median_score.tex', "w")
+file.write(table.round(3).to_latex().replace('\$', '$').replace('\_', ('_')))
+file.close()
+
+print(rs)

### 2020-04-15 paper/perfomances_table.tex
checks that notebooks run

--- 2020-01-28 paper/perfomances_table.tex
@@
-\begin{tabular}{lllllllll}
+\begin{tabular}{lllllllllllll}
 \toprule
-{} &                     Name & \$\textbackslash bar\{r\}\$ &                   Name & \$\textbackslash bar\{r\}\$ &               Name & \$\textbackslash bar\{r\}\$ &                 Name & \$\textbackslash bar\{r\}\$ \\
+{} &                     Name & \$\textbackslash bar\{r\}\$ &                   Name & \$\textbackslash bar\{r\}\$ &                        Name & \$\textbackslash bar\{r\}\$ &               Name & \$\textbackslash bar\{r\}\$ &                       Name & \$\textbackslash bar\{r\}\$ &                 Name & \$\textbackslash bar\{r\}\$ \\
 \midrule
-0  &            Evolved HMM 5 &   0.00667 &                 Grumpy &    0.1402 &          Fortress4 &   0.01266 &           Alternator &    0.3037 \\
-1  &           Evolved FSM 16 &   0.00995 &                    \$e\$ &   0.19388 &           Defector &   0.01429 &               \$\textbackslash phi\$ &   0.30978 \\
-2  &     EvolvedLookerUp2\_2\_2 &   0.01064 &         Tit For 2 Tats &   0.20617 &  Better and Better &   0.01587 &                  \$e\$ &    0.3125 \\
-3  &  Evolved FSM 16 Noise 05 &   0.01667 &  Slow Tit For Two Tats &   0.20962 &    Tricky Defector &   0.01875 &                \$\textbackslash pi\$ &   0.31686 \\
-4  &        PSO Gambler 2\_2\_2 &   0.02143 &           Cycle Hunter &   0.21538 &          Fortress3 &   0.02174 &    Limited Retaliate &   0.35263 \\
-5  &              Evolved ANN &   0.02878 &         Risky QLearner &   0.22222 &     Gradual Killer &   0.02532 &     Anti Tit For Tat &   0.35431 \\
-6  &            Evolved ANN 5 &    0.0339 &            Retaliate 3 &   0.22887 &         Aggravater &   0.02778 &          Retaliate 3 &   0.35563 \\
-7  &        PSO Gambler 1\_1\_1 &   0.03704 &          Cycler CCCCCD &   0.23507 &             Raider &   0.03077 &  Limited Retaliate 3 &   0.35563 \\
-8  &            Evolved FSM 4 &   0.04891 &            Retaliate 2 &   0.23913 &         Cycler DDC &   0.04545 &            Retaliate &   0.35714 \\
-9  &         PSO Gambler Mem1 &   0.05036 &        Defector Hunter &   0.24038 &        Hard Prober &   0.05128 &          Retaliate 2 &   0.35767 \\
-10 &                 Winner12 &   0.06011 &              Retaliate &   0.24177 &         SolutionB1 &   0.06024 &  Limited Retaliate 2 &   0.36134 \\
-11 &             Fool Me Once &    0.0614 &    Hard Tit For 2 Tats &      0.25 &      Meta Minority &   0.06077 &             Hopeless &   0.36842 \\
-12 &                      DBS &   0.07143 &               ShortMem &   0.25286 &              Bully &   0.06081 &    Arrogant QLearner &   0.40651 \\
-13 &            DoubleCrosser &     0.072 &    Limited Retaliate 3 &   0.25316 &    Fool Me Forever &    0.0708 &    Cautious QLearner &   0.40909 \\
-14 &              BackStabber &   0.07519 &      Limited Retaliate &   0.25706 &             EasyGo &   0.07101 &      Fool Me Forever &   0.41764 \\
+0  &            Evolved HMM 5 &     0.007 &                 Grumpy &      0.14 &                         DBS &         0 &          Fortress4 &     0.013 &             Evolved FSM 16 &         0 &           Alternator &     0.304 \\
+1  &           Evolved FSM 16 &      0.01 &                    \$e\$ &      0.19 &     Evolved FSM 16 Noise 05 &     0.008 &           Defector &     0.014 &    Evolved FSM 16 Noise 05 &     0.013 &               \$\textbackslash phi\$ &      0.31 \\
+2  &     EvolvedLookerUp2\_2\_2 &     0.011 &         Tit For 2 Tats &     0.206 &      Evolved ANN 5 Noise 05 &     0.013 &  Better and Better &     0.016 &                       MEM2 &     0.027 &                  \$e\$ &     0.312 \\
+3  &  Evolved FSM 16 Noise 05 &     0.017 &  Slow Tit For Two Tats &      0.21 &                 BackStabber &     0.024 &    Tricky Defector &     0.019 &              Evolved HMM 5 &     0.043 &                \$\textbackslash pi\$ &     0.317 \\
+4  &        PSO Gambler 2\_2\_2 &     0.022 &           Cycle Hunter &     0.215 &               DoubleCrosser &     0.025 &          Fortress3 &     0.022 &       EvolvedLookerUp2\_2\_2 &     0.049 &    Limited Retaliate &     0.353 \\
+5  &              Evolved ANN &     0.029 &         Risky QLearner &     0.222 &               Evolved ANN 5 &     0.028 &     Gradual Killer &     0.025 &       Spiteful Tit For Tat &     0.059 &     Anti Tit For Tat &     0.354 \\
+6  &            Evolved ANN 5 &     0.034 &          Cycler CCCCCD &     0.229 &                 Evolved ANN &     0.038 &         Aggravater &     0.028 &           Nice Meta Winner &     0.069 &  Limited Retaliate 3 &     0.356 \\
+7  &        PSO Gambler 1\_1\_1 &     0.037 &            Retaliate 3 &      0.23 &        Spiteful Tit For Tat &     0.051 &             Raider &     0.031 &         NMWE Finite Memory &     0.069 &          Retaliate 3 &     0.356 \\
+8  &            Evolved FSM 4 &     0.049 &            Retaliate 2 &     0.239 &               Evolved HMM 5 &     0.051 &         Cycler DDC &     0.045 &         NMWE Deterministic &      0.07 &            Retaliate &     0.357 \\
+9  &         PSO Gambler Mem1 &      0.05 &        Defector Hunter &      0.24 &              Level Punisher &     0.052 &        Hard Prober &     0.051 &                    Grudger &      0.07 &          Retaliate 2 &     0.358 \\
+10 &                 Winner12 &      0.06 &              Retaliate &     0.242 &                   Omega TFT &     0.059 &         SolutionB1 &      0.06 &           NMWE Long Memory &     0.074 &  Limited Retaliate 2 &     0.361 \\
+11 &             Fool Me Once &     0.061 &    Hard Tit For 2 Tats &      0.25 &                Fool Me Once &     0.059 &      Meta Minority &     0.061 &  Nice Meta Winner Ensemble &     0.076 &             Hopeless &     0.368 \\
+12 &                      DBS &     0.071 &      Arrogant QLearner &      0.25 &  PSO Gambler 2\_2\_2 Noise 05 &     0.067 &              Bully &     0.061 &       EvolvedLookerUp1\_1\_1 &     0.077 &    Arrogant QLearner &     0.406 \\
+13 &            DoubleCrosser &     0.072 &    Limited Retaliate 3 &     0.253 &              Evolved FSM 16 &     0.078 &             EasyGo &     0.071 &            NMWE Memory One &      0.08 &    Cautious QLearner &     0.409 \\
+14 &              BackStabber &     0.075 &               ShortMem &     0.253 &                  EugineNier &      0.08 &    Fool Me Forever &     0.071 &            NMWE Stochastic &     0.085 &      Fool Me Forever &     0.418 \\
 \bottomrule

### 2020-04-16 tasks.py
point to data folder instead of src

@@ -65,4 +65,4 @@ def test(c):
 
 @task
 def merge(c):
-    c.run("cat src/*_3_processed.csv > src/merged_3_processed.csv")
+    c.run("cat data/*_3_processed.csv > data/merged_3_processed.csv")

### 2020-04-16 src/regression.py
correct path to scripts

@@ -33,4 +33,6 @@ file = open('paper/regression_merged_result_on_median_score.tex', "w")
 file.write(table.round(3).to_latex().replace('\$', '$').replace('\_', ('_')))
 file.close()
 
-print(rs)
+file = open('paper/r_square_merged_result_on_median_score.tex', "w")
+file.write(rs)
+file.close()

### 2020-04-16 tasks.py
revisit merged task

@@ -1,4 +1,5 @@
 from invoke import task
+import pandas as pd
 
 @task
 def unpack(c):
@@ -65,4 +66,11 @@ def test(c):
 
 @task
 def merge(c):
-    c.run("cat data/*_3_processed.csv > data/merged_3_processed.csv")
+    dfs = []
+    for name in ['standard', 'noise', 'probend', 'probend_noise']:
+        df = pd.read_csv(f'data/{name}_3_processed.csv')
+
+        dfs.append(df)
+    df = pd.concat(dfs)
+    df.reset_index(inplace=True)
+    df.to_csv('data/merged_3_processed.csv')

### 2020-04-16 src/main.py
Cleans repos and adds to documentation (#29)
* cleans and documents plot script

* remove any pbs related files

* add to environment yml and requirements.txt

* remove unused files

* adds invoke for tests

* add tasks for downloading data, unpacking and processing

* run notebooks and rename notebook

* add information for the merged data set analysis

* read through readme

@@ -29,7 +29,7 @@ number_of_parameter_sets = 20
 try:
     directory = sys.argv[1]
 except IndexError:
-    directory = "../data/"
+    directory = "data/"
 
 try:
     min_seed, max_seed = map(int, sys.argv[2:])

### 2020-04-16 src/pbs_file_generator.py

@@ -1,50 +1,0 @@
-import os
-
-directory_name = "pbs"
-
-try:
-    os.mkdir(directory_name)
-    print("Directory ", directory_name, " Created")
-except FileExistsError:
-    pass
-
-submit_script = ""
-for name, min_seed, max_seed in [
-    ("0-999", 0, 1000),
-    ("1000-1999", 1000, 2000),
-    ("2000-2999", 2000, 3000),
-    ("3000-3999", 3000, 4000),
-    ("4000-4999", 4000, 5000),
-    ("5000-5999", 5000, 6000),
-    ("6000-6999", 6000, 7000),
-    ("7000-7999", 7000, 8000),
-    ("8000-8999", 8000, 9000),
-    ("9000-9999", 9000, 10000),
-]:
-
-    pbs_file = """#!/bin/bash
-#PBS -q workq
-#PBS -N {}
-#PBS -P PR350
-#PBS -o axlml{}out.txt
-#PBS -e axlml{}err.txt
-#PBS -l select=1:ncpus=16:mpiprocs=16
-#PBS -l place=scatter:excl
-#PBS -l walltime=70:00:00
-
-export MPLBACKEND="agg"
-# Run std
-cd /home/c1569433/rsc/axlml/src
-/home/c1569433/anaconda3/envs/axlml/bin/python main.py /scratch/c1569433/axlml/data/ {} {} 
-""".format(
-        name, name, name, min_seed, max_seed
-    )
-
-    with open("pbs/{}.pbs".format(name), "w") as f:
-        f.write(pbs_file)
-
-    submit_script += "qsub pbs/{}.pbs \n".format(name)
-
-with open("submit_meta_workers.sh", "w") as f:
-    f.write(submit_script)
-    print("File submit_meta_workers.sh Created")

### 2020-04-16 src/plot.py

@@ -1,9 +1,4 @@
-import matplotlib.pyplot as plt
-import seaborn as sns
-import numpy as np
-
-c = sns.xkcd_rgb["denim blue"]
-
+"""Contains the features' labels. These are used for plotting."""
 
 features_labels = {
     "CC_to_C_rate": "$CC$ to $C$ rate",
@@ -32,79 +27,3 @@ features_labels = {
     "memory_usage": "memory usage",
     "repetitions": r"$k$",
 }
-
-
-def violin_plot(df, x, y, xlabel, ylabel, title, size=10):
-    join_plot = sns.jointplot(
-        x=x,
-        y=y,
-        data=df,
-        kind="reg",
-        stat_func=None,
-        xlim=(0, 1),
-        ylim=(0, 1),
-        scatter_kws={"s": size},
-    )
-
-    plt.subplots_adjust(top=0.95)
-    join_plot.fig.suptitle(title)
-    join_plot.set_axis_labels(xlabel, ylabel)
-
-    plt.show()
-    return join_plot
-
-
-def r_distribution(
-    x,
-    y1,
-    y2,
-    y3,
-    y4,
-    title,
-    label1="max",
-    label2="min",
-    label3="mean",
-    label4="median",
-):
-    rs = np.linspace(0, 1, 20)
-    fig, axes = plt.subplots(figsize=(6, 5))
-    axes.set_title(title)
-    axes.set_xlabel(r"$r$")
-    colormap = plt.cm.CMRmap
-    plt.gca().set_color_cycle([colormap(i) for i in np.linspace(0, 0.9, 4)])
-    plt.plot(rs, [sum(x >= r * y1) / len(x) for r in rs], label=label1)
-    plt.plot(rs, [sum(x >= r * y2) / len(x) for r in rs], label=label2)
-    plt.plot(rs, [sum(x >= r * y3) / len(x) for r in rs], label=label3)
-    plt.plot(rs, [sum(x >= r * y4) / len(x) for r in rs], label=label4)
-    plt.legend(loc=3)
-
-
-def r_distribution_mult_types(
-    x1,
-    x2,
-    x3,
-    x4,
-    y1,
-    y2,
-    y3,
-    y4,
-    title,
-    label1="standard",
-    label2="noisy",
-    label3="probend",
-    label4="noisy + probend",
-    filename="fig.pdf",
-):
-    rs = np.linspace(0, 1, 20)
[…]

### 2020-04-16 src/regression.py

@@ -1,0 +1,38 @@
+"""A script for running the regression analysis on the marged data set."""
+import imp
+
+import pandas as pd
+import statsmodels.api as sm
+
+plot = imp.load_source("plot", "src/plot.py")
+
+df =  pd.read_csv('data/merged_3_processed.csv')
+
+features = [
+    "CC_to_C_rate",
+    "CD_to_C_rate",
+    "DC_to_C_rate",
+    "SSE",
+    "Cooperation_rating_comp_to_min",
+    "Cooperation_rating_comp_to_mean",
+]
+
+xs = features.copy()
+X = df[xs].values
+y = df['Median_score'].values
+
+X = sm.add_constant(X)
+model = sm.OLS(y, X).fit()
+
+table = model.summary2(xname=['constant'] +xs)
+rs = table.tables[0][2][0] + table.tables[0][3][0]
+table = table.tables[1][['Coef.', 'P>|t|']].round(5)
+table.index = ['constant'] + [plot.features_labels[index] for index in table.index[1:]]
+
+file = open('paper/regression_merged_result_on_median_score.tex', "w")
+file.write(table.round(3).to_latex().replace('\$', '$').replace('\_', ('_')))
+file.close()
+
+file = open('paper/r_square_merged_result_on_median_score.tex', "w")
+file.write(rs)
+file.close()

### 2020-04-16 src/test_read_in.py

@@ -1,139 +1,0 @@
-import unittest
-import read_in
-import axelrod
-import pandas
-import numpy
-
-
-class TestStrategies(unittest.TestCase):
-    df = read_in.strategies_properties()
-
-    def test_strategies_properties(self):
-
-        self.assertIsInstance(self.df, pandas.DataFrame)
-        self.assertEqual(len(self.df), len(axelrod.strategies))
-        self.assertTrue([nm.name for nm in axelrod.strategies],
-                        self.df['Name'])
-        for memory_depth in self.df['Memory_depth']:
-            self.assertIsInstance(memory_depth, float)
-
-        for use_of_game in self.df['Makes_use_of_game']:
-
-            self.assertIsInstance(use_of_game, bool)
-
-        for use_of_length in self.df['Makes_use_of_length']:
-            self.assertIsInstance(use_of_length, bool)
-
-    def test_specific_strategy_properties(self):
-
-        tit_for_tat = self.df[self.df['Name'] == 'Tit For Tat']
-        self.assertTrue(tit_for_tat.Name.all(), 'Tit For Tat')
-        self.assertTrue(tit_for_tat.Memory_depth.all(), 1.0)
-        self.assertFalse(tit_for_tat.Stochastic.all())
-        self.assertEqual(tit_for_tat.Makes_use_of_game.all(), 0.0)
-        self.assertEqual(tit_for_tat.Makes_use_of_length.all(), 0.0)
-
-        adaptive = self.df[self.df['Name'] == 'Adaptive']
-        self.assertTrue(adaptive.Name.all(), 'Adaptive')
-        self.assertTrue(adaptive.Memory_depth.all(), numpy.inf)
-        self.assertFalse(adaptive.Stochastic.all())
-        self.assertEqual(adaptive.Makes_use_of_game.all(), 1.0)
-        self.assertEqual(adaptive.Makes_use_of_length.all(), 0.0)
-
-
-class TestParameters(unittest.TestCase):
-
-    def test_pameters_data_frame(self):
-        parameters_df = read_in.parameters_data_frame()
-
-        self.assertIsInstance(parameters_df, pandas.DataFrame)
-        self.assertEqual(len(parameters_df), 10002)
-        self.assertTrue(parameters_df.columns.all(), ['noise', 'probend',
-                                                      'repetitions', 'seed',
-                                                      'size', 'turns'])
-
-
-class TestReader(unittest.TestCase):
[…]

### 2020-04-16 tasks.py

@@ -1,0 +1,76 @@
+from invoke import task
+import pandas as pd
+
+@task
+def unpack(c):
+    """
+    Unpack downloaded `tar.gz` file
+    """
+    c.run("tar -xzf raw_data.tar.gz --directory data")
+
+
+@task
+def get(c):
+    """
+    Download the data from the online archive
+    """
+    c.run(
+        "wget https://zenodo.org/record/3753498/files/raw_data.tar.gz?download=1 -O raw_data.tar.gz"
+    )
+
+
+@task
+def data(c):
+    """
+    Download and unpack data from online archive
+    """
+    print("Downloading data")
+    get(c)
+    print("Unpacking data")
+    unpack(c)
+
+
+@task
+def process(c):
+    """
+    Process raw data
+    """
+    print("Prepare raw data")
+    c.run("python src/prepare_data.py data/raw_data/ all 3")
+
+    for data_type in ['standard', 'noise', 'probend', 'probend_noise']:
+        print(f"Process {data_type} data set")
+        c.run(f"python src/process_data.py data/{data_type}_3.csv")
+
+
+@task
+def prodata(c):
+    """
+    Download and unpack data from online archive
+    """
+    print("Downloading processed data")
+    c.run(
+        "wget https://zenodo.org/record/3753565/files/data.tar.gz?download=1 -O data.tar.gz"
+    )
+    print("Unpacking data")
+    c.run("tar -xzf data.tar.gz")
+
+
+@task
+def test(c):
+    """
+    Test all packaged code and notebooks
+    """
+    c.run("pytest tests")
+
+
+@task
+def merge(c):
+    dfs = []
+    for name in ['standard', 'noise', 'probend', 'probend_noise']:
+        df = pd.read_csv(f'data/{name}_3_processed.csv')
+
+        dfs.append(df)
+    df = pd.concat(dfs)
+    df.reset_index(inplace=True)
+    df.to_csv('data/merged_3_processed.csv')

### 2020-04-17 paper/main.tex
Remove paragraph about TfT
@nikoleta-v3 did some basic analysis (she's going to put the plots up on
the PR) and found that:

- TfT's median C/C_mean was 1.2
- Tf2T's median C/C_mean was 1.37
- Random's median C/C_mean was 0.8

So it's not immediately clear (from the data) that TfT does match the
C_mean (which makes sense if it is never provoked) and in fact, on
average is "as far" from that mean as Random is.

I've added a TODO to include some sort of similar discussion in the
final section.

@@
 strategies, refining the properties described by R. Axelrod in light of
-recent and more diverse opponent populations. These are: be nice, be provocable and forgiving,  % TODO modify this based on discussion about vocabulary.
+recent and more diverse opponent populations. These are: be nice, be somewhat provocable
 be a little envious, be clever, and adapt to the environment. More precisely,
@@
     \item Be ``nice'' in non-noisy environments or when game lengths are longer
-    \item Reciprocate both cooperation and defection; Be provocable and forgiving  % TODO Modify this following decision on vocabulary
+    \item Reciprocate both cooperation and defection correctly; Be somewhat provocable
     \item \st{Do not be too clever} It's ok to be clever
@@
 
-Moreover, the manner in which a strategy achieves a given cooperation rate
-relative to the tournament population average is important. Playing a strategy
-that randomly cooperates with probability $C_{\text{mean}}$ is unlikely to be as effective as it will
-randomly have cooperations matched with defections, and it may be punished for
-defections against cooperations by retailiating opponents. In contrast, TFT naturally
-achieves a cooperation rate near $C_{\text{mean}}$ by virtue of copying its opponent's
-last move while also minimizing instances where it is exploited by an opponent
-(cooperating while the opponent defects), at least in non-noisy tournaments.
-This also explains why Tit For N Tats does not fare well for $N > 1$ as it fails
-to achieve the proper cooperation ratio by tolerating too many defections.
-TFT forces the opponent to pay back the \((C, D)\) round with a \((D, C)\) round before
-returning to mutual cooperation. This explains why TFT performed well
-in Axelrod's original tournaments as most strategies submitted to those tournaments
-were typically cooperative and relatively few strategies played with an easily exploitable
-pattern. TFT does not appear in the top ranks in tournaments with more aggressive
-strategies because it is too nice. Strategies like Grudger will always
-defect after a fixed number of opponent defections, which allows them to
-effectively exploit strategies like Alternator or stochastic strategies that
-have a non-zero chance of cooperating after mutual defection, which TFT will
-not do. Moreover in a noisy environment these strategies will naturally tend
-toward always defecting, leading them to exploit strategies like Cooperator. In
-such a scenario the noisy environment effectively voids R. Axelrod's rule to be nice,
-allowing strategies to attempt exploitation, whereas in a noise-free environment,
-attempting exploitation can be risky if strategies that exhibit a Grudger-like behavior
-are present, reducing the overall value in attempting to exploit strategies like Cooperator.
-% TODO Both NG and MH seem happy with this paragraph but I find it quite a
-% mouthful and not very too the point (took me a few reads). If you're both
-% happy with it that's fine with me but can we just be sure.
-
-Similarly, these results suggest an explanation regarding the intuitively unexpected
-effectiveness of memory-one strategies historically. Given that among the important
-features associated with success are the relative cooperation rate to the population
-average and the four memory-one probabilities of cooperating conditional on the
-previous round of play, these features can be optimized by a memory-one
-strategy such as TFT. Usage of more history becomes valuable when there are
-exploitable opponent patterns. This is indicated by the importance of SSE as a feature,
-showing that the first-approximation provided by a memory-one strategy is no longer
-sufficient.
-
 \begin{figure}[!htbp]
@@
 \(CD\) to \(D\) distribution indicates that if a strategy were to defect against
-the winners they would reciprocate on average with a probability of 0.5.
+the winners the winners would reciprocate on average with a probability of 0.5.
 
@@
 tournaments it was observed that a successful strategy reciprocates with a
-probability of 0.5. This is distinct between the tournament types. In
+probability of 0.5.
+This leads to the recommendation of needing to be somewhat provocable.
+This is distinct between the tournament types. In
 tournaments with noise a strategy is less likely to cooperate following a
@@
 This fact was also indicated numerically by the importance of the strategy
-feature SSE in the analysis of strategy features. These results highlight
+feature SSE in the analysis of strategy features.
+
+% TODO Add discussion about what our results imply and how they are explained
+% relative to past performances of TfT and ZDs.
+
+These results highlight
 a central idea in evolutionary game theory in this context: the fitness
@@
 \item be nice, if the environment isn't noisy and the games are long
-    \item be provocable and forgiving,
+    \item be somewhat provocable,
     \item be a little envious,

### 2020-04-25 paper/main.tex
order citations
removes TODO

@@
 robin computer tournament became a common evaluation technique for newly designed
-strategies. Many tournaments have followed Axelrod's~\cite{Bendor1991, Beaufils1997, Stephens2002,
-Kendall2007, Stewart2012, Harper2017} and today more hundreds of strategies exist  % TODO Order these citations
+strategies. Many tournaments have followed Axelrod's~\cite{Beaufils1997, Bendor1991,
+Harper2017, Kendall2007, Stephens2002, Stewart2012} and today more hundreds of strategies exist
 in the literature.

### 2020-04-25 paper/main.tex
refere to Tit For Tat as TFT instead of TfT in appendix
removes TODO

@@
 The winner of both of R. Axelrod's tournaments~\cite{Axelrod1980a, Axelrod1980b}
-was the simple strategy Tit For Tat (TFT) which cooperates  % TODO In the appendix we referr to TFT as TfT, we need to be consistent throughout.
+was the simple strategy Tit For Tat (TFT) which cooperates
 on the first turn and thereafter copies the previous action of its opponent,

### 2020-04-25 paper/main.tex
cite raw data set
removes TODO

@@
 possible due to an open source library called Axelrod-Python (APL),
-are covered in Section~\ref{section:data_collection}. The data set generated  % TODO Modify this when the raw as well as the processed data is archived
-for this work has been made publicly available~\cite{data} and can be used
+are covered in Section~\ref{section:data_collection}. The raw as well as the processed
+data set generated
+for this work has been made publicly available~\cite{data, raw_data} and can be used
 for further analysis and insights.
@@
 The data set described in this work contains the largest number of IPD tournaments,
-to the authors knowledge, and it available at~\cite{data}. Further data mining % TODO Modify this when the raw data is also archived
+to the authors knowledge. The raw data set is available at~\cite{raw_data} and the
+processed data at~\cite{data}. Further data mining
 could be applied and provide new insights in the field.

### 2020-04-25 paper/main.tex
maths C, D, R, S, T, P in introduction

@@
 self-interest clashes with collective interest. At each turn of the game both
-players, simultaneously and independently, decide between cooperation (C) and
-defection (D), given memory of all prior interactions. The payoffs for each
+players, simultaneously and independently, decide between cooperation (\(C\)) and
+defection (\(D\)), given memory of all prior interactions. The payoffs for each
 player, at each turn, is influenced by their own choice and the choice of the
@@
 \begin{tabular}{c|c|c}
-& Cooperate (C) & Defect (D) \\
+& Cooperate (\(C\)) & Defect (\(D\)) \\
 \hline
-Cooperate (C) & R & S \\
+Cooperate (\(C\)) & \(R\) & \(S\) \\
 \hline
-Defect (D) & T & P \\
+Defect (\(D\)) & \(T\) & \(P\) \\
 \end{tabular}}

### 2020-04-25 paper/main.tex
minor copy edits to introduction

@@
 strategies. Many tournaments have followed Axelrod's~\cite{Beaufils1997, Bendor1991,
-Harper2017, Kendall2007, Stephens2002, Stewart2012} and today more hundreds of strategies exist
+Harper2017, Kendall2007, Stephens2002, Stewart2012} and today hundreds of more strategies exist
 in the literature.
@@
 The lack of testing against formally defined strategies and tournament winners
-is understandable given the effort required to implement the hundreds of published IPD strategies
+is understandable given the effort required to implement the hundreds of published IPD strategies.
 Implementing prior strategies faithfully is often extremely difficult or
@@
 in~\cite{Press2012}. These strategies attempt to force a linear relationship between
-stationary payoffs against other memory-one opponents, potentally ensuring that they
+stationary payoffs against other memory-one opponents, potentially ensuring that they
 receive a higher average payout. While ZDs were introduced with a small tournament in
@@
 this manuscript evaluates the performance of \numberofstrategies
-strategies in \numberofalltournaments tournaments. Furthermore a large portion
+strategies in \numberofalltournaments tournaments. Furthermore, a large portion
 of the strategies used in this manuscript are drawn from known and named strategies
@@
 or those of a certain structural form such as finite state machines or deterministic
-memory two strategies). Additionally, our tournaments come in a
+memory-two strategies). Additionally, our tournaments come in a
 number of variations including standard tournaments emulating R. Axelrod's original tournaments,

### 2020-04-25 paper/main.tex
adds a bit on generosity and forgiveness in introduction

@@
 
+Forgiveness in R. Axelrod's terms is a two round procedure. Though essentially
+it is the strategy's ability to go from a \(DC\) to \(C\) aiming to achieve
+mutual cooperation again, the only way TFT would end up in \(DC\), in
+environments without noise, is if it had received a defection and it retaliated.
+Following, an opponent's defection if the opponent were to ``apologise''
+(resulting in a \(DC\) round), then TFT would forgive its opponent since mutual
+cooperation is better than mutual defection.
 As a result of the strategy's strong performance in both tournaments, and moreover in a
@@
 that TFT suffered in environments with noise. This was
-mainly due to the strategy's lack of generosity and contrition. Since TFT immediately
+mainly due to the strategy being too provocable and its lack of generosity and contrition. Since TFT immediately
 punishes a defection, in a noisy environment it can get stuck in a
@@
     \item Be ``nice'' in non-noisy environments or when game lengths are longer
-    \item Reciprocate both cooperation and defection correctly; Be somewhat provocable
+    \item Reciprocate both cooperation and defection correctly; Be provocable and generous
     \item \st{Do not be too clever} It's ok to be clever

### 2020-04-25 paper/main.tex
fixes broken sentence for normalised rank

@@
 and the rate of which the strategy cooperated after each state. The \textbf{normalised rank}
-feature that is manually added. The rank \(R\) of a given.
-strategy can vary between 0 (first) and \(N-1\) (last). Thus, the normalised rank,
+is a feature that has been manually added to the result summary. The rank \(R\) of a given
+strategy can vary between 0 (first) and \(N-1\) (last), and thus the normalised rank,
 denoted as $r$, is calculated as a strategy's rank divided by \(N - 1\).

### 2020-04-25 paper/main.tex
minor copy edits to performance section

@@
     strategies that had been trained using reinforcement learning techniques.
-    \item In noisy environments where the noise probability strictly less than
+    \item In noisy environments where a noise probability strictly less than
     0.1 was considered, the successful strategies were strategies specifically
@@
 and more specifically, the suggestions `Do not be clever' and `Do not be envious'.
-We dig deeper into the crucial strategy features for success in the following sections.
+We dig deeper into the crucial strategy features for success in the following section.
 

### 2020-04-25 paper/main.tex
fixes discussion on sse distributions and CD to C rates

@@
 opponents. The winners of the tournaments considered in this work are
-envious, but not as much as many ZDs. This highlights why TFT's early tournament
-success fails to generalize -- it never attempts to defect against a cooperating
-or exploitable opponent (e.g. Alternator). Moreover, many of the strategies in
-the library will not tolerate exploitation attempts. A clever strategy can
-achieve mutual cooperation with stronger strategies while also being able to
-exploit weaker strategies. This is why ZDs fail to appear in the tops
-ranks -- they try to exploit all opponents and cannot actively adapt back to
-mutual cooperation against stronger strategies, which requires more depth of memory.
-\footnote{Note that ZDs also tend to perform poorly in population games for
-a similar reason: they attempt to exploit other players using ZDs, failing to
-form a cooperative subpopulation. This makes them good invaders but poor resisters of invasion.}
+envious, but not as much as many ZDs.
+Though the exact interactions between the matches have not been recorded here,
+the work of~\cite{Harper2017} which introduced the trained strategies that
+appeared in the top ranked strategies of Section~\ref{section:top_performances}
+did. In~\cite{Harper2017} it was shown that clever strategies managed to achieve
+mutual cooperation with stronger strategies whilst exploiting the weaker
+strategies. This could potentially be what is happening with the clever winners
+of our analysis, and would explain the SSE distributions. This could also
+be the reason why ZDs fail to appear in the tops ranks -- they try to exploit
+all opponents and cannot actively adapt back to mutual cooperation against
+stronger strategies, which requires more depth of memory. \footnote{Note that
+ZDs also tend to perform poorly in population games for a similar reason: they
+attempt to exploit other players using ZDs, failing to form a cooperative
+subpopulation. This makes them good invaders but poor resisters of invasion.}
 
@@
 tournaments it was observed that a successful strategy reciprocates with a
-probability of 0.5.
-This leads to the recommendation of needing to be somewhat provocable.
-This is distinct between the tournament types. In
+probability of 0.5, and in a setting that the type
+of the tournament can vary between all the examined types a winning strategy
+would reciprocate on average with a probability of 0.58. In
 tournaments with noise a strategy is less likely to cooperate following a
 defection compared to standard tournaments, and in probabilistic ending
-tournaments a strategy will reciprocate a defection. In a setting that the type
-of the tournament can vary between all the examined types a winning strategy
-would reciprocate on average with a probability of 0.58.
+tournaments a strategy will reciprocate a defection.
+This leads to revisit the recommendation of being provocable to defections made
+by R. Axerlod. In fact only in tournament that are not long a strategy should
+be too provocable, in the rest of the settings a strategy should be more
+generous.
 
@@
 \section{Discussion}\label{section:conclusion}
+
+This highlights why TFT's early tournament
+success fails to generalize -- it never attempts to defect against a cooperating
+or exploitable opponent (e.g. Alternator).
 

### 2020-04-25 paper/main.tex
minor copy edits in evaluation of performance section

@@
 
-The distributions of SSE and \(CD\) to \(D\) rate for the winners of standard
+The distributions of SSE and \(CD\) to \(C\) rate for the winners of standard
 tournaments are also given in Figure~\ref{fig:discussion_standard}. The SSE
@@
 matches where they did not try to extortionate their opponents. Furthermore, the
-\(CD\) to \(D\) distribution indicates that if a strategy were to defect against
+\(CD\) to \(C\) distribution indicates that if a strategy were to defect against
 the winners the winners would reciprocate on average with a probability of 0.5.

### 2020-04-25 paper/main.tex
rewrites discussion while trying to keep everyones inputs

@@
 
-This highlights why TFT's early tournament
-success fails to generalize -- it never attempts to defect against a cooperating
-or exploitable opponent (e.g. Alternator).
-
-This manuscript has explored the performance of \numberofstrategies strategies
-of the IPD in a large number of computer tournaments.
-We analyzed and extracted the salient features of the best performing strategies
-across various tournament types, casting the results in terms of R. Axelrod's
-original suggested features of good IPD strategies. Moreover, our results
-shed light on the historic performance of TFT, ZDs,
-and memory-one strategies generally. Strategies need to match their play
-to the cooperativeness of the tournament population and do so in a way that
-prevents or minimizes exploitation. Overall we see that complex or clever
-strategies can be effective, whether trained against a corpus of possible
-opponents or purposely designed to mitigate the impact of noise such as
-in the strategy DBS. Further, we showed that while the type of exploitation
-attempted by ZDs is not typically effective in tournaments, more
-sophisticated strategies capable of selectively exploiting weaker opponents
-while mutually cooperating with stronger opponents can be highly successful.
-This fact was also indicated numerically by the importance of the strategy
-feature SSE in the analysis of strategy features.
-
-% TODO Add discussion about what our results imply and how they are explained
-% relative to past performances of TfT and ZDs.
-
-These results highlight
-a central idea in evolutionary game theory in this context: the fitness
-landscape is a function of the population (where fitness in this case is
-tournament performance). While that may seem obvious now, it shows why
-historical tournament results on small or arbitrary populations of strategies
-have so often failed to produce generalizable results.
-
-Highly noisy or tournaments with short matches favor less cooperative strategies.
-These environments mitigate the value of being nice. Uncertainty enables
-exploitation, reducing the ability of maintaining or enforcing mutual cooperation,
-while triggering grudging strategies to switch from typically cooperating to
-typically defecting. Accordingly, we find that in noisy tournaments
-the best performing players cooperate a lower rate than the tournament
-population on average. Nevertheless we found some strategies designed or trained
-for noisy environments were also highly ranked in noise-free tournaments. This
-indicates that strategy complexity is not necessarily a liability, rather it
-can confer adaptability to a more diverse set of environments.
-
-In Section~\ref{section:top_performances}, the tournaments results were used to
-present the top performances. The data set contained results from four different
-settings, and these were also studied individually. In standard tournaments
-complex strategies trained using reinforcement learning ranked in the top spots.
-Some of these strategies ranked again in the top spots in probabilistic
-ending tournaments when a \(p_e\) of less 0.1 was considered and in noisy tournaments
-when \(p_n\) was less than 0.1. In probabilistic
-ending tournaments \(p_e\) was designed to vary between 0 and 1. It was demonstrated
-that for values larger than 0.1, as stated in the Folk Theorem, defecting strategies
-were winning the tournaments because there was a high likelihood of the game
-ending in the next turn. In tournaments with noise the median ranks of the top
-15 strategies had the highest values and the \(r\) distributions were bimodal.
-The top rank strategies were performing both well and bad, and this indicates
-that in noisy tournaments where the noise can vary substantially,
-there were no strategies that can guarantee winning across a range of noise.
-However, if the probability of noise was constrained at 0.1 then strategies
-designed for noisy tournaments indeed performed well.
-
-So what is the best way of playing the IPD? And is there a single dominant
-strategy for the IPD?
-
-There was not a single strategy within the collection of the
-\numberofstrategies strategies that managed to perform well in all the
-tournaments variations it competed in.
-Even if on average a strategy ranked highly in a specific environment this did not
-guarantee its success over the different tournament types. However, the results
-of sections~\ref{section:top_performances}
-and~\ref{section:evaluation_of_performance} demonstrated that there are
-properties associated with the success of strategies. A few of the properties that
-have been identified by this manuscript's analysis contradict the properties of
-Axelrod~\cite{Axelrod1981}. Namely, in Section~\ref{section:top_performances} it
-was shown that trained strategies dominated several
-tournaments across tournament types, hinting that successful IPD strategies are
-often clever or more complex than simple strategies like TFT or ZDs. Most of the
-successful strategies highlighted
-in~Section~\ref{section:top_performances} were strategies that begin with
-cooperation.
-
-Furthermore, in Section~\ref{section:top_performances}
-and~\ref{section:evaluation_of_performance} it was shown that envious strategies
-performed well. Though these were not the most envious strategies in the
-tournaments (ZDs were included), these strategies benefited by being a bit
-envious. From Section~\ref{section:evaluation_of_performance} it was concluded
-that there is a significant importance in adapting to the environment, and more
-specifically in this work, to the mean cooperator. This section also
-demonstrated that a strategy should reciprocate, as suggested by R. Axelrod, but in
-some environments, such as standard and noisy, it should relax its readiness to
-do so.
-
-Thus, the five properties successful strategies need to have in a IPD competition
-are:
+This manuscript explored the performance of \numberofstrategies strategies of
+the IPD in \numberofalltournaments computer tournaments. The collection of
+computer tournaments presented here is the largest and more diverse collection in the
+literature. The \numberofstrategies strategies are drawn from known named
+strategies in IPD literature and the computer tournaments include tournaments of
+four different settings.
+
+So what is the best way of playing the IPD? And is
+there a single dominant strategy for the IPD? There was not a single strategy
+within the collection of the \numberofstrategies strategies that managed to
+perform well in all the tournaments variations it competed in. Even if on
+average a strategy ranked highly in a specific environment this did not
+guarantee its success over the different tournament types. Nevertheless, in
+Sections~\ref{section:top_performances}
+and~\ref{section:evaluation_of_performance} we examined the best performing
+strategies across various tournament types and analysed their salient features,
+and demonstrated that there are properties associated with the success of
+strategies, contradicting the originally suggested properties of R.
+Axelrod~\cite{Axelrod1981}.
+
+We showed that complex or \textbf{clever} strategies can be effective, whether
+trained against a corpus of possible opponents or purposely designed to mitigate
+the impact of noise such as in the strategy DBS. Moreover, we found some
+strategies designed or trained for noisy environments were also highly ranked in
+noise-free tournaments which reinforces the idea that strategies'
+complexity/cleverness is not necessarily a liability, rather it can confer
+adaptability to a more diverse set of environments.
+We also showed that while the type of exploitation attempted by ZDs is
+not typically effective in standard tournaments, \textbf{envious} strategies
+capable of both exploiting and not their opponents can be highly successful.
+Based on the results of~\cite{Harper2017} this could be because they are
+selectively exploiting weaker opponents while mutually cooperating with stronger
+opponents. Highly noisy or tournaments with short matches also favoured envious
+strategies. These environments mitigated the value of being nice. Uncertainty
+enables exploitation, reducing the ability of maintaining or enforcing mutual
+cooperation, while triggering grudging strategies to switch from typically
+cooperating to typically defecting.
+
+The features analysis of the best performing strategies demonstrated that a
+strategy should reciprocate, as suggested by R. Axelrod, but it should relax its
+readiness to do so and be more \textbf{generous}. For noisy environments this is
+inline with the results of~\cite{Bendor1991, Donninger1986, Molander1985,
+Hammerstein1984}, however, we also showed that generosity pays off even in
+standard settings, and that in fact the only setting a strategy would want to be
+too provocable is when the matches are not long. Forgiveness as defined by R.
+Axerlod was not explored here. This was mainly because the two round states were
+not recorded during the data collection. That is something we would aim to
+incorporate in future work.
+The features analysis also concluded that
+there is a significant importance in \textbf{adapting to the environment}, and
+more specifically, to the mean cooperator. Moreover, the manner in which a
+strategy achieves a given cooperation rate relative to the tournament population
+average is important. In standard tournaments a strategy would aim to be the
+mean the cooperator while in noisy tournaments the best performing players
+cooperate a lower rate than the tournament population on average.
+
+This could potentially explain the early success of TFT. TFT naturally achieves
+a cooperation rate near $C_{\text{mean}}$ by virtue of copying its opponent's
+last move while also minimizing instances where it is exploited by an opponent
+(cooperating while the opponent defects), at least in non-noisy tournaments. It
+could also explain why Tit For \(N\) Tats does not fare well for $N > 1$ -- it
+fails to achieve the proper cooperation ratio by tolerating too many defections.
+
+Similarly, our results could suggest an explanation regarding the intuitively
+unexpected effectiveness of memory-one strategies historically. Given that among
+the important features associated with success are the relative cooperation rate
+to the population average and the four memory-one probabilities of cooperating
+conditional on the previous round of play, these features can be optimized by a
+memory-one strategy such as TFT. Usage of more history becomes valuable when
+there are exploitable opponent patterns. This is indicated by the importance of
+SSE as a feature, showing that the first-approximation provided by a memory-one
+strategy is no longer sufficient.
+
+These results highlight a central idea in evolutionary game theory in this
+context: the fitness landscape is a function of the population (where fitness in
+this case is tournament performance). While that may seem obvious now, it shows
+why historical tournament results on small or arbitrary populations of
+strategies have so often failed to produce generalizable results.
+
+Overall, the five properties successful strategies need to have in a IPD competition
+based on the analysis that has been presented in this manuscript are:
 
 \begin{itemize}
-\item be nice, if the environment isn't noisy and the games are long
-    \item be somewhat provocable,
-    \item be a little envious,
-    \item be clever,
-    \item adapt to the environment (including the population of strategies).
+    \item Be ``nice'' in non-noisy environments or when game lengths are longer
+    \item Be provocable but also generous when game lengths are longer
+    \item Be a little bit envious
+    \item It's ok to be clever
+    \item Adapt to the environment (including the population of strategies).
 \end{itemize}

### 2020-04-25 paper/main.tex
minor edits to abstract

@@
 strategies in \numberofalltournaments tournaments, present the top performing strategies across multiple
-tournament types, and distill their salient features. The results show that there is not yet a single
-strategy that performs well in diverse Iterated Prisoner's Dilemma scenarios.
-Nevertheless there are several properties that heavily influence the best performing
-strategies, refining the properties described by R. Axelrod in light of
-recent and more diverse opponent populations. These are: be nice, be somewhat provocable
+tournament types, and distill their salient features.
+The results show that there is not yet a single
+strategy that performs well in diverse Iterated Prisoner's Dilemma scenarios,
+nevertheless there are several properties that heavily influence the best performing
+strategies. Refining the properties described by R. Axelrod in light of
+recent and more diverse opponent populations these are: be nice, be provocable and generous,
 be a little envious, be clever, and adapt to the environment. More precisely,
@@
 and that the manner in which a strategy achieves the ideal cooperation rate is crucial.
-The features of high performing strategies reveal why strategies such as Tit For Tat
+The features of high performing strategies help cast some light on why strategies such as Tit For Tat
 performed historically well in tournaments and why zero-determinant strategies

### 2020-04-28 paper/main.tex
minor typos fixes by v.k.
Co-Authored-By: Vince Knight <vincent.knight@gmail.com>

@@
 nevertheless there are several properties that heavily influence the best performing
-strategies. Refining the properties described by R. Axelrod in light of
-recent and more diverse opponent populations these are: be nice, be provocable and generous,
+strategies. This refines the properties described by R. Axelrod in light of
+recent and more diverse opponent populations to be: be nice, be provocable and generous,
 be a little envious, be clever, and adapt to the environment. More precisely,
@@
 tournaments a strategy will reciprocate a defection.
-This leads to revisit the recommendation of being provocable to defections made
-by R. Axerlod. In fact only in tournament that are not long a strategy should
-be too provocable, in the rest of the settings a strategy should be more
+This leads to revisiting the recommendation of being provocable to defections made
+by R. Axerlod. In fact only in tournaments with short matches should a strategy
+be provocable, in the rest of the settings a strategy should be more
 generous.
@@
 the IPD in \numberofalltournaments computer tournaments. The collection of
-computer tournaments presented here is the largest and more diverse collection in the
-literature. The \numberofstrategies strategies are drawn from known named
-strategies in IPD literature and the computer tournaments include tournaments of
-four different settings.
+computer tournaments presented here is the largest and most diverse collection in the
+literature. The \numberofstrategies strategies are drawn from the APL and include
+strategies from the IPD literature. The computer tournaments include tournaments of
+four different types.
 
 So what is the best way of playing the IPD? And is
-there a single dominant strategy for the IPD? There was not a single strategy
+there a single dominant strategy for the IPD?
+
+There was not a single strategy
 within the collection of the \numberofstrategies strategies that managed to
@@
 and~\ref{section:evaluation_of_performance} we examined the best performing
-strategies across various tournament types and analysed their salient features,
-and demonstrated that there are properties associated with the success of
-strategies, contradicting the originally suggested properties of R.
+strategies across various tournament types and analysed their salient features.
+this demonstrated that there are properties associated with the success of
+strategies which in fact contradict the originally suggested properties of R.
 Axelrod~\cite{Axelrod1981}.
@@
 trained against a corpus of possible opponents or purposely designed to mitigate
-the impact of noise such as in the strategy DBS. Moreover, we found some
+the impact of noise such as the DBS strategy. Moreover, we found some
 strategies designed or trained for noisy environments were also highly ranked in
@@
 there is a significant importance in \textbf{adapting to the environment}, and
-more specifically, to the mean cooperator. Moreover, the manner in which a
+more specifically, to the mean cooperator. 
+In standard tournaments a strategy would aim to be the
+mean the cooperator while in noisy tournaments the best performing players
+cooperate at a lower rate than the tournament population on average.
+Moreover, the manner in which a
 strategy achieves a given cooperation rate relative to the tournament population
-average is important. In standard tournaments a strategy would aim to be the
-mean the cooperator while in noisy tournaments the best performing players
-cooperate a lower rate than the tournament population on average.
+average is important.
 
@@
     \item Be a little bit envious
-    \item It's ok to be clever
+    \item Be clever
     \item Adapt to the environment (including the population of strategies).

### 2020-04-29 paper/main.tex
eliminates the initial be in abstract

@@
 strategies. This refines the properties described by R. Axelrod in light of
-recent and more diverse opponent populations to be: be nice, be provocable and generous,
+recent and more diverse opponent populations to: be nice, be provocable and generous,
 be a little envious, be clever, and adapt to the environment. More precisely,

### 2020-04-29 paper/main.tex
rephrases the 100 strategies sentence.

@@
 strategies. Many tournaments have followed Axelrod's~\cite{Beaufils1997, Bendor1991,
-Harper2017, Kendall2007, Stephens2002, Stewart2012} and today hundreds of more strategies exist
-in the literature.
+Harper2017, Kendall2007, Stephens2002, Stewart2012} and now the
+literature and various codebases contain hundreds of strategies.
 

### 2020-04-29 paper/main.tex
tweaks forgiveness paragraph based on marc's comments

@@
 
-Forgiveness in R. Axelrod's terms is a two round procedure. Though essentially
-it is the strategy's ability to go from a \(DC\) to \(C\) aiming to achieve
+Forgiveness is a strategy's ability to go from a \(DC\) to \(C\) aiming to achieve
 mutual cooperation again, the only way TFT would end up in \(DC\), in
-environments without noise, is if it had received a defection and it retaliated.
-Following, an opponent's defection if the opponent were to ``apologise''
-(resulting in a \(DC\) round), then TFT would forgive its opponent since mutual
-cooperation is better than mutual defection.
+environments without noise, is if it had received a defection and then retaliated.
+Subsequently, TFT would forgive an opponent that apologises (in a \(DC\) round)
+by returning to cooperation, since mutual cooperation is better than mutual defection.
 As a result of the strategy's strong performance in both tournaments, and moreover in a

### 2020-04-29 paper/main.tex
softens property suggestion
minor rewording for "the data and raw data"

@@
     \item Be ``nice'' in non-noisy environments or when game lengths are longer
-    \item Reciprocate both cooperation and defection correctly; Be provocable and generous
+    \item Reciprocate both cooperation and defection appropriately; Be provocable and generous but not extremely
     \item \st{Do not be too clever} It's ok to be clever
@@
 possible due to an open source library called Axelrod-Python (APL),
-are covered in Section~\ref{section:data_collection}. The raw as well as the processed
-data set generated
-for this work has been made publicly available~\cite{data, raw_data} and can be used
+are covered in Section~\ref{section:data_collection}. The raw and processed data
+sets have been made publicly available~\cite{data, raw_data} and can be used
 for further analysis and insights.

### 2020-04-29 paper/main.tex
changes "a" to "the"

@@
     strategies that had been trained using reinforcement learning techniques.
-    \item In noisy environments where a noise probability strictly less than
+    \item In noisy environments where the noise probability strictly less than
     0.1 was considered, the successful strategies were strategies specifically

### 2020-04-29 paper/main.tex
minor fixes to the language

@@
 mutual cooperation with stronger strategies whilst exploiting the weaker
-strategies. This could potentially be what is happening with the clever winners
+strategies. This could explain the clever winners
 of our analysis, and would explain the SSE distributions. This could also
@@
 Axerlod was not explored here. This was mainly because the two round states were
-not recorded during the data collection. That is something we would aim to
-incorporate in future work.
+not recorded during the data collection. This could be a topic of future work
+that examines the impact of considering more rounds of history.
 The features analysis also concluded that
@@
 In standard tournaments a strategy would aim to be the
-mean the cooperator while in noisy tournaments the best performing players
+mean cooperator while in noisy tournaments the best performing players
 cooperate at a lower rate than the tournament population on average.

### 2020-04-29 paper/main.tex
removes footnote
Co-Authored-By: Vince Knight <vincent.knight@gmail.com>

@@
 all opponents and cannot actively adapt back to mutual cooperation against
-stronger strategies, which requires more depth of memory. \footnote{Note that
+stronger strategies, which requires more depth of memory. Note that
 ZDs also tend to perform poorly in population games for a similar reason: they
 attempt to exploit other players using ZDs, failing to form a cooperative
-subpopulation. This makes them good invaders but poor resisters of invasion.}
+subpopulation. This makes them good invaders but poor resisters of invasion.
 

### 2020-04-29 paper/main.tex
specify that a strategy should be provocable in a setting and generous in the rest

@@
     \item Be ``nice'' in non-noisy environments or when game lengths are longer
-    \item Reciprocate both cooperation and defection appropriately; Be provocable and generous but not extremely
+    \item Reciprocate both cooperation and defection appropriately;
+    Be provocable in tournaments with short matches, and generous when matches are longer
     \item \st{Do not be too clever} It's ok to be clever
@@
 tournaments a strategy will reciprocate a defection.
-This leads to revisiting the recommendation of being provocable to defections made
-by R. Axerlod. In fact only in tournaments with short matches should a strategy
-be provocable, in the rest of the settings a strategy should be more
-generous.
+This leads to adjusting the recommendation of being provocable to defections made
+by R. Axerlod. A strategy should be provocable in tournaments with short matches,
+but in the rest of the settings a strategy should be more generous.
 
@@
     \item Be ``nice'' in non-noisy environments or when game lengths are longer
-    \item Be provocable but also generous when game lengths are longer
+    \item Be provocable in tournaments with short matches, and generous when matches are longer
     \item Be a little bit envious

### 2020-04-29 paper/main.tex
adds citation to statement regarding ZDs

@@
 attempt to exploit other players using ZDs, failing to form a cooperative
-subpopulation. This makes them good invaders but poor resisters of invasion.
+subpopulation~\cite{Knight2017evolution}. This makes them good invaders but poor resisters of invasion.
 

### 2023-11-12 paper/main.tex
drafts sections Data Collection and Top Ranked Strategies

@@
 \newcommand{\numberofstrategies}{\input{unique_number_of_strategies.tex}}
+\def\axelrod{\texttt{Axelrod-Python }}
 
@@
 
-The data set generated for this manuscript was created with APL version 3.0.0.
-APL allows for different types of IPD computer
-tournaments to be simulated and contains a large list of strategies.
-Most of these are strategies described in the literature with a few exceptions
-of strategies that have been contributed specifically to the package. This
-paper makes use of \numberofstrategies strategies implemented in version 3.0.0. A
-list of the strategies is given in the Appendix~\ref{app:list_of_players}.
-APL features several tournament types, this work considers
-standard, noisy, probabilistic ending, and noisy probabilistic ending
-tournaments.
+The data set generated for this manuscript was created using \axelrod version 3.0.0.
+\axelrod enables the simulation of Iterated Prisoner's Dilemma
+computer tournaments and contains an extensive list of strategies. Most of these
+strategies are described in the literature, with a few exceptions contributed
+specifically to the package. In this paper, we use a total of \numberofstrategies
+strategies. You can find a list of these strategies in the Supplementary Material.
 
-\textbf{Standard tournaments} are tournaments similar to that of R. Axelrod's well-known
-tournaments~\cite{Axelrod1980a}. There are \(N\) strategies which all play an iterated
-game of \(n\) number of turns against each other. Note that self-interactions
-are not included. Similarly, \textbf{noisy
-tournaments} have \(N\) strategies and \(n\) number of turns, but at each turn
-there is a probability \(p_n\) that a player's action will be flipped.
-\textbf{Probabilistic ending tournaments}, are of size \(N\) and after each turn
-a match between strategies ends with a given probability \(p_e\). Finally,
-\textbf{noisy probabilistic ending} tournaments have both a noise probability
-\(p_n\) and an ending probability \(p_e\). For smoothing the simulated results a
-tournament is repeated for \(k\) number of times. This was allowed to vary
-in order to evaluate the effect of smoothing. The winner of each tournament
-is based on the median score a strategy achieved and not by the number of wins.
-
-The process of collecting tournament results is described by
-Algorithm~\ref{algorithm:data_generation}. For each trial a random size \(N\) is
-selected, and from the \numberofstrategies strategies a random list of \(N\) strategies is
-chosen. For the given list of strategies a standard, a noisy, a probabilistic
-ending and a noisy probabilistic ending tournament are performed and repeated
-\(k\) times. The parameters for the tournaments, as well as the number of
-repetitions, are selected once for each trial. The parameters and their
-respective minimum and maximum values are given by
-Table~\ref{table:parameters_values}.
-
-\begin{table}[!htbp]
-    \begin{center}
-        \resizebox{.6\textwidth}{!}{
-        \begin{tabular}{lcccc}
-    \toprule
-    parameter & parameter explanation &   min value & max value \\
-    \midrule
-    $N$ & number of strategies  & 3 & 195 \\
-    $k$ & number of repetitions  & 10 & 100 \\
-    $n$ & number of turns      & 1 & 200 \\
-    $p_n$ & probability of flipping action at each turn  & 0 & 1   \\
-    $p_e$ & probability of match ending in the next turn & 0 & 1   \\
-    \bottomrule
-        \end{tabular}}
-    \end{center}
-    \caption{Data collection; parameters' values}
-    \label{table:parameters_values}
-\end{table}
-
-The source code for the data collection, as well as the source code for
-the analysis, which will be discussed in the following sections, have been written
-following best practices~\cite{Aberdour2007, Benureau2018}
-and is available here. %TODO archive code and include github url as well.
+The package supports several tournament types, and this work considers standard,
+noisy, probabilistic ending, and noisy probabilistic ending tournaments.
+{\it Standard tournaments} are similar to Axelrod's well-known
+tournaments~\cite{Axelrod1980a}. In these tournaments, there are \(N\)
+strategies, and each strategy plays an iterated game with \(n\) turns against
+all other strategies, not including self-interactions.
+{\it Noisy tournaments} also involve \(N\) strategies and \(n\) turns, but
+in each turn, there is a probability \(p_n\) that a player's action is
+flipped.
+{\it Probabilistic ending tournaments} consist of \(N\) strategies, and
+after each turn, a match between strategies ends with a given probability
+\(p_e\).
+Finally, {\it noisy probabilistic ending tournaments} incorporate both a
+noise probability \(p_n\) and an ending probability \(p_e\). For smoother
+results, each tournament is repeated \(k\) times, and this repetition factor was
+allowed to vary to assess the impact of smoothing. The winner of each tournament
+is determined based on the average score achieved by a strategy from the entire
+set of repetitions, not by the number of wins.
+The process of collecting tournament results is outlined in
+Algorithm~\ref{algorithm:data_generation}. For each trial, we choose a random
+size \(N\) is selected, and a random list of \(N\) strategies from the
+\numberofstrategies available. Subsequently, standard, noisy, probabilistic
+ending, and noisy probabilistic ending tournaments are conducted for the
+selected list of strategies. The parameters for the tournaments, as well as the
+number of repetitions, are chosen once for each trial.
 
@@
     \setstretch{1.35}
-    \ForEach{\text{seed} $\in [0, 11420]$}{
-        $N \gets \text{randomly select integer}\in [N_{min}, N_{max}]$\;
+    \For{\text{seed} $\in [0, 11420]$}{
+        $N \gets \text{randomly select integer}\in [3, 195]$\;
         $\text{players} \gets  \text{randomly select $N$ players}$\;
-        $k \gets  \text{randomly select integer}\in [k_{min}, k_{max}]$\;
-        $n \gets  \text{randomly select integer}\in [n_{min}, n_{max}]$\;
-        $p_n \gets  \text{randomly select float}\in [p_{n\, min}, p_{n\, max}]$\;
-        $p_e \gets   \text{randomly select float}\in [p_{e\, min}, p_{e\, max}]$\;
+        $k \gets  \text{randomly select integer}\in [10, 100]$\;
+        $n \gets  \text{randomly select integer}\in [1, 200]$\;
+        $p_n \gets  \text{randomly select float}\in [0, 1]$\;
+        $p_e \gets   \text{randomly select float}\in [0, 1]$\;
         \vspace{0.4cm}
@@
     result noisy probabilistic ending}\;
-    \caption{Data collection Algorithm}
+    \caption{Tournament Data Collection Algorithm}
     \label{algorithm:data_generation}
@@
 
-A total of \uniquenumberofseeds trials of Algorithm~\ref{algorithm:data_generation} have been
-run. For each trial the results for 4 different tournaments were collected,
-thus a total of \numberofalltournaments $(\uniquenumberofseeds \times 4)$ tournament results have been
-retrieved. Each tournament outputs a result summary in the form of
-Table~\ref{table:output_result}. Each strategy has participated on average in
-5154 tournaments of each type. The strategy with the maximum participation in each
-tournament type is Inverse Punisher with 5639 entries. The strategy with the
-minimum entries is EvolvedLookerUp 1 1 1 which was selected in 4693 trials.
-
-A result summary (Table~\ref{table:output_result}) has \(N\) rows
-because each row contains information for each strategy that participated in the
-tournament. The information includes the strategy's rank, median score, the rate
-with which the strategy cooperated $(C_r)$, its match win count, and the
-probability that the strategy cooperated in the opening move. Moreover, the
-probabilities of a strategy being in any of the four states ($CC, CD, DC, DD$),
-and the rate of which the strategy cooperated after each state. The \textbf{normalised rank}
-is a feature that has been manually added to the result summary. The rank \(R\) of a given
-strategy can vary between 0 (first) and \(N-1\) (last), and thus the normalised rank,
-denoted as $r$, is calculated as a strategy's rank divided by \(N - 1\).
+We have run a total of \uniquenumberofseeds trials of
+Algorithm~\ref{algorithm:data_generation}. For each trial, we collect the
+results for four different tournaments, resulting in a total of
+\numberofalltournaments $(\uniquenumberofseeds \times 4)$ tournament results.
+Each tournament outputs a result summary in the form of
+Table~\ref{table:output_result}. Each strategy has participated, on average, in
+5154 tournaments of each type. The strategy with the maximum participation in
+each tournament type is Inverse Punisher with 5639 entries. The strategy with
+the minimum entries is EvolvedLookerUp 1 1 1, which was selected in 4693 trials.
+During the data collection process, we allowed the probabilities of noise and
+tournament ending to vary between 0 and 1. However, commonly used values for
+these probabilities are \(p_n < 0.5\) and \(p_e < 0.1\) (for more details, see the
+Supplementary Material). Therefore, in this context, we will focus on these
+subsets for the three tournament types: noisy, probabilistic ending, and noisy
+probabilistic ending. The results presented here pertain to these subsets.
+Specifically, there are a total of 5650, 1134, and 565 runs for each of the
+three tournament types, respectively. We also provide an analysis of the paper
+considering the entire datasets, and these results are presented in the
+Supplementary Material.
 
@@
 \end{center}
-\caption{Output result of a single tournament.}\label{table:output_result}
+\caption{\textbf{Result Summary Example of a Tournament.}
+A result summary consists of \(N\) rows, with each row containing information
+for each strategy that participated in the tournament. This information includes
+the strategy's rank (\(R\)), median score, the cooperation rate (\(C_r\)), the number of
+match wins, and the probability that the strategy cooperated in the opening
+move. Additionally, it provides the probabilities of a strategy being in any of
+the four states ($CC, CD, DC, DD$) and the cooperation rate after each state.}\label{table:output_result}
 \end{table}
@@
 
-The performance of each strategy is evaluated in the four tournament types
-presented in Section \ref{section:data_collection}, followed by an
-evaluation of their performance over all the \numberofalltournaments simulated
-tournaments of this work. Each strategy participated in multiple tournaments of
-the same type (on average 5154). For example TFT participated in a
-total of 5114 tournaments of each type. The strategy's normalised rank
-distribution in these is given in Figure~\ref{fig:tit_for_tat_r_distribution}. A
-value of \(r = 0\) corresponds to a strategy winning the tournament where a
-value of \(r = 1\) corresponds to the strategy coming last. Because of the
-strategies' multiple entries their overall performance is evaluated based on the
-\textbf{median normalised rank} denoted as \(\bar{r}\).
+A strategy has participated in multiple tournaments of each type, and to
+evaluate its overall performance, we introduce a measure called the {\textit
+normalized rank}. In each tournament, the strategies receive a rank, where 0
+denotes that the strategy was the winner, and \(N-1\) indicates that the
+strategy came last in the tournament. The normalized rank, denoted as \(r\), is
+calculated as \(r = \frac{R}{N-1}\). Thus, the rank a strategy achieved over the
+number of players in the tournament. The performance of the strategies is
+assessed based on the {\it median of the normalized rank}, denoted as
+\(\bar{r}\).
 
-\begin{figure}[!htbp]
+For example, let's consider the well-known strategies Tit For Tat and
+Gradual. Each strategy participated in several tournaments of each type (see
+Figure~\ref{fig:normalised_rank_distributions}).
+We show the distribution of the ranks of these
+strategies in each of the four tournaments. We can observe that in tournaments
+with the presence of noise, Tit For Tat has a normally distributed normalized
+rank around 1/2. In tournaments without noise, the strategy performs better,
+achieving its best performance in probabilistic ending tournaments with a median
+normalized rank of 0.298.
+In comparison, Gradual's performance has longer tails, indicating that there
+were tournaments where the strategy performed very well or very poorly. Overall,
+Gradual achieves a lower median rank, signifying that it performs better than
+Tit For Tat except in the case of noisy and probabilistic ending tournaments.
+
+\begin{figure}[h]
     \centering
-    \includegraphics[width=.8\textwidth]{../images/tit_for_tat_r_distributions.pdf}
-    \caption{TFT's $r$ distribution in tournaments. Lower values of \(r\)
-    correspond to better performances. The best performance
-    of the strategy has been in standard tournaments where it achieved a $\bar{r}$
-    of 0.34.}
-    \label{fig:tit_for_tat_r_distribution}
+    \includegraphics[width=\textwidth]{../images/normalised_rank_distributions.pdf}
+    \caption{\textbf{Examples of normalized rank distributions for two
+    strategies, Tit For Tat and Gradual.} We plot the distributions of \(r\) for
+    the two strategies in the four tournament types. As a reminder, lower values
+    of \(r\) correspond to better performances. In each plot, we also show the
+    number of data points. Both strategies participated in a similar number of
+    tournaments. Based on the median rank, which we use in this work to define
+    overall performance, Tit For Tat performs best in probabilistic ending
+    tournaments, whereas Gradual was in standard tournaments. The best
+    performance of the Gradual strategy has been in standard tournaments where
+    it achieved a \(\bar{r}\) of 0.34.}
+    \label{fig:normalised_rank_distributions}
 \end{figure}
 
-The top 15 strategies for each tournament type based on \(\bar{r}\) are given in
-Table~\ref{table:top_performances}. The data collection process was designed such
-that the probabilities of noise and ending of the match varied between 0 and
-1. However, commonly used values for these probabilities are values less than 0.1.
-Thus,
-Table~\ref{table:top_performances} also includes the top 15 strategies in noisy
-tournaments with \(p_n < 0.1\) and probabilistic ending tournaments with \(p_e <
-0.1\).
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=.8\textwidth]{../images/top_performers.pdf}
+    \caption{\(r\) distributions of the top 15 strategies in different
+    environments. A lower value of \(\bar{r}\) corresponds to a more successful
+    performance. A strategy's \(r\) distribution skewed towards zero indicates
+    that the strategy ranked highly in most tournaments it participated in. Most
+    distributions are skewed towards zero except the distributions with
+    unrestricted noise, supporting the conclusions from
+    Table~\ref{table:top_performances}.}\label{fig:r_distributions}
+\end{figure}
 
 \newcolumntype{g}{>{\columncolor{Gray}}l}
-\begin{table}[!htbp]
+\begin{table}[t]
     \begin{center}
@@
 
-The \(r\) distributions for the top ranked strategies of Table~\ref{table:top_performances}
-are given by Figure~\ref{fig:r_distributions}.
+The top 15 strategies for each tournament type, based on \(\bar{r}\), are
+presented in Table~\ref{table:top_performances}, while the \(r\) distributions
+for the top-ranked strategies can be found in Figure~\ref{fig:r_distributions}.
+In standard tournaments, 10 out of the 15 top strategies were introduced
+in~\cite{Harper2017}. These strategies are based on finite state automata (FSM),
+hidden Markov models (HMM), artificial neural networks (ANN), lookup tables
+(LookerUp), and stochastic lookup tables (Gambler). They have been trained using
+reinforcement learning algorithms (evolutionary and particle swarm algorithms)
+to perform well against a subset of the strategies in \axelrod in a standard
+tournament. Thus, their performance in the specific setting was anticipated,
+although still noteworthy given the random sampling of tournament participants.
+DoubleCrosser and BackStabber, both from the \axelrod, use the number of turns and
+are set to defect in the last two rounds. These strategies can be characterized
+as “cheaters” because their source code allows them to know the number of turns
+(unless the match has a probabilistic ending). These strategies were expected to
+not perform as well in tournaments where the number of turns is not specified.
+Finally, Winner 12~\cite{mathieu2017} and DBS~\cite{Au2006} are both from the
+literature. DBS is a strategy specifically designed for noisy environments;
+however, it ranks highly in standard tournaments as well. Similarly, the
+fourth-ranked player, Evolved FSM 16 Noise 05, was trained for noisy tournaments
+yet performs well in standard tournaments.
 
-\begin{figure*}[!htbp]
-    \centering
-    \begin{subfigure}{0.485\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/r_distribution_standard.pdf}
-        \caption{$r$ distributions of top 15 strategies in standard tournaments.}\label{fig:std_results}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.485\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/r_distribution_noise_subset.pdf}
-        \caption{$r$ distributions of top 15 strategies in noisy tournaments with \(p_n < 0.1\).}\label{fig:noise_subset_results}
-    \end{subfigure}
-    \vskip\baselineskip
-    \begin{subfigure}{0.485\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/r_distribution_noise.pdf}
-        \caption{$r$ distributions of top 15 strategies in noisy tournaments.}\label{fig:noise_results}
-    \end{subfigure}
-    \quad
-    \begin{subfigure}{0.485\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/r_distribution_probend_subset.pdf}
-        \caption{\(r\) distributions of top 15 strategies in 1139 probabilistic ending
-        tournaments with \(p_e < 0.1\).}
-        \label{fig:probend_subset_results}
-    \end{subfigure}
-    \vskip\baselineskip
-    \begin{subfigure}{0.485\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/r_distribution_probend.pdf}
-        \caption{$r$ distributions of top 15 strategies in probabilistic ending tournaments.}\label{fig:probend_results}
-    \end{subfigure}
-    \quad
-    \begin{subfigure}{0.485\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/r_distribution_probend_noise.pdf}
-        \caption{$r$ distributions of top 15 strategies in noisy probabilistic ending tournaments.}
-        \label{fig:probend_noise_results}
-    \end{subfigure}
-    \caption{\(r\) distributions of the top 15 strategies in different
-    environments. A lower value of \(\bar{r}\) corresponds to a more successful
-    performance. A strategy's \(r\) distribution skewed towards zero indicates
-    that the strategy ranked highly in most tournaments it participated in. Most
-    distributions are skewed towards zero except the distributions with
-    unrestricted noise, supporting the conclusions from
-    Table~\ref{table:top_performances}.}\label{fig:r_distributions}
-\end{figure*}
-
-In standard tournaments 10 out of the 15 top strategies were introduced
-in~\cite{Harper2017}. These are strategies based on finite state automata (FSM),
-hidden Markov models (HMM), artificial neural networks (ANN), lookup tables
-(LookerUp) and stochastic lookup tables (Gambler) that have been trained using
-reinforcement learning algorithms (evolutionary and particle swarm algorithms).
-They have been trained to perform well against a subset of the strategies
-in APL in a standard tournament, thus their performance in the
-specific setting was anticipated although still noteworthy given the random
-sampling of tournament participants. DoubleCrosser, BackStabber and Fool Me Once, are
-strategies not from the literature but from the APL. DoubleCrosser is an extension
-of BackStabber and both strategies make use of the number of turns because they are
-set to defect on the last two rounds. It should be noted that these
-strategies can be characterised as ``cheaters'' because the source code of the strategies
-allows them to know the number of turns in a match (unless the match has a probabilistic ending). These strategies were expected to not perform as well in
-tournaments where the number of turns is not specified. Finally, Winner
-12~\cite{mathieu2017} and DBS~\cite{Au2006} are both from the literature.
-DBS is a strategy specifically designed for noisy environments, however, it ranks
-highly in standard tournaments as well. Similarly the fourth ranked player,
-Evolved FSM 16 Noise 05, was
-trained for noisy tournaments yet performs well in standard tournaments.
-Figure~\ref{fig:std_results} shows that these strategies typically perform
-well in any standard tournament in which they participate.
-
-In the case of noisy tournaments with smaller noise \(p_n < 0.1\) the top
-performing strategies
-include strategies specifically designed for noisy tournaments. These are DBS,
-Evolved FSM 16 Noise 05, Evolved ANN 5 Noise 05, PSO Gambler 2 2 2 Noise 05 and
-Omega Tit For Tat~\cite{kendall2007iterated}. Omega TFT, a strategy designed
-to break the deadlocking cycles of \(CD\) and \(DC\) that TFT can fall into in noisy
-environments, places 10th. The rest of the top ranks are
-occupied by strategies which performed well in standard tournaments and
+In the case of noisy tournaments, the
+top-performing strategies include strategies specifically designed for noisy
+tournaments. These are DBS, Evolved FSM 16 Noise 05, Evolved ANN 5 Noise 05, PSO
+Gambler 2 2 2 Noise 05, and Omega Tit For Tat~\cite{kendall2007iterated}. Omega
+TFT, a strategy designed to break the deadlocking cycles of \(CD\) and \(DC\)
+that TFT can fall into in noisy environments, places 10th. The rest of the top
+ranks are occupied by strategies that performed well in standard tournaments and
 deterministic strategies such as Spiteful Tit For Tat~\cite{prison}, Level
@@
 
-In contrast, the performance of the top ranked strategies in noisy environments
-when \(p_n\in [0, 1]\) is bimodal. The top strategies include strategies which
-decide their actions based on the cooperation to defection ratio, such as
-ShortMem~\cite{Andre2013}, Grumpy~\cite{axelrodproject} and
-e~\cite{axelrodproject}, and the Retaliate strategies which are designed to
-defect if the opponent has tricked them more often than a given percentage of the times that
-they have done the same. The bimodality of the \(r\) distributions is explained
-by Figure~\ref{fig:effect_of_noise} which demonstrates that the top 6 strategies
-were highly ranked due to the their performance in tournaments with \(p_n>0.5\),
-and that in tournaments with \(p_n<0.5\) they
-performed poorly. At a noisy level of \(0.5\) or greater, mostly cooperative strategies
-become mostly defectors and vice versa.
+The most effective strategies in probabilistic ending tournaments with \(p_e<
+0.1\) are a series of ensemble Meta strategies, trained strategies which
+performed well in standard tournaments, and Grudger~\cite{axelrodproject} and
+Spiteful Tit for Tat~\cite{prison}. The Meta strategies~\cite{axelrodproject}
+utilize a team of strategies and aggregate the potential actions of the team
+members into a single action in various ways.
 
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.92\textwidth]{../images/noise_effect.pdf}
-    \caption{Normalised rank \(r\) distributions for top 6 strategies in noisy tournaments over
-    the probability of noisy ($p_n$).}
-    \label{fig:effect_of_noise}
-\end{figure}
+Overall, the analysis reveals that dominating strategies in standard tournaments
+were those trained using reinforcement learning techniques. In standard
+tournaments, these dominating strategies exhibited a clear trend of being
+trained through reinforcement learning techniques. Additionally, in environments
+with a noise probability strictly less than 0.1, successful strategies were
+purposefully designed or trained to adapt to noisy conditions. Furthermore, in
+tournaments with probabilistic endings, the highly ranked strategies leaned
+towards defecting strategies and trained finite state automata, as demonstrated
+by the works of Ashlock et al.~\cite{Ashlock2006,Ashlock2014}. Their prominence
+in tournaments where the probability of the game ending after each turn exceeded
+0.1 underscored their effectiveness. Similarly, in probabilistic tournaments
+with \(p_e\) less than 0.1, the highly ranked strategies were characterized by
+their reliance on the behavior of others. Notably, from the comprehensive set of
+strategies considered, no strategy demonstrated consistent success in noisy
+environments unless the noise value was limited to less than 0.1.
 
-The most effective strategies in probabilistic ending
-tournaments with \(p_e< 0.1\) are a series of ensemble Meta strategies, trained strategies
-which performed well
-in standard tournaments, and Grudger~\cite{axelrodproject} and Spiteful Tit for
-Tat~\cite{prison}. The Meta strategies~\cite{axelrodproject} utilize a team of
-strategies and aggregate the potential actions of the team members into a single action
-in various ways. Figure~\ref{fig:probend_subset_results} indicates that these strategies
-performed well in any probabilistic ending tournament.
-
-In probabilistic ending tournaments with \(p_e \in [0, 1]\) the top ranks are
-mostly occupied by defecting strategies such as Better and Better, Gradual
-Killer, Hard Prober (all from~\cite{axelrodproject}), Bully (Reverse Tit For
-Tat)~\cite{Nachbar1992} and Defector, and a series of strategies based on finite
-state automata introduced by Daniel Ashlock and Wendy Ashlock: Fortress 3,
-Fortress 4 (both introduced in~\cite{Ashlock2006}), Raider~\cite{Ashlock2014}
-and Solution B1~\cite{Ashlock2014}. The success of defecting strategies in
-probabilistic ending tournaments is due to larger values of
-\(p_e\) which lead to shorter matches (the expected number of rounds is \(1 / p_e\)), so the
-impact of the PD being iterated is subdued. This is captured by the Folk
-Theorem~\cite{Fudenberg2009} as defecting strategies do better when the likelihood
-of the game ending in the next turn increases.
-This is demonstrated by Figure~\ref{fig:effect_of_probend}, which gives the
-distributions of \(r\) for the top 6 strategies in probabilistic ending tournaments
-over \(p_e\).
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.92\textwidth]{../images/folk_theorem.pdf}
-    \caption{Normalised rank \(r\) distributions for top 6 strategies in probabilistic ending tournaments
-    over $p_e$. The 6 strategies start of with a high median rank,
-    however, their ranked decreased as the the probability of the game ending
-    increased and at the point of \(p_e = 0.1\).}
-    \label{fig:effect_of_probend}
-\end{figure}
-
-The top performances in tournaments with both noise and a probabilistic ending
-and the top performances over the entire data set have the largest median values
-compared to the top rank strategies of the other tournament types,
-Figure~\ref{fig:probend_noise_results} and Figure~\ref{fig:overall_results}. The
-\(\bar{r}\) for the top strategy is approximately at 0.3, indicating that the
-most successful strategy can on average just place in the top 30\% of the
-competition.
-
-\begin{table}[!htbp]
-    \centering
-    \resizebox{.30\textwidth}{!}{
-    \input{performance_merged_table.tex}}
-    \caption{Top performances over all the tournaments. The top ranks include
-    strategies that have been previously mentioned. The set of Retaliate
-    strategies occupy the top spots followed by BackStabber and DoubleCrosser.
-    The distributions of the Retaliate strategies have no statistical
-    difference. PSO Gambler and Evolved HMM 5 are trained strategies introduced
-    in~\cite{Harper2017} and Nice Meta Winner and NMWE Memory One are strategies
-    based on teams. Grudger is a strategy from R. Axelrod's original tournament and
-    Forgetful Fool Me Once is based on the same approach as
-    Grudger.}\label{table:overall_results}
-\end{table}
-
-\begin{figure}[!htbp]
-        \centering
-        \includegraphics[width=.65\textwidth]{../images/performance_merged.pdf}
-        \caption{Normalised rank \(r\) distributions for best performed strategies in the data set~\cite{data}.
-        A lower value of \(\bar{r}\) corresponds to a more successful
-        performance.}
-        \label{fig:overall_results}
-\end{figure}
-
-On the whole, the analysis of this manuscript has shown that:
-
-\begin{itemize}
-    \item In standard tournaments the dominating strategies were
-    strategies that had been trained using reinforcement learning techniques.
-    \item In noisy environments where the noise probability strictly less than
-    0.1 was considered, the successful strategies were strategies specifically
-    designed or trained for noisy environments.
-    \item In probabilistic ending tournaments most of the highly ranked
-    strategies were defecting strategies and trained finite state automata, all
-    by the authors of~\cite{Ashlock2006, Ashlock2014}. These strategies ranked
-    high due to their performance in tournaments where the probability of the
-    game ending after each turn was bigger than 0.1.
-    \item In probabilistic tournaments with \(p_e\) less than 0.1 the highly
-    ranked strategies were strategies based on the behaviour of others.
-    \item From the collection of strategies considered here,  no strategy can be
-    consistently successful in noisy environments, except if the value of noise
-    is constrained to less than a 0.1.
-\end{itemize}
-
-Though there is not a single strategy that repeatably outranks all others in any
-of the distinct tournament types, or even across the tournament types, there
-are specific types of strategies have been repeatably ranked in the top ranks.
-These have been strategies that have been trained, strategies that retailiate,
-and strategies that would adapt their behaviour based on preassigned rules
-to achieve the highest outcome. These results contradict some of R. Axelrod's suggestions,
-and more specifically, the suggestions `Do not be clever' and `Do not be envious'.
-We dig deeper into the crucial strategy features for success in the following section.
+Though there is not a single strategy that consistently outranks all others in
+any of the distinct tournament types or even across the tournament types, there
+are specific types of strategies that have been repeatedly ranked in the top
+ranks. These include strategies that have been trained, strategies that
+retaliate, and strategies that adapt their behavior based on preassigned rules
+to achieve the highest outcome. These results contradict some of Axelrod's
+suggestions, and more specifically, the suggestions ``Do not be clever'' and
+``Do not be envious''. We delve deeper into the crucial strategy features for
+success in the following section.
 
@@
 
-\appendix
-
-\input{parameters_section}
-\input{correlation_section}
-\input{random_forest_evaluation}
-\input{regression_on_median_score}
-\input{strategies_list_section}
-
 \end{document}

### 2023-11-12 paper/perfomances_table.tex
drafts sections Data Collection and Top Ranked Strategies

--- 2020-02-03 paper/perfomances_table.tex
@@
-\begin{tabular}{lllllllllllll}
+\begin{tabular}{lllllllll}
 \toprule
-{} &                     Name & $ \bar\{r\}$  &                   Name & $ \bar\{r\}$  &                        Name & $ \bar\{r\}$  &               Name & $ \bar\{r\}$  &                       Name & $ \bar\{r\}$  &                 Name & $ \bar\{r\}$  \\
+{} &                     Name & \$\textbackslash bar\{r\}\$ &                       Name & \$\textbackslash bar\{r\}\$ &                       Name & \$\textbackslash bar\{r\}\$ &                       Name & \$\textbackslash bar\{r\}\$ \\
 \midrule
-0  &            Evolved HMM 5 &     0.007 &                 Grumpy &      0.14 &                         DBS &         0 &          Fortress4 &     0.013 &             Evolved FSM 16 &         0 &           Alternator &     0.304 \\
-1  &           Evolved FSM 16 &      0.01 &                    $ e$  &     0.194 &     Evolved FSM 16 Noise 05 &     0.008 &           Defector &     0.014 &    Evolved FSM 16 Noise 05 &     0.013 &               $ \textbackslash phi$  &      0.31 \\
-2  &     EvolvedLookerUp2 2 2 &     0.011 &         Tit For 2 Tats &     0.206 &      Evolved ANN 5 Noise 05 &     0.013 &  Better and Better &     0.016 &                       MEM2 &     0.027 &                  $ e$  &     0.312 \\
-3  &  Evolved FSM 16 Noise 05 &     0.017 &  Slow Tit For Two Tats &      0.21 &                 BackStabber &     0.024 &    Tricky Defector &     0.019 &              Evolved HMM 5 &     0.044 &                $ \textbackslash pi$  &     0.317 \\
-4  &        PSO Gambler 2 2 2 &     0.021 &           Cycle Hunter &     0.215 &               DoubleCrosser &     0.025 &          Fortress3 &     0.022 &       EvolvedLookerUp2 2 2 &     0.049 &    Limited Retaliate &     0.353 \\
-5  &              Evolved ANN &     0.029 &         Risky QLearner &     0.222 &               Evolved ANN 5 &     0.028 &     Gradual Killer &     0.025 &       Spiteful Tit For Tat &      0.06 &     Anti Tit For Tat &     0.354 \\
-6  &            Evolved ANN 5 &     0.034 &            Retaliate 3 &     0.229 &                 Evolved ANN &     0.038 &         Aggravater &     0.028 &           Nice Meta Winner &     0.068 &  Limited Retaliate 3 &     0.356 \\
-7  &        PSO Gambler 1 1 1 &     0.037 &          Cycler CCCCCD &     0.235 &        Spiteful Tit For Tat &     0.051 &             Raider &     0.031 &         NMWE Finite Memory &     0.069 &          Retaliate 3 &     0.356 \\
-8  &            Evolved FSM 4 &     0.049 &            Retaliate 2 &     0.239 &               Evolved HMM 5 &     0.051 &         Cycler DDC &     0.045 &         NMWE Deterministic &      0.07 &            Retaliate &     0.357 \\
-9  &         PSO Gambler Mem1 &      0.05 &        Defector Hunter &      0.24 &              Level Punisher &     0.052 &        Hard Prober &     0.051 &                    Grudger &      0.07 &          Retaliate 2 &     0.358 \\
-10 &                 Winner12 &      0.06 &              Retaliate &     0.242 &                   Omega TFT &     0.059 &         SolutionB1 &      0.06 &           NMWE Long Memory &     0.074 &  Limited Retaliate 2 &     0.361 \\
-11 &             Fool Me Once &     0.061 &    Hard Tit For 2 Tats &      0.25 &                Fool Me Once &     0.059 &      Meta Minority &     0.061 &  Nice Meta Winner Ensemble &     0.076 &             Hopeless &     0.368 \\
-12 &                      DBS &     0.071 &    Limited Retaliate 3 &     0.253 &  PSO Gambler 2 2 2 Noise 05 &     0.067 &              Bully &     0.061 &       EvolvedLookerUp1 1 1 &     0.077 &    Arrogant QLearner &     0.407 \\
-13 &            DoubleCrosser &     0.072 &               ShortMem &     0.253 &              Evolved FSM 16 &     0.078 &             EasyGo &     0.071 &            NMWE Memory One &      0.08 &    Cautious QLearner &     0.409 \\
-14 &              BackStabber &     0.075 &      Limited Retaliate &     0.257 &                  EugineNier &      0.08 &    Fool Me Forever &     0.071 &                   Winner12 &     0.085 &      Fool Me Forever &     0.418 \\
+0  &            Evolved HMM 5 &     0.007 &                       MEM2 &     0.061 &             Evolved FSM 16 &       0.0 &                   Defector &     0.006 \\
+1  &           Evolved FSM 16 &      0.01 &       Spiteful Tit For Tat &     0.063 &    Evolved FSM 16 Noise 05 &     0.013 &          Better and Better &     0.011 \\
+2  &     EvolvedLookerUp2\_2\_2 &     0.011 &           Nice Meta Winner &     0.066 &                       MEM2 &     0.027 &                 Aggravater &     0.014 \\
+3  &  Evolved FSM 16 Noise 05 &     0.017 &                    Grudger &     0.067 &              Evolved HMM 5 &     0.043 &                  Fortress4 &     0.021 \\
+4  &        PSO Gambler 2\_2\_2 &     0.022 &    Meta Winner Long Memory &     0.073 &       EvolvedLookerUp2\_2\_2 &     0.049 &            Tricky Defector &     0.038 \\
+5  &              Evolved ANN &     0.029 &                   Forgiver &     0.074 &       Spiteful Tit For Tat &     0.059 &    Meta Winner Long Memory &     0.049 \\
+6  &            Evolved ANN 5 &     0.034 &               Fool Me Once &     0.074 &           Nice Meta Winner &     0.069 &     Meta Winner Memory One &      0.05 \\
+7  &        PSO Gambler 1\_1\_1 &     0.037 &                Meta Winner &     0.075 &         NMWE Finite Memory &     0.069 &  Meta Winner Finite Memory &      0.05 \\
+8  &            Evolved FSM 4 &     0.049 &     Meta Winner Memory One &     0.076 &         NMWE Deterministic &      0.07 &     Meta Winner Stochastic &     0.051 \\
+9  &         PSO Gambler Mem1 &      0.05 &  Meta Winner Finite Memory &     0.077 &                    Grudger &      0.07 &  Meta Winner Deterministic &     0.052 \\
+10 &                 Winner12 &      0.06 &  Meta Winner Deterministic &     0.078 &           NMWE Long Memory &     0.074 &                Meta Winner &     0.053 \\
+11 &             Fool Me Once &     0.061 &         NMWE Deterministic &     0.087 &  Nice Meta Winner Ensemble &     0.076 &       Meta Winner Ensemble &     0.059 \\
+12 &                      DBS &     0.071 &           NMWE Long Memory &     0.087 &       EvolvedLookerUp1\_1\_1 &     0.077 &                  Fortress3 &      0.07 \\
+13 &            DoubleCrosser &     0.072 &         CollectiveStrategy &     0.087 &            NMWE Memory One &      0.08 &         CollectiveStrategy &     0.077 \\
+14 &              BackStabber &     0.075 &                   Defector &     0.089 &            NMWE Stochastic &     0.085 &                   Prober 3 &      0.08 \\
 \bottomrule

### 2023-11-12 paper/top_perfomances.tex
finalises top performances section
drafts sections Data Collection and Top Ranked Strategies

--- 2019-11-11 paper/top_perfomances.tex
@@
-\begin{tabular}{lggllggllr}
+% \midrule
+% & Name & $\bar{r}$ &                 Name & $\bar{r}$ &               Name & $\bar{r}$ &                 Name & $\bar{r}$ &                 Name & $\bar{r}$ &                 Name & $\bar{r}$ \\
+% \midrule
+% 0  &            Evolved HMM 5 &     0.007 &                 Grumpy &     0.140 &                         DBS &     0.000 &          Fortress4 &     0.013 &             Evolved FSM 16 &     0.000 &           Alternator &     0.304 \\
+% 1  &           Evolved FSM 16 &     0.010 &                    $e$ &     0.194 &     Evolved FSM 16 Noise 05 &     0.008 &           Defector &     0.014 &    Evolved FSM 16 Noise 05 &     0.013 &              $\phi$  &     0.310 \\
+% 2  &     EvolvedLookerUp2 2 2 &     0.011 &         Tit For 2 Tats &     0.206 &      Evolved ANN 5 Noise 05 &     0.013 &  Better and Better &     0.016 &                       MEM2 &     0.027 &                $e$   &     0.312 \\
+% 3  &  Evolved FSM 16 Noise 05 &     0.017 &  Slow Tit For Two Tats &     0.210 &                 BackStabber &     0.024 &    Tricky Defector &     0.019 &              Evolved HMM 5 &     0.044 &               $\pi$  &     0.317 \\
+% 4  &        PSO Gambler 2 2 2 &     0.021 &           Cycle Hunter &     0.215 &               DoubleCrosser &     0.025 &          Fortress3 &     0.022 &       EvolvedLookerUp2 2 2 &     0.049 &    Limited Retaliate &     0.353 \\
+% 5  &              Evolved ANN &     0.029 &         Risky QLearner &     0.222 &               Evolved ANN 5 &     0.028 &     Gradual Killer &     0.025 &       Spiteful Tit For Tat &     0.060 &     Anti Tit For Tat &     0.354 \\
+% 6  &            Evolved ANN 5 &     0.034 &            Retaliate 3 &     0.229 &                 Evolved ANN &     0.038 &         Aggravater &     0.028 &           Nice Meta Winner &     0.068 &  Limited Retaliate 3 &     0.356 \\
+% 7  &        PSO Gambler 1 1 1 &     0.037 &          Cycler CCCCCD &     0.235 &        Spiteful Tit For Tat &     0.051 &             Raider &     0.031 &         NMWE Finite Memory &     0.069 &          Retaliate 3 &     0.356 \\
+% 8  &            Evolved FSM 4 &     0.049 &            Retaliate 2 &     0.239 &               Evolved HMM 5 &     0.051 &         Cycler DDC &     0.045 &         NMWE Deterministic &     0.070 &            Retaliate &     0.357 \\
+% 9  &         PSO Gambler Mem1 &     0.050 &        Defector Hunter &     0.240 &              Level Punisher &     0.052 &        Hard Prober &     0.051 &                    Grudger &     0.070 &          Retaliate 2 &     0.358 \\
+% 10 &                 Winner12 &     0.060 &              Retaliate &     0.242 &                   Omega TFT &     0.059 &         SolutionB1 &     0.060 &           NMWE Long Memory &     0.074 &  Limited Retaliate 2 &     0.361 \\
+% 11 &             Fool Me Once &     0.061 &    Hard Tit For 2 Tats &     0.250 &                Fool Me Once &     0.059 &      Meta Minority &     0.061 &  Nice Meta Winner Ensemble &     0.076 &             Hopeless &     0.368 \\
+% 12 &                      DBS &     0.071 &    Limited Retaliate 3 &     0.253 &  PSO Gambler 2 2 2 Noise 05 &     0.067 &              Bully &     0.061 &       EvolvedLookerUp1 1 1 &     0.077 &    Arrogant QLearner &     0.407 \\
+% 13 &            DoubleCrosser &     0.072 &               ShortMem &     0.253 &              Evolved FSM 16 &     0.078 &             EasyGo &     0.071 &            NMWE Memory One &     0.080 &    Cautious QLearner &     0.409 \\
+% 14 &              BackStabber &     0.075 &      Limited Retaliate &     0.257 &                  EugineNier &     0.080 &    Fool Me Forever &     0.071 &                   Winner12 &     0.085 &      Fool Me Forever &     0.418 \\
+% \bottomrule
+% \end{tabular}
+
+\begin{tabular}{lggllggllggllr}
     \toprule
-& \multicolumn{2}{g}{Standard} & \multicolumn{2}{c}{Noisy} & \multicolumn{2}{g}{Probabilistic ending} &  \multicolumn{2}{c}{Noisy probabilistic ending} \\
+    & \multicolumn{2}{g}{Standard} & \multicolumn{2}{g}{Noisy (\(p_n < 0.5\))} & \multicolumn{2}{g}{Probabilistic ending (\(p_e < 0.1\))} &  \multicolumn{2}{c}{Noisy probabilistic ending} \\
+    \toprule
+    {} &                     Name & $\bar{r}$ &                       Name & $\bar{r}$ &                       Name & $\bar{r}$ &                       Name & $\bar{r}$ \\
     \midrule
-& Name & $\bar{r}$ &                 Name & $\bar{r}$ &               Name & $\bar{r}$ &                 Name & $\bar{r}$ \\
-\midrule
-0  &            Evolved HMM 5 &   0.00667 &                 Grumpy &   0.14020 &          Fortress4 &   0.01266 &           Alternator &   0.30370 \\
-1  &           Evolved FSM 16 &   0.00995 &                    $e$ &   0.19388 &           Defector &   0.01429 &               $\phi$ &   0.30978 \\
-2  &     EvolvedLookerUp2 2 2 &   0.01064 &         Tit For 2 Tats &   0.20617 &  Better and Better &   0.01587 &                  $e$ &   0.31250 \\
-3  &  Evolved FSM 16 Noise 05 &   0.01667 &  Slow Tit For Two Tats &   0.20962 &    Tricky Defector &   0.01875 &                $\pi$ &   0.31686 \\
-4  &        PSO Gambler 2 2 2 &   0.02143 &           Cycle Hunter &   0.21538 &          Fortress3 &   0.02174 &    Limited Retaliate &   0.35263 \\
-5  &              Evolved ANN &   0.02878 &         Risky QLearner &   0.22222 &     Gradual Killer &   0.02532 &     Anti Tit For Tat &   0.35431 \\
-6  &            Evolved ANN 5 &   0.03390 &            Retaliate 3 &   0.22887 &         Aggravater &   0.02778 &          Retaliate 3 &   0.35563 \\
-7  &        PSO Gambler 1 1 1 &   0.03704 &          Cycler CCCCCD &   0.23507 &             Raider &   0.03077 &  Limited Retaliate 3 &   0.35563 \\
-8  &            Evolved FSM 4 &   0.04891 &            Retaliate 2 &   0.23913 &         Cycler DDC &   0.04545 &            Retaliate &   0.35714 \\
-9  &         PSO Gambler Mem1 &   0.05036 &        Defector Hunter &   0.24038 &        Hard Prober &   0.05128 &          Retaliate 2 &   0.35767 \\
-10 &                 Winner12 &   0.06011 &              Retaliate &   0.24177 &         SolutionB1 &   0.06024 &  Limited Retaliate 2 &   0.36134 \\
-11 &             Fool Me Once &   0.06140 &    Hard Tit For 2 Tats &   0.25000 &      Meta Minority &   0.06077 &             Hopeless &   0.36842 \\
-12 &                      DBS &   0.07143 &               ShortMem &   0.25286 &              Bully &   0.06081 &    Arrogant QLearner &   0.40651 \\
-13 &            DoubleCrosser &   0.07200 &    Limited Retaliate 3 &   0.25316 &    Fool Me Forever &   0.07080 &    Cautious QLearner &   0.40909 \\
-14 &              BackStabber &   0.07519 &      Limited Retaliate &   0.25706 &             EasyGo &   0.07101 &      Fool Me Forever &   0.41764 \\
+    0  &            Evolved HMM 5 &     0.007 &                       MEM2 &     0.061 &             Evolved FSM 16 &       0.0 &                   Defector &     0.006 \\
+    1  &           Evolved FSM 16 &      0.01 &       Spiteful Tit For Tat &     0.063 &    Evolved FSM 16 Noise 05 &     0.013 &          Better and Better &     0.011 \\
+    2  &     EvolvedLookerUp2\_2\_2 &     0.011 &           Nice Meta Winner &     0.066 &                       MEM2 &     0.027 &                 Aggravater &     0.014 \\
+    3  &  Evolved FSM 16 Noise 05 &     0.017 &                    Grudger &     0.067 &              Evolved HMM 5 &     0.043 &                  Fortress4 &     0.021 \\
+    4  &        PSO Gambler 2\_2\_2 &     0.022 &    Meta Winner Long Memory &     0.073 &       EvolvedLookerUp2\_2\_2 &     0.049 &            Tricky Defector &     0.038 \\
+    5  &              Evolved ANN &     0.029 &                   Forgiver &     0.074 &       Spiteful Tit For Tat &     0.059 &    Meta Winner Long Memory &     0.049 \\
+    6  &            Evolved ANN 5 &     0.034 &               Fool Me Once &     0.074 &           Nice Meta Winner &     0.069 &     Meta Winner Memory One &      0.05 \\
+    7  &        PSO Gambler 1\_1\_1 &     0.037 &                Meta Winner &     0.075 &         NMWE Finite Memory &     0.069 &  Meta Winner Finite Memory &      0.05 \\
+    8  &            Evolved FSM 4 &     0.049 &     Meta Winner Memory One &     0.076 &         NMWE Deterministic &      0.07 &     Meta Winner Stochastic &     0.051 \\
+    9  &         PSO Gambler Mem1 &      0.05 &  Meta Winner Finite Memory &     0.077 &                    Grudger &      0.07 &  Meta Winner Deterministic &     0.052 \\
+    10 &                 Winner12 &      0.06 &  Meta Winner Deterministic &     0.078 &           NMWE Long Memory &     0.074 &                Meta Winner &     0.053 \\
+    11 &             Fool Me Once &     0.061 &         NMWE Deterministic &     0.087 &  Nice Meta Winner Ensemble &     0.076 &       Meta Winner Ensemble &     0.059 \\
+    12 &                      DBS &     0.071 &           NMWE Long Memory &     0.087 &       EvolvedLookerUp1\_1\_1 &     0.077 &                  Fortress3 &      0.07 \\
+    13 &            DoubleCrosser &     0.072 &         CollectiveStrategy &     0.087 &            NMWE Memory One &      0.08 &         CollectiveStrategy &     0.077 \\
+    14 &              BackStabber &     0.075 &                   Defector &     0.089 &            NMWE Stochastic &     0.085 &                   Prober 3 &      0.08 \\
     \bottomrule

### 2023-12-01 paper/main.tex
working on main paper for the special issue

@@
 \usepackage{soul}
+\usepackage{enumerate}
 \usepackage[table]{xcolor}
 %%%%%%%%%%%%%%%%%
+
+\newcommand{\colortext}[1]{\textcolor{blue}{#1}}
 
@@
 \newcommand{\numberofstrategies}{\input{unique_number_of_strategies.tex}}
-\def\axelrod{\texttt{Axelrod-Python }}
+\def\axelrod{\texttt{Axelrod-Python}}
+\def\TFT{\texttt{TFT}}
+\def\IPD{\texttt{IPD}}
 
@@
 introduction of the zero-determinant strategies, to the use of sophisticated learning
-structures such as neural networks, many new strategies have been introduced and tested
+structures such as neural networks. Many new strategies have been introduced and tested
 in a variety of tournaments and population dynamics. Typical results in the literature,
@@
 of conclusions. We analyze a large collection of \numberofstrategies
-strategies in \numberofalltournaments tournaments, present the top performing strategies across multiple
+strategies in thousands of tournaments, present the top performing strategies across multiple
 tournament types, and distill their salient features.
@@
 nevertheless there are several properties that heavily influence the best performing
-strategies. This refines the properties described by R. Axelrod in light of
+strategies. This refines the properties described by Axelrod in light of
 recent and more diverse opponent populations to: be nice, be provocable and generous,
@@
 we find that strategies perform best when their probability of cooperation
-matches the total tournament population's aggregate cooperation probabilities,
-or a proportion thereof in the case of noisy and probabilistically ending tournaments,
-and that the manner in which a strategy achieves the ideal cooperation rate is crucial.
-The features of high performing strategies help cast some light on why strategies such as Tit For Tat
-performed historically well in tournaments and why zero-determinant strategies
-typically do not fare well in tournament settings.
+matches the total tournament population's aggregate cooperation probabilities.
+The features of high performing strategies help cast some light on why
+strategies such as Tit For Tat performed historically well in tournaments and
+why zero-determinant strategies typically do not fare well in tournament
+settings. Furthermore, our findings have implications for the future training of
+autonomous agents. Understanding the crucial features for incorporation into
+these agents becomes paramount.
 \end{abstract}
+
+% or a proportion thereof in the case of noisy and probabilistically ending tournaments,
+% and that the manner in which a strategy achieves the ideal cooperation rate is crucial.
 
@@
 
-The Iterated Prisoner's Dilemma (IPD) is a repeated two player game that models
-behavioural interactions, specifically interactions where
-self-interest clashes with collective interest. At each turn of the game both
-players, simultaneously and independently, decide between cooperation (\(C\)) and
-defection (\(D\)), given memory of all prior interactions. The payoffs for each
-player, at each turn, is influenced by their own choice and the choice of the
-other player. The payoffs of the game are defined by:
+The Iterated Prisoner's Dilemma (\IPD) is a repeated two-player game that models
+behavioral interactions, specifically interactions where self-interest clashes
+with collective interest. In each turn of the game, both players simultaneously
+and independently decide between cooperation (\(C\)) and defection (\(D\)). This
+decision is made with the memory of all prior interactions. The payoffs for each
+player at each turn are influenced by their own choice, and the choice of the
+other player. To this end, the payoffs of the game are defined by,
 
@@
 \hline
-Cooperate (\(C\)) & \(R\) & \(S\) \\
+Cooperate (\(C\)) & \(R, R\) & \(S, T\) \\
 \hline
-Defect (\(D\)) & \(T\) & \(P\) \\
+Defect (\(D\)) & \(T, S\) & \(P, P\) \\
 \end{tabular}}
@@
 
-where typically \(T > R > P > S\) and \(2R > T + S\). The most common values used in
-the literature~\cite{Axelrod1981} are $R=3, P=1, T=5, S=0$. These values are also
-used in this work.
+where typically \(T > R > P > S\) and \(2R > T + S\). The most common values
+used in the literature~\cite{Axelrod1981} are \(R=3\), \(P=1\), \(T=5\),
+\(S=0\), and these are the values also used in this work.
 
-Conceptualising strategies and understanding the best way of playing the game
-has been of interest to the scientific community since the formulation of the
-game in 1950~\cite{Flood1958}. Following the computer tournaments of R. Axelrod in the
-1980's~\cite{Axelrod1980a, Axelrod1980b}, a strategy's performance in a round
-robin computer tournament became a common evaluation technique for newly designed
-strategies. Many tournaments have followed Axelrod's~\cite{Beaufils1997, Bendor1991,
-Harper2017, Kendall2007, Stephens2002, Stewart2012} and now the
-literature and various codebases contain hundreds of strategies.
+Conceptualizing strategies and understanding the best way to play the game have
+been of interest to the scientific community since the formulation of the game
+in 1950~\cite{Flood1958}. Following Axelrod's computer tournaments in the
+1980s~\cite{Axelrod1980a, Axelrod1980b}, round-robin computer tournaments became
+a common evaluation technique for newly designed strategies.
+The winner of both of Axelrod's tournaments~\cite{Axelrod1980a, Axelrod1980b}
+was the simple strategy Tit For Tat (\TFT{}). \TFT{} cooperates on the first turn
+and thereafter copies the previous action of its opponent, retaliating against
+defections with a defection and forgiving a defection if followed by
+cooperation. Axelrod concluded that the strategy's robustness was due to four
+properties, which he adapted into four suggestions for success in an \IPD{}
+tournament:
 
-The winner of both of R. Axelrod's tournaments~\cite{Axelrod1980a, Axelrod1980b}
-was the simple strategy Tit For Tat (TFT) which cooperates
-on the first turn and thereafter copies the previous action of its opponent,
-retailiating against defections with a defection, and forgiving a defection if followed
-by a cooperation. R. Axelrod concluded that the strategy's robustness was due to four
-properties, which he adapted into four suggestions on doing well in an IPD:
+\begin{enumerate}[(i)]
+    \item Do not be envious by striving for a payoff larger than the opponent's payoff.
+    \item Be ``nice''; Do not be the first to defect.
+    \item Reciprocate both cooperation and defection; Be provocable to retaliation and forgiveness.
+    \item Do not be too clever by scheming to exploit the opponent.
+\end{enumerate}
 
-\begin{itemize}
-    \item Do not be envious by striving for a payoff larger than the opponent's payoff
-    \item Be ``nice''; Do not be the first to defect
-    \item Reciprocate both cooperation and defection; Be provocable to retaliation and forgiveness
-    \item Do not be too clever by scheming to exploit the opponent
-\end{itemize}
+Forgiveness, in this context, is a strategy's ability to cooperate after a
+\(DC\) outcome to achieve mutual cooperation again. In environments without
+noise, \TFT{} would end up in \(DC\) only if it had received a defection and
+then retaliated. Subsequently, \TFT{} would forgive an opponent that apologizes
+(in a \(DC\) round) by returning to cooperation, as mutual cooperation is deemed
+better than mutual defection.
 
-Forgiveness is a strategy's ability to go from a \(DC\) to \(C\) aiming to achieve
-mutual cooperation again, the only way TFT would end up in \(DC\), in
-environments without noise, is if it had received a defection and then retaliated.
-Subsequently, TFT would forgive an opponent that apologises (in a \(DC\) round)
-by returning to cooperation, since mutual cooperation is better than mutual defection.
-As a result of the strategy's strong performance in both tournaments, and moreover in a
-series of evolutionary experiments~\cite{Axelrod1981}, TFT was often
-claimed to be a highly robust (and sometimes the most robust) strategy for the IPD.
+Due to the strategy's strong performance in both tournaments and a series of
+evolutionary experiments~\cite{Axelrod1981}, \TFT{} was often claimed to be a
+highly robust (and sometimes the most robust) strategy for the \IPD.
+There are strategies that have built upon \TFT{} and the reciprocity-based
+approach. In~\cite{Beaufils1997}, a strategy called Gradual was introduced,
+constructed to have the same qualities as those of \TFT{} with one
+addition. Gradual has a memory of the previous rounds of play in the game,
+recording the number of defections by the opponent and punishing them with a
+growing number of defections. It then enters a calming state in which it
+cooperates for two rounds. A strategy with the same intuition as Gradual is
+Adaptive Tit for Tat~\cite{tzafestas-2000a}. Adaptive Tit for Tat maintains a
+continually updated estimate of the opponent's behavior and uses this estimate
+to condition its future actions.
+Other research has built upon the limitations of \TFT. For example,
+in~\cite{Bendor1991, Donninger1986, Molander1985, Hammerstein1984}, it was shown
+that \TFT{} suffered in environments with noise. This was mainly due to the
+strategy being too provocable and its lack of generosity and contrition. Since
+\TFT{} immediately punishes a defection, in a noisy environment, it can get
+stuck in a repeated cycle of defections and cooperations. Some new strategies,
+more robust in tournaments with noise, were soon introduced, including Nice and
+Forgiving~\cite{Bendor1991}, Generous Tit For Tat~\cite{Nowak1992}, and Pavlov
+(aka Win Stay Lose Shift)~\cite{Nowak1993}, as well as later variants such as
+OmegaTFT \cite{kendall2007iterated}.
 
-There are strategies which have built upon TFT and the reciprocity based approach.
-In~\cite{Beaufils1997} a strategy called Gradual was introduced, constructed to have the
-same qualities as those of TFT with one addition. Gradual has a memory
-of the previous rounds of play of the game, recording the number of defections
-by the opponent and punishing them with a growing number of defections. It
-then enters a calming state in which it cooperates for two rounds. A
-strategy with the same intuition as Gradual is Adaptive Tit for
-Tat~\cite{tzafestas-2000a}. Adaptive Tit for Tat maintains a continually updated estimate of the
-opponent's behaviour and uses this estimate to condition its future actions.
+Finally, others introduced strategies deviating completely from the originally
+suggested properties of success. For example, a set of ``envious'' Iterated
+Prisoner's Dilemma (\IPD) strategies were introduced, called zero-determinant
+strategies (ZDs), in~\cite{Press2012}. These strategies attempt to force a
+linear relationship between stationary payoffs against other memory-one
+opponents, potentially ensuring that they receive a higher average payout. While
+ZDs were introduced with a small tournament in which some were reportedly
+successful \cite{Stewart2012}, this result has not generally held in future
+work~\cite{mathieu2017}. Furthermore, in~\cite{Harper2017}, a series of ``clever''
+strategies trained using reinforcement learning were introduced. These
+strategies were trained using lookup tables~\cite{Axelrod1987}, hidden Markov
+models~\cite{Harper2017}, and finite-state automata~\cite{Miller1996}, on
+on a set of 170 strategies.
 
-Other work has built upon the limitations of TFT, and in some cases have shown
-that suggestions made by R. Axelrod did not necessarily apply in alternative environmental settings.
-In~\cite{Bendor1991, Donninger1986, Molander1985, Hammerstein1984} it was shown
-that TFT suffered in environments with noise. This was
-mainly due to the strategy being too provocable and its lack of generosity and contrition. Since TFT immediately
-punishes a defection, in a noisy environment it can get stuck in a
-repeated cycle of defections and cooperations. Some new strategies, more
-robust in tournaments with noise, were soon introduced, including
-Nice and Forgiving~\cite{Bendor1991}, Generous Tit For Tat~\cite{Nowak1992},
-and Pavlov (aka Win Stay Lose Shift)~\cite{Nowak1993}, as well as later
-variants such as OmegaTFT \cite{kendall2007iterated}. The introduction of a new strategy
-is often accompanied by a claim that the new strategy is the best known, despite
-only being tested against a small number of opponents or against specific classes of
-opponents not necessarily representative of all possible or all published strategies.
-The lack of testing against formally defined strategies and tournament winners
-is understandable given the effort required to implement the hundreds of published IPD strategies.
-Implementing prior strategies faithfully is often extremely difficult or
-impossible due to insufficient descriptions and lack of published
-implementations or code.
-This calls into question any claims of superiority or robustness of newly introduced strategies.
+One thing that has remained the same is that the introduction of a new strategy
+is often accompanied by a claim that the new strategy is the best performing
+strategy for the \IPD, often without extensive testing against a broad spectrum
+of opponents or representative classes of opponents. This lack of comprehensive
+testing against formally defined strategies and tournament winners is
+justified given the substantial effort required to implement the numerous
+published \IPD{} strategies. The accuracy of implementing prior strategies is
+often hindered by insufficient descriptions and a dearth of published
+implementations or code. Despite these challenges, the absence of thorough
+testing raises concerns about claims regarding the superiority or robustness of
+newly introduced strategies.
 
-A set of envious IPD strategies were introduced called zero-determinant strategies (ZDs)
-in~\cite{Press2012}. These strategies attempt to force a linear relationship between
-stationary payoffs against other memory-one opponents, potentially ensuring that they
-receive a higher average payout. While ZDs were introduced with a small tournament in
-which some were reportedly successful \cite{Stewart2012}, this result has not generally
-held in future work. In~\cite{Harper2017} a series of strategies trained using
-reinforcement learning were introduced, and a tournament containing over 200 strategies
-featured no ZDs ranking in top spots. Instead, the top ranked strategies
-were a set of ``clever'' (in the sense of R. Axelrod's characteristics) trained
-strategies based on lookup tables~\cite{Axelrod1987}, hidden Markov
-models~\cite{Harper2017}, and finite state automata~\cite{Miller1996}.
-Similarly, in \cite{mathieu2017}, a set of evolutionarily-trained strategies,
-and a pre-selected set of known strategies, outperformed a collection of 12 ZDs.
-
-Though only select pieces of work have been discussed, there is a broad collection
-of strategies in the literature, and new strategies and competitions are
-published frequently~\cite{Glynatsi2019}. The question, however, still remains
-the same: what is the best way to play the game?
-
-Compared to other works, where typically a few selected or introduced strategies
-are evaluated on a small number of tournaments and/or small number of opponents,
-this manuscript evaluates the performance of \numberofstrategies
-strategies in \numberofalltournaments tournaments. Furthermore, a large portion
-of the strategies used in this manuscript are drawn from known and named strategies
-in IPD literature, including many previous tournament winners,
-in contrast to other work that may have randomly generated many essentially arbitrary
-strategies (typically restrained to a class such as memory-one strategies,
-or those of a certain structural form such as finite state machines or deterministic
-memory-two strategies). Additionally, our tournaments come in a
-number of variations including standard tournaments emulating R. Axelrod's original tournaments,
-tournaments with noise, probabilistic match length, and both noise and probabilistic match length.
-This diversity of strategies and tournament types yields new insights and tests
+In this paper we evaluate the performance of a significant number of \IPD{}
+strategies across a diverse array of tournaments. Many of the strategies used in
+our analysis are drawn from well-known and named strategies in \IPD{} literature,
+including previous tournament winners. This contrasts with other work that may
+have randomly generated essentially arbitrary strategies, often constrained to
+specific classes such as memory-one strategies or those of a certain structural
+form like finite state machines or deterministic memory-two strategies.
+Furthermore, our tournaments encompass various variations, including standard
+tournaments resembling Axelrod's original ones, tournaments with noise,
+probabilistic match length, and both noise and probabilistic match length. This
+diversity in strategies and tournament types provides new insights and tests
 earlier claims in alternative settings against known powerful strategies.
 
-The later part of the paper evaluates the impact of various strategy features
-on the performance of the strategies using standard statistical and machine learning techniques. These
-features include measures regarding a strategy's behaviour and measures regarding
-the tournaments. This rigorous analysis reinforces the discussion started by R. Axelrod
-and concludes that the properties of a successful strategy in the IPD are:
+It is important to note that we do not assert the existence of a single
+best-performing strategy across all tournaments or tournament types. On the
+contrary, our work demonstrates that such a strategy does not exist. The primary
+objective of this paper, presented in the latter parts of the paper, is to
+continue the discussion on the properties of successful strategies, a
+conversation started by Axelrod. 
+The results of our analysis conclude that the properties of a successful
+strategy in the Iterated Prisoner's Dilemma (\IPD{}) are:
 
-\begin{itemize}
-    \item \st{Do not be envious} Be a little bit envious
+\begin{enumerate}[(i)]
+    \item Be a little bit envious
     \item Be ``nice'' in non-noisy environments or when game lengths are longer
@@
     Be provocable in tournaments with short matches, and generous when matches are longer
-    \item \st{Do not be too clever} It's ok to be clever
+    \item  It's ok to be clever
     \item Adapt to the environment; Adjust to the mean population cooperation
-\end{itemize}
+\end{enumerate}
 
-The different tournament types as well as the data collection, made
-possible due to an open source library called Axelrod-Python (APL),
-are covered in Section~\ref{section:data_collection}. The raw and processed data
-sets have been made publicly available~\cite{data, raw_data} and can be used
-for further analysis and insights.
-Section~\ref{section:top_performances}, focuses on the best performing
-strategies for each type of tournament and overall.
-Section~\ref{section:evaluation_of_performance}, explores the traits which
-contribute to good performance, and finally the results are summarised in
-Section~\ref{section:conclusion}. This manuscripts uses several parameters,
-introduced in the following sections. The full set of
-parameters and their definitions are given in Appendix~\ref{app:parameters}.
+We believe that the discussion on the properties of winning strategies holds
+significant importance. It aims to provide guidance to researchers designing new
+strategies and those training strategies. Moreover, conducting a similar
+analysis can shed light on already trained strategies, aiding in understanding
+the key features they have autonomously developed during their training
+processes.
+% ToDO: Not sure if this is enough to justify how our work is important for AI.
+% It would be nice to have a sentence or two since it fits the special issue
+% theme.
+
+The rest of the paper is organized as follows. In
+section~\ref{section:data_collection}, we describe the data collection process.
+In subsection~\ref{section:top_performances}, we present the best performing
+strategies for each type of tournament.
+Subsection~\ref{section:evaluation_of_performance} explores the traits that
+contribute to good performance, and in
+subsection~\ref{section:winning_features}, we focus on the features of the
+winners of the tournaments. Finally, the results are summarized in
+section~\ref{section:conclusion}. This manuscript introduces several parameters,
+which are discussed in the following sections; the full set of parameters and
+their definitions are also provided in the Supplementary Material.
 
@@
 
-The data set generated for this manuscript was created using \axelrod version 3.0.0.
-\axelrod enables the simulation of Iterated Prisoner's Dilemma
-computer tournaments and contains an extensive list of strategies. Most of these
+The data collection of various types of tournaments and the use of different
+strategies are made possible due to an open-source library called \axelrod{}~\cite{axelrodproject}
+(version 3.0.0). \axelrod{} enables the simulation of \IPD{}
+tournaments and contains an extensive list of strategies. Most of these
 strategies are described in the literature, with a few exceptions contributed
-specifically to the package. In this paper, we use a total of \numberofstrategies
-strategies. You can find a list of these strategies in the Supplementary Material.
+specifically to the package. In this paper, we use a total of
+\numberofstrategies strategies, which can be found in the Supplementary
+Material. The package supports several tournament types, and this work considers
+standard, noisy, probabilistic ending, and noisy probabilistic ending
+tournaments.
 
-The package supports several tournament types, and this work considers standard,
-noisy, probabilistic ending, and noisy probabilistic ending tournaments.
 {\it Standard tournaments} are similar to Axelrod's well-known
@@
 in each turn, there is a probability \(p_n\) that a player's action is
-flipped.
-{\it Probabilistic ending tournaments} consist of \(N\) strategies, and
-after each turn, a match between strategies ends with a given probability
+flipped. Compared to these two tournaments, in 
+{\it probabilistic ending tournaments} the number of turns is not fixed. Instead,
+a match between strategies ends with a given probability
 \(p_e\).
@@
 set of repetitions, not by the number of wins.
+
 The process of collecting tournament results is outlined in
-Algorithm~\ref{algorithm:data_generation}. For each trial, we choose a random
-size \(N\) is selected, and a random list of \(N\) strategies from the
-\numberofstrategies available. Subsequently, standard, noisy, probabilistic
-ending, and noisy probabilistic ending tournaments are conducted for the
-selected list of strategies. The parameters for the tournaments, as well as the
-number of repetitions, are chosen once for each trial.
+Algorithm~\ref{algorithm:data_generation}. For each trial, a random size \(N\)
+is selected, and a random list of \(N\) strategies from the \numberofstrategies
+available. Subsequently, one standard, one noisy, one probabilistic ending, and
+one noisy probabilistic ending tournament are conducted for the selected list of
+strategies. The parameters for the tournaments, as well as the number of
+repetitions, are chosen once for each trial. We have run a total of
+\uniquenumberofseeds trials of Algorithm~\ref{algorithm:data_generation}. For
+each trial, we collect the results for four different tournaments, resulting in
+a total of \numberofalltournaments $(\uniquenumberofseeds \times 4)$ tournament
+results. Each tournament outputs a result summary in the form of
+Table~\ref{table:output_result}.
 
@@
 
-We have run a total of \uniquenumberofseeds trials of
-Algorithm~\ref{algorithm:data_generation}. For each trial, we collect the
-results for four different tournaments, resulting in a total of
-\numberofalltournaments $(\uniquenumberofseeds \times 4)$ tournament results.
-Each tournament outputs a result summary in the form of
-Table~\ref{table:output_result}. Each strategy has participated, on average, in
-5154 tournaments of each type. The strategy with the maximum participation in
-each tournament type is Inverse Punisher with 5639 entries. The strategy with
-the minimum entries is EvolvedLookerUp 1 1 1, which was selected in 4693 trials.
-During the data collection process, we allowed the probabilities of noise and
-tournament ending to vary between 0 and 1. However, commonly used values for
-these probabilities are \(p_n < 0.5\) and \(p_e < 0.1\) (for more details, see the
-Supplementary Material). Therefore, in this context, we will focus on these
-subsets for the three tournament types: noisy, probabilistic ending, and noisy
-probabilistic ending. The results presented here pertain to these subsets.
-Specifically, there are a total of 5650, 1134, and 565 runs for each of the
-three tournament types, respectively. We also provide an analysis of the paper
-considering the entire datasets, and these results are presented in the
-Supplementary Material.
-
 \newcolumntype{g}{>{\columncolor{Gray}}c}
-\begin{table}[!htbp]
+\begin{table}[b]
     \begin{center}
@@
 
-\section{Top ranked strategies}\label{section:top_performances}
+During the data collection process, the probabilities of noise (\(p_n\)) and
+tournament ending (\(p_e\)) were allowed to take values between 0 and 1.
+However, commonly used values for these probabilities are \(p_n \leq 0.1\) and
+\(p_e \leq 0.1\). This is to make the results more interpretable. For example,
+consider a strategy competing in an environment with \(p_n > 0.1\). In cases
+with a high value of noise, most of the actions the strategy takes are the
+complete opposite of what the strategy is designed to do. Therefore, we will
+focus on the tournaments for which \(p_n \leq 0.1\) and \(p_e \leq 0.1\). Thus,
+the results presented here pertain to subsets of the noisy and probabilistic
+ending tournaments. Specifically, the results rely on 1150 tournaments with
+noise, 1134 tournaments with a probabilistic ending, and 117 tournaments with
+both noise and a probabilistic ending. We also provide an analysis of the paper
+considering the entire datasets, and these results are presented in the
+Supplementary Material. The general results of the analysis are not affected by
+the restriction of the noise and probabilistic ending probabilities.
+%ToDo: Do we need to justify better why we only consider tournaments with
+%noisy and ending probabilities less than 0.1?
+
+\section{Results}
+\subsection{Top ranked strategies across tournaments}\label{section:top_performances}
 
 A strategy has participated in multiple tournaments of each type, and to
-evaluate its overall performance, we introduce a measure called the {\textit
-normalized rank}. In each tournament, the strategies receive a rank, where 0
+evaluate its overall performance, we introduce a measure called the {\it
+normalized rank}. In each tournament, the strategies receive a rank (\(R\)), where 0
 denotes that the strategy was the winner, and \(N-1\) indicates that the
@@
 
-For example, let's consider the well-known strategies Tit For Tat and
-Gradual. Each strategy participated in several tournaments of each type (see
-Figure~\ref{fig:normalised_rank_distributions}).
-We show the distribution of the ranks of these
-strategies in each of the four tournaments. We can observe that in tournaments
-with the presence of noise, Tit For Tat has a normally distributed normalized
-rank around 1/2. In tournaments without noise, the strategy performs better,
-achieving its best performance in probabilistic ending tournaments with a median
-normalized rank of 0.298.
-In comparison, Gradual's performance has longer tails, indicating that there
-were tournaments where the strategy performed very well or very poorly. Overall,
-Gradual achieves a lower median rank, signifying that it performs better than
-Tit For Tat except in the case of noisy and probabilistic ending tournaments.
+For example, let's consider the well-known strategies \TFT{} and Gradual. Each
+strategy participated in several tournaments of each type. In
+Figure~\ref{fig:normalised_rank_distributions} we show the distribution of the
+normalised ranks of these strategies in each of the four tournaments. We can
+observe that \TFT{} has a normally distributed normalized rank. In comparison,
+Gradual's performance has longer tails, indicating that there were tournaments
+where the strategy performed very well or very poorly. Overall, Gradual achieves
+a lower median rank, signifying that it performs better than \TFT{} except in
+the case of noisy and probabilistic ending tournaments.
 
-\begin{figure}[h]
+\begin{figure}[!htbp]
     \centering
@@
     \caption{\textbf{Examples of normalized rank distributions for two
-    strategies, Tit For Tat and Gradual.} We plot the distributions of \(r\) for
-    the two strategies in the four tournament types. As a reminder, lower values
-    of \(r\) correspond to better performances. In each plot, we also show the
-    number of data points. Both strategies participated in a similar number of
-    tournaments. Based on the median rank, which we use in this work to define
-    overall performance, Tit For Tat performs best in probabilistic ending
-    tournaments, whereas Gradual was in standard tournaments. The best
-    performance of the Gradual strategy has been in standard tournaments where
-    it achieved a \(\bar{r}\) of 0.34.}
+    strategies, \TFT{} and Gradual.} We plot the distributions of \(r\) for the
+    two strategies in the four tournament types. As a reminder, lower values of
+    \(r\) correspond to better performances. The top left quadrant of each plot
+    shows the distribution for standard tournaments (fixed number of turns and
+    no noise). The top right quadrant shows the distribution for noisy
+    tournaments (fixed number of turns and noise). The bottom left quadrant
+    shows the distribution for probabilistic ending tournaments (no noise and
+    probabilistic ending). Finally, the bottom right quadrant shows the
+    distribution for noisy probabilistic ending tournaments (noise and
+    probabilistic ending). In each quadrant, we also show the number of data
+    points. Both strategies participated in a similar number of tournaments.
+    Based on the median rank, which we use in this work to define overall
+    performance, \TFT{} performs best in probabilistic ending tournaments,
+    whereas Gradual was in standard tournaments.}
     \label{fig:normalised_rank_distributions}
@@
 
-\begin{figure}[t]
+\begin{figure}[!htbp]
     \centering
-    \includegraphics[width=.8\textwidth]{../images/top_performers.pdf}
-    \caption{\(r\) distributions of the top 15 strategies in different
-    environments. A lower value of \(\bar{r}\) corresponds to a more successful
+    \includegraphics[width=\textwidth]{../images/top_performers.pdf}
+    \caption{\textbf{\(r\) distributions of the top 15 strategies in different
+    environments.} A lower value of \(\bar{r}\) corresponds to a more successful
     performance. A strategy's \(r\) distribution skewed towards zero indicates
     that the strategy ranked highly in most tournaments it participated in. Most
-    distributions are skewed towards zero except the distributions with
-    unrestricted noise, supporting the conclusions from
-    Table~\ref{table:top_performances}.}\label{fig:r_distributions}
+    distributions are skewed towards zero.}\label{fig:r_distributions}
 \end{figure}
@@
 \newcolumntype{g}{>{\columncolor{Gray}}l}
-\begin{table}[t]
+\begin{table}[!htbp]
     \begin{center}
@@
 ranks indicate that trained strategies perform well in a variety of
-environments, but so do simple deterministic strategies. The normalised medians
-are close to 0 for most environments, except environments with noise not
-restricted to 0.1 regardless of the number of turns. Noisy and noisy probabilistic
-ending tournaments have the highest medians.}
+environments, but so do simple deterministic strategies. For noisy tournaments
+DBS is the top ranked strategy with \(\bar{r}=0\), thus DBS won every tournament
+it participated in. The same for Evolved FSM 16 Noise 05 in probabilistic ending.}
 \label{table:top_performances}
@@
 for the top-ranked strategies can be found in Figure~\ref{fig:r_distributions}.
-In standard tournaments, 10 out of the 15 top strategies were introduced
-in~\cite{Harper2017}. These strategies are based on finite state automata (FSM),
-hidden Markov models (HMM), artificial neural networks (ANN), lookup tables
-(LookerUp), and stochastic lookup tables (Gambler). They have been trained using
-reinforcement learning algorithms (evolutionary and particle swarm algorithms)
-to perform well against a subset of the strategies in \axelrod in a standard
-tournament. Thus, their performance in the specific setting was anticipated,
-although still noteworthy given the random sampling of tournament participants.
-DoubleCrosser and BackStabber, both from the \axelrod, use the number of turns and
-are set to defect in the last two rounds. These strategies can be characterized
-as “cheaters” because their source code allows them to know the number of turns
-(unless the match has a probabilistic ending). These strategies were expected to
-not perform as well in tournaments where the number of turns is not specified.
-Finally, Winner 12~\cite{mathieu2017} and DBS~\cite{Au2006} are both from the
-literature. DBS is a strategy specifically designed for noisy environments;
-however, it ranks highly in standard tournaments as well. Similarly, the
-fourth-ranked player, Evolved FSM 16 Noise 05, was trained for noisy tournaments
-yet performs well in standard tournaments.
+
+In standard tournaments dominating strategies were those
+trained using reinforcement learning techniques. 10 out of the 15 top strategies
+were introduced in~\cite{Harper2017}. These strategies are based on finite state
+automata (FSM), hidden Markov models (HMM), artificial neural networks (ANN),
+lookup tables (LookerUp), and stochastic lookup tables (Gambler). They have been
+trained using reinforcement learning algorithms (evolutionary and particle swarm
+algorithms) to perform well against a subset of the strategies in \axelrod{} in a
+standard tournament. Thus, their performance in the specific setting was
+anticipated, although still noteworthy given the random sampling of tournament
+participants. DoubleCrosser and BackStabber, both from the \axelrod, use the
+number of turns and are set to defect in the last two rounds. These strategies
+can be characterized as “cheaters” because their source code allows them to know
+the number of turns (unless the match has a probabilistic ending). These
+strategies were expected to not perform as well in tournaments where the number
+of turns is not specified. Finally, Winner 12~\cite{mathieu2017} and
+DBS~\cite{Au2006} are both from the literature. DBS is a strategy specifically
+designed for noisy environments; however, it ranks highly in standard
+tournaments as well. Similarly, the fourth-ranked player, Evolved FSM 16 Noise
+05, was trained for noisy tournaments yet performs well in standard tournaments.
 
@@
 
-The most effective strategies in probabilistic ending tournaments with \(p_e<
-0.1\) are a series of ensemble Meta strategies, trained strategies which
-performed well in standard tournaments, and Grudger~\cite{axelrodproject} and
-Spiteful Tit for Tat~\cite{prison}. The Meta strategies~\cite{axelrodproject}
-utilize a team of strategies and aggregate the potential actions of the team
-members into a single action in various ways.
+Furthermore, in tournaments with probabilistic endings, the highly ranked
+strategies leaned towards defecting strategies and trained finite state
+automata, as demonstrated by the works of Ashlock et
+al.\cite{Ashlock2006,Ashlock2014}. The most effective strategies in
+probabilistic ending tournaments are also a series of ensemble Meta strategies,
+trained strategies that performed well in standard tournaments, and
+Grudger\cite{axelrodproject} and Spiteful Tit for Tat~\cite{prison}. The Meta
+strategies~\cite{axelrodproject} utilize a team of strategies and aggregate the
+potential actions of the team members into a single action in various ways.
 
-Overall, the analysis reveals that dominating strategies in standard tournaments
-were those trained using reinforcement learning techniques. In standard
-tournaments, these dominating strategies exhibited a clear trend of being
-trained through reinforcement learning techniques. Additionally, in environments
-with a noise probability strictly less than 0.1, successful strategies were
-purposefully designed or trained to adapt to noisy conditions. Furthermore, in
-tournaments with probabilistic endings, the highly ranked strategies leaned
-towards defecting strategies and trained finite state automata, as demonstrated
-by the works of Ashlock et al.~\cite{Ashlock2006,Ashlock2014}. Their prominence
-in tournaments where the probability of the game ending after each turn exceeded
-0.1 underscored their effectiveness. Similarly, in probabilistic tournaments
-with \(p_e\) less than 0.1, the highly ranked strategies were characterized by
-their reliance on the behavior of others. Notably, from the comprehensive set of
-strategies considered, no strategy demonstrated consistent success in noisy
-environments unless the noise value was limited to less than 0.1.
+While no single strategy consistently outperforms all others in any of the
+distinct tournament types or across various tournament types, certain types of
+strategies consistently achieve top rankings. These include strategies that have
+undergone training, those that retaliate, and those that adapt their behavior
+based on preassigned rules to optimize outcomes. These findings challenge some
+of Axelrod's suggestions, particularly the advice to ``not be clever'' and ``not
+be envious''.
 
-Though there is not a single strategy that consistently outranks all others in
-any of the distinct tournament types or even across the tournament types, there
-are specific types of strategies that have been repeatedly ranked in the top
-ranks. These include strategies that have been trained, strategies that
-retaliate, and strategies that adapt their behavior based on preassigned rules
-to achieve the highest outcome. These results contradict some of Axelrod's
-suggestions, and more specifically, the suggestions ``Do not be clever'' and
-``Do not be envious''. We delve deeper into the crucial strategy features for
-success in the following section.
+\subsection{The effect of strategy features on performance}\label{section:evaluation_of_performance}
 
-\section{Evaluation of performance}\label{section:evaluation_of_performance}
-
-For each strategy, for each tournament we have a variety of features, described in
-Table~\ref{table:manual_features}. These features are measures regarding a
-strategy's behaviour from the tournaments the strategies competed in as well as
-intrinsic properties such as whether a strategy is deterministic or stochastic.
+For each strategy, we have a variety of features as described in
+Table~\ref{table:manual_features}. These features capture measures related to a
+strategy's behavior in the tournaments it competed in, as well as intrinsic
+properties, such as whether a strategy is deterministic or stochastic. The
+correlation coefficients between the features for performance evaluation, the
+median score and the median normalised rank are given by
+Table~\ref{table:correlations}. The correlation coefficients between all
+features have also been calculated and a graphical representation can be found
+in the Supplementary Material.
 
@@
     \end{center}
-    \caption{The features which are included in the performance evaluation
-    analysis. Stochastic, makes use of length and makes use of game are APL
+    \caption{\textbf{Included features for performance evaluation analysis.}
+    Stochastic, makes use of length and makes use of game are APL
     classifiers that determine whether a strategy is stochastic or deterministic,
@@
     no extortionate behaviour at all whereas a value of 0 indicates that a
-    strategy is behaving as a ZDs. The rest of the features considered are the $CC$
+    strategy is behaving as a ZDs. The
+    memory usage of strategies is the number of rounds of play used by the strategy
+    when deciding on an action,  divided by the number of turns in each match. For
+    example, Winner12 uses the previous two rounds of play, and if participating in
+    a match with 100 turns its memory usage would be 2/100. For strategies with an
+    infinite memory size, for example Evolved FSM 16 Noise 05, memory usage is equal
+    to 1. Note that for tournaments with a probabilistic ending the number of turns
+    was not collected, so the memory usage feature is not used for probabilistic
+    ending tournaments. The rest of the features considered are the $CC$
     to $C$, $CD$ to $C$, $DC$ to $C$, and $DD$ to $C$ rates as well as
@@
 \end{table}
-
-The memory usage of strategies is the number of
-rounds of play used by the strategy divided by the number of turns in each match.
-For example, Winner12 uses the previous two rounds of play, and if participating
-in a match with 100 turns its memory usage would be 2/100.
-For strategies with an infinite memory size, for example Evolved
-FSM 16 Noise 05, memory usage is equal to 1.
-Note that for tournaments with a probabilistic
-ending the number of turns was not collected, so the memory usage feature is not
-used for probabilistic ending tournaments.
-
-The correlation coefficients between the features of
-Table~\ref{table:manual_features} the median score and the median normalised
-rank are given by Table~\ref{table:correlations}. The correlation coefficients
-between all features of Table~\ref{table:manual_features} have been calculated
-and a graphical representation can be found in the
-Appendix~\ref{app:correlations}.
 
@@
 defection, that is not retaliating, is associated to lesser overall success in terms of normalised rank.
-Figure~\ref{fig:rates_of_winners_in_standard_tournaments} confirms that the
-winners of standard tournaments always cooperate after a mutual cooperation and
-almost always defect after a mutual defection.
+Compared to standard tournaments, in both noisy and noisy probabilistic ending
+tournaments the higher the rates of cooperation the lower a strategy's success
+and median score. A strategy would not want to cooperate more than both
+the mean and median cooperator in such settings. In probabilistic ending
+tournaments, the cooperation rate of the winners and it's relative comparison
+to the cooperation rates of the tournament have no effect. The only features
+that have an effect are the $CD$ to $C$ rate, which is the tendency of a strategy
+to forgive and the SSE rate have a positivist effect on the normalised rank.
 
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.8\textwidth]{../images/rates_of_winners_in_standard_tournaments.pdf}
-    \caption{Distributions of $CC$ to $C$ and $DD$ to $C$ for the winners in
-    standard tournaments.}\label{fig:rates_of_winners_in_standard_tournaments}
-\end{figure}
-
-Compared to standard tournaments, in both noisy and in probabilistic ending
-tournaments the higher the rates of cooperation the lower a strategy's success
-and median score. A strategy would want to cooperate less than both
-the mean and median cooperator in such settings. In probabilistic ending
-tournaments the correlation coefficients have larger values, indicating a
-stronger effect. Thus a strategy will be punished more by its cooperative
-behaviour in probabilistic ending environments, supporting the results of
-Section~\ref{section:evaluation_of_performance}
-as well. The distributions of the $C_r$ of the winners in
-both tournaments are given by Figure~\ref{fig:c_r_distributions}. It confirms
-that the winners in noisy tournaments cooperated less than 35\% of the time
-and in probabilistic ending tournaments less than 10\%.
-In noisy probabilistic ending tournaments and over all the tournaments' results,
-the only features that had a moderate effect are $C_r/C_{\text{mean}},
-C_r/C_{\text{max}}$ and $C_r$. In such environments cooperative behaviour
-appears to be punished less than in noisy and probabilistic ending
-tournaments.
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=.8\textwidth]{../images/c_r_winners_tournaments.pdf}
-    \caption{$C_r$ distributions of the winners in noisy and in probabilistic
-    ending tournaments.}\label{fig:c_r_distributions}
-\end{figure}
-
-A multivariate linear regression has been fitted to model the relationship between
-the features and the normalised rank. Based on the graphical representation of
-the correlation matrices given in Appendix~\ref{app:correlations} several of the
-features are highly correlated and have been removed
-before fitting the linear regression model. The features included are given
-by Table~\ref{table:linear_regression} alongside their corresponding \(p\) values
-in the distinct tournaments and their regression coefficients.
+A multivariate linear regression has been fitted to model the relationship
+between the features and the normalised rank. Based on the graphical
+representation of the correlation matrices given in Supplementary Information
+several of the features are highly correlated and have been removed before
+fitting the linear regression model. The features included are given by
+Table~\ref{table:linear_regression} alongside their corresponding \(p\) values
+in the distinct tournaments and their regression coefficients. The rate $CD$ to
+$C$ has a positively statistically significant effect on the normalized rank,
+across all tournament types. This suggests that forgiveness tends to lower one's
+performance. In the case of probabilistic ending tournaments, the coefficient of
+the $CD$ to $C$ rate is the highest, indicating that one is more harshly
+``punished'' when showing forgiveness. Similarly, the SEE error rate has a
+positive effect on the normalized rank, suggesting that being extortionate pays
+off, especially in noisy tournaments. The measures of cooperation, $C_r$ and
+$C_r / C_{\text{max}}$, also exhibit a significant effect. In noisy
+probabilistic ending tournaments, this effect is positive; however, the
+coefficient is very close to zero. In other tournament types, the effect is
+negative, indicating that one should aim to be less cooperative than the mean
+cooperator of the tournament. However, we cannot interpret the result as
+suggesting that a strategy should be as uncooperative as possible.
 
 \newcolumntype{g}{>{\columncolor{Gray}}c}
-\begin{table}[h]
+\begin{table}[!htbp]
     \begin{center}
@@
     \end{center}
-    \caption{Results of multivariate linear regressions with \(r\) as the dependent variable.
-    \(R\) squared is reported for each model.}
+    \caption{\textbf{Results of multivariate linear regressions with \(r\) as
+    the dependent variable.} \(R\) squared is reported for each model. The $R$
+    scores of the fitted models indicate their capability to explain some of the
+    variation in the median rank. Most of the features have a statistically
+    significant effect on the normalized rank.
+    A multivariate linear regression has also be fitted on the median score. The
+    coefficients and \(p\) values of the features can be found in
+    Supplementary Information. Both approaches lead to similar conclusions.}
     \label{table:linear_regression}
@@
 
-A multivariate linear regression has also be fitted on the median score. The
-coefficients and \(p\) values of the features can be found in
-Appendix~\ref{app:regression_median_score}. This approach leads to similar conclusions.
+A third method that evaluates the importance of the features in
+Table~\ref{table:manual_features} using clustering and random forests can be
+found in the Supplementary Information. The results uphold the outcomes of the
+correlation and multivariate regression. It also evaluates the effects of the
+whether or not a strategy is stochastic, makes use of the knowledge of the
+utility values, or makes use of match length. These were not evaluated by the
+methods above because there are binary variables. The results showed that they
+have no significant effect on a strategy's performance.
 
-The feature \(C_{r} / C_{\text{mean}}\) has a statistically significant effect
-across all models and a high regression coefficient. It has both a positive and
-negative impact on the normalised rank depending on the environment. For
-standard tournaments, Figure~\ref{fig:discussion_standard} gives the
-distributions of several features for the winners of standard tournaments. The
-\(C_{r} / C_{\text{mean}}\) distribution of the winner is also given in
-Figure~\ref{fig:discussion_standard}. A value of \(C_r / C_{\text{mean}} = 1\)
-implies that the cooperating ratio of the winner was the same as the mean
-cooperating ratio of the tournament, and in standard tournaments, the median is
-1. Therefore, an effective strategy in standard tournaments was the mean
-cooperator of its respective tournament.
+The results presented here suggest that forgiveness and a strategy's cooperation
+rate, particularly in comparison to the tournament averages, are significant
+features. The findings imply that the
+forgiveness exhibited by strategies may not consistently contribute to favorable
+outcomes. Nevertheless, it is essential to exercise caution in extrapolating the
+implications of this analysis. For example, the analysis is limited as we only
+consider a linear relationship between these parameters and the rank. To further
+investigate the effects of the parameters discussed in this section, we have
+conducted a more detailed analysis in the next section, focusing on the
+performances of the winners of the tournaments.
 
-The distributions of SSE and \(CD\) to \(C\) rate for the winners of standard
-tournaments are also given in Figure~\ref{fig:discussion_standard}. The SSE
-distributions for the winners indicate that the strategy behaved in a ZD way in
-several tournaments, however, not constantly. The winners participated in
-matches where they did not try to extortionate their opponents. Furthermore, the
-\(CD\) to \(C\) distribution indicates that if a strategy were to defect against
-the winners the winners would reciprocate on average with a probability of 0.5.
+\subsection{Features of top performing strategies}\label{section:winning_features}
+
+In Figure~\ref{fig:discussion_cooperation_measures}, we present the
+distributions of the cooperation ratio and \(C_r / C_{\text{mean}}\) for the
+winners of tournaments. A value of \(C_r / C_{\text{mean}} = 1\) implies that
+the cooperation ratio of the winner was the same as the mean cooperating ratio
+of the tournament, and we observe that this occurs for most tournament types,
+apart from the case of noisy and probabilistically ending tournaments. In the
+case of noisy tournaments, there are winners that did not cooperate exactly as
+such but are fairly distributed around 1. Interestingly, in the case of
+probabilistic ending tournaments, there are several winners that cooperated much
+less than that, confirming the results of the previous section that defecting
+strategies can we winner in probabilistic ending tournaments. The distribution
+of the cooperation rates showcases a high cooperation rate in standard
+tournaments and probabilistic ending tournaments. In tournaments with noise, we
+observe a much less cooperative behavior, which could result from strategies
+being cautious of potential flip actions by the co-player or strategies not
+suited for noise holding grudges against defections.
 
@@
         \centering
-        \includegraphics[width=\textwidth]{../images/standard_discussion.pdf}
-        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
-        for the winners of standard tournaments. A
-        value of \(C_r / C_{\text{mean}} = 1\) imply that the cooperating ratio of the
-        winner was the same as the mean cooperating ratio of the tournament. An SSE distribution
-        skewed towards 0 indicates a extortionate behaviour by the strategy.}
-        \label{fig:discussion_standard}
+        \includegraphics[width=\textwidth]{../images/features_result.pdf}
+        \caption{\textbf{Distributions of \(C_r\) and \(C_r / C_{\text{mean}}\)
+        for the winners of tournaments.} A value of \(C_r / C_{\text{mean}} =
+        1\) imply that the cooperating ratio of the winner was the same as the
+        mean cooperating ratio of the tournament.}
+        \label{fig:discussion_cooperation_measures}
 \end{figure}
 
-Similarly for the rest of the different tournaments types, and the entire data
-set the distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
-are given by Figures~\ref{fig:discussion_noisy},~\ref{fig:discussion_probend},
-\ref{fig:discussion_probend_noisy} and~\ref{fig:discussion_entire_data}.
+Analyzing the SSE distributions across different tournament types
+(Figure~\ref{fig:discussion_sse}) suggests that successful strategies exhibit
+some extortionate behavior, though not consistently. ZDs are a set of strategies
+that are often envious, as they attempt to exploit their opponents. The winners
+of the tournaments considered in this work demonstrate envious behavior, but not
+to the extent observed in many ZDs. While the exact interactions between matches
+are not recorded here, the work of~\cite{Harper2017}, which introduced the
+trained strategies appearing in the top-ranked strategies of
+Section~\ref{section:top_performances}, did record such interactions.
+In~\cite{Harper2017}, it was shown that clever strategies managed to achieve
+mutual cooperation with stronger strategies while exploiting weaker ones. This
+could explain the clever winners in our analysis and the observed SSE
+distributions.
 
-Based on the \(C_r / C_{\text{mean}}\) distributions the successful strategies
-have adapted differently to the mean cooperator depending on the tournament
-type. In noisy tournaments where the median of the distribution is at 0.67, and
-thereupon the winners cooperated 67\% of the time the mean cooperator did. In
-tournaments with noise and a probabilistic ending the winners cooperated 60\%,
-whereas in settings that the type of the tournament can vary between all the
-types the winners cooperated 67\% of the time the mean cooperator did. Lastly,
-in probabilistic ending tournaments above more defecting
-strategies prevail (Section~\ref{section:top_performances}), and this result is
-reflected here.
+This might also be the reason why ZDs fail to appear in the top ranks—they
+attempt to exploit all opponents and cannot actively adapt back to mutual
+cooperation against stronger strategies, which requires a deeper memory. It's
+worth noting that ZDs tend to perform poorly in population games for a similar
+reason: they aim to exploit other players using ZDs, failing to form a
+cooperative subpopulation~\cite{Knight2017evolution}. This makes them effective
+invaders but poor at resisting invasion.
 
@@
         \centering
-        \includegraphics[width=\textwidth]{../images/noisy_discussion.pdf}
-        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
-        for the winners of noisy tournaments.}
-        \label{fig:discussion_noisy}
+        \includegraphics[width=.75\textwidth]{../images/sse.pdf}
+        \caption{\textbf{Distributions of SSE error for the winners of
+        tournaments.} An SSE distribution skewed towards 0 indicates a
+        extortionate behaviour by the strategy.}
+        \label{fig:discussion_sse}
 \end{figure}
 
-The probability of noise has been observed to substantially affect optimal
-behaviour.
-Figure~\ref{fig:compared_to_mean_over_noise_probability} gives the ratio \(C_r /
-C_{\text{mean}}\) for the winners in tournaments with noise, over the
-probability of noise. From Figure~\ref{fig:noisy_discussion_over_noise} it is
-clear that the cooperating only 67\% of the time the mean cooperator did is
-optimal only when \(p_n \in [0.2, 0.4)\) and \(p_n \in [0.6, 0.7]\). In
-environments with \(p_n < 0.1\) the winners want to be close to the mean
-cooperator, similarly to standard tournaments, and as the probability of noise
-is exceeding 0.5 (where the game is effectively inverted) strategies should
-aim to be less and less cooperative.
+Finally, we examine the distributions of the cooperation rates after the
+outcomes \(CC, CD, DC\), and \(DD\), as shown in
+Figure~\ref{fig:discussion_rates}. In the case of cooperating after mutual
+cooperation, the results align with expectations; the distributions skew towards
+1, indicating that the winners of the tournaments are more likely to cooperate
+after mutual cooperation. Regarding the \(CD\) outcome and the likelihood to
+cooperate after such a result, capturing forgiveness, the distributions skew
+towards 1/2, not 1, suggesting that strategies need to reduce their readiness to
+forgive. This aligns with the known result that Generous Tit For Tat generally
+outperforms \TFT{} in most settings. Interestingly, in probabilistic ending
+tournaments, there is a peak at 0, suggesting that in such tournaments,
+strategies should not be too generous in short matches.
 
-Figure~\ref{fig:compared_to_mean_over_noise_probability} gives \(C_r /
-C_{\text{mean}}\) for the winners over \(p_n\) in tournaments with noise and a
-probabilistic ending. The optimal proportions of cooperations are different
-now that the number of turns is not fixed, successful strategies
-want to be more defecting that the mean cooperator, that only changes when
-\(p_n\) approaches 0.5. Figure~\ref{fig:compared_to_mean_over_noise_probability}
-demonstrates how the adjustments to \(C_r /C_{\text{mean}}\) change over the
-noise in the to the environment, and thus supports how important adapting to
-the environment is for a strategy to be successful.
-
-\begin{figure}[!htbp]
-    \centering
-    \begin{subfigure}{0.485\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/noisy_discussion_over_noise.pdf}
-        \caption{\(C_r / C_{\text{mean}}\) distribution for winners in noisy tournaments over
-        \(p_n\).}\label{fig:noisy_discussion_over_noise}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}{0.485\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{../images/noisy_probend_discussion_over_noise.pdf}
-        \caption{\(C_r / C_{\text{mean}}\) distribution for winners in noisy probabilistic ending tournaments over
-        \(p_n\).}\label{fig:noisy_probend_discussion_over_noise}
-    \end{subfigure}
-    \caption{\(C_r / C_{\text{mean}}\) distributions over intervals of \(p_n\).
-    These distributions model the optimal proportion of cooperation
-    compared to \(C_{\text{mean}}\) as a function of (\(p_n\)).}
-    \label{fig:compared_to_mean_over_noise_probability}
-\end{figure}
-
-The distributions of the SSE across the tournament types suggest that successful
-strategies exhibit some extortionate behaviour, but not constantly.
-ZDs are a set of strategies that are often envious as they try to exploit their
-opponents. The winners of the tournaments considered in this work are
-envious, but not as much as many ZDs.
-Though the exact interactions between the matches have not been recorded here,
-the work of~\cite{Harper2017} which introduced the trained strategies that
-appeared in the top ranked strategies of Section~\ref{section:top_performances}
-did. In~\cite{Harper2017} it was shown that clever strategies managed to achieve
-mutual cooperation with stronger strategies whilst exploiting the weaker
-strategies. This could explain the clever winners
-of our analysis, and would explain the SSE distributions. This could also
-be the reason why ZDs fail to appear in the tops ranks -- they try to exploit
-all opponents and cannot actively adapt back to mutual cooperation against
-stronger strategies, which requires more depth of memory. Note that
-ZDs also tend to perform poorly in population games for a similar reason: they
-attempt to exploit other players using ZDs, failing to form a cooperative
-subpopulation~\cite{Knight2017evolution}. This makes them good invaders but poor resisters of invasion.
+A strategy's effort to make amends is captured by the distributions of the
+\(DC\) to \(C\) rates. In noisy tournaments, winners are less likely to
+cooperate after a defection; however, there are still behaviors that attempt to
+make up for their defection. In standard tournaments and probabilistic ending
+tournaments, we observe two hubs of behaviors, one at 0 and one at 0.4-0.5,
+indicating that some winners are exploiting whether to try to make up, but with
+a small probability. This is also reflected in the \(DD\) to \(D\) rates, where
+in standard and probabilistic ending tournaments, there are winners that attempt
+to recover from a \(DD\) outcome. The remaining results are as expected, skewed
+towards 0.
 
@@
         \centering
-        \includegraphics[width=\textwidth]{../images/probend_discussion.pdf}
-        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
-        for the winners of probabilistic ending tournaments.}
-        \label{fig:discussion_probend}
+        \includegraphics[width=\textwidth]{../images/rates_result.pdf}
+        \caption{\textbf{Distributions of rates $CC$ to $C$, $CD$ to $C$, $DC$
+        to $C$, and $DD$ to $C$ for the winners of
+        tournaments.}}\label{fig:discussion_rates}
 \end{figure}
-
-The distributions of the \(CD\) to \(C\) rate evaluate the behaviour of a
-successful strategy after its opponent has defected against it. In standard
-tournaments it was observed that a successful strategy reciprocates with a
-probability of 0.5, and in a setting that the type
-of the tournament can vary between all the examined types a winning strategy
-would reciprocate on average with a probability of 0.58. In
-tournaments with noise a strategy is less likely to cooperate following a
-defection compared to standard tournaments, and in probabilistic ending
-tournaments a strategy will reciprocate a defection.
-This leads to adjusting the recommendation of being provocable to defections made
-by R. Axerlod. A strategy should be provocable in tournaments with short matches,
-but in the rest of the settings a strategy should be more generous.
-
-\begin{figure}[!htbp]
-    \centering
-        \centering
-        \includegraphics[width=\textwidth]{../images/probend_noisy_discussion.pdf}
-        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
-        for the winners of noisy probabilistic ending tournaments.}
-        \label{fig:discussion_probend_noisy}
-\end{figure}
-
-Further statistically significant features with strong effects include \(C_r /
-C_{\text{min}}\), \(C_r / C_{\text{max}}\), \(C_{\text{min}}\) and
-\(C_{\text{max}}\). These add more emphasis on how important it is for a  a
-strategy to adapt to its environment. Finally, the features number of turns,
-repetitions and the probabilities of noise and the game ending had no
-significant effects based on the multivariate regression models.
-
-\begin{figure}[!htbp]
-    \centering
-        \centering
-        \includegraphics[width=\textwidth]{../images/entire_data_discussion.pdf}
-        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
-        for the winners over the tournaments of the entire data set.}
-        \label{fig:discussion_entire_data}
-\end{figure}
-
-A third method that evaluates the importance of the features in
-Table~\ref{table:manual_features} using clustering and random forests can be found in
-the Appendix~\ref{app:clustering}. The results uphold the outcomes of the
-correlation and multivariate regression. It also evaluates the effects
-of the whether or not a strategy is stochastic, makes use of the knowledge of the utility values, or makes use of match length.
-These were not evaluated by the methods above because there are binary variables.
-The results showed that they have no significant effect on a strategy's
-performance.
 
@@
 This manuscript explored the performance of \numberofstrategies strategies of
-the IPD in \numberofalltournaments computer tournaments. The collection of
-computer tournaments presented here is the largest and most diverse collection in the
-literature. The \numberofstrategies strategies are drawn from the APL and include
-strategies from the IPD literature. The computer tournaments include tournaments of
-four different types.
-
-So what is the best way of playing the IPD? And is
-there a single dominant strategy for the IPD?
-
-There was not a single strategy
-within the collection of the \numberofstrategies strategies that managed to
-perform well in all the tournaments variations it competed in. Even if on
-average a strategy ranked highly in a specific environment this did not
+the \IPD{} in thousands of computer tournaments. The collection of computer
+tournaments presented here is the largest and most diverse collection in the
+literature. The \numberofstrategies strategies are drawn from the APL and
+include strategies from the \IPD{} literature. The computer tournaments include
+tournaments of four different types. So what is the best way of playing the
+\IPD{}? And is there a single dominant strategy for the \IPD{}? There was not a
+single strategy within the collection of the \numberofstrategies strategies that
+managed to perform well in all the tournaments variations it competed in. Even
+if on average a strategy ranked highly in a specific environment this did not
 guarantee its success over the different tournament types. Nevertheless, in
-Sections~\ref{section:top_performances}
+subsections~\ref{section:top_performances}
 and~\ref{section:evaluation_of_performance} we examined the best performing
@@
 this demonstrated that there are properties associated with the success of
-strategies which in fact contradict the originally suggested properties of R.
+strategies which in fact contradict the originally suggested properties of
 Axelrod~\cite{Axelrod1981}.
@@
 The features analysis of the best performing strategies demonstrated that a
-strategy should reciprocate, as suggested by R. Axelrod, but it should relax its
+strategy should reciprocate, as suggested by Axelrod, but it should relax its
 readiness to do so and be more \textbf{generous}. For noisy environments this is
@@
 cooperate at a lower rate than the tournament population on average.
-Moreover, the manner in which a
-strategy achieves a given cooperation rate relative to the tournament population
-average is important.
 
@@
 strategy is no longer sufficient.
-
 These results highlight a central idea in evolutionary game theory in this
@@
 
-\begin{itemize}
+\begin{enumerate}[(i)]
     \item Be ``nice'' in non-noisy environments or when game lengths are longer
@@
     \item Adapt to the environment (including the population of strategies).
-\end{itemize}
+\end{enumerate}
 
-The data set described in this work contains the largest number of IPD tournaments,
-to the authors knowledge. The raw data set is available at~\cite{raw_data} and the
-processed data at~\cite{data}. Further data mining
+The data set described in this work contains the largest number of IPD
+tournaments, to the authors knowledge. The raw data set is available
+at~\cite{raw_data} and the processed data at~\cite{data}. Further data mining
 could be applied and provide new insights in the field.
@@
 
-A variety of software have been used in this work:
+A variety of open-source software have been used in this work. The authors would
+like to express their gratitude to the open-source software community, whose
+invaluable contributions significantly enhanced the development and execution of
+this research. Namely, the authors would like to thank the developers of the
+following software packages: Axelrod-Python library for IPD
+simulations~\cite{axelrodproject}, the Matplotlib library for
+visualisation~\cite{hunter2007matplotlib}, The Numpy library for data
+manipulation~\cite{walt2011numpy}, and finally the scikit-learn library for data
+analysis~\cite{scikit-learn}.
 
-\begin{itemize}
-    \item The Axelrod-Python library for IPD simulations~\cite{axelrodproject}.
-    \item The Matplotlib library for visualisation~\cite{hunter2007matplotlib}.
-    \item The Numpy library for data manipulation~\cite{walt2011numpy}.
-    \item The scikit-learn library for data analysis~\cite{scikit-learn}.
-\end{itemize}
+\section{Data availability statement}
+
+The raw and processed datasets have been made publicly available~\cite{data,
+raw_data} and can be used for further analysis and insights.
 

### 2023-12-01 paper/perfomances_table.tex
working on main paper for the special issue

@@
 \midrule
-0  &            Evolved HMM 5 &     0.007 &                       MEM2 &     0.061 &             Evolved FSM 16 &       0.0 &                   Defector &     0.006 \\
-1  &           Evolved FSM 16 &      0.01 &       Spiteful Tit For Tat &     0.063 &    Evolved FSM 16 Noise 05 &     0.013 &          Better and Better &     0.011 \\
-2  &     EvolvedLookerUp2\_2\_2 &     0.011 &           Nice Meta Winner &     0.066 &                       MEM2 &     0.027 &                 Aggravater &     0.014 \\
-3  &  Evolved FSM 16 Noise 05 &     0.017 &                    Grudger &     0.067 &              Evolved HMM 5 &     0.043 &                  Fortress4 &     0.021 \\
-4  &        PSO Gambler 2\_2\_2 &     0.022 &    Meta Winner Long Memory &     0.073 &       EvolvedLookerUp2\_2\_2 &     0.049 &            Tricky Defector &     0.038 \\
-5  &              Evolved ANN &     0.029 &                   Forgiver &     0.074 &       Spiteful Tit For Tat &     0.059 &    Meta Winner Long Memory &     0.049 \\
-6  &            Evolved ANN 5 &     0.034 &               Fool Me Once &     0.074 &           Nice Meta Winner &     0.069 &     Meta Winner Memory One &      0.05 \\
-7  &        PSO Gambler 1\_1\_1 &     0.037 &                Meta Winner &     0.075 &         NMWE Finite Memory &     0.069 &  Meta Winner Finite Memory &      0.05 \\
-8  &            Evolved FSM 4 &     0.049 &     Meta Winner Memory One &     0.076 &         NMWE Deterministic &      0.07 &     Meta Winner Stochastic &     0.051 \\
-9  &         PSO Gambler Mem1 &      0.05 &  Meta Winner Finite Memory &     0.077 &                    Grudger &      0.07 &  Meta Winner Deterministic &     0.052 \\
-10 &                 Winner12 &      0.06 &  Meta Winner Deterministic &     0.078 &           NMWE Long Memory &     0.074 &                Meta Winner &     0.053 \\
-11 &             Fool Me Once &     0.061 &         NMWE Deterministic &     0.087 &  Nice Meta Winner Ensemble &     0.076 &       Meta Winner Ensemble &     0.059 \\
-12 &                      DBS &     0.071 &           NMWE Long Memory &     0.087 &       EvolvedLookerUp1\_1\_1 &     0.077 &                  Fortress3 &      0.07 \\
-13 &            DoubleCrosser &     0.072 &         CollectiveStrategy &     0.087 &            NMWE Memory One &      0.08 &         CollectiveStrategy &     0.077 \\
-14 &              BackStabber &     0.075 &                   Defector &     0.089 &            NMWE Stochastic &     0.085 &                   Prober 3 &      0.08 \\
+0  &            Evolved HMM 5 &     0.007 &                         DBS &       0.0 &             Evolved FSM 16 &       0.0 &                     Raider &     0.022 \\
+1  &           Evolved FSM 16 &      0.01 &     Evolved FSM 16 Noise 05 &     0.008 &    Evolved FSM 16 Noise 05 &     0.013 &                       MEM2 &     0.037 \\
+2  &     EvolvedLookerUp2\_2\_2 &     0.011 &      Evolved ANN 5 Noise 05 &     0.013 &                       MEM2 &     0.027 &                   Prober 3 &     0.039 \\
+3  &  Evolved FSM 16 Noise 05 &     0.017 &                 BackStabber &     0.024 &              Evolved HMM 5 &     0.043 &    Evolved FSM 16 Noise 05 &     0.048 \\
+4  &        PSO Gambler 2\_2\_2 &     0.022 &               DoubleCrosser &     0.025 &       EvolvedLookerUp2\_2\_2 &     0.049 &                Hard Prober &     0.072 \\
+5  &              Evolved ANN &     0.029 &               Evolved ANN 5 &     0.028 &       Spiteful Tit For Tat &     0.059 &       Spiteful Tit For Tat &     0.078 \\
+6  &            Evolved ANN 5 &     0.034 &                 Evolved ANN &     0.038 &           Nice Meta Winner &     0.069 &          Better and Better &     0.089 \\
+7  &        PSO Gambler 1\_1\_1 &     0.037 &        Spiteful Tit For Tat &     0.051 &         NMWE Finite Memory &     0.069 &                    Grudger &     0.091 \\
+8  &            Evolved FSM 4 &     0.049 &               Evolved HMM 5 &     0.051 &         NMWE Deterministic &      0.07 &                  Fortress4 &     0.096 \\
+9  &         PSO Gambler Mem1 &      0.05 &              Level Punisher &     0.052 &                    Grudger &      0.07 &     Meta Winner Memory One &     0.099 \\
+10 &                 Winner12 &      0.06 &                   Omega TFT &     0.059 &           NMWE Long Memory &     0.074 &           NMWE Long Memory &     0.099 \\
+11 &             Fool Me Once &     0.061 &                Fool Me Once &     0.059 &  Nice Meta Winner Ensemble &     0.076 &           Nice Meta Winner &     0.104 \\
+12 &                      DBS &     0.071 &  PSO Gambler 2\_2\_2 Noise 05 &     0.067 &       EvolvedLookerUp1\_1\_1 &     0.077 &         NMWE Deterministic &     0.109 \\
+13 &            DoubleCrosser &     0.072 &              Evolved FSM 16 &     0.078 &            NMWE Memory One &      0.08 &            NMWE Memory One &     0.112 \\
+14 &              BackStabber &     0.075 &                  EugineNier &      0.08 &            NMWE Stochastic &     0.085 &  Nice Meta Winner Ensemble &     0.115 \\
 \bottomrule

### 2023-12-01 paper/top_perfomances.tex
working on main paper for the special issue

--- 2019-11-11 paper/top_perfomances.tex
@@
-\begin{tabular}{lggllggllr}
+\begin{tabular}{lggllggllggllr}
     \toprule
-& \multicolumn{2}{g}{Standard} & \multicolumn{2}{c}{Noisy} & \multicolumn{2}{g}{Probabilistic ending} &  \multicolumn{2}{c}{Noisy probabilistic ending} \\
+    & \multicolumn{2}{g}{Standard} & \multicolumn{2}{g}{Noisy (\(p_n \leq 0.1\))} & \multicolumn{2}{g}{Probabilistic ending (\(p_e \leq 0.1\))} &  \multicolumn{2}{c}{Noisy probabilistic ending} \\
+    \toprule
+    {} &                     Name & $\bar{r}$ &                       Name & $\bar{r}$ &                       Name & $\bar{r}$ &                       Name & $\bar{r}$ \\
     \midrule
-& Name & $\bar{r}$ &                 Name & $\bar{r}$ &               Name & $\bar{r}$ &                 Name & $\bar{r}$ \\
-\midrule
-0  &            Evolved HMM 5 &   0.00667 &                 Grumpy &   0.14020 &          Fortress4 &   0.01266 &           Alternator &   0.30370 \\
-1  &           Evolved FSM 16 &   0.00995 &                    $e$ &   0.19388 &           Defector &   0.01429 &               $\phi$ &   0.30978 \\
-2  &     EvolvedLookerUp2 2 2 &   0.01064 &         Tit For 2 Tats &   0.20617 &  Better and Better &   0.01587 &                  $e$ &   0.31250 \\
-3  &  Evolved FSM 16 Noise 05 &   0.01667 &  Slow Tit For Two Tats &   0.20962 &    Tricky Defector &   0.01875 &                $\pi$ &   0.31686 \\
-4  &        PSO Gambler 2 2 2 &   0.02143 &           Cycle Hunter &   0.21538 &          Fortress3 &   0.02174 &    Limited Retaliate &   0.35263 \\
-5  &              Evolved ANN &   0.02878 &         Risky QLearner &   0.22222 &     Gradual Killer &   0.02532 &     Anti Tit For Tat &   0.35431 \\
-6  &            Evolved ANN 5 &   0.03390 &            Retaliate 3 &   0.22887 &         Aggravater &   0.02778 &          Retaliate 3 &   0.35563 \\
-7  &        PSO Gambler 1 1 1 &   0.03704 &          Cycler CCCCCD &   0.23507 &             Raider &   0.03077 &  Limited Retaliate 3 &   0.35563 \\
-8  &            Evolved FSM 4 &   0.04891 &            Retaliate 2 &   0.23913 &         Cycler DDC &   0.04545 &            Retaliate &   0.35714 \\
-9  &         PSO Gambler Mem1 &   0.05036 &        Defector Hunter &   0.24038 &        Hard Prober &   0.05128 &          Retaliate 2 &   0.35767 \\
-10 &                 Winner12 &   0.06011 &              Retaliate &   0.24177 &         SolutionB1 &   0.06024 &  Limited Retaliate 2 &   0.36134 \\
-11 &             Fool Me Once &   0.06140 &    Hard Tit For 2 Tats &   0.25000 &      Meta Minority &   0.06077 &             Hopeless &   0.36842 \\
-12 &                      DBS &   0.07143 &               ShortMem &   0.25286 &              Bully &   0.06081 &    Arrogant QLearner &   0.40651 \\
-13 &            DoubleCrosser &   0.07200 &    Limited Retaliate 3 &   0.25316 &    Fool Me Forever &   0.07080 &    Cautious QLearner &   0.40909 \\
-14 &              BackStabber &   0.07519 &      Limited Retaliate &   0.25706 &             EasyGo &   0.07101 &      Fool Me Forever &   0.41764 \\
+    0  &            Evolved HMM 5 &     0.007 &                         DBS &       0.0 &             Evolved FSM 16 &       0.0 &                     Raider &     0.022 \\
+    1  &           Evolved FSM 16 &      0.01 &     Evolved FSM 16 Noise 05 &     0.008 &    Evolved FSM 16 Noise 05 &     0.013 &                       MEM2 &     0.037 \\
+    2  &     EvolvedLookerUp2\_2\_2 &     0.011 &      Evolved ANN 5 Noise 05 &     0.013 &                       MEM2 &     0.027 &                   Prober 3 &     0.039 \\
+    3  &  Evolved FSM 16 Noise 05 &     0.017 &                 BackStabber &     0.024 &              Evolved HMM 5 &     0.043 &    Evolved FSM 16 Noise 05 &     0.048 \\
+    4  &        PSO Gambler 2\_2\_2 &     0.022 &               DoubleCrosser &     0.025 &       EvolvedLookerUp2\_2\_2 &     0.049 &                Hard Prober &     0.072 \\
+    5  &              Evolved ANN &     0.029 &               Evolved ANN 5 &     0.028 &       Spiteful Tit For Tat &     0.059 &       Spiteful Tit For Tat &     0.078 \\
+    6  &            Evolved ANN 5 &     0.034 &                 Evolved ANN &     0.038 &           Nice Meta Winner &     0.069 &          Better and Better &     0.089 \\
+    7  &        PSO Gambler 1\_1\_1 &     0.037 &        Spiteful Tit For Tat &     0.051 &         NMWE Finite Memory &     0.069 &                    Grudger &     0.091 \\
+    8  &            Evolved FSM 4 &     0.049 &               Evolved HMM 5 &     0.051 &         NMWE Deterministic &      0.07 &                  Fortress4 &     0.096 \\
+    9  &         PSO Gambler Mem1 &      0.05 &              Level Punisher &     0.052 &                    Grudger &      0.07 &     Meta Winner Memory One &     0.099 \\
+    10 &                 Winner12 &      0.06 &                   Omega TFT &     0.059 &           NMWE Long Memory &     0.074 &           NMWE Long Memory &     0.099 \\
+    11 &             Fool Me Once &     0.061 &                Fool Me Once &     0.059 &  Nice Meta Winner Ensemble &     0.076 &           Nice Meta Winner &     0.104 \\
+    12 &                      DBS &     0.071 &  PSO Gambler 2\_2\_2 Noise 05 &     0.067 &       EvolvedLookerUp1\_1\_1 &     0.077 &         NMWE Deterministic &     0.109 \\
+    13 &            DoubleCrosser &     0.072 &              Evolved FSM 16 &     0.078 &            NMWE Memory One &      0.08 &            NMWE Memory One &     0.112 \\
+    14 &              BackStabber &     0.075 &                  EugineNier &      0.08 &            NMWE Stochastic &     0.085 &  Nice Meta Winner Ensemble &     0.115 \\
     \bottomrule

### 2023-12-01 paper/correlation_section.tex
finish SI section analysis with all data and clean notebooks
The notebooks now include code to run the analysis for both the
main paper and the SI

@@
 
-A graphical representation of the correlation coefficients for the features in
-Table~\ref{table:manual_features}.
+In this section we present the correlation coefficients for the features
+presented in Table 3 of the main manuscript. The correlation coefficients
+are calculated using the Spearman's rank correlation coefficient. The results
+are presented as a graphical representation.
 
@@
         \end{center}
-        \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-        for standard tournaments}
+        \caption{Correlation coefficients of strategies' features for standard tournaments.}
+\end{figure}
+\begin{figure}[!htbp]
+    \begin{center}
+        \includegraphics[width=.75\linewidth]{../images/subset_noise_correlation_plot.pdf}
+    \end{center}
+    \caption{Correlation coefficients of strategies' features for noisy tournaments with $p_n \leq 0.1$.}
 \end{figure}
@@
     \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-    for noisy tournaments}
+    \caption{Correlation coefficients of strategies' features for noisy tournaments.}
+\end{figure}
+\begin{figure}[!htbp]
+    \begin{center}
+        \includegraphics[width=.75\linewidth]{../images/subset_probend_correlation_plot.pdf}
+    \end{center}
+    \caption{Correlation coefficients of strategies' features for probabilistic ending tournaments with $p_e \leq 0.1$.}
 \end{figure}
@@
     \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-    for probabilistic ending tournaments}
+    \caption{Correlation coefficients of strategies' features for probabilistic ending tournaments.}
+\end{figure}
+\begin{figure}[!htbp]
+    \begin{center}
+        \includegraphics[width=.75\linewidth]{../images/subset_probend_noise_correlation_plot.pdf}
+    \end{center}
+    \caption{Correlation coefficients of strategies' features for noisy probabilistic ending tournaments
+    with $p_n \leq 0.1$ and $p_e \leq 0.1$.}
 \end{figure}
@@
     \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-    for noisy probabilistic ending tournaments}
+    \caption{Correlation coefficients of strategies' features for noisy probabilistic ending tournaments.}
 \end{figure}
-\begin{figure}[!htbp]
-    \begin{center}
-        \includegraphics[width=.75\linewidth]{../images/merged_correlation_plot.pdf}
-    \end{center}
-    \caption{Correlation coefficients of features in Table~\ref{table:manual_features}
-    for data set}
-\end{figure}

### 2023-12-01 paper/result_with_entire_dataset.tex
finish SI section analysis with all data and clean notebooks
The notebooks now include code to run the analysis for both the
main paper and the SI

\section{Top ranked strategies and features analysis for the entire data set}

In this section we carry out a similar analysis as the one presented in
main manuscript, but this time we use the entire data set for noisy and
probabilistic ending tournaments.

\subsection{Top ranked strategies across tournaments}

The top 15 strategies for each tournament type based on \(\bar{r}\) are given in
Table~\ref{table:top_performances}. The data collection process was designed
such that the probabilities of noise and ending of the match varied between 0
and 1. However, commonly used values for these probabilities are values less
than 0.1. Thus, Table~\ref{table:top_performances} also includes the top 15
strategies in noisy tournaments with \(p_n < 0.1\) and probabilistic ending
tournaments with \(p_e < 0.1\).

\newcolumntype{g}{>{\columncolor{Gray}}l}
\begin{table}[!htbp]
    \begin{center}
    \resizebox{\textwidth}{!}{
        \input{top_perfomances_full_data_set.tex}
    }
\end{center}
\caption{Top performances for each tournament type based on $\bar{r}$. The
results of each type are based on 11420 unique tournaments. The
results for noisy tournaments with \(p_n < 0.1\) are based on 1151 tournaments,
and for probabilistic ending tournaments with \(p_e < 0.1\) on 1139. The top
ranks indicate that trained strategies perform well in a variety of
environments, but so do simple deterministic strategies. The normalised medians
are close to 0 for most environments, except environments with noise not
restricted to 0.1 regardless of the number of turns. Noisy and noisy probabilistic
ending tournaments have the highest medians.}
\label{table:top_performances}
\end{table}

The \(r\) distributions for the top ranked strategies of Table~\ref{table:top_performances}
are given by Figure~\ref{fig:r_distributions}.

\begin{figure*}[!htbp]
    \centering
    \begin{subfigure}{0.485\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/r_distribution_standard.pdf}
        \caption{$r$ distributions of top 15 strategies in standard tournaments.}\label{fig:std_results}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.485\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/r_distribution_noise_subset.pdf}
        \caption{$r$ distributions of top 15 strategies in noisy tournaments with \(p_n < 0.1\).}\label{fig:noise_subset_results}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}{0.485\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/r_distribution_noise.pdf}
        \caption{$r$ distributions of top 15 strategies in noisy tournaments.}\label{fig:noise_results}
    \end{subfigure}
    \quad
    \begin{subfigure}{0.485\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/r_distribution_probend_subset.pdf}
        \caption{\(r\) distributions of top 15 strategies in 1139 probabilistic ending
        tournaments with \(p_e < 0.1\).}
        \label{fig:probend_subset_results}
    \end{subfigure}
    \vskip\baselineskip
    \begin{subfigure}{0.485\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/r_distribution_probend.pdf}
        \caption{$r$ distributions of top 15 strategies in probabilistic ending tournaments.}\label{fig:probend_results}
    \end{subfigure}
    \quad
    \begin{subfigure}{0.485\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/r_distribution_probend_noise.pdf}
        \caption{$r$ distributions of top 15 strategies in noisy probabilistic ending tournaments.}
        \label{fig:probend_noise_results}
    \end{subfigure}
    \caption{\(r\) distributions of the top 15 strategies in different
    environments. A lower value of \(\bar{r}\) corresponds to a more successful
    performance. A strategy's \(r\) distribution skewed towards zero indicates
    that the strategy ranked highly in most tournaments it participated in. Most
    distributions are skewed towards zero except the distributions with
    unrestricted noise, supporting the conclusions from
    Table~\ref{table:top_performances}.}\label{fig:r_distributions}
\end{figure*}

In standard tournaments 10 out of the 15 top strategies were introduced
in~\cite{Harper2017}. These are strategies based on finite state automata (FSM),
hidden Markov models (HMM), artificial neural networks (ANN), lookup tables
(LookerUp) and stochastic lookup tables (Gambler) that have been trained using
reinforcement learning algorithms (evolutionary and particle swarm algorithms).
They have been trained to perform well against a subset of the strategies
in APL in a standard tournament, thus their performance in the
specific setting was anticipated although still noteworthy given the random
sampling of tournament participants. DoubleCrosser, BackStabber and Fool Me Once, are
strategies not from the literature but from the APL. DoubleCrosser is an extension
of BackStabber and both strategies make use of the number of turns because they are
set to defect on the last two rounds. It should be noted that these
strategies can be characterised as ``cheaters'' because the source code of the strategies
allows them to know the number of turns in a match (unless the match has a probabilistic ending). These strategies were expected to not perform as well in
tournaments where the number of turns is not specified. Finally, Winner
12~\cite{mathieu2017} and DBS~\cite{Au2006} are both from the literature.
DBS is a strategy specifically designed for noisy environments, however, it ranks
highly in standard tournaments as well. Similarly the fourth ranked player,
Evolved FSM 16 Noise 05, was
trained for noisy tournaments yet performs well in standard tournaments.
Figure~\ref{fig:std_results} shows that these strategies typically perform
well in any standard tournament in which they participate.

In the case of noisy tournaments with smaller noise \(p_n < 0.1\) the top
performing strategies
include strategies specifically designed for noisy tournaments. These are DBS,
Evolved FSM 16 Noise 05, Evolved ANN 5 Noise 05, PSO Gambler 2 2 2 Noise 05 and
Omega Tit For Tat~\cite{kendall2007iterated}. Omega TFT, a strategy designed
to break the deadlocking cycles of \(CD\) and \(DC\) that TFT can fall into in noisy
environments, places 10th. The rest of the top ranks are
occupied by strategies which performed well in standard tournaments and
deterministic strategies such as Spiteful Tit For Tat~\cite{prison}, Level
Punisher~\cite{Eckhart2015}, Eugine Nier~\cite{lesswrong}.

In contrast, the performance of the top ranked strategies in noisy environments
when \(p_n\in [0, 1]\) is bimodal. The top strategies include strategies which
decide their actions based on the cooperation to defection ratio, such as
ShortMem~\cite{Andre2013}, Grumpy~\cite{axelrodproject} and
e~\cite{axelrodproject}, and the Retaliate strategies which are designed to
defect if the opponent has tricked them more often than a given percentage of the times that
they have done the same. The bimodality of the \(r\) distributions is explained
by Figure~\ref{fig:effect_of_noise} which demonstrates that the top 6 strategies
were highly ranked due to the their performance in tournaments with \(p_n>0.5\),
and that in tournaments with \(p_n<0.5\) they
performed poorly. At a noisy level of \(0.5\) or greater, mostly cooperative strategies
become mostly defectors and vice versa.

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.92\textwidth]{../images/noise_effect.pdf}
    \caption{Normalised rank \(r\) distributions for top 6 strategies in noisy tournaments over
    the probability of noisy ($p_n$).}
    \label{fig:effect_of_noise}
\end{figure}

The most effective strategies in probabilistic ending
tournaments with \(p_e< 0.1\) are a series of ensemble Meta strategies, trained strategies
which performed well
in standard tournaments, and Grudger~\cite{axelrodproject} and Spiteful Tit for
Tat~\cite{prison}. The Meta strategies~\cite{axelrodproject} utilize a team of
strategies and aggregate the potential actions of the team members into a single action
in various ways. Figure~\ref{fig:probend_subset_results} indicates that these strategies
performed well in any probabilistic ending tournament.

In probabilistic ending tournaments with \(p_e \in [0, 1]\) the top ranks are
mostly occupied by defecting strategies such as Better and Better, Gradual
Killer, Hard Prober (all from~\cite{axelrodproject}), Bully (Reverse Tit For
Tat)~\cite{Nachbar1992} and Defector, and a series of strategies based on finite
state automata introduced by Daniel Ashlock and Wendy Ashlock: Fortress 3,
Fortress 4 (both introduced in~\cite{Ashlock2006}), Raider~\cite{Ashlock2014}
and Solution B1~\cite{Ashlock2014}. The success of defecting strategies in
probabilistic ending tournaments is due to larger values of
\(p_e\) which lead to shorter matches (the expected number of rounds is \(1 / p_e\)), so the
impact of the PD being iterated is subdued. This is captured by the Folk
Theorem~\cite{Fudenberg2009} as defecting strategies do better when the likelihood
of the game ending in the next turn increases.
This is demonstrated by Figure~\ref{fig:effect_of_probend}, which gives the
distributions of \(r\) for the top 6 strategies in probabilistic ending tournaments
over \(p_e\).

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.92\textwidth]{../images/folk_theorem.pdf}
    \caption{Normalised rank \(r\) distributions for top 6 strategies in probabilistic ending tournaments
    over $p_e$. The 6 strategies start of with a high median rank,
    however, their ranked decreased as the the probability of the game ending
    increased and at the point of \(p_e = 0.1\).}
    \label{fig:effect_of_probend}
\end{figure}

The top performances in tournaments with both noise and a probabilistic ending
have the largest median values compared to the top rank strategies of the other
tournament types. The \(\bar{r}\) for the top strategy is approximately at 0.3,
indicating that the most successful strategy can on average just place in the
top 30\% of the competition.

On the whole, the analysis has shown that:

\begin{itemize}
    \item In standard tournaments the dominating strategies were
    strategies that had been trained using reinforcement learning techniques.
    \item In noisy environments where the noise probability strictly less than
    0.1 was considered, the successful strategies were strategies specifically
    designed or trained for noisy environments.
    \item In probabilistic ending tournaments most of the highly ranked
    strategies were defecting strategies and trained finite state automata, all
    by the authors of~\cite{Ashlock2006, Ashlock2014}. These strategies ranked
    high due to their performance in tournaments where the probability of the
    game ending after each turn was bigger than 0.1.
    \item In probabilistic tournaments with \(p_e\) less than 0.1 the highly
    ranked strategies were strategies based on the behaviour of others.
    \item From the collection of strategies considered here,  no strategy can be
    consistently successful in noisy environments, except if the value of noise
    is constrained to less than a 0.1.
\end{itemize}

\section{The effect of strategy features on performance}

The correlation coefficients between the strategies' features and the median
score and the median normalised rank for the full dataset of tournaments are
given by Table~\ref{table:correlations}. The correlation coefficients between
all features have been calculated and a graphical representation can be found in
the Section~\ref{app:correlations}.

\newcolumntype{g}{>{\columncolor{Gray}}c}
\begin{table}[!htbp]
    \begin{center}
    \resizebox{.9\textwidth}{!}{
        \input{correlations_table_full_dataset.tex}
    }
\end{center}
\caption{Correlations between the strategies' features
and the normalised rank and the median score.}\label{table:correlations}
\end{table}

In standard tournaments the features $CC$ to $C$, $C_r$, $C_r / C_{\text{max}}$
and the cooperating ratio compared to $C_{\text{median}}$ and $C_{\text{mean}}$
have a moderately negative effect on the normalised rank (smaller rank is
better), and a moderate positive on the median score. The SSE error and the $DD$
to $C$ rate have the opposite effects. Thus, in standard tournaments behaving
cooperatively corresponds to a more successful performance. Even though being
nice generally pays off that does not hold against defective strategies. Being
more cooperative after a mutual defection, that is not retaliating, is
associated to lesser overall success in terms of normalised rank.
Figure~\ref{fig:rates_of_winners_in_standard_tournaments} confirms that the
winners of standard tournaments always cooperate after a mutual cooperation and
almost always defect after a mutual defection.

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.8\textwidth]{../images/rates_of_winners_in_standard_tournaments.pdf}
    \caption{Distributions of $CC$ to $C$ and $DD$ to $C$ for the winners in
    standard tournaments.}\label{fig:rates_of_winners_in_standard_tournaments}
\end{figure}

Compared to standard tournaments, in both noisy and in probabilistic ending
tournaments the higher the rates of cooperation the lower a strategy's success
and median score. A strategy would want to cooperate less than both the mean and
median cooperator in such settings. In probabilistic ending tournaments the
correlation coefficients have larger values, indicating a stronger effect. Thus
a strategy will be punished more by its cooperative behaviour in probabilistic
ending environments, supporting the results of the previous subsection as well.
The distributions of the $C_r$ of the winners in both tournaments are given by
Figure~\ref{fig:c_r_distributions}. It confirms that the winners in noisy
tournaments cooperated less than 35\% of the time and in probabilistic ending
tournaments less than 10\%. In noisy probabilistic ending tournaments and over
all the tournaments' results, the only features that had a moderate effect are
$C_r/C_{\text{mean}}, C_r/C_{\text{max}}$ and $C_r$. In such environments
cooperative behaviour appears to be punished less than in noisy and
probabilistic ending tournaments.

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.8\textwidth]{../images/c_r_winners_tournaments.pdf}
    \caption{$C_r$ distributions of the winners in noisy and in probabilistic
    ending tournaments.}\label{fig:c_r_distributions}
\end{figure}

A multivariate linear regression has been fitted to model the relationship between
the features and the normalised rank. Based on the graphical representation of
the correlation matrices given in Section~\ref{app:correlations} several of the
features are highly correlated and have been removed
before fitting the linear regression model. The features included are given
by Table~\ref{table:linear_regression} alongside their corresponding \(p\) values
in the distinct tournaments and their regression coefficients.

\newcolumntype{g}{>{\columncolor{Gray}}c}
\begin{table}[h]
    \begin{center}
\resizebox{\textwidth}{!}{
    \input{regression_table_full_dataset.tex}}
    \end{center}
    \caption{Results of multivariate linear regressions with \(r\) as the dependent variable.
    \(R\) squared is reported for each model.}
    \label{table:linear_regression}
\end{table}

A multivariate linear regression has also be fitted on the median score. The
coefficients and \(p\) values of the features can be found in
Section~\ref{app:regression_median_score}. This approach leads to similar conclusions.

The feature \(C_{r} / C_{\text{mean}}\) has a statistically significant effect
across all models and a high regression coefficient. It has both a positive and
negative impact on the normalised rank depending on the environment. For
standard tournaments, Figure~\ref{fig:discussion_standard} gives the
distributions of several features for the winners of standard tournaments. The
\(C_{r} / C_{\text{mean}}\) distribution of the winner is also given in
Figure~\ref{fig:discussion_standard}. A value of \(C_r / C_{\text{mean}} = 1\)
implies that the cooperating ratio of the winner was the same as the mean
cooperating ratio of the tournament, and in standard tournaments, the median is
1. Therefore, an effective strategy in standard tournaments was the mean
cooperator of its respective tournament.

The distributions of SSE and \(CD\) to \(C\) rate for the winners of standard
tournaments are also given in Figure~\ref{fig:discussion_standard}. The SSE
distributions for the winners indicate that the strategy behaved in a ZD way in
several tournaments, however, not constantly. The winners participated in
matches where they did not try to extortionate their opponents. Furthermore, the
\(CD\) to \(C\) distribution indicates that if a strategy were to defect against
the winners the winners would reciprocate on average with a probability of 0.5.

\begin{figure}[!htbp]
    \centering
        \centering
        \includegraphics[width=\textwidth]{../images/standard_discussion.pdf}
        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
        for the winners of standard tournaments. A
        value of \(C_r / C_{\text{mean}} = 1\) imply that the cooperating ratio of the
        winner was the same as the mean cooperating ratio of the tournament. An SSE distribution
        skewed towards 0 indicates a extortionate behaviour by the strategy.}
        \label{fig:discussion_standard}
\end{figure}

Similarly for the rest of the different tournaments types, and the entire data
set the distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
are given by Figures~\ref{fig:discussion_noisy},~\ref{fig:discussion_probend},
\ref{fig:discussion_probend_noisy} and~\ref{fig:discussion_entire_data}.

Based on the \(C_r / C_{\text{mean}}\) distributions the successful strategies
have adapted differently to the mean cooperator depending on the tournament
type. In noisy tournaments where the median of the distribution is at 0.67, and
thereupon the winners cooperated 67\% of the time the mean cooperator did. In
tournaments with noise and a probabilistic ending the winners cooperated 60\%,
whereas in settings that the type of the tournament can vary between all the
types the winners cooperated 67\% of the time the mean cooperator did. Lastly,
in probabilistic ending tournaments above more defecting
strategies prevail (Section~\ref{section:top_performances}), and this result is
reflected here.

\begin{figure}[!htbp]
    \centering
        \centering
        \includegraphics[width=\textwidth]{../images/noisy_discussion.pdf}
        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
        for the winners of noisy tournaments.}
        \label{fig:discussion_noisy}
\end{figure}

The probability of noise has been observed to substantially affect optimal
behaviour.
Figure~\ref{fig:compared_to_mean_over_noise_probability} gives the ratio \(C_r /
C_{\text{mean}}\) for the winners in tournaments with noise, over the
probability of noise. From Figure~\ref{fig:noisy_discussion_over_noise} it is
clear that the cooperating only 67\% of the time the mean cooperator did is
optimal only when \(p_n \in [0.2, 0.4)\) and \(p_n \in [0.6, 0.7]\). In
environments with \(p_n < 0.1\) the winners want to be close to the mean
cooperator, similarly to standard tournaments, and as the probability of noise
is exceeding 0.5 (where the game is effectively inverted) strategies should
aim to be less and less cooperative.

Figure~\ref{fig:compared_to_mean_over_noise_probability} gives \(C_r /
C_{\text{mean}}\) for the winners over \(p_n\) in tournaments with noise and a
probabilistic ending. The optimal proportions of cooperations are different
now that the number of turns is not fixed, successful strategies
want to be more defecting that the mean cooperator, that only changes when
\(p_n\) approaches 0.5. Figure~\ref{fig:compared_to_mean_over_noise_probability}
demonstrates how the adjustments to \(C_r /C_{\text{mean}}\) change over the
noise in the to the environment, and thus supports how important adapting to
the environment is for a strategy to be successful.

\begin{figure}[!htbp]
    \centering
    \begin{subfigure}{0.485\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/noisy_discussion_over_noise.pdf}
        \caption{\(C_r / C_{\text{mean}}\) distribution for winners in noisy tournaments over
        \(p_n\).}\label{fig:noisy_discussion_over_noise}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.485\textwidth}
        \centering
        \includegraphics[width=\textwidth]{../images/noisy_probend_discussion_over_noise.pdf}
        \caption{\(C_r / C_{\text{mean}}\) distribution for winners in noisy probabilistic ending tournaments over
        \(p_n\).}\label{fig:noisy_probend_discussion_over_noise}
    \end{subfigure}
    \caption{\(C_r / C_{\text{mean}}\) distributions over intervals of \(p_n\).
    These distributions model the optimal proportion of cooperation
    compared to \(C_{\text{mean}}\) as a function of (\(p_n\)).}
    \label{fig:compared_to_mean_over_noise_probability}
\end{figure}

The distributions of the SSE across the tournament types suggest that successful
strategies exhibit some extortionate behaviour, but not constantly.
ZDs are a set of strategies that are often envious as they try to exploit their
opponents. The winners of the tournaments considered in this work are
envious, but not as much as many ZDs.

\begin{figure}[!htbp]
    \centering
        \centering
        \includegraphics[width=\textwidth]{../images/probend_discussion.pdf}
        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
        for the winners of probabilistic ending tournaments.}
        \label{fig:discussion_probend}
\end{figure}

The distributions of the \(CD\) to \(C\) rate evaluate the behaviour of a
successful strategy after its opponent has defected against it. In standard
tournaments it was observed that a successful strategy reciprocates with a
probability of 0.5, and in a setting that the type
of the tournament can vary between all the examined types a winning strategy
would reciprocate on average with a probability of 0.58. In
tournaments with noise a strategy is less likely to cooperate following a
defection compared to standard tournaments, and in probabilistic ending
tournaments a strategy will reciprocate a defection.
This leads to adjusting the recommendation of being provocable to defections made
by Axerlod. A strategy should be provocable in tournaments with short matches,
but in the rest of the settings a strategy should be more generous.

\begin{figure}[!htbp]
    \centering
        \centering
        \includegraphics[width=\textwidth]{../images/probend_noisy_discussion.pdf}
        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
        for the winners of noisy probabilistic ending tournaments.}
        \label{fig:discussion_probend_noisy}
\end{figure}

Further statistically significant features with strong effects include \(C_r /
C_{\text{min}}\), \(C_r / C_{\text{max}}\), \(C_{\text{min}}\) and
\(C_{\text{max}}\). These add more emphasis on how important it is for a  a
strategy to adapt to its environment. Finally, the features number of turns,
repetitions and the probabilities of noise and the game ending had no
significant effects based on the multivariate regression models.

\begin{figure}[!htbp]
    \centering
        \centering
        \includegraphics[width=\textwidth]{../images/entire_data_discussion.pdf}
        \caption{Distributions of \(C_r / C_{\text{mean}}\), SSE and \(CD\) to \(C\) ratio
        for the winners over the tournaments of the entire data set.}
        \label{fig:discussion_entire_data}
\end{figure}

### 2023-12-01 paper/main.tex
last corrections to the paper and commit si

@@
 \usepackage[table]{xcolor}
+\usepackage{authblk}
 %%%%%%%%%%%%%%%%%
@@
 \title{Properties of Winning Iterated Prisoner's Dilemma Strategies.}
-\author{Nikoleta E. Glynatsi, Vincent A. Knight, Marc Harper}
+\author[1]{Nikoleta E. Glynatsi}
+\author[2]{Vincent Knight}
+\author[3]{Marc Harper}
+
+\affil[1]{Max Planck Institute for Evolutionary Biology, Research Group Dynamics of Social
+Behavior, Germany}
+\affil[2]{Cardiff University, School of Mathematics, UK}
+\affil[3]{Google Inc., Mountain View, CA, USA}
 \date{}
@@
 of conclusions. We analyze a large collection of \numberofstrategies
-strategies in thousands of tournaments, present the top performing strategies across multiple
+strategies in thousands of computer tournaments, present the top performing strategies across multiple
 tournament types, and distill their salient features.
@@
 autonomous agents. Understanding the crucial features for incorporation into
-these agents becomes paramount.
+these agents becomes essential.
 \end{abstract}
-
-% or a proportion thereof in the case of noisy and probabilistically ending tournaments,
-% and that the manner in which a strategy achieves the ideal cooperation rate is crucial.
 
@@
 strategy for the \IPD, often without extensive testing against a broad spectrum
-of opponents or representative classes of opponents. This lack of comprehensive
-testing against formally defined strategies and tournament winners is
-justified given the substantial effort required to implement the numerous
-published \IPD{} strategies. The accuracy of implementing prior strategies is
-often hindered by insufficient descriptions and a dearth of published
+of opponents or representative classes of opponents. The lack of testing against
+formally defined strategies and tournament winners is understandable given the
+effort required to implement the hundreds of published \IPD{} strategies.
+Implementing prior strategies faithfully is often extremely difficult or
+impossible due to insufficient descriptions and lack of published
 implementations or code. Despite these challenges, the absence of thorough
@@
     \item Reciprocate both cooperation and defection appropriately;
-    Be provocable in tournaments with short matches, and generous when matches are longer
+    Be provocable in tournaments with short matches, and generous in tournaments with noise
     \item  It's ok to be clever
@@
     \begin{center}
-    \resizebox{.9\textwidth}{!}{
+    \resizebox{.8\textwidth}{!}{
         \input{correlations_table.tex}
@@
 \end{center}
-\caption{Correlations between the features of Table~\ref{table:manual_features}
-and the normalised rank and the median score.}\label{table:correlations}
+\caption{\textbf{Correlations between the features of Table~\ref{table:manual_features}
+and the normalised rank and the median score.}
+The correlation coefficients are calculated using the Spearman's rank
+correlation coefficient.}\label{table:correlations}
 \end{table}
 
-In standard tournaments the features $CC$ to $C$, $C_r$, $C_r / C_{\text{max}}$
-and the cooperating ratio compared to $C_{\text{median}}$ and $C_{\text{mean}}$
-have a moderately negative effect on the normalised rank (smaller rank is better), and a moderate positive
-on the median score. The SSE error and the $DD$ to $C$ rate have the opposite
-effects. Thus, in standard tournaments behaving cooperatively corresponds to a
-more successful performance. Even though being nice generally pays off
-that does not hold against defective strategies. Being more cooperative after a mutual
-defection, that is not retaliating, is associated to lesser overall success in terms of normalised rank.
+In standard tournaments, the features \(CC\) to \(C\), \(C_r\), \(C_r /
+C_{\text{max}}\), and the cooperating ratio compared to \(C_{\text{median}}\)
+and \(C_{\text{mean}}\) have a moderately negative effect on the normalized rank
+(a smaller rank is better) and a moderate positive effect on the median score.
+The SSE error and the \(DD\) to \(C\) rate have the opposite effects. Thus, in
+standard tournaments, behaving cooperatively corresponds to a more successful
+performance. Even though being nice generally pays off, that does not hold
+against defective strategies. Being more cooperative after a mutual defection,
+that is not retaliating, is associated with lesser overall success in terms of
+normalized rank.
 Compared to standard tournaments, in both noisy and noisy probabilistic ending
-tournaments the higher the rates of cooperation the lower a strategy's success
-and median score. A strategy would not want to cooperate more than both
-the mean and median cooperator in such settings. In probabilistic ending
-tournaments, the cooperation rate of the winners and it's relative comparison
-to the cooperation rates of the tournament have no effect. The only features
-that have an effect are the $CD$ to $C$ rate, which is the tendency of a strategy
-to forgive and the SSE rate have a positivist effect on the normalised rank.
+tournaments, the higher the rates of cooperation, the lower a strategy's success
+and median score. A strategy would not want to cooperate more than both the mean
+and median cooperator in such settings. In probabilistic ending tournaments, the
+cooperation rate of the winners and its relative comparison to the cooperation
+rates of the tournament have no effect. The only features that have an effect
+are the \(CD\) to \(C\) rate, which is the tendency of a strategy to forgive,
+and the SSE rate, which has a positive effect on the normalized rank.
 
 A multivariate linear regression has been fitted to model the relationship
-between the features and the normalised rank. Based on the graphical
-representation of the correlation matrices given in Supplementary Information
-several of the features are highly correlated and have been removed before
-fitting the linear regression model. The features included are given by
+between the features and the normalized rank. Based on the graphical
+representation of the correlation matrices given in the Supplementary
+Information, several features are highly correlated and have been removed before
+fitting the linear regression model. The features included are given in
 Table~\ref{table:linear_regression} alongside their corresponding \(p\) values
-in the distinct tournaments and their regression coefficients. The rate $CD$ to
-$C$ has a positively statistically significant effect on the normalized rank,
-across all tournament types. This suggests that forgiveness tends to lower one's
-performance. In the case of probabilistic ending tournaments, the coefficient of
-the $CD$ to $C$ rate is the highest, indicating that one is more harshly
-``punished'' when showing forgiveness. Similarly, the SEE error rate has a
+in distinct tournaments and their regression coefficients. The \(CD\) to \(C\)
+rate has a positively statistically significant effect on the normalized rank
+across all tournament types. This suggests that being generous tends to
+lower one's performance. In the case of probabilistic ending tournaments, the
+coefficient of the \(CD\) to \(C\) rate is the highest, indicating that one
+should be more provocative in this setting. Similarly, the SEE error rate has a
 positive effect on the normalized rank, suggesting that being extortionate pays
-off, especially in noisy tournaments. The measures of cooperation, $C_r$ and
-$C_r / C_{\text{max}}$, also exhibit a significant effect. In noisy
+off, especially in noisy tournaments. The measures of cooperation, \(C_r\) and
+\(C_r / C_{\text{max}}\), also exhibit a significant effect. In noisy
 probabilistic ending tournaments, this effect is positive; however, the
@@
     \begin{center}
-\resizebox{\textwidth}{!}{
+\resizebox{.8\textwidth}{!}{
     \input{regression_table.tex}}
@@
 
-A third method that evaluates the importance of the features in
-Table~\ref{table:manual_features} using clustering and random forests can be
-found in the Supplementary Information. The results uphold the outcomes of the
-correlation and multivariate regression. It also evaluates the effects of the
-whether or not a strategy is stochastic, makes use of the knowledge of the
-utility values, or makes use of match length. These were not evaluated by the
-methods above because there are binary variables. The results showed that they
-have no significant effect on a strategy's performance.
-
-The results presented here suggest that forgiveness and a strategy's cooperation
-rate, particularly in comparison to the tournament averages, are significant
-features. The findings imply that the
-forgiveness exhibited by strategies may not consistently contribute to favorable
-outcomes. Nevertheless, it is essential to exercise caution in extrapolating the
-implications of this analysis. For example, the analysis is limited as we only
+The results presented here suggest that generosity/provocation and a strategy's
+cooperation rate, particularly in comparison to the tournament averages, are
+significant features. The analysis suggests that strategies should be more
+generous in noisy tournaments and less generous in probabilistic ending
+tournaments. Moreover, strategies should aim to not cooperate more than the mean
+cooperator in their tournaments. We note the analysis is limited as we only
 consider a linear relationship between these parameters and the rank. To further
@@
 of the tournament, and we observe that this occurs for most tournament types,
-apart from the case of noisy and probabilistically ending tournaments. In the
-case of noisy tournaments, there are winners that did not cooperate exactly as
-such but are fairly distributed around 1. Interestingly, in the case of
+apart from the case of noisy and probabilistically ending tournaments. In the case of
 probabilistic ending tournaments, there are several winners that cooperated much
 less than that, confirming the results of the previous section that defecting
-strategies can we winner in probabilistic ending tournaments. The distribution
+strategies can be winners in probabilistic ending tournaments. The distribution
 of the cooperation rates showcases a high cooperation rate in standard
@@
         \caption{\textbf{Distributions of SSE error for the winners of
-        tournaments.} An SSE distribution skewed towards 0 indicates a
-        extortionate behaviour by the strategy.}
+        tournaments.} As a reminder, the SSE error shows how close a strategy is
+        to behaving as a ZDs, and subsequently, in an extortionate way. A SSE
+        value of 1 indicates no extortionate behaviour at all whereas a value of
+        0 indicates that a strategy is behaving as a ZDs.}
         \label{fig:discussion_sse}
@@
 after mutual cooperation. Regarding the \(CD\) outcome and the likelihood to
-cooperate after such a result, capturing forgiveness, the distributions skew
+cooperate after such a result, capturing generosity, the distributions skew
 towards 1/2, not 1, suggesting that strategies need to reduce their readiness to
 forgive. This aligns with the known result that Generous Tit For Tat generally
-outperforms \TFT{} in most settings. Interestingly, in probabilistic ending
-tournaments, there is a peak at 0, suggesting that in such tournaments,
-strategies should not be too generous in short matches.
+outperforms \TFT{} in most settings. In probabilistic ending tournaments, there
+is a peak at 0, suggesting that strategies should not be too generous in
+tournaments with short matches. Such a peak also appears in standard
+tournaments; however, not in tournaments with noise, where a strategy should be
+more generous.
 
-A strategy's effort to make amends is captured by the distributions of the
-\(DC\) to \(C\) rates. In noisy tournaments, winners are less likely to
-cooperate after a defection; however, there are still behaviors that attempt to
-make up for their defection. In standard tournaments and probabilistic ending
-tournaments, we observe two hubs of behaviors, one at 0 and one at 0.4-0.5,
-indicating that some winners are exploiting whether to try to make up, but with
-a small probability. This is also reflected in the \(DD\) to \(D\) rates, where
-in standard and probabilistic ending tournaments, there are winners that attempt
-to recover from a \(DD\) outcome. The remaining results are as expected, skewed
-towards 0.
+Part of a strategy's envious behavior can be captured by the rate of \(DC\) to
+\(C\). In noisy tournaments, winners are not too envious, but in tournaments
+without noise, we can see that winners behave in two ways. Some are a bit
+envious, whereas others are very envious. In the \(DD\) to \(D\), we can observe
+that, expectedly, the results are skewed towards 0. However, there are winners
+that attempt to recover from a \(DD\) outcome. The remaining results are as
+expected, skewed towards 0.
 
@@
 standard settings, and that in fact the only setting a strategy would want to be
-too provocable is when the matches are not long. Forgiveness as defined by R.
+too provocable is when the matches are not long.
+Forgiveness as defined by
 Axerlod was not explored here. This was mainly because the two round states were
@@
 more specifically, to the mean cooperator. 
-In standard tournaments a strategy would aim to be the
-mean cooperator while in noisy tournaments the best performing players
-cooperate at a lower rate than the tournament population on average.
+In most tournament types, the winner of the tournament was also the average
+cooperator. Even in tournaments with short matches where defecting behavior
+could secure a win, a large number of winners were average cooperators.
 
-This could potentially explain the early success of TFT. TFT naturally achieves
+This could potentially explain the early success of \TFT. \TFT{} naturally achieves
 a cooperation rate near $C_{\text{mean}}$ by virtue of copying its opponent's
@@
 conditional on the previous round of play, these features can be optimized by a
-memory-one strategy such as TFT. Usage of more history becomes valuable when
+memory-one strategy such as \TFT. Usage of more history becomes valuable when
 there are exploitable opponent patterns. This is indicated by the importance of
@@
 
-Overall, the five properties successful strategies need to have in a IPD competition
+Overall, the five properties successful strategies need to have in a \IPD{} competition
 based on the analysis that has been presented in this manuscript are:
@@
     \item Be ``nice'' in non-noisy environments or when game lengths are longer
-    \item Be provocable in tournaments with short matches, and generous when matches are longer
+    \item Be provocable in tournaments with short matches, and generous in tournaments with noise
     \item Be a little bit envious
@@
 
-The data set described in this work contains the largest number of IPD
+The results presented here were based only on a subset of the whole data we have
+collected. The analysis of the full dataset is discussed in the Supplementary Information.
+However, we can see that the general results of our work remain the same. In the
+Supplementary Information, we also evaluate the importance of features using a
+random forest classifier and a clustering approach. The results of these
+analyses are also in line with the results presented here.
+
+The data set described in this work contains the largest number of \IPD{}
 tournaments, to the authors knowledge. The raw data set is available

### 2023-12-01 paper/result_with_entire_dataset.tex
last corrections to the paper and commit si

@@
-\section{Top ranked strategies and features analysis for the entire data set}
+\section{Top ranked strategies and features analysis for the entire data set}\label{app:analysis_full_dataset}
 
@@
 \end{figure}
+
+A third method that evaluates the importance of features using clustering and
+random forests can be found in the Section~\ref{app:clustering}. The results uphold
+the outcomes of the correlation and multivariate regression. It also evaluates
+the effects of the whether or not a strategy is stochastic, makes use of the
+knowledge of the utility values, or makes use of match length. These were not
+evaluated by the methods above because there are binary variables. The results
+showed that they have no significant effect on a strategy's performance.

### 2023-12-01 paper/si.tex
last corrections to the paper and commit si

--- 2023-12-01 paper/main.tex
@@
 \usepackage{soul}
-\usepackage{enumerate}
 \usepackage[table]{xcolor}
 %%%%%%%%%%%%%%%%%
-
-\newcommand{\colortext}[1]{\textcolor{blue}{#1}}
 
@@
 \newcommand{\numberofstrategies}{\input{unique_number_of_strategies.tex}}
-\def\axelrod{\texttt{Axelrod-Python}}
-\def\TFT{\texttt{TFT}}
-\def\IPD{\texttt{IPD}}
+\def\axelrod{\texttt{Axelrod-Python }}
 
@@
 
-\title{Properties of Winning Iterated Prisoner's Dilemma Strategies.}
+\title{{\LARGE Electronic supplementary material}\\{\bf \LARGE Properties of Winning Iterated Prisoner's Dilemma Strategies}}
 \author{Nikoleta E. Glynatsi, Vincent A. Knight, Marc Harper}
@@
 \begin{document}
-
 \maketitle
 
-\begin{abstract}
-Researchers have explored the performance of Iterated Prisoner's Dilemma strategies
-for decades: from the celebrated performance of Tit for Tat, to the
-introduction of the zero-determinant strategies, to the use of sophisticated learning
-structures such as neural networks. Many new strategies have been introduced and tested
-in a variety of tournaments and population dynamics. Typical results in the literature,
-however, rely on performance against a small number of somewhat arbitrarily selected
-strategies in a small number of tournaments, casting doubt on the generalizability
-of conclusions. We analyze a large collection of \numberofstrategies
-strategies in thousands of tournaments, present the top performing strategies across multiple
-tournament types, and distill their salient features.
-The results show that there is not yet a single
-strategy that performs well in diverse Iterated Prisoner's Dilemma scenarios,
-nevertheless there are several properties that heavily influence the best performing
-strategies. This refines the properties described by Axelrod in light of
-recent and more diverse opponent populations to: be nice, be provocable and generous,
-be a little envious, be clever, and adapt to the environment. More precisely,
-we find that strategies perform best when their probability of cooperation
-matches the total tournament population's aggregate cooperation probabilities.
-The features of high performing strategies help cast some light on why
-strategies such as Tit For Tat performed historically well in tournaments and
-why zero-determinant strategies typically do not fare well in tournament
-settings. Furthermore, our findings have implications for the future training of
-autonomous agents. Understanding the crucial features for incorporation into
-these agents becomes paramount.
-\end{abstract}
+%% BRIEF INTRO %%
 
-% or a proportion thereof in the case of noisy and probabilistically ending tournaments,
-% and that the manner in which a strategy achieves the ideal cooperation rate is crucial.
+\noindent
+This document provides additional details and analysis based on the complete
+datasets for noisy and probabilistic ending tournaments. In
+Section~\ref{app:parameters}, a summary of all parameters and notation used in
+the manuscript is presented. Section~\ref{app:analysis_full_dataset} offers
+further details on the correlation analysis and includes additional information.
+In Section~\ref{app:correlations}, we present the results of the correlation
+analysis when all features of the strategies are considered. In
+Section~\ref{app:clustering}, the results of the random forest and clustering
+evaluations with the inclusion of all features are discussed.
+Section~\ref{app:regression_median_score} presents the results of the regression
+analysis on the median score of the strategies. Finally, in
+Section~\ref{app:list_of_players}, a comprehensive list of all strategies
+considered in this work is provided.
 
-\section{Background}
-
-The Iterated Prisoner's Dilemma (\IPD) is a repeated two-player game that models
-behavioral interactions, specifically interactions where self-interest clashes
-with collective interest. In each turn of the game, both players simultaneously
-and independently decide between cooperation (\(C\)) and defection (\(D\)). This
-decision is made with the memory of all prior interactions. The payoffs for each
-player at each turn are influenced by their own choice, and the choice of the
-other player. To this end, the payoffs of the game are defined by,
-
-\begin{center}
-{\renewcommand{\arraystretch}{2}%
-\begin{tabular}{c|c|c}
-& Cooperate (\(C\)) & Defect (\(D\)) \\
-\hline
-Cooperate (\(C\)) & \(R, R\) & \(S, T\) \\
-\hline
-Defect (\(D\)) & \(T, S\) & \(P, P\) \\
-\end{tabular}}
-\end{center}
-
-where typically \(T > R > P > S\) and \(2R > T + S\). The most common values
-used in the literature~\cite{Axelrod1981} are \(R=3\), \(P=1\), \(T=5\),
-\(S=0\), and these are the values also used in this work.
-
-Conceptualizing strategies and understanding the best way to play the game have
-been of interest to the scientific community since the formulation of the game
-in 1950~\cite{Flood1958}. Following Axelrod's computer tournaments in the
-1980s~\cite{Axelrod1980a, Axelrod1980b}, round-robin computer tournaments became
-a common evaluation technique for newly designed strategies.
-The winner of both of Axelrod's tournaments~\cite{Axelrod1980a, Axelrod1980b}
-was the simple strategy Tit For Tat (\TFT{}). \TFT{} cooperates on the first turn
-and thereafter copies the previous action of its opponent, retaliating against
-defections with a defection and forgiving a defection if followed by
-cooperation. Axelrod concluded that the strategy's robustness was due to four
-properties, which he adapted into four suggestions for success in an \IPD{}
-tournament:
-
-\begin{enumerate}[(i)]
-    \item Do not be envious by striving for a payoff larger than the opponent's payoff.
-    \item Be ``nice''; Do not be the first to defect.
-    \item Reciprocate both cooperation and defection; Be provocable to retaliation and forgiveness.
-    \item Do not be too clever by scheming to exploit the opponent.
-\end{enumerate}
-
-Forgiveness, in this context, is a strategy's ability to cooperate after a
-\(DC\) outcome to achieve mutual cooperation again. In environments without
-noise, \TFT{} would end up in \(DC\) only if it had received a defection and
-then retaliated. Subsequently, \TFT{} would forgive an opponent that apologizes
-(in a \(DC\) round) by returning to cooperation, as mutual cooperation is deemed
-better than mutual defection.
-
-Due to the strategy's strong performance in both tournaments and a series of
-evolutionary experiments~\cite{Axelrod1981}, \TFT{} was often claimed to be a
-highly robust (and sometimes the most robust) strategy for the \IPD.
-There are strategies that have built upon \TFT{} and the reciprocity-based
-approach. In~\cite{Beaufils1997}, a strategy called Gradual was introduced,
-constructed to have the same qualities as those of \TFT{} with one
-addition. Gradual has a memory of the previous rounds of play in the game,
-recording the number of defections by the opponent and punishing them with a
-growing number of defections. It then enters a calming state in which it
-cooperates for two rounds. A strategy with the same intuition as Gradual is
-Adaptive Tit for Tat~\cite{tzafestas-2000a}. Adaptive Tit for Tat maintains a
-continually updated estimate of the opponent's behavior and uses this estimate
-to condition its future actions.
-Other research has built upon the limitations of \TFT. For example,
-in~\cite{Bendor1991, Donninger1986, Molander1985, Hammerstein1984}, it was shown
-that \TFT{} suffered in environments with noise. This was mainly due to the
-strategy being too provocable and its lack of generosity and contrition. Since
-\TFT{} immediately punishes a defection, in a noisy environment, it can get
-stuck in a repeated cycle of defections and cooperations. Some new strategies,
-more robust in tournaments with noise, were soon introduced, including Nice and
-Forgiving~\cite{Bendor1991}, Generous Tit For Tat~\cite{Nowak1992}, and Pavlov
-(aka Win Stay Lose Shift)~\cite{Nowak1993}, as well as later variants such as
-OmegaTFT \cite{kendall2007iterated}.
-
-Finally, others introduced strategies deviating completely from the originally
-suggested properties of success. For example, a set of ``envious'' Iterated
-Prisoner's Dilemma (\IPD) strategies were introduced, called zero-determinant
-strategies (ZDs), in~\cite{Press2012}. These strategies attempt to force a
-linear relationship between stationary payoffs against other memory-one
-opponents, potentially ensuring that they receive a higher average payout. While
-ZDs were introduced with a small tournament in which some were reportedly
-successful \cite{Stewart2012}, this result has not generally held in future
-work~\cite{mathieu2017}. Furthermore, in~\cite{Harper2017}, a series of ``clever''
-strategies trained using reinforcement learning were introduced. These
-strategies were trained using lookup tables~\cite{Axelrod1987}, hidden Markov
-models~\cite{Harper2017}, and finite-state automata~\cite{Miller1996}, on
-on a set of 170 strategies.
-
-One thing that has remained the same is that the introduction of a new strategy
-is often accompanied by a claim that the new strategy is the best performing
-strategy for the \IPD, often without extensive testing against a broad spectrum
-of opponents or representative classes of opponents. This lack of comprehensive
-testing against formally defined strategies and tournament winners is
-justified given the substantial effort required to implement the numerous
-published \IPD{} strategies. The accuracy of implementing prior strategies is
-often hindered by insufficient descriptions and a dearth of published
-implementations or code. Despite these challenges, the absence of thorough
-testing raises concerns about claims regarding the superiority or robustness of
-newly introduced strategies.
-
-In this paper we evaluate the performance of a significant number of \IPD{}
-strategies across a diverse array of tournaments. Many of the strategies used in
-our analysis are drawn from well-known and named strategies in \IPD{} literature,
-including previous tournament winners. This contrasts with other work that may
-have randomly generated essentially arbitrary strategies, often constrained to
-specific classes such as memory-one strategies or those of a certain structural
-form like finite state machines or deterministic memory-two strategies.
-Furthermore, our tournaments encompass various variations, including standard
-tournaments resembling Axelrod's original ones, tournaments with noise,
-probabilistic match length, and both noise and probabilistic match length. This
-diversity in strategies and tournament types provides new insights and tests
-earlier claims in alternative settings against known powerful strategies.
-
-It is important to note that we do not assert the existence of a single
-best-performing strategy across all tournaments or tournament types. On the
-contrary, our work demonstrates that such a strategy does not exist. The primary
-objective of this paper, presented in the latter parts of the paper, is to
-continue the discussion on the properties of successful strategies, a
-conversation started by Axelrod. 
-The results of our analysis conclude that the properties of a successful
-strategy in the Iterated Prisoner's Dilemma (\IPD{}) are:
-
-\begin{enumerate}[(i)]
-    \item Be a little bit envious
-    \item Be ``nice'' in non-noisy environments or when game lengths are longer
-    \item Reciprocate both cooperation and defection appropriately;
-    Be provocable in tournaments with short matches, and generous when matches are longer
-    \item  It's ok to be clever
-    \item Adapt to the environment; Adjust to the mean population cooperation
-\end{enumerate}
-
-We believe that the discussion on the properties of winning strategies holds
-significant importance. It aims to provide guidance to researchers designing new
-strategies and those training strategies. Moreover, conducting a similar
-analysis can shed light on already trained strategies, aiding in understanding
-the key features they have autonomously developed during their training
-processes.
-% ToDO: Not sure if this is enough to justify how our work is important for AI.
-% It would be nice to have a sentence or two since it fits the special issue
-% theme.
-
-The rest of the paper is organized as follows. In
-section~\ref{section:data_collection}, we describe the data collection process.
-In subsection~\ref{section:top_performances}, we present the best performing
-strategies for each type of tournament.
-Subsection~\ref{section:evaluation_of_performance} explores the traits that
-contribute to good performance, and in
-subsection~\ref{section:winning_features}, we focus on the features of the
-winners of the tournaments. Finally, the results are summarized in
-section~\ref{section:conclusion}. This manuscript introduces several parameters,
-which are discussed in the following sections; the full set of parameters and
-their definitions are also provided in the Supplementary Material.
-
-\section{Data collection}\label{section:data_collection}
-
-The data collection of various types of tournaments and the use of different
-strategies are made possible due to an open-source library called \axelrod{}~\cite{axelrodproject}
-(version 3.0.0). \axelrod{} enables the simulation of \IPD{}
-tournaments and contains an extensive list of strategies. Most of these
-strategies are described in the literature, with a few exceptions contributed
-specifically to the package. In this paper, we use a total of
-\numberofstrategies strategies, which can be found in the Supplementary
-Material. The package supports several tournament types, and this work considers
-standard, noisy, probabilistic ending, and noisy probabilistic ending
-tournaments.
-
-{\it Standard tournaments} are similar to Axelrod's well-known
-tournaments~\cite{Axelrod1980a}. In these tournaments, there are \(N\)
-strategies, and each strategy plays an iterated game with \(n\) turns against
-all other strategies, not including self-interactions.
-{\it Noisy tournaments} also involve \(N\) strategies and \(n\) turns, but
-in each turn, there is a probability \(p_n\) that a player's action is
-flipped. Compared to these two tournaments, in 
-{\it probabilistic ending tournaments} the number of turns is not fixed. Instead,
-a match between strategies ends with a given probability
-\(p_e\).
-Finally, {\it noisy probabilistic ending tournaments} incorporate both a
-noise probability \(p_n\) and an ending probability \(p_e\). For smoother
-results, each tournament is repeated \(k\) times, and this repetition factor was
-allowed to vary to assess the impact of smoothing. The winner of each tournament
-is determined based on the average score achieved by a strategy from the entire
-set of repetitions, not by the number of wins.
-
-The process of collecting tournament results is outlined in
-Algorithm~\ref{algorithm:data_generation}. For each trial, a random size \(N\)
-is selected, and a random list of \(N\) strategies from the \numberofstrategies
-available. Subsequently, one standard, one noisy, one probabilistic ending, and
-one noisy probabilistic ending tournament are conducted for the selected list of
-strategies. The parameters for the tournaments, as well as the number of
-repetitions, are chosen once for each trial. We have run a total of
-\uniquenumberofseeds trials of Algorithm~\ref{algorithm:data_generation}. For
-each trial, we collect the results for four different tournaments, resulting in
-a total of \numberofalltournaments $(\uniquenumberofseeds \times 4)$ tournament
-results. Each tournament outputs a result summary in the form of
-Table~\ref{table:output_result}.
-
-\begin{algorithm}[!htbp]
-    \setstretch{1.35}
-    \For{\text{seed} $\in [0, 11420]$}{
-        $N \gets \text{randomly select integer}\in [3, 195]$\;
-        $\text{players} \gets  \text{randomly select $N$ players}$\;
-        $k \gets  \text{randomly select integer}\in [10, 100]$\;
-        $n \gets  \text{randomly select integer}\in [1, 200]$\;
-        $p_n \gets  \text{randomly select float}\in [0, 1]$\;
-        $p_e \gets   \text{randomly select float}\in [0, 1]$\;
-        \vspace{0.4cm}
-        $\text{result standard}$ $\gets$ Axelrod.tournament$(\text{players}, n, k)$\;
-        $\text{result noisy}$ $\gets$ Axelrod.tournament$(\text{players}, n, p_n, k)$\;
-        $\text{result probabilistic ending}$ $\gets$ Axelrod.tournament$(\text{players}, p_e, k)$\;
-        $\text{result noisy probabilistic ending}$ $\gets$ Axelrod.tournament$(\text{players}, p_n, p_e, k)$\;
-
-    }
-    \KwRet{result standard, result noisy, result probabilistic ending,
-    result noisy probabilistic ending}\;
-    \caption{Tournament Data Collection Algorithm}
-    \label{algorithm:data_generation}
-\end{algorithm}
-
-\newcolumntype{g}{>{\columncolor{Gray}}c}
-\begin{table}[b]
-    \begin{center}
-    \resizebox{\textwidth}{!}{
-    \begin{tabular}{ccccccgcgcgcgcg}
-    \toprule
-    & & & & & &   \multicolumn{8}{g}{Rates}  \\
-    Rank & Name & Median score & Cooperation rating $(C_r)$ & Win & Initial C &
-    CC & CD & DC & DD & CC to C & CD to C & DC to C & DD to C \\
-    0 &  EvolvedLookerUp2 2 2 & 2.97 & 0.705 & 28.0 & 1.0 & 0.639 & 0.066 & 0.189 &
-    0.106 & 0.836 & 0.481 & 0.568 & 0.8 \\
-    1 &  Evolved FSM 16 Noise 05 & 2.875 & 0.697 & 21.0 & 1.0 & 0.676 &
-    0.020 & 0.135 & 0.168 & 0.985 & 0.571 & 0.392 & 0.07 \\
-    2 & PSO Gambler 1 1 1 & 2.874 & 0.684 &  23.0 &     1.0 &    0.651 &    0.034 &    0.152 &    0.164
-    & 1.000 & 0.283 & 0.000 & 0.136 \\
-    3 &  PSO Gambler Mem1 &  2.861 &        0.706 &  23.0 &      1.0 &    0.663
-    &    0.042 &    0.145 &    0.150 &  1.000 &  0.510 &  0.000 &  0.122 \\
-    4 &          Winner12 &  2.835 &        0.682 &  20.0 &      1.0 &
-    0.651 &    0.031 &    0.141 &    0.177 &  1.000 &  0.441 &  0.000 &  0.462 \\
-    $\dots$ & $\dots$ & $\dots$ & $\dots$ & $\dots$ & $\dots$ & $\dots$ & $\dots$ &
-    $\dots$ & $\dots$ & $\dots$ & $\dots$ & $\dots$ & $\dots$ \\
-    \bottomrule
-    \end{tabular}}
-\end{center}
-\caption{\textbf{Result Summary Example of a Tournament.}
-A result summary consists of \(N\) rows, with each row containing information
-for each strategy that participated in the tournament. This information includes
-the strategy's rank (\(R\)), median score, the cooperation rate (\(C_r\)), the number of
-match wins, and the probability that the strategy cooperated in the opening
-move. Additionally, it provides the probabilities of a strategy being in any of
-the four states ($CC, CD, DC, DD$) and the cooperation rate after each state.}\label{table:output_result}
-\end{table}
-
-During the data collection process, the probabilities of noise (\(p_n\)) and
-tournament ending (\(p_e\)) were allowed to take values between 0 and 1.
-However, commonly used values for these probabilities are \(p_n \leq 0.1\) and
-\(p_e \leq 0.1\). This is to make the results more interpretable. For example,
-consider a strategy competing in an environment with \(p_n > 0.1\). In cases
-with a high value of noise, most of the actions the strategy takes are the
-complete opposite of what the strategy is designed to do. Therefore, we will
-focus on the tournaments for which \(p_n \leq 0.1\) and \(p_e \leq 0.1\). Thus,
-the results presented here pertain to subsets of the noisy and probabilistic
-ending tournaments. Specifically, the results rely on 1150 tournaments with
-noise, 1134 tournaments with a probabilistic ending, and 117 tournaments with
-both noise and a probabilistic ending. We also provide an analysis of the paper
-considering the entire datasets, and these results are presented in the
-Supplementary Material. The general results of the analysis are not affected by
-the restriction of the noise and probabilistic ending probabilities.
-%ToDo: Do we need to justify better why we only consider tournaments with
-%noisy and ending probabilities less than 0.1?
-
-\section{Results}
-\subsection{Top ranked strategies across tournaments}\label{section:top_performances}
-
-A strategy has participated in multiple tournaments of each type, and to
-evaluate its overall performance, we introduce a measure called the {\it
-normalized rank}. In each tournament, the strategies receive a rank (\(R\)), where 0
-denotes that the strategy was the winner, and \(N-1\) indicates that the
-strategy came last in the tournament. The normalized rank, denoted as \(r\), is
-calculated as \(r = \frac{R}{N-1}\). Thus, the rank a strategy achieved over the
-number of players in the tournament. The performance of the strategies is
-assessed based on the {\it median of the normalized rank}, denoted as
-\(\bar{r}\).
-
-For example, let's consider the well-known strategies \TFT{} and Gradual. Each
-strategy participated in several tournaments of each type. In
-Figure~\ref{fig:normalised_rank_distributions} we show the distribution of the
-normalised ranks of these strategies in each of the four tournaments. We can
-observe that \TFT{} has a normally distributed normalized rank. In comparison,
-Gradual's performance has longer tails, indicating that there were tournaments
-where the strategy performed very well or very poorly. Overall, Gradual achieves
-a lower median rank, signifying that it performs better than \TFT{} except in
-the case of noisy and probabilistic ending tournaments.
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=\textwidth]{../images/normalised_rank_distributions.pdf}
-    \caption{\textbf{Examples of normalized rank distributions for two
-    strategies, \TFT{} and Gradual.} We plot the distributions of \(r\) for the
-    two strategies in the four tournament types. As a reminder, lower values of
-    \(r\) correspond to better performances. The top left quadrant of each plot
-    shows the distribution for standard tournaments (fixed number of turns and
-    no noise). The top right quadrant shows the distribution for noisy
-    tournaments (fixed number of turns and noise). The bottom left quadrant
-    shows the distribution for probabilistic ending tournaments (no noise and
-    probabilistic ending). Finally, the bottom right quadrant shows the
-    distribution for noisy probabilistic ending tournaments (noise and
-    probabilistic ending). In each quadrant, we also show the number of data
-    points. Both strategies participated in a similar number of tournaments.
-    Based on the median rank, which we use in this work to define overall
-    performance, \TFT{} performs best in probabilistic ending tournaments,
-    whereas Gradual was in standard tournaments.}
-    \label{fig:normalised_rank_distributions}
-\end{figure}
-
-\begin{figure}[!htbp]
-    \centering
-    \includegraphics[width=\textwidth]{../images/top_performers.pdf}
-    \caption{\textbf{\(r\) distributions of the top 15 strategies in different
-    environments.} A lower value of \(\bar{r}\) corresponds to a more successful
-    performance. A strategy's \(r\) distribution skewed towards zero indicates
-    that the strategy ranked highly in most tournaments it participated in. Most
-    distributions are skewed towards zero.}\label{fig:r_distributions}
-\end{figure}
-
-\newcolumntype{g}{>{\columncolor{Gray}}l}
-\begin{table}[!htbp]
-    \begin{center}
-    \resizebox{\textwidth}{!}{
-        \input{top_perfomances.tex}
-    }
-\end{center}
-\caption{Top performances for each tournament type based on $\bar{r}$. The
-results of each type are based on 11420 unique tournaments. The
-results for noisy tournaments with \(p_n < 0.1\) are based on 1151 tournaments,
-and for probabilistic ending tournaments with \(p_e < 0.1\) on 1139. The top
-ranks indicate that trained strategies perform well in a variety of
-environments, but so do simple deterministic strategies. For noisy tournaments
-DBS is the top ranked strategy with \(\bar{r}=0\), thus DBS won every tournament
-it participated in. The same for Evolved FSM 16 Noise 05 in probabilistic ending.}
-\label{table:top_performances}
-\end{table}
-
-The top 15 strategies for each tournament type, based on \(\bar{r}\), are
-presented in Table~\ref{table:top_performances}, while the \(r\) distributions
-for the top-ranked strategies can be found in Figure~\ref{fig:r_distributions}.
-
-In standard tournaments dominating strategies were those
-trained using reinforcement learning techniques. 10 out of the 15 top strategies
-were introduced in~\cite{Harper2017}. These strategies are based on finite state
-automata (FSM), hidden Markov models (HMM), artificial neural networks (ANN),
-lookup tables (LookerUp), and stochastic lookup tables (Gambler). They have been
-trained using reinforcement learning algorithms (evolutionary and particle swarm
-algorithms) to perform well against a subset of the strategies in \axelrod{} in a
-standard tournament. Thus, their performance in the specific setting was
-anticipated, although still noteworthy given the random sampling of tournament
-participants. DoubleCrosser and BackStabber, both from the \axelrod, use the
-number of turns and are set to defect in the last two rounds. These strategies
-can be characterized as “cheaters” because their source code allows them to know
-the number of turns (unless the match has a probabilistic ending). These
-strategies were expected to not perform as well in tournaments where the number
-of turns is not specified. Finally, Winner 12~\cite{mathieu2017} and
-DBS~\cite{Au2006} are both from the literature. DBS is a strategy specifically
-designed for noisy environments; however, it ranks highly in standard
-tournaments as well. Similarly, the fourth-ranked player, Evolved FSM 16 Noise
-05, was trained for noisy tournaments yet performs well in standard tournaments.
-
-In the case of noisy tournaments, the
-top-performing strategies include strategies specifically designed for noisy
-tournaments. These are DBS, Evolved FSM 16 Noise 05, Evolved ANN 5 Noise 05, PSO
-Gambler 2 2 2 Noise 05, and Omega Tit For Tat~\cite{kendall2007iterated}. Omega
-TFT, a strategy designed to break the deadlocking cycles of \(CD\) and \(DC\)
-that TFT can fall into in noisy environments, places 10th. The rest of the top
-ranks are occupied by strategies that performed well in standard tournaments and
-deterministic strategies such as Spiteful Tit For Tat~\cite{prison}, Level
-Punisher~\cite{Eckhart2015}, Eugine Nier~\cite{lesswrong}.
-
-Furthermore, in tournaments with probabilistic endings, the highly ranked
-strategies leaned towards defecting strategies and trained finite state
-automata, as demonstrated by the works of Ashlock et
-al.\cite{Ashlock2006,Ashlock2014}. The most effective strategies in
-probabilistic ending tournaments are also a series of ensemble Meta strategies,
-trained strategies that performed well in standard tournaments, and
-Grudger\cite{axelrodproject} and Spiteful Tit for Tat~\cite{prison}. The Meta
-strategies~\cite{axelrodproject} utilize a team of strategies and aggregate the
-potential actions of the team members into a single action in various ways.
-
-While no single strategy consistently outperforms all others in any of the
-distinct tournament types or across various tournament types, certain types of
-strategies consistently achieve top rankings. These include strategies that have
-undergone training, those that retaliate, and those that adapt their behavior
-based on preassigned rules to optimize outcomes. These findings challenge some
-of Axelrod's suggestions, particularly the advice to ``not be clever'' and ``not
-be envious''.
-
-\subsection{The effect of strategy features on performance}\label{section:evaluation_of_performance}
-
-For each strategy, we have a variety of features as described in
-Table~\ref{table:manual_features}. These features capture measures related to a
-strategy's behavior in the tournaments it competed in, as well as intrinsic
-properties, such as whether a strategy is deterministic or stochastic. The
-correlation coefficients between the features for performance evaluation, the
-median score and the median normalised rank are given by
-Table~\ref{table:correlations}. The correlation coefficients between all
-features have also been calculated and a graphical representation can be found
-in the Supplementary Material.
-
-\newcolumntype{g}{>{\columncolor{Gray}}c}
-\begin{table}[!htbp]
-    \begin{center}
-    \resizebox{.99\textwidth}{!}{
-    \begin{tabular}{gcgcgc}
-    \toprule
-    feature & feature explanation &  source & value type & min value & max value \\
-    \midrule
-stochastic  &  If a strategy is stochastic & strategy classifier from APL & boolean  & Na &  Na \\
-makes use of game &  If a strategy makes used of the game information & strategy classifier from APL & boolean  & Na &  Na \\
-makes use of length &  If a strategy makes used of the number of turns & strategy classifier from APL & boolean  & Na &  Na \\
-memory usage &  The memory size of a strategy divided by the number of turns & memory size from APL & float & 0 &  1 \\
-SSE & A measure of how far a strategy is from ZD behaviour & method described in~\cite{Knight2019} & float & 0 & 1 \\
-max cooperating rate $(C_{\text{max}})$  & The biggest cooperating rate in a given tournament  & result summary  & float & 0 & 1\\
-min cooperating rate $(C_{\text{min}})$ & The smallest cooperating rate in a given tournament  & result summary  & float & 0 & 1\\
-median cooperating rate $(C_{\text{median}})$ & The median cooperating rate in a given tournament  & result summary  & float & 0 & 1\\
-mean cooperating rate $(C_{\text{mean}})$ & The mean cooperating rate in a given tournament  & result summary  & float & 0 & 1 \\
-$C_r$ / $C_{\text{max}}$ & A strategy's cooperating rate divided by the maximum & result summary  & float & 0 & 1 \\
-$C_{\text{min}}$ / $C_r$ & A strategy's cooperating rate divided by the minimum & result summary  & float & 0 & 1 \\
-$C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median  & result summary  & float & 0 & 1\\
-$C_r$ / $C_{\text{mean}}$ & A strategy's cooperating rate divided by the mean & result summary  & float & 0 & 1 \\
-$C_r$ & The cooperating ratio of a strategy & result summary  & float & 0 & 1 \\
-$CC$ to $C$ rate & The probability a strategy will cooperate after a mutual cooperation & result summary  & float & 0 & 1\\
-$CD$ to $C$ rate & The probability a strategy will cooperate after being betrayed by the opponent & result summary  & float & 0 & 1 \\
-$DC$ to $C$ rate & The probability a strategy will cooperate after betraying the opponent & result summary  & float & 0 & 1 \\
-$DD$ to $C$ rate & The probability a strategy will cooperate after a mutual defection & result summary  & float & 0 & 1 \\
-$p_n$ & The probability of a player's action being flip at each interaction & trial summary & float & 0 & 1 \\
-$n$ & The number of turns & trial summary & integer & 1 & 200 \\
-$p_e$ & The probability of a match ending in the next turn & trial summary & float & 0 & 1 \\
-$N$ & The number of strategies in the tournament & trial summary & integer & 3 & 195 \\
-$k$ & The number of repetitions of a given tournament & trial summary & integer & 10 & 100 \\
-    \bottomrule
-        \end{tabular}}
-    \end{center}
-    \caption{\textbf{Included features for performance evaluation analysis.}
-    Stochastic, makes use of length and makes use of game are APL
-    classifiers that determine whether a strategy is stochastic or deterministic,
-    whether it makes use of the number of turns or the game's payoffs. The
-    memory usage is calculated as the number of turns the strategy considers to
-    make an action (which is specified in the APL) divided by the number of
-    turns. The SSE (introduced in~\cite{Knight2019}) shows how close a strategy
-    is to behaving as a ZDs, and subsequently, in an extortionate way. The
-    method identifies the ZDs closest to a given strategy and calculates the
-    algebraic distance between them as the sum of squared error (SSE). A SSE value of 1 indicates
-    no extortionate behaviour at all whereas a value of 0 indicates that a
-    strategy is behaving as a ZDs. The
-    memory usage of strategies is the number of rounds of play used by the strategy
-    when deciding on an action,  divided by the number of turns in each match. For
-    example, Winner12 uses the previous two rounds of play, and if participating in
-    a match with 100 turns its memory usage would be 2/100. For strategies with an
-    infinite memory size, for example Evolved FSM 16 Noise 05, memory usage is equal
-    to 1. Note that for tournaments with a probabilistic ending the number of turns
-    was not collected, so the memory usage feature is not used for probabilistic
-    ending tournaments. The rest of the features considered are the $CC$
-    to $C$, $CD$ to $C$, $DC$ to $C$, and $DD$ to $C$ rates as well as
-    cooperating ratio of a strategy, the minimum (\(C_{min}\)), maximum
-    (\(C_{max}\)), mean (\(C_{mean}\)) and median (\(C_{median}\)) cooperating
-    ratios of each tournament.}
-    \label{table:manual_features}
-\end{table}
-
-\newcolumntype{g}{>{\columncolor{Gray}}c}
-\begin{table}[!htbp]
-    \begin{center}
-    \resizebox{.9\textwidth}{!}{
-        \input{correlations_table.tex}
-    }
-\end{center}
-\caption{Correlations between the features of Table~\ref{table:manual_features}
-and the normalised rank and the median score.}\label{table:correlations}
-\end{table}
-
-In standard tournaments the features $CC$ to $C$, $C_r$, $C_r / C_{\text{max}}$
-and the cooperating ratio compared to $C_{\text{median}}$ and $C_{\text{mean}}$
-have a moderately negative effect on the normalised rank (smaller rank is better), and a moderate positive
-on the median score. The SSE error and the $DD$ to $C$ rate have the opposite
-effects. Thus, in standard tournaments behaving cooperatively corresponds to a
-more successful performance. Even though being nice generally pays off
-that does not hold against defective strategies. Being more cooperative after a mutual
-defection, that is not retaliating, is associated to lesser overall success in terms of normalised rank.
-Compared to standard tournaments, in both noisy and noisy probabilistic ending
-tournaments the higher the rates of cooperation the lower a strategy's success
-and median score. A strategy would not want to cooperate more than both
-the mean and median cooperator in such settings. In probabilistic ending
-tournaments, the cooperation rate of the winners and it's relative comparison
-to the cooperation rates of the tournament have no effect. The only features
-that have an effect are the $CD$ to $C$ rate, which is the tendency of a strategy
-to forgive and the SSE rate have a positivist effect on the normalised rank.
-
-A multivariate linear regression has been fitted to model the relationship
-between the features and the normalised rank. Based on the graphical
-representation of the correlation matrices given in Supplementary Information
-several of the features are highly correlated and have been removed before
-fitting the linear regression model. The features included are given by
-Table~\ref{table:linear_regression} alongside their corresponding \(p\) values
-in the distinct tournaments and their regression coefficients. The rate $CD$ to
-$C$ has a positively statistically significant effect on the normalized rank,
-across all tournament types. This suggests that forgiveness tends to lower one's
-performance. In the case of probabilistic ending tournaments, the coefficient of
-the $CD$ to $C$ rate is the highest, indicating that one is more harshly
-``punished'' when showing forgiveness. Similarly, the SEE error rate has a
-positive effect on the normalized rank, suggesting that being extortionate pays
-off, especially in noisy tournaments. The measures of cooperation, $C_r$ and
-$C_r / C_{\text{max}}$, also exhibit a significant effect. In noisy
-probabilistic ending tournaments, this effect is positive; however, the
-coefficient is very close to zero. In other tournament types, the effect is
-negative, indicating that one should aim to be less cooperative than the mean
-cooperator of the tournament. However, we cannot interpret the result as
-suggesting that a strategy should be as uncooperative as possible.
-
-\newcolumntype{g}{>{\columncolor{Gray}}c}
-\begin{table}[!htbp]
-    \begin{center}
-\resizebox{\textwidth}{!}{
-    \input{regression_table.tex}}
-    \end{center}
-    \caption{\textbf{Results of multivariate linear regressions with \(r\) as
-    the dependent variable.} \(R\) squared is reported for each model. The $R$
-    scores of the fitted models indicate their capability to explain some of the
-    variation in the median rank. Most of the features have a statistically
-    significant effect on the normalized rank.
-    A multivariate linear regression has also be fitted on the median score. The
-    coefficients and \(p\) values of the features can be found in
-    Supplementary Information. Both approaches lead to similar conclusions.}
-    \label{table:linear_regression}
-\end{table}
-
-A third method that evaluates the importance of the features in
-Table~\ref{table:manual_features} using clustering and random forests can be
-found in the Supplementary Information. The results uphold the outcomes of the
-correlation and multivariate regression. It also evaluates the effects of the
-whether or not a strategy is stochastic, makes use of the knowledge of the
-utility values, or makes use of match length. These were not evaluated by the
-methods above because there are binary variables. The results showed that they
-have no significant effect on a strategy's performance.
-
-The results presented here suggest that forgiveness and a strategy's cooperation
-rate, particularly in comparison to the tournament averages, are significant
-features. The findings imply that the
-forgiveness exhibited by strategies may not consistently contribute to favorable
-outcomes. Nevertheless, it is essential to exercise caution in extrapolating the
-implications of this analysis. For example, the analysis is limited as we only
-consider a linear relationship between these parameters and the rank. To further
-investigate the effects of the parameters discussed in this section, we have
-conducted a more detailed analysis in the next section, focusing on the
-performances of the winners of the tournaments.
-
-\subsection{Features of top performing strategies}\label{section:winning_features}
-
-In Figure~\ref{fig:discussion_cooperation_measures}, we present the
-distributions of the cooperation ratio and \(C_r / C_{\text{mean}}\) for the
-winners of tournaments. A value of \(C_r / C_{\text{mean}} = 1\) implies that
-the cooperation ratio of the winner was the same as the mean cooperating ratio
-of the tournament, and we observe that this occurs for most tournament types,
-apart from the case of noisy and probabilistically ending tournaments. In the
-case of noisy tournaments, there are winners that did not cooperate exactly as
-such but are fairly distributed around 1. Interestingly, in the case of
-probabilistic ending tournaments, there are several winners that cooperated much
-less than that, confirming the results of the previous section that defecting
-strategies can we winner in probabilistic ending tournaments. The distribution
-of the cooperation rates showcases a high cooperation rate in standard
-tournaments and probabilistic ending tournaments. In tournaments with noise, we
-observe a much less cooperative behavior, which could result from strategies
-being cautious of potential flip actions by the co-player or strategies not
-suited for noise holding grudges against defections.
-
-\begin{figure}[!htbp]
-    \centering
-        \centering
-        \includegraphics[width=\textwidth]{../images/features_result.pdf}
-        \caption{\textbf{Distributions of \(C_r\) and \(C_r / C_{\text{mean}}\)
-        for the winners of tournaments.} A value of \(C_r / C_{\text{mean}} =
-        1\) imply that the cooperating ratio of the winner was the same as the
-        mean cooperating ratio of the tournament.}
-        \label{fig:discussion_cooperation_measures}
-\end{figure}
-
-Analyzing the SSE distributions across different tournament types
-(Figure~\ref{fig:discussion_sse}) suggests that successful strategies exhibit
-some extortionate behavior, though not consistently. ZDs are a set of strategies
-that are often envious, as they attempt to exploit their opponents. The winners
-of the tournaments considered in this work demonstrate envious behavior, but not
-to the extent observed in many ZDs. While the exact interactions between matches
-are not recorded here, the work of~\cite{Harper2017}, which introduced the
-trained strategies appearing in the top-ranked strategies of
-Section~\ref{section:top_performances}, did record such interactions.
-In~\cite{Harper2017}, it was shown that clever strategies managed to achieve
-mutual cooperation with stronger strategies while exploiting weaker ones. This
-could explain the clever winners in our analysis and the observed SSE
-distributions.
-
-This might also be the reason why ZDs fail to appear in the top ranks—they
-attempt to exploit all opponents and cannot actively adapt back to mutual
-cooperation against stronger strategies, which requires a deeper memory. It's
-worth noting that ZDs tend to perform poorly in population games for a similar
-reason: they aim to exploit other players using ZDs, failing to form a
-cooperative subpopulation~\cite{Knight2017evolution}. This makes them effective
-invaders but poor at resisting invasion.
-
-\begin{figure}[!htbp]
-    \centering
-        \centering
-        \includegraphics[width=.75\textwidth]{../images/sse.pdf}
-        \caption{\textbf{Distributions of SSE error for the winners of
-        tournaments.} An SSE distribution skewed towards 0 indicates a
-        extortionate behaviour by the strategy.}
-        \label{fig:discussion_sse}
-\end{figure}
-
-Finally, we examine the distributions of the cooperation rates after the
-outcomes \(CC, CD, DC\), and \(DD\), as shown in
-Figure~\ref{fig:discussion_rates}. In the case of cooperating after mutual
-cooperation, the results align with expectations; the distributions skew towards
-1, indicating that the winners of the tournaments are more likely to cooperate
-after mutual cooperation. Regarding the \(CD\) outcome and the likelihood to
-cooperate after such a result, capturing forgiveness, the distributions skew
-towards 1/2, not 1, suggesting that strategies need to reduce their readiness to
-forgive. This aligns with the known result that Generous Tit For Tat generally
-outperforms \TFT{} in most settings. Interestingly, in probabilistic ending
-tournaments, there is a peak at 0, suggesting that in such tournaments,
-strategies should not be too generous in short matches.
-
-A strategy's effort to make amends is captured by the distributions of the
-\(DC\) to \(C\) rates. In noisy tournaments, winners are less likely to
-cooperate after a defection; however, there are still behaviors that attempt to
-make up for their defection. In standard tournaments and probabilistic ending
-tournaments, we observe two hubs of behaviors, one at 0 and one at 0.4-0.5,
-indicating that some winners are exploiting whether to try to make up, but with
-a small probability. This is also reflected in the \(DD\) to \(D\) rates, where
-in standard and probabilistic ending tournaments, there are winners that attempt
-to recover from a \(DD\) outcome. The remaining results are as expected, skewed
-towards 0.
-
-\begin{figure}[!htbp]
-    \centering
-        \centering
-        \includegraphics[width=\textwidth]{../images/rates_result.pdf}
-        \caption{\textbf{Distributions of rates $CC$ to $C$, $CD$ to $C$, $DC$
-        to $C$, and $DD$ to $C$ for the winners of
-        tournaments.}}\label{fig:discussion_rates}
-\end{figure}
-
-\section{Discussion}\label{section:conclusion}
-
-This manuscript explored the performance of \numberofstrategies strategies of
-the \IPD{} in thousands of computer tournaments. The collection of computer
-tournaments presented here is the largest and most diverse collection in the
-literature. The \numberofstrategies strategies are drawn from the APL and
-include strategies from the \IPD{} literature. The computer tournaments include
-tournaments of four different types. So what is the best way of playing the
-\IPD{}? And is there a single dominant strategy for the \IPD{}? There was not a
-single strategy within the collection of the \numberofstrategies strategies that
-managed to perform well in all the tournaments variations it competed in. Even
-if on average a strategy ranked highly in a specific environment this did not
-guarantee its success over the different tournament types. Nevertheless, in
-subsections~\ref{section:top_performances}
-and~\ref{section:evaluation_of_performance} we examined the best performing
-strategies across various tournament types and analysed their salient features.
-this demonstrated that there are properties associated with the success of
-strategies which in fact contradict the originally suggested properties of
-Axelrod~\cite{Axelrod1981}.
-
-We showed that complex or \textbf{clever} strategies can be effective, whether
-trained against a corpus of possible opponents or purposely designed to mitigate
-the impact of noise such as the DBS strategy. Moreover, we found some
-strategies designed or trained for noisy environments were also highly ranked in
-noise-free tournaments which reinforces the idea that strategies'
-complexity/cleverness is not necessarily a liability, rather it can confer
-adaptability to a more diverse set of environments.
-We also showed that while the type of exploitation attempted by ZDs is
-not typically effective in standard tournaments, \textbf{envious} strategies
-capable of both exploiting and not their opponents can be highly successful.
-Based on the results of~\cite{Harper2017} this could be because they are
-selectively exploiting weaker opponents while mutually cooperating with stronger
-opponents. Highly noisy or tournaments with short matches also favoured envious
-strategies. These environments mitigated the value of being nice. Uncertainty
-enables exploitation, reducing the ability of maintaining or enforcing mutual
-cooperation, while triggering grudging strategies to switch from typically
-cooperating to typically defecting.
-
-The features analysis of the best performing strategies demonstrated that a
-strategy should reciprocate, as suggested by Axelrod, but it should relax its
-readiness to do so and be more \textbf{generous}. For noisy environments this is
-inline with the results of~\cite{Bendor1991, Donninger1986, Molander1985,
-Hammerstein1984}, however, we also showed that generosity pays off even in
-standard settings, and that in fact the only setting a strategy would want to be
-too provocable is when the matches are not long. Forgiveness as defined by R.
-Axerlod was not explored here. This was mainly because the two round states were
-not recorded during the data collection. This could be a topic of future work
-that examines the impact of considering more rounds of history.
-The features analysis also concluded that
-there is a significant importance in \textbf{adapting to the environment}, and
-more specifically, to the mean cooperator. 
-In standard tournaments a strategy would aim to be the
-mean cooperator while in noisy tournaments the best performing players
-cooperate at a lower rate than the tournament population on average.
-
-This could potentially explain the early success of TFT. TFT naturally achieves
-a cooperation rate near $C_{\text{mean}}$ by virtue of copying its opponent's
-last move while also minimizing instances where it is exploited by an opponent
-(cooperating while the opponent defects), at least in non-noisy tournaments. It
-could also explain why Tit For \(N\) Tats does not fare well for $N > 1$ -- it
-fails to achieve the proper cooperation ratio by tolerating too many defections.
-
-Similarly, our results could suggest an explanation regarding the intuitively
-unexpected effectiveness of memory-one strategies historically. Given that among
-the important features associated with success are the relative cooperation rate
-to the population average and the four memory-one probabilities of cooperating
-conditional on the previous round of play, these features can be optimized by a
-memory-one strategy such as TFT. Usage of more history becomes valuable when
-there are exploitable opponent patterns. This is indicated by the importance of
-SSE as a feature, showing that the first-approximation provided by a memory-one
-strategy is no longer sufficient.
-These results highlight a central idea in evolutionary game theory in this
-context: the fitness landscape is a function of the population (where fitness in
-this case is tournament performance). While that may seem obvious now, it shows
-why historical tournament results on small or arbitrary populations of
-strategies have so often failed to produce generalizable results.
-
-Overall, the five properties successful strategies need to have in a IPD competition
-based on the analysis that has been presented in this manuscript are:
-
-\begin{enumerate}[(i)]
-    \item Be ``nice'' in non-noisy environments or when game lengths are longer
-    \item Be provocable in tournaments with short matches, and generous when matches are longer
-    \item Be a little bit envious
-    \item Be clever
-    \item Adapt to the environment (including the population of strategies).
-\end{enumerate}
-
-The data set described in this work contains the largest number of IPD
-tournaments, to the authors knowledge. The raw data set is available
-at~\cite{raw_data} and the processed data at~\cite{data}. Further data mining
-could be applied and provide new insights in the field.
+\input{parameters_section}
+\input{result_with_entire_dataset}
+\input{correlation_section}
+\input{random_forest_evaluation}
+\input{regression_on_median_score}
+\input{strategies_list_section}
 
@@
 
-\section{Acknowledgements}
-
-A variety of open-source software have been used in this work. The authors would
-like to express their gratitude to the open-source software community, whose
-invaluable contributions significantly enhanced the development and execution of
-this research. Namely, the authors would like to thank the developers of the
-following software packages: Axelrod-Python library for IPD
-simulations~\cite{axelrodproject}, the Matplotlib library for
-visualisation~\cite{hunter2007matplotlib}, The Numpy library for data
-manipulation~\cite{walt2011numpy}, and finally the scikit-learn library for data
-analysis~\cite{scikit-learn}.
-
-\section{Data availability statement}
-
-The raw and processed datasets have been made publicly available~\cite{data,
-raw_data} and can be used for further analysis and insights.
-
 \end{document}

### 2023-12-28 paper/main.tex
Some copy edits for special issue version (#34)
* Update main.tex

* Update regression_table.tex

Fix Typo

@@
 Researchers have explored the performance of Iterated Prisoner's Dilemma strategies
-for decades: from the celebrated performance of Tit for Tat, to the
-introduction of the zero-determinant strategies, to the use of sophisticated learning
+for decades, from the celebrated performance of Tit for Tat to the
+introduction of the zero-determinant strategies and the use of sophisticated learning
 structures such as neural networks. Many new strategies have been introduced and tested
@@
 decision is made with the memory of all prior interactions. The payoffs for each
-player at each turn are influenced by their own choice, and the choice of the
-other player. To this end, the payoffs of the game are defined by,
+player at each turn are influenced by their own choice and the choice of the
+other player. To this end, the payoffs of the game are defined by
 
@@
     \item Do not be envious by striving for a payoff larger than the opponent's payoff.
-    \item Be ``nice''; Do not be the first to defect.
+    \item Be ``nice'' by not being the first to defect.
     \item Reciprocate both cooperation and defection; Be provocable to retaliation and forgiveness.
@@
 models~\cite{Harper2017}, and finite-state automata~\cite{Miller1996}, on
-on a set of 170 strategies.
+a set of 170 strategies.
 
@@
 form like finite state machines or deterministic memory-two strategies.
-Furthermore, our tournaments encompass various variations, including standard
+Furthermore, our tournaments encompass variations including standard
 tournaments resembling Axelrod's original ones, tournaments with noise,
@@
 best-performing strategy across all tournaments or tournament types. On the
-contrary, our work demonstrates that such a strategy does not exist. The primary
+contrary, our work demonstrates that such a strategy does not exist
+(notwithstanding a few strategies with broadly high performance). The primary
 objective of this paper, presented in the latter parts of the paper, is to
@@
 significant importance. It aims to provide guidance to researchers designing new
-strategies and those training strategies. Moreover, conducting a similar
+strategies and those training strategies. Specifically, much like the recognized
+value of diversity in training datasets, such as variations in image perspective,
+skin color, etc., are critical in training accurate and generalizable machine
+learning models, we show that diversity in the population of opponent strategies
+is of paramount importance in the construction and evaluation of game theory
+strategies. As AI agents start to interact as scale, they will benefit from
+exposure to a wide variety of alternative agents. Moreover, conducting a similar
 analysis can shed light on already trained strategies, aiding in understanding
@@
 processes.
-% ToDO: Not sure if this is enough to justify how our work is important for AI.
-% It would be nice to have a sentence or two since it fits the special issue
-% theme.
 
@@
 normalised ranks of these strategies in each of the four tournaments. We can
-observe that \TFT{} has a normally distributed normalized rank. In comparison,
+observe that \TFT{} looks to be normally distributed normalized rank. In comparison,
 Gradual's performance has longer tails, indicating that there were tournaments
@@
 a lower median rank, signifying that it performs better than \TFT{} except in
-the case of noisy and probabilistic ending tournaments.
+the case of noisy and probabilistic ending tournaments (lower rank is better).
 
@@
 tournaments presented here is the largest and most diverse collection in the
-literature. The \numberofstrategies strategies are drawn from the APL and
+literature. The \numberofstrategies strategies are drawn from the Axelrod Python Library and
 include strategies from the \IPD{} literature. The computer tournaments include

### 2023-12-28 paper/main.tex
change NG affiliation, note that VK and MH contributed equally + ref style
adding a bit more discussion based on MH thoughts

@@
 \title{Properties of Winning Iterated Prisoner's Dilemma Strategies.}
-\author[1]{Nikoleta E. Glynatsi}
-\author[2]{Vincent Knight}
-\author[3]{Marc Harper}
+\author[1, 2]{Nikoleta E. Glynatsi}
+\author[2, $\dagger$]{Vincent Knight}
+\author[3, $\dagger$]{Marc Harper}
 
@@
 \affil[3]{Google Inc., Mountain View, CA, USA}
+\affil[$\dagger$]{V.K. and M.H. contributed equally to this work.}
 \date{}
@@
 strategies in a small number of tournaments, casting doubt on the generalizability
-of conclusions. We analyze a large collection of \numberofstrategies
+of conclusions. In this work, we analyze a large collection of \numberofstrategies
 strategies in thousands of computer tournaments, present the top performing strategies across multiple
@@
 settings. Furthermore, our findings have implications for the future training of
-autonomous agents. Understanding the crucial features for incorporation into
+autonomous agents, as understanding the crucial features for incorporation into
 these agents becomes essential.
@@
 
-In this paper we evaluate the performance of a significant number of \IPD{}
+In this paper, we evaluate the performance of a significant number of \IPD{}
 strategies across a diverse array of tournaments. Many of the strategies used in
-our analysis are drawn from well-known and named strategies in \IPD{} literature,
-including previous tournament winners. This contrasts with other work that may
-have randomly generated essentially arbitrary strategies, often constrained to
-specific classes such as memory-one strategies or those of a certain structural
-form like finite state machines or deterministic memory-two strategies.
-Furthermore, our tournaments encompass variations including standard
+our analysis are drawn from well-known and named strategies in \IPD{}
+literature, including previous tournament winners. This contrasts with other
+work that may have randomly generated essentially arbitrary strategies, often
+constrained to specific classes such as memory-one strategies or those of a
+certain structural form like finite state machines or deterministic memory-two
+strategies. Furthermore, our tournaments encompass variations, including standard
 tournaments resembling Axelrod's original ones, tournaments with noise,
@@
 earlier claims in alternative settings against known powerful strategies.
+More specifically, we show that the previous tournament
+winners are lacking against large enough opponent pools; they do not appear
+among the top-performing strategies anymore. This could be due to likely
+suffering from a lack of diversity in the strategies they were trained/tested
+against, finding it hard to adapt to the new strategies.
 
@@
 
-This manuscript explored the performance of \numberofstrategies strategies of
+This manuscript explores the performance of \numberofstrategies strategies in
 the \IPD{} in thousands of computer tournaments. The collection of computer
-tournaments presented here is the largest and most diverse collection in the
-literature. The \numberofstrategies strategies are drawn from the Axelrod Python Library and
-include strategies from the \IPD{} literature. The computer tournaments include
-tournaments of four different types. So what is the best way of playing the
-\IPD{}? And is there a single dominant strategy for the \IPD{}? There was not a
-single strategy within the collection of the \numberofstrategies strategies that
-managed to perform well in all the tournaments variations it competed in. Even
-if on average a strategy ranked highly in a specific environment this did not
-guarantee its success over the different tournament types. Nevertheless, in
-subsections~\ref{section:top_performances}
-and~\ref{section:evaluation_of_performance} we examined the best performing
-strategies across various tournament types and analysed their salient features.
-this demonstrated that there are properties associated with the success of
-strategies which in fact contradict the originally suggested properties of
-Axelrod~\cite{Axelrod1981}.
+tournaments presented here is the largest and most diverse in the literature.
+The \numberofstrategies strategies are drawn from \axelrod{} library and include
+strategies from the \IPD{} literature. The computer tournaments encompass four
+different types. So, what is the best way to play the \IPD{}? And is there a
+single dominant strategy for the \IPD{}? There was not a single strategy within
+the collection of \numberofstrategies strategies that managed to perform well in
+all the tournament variations it competed in. A strategy ranking highly in a
+specific environment did not guarantee its success over different tournament
+types, with a few exceptions - strategies that generalize better. Already
+well-known in the AI/ML literature, adding noise to training data leads to more
+robust models. We see that clearly here, where the strategies trained for noise
+(or designed for noise) tend to be better generalists. There were instances
+where a few strategies trained in narrow conditions outperformed more generalist
+strategies, as they tend to overfit. However, the strategies trained with noise
+perform well in general, whilst the strategies trained specifically on no noise
+or small subpopulations do not.
 
+We also examined the best-performing strategies across various tournament
+types and analyzed their salient features. This demonstrated that there are
+properties associated with the success of strategies that contradict the
+originally suggested properties of Axelrod~\cite{Axelrod1981}.
 We showed that complex or \textbf{clever} strategies can be effective, whether
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{naturemag}
 \bibliography{bibliography}

### 2023-12-30 paper/main.tex
move last sections around
addressing MH last comment

@@
 tournament types, and distill their salient features. 
-The results show that there is not yet a single
-strategy that performs well in diverse Iterated Prisoner's Dilemma scenarios,
-nevertheless there are several properties that heavily influence the best performing
-strategies. This refines the properties described by Axelrod in light of
-recent and more diverse opponent populations to: be nice, be provocable and generous,
-be a little envious, be clever, and adapt to the environment. More precisely,
+We find that although a strategy's high ranking in a specific environment
+does not guarantee success across different tournament types, certain strategies
+consistently perform well across various settings. Notably,
+strategies designed or trained for noise are the strategies that generalise
+better—an observation well established in AI/ML literature where adding noise to
+training data enhances model robustness.
+We identify several crucial properties
+heavily influencing the success of strategies, refining Axelrod's described
+properties in light of encounters with more diverse opponents to: being
+cooperative, responsive to provocation, generous yet slightly envious, clever,
+and adaptable to the prevailing environment. More precisely,
 we find that strategies perform best when their probability of cooperation
@@
 best-performing strategy across all tournaments or tournament types. On the
-contrary, our work demonstrates that such a strategy does not exist
+contrary, our work demonstrates that such a strategy does not always exist
 (notwithstanding a few strategies with broadly high performance). The primary
@@
 different types. So, what is the best way to play the \IPD{}? And is there a
-single dominant strategy for the \IPD{}? There was not a single strategy within
-the collection of \numberofstrategies strategies that managed to perform well in
-all the tournament variations it competed in. A strategy ranking highly in a
+single dominant strategy for the \IPD{}?
+A strategy ranking highly in a
 specific environment did not guarantee its success over different tournament
@@
 
-\bibliographystyle{naturemag}
-\bibliography{bibliography}
+\section{Data availability statement}
+
+The raw and processed datasets have been made publicly available~\cite{data,
+raw_data} and can be used for further analysis and insights.
 
@@
 
+N.G. acknowledges the generous support of the European Research Council Starting
+Grant 850529: E-DIRECT and the Max Planck Society.
 A variety of open-source software have been used in this work. The authors would
@@
 
-\section{Data availability statement}
-
-The raw and processed datasets have been made publicly available~\cite{data,
-raw_data} and can be used for further analysis and insights.
+\bibliographystyle{naturemag}
+\bibliography{bibliography}
 

### 2023-12-30 paper/main.tex
anonymize manuscript for submission

@@
 \usepackage{authblk}
+\usepackage{lineno}
 %%%%%%%%%%%%%%%%%
@@
 
+% \linenumbers
+
 \title{Properties of Winning Iterated Prisoner's Dilemma Strategies.}
-\author[1, 2]{Nikoleta E. Glynatsi}
-\author[2, $\dagger$]{Vincent Knight}
-\author[3, $\dagger$]{Marc Harper}
+\author{}
+% \author[1, 2]{Nikoleta E. Glynatsi}
+% \author[2, $\dagger$]{Vincent Knight}
+% \author[3, $\dagger$]{Marc Harper}
 
-\affil[1]{Max Planck Institute for Evolutionary Biology, Research Group Dynamics of Social
-Behavior, Germany}
-\affil[2]{Cardiff University, School of Mathematics, UK}
-\affil[3]{Google Inc., Mountain View, CA, USA}
-\affil[$\dagger$]{V.K. and M.H. contributed equally to this work.}
+% \affil[1]{Max Planck Institute for Evolutionary Biology, Research Group Dynamics of Social
+% Behavior, Germany}
+% \affil[2]{Cardiff University, School of Mathematics, UK}
+% \affil[3]{Google Inc., Mountain View, CA, USA}
+% \affil[$\dagger$]{V.K. and M.H. contributed equally to this work.}
 \date{}
@@
 The data set described in this work contains the largest number of \IPD{}
-tournaments, to the authors knowledge. The raw data set is available
-at~\cite{raw_data} and the processed data at~\cite{data}. Further data mining
+tournaments, to the authors knowledge. The raw data set and the processed data
+have been made available online. Further data mining
 could be applied and provide new insights in the field.
@@
 
-The raw and processed datasets have been made publicly available~\cite{data,
-raw_data} and can be used for further analysis and insights.
+The raw and processed datasets have been made publicly available
+% ~\cite{data, raw_data} 
+and can be used for further analysis and insights.
 
@@
 
-N.G. acknowledges the generous support of the European Research Council Starting
-Grant 850529: E-DIRECT and the Max Planck Society.
+% N.G. acknowledges the generous support of the European Research Council Starting
+% Grant 850529: E-DIRECT and the Max Planck Society.
 A variety of open-source software have been used in this work. The authors would

### 2023-12-30 paper/main.tex
Update main.tex

@@
 however, rely on performance against a small number of somewhat arbitrarily selected
-strategies in a small number of tournaments, casting doubt on the generalizability
+strategies in a small number of tournaments and environments, casting doubt on the generalizability
 of conclusions. In this work, we analyze a large collection of \numberofstrategies
@@
 Due to the strategy's strong performance in both tournaments and a series of
-evolutionary experiments~\cite{Axelrod1981}, \TFT{} was often claimed to be a
+evolutionary experiments~\cite{Axelrod1981}, \TFT{} is often claimed to be a
 highly robust (and sometimes the most robust) strategy for the \IPD.
@@
     \item Be a little bit envious
-    \item Be ``nice'' in non-noisy environments or when game lengths are longer
+    \item Be ``nice'' in non-noisy environments or when game lengths are longer (if known)
     \item Reciprocate both cooperation and defection appropriately;
@@
 learning models, we show that diversity in the population of opponent strategies
-is of paramount importance in the construction and evaluation of game theory
+is paramount in the construction and evaluation of game theory
 strategies. As AI agents start to interact as scale, they will benefit from

### 2024-08-07 paper/main.tex
update paper

--- 2023-12-30 paper/main.tex
@@
 however, rely on performance against a small number of somewhat arbitrarily selected
-strategies in a small number of tournaments, casting doubt on the generalizability
+strategies, casting doubt on the generalizability
 of conclusions. In this work, we analyze a large collection of \numberofstrategies
@@
 tournament types, and distill their salient features.
-We find that although a strategy's high ranking in a specific environment
-does not guarantee success across different tournament types, certain strategies
-consistently perform well across various settings. Notably,
-strategies designed or trained for noise are the strategies that generalise
-better—an observation well established in AI/ML literature where adding noise to
-training data enhances model robustness.
-We identify several crucial properties
-heavily influencing the success of strategies, refining Axelrod's described
-properties in light of encounters with more diverse opponents to: being
-cooperative, responsive to provocation, generous yet slightly envious, clever,
-and adaptable to the prevailing environment. More precisely,
+The results show that there is not yet a single
+strategy that performs well in diverse Iterated Prisoner's Dilemma scenarios,
+nevertheless there are several properties that heavily influence the best performing
+strategies. This refines the properties described by Axelrod in light of
+recent and more diverse opponent populations to: be nice, be provocable and generous,
+be a little envious, be clever, and adapt to the environment. More precisely,
 we find that strategies perform best when their probability of cooperation
@@
 why zero-determinant strategies typically do not fare well in tournament
-settings. Furthermore, our findings have implications for the future training of
-autonomous agents, as understanding the crucial features for incorporation into
-these agents becomes essential.
+settings.
 \end{abstract}
 
-\section{Background}
+\section{Introduction}
 
@@
 behavioral interactions, specifically interactions where self-interest clashes
-with collective interest. In each turn of the game, both players simultaneously
+with collective interest. It encompasses a wide range of social and
+biological phenomena. In each turn of the game, both players simultaneously
 and independently decide between cooperation (\(C\)) and defection (\(D\)). This
@@
 been of interest to the scientific community since the formulation of the game
-in 1950~\cite{Flood1958}. Following Axelrod's computer tournaments in the
-1980s~\cite{Axelrod1980a, Axelrod1980b}, round-robin computer tournaments became
-a common evaluation technique for newly designed strategies.
+\cite{Axelrod1980a, Beaufils1997, Press2012, Tzafestas2000, Hilbe2017,
+Glynatsi2020, Murase2021, Schmid2022, Chen2023}.
+This extends to both tournament settings and population dynamics.
+Computer tournaments became a common evaluation technique for newly designed
+strategies following Axelrod's computer tournaments in the
+1980s~\cite{Axelrod1980a, Axelrod1980b}.
 The winner of both of Axelrod's tournaments~\cite{Axelrod1980a, Axelrod1980b}
@@
 strategies (ZDs), in~\cite{Press2012}. These strategies attempt to force a
-linear relationship between stationary payoffs against other memory-one
+linear relationship between stationary payoffs against their
 opponents, potentially ensuring that they receive a higher average payout. While
@@
 best-performing strategy across all tournaments or tournament types. On the
-contrary, our work demonstrates that such a strategy does not always exist
+contrary, our work demonstrates that such a strategy does not exist
 (notwithstanding a few strategies with broadly high performance). The primary
@@
 is of paramount importance in the construction and evaluation of game theory
-strategies. As AI agents start to interact as scale, they will benefit from
-exposure to a wide variety of alternative agents. Moreover, conducting a similar
+strategies. Moreover, conducting a similar
 analysis can shed light on already trained strategies, aiding in understanding
@@
 
-\section{Data collection}\label{section:data_collection}
+\section{Model}\label{section:data_collection}
 
@@
 memory usage &  The memory size of a strategy divided by the number of turns & memory size from APL & float & 0 &  1 \\
-SSE & A measure of how far a strategy is from ZD behaviour & method described in~\cite{Knight2019} & float & 0 & 1 \\
+SSE & A measure of how far a strategy is from ZD behaviour & method described in~\cite{Knight2024} & float & 0 & 1 \\
 max cooperating rate $(C_{\text{max}})$  & The biggest cooperating rate in a given tournament  & result summary  & float & 0 & 1\\
@@
     make an action (which is specified in the APL) divided by the number of
-    turns. The SSE (introduced in~\cite{Knight2019}) shows how close a strategy
+    turns. The SSE (introduced in~\cite{Knight2024}) shows how close a strategy
     is to behaving as a ZDs, and subsequently, in an extortionate way. The
@@
 reason: they aim to exploit other players using ZDs, failing to form a
-cooperative subpopulation~\cite{Knight2017evolution}. This makes them effective
+cooperative subpopulation~\cite{Knight2018evolution}. This makes them effective
 invaders but poor at resisting invasion.
@@
 different types. So, what is the best way to play the \IPD{}? And is there a
-single dominant strategy for the \IPD{}?
-A strategy ranking highly in a
+single dominant strategy for the \IPD{}? There was not a single strategy within
+the collection of \numberofstrategies strategies that managed to perform well in
+all the tournament variations it competed in. A strategy ranking highly in a
 specific environment did not guarantee its success over different tournament

### 2024-11-03 paper/main.tex
wip addressing reviewers' comments

@@
 \usepackage{authblk}
+\usepackage{listings}
 %%%%%%%%%%%%%%%%%
@@
 \setlength{\tabcolsep}{3pt}
+
+\definecolor{codegreen}{rgb}{0,0.6,0}
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\definecolor{codepurple}{rgb}{0.58,0,0.82}
+\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
+
+\lstdefinestyle{mystyle}{
+    backgroundcolor=\color{backcolour},   
+    commentstyle=\color{codegreen},
+    keywordstyle=\color{codegreen},
+    stringstyle=\color{codegreen},
+    basicstyle=\ttfamily\footnotesize,
+    breakatwhitespace=false,         
+    breaklines=true,                 
+    captionpos=b,                    
+    keepspaces=true,                                             
+    showspaces=false,                
+    showstringspaces=false,
+    showtabs=false,                  
+    tabsize=2
+}
+
+\lstset{style=mystyle}
 
@@
 been of interest to the scientific community since the formulation of the game
-\cite{Axelrod1980a, Beaufils1997, Press2012, Tzafestas2000, Hilbe2017,
-Glynatsi2020, Murase2021, Schmid2022, Chen2023}.
+\cite{Axelrod1980a, Nowak1992, Nowak1993, Beaufils1997, Press2012, Tzafestas2000, Hilbe2017,
+Glynatsi2020, Murase2021, Schmid2022, Li2022, Chen2023}.
 This extends to both tournament settings and population dynamics.
@@
 newly introduced strategies.
+
+Beyond these difficulties, we believe that limited comprehensive analyses are
+rooted in field conventions. Tournaments or evolutionary dynamics often rely on
+a select list of hand-picked strategies chosen by modelers, typically based on
+specific properties they wish to examine. This practice may stem from
+misconceptions, such as the assumption that because \TFT{} performs
+relatively well, it is sufficient to test only against \TFT{} variants.
+Another misconception may stem from the Press \& Dyson result~\cite{Press2012},
+which implies that lower memory strategies will always dominate pairwise
+interactions, leading some to consider only memory-one strategies. However, this
+result holds strictly only in pairwise interactions.
+
+It is not only the set of strategies or the tournament parameters such as noise
+that may impact results but also the design of the round-robin tournament itself. To
+address this~\cite{Rapoport2015} separately examined the effects of changes in format, objective
+criteria, and payoff values on tournament outcomes. They demonstrated that
+\TFT's performance declined under certain conditions. To our knowledge,
+this is the only study that has reanalyzed the tournament structure and
+critically evaluated it. However, in this work, we employ an extensive list of
+strategies made possible by the \axelrod{} package, an approach that would
+have been difficult to achieve previously. Unlike the authors of that study, we
+do not consider a new tournament design.
 
@@
 
+To run a tournament, only a few lines of code are required
+(Figure~\ref{fig:axelrod_code}). Specifically, one needs to define the list of
+strategies that the players use when participating in the tournament, the number
+of repetitions, the number of turns or the probability of each match ending, and
+the probability of noise. We demonstrate two examples in
+Figure~\ref{fig:axelrod_code}: one with a fixed number of turns and one with a
+probabilistic ending. A tournament is an instance of the `Tournament` class. To
+execute the tournament, users need to run the `play()` method, which returns an
+instance of the `Results` class. This instance includes many details of the
+tournament, such as the winner and the average score. Additionally, a more
+detailed summary of the tournament is provided, which we use in this analysis
+and describe in detail below.
+
+\begin{figure}
+\begin{lstlisting}[language=Python]
+>>> import axelrod as axl
+
+>>> players = [axl.TitForTat(), axl.GTFT(), axl.Gradual(), axl.EvolvedLookerUp2_2_2()]
+
+>>> standard_tournament = axl.Tournament(players=players, turns=50, repetitions=10, noise=0)
+
+>>> results = standard_tournament.play()
+
+>>> prob_noisy_end_tournament = axl.Tournament(players=players, prob_end=0.5,
+...                                            repetitions=10, noise=0.001)
+
+>>> results = prob_noisy_end_tournament.play()
+\end{lstlisting}
+\caption{{\bf Example usage of the \axelrod package for running tournaments.}
+The strategies that players use are saved in a list, which is then passed to the
+Tournament class. In this example, strategies we previously discussed, such as \TFT, Generous Tit-for-Tat, Gradual, and a stochastic strategy
+evolved through reinforcement learning, are included. We create a standard
+tournament where noise is set to 0, as
+well as a noisy tournament with probabilistic ending. Once an instance of the
+tournament class is defined, executing the tournament is straightforward. The play()
+method generates all possible pairs from the list of strategies, including
+pairs where each strategy plays against itself, and then iterates through each
+match to play it. Each match is repeated according to the specified number of
+repetitions, with results aggregated to a tournament summary.}\label{fig:axelrod_code}
+\end{figure}
+
 The process of collecting tournament results is outlined in
@@
 Table~\ref{table:output_result}.
+
+The summary contains statistics regarding each strategy that participated in the
+tournament, such as its rank, cooperation rate, time spent in each state, and
+the probability of cooperating after each of the four possible outcomes of the
+previous round. In our analysis, we will use the measures for each strategy that
+are provided in the summary, as well as additional measures we calculated.
+Namely, these include the SSE error, the average cooperation in each tournament,
+the maximum, and the minimum values. The SSE (introduced in~\cite{Knight2024})
+shows how close a strategy is to behaving as a ZDs, and subsequently, in an
+extortionate way. We also consider how each strategy's cooperation rate \(C_r\)
+compares to those of the tournament as a whole, for example, by comparing
+\(C_r\) to \(C_{\text{max}}\).
 
@@
 \newcolumntype{g}{>{\columncolor{Gray}}c}
-\begin{table}[b]
+\begin{table}[t]
     \begin{center}
@@
 $C_r$ / $C_{\text{max}}$ & A strategy's cooperating rate divided by the maximum & result summary  & float & 0 & 1 \\
-$C_{\text{min}}$ / $C_r$ & A strategy's cooperating rate divided by the minimum & result summary  & float & 0 & 1 \\
+$C_{\text{min}}$ / $C_r$ & The minimum divided by a strategy's cooperating rate & result summary  & float & 0 & 1 \\
 $C_r$ / $C_{\text{median}}$ & A strategy's cooperating rate divided by the median  & result summary  & float & 0 & 1\\
@@
 and the normalised rank and the median score.}
-The correlation coefficients are calculated using the Spearman's rank
-correlation coefficient.}\label{table:correlations}
+For each type of tournament, standard, noisy, probabilistic ending, and noisy
+probabilistic ending, we run a correlation analsysif. For each tournament we
+check the correlation between each feature used in our analysis and the normalised
+random and median score. Note that the correlation coefficients are calculated
+using the Spearman's rank correlation coefficient. A negative value
+indicates a negative correlation and in the case of the normalised rank
+a smaller rank translats to better position in the tournament.}\label{table:correlations}
 \end{table}
@@
         \includegraphics[width=\textwidth]{../images/features_result.pdf}
-        \caption{\textbf{Distributions of \(C_r\) and \(C_r / C_{\text{mean}}\)
-        for the winners of tournaments.} A value of \(C_r / C_{\text{mean}} =
-        1\) imply that the cooperating ratio of the winner was the same as the
-        mean cooperating ratio of the tournament.}
+        \caption{{\bf Distributions of \(C_r\) and \(C_r / C_{\text{mean}}\)
+        for the winners of tournaments.} In this distribution, we consider the
+        winners of the tournaments, specifically the strategies that ranked
+        first in each tournament. For each type of tournament, we plot the
+        cooperation rate of the winner in the tournament they won, as well as
+        the ratio of the winner's cooperation rate to that of the entire
+        tournament. A value of \(C_r / C_{\text{mean}} = 1\) implies that the
+        cooperation ratio of the winner was the same as the mean cooperation
+        ratio of the tournament.}
         \label{fig:discussion_cooperation_measures}
@@
         \includegraphics[width=.75\textwidth]{../images/sse.pdf}
-        \caption{\textbf{Distributions of SSE error for the winners of
-        tournaments.} As a reminder, the SSE error shows how close a strategy is
-        to behaving as a ZDs, and subsequently, in an extortionate way. A SSE
-        value of 1 indicates no extortionate behaviour at all whereas a value of
-        0 indicates that a strategy is behaving as a ZDs.}
+        \caption{\textbf{Distributions of SSE error for the winners of tournaments.}
+        Here, we again consider the winners of the tournaments, separated by type of
+        tournament, and plot their SSE error. As a reminder, the SSE error indicates how
+        closely a strategy behaves like a Zero-Determinant (ZD) strategy, and
+        subsequently, in an extortionate way. An SSE value of 1 indicates no
+        extortionate behavior at all, whereas a value of 0 indicates that a strategy is
+        behaving as a ZD.}
         \label{fig:discussion_sse}
@@
         \includegraphics[width=\textwidth]{../images/rates_result.pdf}
-        \caption{\textbf{Distributions of rates $CC$ to $C$, $CD$ to $C$, $DC$
-        to $C$, and $DD$ to $C$ for the winners of
-        tournaments.}}\label{fig:discussion_rates}
+        \caption{\textbf{Distributions of rates \(CC\) to \(C\), \(CD\) to \(C\), \(DC\)
+        to \(C\), and \(DD\) to \(C\) for the winners of tournaments.} The result
+        summary from the tournaments records how often each strategy cooperated after
+        each possible outcome of the previous round. Specifically, we analyze the
+        probability with which a strategy chose \(C\) following the outcomes. Here, we
+        plot the distributions of these probabilities for the winners of the
+        tournaments. We separate them by type of tournament, from top to bottom:
+        standard, noisy, probabilistic ending, and noisy probabilistic ending. From left
+        to right, we plot the distributions of cooperation after the outcomes \(CC\),
+        \(CD\), \(DC\), and \(DD\).}\label{fig:discussion_rates}
 \end{figure}
@@
 
+To this end, many strategies, such as Win-Stay-Lose-Shift and Generous
+Tit For Tat, emerged due to their strong performance in evolutionary dynamics.
+Axelrod's original work relied on computer tournaments, so we chose to remain
+consistent with this approach, as a comprehensive study like ours had not yet
+been undertaken. However, evolutionary settings would be an exciting direction
+for future study.
+
 Overall, the five properties successful strategies need to have in a \IPD{} competition

### 2024-11-04 paper/main.tex
first draft of revision

@@
 \usepackage{listings}
+\usepackage{xparse}
+
+\NewDocumentCommand{\codeword}{v}{%
+\texttt{\textcolor{teal}{#1}}%
+}
+
 %%%%%%%%%%%%%%%%%
@@
 strategies and those training strategies. Specifically, much like the recognized
-value of diversity in training datasets, such as variations in image perspective,
-skin color, etc., are critical in training accurate and generalizable machine
-learning models, we show that diversity in the population of opponent strategies
-is of paramount importance in the construction and evaluation of game theory
-strategies. Moreover, conducting a similar
-analysis can shed light on already trained strategies, aiding in understanding
-the key features they have autonomously developed during their training
-processes.
+value of diversity in training datasets~\cite{Gong:IEEE:2019}, such as
+variations in image perspective, skin color, etc., are critical in training
+accurate and generalizable machine learning models, we show that diversity in
+the population of opponent strategies is of paramount importance in the
+construction and evaluation of game theory strategies. Moreover, conducting a
+similar analysis can shed light on already trained strategies, aiding in
+understanding the key features they have autonomously developed during their
+training processes.
 
@@
 Figure~\ref{fig:axelrod_code}: one with a fixed number of turns and one with a
-probabilistic ending. A tournament is an instance of the `Tournament` class. To
-execute the tournament, users need to run the `play()` method, which returns an
-instance of the `Results` class. This instance includes many details of the
-tournament, such as the winner and the average score. Additionally, a more
-detailed summary of the tournament is provided, which we use in this analysis
-and describe in detail below.
+probabilistic ending. A tournament is an instance of the \texttt{Tournament}
+class. To execute the tournament, users need to run the \texttt{play()}
+method, which returns an instance of the \texttt{ResultSet} class. This
+instance includes many details of the tournament, such as the winner and the
+average score of the participants. Additionally, the instance contains a more
+detailed summary of the tournament, which we use in our analysis. We describe
+the results summary in detail below.
 
@@
 \end{lstlisting}
-\caption{{\bf Example usage of the \axelrod package for running tournaments.}
+\caption{{\bf Example usage of the \axelrod{} package for running tournaments.}
 The strategies that players use are saved in a list, which is then passed to the
@@
 evolved through reinforcement learning, are included. We create a standard
-tournament where noise is set to 0, as
+tournament where \texttt{noise} is set to 0, as
 well as a noisy tournament with probabilistic ending. Once an instance of the
-tournament class is defined, executing the tournament is straightforward. The play()
+tournament class is defined, executing the tournament is straightforward. The \texttt{play()}
 method generates all possible pairs from the list of strategies, including
@@
 The summary contains statistics regarding each strategy that participated in the
-tournament, such as its rank, cooperation rate, time spent in each state, and
-the probability of cooperating after each of the four possible outcomes of the
-previous round. In our analysis, we will use the measures for each strategy that
-are provided in the summary, as well as additional measures we calculated.
-Namely, these include the SSE error, the average cooperation in each tournament,
-the maximum, and the minimum values. The SSE (introduced in~\cite{Knight2024})
-shows how close a strategy is to behaving as a ZDs, and subsequently, in an
-extortionate way. We also consider how each strategy's cooperation rate \(C_r\)
-compares to those of the tournament as a whole, for example, by comparing
-\(C_r\) to \(C_{\text{max}}\).
-
-\begin{algorithm}[!htbp]
-    \setstretch{1.35}
-    \For{\text{seed} $\in [0, 11420]$}{
-        $N \gets \text{randomly select integer}\in [3, 195]$\;
-        $\text{players} \gets  \text{randomly select $N$ players}$\;
-        $k \gets  \text{randomly select integer}\in [10, 100]$\;
-        $n \gets  \text{randomly select integer}\in [1, 200]$\;
-        $p_n \gets  \text{randomly select float}\in [0, 1]$\;
-        $p_e \gets   \text{randomly select float}\in [0, 1]$\;
-        \vspace{0.4cm}
-        $\text{result standard}$ $\gets$ Axelrod.tournament$(\text{players}, n, k)$\;
-        $\text{result noisy}$ $\gets$ Axelrod.tournament$(\text{players}, n, p_n, k)$\;
-        $\text{result probabilistic ending}$ $\gets$ Axelrod.tournament$(\text{players}, p_e, k)$\;
-        $\text{result noisy probabilistic ending}$ $\gets$ Axelrod.tournament$(\text{players}, p_n, p_e, k)$\;
-
-    }
-    \KwRet{result standard, result noisy, result probabilistic ending,
-    result noisy probabilistic ending}\;
-    \caption{Tournament Data Collection Algorithm}
-    \label{algorithm:data_generation}
-\end{algorithm}
+tournament, such as its rank, cooperation rate, time spent in each state when
+only a single past round is considered, and the probability of cooperating after
+each of the four possible outcomes of the previous round. In our analysis, we
+will use the measures for each strategy provided in the summary, as well as
+additional measures we calculated. Namely, these include the SSE error, the
+average, median, maximum, and minimum cooperation rates in each tournament. The
+SSE (introduced in~\cite{Knight2024}) shows how closely a strategy behaves as a
+zero-determinant strategy and subsequently in an extortionate way. We also
+consider how each strategy's cooperation rate \(C_r\) compares to those of the
+tournament as a whole, for example, by comparing \(C_r\) to \(C_{\text{max}}\).
 
 \newcolumntype{g}{>{\columncolor{Gray}}c}
-\begin{table}[t]
+\begin{table}[b]
     \begin{center}
@@
 \end{table}
+
+\begin{algorithm}[!htbp]
+    \setstretch{1.35}
+    \For{\text{seed} $\in [0, 11420]$}{
+        $N \gets \text{randomly select integer}\in [3, 195]$\;
+        $\text{players} \gets  \text{randomly select $N$ players}$\;
+        $k \gets  \text{randomly select integer}\in [10, 100]$\;
+        $n \gets  \text{randomly select integer}\in [1, 200]$\;
+        $p_n \gets  \text{randomly select float}\in [0, 1]$\;
+        $p_e \gets   \text{randomly select float}\in [0, 1]$\;
+        \vspace{0.4cm}
+        $\text{result standard}$ $\gets$ Axelrod.tournament$(\text{players}, n, k)$\;
+        $\text{result noisy}$ $\gets$ Axelrod.tournament$(\text{players}, n, p_n, k)$\;
+        $\text{result probabilistic ending}$ $\gets$ Axelrod.tournament$(\text{players}, p_e, k)$\;
+        $\text{result noisy probabilistic ending}$ $\gets$ Axelrod.tournament$(\text{players}, p_n, p_e, k)$\;
+
+    }
+    \KwRet{result standard, result noisy, result probabilistic ending,
+    result noisy probabilistic ending}\;
+    \caption{Tournament Data Collection Algorithm}
+    \label{algorithm:data_generation}
+\end{algorithm}
 
@@
 \caption{\textbf{Correlations between the features of Table~\ref{table:manual_features}
-and the normalised rank and the median score.}
-For each type of tournament, standard, noisy, probabilistic ending, and noisy
-probabilistic ending, we run a correlation analsysif. For each tournament we
-check the correlation between each feature used in our analysis and the normalised
-random and median score. Note that the correlation coefficients are calculated
-using the Spearman's rank correlation coefficient. A negative value
-indicates a negative correlation and in the case of the normalised rank
-a smaller rank translats to better position in the tournament.}\label{table:correlations}
+and the normalised rank and the median score.} For each type of
+tournament, standard, noisy, probabilistic ending, and noisy probabilistic
+ending, we conduct a correlation analysis. For each tournament, we check the
+correlation between each feature used in our analysis and the normalized random
+and median scores. Note that the correlation coefficients are calculated using
+Spearman's rank correlation coefficient. A negative value indicates a negative
+correlation, and in the case of the normalized rank, a smaller rank translates
+to a better position in the tournament.}\label{table:correlations}
 \end{table}
@@
 well-known in the AI/ML literature, adding noise to training data leads to more
-robust models. We see that clearly here, where the strategies trained for noise
+robust models~\cite{Bishop1995}. We see that clearly here, where the strategies trained for noise
 (or designed for noise) tend to be better generalists. There were instances

### 2025-07-28 Reply/Point-by-Point-Reply.md
Submission cb (#38)
* drafts sections Data Collection and Top Ranked Strategies

* working on main paper for the special issue

* finish off top performance analysis for paper and si

* finish SI section analysis with all data and clean notebooks

The notebooks now include code to run the analysis for both the
main paper and the SI

* last corrections to the paper and commit si

* commit new notebooks

* Some copy edits for special issue version (#34)

* Update main.tex

* Update regression_table.tex

Fix Typo

* change NG affiliation, note that VK and MH contributed equally + ref style

* add

# Point-by-Point Reply

First, we would like to thank the editor and reviewers for their valuable
feedback. Their comments have been helpful and constructive, and we have
revised our manuscript accordingly. In particular, we have made the following
changes:

- Motivated by a comment from Reviewer #1, we have expanded the discussion to
  include further work and revised the introduction to address why such a study
  was not feasible until now.

- Reviewer #1 suggested adding more detail about the Axelrod-Python packages. We
  have included additional explanations to clarify this aspect of our work.

- As suggested by Reviewer #1, we have added references to relevant statements
  throughout the manuscript.

- In line with Reviewer #1's suggestion, we have enriched the captions to
  provide more details for each figure.

- Reviewer #2's comments, we have clarified the measures in the main text, which
  were previously only explained in the figure captions.

# Editor Remarks to Author:

Comment: Thank you very much for submitting your manuscript "Properties of Winning
Iterated Prisoner's Dilemma Strategies" for consideration at PLOS Computational
Biology. As with all papers reviewed by the journal, your manuscript was
reviewed by members of the editorial board and by several independent reviewers.
The reviewers appreciated the attention to an important topic. Based on the
reviews, we are likely to accept this manuscript for publication, providing that
you modify the manuscript according to the review recommendations.

Reply: Thank you for considering our paper and for providing positive feedback.
The reviewers’ comments have been very helpful.  Please find all details aboutx
how we addressed each comment raised by the reiweres in our response to the
reviewers below.

# Reviewer 1

Comment: Summary: This paper explores the performance of strategies in the IPD.
This research analyses 195 strategies across thousands of computer tournaments,
examining what makes certain strategies more successful in diverse IPD
environments. The study used four different types of tournaments: Standard
tournaments, Noisy tournaments, Probabilistic ending tournaments and Noisy
probabilistic ending tournaments. They find that no single strategy excels in
all settings. However, several key traits appear in successful strategies,
particularly the ability to adjust to the environment and population dynamics.

Thanks for this submission, I find the text easy to read and all the concepts
well explained.

Reply: Thank you for carefully reading our manuscript, and for the constructive
feedback below.

---

Comment: This seems like a low-hanging fruit idea for someone like
Axelrod-Python. If they have all of these strategies, what is the best, after
all, they maintain and add new strategies to the library, why do you think this
hasn't been done before? I feel the data analysis and the interpretation is
sound, but maybe can you add other efforts to do the same, and what do you do
differently?

Reply: We agree with the reviewer’s comment that this could be considered a
``low-hanging fruit'' idea for the developers of the Axelrod-Python library. We
understand that the reviewer is asking whether this type of analysis has been
done before; if so, what did we do differently?

To start, we would like to emphasize that this analysis would not have been
feasible before the development of the Axelrod-Python library. Previously,
researchers would have needed to locate, understand, and implement code for each
strategy from the literature in order to conduct a large-scale tournament.
Additionally, they would have had to develop all the necessary code to manage
the tournament, a challenging task for any researcher. The creation of the
Axelrod-Python package has made such an analysis feasible. This package is the
result of a collaborative effort that has produced a substantial database of
strategies from the literature. We would also like to highlight that the
library’s open-source nature has encouraged contributions from a broad user
base.

Since the package’s development, we believe the reasons for limited
comprehensive analyses are rooted in field conventions. In our field,
tournaments or evolutionary dynamics often rely on a select list of hand picked
strategies chosen by modelers, typically based on specific properties they wish
to examine. This practice may stem from certain misconceptions, such as the
assumption that because Tit-for-Tat performs relatively well, testing against
only Tit-for-Tat variants is sufficient. Another misconception may arise from
the Press & Dyson result, which suggests that lower memory strategies will
always dominate in pairwise interactions, leading some researchers to consider
only memory-one strategies. However, this result strictly applies only to
pairwise interactions.

We did find one example where the setup of the tournament itself was questioned.
Specifically, in Is Tit-for-Tat the Answer? On the Conclusions Drawn from
Axelrod's Tournaments (Rapoport, 2015), Rapoport examined the effects of
variations in format, objective criteria, and payoff values on tournament
outcomes. However, their study analyzed different effects than ours and used a
single tournament setup with a specific selection of strategies. They focused on
Axelrod’s original tournament and demonstrated how certain changes affected the
outcome. For example, including strategies like the “kingmakers” positively
impacted the performance of Tit For Tat.

Changes: We have updated the introduction to clearly state why such an analysis
has not been done before, and we discuss the work of Rapoport (2015).

---

Comment: You mention somewhere that there are evolutionary approaches to
this, specifically evolutionary game theory approaches. Maybe adding why you
chose to do computer simulations instead? (I know that EGT has some constraints,
but highlight why you do how you do it to overcome those constraints).

Reply: Excellent observation. Many strategies, such as Win-Stay-Lose-Shift
and Generous Tit For Tat, emerged due to their strong performance in
evolutionary dynamics. Axelrod's original work involved computer tournaments, so
we chose to remain consistent with this approach since this comprehensive study
had not yet been undertaken.

Moreover, in evolutionary dynamics, there are several factors to consider, such
as which evolutionary process to apply and the high computational cost. However,
it remains an interesting question. For example, we could consider strategy
performance in terms of fixation probabilities in the case of low mutation
rates. This is future work we would be eager to pursue.

Changes: We've added a paragraph to the discussion section outlining
potential extensions into evolutionary dynamics.

---

Comment: I don't know if it's enough to say that you used Axelrod-Python,
but maybe also add how these tournaments are performed? I haven't used the tool,
so I don't know how they simulate those exactly. I feel the library itself is
central to how the results are generated, so maybe expand a bit on that.

Reply: Thank you for this suggestion. We agree that many readers may not be
familiar with the Axelrod-Python package.

Changes: We've expanded the methodology section to include more details on how
to run tournaments using the Axelrod library. We have included a figure showing
a code example of how to run such a tournament.

---

Comment: Check for references when you make statements.

Reply: We thank the reviewer for this comment.

Changes: We have added references to the sentences indicated by the reviewer
and in addition the following sentences:

- "Speciﬁcally, much like the recognized value of diversity in training datasets, such as variations in image perspective,..."

- "Already well-known in the AI/ML literature, adding noise to training data
  leads to more robust models"

---

Comment: I believe it's a matter of style, but I prefer if figures are
self-explanatory. As you did with Figure 1, where you guide the reader through
what is shown, Table 4 and Figures 3,4 and 5 lack some context in the figure
labels, especially in figures like 5, some guidance is appreciated.

Reply: We agree that figures should be self-explanatory.

Changes: We have included additional details in the figures and tables that were
previously missing. These were Table 4 and Figures 3, 4, and 5 (now Figures 4,
5, and 6).

---

# Reviewer 2

Comment: The authors uncover properties of winning strategies in the iterated
Prisoner’s Dilemma (IPD), one of the most renowned paradigms for studying
cooperation over the past decades. They consider a large collection of 195
strategies in thousands of computer tournaments and conduct a thorough analysis
of their performance. Their conclusions refine the properties described by
Axelrod: a successful strategy needs to be nice, provocable, generous, somewhat
envious, clever, and adaptable to the environment.

There are several aspects of this work that I appreciate greatly. First, the
inclusiveness of the study design is commendable: it not only includes all kinds
of strategies from IPD literature but also incorporates variations in the
tournaments (such as random noise and match length). Second, their findings
challenge some of Axelrod’s suggestions, particularly the advice to “not be
clever” and “not be envious.” Additionally, I find the property of being
adaptable to the environment—explained by the authors as a strategy’s
cooperation rate compared to the average cooperation rate in a tournament—very
inspiring.

Reply: Thank you for your comprehensive summary of our work! We appreciate the
comments.

---

Comment: On page 8, I suggest including the explanations for C_max,
C_median, C_mean, and SSE error in the main text, as they currently seem to be
defined only in figures and tables.

Reply: Thank you for this suggestion. These measures should indeed be
explained in the main text as well.

Changes: We have included explanations of each measure in the main text, in
section "Model".

---

Comment:  In Table 3 on page 9, there is a contradiction between "A
strategy's cooperating rate divided by the minimum" and "C_min/C_r."

Reply: Correct. That is a typo. We have addressed this.

---

Comment: On page 13, the sentence "envious strategies capable of both
exploiting and not their opponents…" appears to be incomplete.

Reply: This is indeed correct; the sentence is incomplete. The sentence should
read: ``We also showed that while the type of exploitation attempted by ZDs is
not typically effective in standard tournaments, envious strategies capable of
both exploiting and not their opponents can be highly successful''.

### 2025-07-28 paper/main.tex
Submission cb (#38)
* drafts sections Data Collection and Top Ranked Strategies

* working on main paper for the special issue

* finish off top performance analysis for paper and si

* finish SI section analysis with all data and clean notebooks

The notebooks now include code to run the analysis for both the
main paper and the SI

* last corrections to the paper and commit si

* commit new notebooks

* Some copy edits for special issue version (#34)

* Update main.tex

* Update regression_table.tex

Fix Typo

* change NG affiliation, note that VK and MH contributed equally + ref style

* add

@@
 our analysis are drawn from well-known and named strategies in \IPD{}
-literature, including previous tournament winners. This contrasts with other
-work that may have randomly generated essentially arbitrary strategies, often
-constrained to specific classes such as memory-one strategies or those of a
+literature, including previous tournament winners.
+This contrasts with other work that is often constrained to specific classes such as 
+as memory-one strategies or those of a
 certain structural form like finite state machines or deterministic memory-two
@@
 
-Similarly, our results could suggest an explanation regarding the intuitively
-unexpected effectiveness of memory-one strategies historically. Given that among
-the important features associated with success are the relative cooperation rate
-to the population average and the four memory-one probabilities of cooperating
-conditional on the previous round of play, these features can be optimized by a
-memory-one strategy such as \TFT. Usage of more history becomes valuable when
-there are exploitable opponent patterns. This is indicated by the importance of
-SSE as a feature, showing that the first-approximation provided by a memory-one
-strategy is no longer sufficient.
-These results highlight a central idea in evolutionary game theory in this
-context: the fitness landscape is a function of the population (where fitness in
-this case is tournament performance). While that may seem obvious now, it shows
-why historical tournament results on small or arbitrary populations of
-strategies have so often failed to produce generalizable results.
+Our results may also help explain the historically unexpected effectiveness of
+memory-one strategies~\cite{Camerer2011}. The success of these strategies
+contradicts the intuitive assumption that a longer memory and therefore more
+information would yield better strategic performance~\cite{Binmore1987}. Given
+that among the important features associated with success are the relative
+cooperation rate to the population average and the four memory-one probabilities
+of cooperating conditional on the previous round of play, these features can be
+optimized by a memory-one strategy such as \TFT. Usage of more history becomes
+valuable when there are exploitable opponent patterns. This is indicated by the
+importance of SSE as a feature, showing that the first-approximation provided by
+a memory-one strategy is no longer sufficient. These results highlight a central
+idea in evolutionary game theory in this context: the fitness landscape is a
+function of the population (where fitness in this case is tournament
+performance)~\cite{Hofbauer2003}. While that may seem obvious now, it shows why
+historical tournament results on small or arbitrary populations of strategies
+have so often failed to produce generalizable results.
 
@@
 
-The raw and processed datasets have been made publicly available~\cite{data,
-raw_data} and can be used for further analysis and insights.
+The raw and processed datasets have been made publicly available~\cite{raw_data, data}
+and can be used for further analysis and insights.
 

### 2025-07-28 paper/perfomances_table_full_dataset.tex
Submission cb (#38)
* drafts sections Data Collection and Top Ranked Strategies

* working on main paper for the special issue

* finish off top performance analysis for paper and si

* finish SI section analysis with all data and clean notebooks

The notebooks now include code to run the analysis for both the
main paper and the SI

* last corrections to the paper and commit si

* commit new notebooks

* Some copy edits for special issue version (#34)

* Update main.tex

* Update regression_table.tex

Fix Typo

* change NG affiliation, note that VK and MH contributed equally + ref style

* add

\begin{tabular}{lllllllllllll}
\toprule
{} &                     Name & \$\textbackslash bar\{r\}\$ &                   Name & \$\textbackslash bar\{r\}\$ &                        Name & \$\textbackslash bar\{r\}\$ &               Name & \$\textbackslash bar\{r\}\$ &                       Name & \$\textbackslash bar\{r\}\$ &                 Name & \$\textbackslash bar\{r\}\$ \\
\midrule
0  &            Evolved HMM 5 &     0.007 &                 Grumpy &      0.14 &                         DBS &       0.0 &          Fortress4 &     0.013 &             Evolved FSM 16 &       0.0 &           Alternator &     0.304 \\
1  &           Evolved FSM 16 &      0.01 &                    \$e\$ &      0.19 &     Evolved FSM 16 Noise 05 &     0.008 &           Defector &     0.014 &    Evolved FSM 16 Noise 05 &     0.013 &               \$\textbackslash phi\$ &      0.31 \\
2  &     EvolvedLookerUp2\_2\_2 &     0.011 &         Tit For 2 Tats &     0.206 &      Evolved ANN 5 Noise 05 &     0.013 &  Better and Better &     0.016 &                       MEM2 &     0.027 &                  \$e\$ &     0.312 \\
3  &  Evolved FSM 16 Noise 05 &     0.017 &  Slow Tit For Two Tats &      0.21 &                 BackStabber &     0.024 &    Tricky Defector &     0.019 &              Evolved HMM 5 &     0.043 &                \$\textbackslash pi\$ &     0.317 \\
4  &        PSO Gambler 2\_2\_2 &     0.022 &           Cycle Hunter &     0.215 &               DoubleCrosser &     0.025 &          Fortress3 &     0.022 &       EvolvedLookerUp2\_2\_2 &     0.049 &    Limited Retaliate &     0.353 \\
5  &              Evolved ANN &     0.029 &         Risky QLearner &     0.222 &               Evolved ANN 5 &     0.028 &     Gradual Killer &     0.025 &       Spiteful Tit For Tat &     0.059 &     Anti Tit For Tat &     0.354 \\
6  &            Evolved ANN 5 &     0.034 &          Cycler CCCCCD &     0.229 &                 Evolved ANN &     0.038 &         Aggravater &     0.028 &           Nice Meta Winner &     0.069 &  Limited Retaliate 3 &     0.356 \\
7  &        PSO Gambler 1\_1\_1 &     0.037 &            Retaliate 3 &      0.23 &        Spiteful Tit For Tat &     0.051 &             Raider &     0.031 &         NMWE Finite Memory &     0.069 &          Retaliate 3 &     0.356 \\
8  &            Evolved FSM 4 &     0.049 &            Retaliate 2 &     0.239 &               Evolved HMM 5 &     0.051 &         Cycler DDC &     0.045 &         NMWE Deterministic &      0.07 &            Retaliate &     0.357 \\
9  &         PSO Gambler Mem1 &      0.05 &        Defector Hunter &      0.24 &              Level Punisher &     0.052 &        Hard Prober &     0.051 &                    Grudger &      0.07 &          Retaliate 2 &     0.358 \\
10 &                 Winner12 &      0.06 &              Retaliate &     0.242 &                   Omega TFT &     0.059 &         SolutionB1 &      0.06 &           NMWE Long Memory &     0.074 &  Limited Retaliate 2 &     0.361 \\
11 &             Fool Me Once &     0.061 &    Hard Tit For 2 Tats &      0.25 &                Fool Me Once &     0.059 &      Meta Minority &     0.061 &  Nice Meta Winner Ensemble &     0.076 &             Hopeless &     0.368 \\
12 &                      DBS &     0.071 &      Arrogant QLearner &      0.25 &  PSO Gambler 2\_2\_2 Noise 05 &     0.067 &              Bully &     0.061 &       EvolvedLookerUp1\_1\_1 &     0.077 &    Arrogant QLearner &     0.406 \\
13 &            DoubleCrosser &     0.072 &    Limited Retaliate 3 &     0.253 &              Evolved FSM 16 &     0.078 &             EasyGo &     0.071 &            NMWE Memory One &      0.08 &    Cautious QLearner &     0.409 \\
14 &              BackStabber &     0.075 &               ShortMem &     0.253 &                  EugineNier &      0.08 &    Fool Me Forever &     0.071 &            NMWE Stochastic &     0.085 &      Fool Me Forever &     0.418 \\
\bottomrule
\end{tabular}

### 2025-07-28 paper/regression_on_median_score.tex
Submission cb (#38)
* drafts sections Data Collection and Top Ranked Strategies

* working on main paper for the special issue

* finish off top performance analysis for paper and si

* finish SI section analysis with all data and clean notebooks

The notebooks now include code to run the analysis for both the
main paper and the SI

* last corrections to the paper and commit si

* commit new notebooks

* Some copy edits for special issue version (#34)

* Update main.tex

* Update regression_table.tex

Fix Typo

* change NG affiliation, note that VK and MH contributed equally + ref style

* add

@@
 
-A multivariate linear regression has also been fitted to model the relationship between
-the features and the median score. The features included are given
-by Table~\ref{table:linear_regression_on_median} alongside their corresponding \(p\) values
-in the distinct tournaments and their regression coefficients.
+A multivariate linear regression has also been fitted to model the relationship
+between the features and the median score. The features included are given in
+Table~\ref{table:linear_regression_on_median} alongside their corresponding
+\(p\) values in distinct tournaments and their regression coefficients.
+Table~\ref{table:linear_regression_on_median} provides the results when
+considering tournaments with \(p_n \leq 0.1\) and \(p_e \leq 0.1\). The results
+when the probabilities are not constrained are given in
+Table~\ref{table:linear_regression_on_median_full_dataset}.
 
 \newcolumntype{g}{>{\columncolor{Gray}}c}
-\begin{table}[h]
+\begin{table}[!htbp]
     \begin{center}
-\resizebox{\textwidth}{!}{
+\resizebox{.8\textwidth}{!}{
 \begin{tabular}{lggccggccgg}
     \toprule
-    & \multicolumn{2}{g}{Standard} & \multicolumn{2}{c}{Noisy} & \multicolumn{2}{g}{Probabilistic ending} & \multicolumn{2}{c}{Noisy probabilistic ending} & \multicolumn{2}{g}{Overall}\\
+    & \multicolumn{2}{g}{Standard} & \multicolumn{2}{c}{Noisy} & \multicolumn{2}{g}{Probabilistic ending} & \multicolumn{2}{c}{Noisy probabilistic ending}\\
     \midrule
-    & \multicolumn{2}{g}{\(R\) adjusted: 0.576} & \multicolumn{2}{c}{\(R\) adjusted: 0.679} & \multicolumn{2}{g}{\(R\) adjusted: 0.816} & \multicolumn{2}{c}{\(R\) adjusted: 0.930} & \multicolumn{2}{g}{\(R\) adjusted: 0.318} \\
-    {} &  Coefficient &  \(p\)-value &  Coefficient &  \(p\)-value &  Coefficient &  \(p\)-value &  Coefficient &  \(p\)-value &  Coefficient &  \(p\)-value \\
+    & \multicolumn{2}{g}{\(R\) adjusted: 0.576} & \multicolumn{2}{c}{\(R\) adjusted: 0.561} & \multicolumn{2}{g}{\(R\) adjusted: 0.488} & \multicolumn{2}{c}{\(R\) adjusted: 0.762}\\
+    {} &  Coefficient &  \(p\)-value &  Coefficient &  \(p\)-value &  Coefficient &  \(p\)-value &  Coefficient &  \(p\)-value \\
     \midrule
-    $CC$ to $C$ rate   &  0.043 &  0.000 & -0.380 &  0.000 &  0.224 &  0.000 &  0.078 &    0.0 &  0.308 &    0.0 \\
-    $CD$ to $C$ rate   & -0.325 &  0.000 &  0.124 &  0.000 &  0.060 &  0.000 &  0.073 &    0.0 & -0.014 &    0.0 \\
-    $C_r$ / $C_{max}$  &      - &      - & -1.044 &  0.000 &      - &      - & -1.251 &    0.0 &      - &      - \\
-    $C_r$ / $C_{mean}$ &  0.553 &  0.000 & -0.101 &  0.000 & -1.136 &  0.000 & -0.089 &    0.0 & -0.665 &    0.0 \\
-    $C_{max}$          &  0.059 &  0.000 &      - &      - & -0.044 &  0.086 & -1.396 &    0.0 &      - &      - \\
-    $C_{mean}$         &  1.837 &  0.000 &  3.078 &  0.000 &  1.506 &  0.000 &  3.645 &    0.0 &      - &      - \\
-    $C_{min}$          &  0.156 &  0.000 &  1.528 &  0.000 &  0.311 &  0.000 &      - &      - &      - &      - \\
-    $C_{min}$ / $C_r$  & -0.049 &  0.000 & -0.378 &  0.000 & -0.204 &  0.000 &      - &      - & -0.257 &    0.0 \\
-    $DC$ to $C$ rate   & -0.204 &  0.000 &  0.074 &  0.000 &  0.066 &  0.000 &  0.066 &    0.0 &  0.007 &    0.0 \\
-    $k$                & -0.000 &  0.853 & -0.000 &  0.987 &  0.000 &  0.008 &  0.000 &    0.0 &      - &      - \\
-    $n$                & -0.000 &  0.000 &      - &      - &      - &      - &      - &      - &      - &      - \\
-    $p_e$              &      - &      - &      - &      - &  0.025 &  0.000 & -0.095 &    0.0 &      - &      - \\
-    $p_n$              &      - &      - &  0.124 &  0.000 &      - &      - &      - &      - &      - &      - \\
-    SSE                & -0.294 &  0.000 & -0.319 &  0.000 &  0.055 &  0.000 &  0.010 &    0.0 & -0.015 &    0.0 \\
-    constant           &  0.925 &  0.000 &  1.536 &  0.000 &  2.466 &  0.000 &  2.299 &    0.0 &  2.924 &    0.0 \\
-    memory usage       &  0.010 &  0.000 & -0.004 &  0.000 &      - &      - &      - &      - &      - &      - \\
+    constant             &  0.928 &  0.000 &  1.082 &  0.000 &  1.259 &  0.000 &  1.642 &  0.000 \\
+    $CC$ to $C$ rate     &  0.043 &  0.000 &  0.104 &  0.000 &  0.024 &  0.000 & -0.032 &  0.000 \\
+    $CD$ to $C$ rate     & -0.325 &  0.000 & -0.052 &  0.000 & -0.229 &  0.000 & -0.110 &  0.000 \\
+    $DC$ to $C$ rate     & -0.204 &  0.000 & -0.076 &  0.000 & -0.102 &  0.000 & -0.070 &  0.000 \\
+    SSE                  & -0.294 &  0.000 & -0.186 &  0.000 & -0.131 &  0.000 & -0.109 &  0.000 \\
+    $C_{max}$            &  0.056 &  0.000 & -0.060 &  0.011 & -0.005 &  0.849 & -0.240 &  0.000 \\
+    $C_{min}$            &  0.156 &  0.000 & -0.159 &  0.000 &  0.012 &  0.385 &  0.083 &  0.005 \\
+    $C_{mean}$           &  1.838 &  0.000 &  2.247 &  0.000 &  1.822 &  0.000 &  2.030 &  0.000 \\
+    $C_{min}$ / $C_r$    & -0.049 &  0.000 &  0.040 &  0.000 & -0.018 &  0.000 & -0.065 &  0.000 \\
+    $C_r$ / $C_{mean}$   &  0.552 &  0.000 & -0.227 &  0.000 &  0.027 &  0.125 & -0.043 &  0.000 \\
+    $k$                  & -0.000 &  0.856 & -0.000 &  0.245 & -0.000 &  0.610 & -0.000 &  0.572 \\
+    $n$                  & -0.000 &  0.000 &      - &      - &      - &      - &      - &      - \\
+    memory usage         &  0.010 &  0.000 &  0.004 &  0.000 &      - &      - &      - &      - \\
+    $C_r$ / $C_{median}$ &      - &      - &  0.252 &  0.000 &  0.181 &  0.000 &      - &      - \\
+    $p_n$                &      - &      - &  0.770 &  0.000 &      - &      - &  0.494 &  0.000 \\
+    $p_e$                &      - &      - &      - &      - &  0.763 &  0.000 &  0.285 &  0.000 \\
+    \bottomrule
+\end{tabular}}
+\end{center}
+\caption{Results of multivariate linear regressions with the median score as the dependent variable.
+\(R\) squared is reported for each model. For noisy tournaments $p_n \leq 0.1$
+and for probabilistic ending tournaments $p_e \leq 0.1$.}
+\label{table:linear_regression_on_median}
+\end{table}
+
+\newcolumntype{g}{>{\columncolor{Gray}}c}
+\begin{table}[!htbp]
+    \begin{center}
+\resizebox{.8\textwidth}{!}{
+\begin{tabular}{lggccggccgg}
+    \toprule
+    & \multicolumn{2}{g}{Standard} & \multicolumn{2}{c}{Noisy} & \multicolumn{2}{g}{Probabilistic ending} & \multicolumn{2}{c}{Noisy probabilistic ending}\\
+    \midrule
+    & \multicolumn{2}{g}{\(R\) adjusted: 0.575} & \multicolumn{2}{c}{\(R\) adjusted: 0.666} & \multicolumn{2}{g}{\(R\) adjusted: 0.816} & \multicolumn{2}{c}{\(R\) adjusted: 0.869} \\
+    {} &  Coefficient &  \(p\)-value &  Coefficient &  \(p\)-value &  Coefficient &  \(p\)-value &  Coefficient &  \(p\)-value\\
+    \midrule
+    constant           &  0.928 &  0.000 &  2.143 &  0.000 &  2.466 &  0.000 &  1.824 &  0.000 \\
+    $CC$ to $C$ rate   &  0.043 &  0.000 & -0.468 &  0.000 &  0.223 &  0.000 & -0.008 &  0.000 \\
+    $CD$ to $C$ rate   & -0.325 &  0.000 &  0.105 &  0.000 &  0.060 &  0.000 &  0.074 &  0.000 \\
+    $DC$ to $C$ rate   & -0.204 &  0.000 &  0.060 &  0.000 &  0.066 &  0.000 & -0.002 &  0.011 \\
+    SSE                & -0.294 &  0.000 & -0.365 &  0.000 &  0.055 &  0.000 & -0.035 &  0.000 \\
+    $C_{max}$          &  0.056 &  0.000 &      - &      - & -0.045 &  0.081 & -0.181 &  0.000 \\
+    $C_{min}$          &  0.156 &  0.000 &  0.264 &  0.000 &  0.311 &  0.000 &      - &      - \\
+    $C_{mean}$         &  1.838 &  0.000 &  2.046 &  0.000 &  1.506 &  0.000 &  2.273 &  0.000 \\
+    $C_{min}$ / $C_r$  & -0.049 &  0.000 & -0.252 &  0.000 & -0.204 &  0.000 &      - &      - \\
+    $C_r$ / $C_{mean}$ &  0.552 &  0.000 & -0.579 &  0.000 & -1.137 &  0.000 & -0.610 &  0.000 \\
+    $k$                & -0.000 &  0.856 &  0.000 &  0.788 &  0.000 &  0.009 &  0.000 &  0.005 \\
+    $n$                & -0.000 &  0.000 &      - &      - &      - &      - &      - &      - \\
+    memory usage       &  0.010 &  0.000 & -0.006 &  0.000 &      - &      - &      - &      - \\
+    $p_n$              &      - &      - &  0.119 &  0.000 &      - &      - &      - &      - \\
+    $p_e$              &      - &      - &      - &      - &  0.025 &  0.000 & -0.028 &  0.000 \\
     \bottomrule
@@
 \(R\) squared is reported for each model.}
-\label{table:linear_regression_on_median}
+\label{table:linear_regression_on_median_full_dataset}
 \end{table}

### 2025-07-28 paper/top_perfomances_full_data_set.tex
Submission cb (#38)
* drafts sections Data Collection and Top Ranked Strategies

* working on main paper for the special issue

* finish off top performance analysis for paper and si

* finish SI section analysis with all data and clean notebooks

The notebooks now include code to run the analysis for both the
main paper and the SI

* last corrections to the paper and commit si

* commit new notebooks

* Some copy edits for special issue version (#34)

* Update main.tex

* Update regression_table.tex

Fix Typo

* change NG affiliation, note that VK and MH contributed equally + ref style

* add

\begin{tabular}{lggllggllggllr}
    \toprule
    & \multicolumn{2}{g}{Standard} & \multicolumn{2}{c}{Noisy} &  \multicolumn{2}{g}{Noisy (\(p_n < 0.1\))} & \multicolumn{2}{c}{Probabilistic ending} & \multicolumn{2}{g}{Probabilistic ending (\(p_e < 0.1\))} &  \multicolumn{2}{c}{Noisy probabilistic ending} \\
    \midrule
    & Name & $\bar{r}$ &                 Name & $\bar{r}$ &               Name & $\bar{r}$ &                 Name & $\bar{r}$ &                 Name & $\bar{r}$ &                 Name & $\bar{r}$ \\
    \midrule
    0  &            Evolved HMM 5 &     0.007 &                 Grumpy &      0.14 &                         DBS &       0.0 &          Fortress4 &     0.013 &             Evolved FSM 16 &       0.0 &           Alternator &     0.304 \\
    1  &           Evolved FSM 16 &      0.01 &                    \$e\$ &      0.19 &     Evolved FSM 16 Noise 05 &     0.008 &           Defector &     0.014 &    Evolved FSM 16 Noise 05 &     0.013 &               \$\textbackslash phi\$ &      0.31 \\
    2  &     EvolvedLookerUp2\_2\_2 &     0.011 &         Tit For 2 Tats &     0.206 &      Evolved ANN 5 Noise 05 &     0.013 &  Better and Better &     0.016 &                       MEM2 &     0.027 &                  \$e\$ &     0.312 \\
    3  &  Evolved FSM 16 Noise 05 &     0.017 &  Slow Tit For Two Tats &      0.21 &                 BackStabber &     0.024 &    Tricky Defector &     0.019 &              Evolved HMM 5 &     0.043 &                \$\textbackslash pi\$ &     0.317 \\
    4  &        PSO Gambler 2\_2\_2 &     0.022 &           Cycle Hunter &     0.215 &               DoubleCrosser &     0.025 &          Fortress3 &     0.022 &       EvolvedLookerUp2\_2\_2 &     0.049 &    Limited Retaliate &     0.353 \\
    5  &              Evolved ANN &     0.029 &         Risky QLearner &     0.222 &               Evolved ANN 5 &     0.028 &     Gradual Killer &     0.025 &       Spiteful Tit For Tat &     0.059 &     Anti Tit For Tat &     0.354 \\
    6  &            Evolved ANN 5 &     0.034 &          Cycler CCCCCD &     0.229 &                 Evolved ANN &     0.038 &         Aggravater &     0.028 &           Nice Meta Winner &     0.069 &  Limited Retaliate 3 &     0.356 \\
    7  &        PSO Gambler 1\_1\_1 &     0.037 &            Retaliate 3 &      0.23 &        Spiteful Tit For Tat &     0.051 &             Raider &     0.031 &         NMWE Finite Memory &     0.069 &          Retaliate 3 &     0.356 \\
    8  &            Evolved FSM 4 &     0.049 &            Retaliate 2 &     0.239 &               Evolved HMM 5 &     0.051 &         Cycler DDC &     0.045 &         NMWE Deterministic &      0.07 &            Retaliate &     0.357 \\
    9  &         PSO Gambler Mem1 &      0.05 &        Defector Hunter &      0.24 &              Level Punisher &     0.052 &        Hard Prober &     0.051 &                    Grudger &      0.07 &          Retaliate 2 &     0.358 \\
    10 &                 Winner12 &      0.06 &              Retaliate &     0.242 &                   Omega TFT &     0.059 &         SolutionB1 &      0.06 &           NMWE Long Memory &     0.074 &  Limited Retaliate 2 &     0.361 \\
    11 &             Fool Me Once &     0.061 &    Hard Tit For 2 Tats &      0.25 &                Fool Me Once &     0.059 &      Meta Minority &     0.061 &  Nice Meta Winner Ensemble &     0.076 &             Hopeless &     0.368 \\
    12 &                      DBS &     0.071 &      Arrogant QLearner &      0.25 &  PSO Gambler 2\_2\_2 Noise 05 &     0.067 &              Bully &     0.061 &       EvolvedLookerUp1\_1\_1 &     0.077 &    Arrogant QLearner &     0.406 \\
    13 &            DoubleCrosser &     0.072 &    Limited Retaliate 3 &     0.253 &              Evolved FSM 16 &     0.078 &             EasyGo &     0.071 &            NMWE Memory One &      0.08 &    Cautious QLearner &     0.409 \\
    14 &              BackStabber &     0.075 &               ShortMem &     0.253 &                  EugineNier &      0.08 &    Fool Me Forever &     0.071 &            NMWE Stochastic &     0.085 &      Fool Me Forever &     0.418 \\
    \bottomrule
    \end{tabular}
